
\section{Experiment}
\label{section: experiment}

%\input{tables/CompareSOTA.tex}
Building upon the LEGO-GraphRAG framework, we develop an implementation that facilitates the seamless integration of modules and methods for constructing GraphRAG instances.\footnote{Our implementation is built in Python and integrates libraries such as Transformers {\cite{transformers}}, iGraph {\cite{iGraph}}, PyTorch{\cite{PyTorch}}, and vLLM {\cite{vLLM}} to support flexible configuration of algorithms, models, and reasoning. The semantic models used are publicly available on the Hugging Face {\cite{huggingfaceHuggingFace}}.}
To assess the effectiveness of the LEGO-GraphRAG framework and our implementation, we create versions of our framework based on the core ideas of three state-of-the-art instances—RoG~\cite{RoG}, KELP~\cite{ref:kelp}, and ToG~\cite{ToG}—and align the experimental setups to ensure a fair comparison. As shown in Table~\ref{table:CompareSOTA}, the instances implemented within our framework exhibit performance comparable to their original counterparts across two datasets. %Notably, 
For KELP, our implementation outperforms the original due to the effective integration of two modules and the optimization of the employed methods.


As shown in Table~\ref{tab:flat_table}, the existing instances are far from covering the four groups of GraphRAG instances within our framework. Thus, we construct {\InstanceNum} distinct GraphRAG instances (numbered and labeled in Table~\ref{tab:flat_table}) by selecting representative methods from {\preRetrieval} and {\retrieval} modules for a detailed empirical study (Section~\ref{exp:instance}). In addition, we conduct separate evaluations of the various methods, strategies, and semantic models utilized in the two modules (Sections~\ref{exp:PreRetrieval} and~\ref{exp:Retrieval}). 




%We implement {\ourmethod} system using Transformers, iGraph, PytTorch and vLLM, which contains 5 layers, which is detailed in Appendix~\ref{system implementations}.
%By modifying the configuration settings of our {\ourmethod} system, users can create tailored instances to suit various applications. For example, in Table~\ref{table:CompareSOTA}, we demonstrate the implementation of modules aligned with state-of-the-art GraphRAG methods and conduct comparative experiments on WebQSP and CWQ datasets. The results highlight the competitive performance of our LEGO-GraphRAG system, showcasing its flexibility and utility. Based on this, in order to carry out a further comprehensive and well-developed study, we combined the solutions of the two modules Table~\ref{tab:flat_table}, constructing {\InstanceNum} distinct GraphRAG instances by selecting representative methods for the {\preRetrieval} and {\Retrieval} modules, as shown in Table~\ref{tab:flat_table}. 
%The specific choices within each method category are based on the trade-off between efficiency and quality, as discussed in detail in Section~\ref{exp:PreRetrieval} and \ref{exp:Retrieval}.
\input{tables/CompareSOTA.tex}

\subsection{Experiment Settings}



%\textbf{Graph and GraphRAG Query Datasets.} 
%{\color{blue}
%This study leverages Freebase~\cite{Freebase}, a large-scale and comprehensive knowledge graph database widely utilized in GraphRAG research~\cite{StructGPT,UniKGQA,KD-CoT,DecAF,RoG,ToG,GNN-RAG,ChatKBQA,GCR,LessIsMore}. 
%Furthermore, we utilized four acknowledged GraphRAG query datasets from Freebase—WebQSP~\cite{webqsp}, CWQ~\cite{CWQ}, GrailQA~\cite{GrailQA}, and WebQuestions~\cite{WebQuestions}—which provide diverse and challenging scenarios for reasoning tasks and are widely used within the GraphRAG community~\cite{StructGPT, RoG, ToG2.0, LessIsMore, GCR, GNN-RAG, DoG}.

%For each dataset, we adhere to established settings~\cite{NSM,ToG,UniKGQA,RoG} to construct dataset-specific graphs, including all triples reachable within the maximum reasoning hops from the question entities, resulting in approximately 100 million nodes and 300 million edges.To balance the evaluation dataset, we randomly selected 1,000 test queries from each of the four GraphRAG query datasets, totaling 4,000 queries, with a 1:1 ratio of simple (one-hop) queries to complex (two-hop and multi-hop) queries.All our experiments (Sections 4.2-4.4) are conducted based on this evaluation dataset.Details of the graphs and datasets are presented in supplemental material.}

\textbf{Graph and GraphRAG Query Datasets.} 
We leverage Freebase~\cite{Freebase}, a large-scale, multi-domain knowledge base (e.g., on finance, law, sports) widely used in GraphRAG research~\cite{StructGPT,UniKGQA,KD-CoT,DecAF,RoG,ToG,GNN-RAG,ChatKBQA,GCR,LessIsMore}, along with four established query datasets, WebQSP~\cite{webqsp}, CWQ~\cite{CWQ}, GrailQA~\cite{GrailQA}, and WebQuestions~\cite{UHop}, covering diverse and challenging GraphRAG scenarios.
Following standard settings~\cite{NSM,ToG,UniKGQA,RoG}, we construct dataset-specific graphs, including all triples reachable within the maximum reasoning hops from query entities (100M nodes, 300M edges) and sample 1,000 test queries per dataset (one-hop: multi-hop is 1:1). All experiments (Sections 4.2–4.4) are conducted based on these datasets.
%, yielding approximately 100 million nodes and 300 million edges. We randomly sample 1,000 test queries per dataset, totaling 4,000 queries, with a 1:1 ratio of one-hop and multi-hop queries.
We also include MetaQA~\cite{MetaQA}, a non-Freebase dataset built on Wiki-Movies~\cite{ref:wikimovie}, a single-domain base focused on movies (40K nodes, 130K edges), with 1,000 test queries to assess cross-base and cross-domain transferability  of our framework.\footnote{Further details of datasets  are in our technical report B.2 and B.3.} 


%Due to Freebase's immense size, we adhere to established settings~\cite{NSM,ToG,UniKGQA,RoG} to construct dataset-specific subgraphs. These subgraphs include all triples reachable within the maximum reasoning hops from the question entities across the employed datasets, resulting in approximately 100 million nodes and 300 million edges.

%To evaluate \ourmethod, we employ four  GraphRAG Query datasets: WebQSP~\cite{webqsp}, CWQ~\cite{CWQ}, GrailQA~\cite{GrailQA}, and WebQuestions~\cite{WebQuestions}. These datasets are widely recognized in the GraphRAG community~\cite{StructGPT,RoG,ToG2.0,LessIsMore,GCR,GNN-RAG,DoG}, providing diverse and challenging scenarios for reasoning tasks.
%Detailed descriptions of the knowledge graph construction process and dataset characteristics are presented in \textbf{Appendix}~\ref{appendix:datasets}.
\interfootnotelinepenalty=10000

\textbf{Metrics.} Our empirical study is based on three key metrics: quality, efficiency, and cost.
{\it \underline{a) Quality.}} 
%\uwave{{\it a).1 For the subgraph-extraction}}, both Recall and F1 score are critical evaluation metrics
%Recall measures the proportion of relevant entities and relations from the ground truth captured in the extracted subgraph.
%In contrast, the F1 score, which is the harmonic mean of Precision and Recall, tends to favor smaller subgraphs that prioritize Precision, potentially at the expense of Recall, even if they contain fewer relevant entities and relationships. 
%This introduces a trade-off in the evaluation of the subgraph-extraction module, despite achieving high F1 scores, which can impair the performance of the downstream path-retrieval module. Thus, it is essential to set a minimum recall threshold (e.g., typically above 60\%) to guarantee adequate coverage of relevant entities and relationships. Once this threshold is met, the focus can shift to evaluating the F1 score.
\uwave{{\it a).1 For the subgraph-extraction}}, F1 Score serves as the primary evaluation metric, balancing Precision and Recall to reflect overall extraction quality.\footnote{
$
\text{{Precision}} = |\mathbf{C}_q \cap \mathbf{A}_q| / |\mathbf{C}_q|
$,
$
\text{{Recall}} = |\mathbf{C}_q \cap \mathbf{A}_q| / |\mathbf{A}_q|
$,
where \( \mathbf{C}_q \) and \( \mathbf{A}_q \) represent the predicted and ground truth sets, respectively. The F1 score is the harmonic mean of Precision and Recall:
$
\text{F1 score} = (2 \cdot \text{{Precision}} \cdot \text{{Recall}}) / (\text{Precision} + \text{Recall})
$
\label{footnote:f1}
} 
However, since this module directly influences the retrieval space for downstream modules, we introduce a minimum Recall threshold to ensure sufficient coverage of relevant entities and relations. 
Relying solely on high F1 Score may favor Precision at the cost of missing important components.
%alone may lead to subgraphs that prioritize Precision but risk omitting graph components relevant to the query.
In practice, a fixed Recall threshold (e.g., around 60\%) is usually sufficient to ensure downstream performance, after which F1 Score can guide subgraph-extraction.
%. Once this constraint is met, subgraph extraction can be effectively guided by F1 Score.
We also explore adaptive thresholding based on query complexity, graph density, downstream tasks, and historical logs, balancing coverage and efficiency.\footnote{
%These factors reflect trade-offs between ensuring sufficient query coverage and limiting subgraph size and redundancy. 
%For example, multi-hop queries or sparse graph regions may require higher Recall to preserve relevant paths, while dense graph regions or chat-oriented tasks benefit from lower thresholds to reduce computational cost. 
Detailed strategies are available in our technical report B.5. }
\uwave{{\it a).2 For the path-retrieval}}, the F1 score\footref{footnote:f1} measures the alignment between the retrieved reasoning paths and the ground truth answers. For sets containing the same number of reasoning paths, a higher F1 score indicates better quality.
\uwave{{\it a).3 For the GraphRAG instance}}, we adopt Hits@1 as the main evaluation metric, following prior work~\cite{knowledgeaugmented, StructGPT, CoK, KB-BINDER, ToG, ToG2.0}. 
It measures the proportion of outputs that exactly match the ground truth.\footnote{Note the gap between the evaluation of path-retrieval and that of the GraphRAG instance, which arises from the ability of LLMs to  utilize the reasoning paths.} We also report two commonly used complementary metrics—F1 score and LLM-based evaluation. Both show similar trends to Hits@1 across different GraphRAG instances and do not affect our experimental conclusions.\footnote{Detailed results are provided in the technical report B.4.}
\underline{b) Efficiency.} We record the runtime of both modules in the GraphRAG instance per query. %during the execution of a single query.
\underline{c) Cost.} We track token cost and peak GPU memory usage of the GraphRAG instance on EEMs and LLMs, reflecting processing load and computational resource demands, respectively.
%The token cost reflects the amount of text processed, while peak GPU memory usage indicates memory demand, impacting resource efficiency and scalability. 

\textbf{Settings for Graph Instance Experiments.} For GraphRAG instances in this study, we selected methods and semantic models that balance efficiency and quality within their respective categories, based on experiments on subgraph-extraction and path-retrieval modules (Sections~\ref{exp:PreRetrieval} and~\ref{exp:Retrieval}).
To ensure fair comparisons, we adjusted parameters within each instance so that all instances ultimately retrieved the same number of reasoning paths.\footnote{In this paper, we follow prior work {\cite{RoG,GNN-RAG,LessIsMore}} by setting the number of reasoning paths to 32. Note that for instances integrating LLMs in OSAR and ISAR, the number of reasoning paths may be fewer than 32 due to the uncertainty in their outputs.} The key experimental settings are as follows, and detailed settings for each instance are provided in supplemental material:
{\it \underline{a) EEMs\&LLMs.}} A sentence-Transformer (ST)~\cite{MiniLM} and {\qwen{2}{72}}~\cite{qwen2} are employed as the EEMs and LLMs implementations, respectively. Note that for all experiments in this paper, the batch size of EEMs is set to 64 and the max input token of LLMs is set to 16k.
{\it \underline{b) SBE.}} The PPR algorithm is applied, with a maximum of nodes $N_{ppr}=1,000$ retained.
{\it \underline{c) SAE.}} Edge pruning (EP) is used for EEMs and LLMs based on subgraphs extracted by PPR, with a maximum of edges $N_{e}=64$ retained.
{\it \underline{d) SBR.}} The Dijkstra algorithm is employed for SPR implementation.
{\it \underline{e) OSAR.}} Select $N_p=32$ reasoning paths from those retrieved using SPR, leveraging both EEMs and LLMs.
{\it \underline{f) ISAR.}} The Beam Search algorithm is selected for implementation and combined with both EEMs and LLMs. The beam width is set to $B=8$, and the maximum path length retained is $L=4$.
{\it \underline{g) Generation.}} We utilize various LLMs with differing architectures and scales~.\footnote{Glm4-9B~\cite{glm2024chatglm}, \llama{3.3}{70}~\cite{llama3}, \qwen{2}{7} and \qwen{2}{72}~\cite{qwen2}}

%performing path-retrieval module analysis experiments on 3000 subgraphs extracted using 3 typical subgraph extraction methods on 4 datasets, where each dataset consists of 250 subgraphs extracted using the PPR method, subgraphs extracted by edge pruning using EEMs and LLMs. 


\textbf{Settings for Module Experiments.}
%To explore the quality and efficiency of each method of subgraph-extraction and path-retrieval module, 
%we select 250 queries with a balanced distribution of hop on each dataset and choose one representative method of each type in the design solutions for the module analysis experiments, the settings are as follows: 
To evaluate the quality and efficiency of methods in subgraph-extraction and path-retrieval modules, we implement representative methods from each method category, and conduct independent experiments. The settings are as follows:
{\it \underline{a) EEMs\&LLMs Selection.}} A variety of EEMs, including statistical model, embedding model, and reranker, are employed. Specifically, we adopt BM25 as a representative statistical model, a sentence-Transformer (ST)~\cite{MiniLM} as a widely used embedding model, BGE-Reranker (BGE)~\cite{BGE} as an effective re-ranker, and \qwen{2}{72}~\cite{qwen2} as the LLM implementation.

{\it \underline{b) Settings for the Subgraph-Extraction Module.}}
\uwave{{\it b).1 SBE.}} We employ PPR as a structural importance-based method, RW as a random walk-based algorithm, and KSE as a neighborhood-based strategy.
\uwave{{\it b).2 SAE.}} Node Pruning (NP), Edge Pruning (EP), and Triple Pruning (TP) are applied across all selected EEMs and LLMs, based on subgraphs extracted by SBE, with PPR selected due to its superior quality and efficiency in our evaluations.

{\it \underline{c) Settings for the Path-Retrieval Module.}}
We extract 3,000 subgraphs from four evaluation datasets using methods implemented in the subgraph-extraction module. From each dataset, 250 test queries (1,000 total) are sampled, and three subgraphs per query are generated using SBE, SAE-EEM, and SAE-LLM, with the most effective implementations selected based on our experiments. These subgraphs are used to evaluate the methods in the path-retrieval module independently. The settings for each method are as:
\uwave{{\it c).1 SBR.}} The Dijkstra algorithm is employed for SPR, while the DFS algorithm is employed for EPR.
\uwave{{\it c).2 OSAR.}} We use all selected EEMs and LLMs to perform semantic evaluation and refinement on the paths obtained through SPR (a superior SBR method based on our evaluation).
\uwave{{\it c).3 ISAR.}} We combine beam search algorithm (\( B = 8 \) and \( L = 4 \)) with all selected EEMs and LLMs.
%, and the beam width is set to \( B = 8 \), 
