



\begin{comment}
%\input{tables/pipeline.tex}
 \section{{\ourmethod} Implementation}
\label{section: instance}


{\color{red} 
This section presents a detailed description of the LEGO-GraphRAG framework, emphasizing its architectural design and core functionalities, which are pivotal for the seamless integration of knowledge graphs (KGs) with user queries. The framework is systematically structured into distinct layers, each addressing a specific aspect of data processing.

Subsection 1:  System overview 

Subsection 2:  Introduction of each layer

\subsection{System Overview}
\label{subsection: system_overview}

As shown in Figure X, the architecture begins with a \textit{Data Ingestion} layer, which transforms KG data into structured triple formats and standardizes user queries into json representations, encapsulating both questions and its central entities. The subsequent \textit{Preprocessing} layer refines this data by eliminating irrelevant entities and relations, filtering unrelated triples, and constructing a coherent graph structure to enhance downstream reasoning processes. The \textit{Retrieval Modules} then provide a unified interface for query-driven subgraph extraction and path reasoning. Specifically, the subgraph extraction module identifies relevant subgraphs based on the input KG and query, while the path retrieval module utilizes these subgraphs to compute reasoning paths aligned with the query context.

Building upon the retrieval results, the \textit{Generation Modules} employ a standardized interface to integrate user queries and reasoning paths, generating precise answers. Additionally, the \textit{Semantic Augmentation} layer enhances the reasoning process by leveraging advanced semantic scoring and ranking mechanisms, which incorporate subgraph and reasoning path information to produce contextually enriched outputs. Finally, the \textit{Integration and Output} layer consolidates all intermediate results, forming a cohesive pipeline that generates the final reasoning path tailored to the input queries.

The framework’s data flow is equally well-orchestrated. Initially, the Subgraph Extraction Module processes KG and query data to produce relevant subgraphs. These subgraphs, coupled with the query, are then processed by the Path Retrieval Module to derive reasoning paths. The Generation Module subsequently combines these reasoning paths with the query to produce the final answer.

A key strength of LEGO-GraphRAG lies in its modularity and extensibility. Each module adheres to a uniform interface specification, enabling seamless replacement or enhancement of individual components. This design philosophy ensures adaptability to diverse requirements, fostering flexibility and extensibility in a wide range of applications.

}






    
Like the {\preRetrieval} module, semantic information can also facilitate the {\color{red} filtering and refinement} of reasoning paths. These solutions can be grouped into three major paradigms:

{\it \underline{a) Semantic Refinement.}} This paradigm begins with the candidate reasoning paths generated by structure-based solutions.
    Paths are scored based on their semantic alignment with the query, and the most relevant ones are selected to refine the candidate set.
 For example, paths generated via Dijkstra’s algorithm can be further filtered and prioritized using semantic models, resulting in a reasoning path set that aligns closely with the query's context.
    
{\it \underline{b) Semantic-Driven Iterative Filtering.}} 
%This paradigm leverages heuristic iterative search algorithms on graphs, enhanced by semantic models, to identify reasoning paths. During the search, semantic models assign heuristic scores to nodes and edges based on their query relevance, dynamically guiding the exploration toward regions that are both structurally and semantically aligned with the query.
%For example, Beam Search integrates semantic relevance as a dynamic heuristic. At each step, candidate paths are evaluated using structural metrics (e.g., path length) and semantic scores, with only the most promising ones expanded further. This combined approach efficiently prioritizes high-quality paths while filtering out noise and irrelevant information.
This approach combines heuristic search algorithms with semantic guidance to identify reasoning paths. Semantic models assign heuristic scores to nodes and edges based on their query relevance, steering the exploration toward graph regions that are both structurally and semantically pertinent. For example, Beam Search integrates semantic relevance into its heuristic scoring, iteratively evaluating paths using structural metrics (e.g., path length) and semantic scores, with only the most promising ones expanded further. 
This approach efficiently prioritizes high-quality paths while filtering out noise and irrelevant information.


{\it \underline{c) Rule/Template-Based Filtering.}} In this paradigm, advanced semantic models generate rules or templates that specify the expected structure of reasoning paths for a given query. These templates include criteria such as entity or relationship types and are matched against the graph to retrieve paths meeting the specified structure. 
For example, for a query about ``disease-related drugs'', a semantic model (e.g., an LLM) might generate a template specifying a reasoning path like ``Disease → Drug → Target''. 
Applying this template to the graph retrieves paths conforming to the specified structure.  
    


Among the three paradigms, Semantic Refinement and Semantic-Driven Iterative Filtering are broadly applicable and form the primary focus of this study. In contrast, Rule/Template-Based Filtering relies heavily on semantic models and domain-specific knowledge, making it more suited for straightforward, well-defined queries and less generalizable for complex scenarios.




As shown in Table X, semantic models can be broadly categorized into two types: \textit{Statistical-based} and \textit{NN-based}. Furthermore, NN-based models are further divided into detailed subcategories. {\color{red} Say sth more technical.}




To investigate the impact of different solution types within the two modules of LEGO-GraphRAG on the overall performance of the GraphRAG process, we construct {\InstanceNum} distinct GraphRAG instances by selecting representative solutions from each module's category. Through empirical experiments on these instances, our objective is to extract key findings that could benefit future research on GraphRAG. To ensure the fairness and rigor of this empirical study, the construction of these instances adheres to the following rules:


\begin{itemize}[leftmargin=10pt]
\item {\bf Solution Coverage and Comparability.} When constructing instances, we ensured that solutions from the majority of types within both modules were covered~\footnote{Except for the {\it rule/template-based extraction} in the subgraph extraction module and {\it rule/template-based filtering} in the path filtering module, we considered all other solution types.}. For solutions that require semantic models, we incorporated the full range of semantic model types. To ensure a fair comparison between solution types within each module, we fixed one module's solution to a basic, structure-based algorithm (e.g., Personalized Pagerank, {\GetShortestPaths}), while allowing the other module's solution to vary across different types. 


\item  {\bf Alignment with Existing Work.} Wherever feasible, we align our instance construction with existing GraphRAG instances in terms of solution choices across the two module. In other words, we implement versions of existing work within the LEGO-GraphRAG framework, thereby facilitating the validation of the design and effectiveness of our proposed framework.
\end{itemize}
  
Table~\ref{tab: pipelines} details the methods used across the two modules in our GraphRAG instances. Next, we present the representative methods used to construct each module in the instance, followed by a discussion on the grouping of these instances.




\subsection{Representative Solutions}
 
\textbf{{\PreRetrieval} Module.} For the structure-based solutions of this module, we select two commonly used algorithms: Personalized PageRank (PPR) and Random Walk with Restart (RWR).

\begin{itemize}[leftmargin=10pt]

\item  \textbf{PPR.} The PPR algorithm operates on a graph $G = (V, E)$ by initiating with query-relevant nodes (entities) $v_i^{(q)} \in \epsilon_q$. This algorithm leverages structural features based on node degrees to identify nodes most closely related to these initial query nodes. Specifically, each node $v \in V$ is assigned an iteratively updated score $\mathbf{p}_v$, calculated as follows:
$\mathbf{p}_v^{(t+1)} = \lambda \mathbf{\mathcal{E}}_v + (1 - \lambda) \sum_{u \in \mathcal{N}(v)} \frac{\mathbf{p}_u^{(t)}}{\deg(u)}$,
where $\lambda$ denotes the teleportation probability, which influences the likelihood of returning to nodes within $\epsilon_q$, and $\mathcal{E}_v$ represents the preference vector highlighting nodes relevant to the query entities. Here, $\mathcal{N}(v)$ refers to the neighborhood of node $v$, and $\deg(u)$ denotes the degree of node $u$. This iterative process proceeds until convergence, resulting in a stable set of PPR scores. Some nodes (denoted as set $V'$) with the higher scores are subsequently chosen as the top-ranked nodes associated with the query. Using this selection, we construct a subgraph $g_q = {(v_i, r, v_j) \mid v_i, v_j \in V', (v_i, r, v_j) \in G}$, which serves as a foundational structure for identifying reasoning paths aligned with the contextual objectives of the query.


\item \textbf{RWR.} Like PPR, RWR ranks node $v \in V$ by iteratively updating the relevance score of the query-relevant nodes (entities)  $v_i^{(q)} \in \epsilon_q$. The key difference is that PPR assigns distinct initial probabilities to enable personalized ranking, whereas RWR restarts at a fixed starting node after each random walk, emphasizing node centrality.
\end{itemize}



For the semantic-enhanced solutions in this module, we implement the semantic pruning paradigm by combining the PPR algorithm with different types of semantic models, all of which, including LLMs, are uniformly used as scoring functions for semantic relevance. In this paper, we select six semantic models as scoring functions, ranging from statistical semantic models to neural network models of varying scales, with some fine-tuned and others in their vanilla (pre-trained) forms, all of which will be described in detail later.

\begin{itemize}[leftmargin=10pt]
\item \textbf{PPR+Pruning by Semantic Models.} For a subgraph $g_q$ extracted by the PPR algorithm based on query $q$ and the associated set of entities and relations $ \epsilon_q = \{v_i^{(q)}, e_i^{(q)}\} $, a scoring function $ S(v, e; \epsilon_q) $ is introduced to measure the semantic similarity between nodes and edges in $g_q$ and the entities and relations within $ \epsilon_q$. By applying threshold scores $ \tau_v $ and $ \tau_e$, only nodes and edges in $ g_q$ that demonstrate a high semantic relevance to the query are retained, resulting in a refined subgraph $ g_q'$:
$
g_q' = \left\{ (v, e) \in g_q \mid S(v, \epsilon_q) \geq \tau_v \text{ and } S(e, \epsilon_q) \geq \tau_e \right\}$. In this paper, we select six semantic models as scoring functions, ranging from statistical semantic models to neural network models of varying scales, with some fine-tuned and others in their vanilla (pre-trained) forms, all of which will be described in detail later.
\end{itemize}


\textbf{{\Retrieval} Module.} For the structure-based solutions in this module, we implement two main types: {\getShortestPaths} and {\getAllPaths}. The former is based on Dijkstra's algorithm, while the latter is implemented using an extended BFS algorithm.

\begin{itemize}[leftmargin=10pt]

\item \textbf{{\GetShortestPaths}.} The {\getShortestPaths} is utilized to identify all shortest paths within the connected subgraph $ g_{(q, v_i^{(q)})} \subseteq g_q $ starting from each query-relevant initial node $v_i^{(q)} \in \epsilon_q $. This approach generates an reasoning path set $\mathcal{P} $, ensuring that within the subgraph, the paths connecting the query node to other entities are structurally optimal, thus facilitating the efficient retrieval of relevant paths. 

\item\textbf{{\GetAllPaths}.} For each query-relevant starting node $v_i^{(q)} \in \epsilon_q$, {\getAllPaths} explores the subgraph level-by-level to generate a distinct set of non-repetitive paths that connect $v_i^{(q)}$ with all reachable nodes. Unlike {\getShortestPaths}'s approach, the reasoning paths derived via {\getAllPaths} incorporate ``detour reasoning chains.'' While these chains do not necessarily follow the shortest path, they may provide LLMs with additional contextually relevant information. Nonetheless, the inclusion of these detour paths can also introduce additional noise.
\end{itemize}

For the semantic-enhanced solutions in this module, we implemented its two main paradigms. Similar to the {\preRetrieval} module, we also use six types of semantic models as scoring functions in both paradigms to assess semantic relevance.



\begin{itemize}[leftmargin=10pt]

\item \textbf{{\GetShortestPaths}+Filtering by Semantic Models.} For the semantic refinement paradigm, we use {\getShortestPaths} to generate a set of reasoning paths from the graph or subgraph. These paths are then evaluated for semantic relevance to the query using different semantic models as scoring functions. Based on a predefined threshold, we select the highest-scoring paths to form the final set of reasoning paths. 

\item \textbf{Beam Search+Filtering by Semantic Models.} For the semantic-driven iterative filtering paradigm,  the Beam Search algorithm is employed to iteratively explore a limited number of high-scoring candidate paths (referred to as beams) to identify the most relevant inference path from each starting node $ v_i^{(q)} $. At each expansion step, the algorithm evaluates the potential extensions of each path within the beam, using semantic models to assess the semantic relevance of the paths to the query, such as by assigning relevance scores. Through the greedy strategy, the algorithm selects the extension direction with the highest score, thus preserving the paths with the highest potential relevance. This process is repeated at each step, maintaining a fixed beam width, until a stopping criterion is met—either when a path reaches a maximum length, all paths end with a terminal token (e.g., end-of-sequence), or no relevant extensions remain—at which point the final output consists of the most relevant reasoning paths.
\end{itemize}



\textbf{Semantic Models.} Based on the categorization of semantic models, we selected six different models: {\it BM25}, {\it ST}, {\ShortRerankModel}, {\it Fine-tuned ST}, {\it Vanilla LLM}, and {\it Fine-tuned LLM}. Among them, BM25 represents a straightforward statistical method that evaluates nodes and edges by calculating term frequency and inverse document frequency (TF-IDF) within the query context. For methods based on  NN models, the ST model leverages a pretrained Transformer-based encoder to calculate semantic similarity scores by embedding nodes, edges, and query-relevant entities, relationships into a shared vector space: $S_{\text{ST}}(v; \epsilon_q)  = \cos(\text{embed}(v), \text{embed}(\epsilon_q))$. Unlike the embedding-based calculation in the ST model, the {\ShortRerankModel} model directly outputs relevance scores for nodes and edges relative to the query without requiring cosine similarity computations, attributed to its refined pre-training on ranking tasks.

Furthermore, the fine-tuned ST model adjusts embeddings within domain-specific graphs to better align with targeted query objectives. This model undergoes fine-tuning with a specialized loss function, $L = \sum_{(v_i, \epsilon_q) \in \mathcal{D}} \max(0, \gamma - S(v_i, \epsilon_q) + S(v_j, \epsilon_q))$, where $\gamma$ represents a margin hyperparameter, and $\mathcal{D}$ contains training sample pairs. The goal is to increase scores for relevant pairs while reducing scores for irrelevant ones, thus enhancing scoring precision for domain-specific queries by minimizing the semantic distance between known relevant pairs. 
In addition, LLMs, whether in their vanilla or fine-tuned versions, can directly output relevance scores or rankings for nodes and edges within the query context. Fine-tuning of LLMs can adopt various approaches, including the aforementioned loss function or rely on specialized fine-tuning frameworks tailored for domain-specific tasks. The original LLM typically assesses relevance through direct inference, while the fine-tuned versions undergo targeted optimization to enhance ranking performance in structured search tasks.

\subsection{Grouping of GraphRAG Instances}
As shown in Table~\ref{tab: pipelines}, from  the perspective of empirical research, the constructed GraphRAG instances can be categorized into 4 groups:
  


\textbf{Basic Group.} In Table~\ref{tab: pipelines}, Instance 0 is designated as the basic instance and serves as a common reference for all other instances. This is because Instance 0 adopts the simplest yet relatively effective methods across the three modules, which also function as fundamental components. 


in the other instances. 



\textbf{{\PreRetrieval} Group.} Instances 1-7 in Table~\ref{tab: pipelines} can be regarded as iterations over various types of methods within the {\preRetrieval} module, with the method of {\retrieval} and {\postRetrieval} modules held constant. Therefore, we group these instances to facilitate the study of how different methods within the {\preRetrieval} module impact performance of GraphRAG.



\textbf{{\Retrieval} Group} (Instances 8-14) and \textbf{{\PostRetrieval} Group} (Instances 15-10) are grouped following a same rationale as described above.


\end{comment}
