%!TEX root = main.tex

\noindent
\textbf{Data Preparation for Machine Learning.}
It has been reported that 80\% of data analysis time and effort is spent on
the process of exploring, cleaning, and preparing the data~\cite{dasu2003exploratory},
and these activities have long been a focus of the database community.
For example, the recent Seattle report on database research~\cite{SeattleDBReport2019}
acknowledges the importance of these activities and the need to support data science ecosystems such as PyData and to ``devote more efforts on the end-to-end data-to-insights pipeline.''
This paper attempts to reduce the data preparation effort by defining a powerful API for accessing knowledge graphs.
To underscore the importance of such an API, note that~\cite{hidden_debt} makes the observation that most of the code in a machine learning system is devoted to tasks other than learning and prediction.
These tasks include collecting and verifying data and preparing it for use in machine learning packages.
This requires a massive amount of ``glue code'', and~\cite{hidden_debt} observes that this glue code can be eliminated by using well-defined common APIs for data access (such as \rdfframes).

Some related work focuses on the end-to-end  machine learning life cycle (e.g.,~\cite{tfx,mlflow,mldp}).
Some systems, such as MLdp~\cite{mldp}, focus primarily on managing input data, 
but they do not have special support for knowledge graphs. \rdfframes provides such support.

\vspace{4pt}
\noindent
\textbf{Database Support for PyData.}
Some recent efforts to provide database support for the PyData ecosystem focus on the scalability of dataframe operations, while other efforts focus on replacing SQL as the traditional data access API with pandas-like APIs.
Koalas\footnote{\url{https://koalas.readthedocs.io/en/latest}}
implements the pandas dataframe API on top of Apache Spark for better scalability.
Modin~\cite{modin} is a scalable dataframe system based on a novel formalism for pandas dataframes.
Ibis\footnote{\url{https://ibis-project.org}}
defines a variant of the dataframe API
(not pandas)
and translates it to SQL so that it can execute on a database system for scalability. Ibis also supports other backends such as Spark.
Koalas and Modin do not support SQL backends, and Ibis does not have a pandas API.
A recent system that addresses these limitations is
Magpie~\cite{magpie},
which
translates pandas operations to Ibis for scalable execution on multiple backends, including SQL database systems. Magpie chooses the best backend for a given program based on the program's complexity and the data size.
Grizzly~\cite{grizzly} is a framework that generates SQL queries from a pandas-like API and ships the SQL to a standard database system for scalable execution.
Grizzly relies on the database system's support for external tables in order to load the data.
It also 
creates user UDFs as native UDFs in the database system.
The AIDA framework~\cite{AIDA2018} allows users to write relational and linear algebra operators in Python and pushes the execution of these operators into a relational database system.
 %blue


All of these recent works are similar in spirit to
\rdfframes in that they replace SQL for data access with a pandas-like API and/or rely on a database backend for scalability. However, all of the works focus on relational data and not graph data.
\rdfframes is the first to define a pandas-like API for graph data (specifically RDF),
and to support a graph database system as a scalable backend.

\vspace{4pt}
\noindent
\textbf{Why RDF?}
Knowledge graphs are typically represented in the RDF data model.
Another popular data model for graphs is the \textit{property graph} data model,
%in which a graph is directed and 
which has labels on nodes and edges as well as (property, value) pairs associated with both.
Property graphs have gained wide adoption in many applications and are supported by popular database systems such as Neo4j\footnote{\url{https://neo4j.com}}
and Amazon Neptune.
Multiple query languages exist for property graphs, and efforts are underway to define a common powerful query language~\cite{g-core}.

A popular query language for property graphs is Gremlin.\footnote{\url{https://tinkerpop.apache.org/gremlin.html}}
Like \rdfframes, Gremlin adopts a navigational approach to querying the graph,
and some of the \rdfframes operators are similar to Gremlin operators.
The popularity of Gremlin is evidence that a navigational approach is attractive to users.
However, all publicly available knowledge graphs including DBpedia~\cite{lehmann2015dbpedia} and YAGO~\cite{yago} are represented in RDF format. Converting RDF graphs to property graphs is not straightforward mainly because the property graph model does not provide globally unique identifiers and linking capability as a basic construct. 
In RDF knowledge graphs, each entity and relation is uniquely identified by a URI, and links between graphs are created by using the URIs from one graph in the other.
\rdfframes offers a navigational API similar to Gremlin to data scientists working with knowledge graphs in RDF format and facilitates the integration of this API with the data analysis tools of the PyData ecosystem. 

\vspace{4pt}
\noindent
\textbf{Why \sparql?}
\rdfframes uses \sparql as the interface for accessing knowledge graphs.
In the early days of RDF, several other query languages were proposed
(see~\cite{haase2004rdfquerylanguages} for a survey), but none of them has seen broad adoption, and \sparql has emerged as the standard.

Some work proposes navigational extensions to \sparql (e.g.,~\cite{nsparql, sparqler}), but these proposals add complex navigational constructs such as path variables
and regular path expressions to the language.
In contrast, the navigation used in \rdfframes is simple and well-supported by standard \sparql
without extensions.
The goal of \rdfframes is not complex navigation, but rather providing a simple yet common and rich suite of data access and preparation operators that can be integrated in a machine learning pipeline.

\vspace{4pt}
\noindent
\textbf{Python Interfaces.}
A Python interface for accessing RDF knowledge graphs is provided by
Google's Data Commons project.\footnote{\url{http://datacommons.org}}
However, the goal of that project is not to provide powerful data access, but rather to synthesize a single graph from multiple knowledge graphs, and to enable browsing for graph exploration.
The provided Python interface has only one data access primitive: following an edge in the graph in either direction, which is but one of many capabilities provided by \rdfframes.

%The AIDA framework~\cite{AIDA2018} recognizes the importance of Python interfaces for machine learning on relational data. It allows users to write relational and linear algebra operators in Python and pushes the execution of these operators into a relational database system. At a high level, \rdfframes addresses the same problem as AIDA but focuses on RDF knowledge graphs rather than relational data, which leads to a very different solution.

The Magellan project~\cite{magellan} provides a set of interoperable Python tools for entity matching pipelines. It is another example of developing data management solutions by extending the PyData ecosystem~\cite{anhai_hilda}, albeit in a very different domain from \rdfframes. The same factors that made Magellan successful in the world of entity matching can make \rdfframes successful in the world of knowledge graphs. 
%\rdfframes addresses a problem that is very different from entity matching, but it adopts the same philosophy of tight integration with PyData.

There are multiple recent Python libraries that provide access to knowledge graphs through a \sparql endpoint over HTTP.
Examples include
pysparql,\footnote{\url{https://code.google.com/archive/p/pysparql}}
sparql-client,\footnote{\url{https://pypi.org/project/sparql-client}}
and 
AllegroGraph Python client.\footnote{\url{https://franz.com/agraph/support/documentation/current/python}}
However, all these libraries solve a very different (and simpler) problem compared to \rdfframes: they take a \sparql query written by the user and handle sending this query to the endpoint and receiving results. On the other hand, the main focus of \rdfframes is \textit{generating} the \sparql query from imperative API calls. Communicating with the endpoint is also handled by \rdfframes, but it is not the primary contribution.



\vspace{4pt}
\noindent
\textbf{Internals of \rdfframes.}
The internal workings of \rdfframes involve a logical representation of a query.
Query optimizers use some form of logical query representation, and we adopt a representation similar to the Query Graph Model~\cite{Pirahesh:1992}.
Another \rdfframes task is to generate \sparql queries from a logical representation.
This task is also performed by systems for federated \sparql query processing (e.g.,~\cite{fedx}) when they send a query to a remote site.
However, the focus in these systems is on answering \sparql triple patterns at different sites, so the queries that they generate are simple.
\rdfframes requires more complex queries so it cannot use federated \sparql  techniques.

