\section{Related Work}
\label{sec:rw}

Our work differs from the following surveys on research problems that are related to extractive KG summarization.

Liu \emph{et~al.}~\shortcite{DBLP:journals/csur/LiuSDK18} reviewed a wide range of methods for \textbf{graph summarization}, but they focused mostly on homogeneous graphs rather than KGs where nodes and edges may be labeled with different types. For labeled graphs, their survey covered \textbf{grouping-based} but not extractive methods, which represent two distinct paradigms of summarization. Previous surveys on KG summarization~\cite{DBLP:journals/vldb/CebiricGKKMTZ19,DBLP:journals/tgdk/ScherpRBCR23} also gave primary attention to grouping-based methods, based on the concept of quotients in particular. Since a grouping-based summary can be viewed as an implicit schema discovered from the KG, the task is also referred to as \textbf{schema discovery}~\cite{DBLP:journals/vldb/Kellou-MenouerK22}.

\textbf{Entity summarization} selects a subset of properties for each given entity in a KG~\cite{DBLP:journals/ws/LiuCGQ21}. An entity summary can be viewed as a special type of extractive KG summary that is restricted to the neighborhood of a particular node. Such locality distinguishes entity summarization from the methods for extractive KG summarization covered in this survey which globally take the entire KG into consideration.

\textbf{Ontology summarization} extracts core concepts or a sub-ontology from a given ontology. Existing methods mainly represent an ontology as a graph to be summarized~\cite{DBLP:journals/ijsc/PouriyehALCAAMK19}. Some of these graph representations resemble a KG but are at the schema level where nodes are classes instead of entities. Accordingly, the optimization objective of ontology summarization differs significantly from those of extractive KG summarization reviewed in this survey.