\section{Introduction}
% 1. 研究背景: 推荐系统 & LLM-based Agents
% % 推荐系统在日常生活中的重要作用。
Recommender systems (RSs) play a vital role in improving user experience and platform economic benefits, which have become an essential part of various domains, such as e-commerce, social media, and so on. 
% % 随着LLM的发展，LLM-based agents在做决策和完成复杂任务方面展现出优秀能力。这些模型的语义理解、规划和决策能力为推荐系统领域提供了新的可能性。
Currently, the advancement of Large Language Models (LLMs)~\cite{brown2020language, gpt42023technical, touvron2023llama, zeng2022glm} has introduced LLM-based agents~\cite{yao2022react, nakano2021webgpt, shen2023hugginggpt} capable of completing complex tasks. These agents' semantic understanding, planning, and decision-making skills unlock new potentials for more nuanced and context-aware recommendations.
% With the recent advances in Large Language Models (LLMs)~\cite{brown2020language, gpt42023technical}, LLM-based agents such as ReAct~\cite{yao2022react}, WebGPT~\cite{nakano2021webgpt}, and HuggingGPT~\cite{shen2023hugginggpt} have shown exceptional capabilities in completing complex tasks. The verbal comprehension, planning, and decision-making abilities of these models offer new opportunities to enrich recommendations.

% 2. 研究现状（相关工作）
% % 研究者们已经开始利用agents的能力解决推荐任务。
Researchers have started to utilize the capabilities of agents to solve recommendation tasks. 
% % 1）一大类工作例如RecAgent，AgentCF，主要侧重于使用agents来模拟用户或物品行为，提供对用户偏好的见解，但无法集成到RS中。
Existing work like ~\cite{zhang2023generative, wang2023RecAgent, zhang2023agentcf} primarily focuses on employing agents for simulating user or item behaviors, providing insights into user preferences but falling short of integration into RSs.
% % 2）一些工作尝试利用代理的能力直接构建recommender，主要使用单一类型的agent, 带有planning和memory组件以及辅助工具（如搜索引擎）。
On the other hand, some studies~\cite{wang2023recmind, huang2023InteRecAgent} attempt to leverage the capabilities of agents to directly build a recommender, primarily using one single agent with planning and memory components and auxiliary tools (e.g., search engine).
% % % 然而，
% Motivation：推荐决策很复杂，单个agent不能很好地应对，缺乏对多智能体的尝试（有用且重要）
However, there are various complex decision-making tasks in recommendation scenarios~\cite{sun2023neighborhood,sun2024collaborative}, on which single-agent instances are unable to perform well.
% It has been demonstrated that single-agent instance performs more poorly than multi-agent collaboration in reasoning, factuality, and question-answering tasks~\cite{liang2023encouraging, du2023improving}.
Multi-agent collaboration, which is near to human workflows, is believed to accomplish complex tasks better with collective intelligence.
Although work~\cite{shu2023rah} proposes a multi-agent recommendation framework, it only has limited agent types and a fixed collaboration mode.

\begin{table*}[t!]
\centering
\caption{Comparison between previous work and our MACRec. Note that \textsl{Single-type Agents} indicate all agents serve the same role (e.g., users), while \textsl{Multi-type Agents} refer to agents having multiple roles and capabilities (e.g., managers, reflectors).}
\label{tab:related_work}
\begin{tabular}{cccccc}
\toprule

\textbf{Model} & \textbf{Objectives} & \textbf{Single-type Agents} & \textbf{Multi-type Agents}  & \textbf{Diverse Rec. Scenarios} & \textbf{Open-source} \\
\midrule
RecAgent~\cite{wang2023RecAgent} & User Simulation & \Checkmark &  &  & \Checkmark \\
Agent4Rec~\cite{zhang2023generative} & User  Simulation & \Checkmark &  &  &  \Checkmark \\
AgentCF~\cite{zhang2023agentcf} & U-I Inter Simulation & & \Checkmark &  &  \\
\midrule
RAH~\cite{shu2023rah} & Recommender &  & \Checkmark &  &  \\
RecMind~\cite{wang2023recmind}  & Recommender & \Checkmark &  & \Checkmark &  \\
InteRecAgent~\cite{huang2023InteRecAgent}  & Recommender & \Checkmark &  &  & \\
\midrule
\textbf{MACRec} & Recommender  & \Checkmark & \Checkmark & \Checkmark & \Checkmark \\
\bottomrule
\end{tabular}
\end{table*}

% 3. Our Framework
To better unleash the potential of multi-agent collaboration for recommendation tasks, we propose \textbf{MACRec}, a novel \textbf{M}ulti-\textbf{A}gent \textbf{C}ollaboration framework for recommender systems, designed to harness the diverse capabilities of each agent. 
Notably, this framework differs from studies for simulation with agents but focuses on building a recommender directly.
MACRec provides customizable agents with abilities powered by LLMs and useful tools. For example, we offer \textsl{Manager} to plan and manage task execution, \textsl{Reflector} to reflect on previous errors, \textsl{User/Item Analysts} to analyze user/item characteristics, \textsl{Searcher} to search more information using the search tool, and \textsl{Task Interpreter} to translate the dialogs into executable recommendation tasks.
These agents with different roles work collaboratively to tackle a specific recommendation task.

% Applications
Additionally, we provide application examples to use MACRec on various recommendation tasks, including rating prediction, sequential recommendation, conversational recommendation,
% interactive recommendation, click-through rates (CTR) prediction,
and explanation generation of recommendation results. 
Considering the varying requirements for agents in different scenarios, we showcase examples of selecting and customizing agents to collaborate on diverse recommendation tasks.
% Understandably, different recommendation scenarios require different sets of agents.
% Our case experiments on rating prediction and sequential recommendation tasks show our framework's practical feasibility and effectiveness. 
Furthermore, we developed an online web interface for our MACRec, providing a user-friendly visualization of the agents' collaboration process.
The main strengths of this work can be summarized as follows:
\begin{itemize}[leftmargin=*]
    \item \textbf{A New Multi-agent Collaboration Framework for Recommendation.}
    % 不同于以往的simulation工作，提出一个新的多智能体合作框架。提供可定制的
    Unlike previous studies focused on user/item simulation with agents, we propose a new multi-agent collaboration framework for recommendation \textbf{MACRec}. In this framework, agents with different abilities, work collaboratively are involved to tackle specific recommendation tasks.
    % \item \textbf{Flexible Collaboration Modes.}
    % \item \textbf{Adaptive Configuration for Distinct Tasks.}
    % support the adaptive customization of agents and how they collaborate across different tasks.
    % The agents in our framework can achieve different collaboration modes by customizing the prompts and system settings.
    
    % By customizing settings for data and agents, the framework can adaptively support numerous tasks.
    % \item \textbf{Adaptive Configuration for various tasks.}
    
    \item \textbf{Diverse Applications on Recommendation Scenarios.}
    We present application examples on various recommendation scenarios, including rating prediction, sequential recommendation, explanation generation,
    % interactive recommendation, CTR prediction, 
    and conversational recommendation.

    \item \textbf{A User-friendly Online Web Interface. } We developed an online web interface for MACRec, visualizing how agents collaboratively tackle tasks.

\end{itemize}


% In this framework, agents with different abilites would collaborate to complete a given recommendation task. During the process of completing tasks, whether intelligent agents cooperate and the effectiveness of cooperation will be trained. 

% 介绍 actor 和 reflector 更进一步地
% To explore the effectiveness of our MAC framework, 
% Additionally, we primarily focus on the reflection-based cooperation mode, assembling an 'actor' agent for task execution and a 'reflector' agent for feedback and reflection.
% In detail, the actor is responsible for completing the main execution process of the task by having a thought, while the reflector provides crucial feedback and reflections on the actor's decisions. Importantly, the reflection process is not mandatory; the decision "whether to cooperate/reflect" is part of the system's dynamic. It is expected that this actor-reflector collaboration will significantly enhance the accuracy and robustness of our system across various recommendation tasks.
% The reflection paradigm compels LLMs to recognize and amend their prior errors. This extra reflection step enhances the precision and robustness of the model outputs, obliging the recommending agent to reach a more thorough and accurate prediction.
