\section{Related Work}
% 换一下顺序
\subsection{Agents-based Recommendation}

Currently, research on integrating LLM-based agents for recommendation can be categorized into two primary orientations: \textsl{simulation-oriented} and \textsl{recommender-oriented} approaches. Table~\ref{tab:related_work} compares our MACRec and previous agents-based work.
% 放在2.2后面
%our MACRec in comparison with previous agents-based work.

The \textsl{simulation-oriented} work focuses on using agents to simulate user behaviors and item characteristics in RSs. RecAgent~\cite{zhang2023generative} and Agent4Rec~\cite{wang2023RecAgent} both propose to use agents as user simulators to empower the evaluation of RSs, which feature single-type agents (as users).
AgentCF ~\cite{zhang2023agentcf} explores the simulation of user-item interactions through user-agents and item-agents. It belongs to a multi-type agent system, with only two types and simple interactions.
This line of research aims to provide a deeper understanding of user preferences but falls short of integration into RSs.

The goal of \textsl{recommender-oriented} studies is to build a "recommender agent" with planning and memory components to tackle recommendation tasks. 
InteRecAgent~\cite{huang2023InteRecAgent} and RecMind~\cite{wang2023recmind} primarily focus on improving a single recommender agent's planning and reflection ability.
% 再明确阐述差异 Diverse Rec  Summary: 强调multi-agents的工作都没有开源，缺少demo系统
RAH~\cite{shu2023rah} proposes a human-centered framework using LLM Agents as assistants.
It supports collaboration among different types of agents, yet only in a fixed mode, whereas MACRec enables adaptable collaboration for various uses. Moreover, RAH lacks publicly accessible code or demos.
% 据我们所知，我们是第一个支持xxx,xxx
To the best of our knowledge, MACRec is the first open-source framework supporting multi-type agents for diverse recommendation scenarios.

% to 
% And it is the first open-source framework for multi-agent recommendation.


\subsection{Multi-agent Collaboration}

% The study of multi-agent collaboration is characterized by exploring how multiple intelligent agents interact and collaborate to achieve complex tasks or goals.
% 早期的multi-agent systems
% Early foundations of multi-agent systems originated from distributed artificial intelligence (DAI)~\cite{chaib1992trends} and multi-agent system (MAS)~\cite{stone2000multiagent}. \citet{wooldridge1995intelligent} laid the foundational principles for agent coordination and communication in MAS. 
Multi-agent systems, initially grounded in DAI~\cite{chaib1992trends} and MAS~\cite{stone2000multiagent}, evolved with foundational concepts of agent coordination and communication by \citet{wooldridge1995intelligent}.
% 基于LLM
The advent of powerful LLMs~\cite{brown2020language, gpt42023technical, touvron2023llama, zeng2022glm} has shifted focus towards their application in multi-agent collaboration. ~\citet{brown2020language} demonstrated LLMs' potential in human-like dialogues, applicable to agent-agent communication. ~\citet{vinyals2019grandmaster, nascimento2023gpt} illustrates how LLM agents can collaborate for shared objectives, achieving specific and complex task solutions. 
Recent work~\cite{du2023improving, zhang2023building, chen2023agentverse} leverage multi-agent collaboration to achieve better performance on complex tasks. CAMEL~\cite{li2023camel} and AutoGen~\cite{wu2023autogen} focus on communicative agent systems for complex task solutions through inter-agent dialogue. 
% 加一句总结，没有用在推荐场景
However, existing research on multi-agent collaboration has not investigated its potential in recommendation scenarios.

% ~\citet{madaan2023self}, ~\citet{hao2023reasoning}, ~\citet{shinn2023reflexion} and ~\citet{yao2023retroformer} employ reflection, a framework to optimize the LLM agent corresponding to feedbacks from other agents set as the environment, supplementing LLMs in task adaptation from merely exploiting the knowledge of pretrain model.

