%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% LaTeX Template for ECAI Papers 
%%% Prepared by Ulle Endriss (version 1.0 of 2023-12-10)

%%% To be used with the ECAI class file ecai.cls.
%%% You also will need a bibliography file (such as mybibfile.bib).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Start your document with the \documentclass{} command.
%%% Use the first variant for the camera-ready paper.
%%% Use the second variant for submission (for double-blind reviewing).

\documentclass{ecai} 
% \documentclass[doubleblind]{ecai} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Load any packages you require here. 

\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{color}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{svg}
\usepackage{comment}
\usepackage{amsmath,amssymb,mathtools}
\usepackage{siunitx}
\urlstyle{same}
\usepackage{enumitem}% http://ctan.org/pkg/enumitem
\setlist[itemize]{noitemsep, topsep=0pt}
\usepackage{amsthm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Define any theorem-like environments you require here.

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{fact}[theorem]{Fact}
\newtheorem{definition}{Definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Define any new commands you require here.

\newcommand{\BibTeX}{B\kern-.05em{\sc i\kern-.025em b}\kern-.08em\TeX}
\newcommand{\ra}{\ensuremath{\rightarrow}}
\newcommand{\Er}{\mathbf{E}}

\newcommand{\Ac}{\ensuremath{\mathcal{A}}}
\newcommand{\Bc}{\ensuremath{\mathcal{B}}}
\newcommand{\Cc}{\ensuremath{\mathcal{C}}}
\newcommand{\Dc}{\ensuremath{\mathcal{D}}}
\newcommand{\Ec}{\ensuremath{\mathcal{E}}}
\newcommand{\Fc}{\ensuremath{\mathcal{F}}}
\newcommand{\Gc}{\ensuremath{\mathcal{G}}}
\newcommand{\Hc}{\ensuremath{\mathcal{H}}}
\newcommand{\Ic}{\ensuremath{\mathcal{I}}}
\newcommand{\Sc}{\ensuremath{\mathcal{S}}}
\newcommand{\Lc}{\ensuremath{\mathcal{L}}}
\newcommand{\Mc}{\ensuremath{\mathcal{M}}}
\newcommand{\Nc}{\ensuremath{\mathcal{N}}}
\newcommand{\Pc}{\ensuremath{\mathcal{P}}}
\newcommand{\Qc}{\ensuremath{\mathcal{Q}}}
\newcommand{\Rc}{\ensuremath{\mathcal{R}}}
\newcommand{\Uc}{\ensuremath{\mathcal{U}}}
\newcommand{\Vc}{\ensuremath{\mathcal{V}}}
\newcommand{\Wc}{\ensuremath{\mathcal{W}}}
\newcommand{\Xc}{\ensuremath{\mathcal{X}}}
\newcommand{\Yc}{\ensuremath{\mathcal{Y}}}
\newcommand{\Zc}{\ensuremath{\mathcal{Z}}}

\newcommand{\Rbb}{\ensuremath{\mathbb{R}}}
\newcommand{\Ibb}{\ensuremath{\mathbb{I}}}
\newcommand{\Zbb}{\ensuremath{\mathbb{Z}}}

\newcommand{\lb}{\ensuremath{\left(}}
\newcommand{\rb}{\ensuremath{\right)}}
\newcommand{\lbr}{\ensuremath{\left\{}}
\newcommand{\rbr}{\ensuremath{\right\}}}
\newcommand{\lsb}{\ensuremath{\left[}}
\newcommand{\rsb}{\ensuremath{\right]}}

\newcommand{\fref}[1]{\fref{#1}}
\newcommand{\sref}[1]{Section~\ref{#1}}
\newcommand{\cref}[1]{Chapter~\ref{#1}}
\newcommand{\coref}[1]{Corollary~\ref{#1}}

\newcommand{\eref}[1]{Equation~(\ref{#1})}
%\newcommand{\eref}[1]{(\ref{#1})}

\newcommand{\tref}[1]{Table~\ref{#1}}
\newcommand{\dref}[1]{Definition~\ref{#1}}
\newcommand{\lref}[1]{Lemma~\ref{#1}}
\newcommand{\thref}[1]{Theorem~\ref{#1}}
\newcommand{\pref}[1]{Proposition~\ref{#1}}
\newcommand{\pgref}[1]{Page~\pageref{#1}}
\newcommand{\qref}[1]{Question~\ref{#1}}
\newcommand{\aref}[1]{Appendix~\ref{#1}}
\newtheorem{problem}{Problem}
\newtheorem{remark}{Remark}
\newcommand{\pfref}[1]{Fig.~\protect\ref{#1} on page~\pageref{#1}}
\newcommand{\psref}[1]{Section~\ref{#1} on page~\pageref{#1}}
\newcommand{\pcref}[1]{Chapter~\ref{#1} on page~\pageref{#1}}
\newcommand{\pcoref}[1]{Corollary~\ref{#1} on page~\pageref{#1}}
\newcommand{\peref}[1]{Equation~(\ref{#1}) on page~\pageref{#1}}
\newcommand{\ptref}[1]{Table~\protect\ref{#1} on page~\pageref{#1}}
\newcommand{\pdref}[1]{Definition~\ref{#1} on page~\pageref{#1}}
\newcommand{\plref}[1]{Lemma~\ref{#1} on page~\pageref{#1}}
\newcommand{\pthref}[1]{Theorem~\ref{#1} on page~\pageref{#1}}
\newcommand{\ppref}[1]{Proposition~\ref{#1} on page~\pageref{#1}}
\newcommand{\pqref}[1]{Question~\ref{#1} on page~\pageref{#1}}
\newcommand{\exref}[1]{Example~\ref{#1} on page~\pageref{#1}}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frontmatter}

%%% Use this command to specify your submission number.
%%% In doubleblind mode, it will be printed on the first page.

\paperid{1338} 

%%% Use this command to specify the title of your paper.

\title{United We Stand: Decentralized Multi-Agent \\Planning With Attrition}

%%% Use this combinations of commands to specify all authors of your 
%%% paper. Use \fnms{} and \snm{} to indicate everyone's first names 
%%% and surname. This will help the publisher with indexing the 
%%% proceedings. Please use a reasonable approximation in case your 
%%% name does not neatly split into "first names" and "surname".
%%% Specifying your ORCID digital identifier is optional. 
%%% Use the \thanks{} command to indicate one or more corresponding 
%%% authors and their email address(es). If so desired, you can specify
%%% author contributions using the \footnote{} command.

\author[A]{\fnms{Nhat}~\snm{Nguyen}\thanks{Corresponding Author. Email: nhatdaoanh.nguyen@adelaide.edu.au}}
\author[A]{\fnms{Duong}~\snm{Nguyen}}
\author[B]{\fnms{Gianluca}~\snm{Rizzo}}
\author[A]{\fnms{Hung}~\snm{Nguyen}} 

\address[A]{The University of Adelaide, Australia}
\address[B]{HES SO Valais, Switzerland, and the University of Foggia, Italy.}

%%% Use this environment to include an abstract of your paper.

\begin{abstract}
Decentralized planning is a key element of cooperative multi-agent systems for information gathering tasks. However, despite the high frequency of agent failures in realistic large deployment scenarios, current approaches perform poorly in the presence of failures, by not converging at all, and/or by making very inefficient use of resources (e.g. energy). In this work, we propose Attritable MCTS (A-MCTS), a decentralized MCTS algorithm capable of timely and efficient adaptation to changes in the set of active agents. It is based on the use of a global reward function for the estimation of each agent's local contribution, and regret matching for coordination. We evaluate its effectiveness in realistic data-harvesting problems under different scenarios. We show both theoretically and experimentally that A-MCTS enables efficient adaptation even under high failure rates. Results suggest that, in the presence of frequent failures, our solution improves substantially over the best existing approaches in terms of global utility and scalability.
\end{abstract}

\end{frontmatter}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{intro.tex}
\input{relatedwork.tex}
\input{model.tex}
\input{problem}
\input{algo.tex}
\input{experiments.tex}

\section{Conclusions}
Achieving efficient coordination in multi-agent planning for information gathering is a critical challenge in practical settings with high attrition rates. In this work, we proposed a new approach to tackle this issue. Our proposed algorithm, Attritable MCTS (A-MCTS), effectively coordinates actions among agents while adapting to agent failures by allowing all agents to jointly optimize the global utility directly with a new coordination technique based on regret matching. Our empirical evaluation demonstrates that A-MCTS improves substantially over the best existing approaches in terms of global utility and scalability in scenarios with frequent agent failures. As a follow-up, we intend to extend A-MCTS to more dynamic systems where new agents can join and the communication is probabilistic. Another line of inquiry is to study the performance of our algorithm in problems with inter-agent dependency, where the actions of an agent can only be enabled by the actions of another.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Use this command to include your bibliography file.
\clearpage
\bibliography{mybibfile}
\newpage
\input{appendix}

\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
