
\section{Experiments}

\subsection{Experimental Settings}

\begin{table}[t]
\centering
\label{tab:dataset_statistics}
\begin{tabular}{lccc}
\toprule
\textbf{Datasets} & \textbf{\#Train} & \textbf{\#Valid} & \textbf{\#Test} \\
\midrule
WebQSP     & 2,848   & 250    & 1,639  \\
\midrule
CWQ        & 27,639  & 3,519  & 3,531   \\
% \midrule
% MetaQA & 329,282 & 39,136 & 30,903 \\ 
\bottomrule
\end{tabular}
\caption{Statistics of KGQA benchmarks.}

\label{tab:datasets}
\end{table}

\paragraph{Datasets.}
To evaluate the effectiveness of \method{}, we conduct experiments on two widely used KGQA benchmarks: WebQSP~\cite{talmor2018web} and CWQ~\cite{yih2016value}. The statistics of these benchmarks are reported in Table~\ref{tab:datasets}. More details about datasets are provided in Appendix~\ref{sec:dataset}.


\paragraph{Baselines.} We compare \method{} with a comprehensive set of baselines. These baselines include: the semantic parsing methods, e.g., KV-Mem~\citep{miller2016key}, EmbedKGQA~\citep{saxena2020improving}, QGG~\citep{lan2020query}, NSM~\citep{he2021improving}, TransferNet~\citep{shi2021transfernet}, KGT5~\citep{saxena2022sequence}, and DECAF~\citep{yu2022decaf};
the retrieval-based methods, e.g., GraftNet~\citep{sun2018open}, PullNet~\citep{sun2019pullnet}, SR+NSM~\citep{zhang2022subgraph}, and SR+NSM+E2E~\citep{zhang2022subgraph};
the general LLMs, including 
Flan-T5-xl~\citep{chung2024scaling}, Alpaca-7B~\citep{taori2023stanford},
Llama3-8B~\citep{dubey2024llama}, Qwen2.5-7B~\citep{team2024qwen2}, ChatGPT~\citep{schulman2022chatgpt}, and ChatGPT+CoT~\citep{wei2022chain};
and recent LLMs with KG methods, including UniKGQA~\citep{jiang2022unikgqa}, KD-CoT~\citep{wang2023knowledge},
Nutrea~\citep{choi2023nutrea}, ToG~\citep{sun2023think}, RoG~\citep{luo2023reasoning}, KAPING~\citep{baek2023knowledge}, ReasoningLM~\citep{jiang2023reasoninglm},
FiDeLis~\citep{sui2024fidelis}, GNN-RAG~\citep{mavromatis2024gnn},
DoG~\citep{ma2025debate},  DualR~\citep{liu2025dual}
, DP~\citep{ma2025deliberation}, and RwT~\citep{shen2025reasoning}. The details are provided in Appendix~\ref{sec:baseline}.

\input{table/main_table}

\paragraph{Implementation Details.}

In \method{}, GPT-4.1 serves as the backbone for context generation, candidate retrieval, relation re-ranking, and exploration summarization~\citep{liu2023evaluating}. Following prior work~\cite{sun2023think, ma2024think}, the reasoning process follows a beam search paradigm with a maximum number of iterations $I=30$ and a maximum length of $L=4$ hops. At each step, the retriever proposes $k=3$ candidate relations for the WebQSP dataset and $k=4$ for the CWQ dataset, which are then filtered and re-ranked by the Dual-Feedback Re-ranking module under a threshold of $\zeta=0.5$. Following prior work~\citep{luo2023reasoning,wang2025dynamically,ma2025deliberation}, performance is evaluated using Hits@1 and F1 score, capturing both exact-match accuracy and robustness in the presence of multiple valid answers.

\input{table/different_backbone}

\subsection{Performance Comparison}

Table~\ref{tab:main_results} reports the performance of \method{} against state-of-the-art baselines on KGQA datasets. The results yield the following observations: (1) Semantic parsing methods map questions into logical forms, while retrieval-based methods extract candidate subgraphs for reasoning. Although these approaches provide interpretability and capture structural semantics, semantic parsing struggles with diverse query patterns, and retrieval methods separate retrieval from reasoning, limiting adaptability in multi-hop inference. In contrast, LLMs with KGs integrate question understanding with structured graph exploration, enabling more flexible path construction and stronger generalization. (2) General-purpose LLMs, such as Flan-T5-xl, Alpaca-7B, and Llama3-8B, rely on strong language understanding and broad contextual reasoning. They can handle diverse queries and generate coherent answers, but without grounding in structured graph semantics they often produce hallucinations or logically inconsistent results, particularly in multi-hop scenarios. In contrast, LLMs with KGs explicitly leverage graph structure to constrain reasoning and ensure factual consistency. As a result, general LLMs consistently underperform compared with LLM+KG methods. (3) LLMs with KGs methods have emerged as the leading paradigm in current KGQA research, as they couple the semantic fluency of LLMs with the structural rigor of knowledge graphs. By explicitly grounding reasoning in KGs, these methods reduce hallucination, ensure factual consistency, and achieve stronger generalization to compositional and multi-hop queries. Recent advances, such as DP and RwT, further illustrate the benefits of incorporating question-specific priors and structured exploration, confirming the effectiveness of this hybrid paradigm. Compared with prior methods, \method{} delivers improved performance, attributed to two main innovations: (i) the use of contextual narratives, which preserve semantic coherence across reasoning steps and prevent logical drift, and (ii) the generalization of prior exploration trajectories into reusable experiential priors, which guide subsequent reasoning and reduce redundant exploration. Together, these components enable \method{} to outperform existing LLM+KG approaches with more coherent and robust multi-hop reasoning.

\subsection{Impact of Different LLMs}

To evaluate the impact of different LLMs as backbone within the \method{} framework, we evaluate several backbones including Llama2-13B~\citep{roque2025evolution}, Qwen3-14B~\citep{team2024qwen2}, GPT-4.1-mini, and GPT-4.1, as reported in Table~\ref{tab:llm_backbone}. The results reveal that: (1) The effectiveness of \method{} depends on the reasoning capacity of the underlying LLMs. The consistent performance gap between medium-scale open-source models and larger proprietary models illustrates the sensitivity of KGQA to planner quality, indicating that more capable LLMs enable more accurate relation selection and more stable multi-hop reasoning. (2) \method{} remains effective even with relatively weaker planners. When instantiated with Llama2-13B, the framework still outperforms strong baselines such as RwT and FiDeLis on both datasets. This indicates that although high-capacity LLMs bring additional improvements, the design of \method{} ensures robustness and competitive performance across a wide range of backbones.

\input{table/ablation}
\subsection{Ablation Study}

We conduct ablation studies to evaluate the contributions of key components in \method{}: (1) \method{} w/o CT, removing the dynamic context generation module; (2) \method{} w/o ER, removing the exploration generalization mechanism; and (3) \method{} w/o ALL, removing both modules simultaneously.

Experimental results are summarized in Table~\ref{tab:ablation_results}. From the results, we find that:
 (1) Removing the dynamic context generation module (\method{} w/o CT) leads to a clear performance drop, indicating that maintaining semantic coherence across reasoning steps is crucial for accurate path reasoning. Without this component, the model cannot ensure that intermediate decisions remain aligned with the overall query goal. (2) Removing the exploration generalization mechanism (\method{} w/o ER) leads to degraded performance, indicating that abstracting exploration priors into reusable knowledge is crucial for improving model performance. Without this component, the model is more likely to repeat similar exploration patterns, reducing the overall reasoning performance of \method{}. (3) When both modules are removed simultaneously (\method{} w/o ALL), the proposed \method{} suffers the largest drop in performance. This result shows that dynamic context generation and exploration generalization are complementary, and their combined effect is critical to realizing the effectiveness of \method{}.


\input{figure/figure_hyper}

\subsection{Sensitivity Analysis}

We perform a sensitivity analysis to examine the effect of three key hyperparameters in \method{}: the number of selected relations $k$, the maximum reasoning path length $L$, and the confidence threshold $\zeta$. The parameter $k$ specifies how many candidate relations are proposed by the LLM-based retriever at each step, $L$ determines the maximum number of hops allowed during path construction, and $\zeta$ is the threshold for relation selection in path expansion.

Figure~\ref{fig:hyper_sensitive} presents the performance of \method{} on the WebQSP and CWQ datasets as we vary $k, L$ within the range of $\{2,3,4,5\}$ and $\zeta$ within the range of $\{0.4,0.5,0.6,0.7\}$. From the results, we find that: (1) As shown in Figure~\ref{fig:hyper_sensitive}(a), increasing $k$ initially improves performance, but the gains plateau and eventually decline as the search space expands. Larger values of $k$ promote broader relational exploration but also introduce irrelevant candidates and additional cost, while smaller values restrict the diversity of relations. To balance these trade-offs, we set $k=3$ for WebQSP and $k=4$ for CWQ as the default configurations. (2) As shown in Figure~\ref{fig:hyper_sensitive}(b), extending the reasoning path length $L$ yields diminishing returns beyond a certain depth. On both WebQSP and CWQ, performance improves steadily from $L=2$ to $L=4$, but declines at $L=5$, suggesting that moderately deep paths are most effective while overly long horizons introduce noise. To balance accuracy and efficiency, we adopt $L=4$ as the default path length in all experiments. (3) As shown in Figure~\ref{fig:hyper_sensitive}(c), the confidence threshold $\zeta$ has a substantial impact on relation selection. Lower thresholds allow noisy candidates that reduce precision, whereas higher thresholds overly restrict expansion and harm recall. A moderate value provides the best trade-off, and we therefore set $\zeta=0.5$ as the default value. 

\input{table/efficiency}

\input{table/case_study1}

\subsection{Computation Consumption Analysis}

Table~\ref{tab:Efficiency} compares the computation consumption of different KGQA methods in terms of LLM calls and token usage, where \method{} achieves lower token consumption and fewer LLM calls. On the WebQSP dataset, \method{} lowers token usage from 10,680 to 8,782 and LLM calls from 15.1 to 14.2, outperforming RwT. On the CWQ dataset, it further reduces tokens from 17,885 to 16,414 and calls from 28.6 to 27.8, again demonstrating clear efficiency gains over RwT. These efficiency gains arise from \method{}, in which contextual narratives preserve semantic coherence across reasoning steps while exploration generalization reduces redundant exploration. As a result, \method{} lowers both LLM call frequency and token consumption, yielding a more efficient and scalable reasoning framework than existing baselines. More results on worst or failure cases can be found in Appendix.~\ref{sec:computation}. 




\subsection{Case study}

Table~\ref{tab:case_study1} presents a case study comparing the outputs of \method{} with four representative LLMs: Llama-2-13B, Qwen-3-14B, GPT 4.1, and GPT 4.1-mini. For the query \textit{“What featured Kim Richards and was produced by Ann Marie Sanerlin?”}, all baseline models produce incorrect answers, often hallucinating films or conflating unrelated television productions. In contrast, \method{} correctly identifies \textit{Race to Witch Mountain} by following a structured \texttt{Reasoning Path} that connects Kim Richards to her film performances and integrates production information to refine the candidate set. The reasoning process of \method{} begins by locating entities associated with Kim Richards and expanding along film-related relations that represent her acting roles. At each hop, the \texttt{Contextual Narrative} guides the model to remain semantically aligned with the query, first retrieving films featuring Kim Richards and then filtering them according to the production information linked to Ann Marie Sanerlin. This narrative grounding ensures that relation selection remains coherent and context-aware throughout the multi-hop reasoning process. In parallel, \texttt{Exploration Patterns} abstracted from prior exploration trajectories capture recurring unproductive behaviors, such as cast–series loops that fail to satisfy producer-related constraints. Through the interplay of narrative guidance and exploration prior, \method{} effectively narrows the search space and converges on the correct answer. Additional case study is provided in Appendix~\ref{sec:case_study}.





