\documentclass[11pt]{article}
\usepackage{xspace}



\pagestyle{empty}

\begin{document}


\hspace{-1.5em}Dear Editors and Reviewers:

\vspace{1em} We would like to submit the enclosed manuscript entitled:

\vspace{1em}
 
``\emph{Explainable Session-based Recommendation via Path Reasoning",} 

\vspace{1em}

\noindent which we wish to be considered for publication in
\emph{IEEE Transactions on Knowledge and Data Engineering}. 

\vspace{.5em}

It is well known that most of the current session-based recommendation (SR) models focus on the problem of how to improve the accuracy of recommendations, while neglecting the process of providing explainability. In this manuscript, we provide a generalized and explainable framework for unexplainable SR models. PR4SR is the first path reasoning approach that uses hierarchical reinforcement learning to provide a generalized and explainable framework for SR. Extensive experiments on four public datasets and a user survey demonstrate the effectiveness and state-of-the-art performance and explainability of PR4SR.

Providing explainable recommendation processes for recommendation models is a popular topic, and TKDE has published a number of innovative papers on this topic. We believe this work can encourage the community to explore more novel and generalizable explainable frameworks.

All authors approved the manuscript and this submission. 
Thank you for receiving our manuscript and considering it for review.
We appreciate your time and look forward to your response.

\vspace{2em}


\hspace{-1.5em}With best regards, \vspace{1em}

\hspace{-1.5em}Yang Cao, Shuo Shang, Jun Wang, and Wei Zhang.
 




\end{document}
