\section{Introduction}
% Retrieval-augmented generation (RAG) has become a standard approach for grounding large language models (LLMs) in external data stores. At the same time, a growing body of work has revealed that RAG pipelines are vulnerable to data extraction attacks. Early studies show that carefully crafted prompts or prompt-injection strategies can cause models to regurgitate private chunks from the retrieval datastore~\cite{zeng2024good,qifollow}. Subsequent work escalates from membership and entity-level inference to near-complete reconstruction of the underlying corpus~\cite{cohen2024unleashing,di2024pirates}, and demonstrates that agent-style RAG systems with memory are particularly susceptible to iterative extraction~\cite{wang2025unveiling,jiang2025feedback,wang2025silent}. However, these attacks all operate over \emph{flat} retrieval stores and evaluate leakage at the level of text chunks or documents, rather than structured knowledge.



Retrieval-augmented generation (RAG) has become a standard paradigm for grounding large language models (LLMs) in external datastores. Alongside its rapid adoption, a growing body of work has shown that RAG pipelines are vulnerable to data extraction attacks: adversarially crafted queries can induce models to reveal private content from the retrieval datastore \cite{zeng2024good, qifollow}. Subsequent studies show that iterative, black-box interactions can scale extraction toward large portions of the underlying corpus, and that agent-style RAG systems with memory and repeated querying can further exacerbate long-horizon reconstruction risks \cite{cohen2024unleashing, di2024pirates, wang2025unveiling, wang2025silent, jiang2025feedback}.
However, existing attacks operate primarily over \emph{flat} retrieval stores and evaluate leakage at the chunk/document level, leaving the security implications of structured knowledge representations largely unexplored.

Graph-based retrieval-augmented generation (GraphRAG) extends RAG by organizing a corpus into a graph of entities and relations, then retrieving relevant knowledge from the graph for augmented generation~\cite{xiao2025graphrag,zhou2025depth}. 
This structure supports retrieval over relationships and enables multi-hop reasoning. While GraphRAG can improve reasoning, it also introduces a qualitatively different attack surface than flat text retrieval: an adversary can chain queries to traverse the graph, expand neighborhoods across turns, and compose relational evidence, potentially amplifying the leakage of structured knowledge. 

Recent work~\cite{liu2025exposing} provides early evidence that GraphRAG systems can leak structured entities and relationships from retrieved subgraphs under black-box query access, highlighting privacy risks beyond conventional RAG. 
However, it remains unclear whether an adaptive, multi-turn adversary can go beyond leaking individual retrieved fragments to reconstruct a large, coherent portion of the hidden graph structure. 
This distinction matters because a reconstructed knowledge graph is a reusable, queryable artifact that can \textit{expose important and sensitive associations} (e.g., medical conditions, communications, organizational ties). Such a relational graph can then enable downstream harms such as linkage and targeted inference, even without verbatim disclosure of long textual descriptions. Graphs are becoming an increasingly important interface for augmenting LLMs with structure, memory, and reasoning support, which makes understanding graph-level security risks increasingly important~\cite{wang2025generalizing,he2025self,luo2026graphs,sahu2026knowledge}.


Therefore, in this paper, we formalize this threat as a 
\emph{query-efficient graph extraction attack}. 
% \emph{budget-constrained graph extraction attack}. 
Given only black-box interactions with a GraphRAG system, the attacker aims to recover its internal graph structure--entities and relations under a fixed query budget. 
Our focus is query efficiency: maximizing recovered graph structure per query while avoiding wasted queries on redundant or low-yield regions.
Compared with prior RAG extraction attack settings, GraphRAG raises additional challenges: (i) GraphRAG responses may mix retrieved subgraph evidence with model-generated text, making entity and edge extraction noisy and prone to hallucination;
(ii) the attacker only has black-box access to the hidden knowledge graph, so naive prompting can waste budget on redundant or low-yield regions; and (iii) effective reconstruction requires long-horizon planning to balance broad exploration with targeted exploitation.

To address these challenges, we propose \textbf{AGEA}, a query-efficient and memory-augmented \textbf{A}gentic \textbf{G}raph \textbf{E}xtraction \textbf{A}ttack framework tailored to GraphRAG.
AGEA coordinates exploration and exploitation using graph-level novelty signals to prioritize high-yield queries and reduce redundancy. It combines an adaptive query planning agent with an external memory of extracted structures and a graph filter agent that reasons over spurious entities/edges before incorporating them into the reconstructed graph. Empirically, these designs enable AGEA to recover a substantially larger portion of the hidden entity–relation graph under the same query budget. 

Our \textbf{main contributions} are: (i) We identify and formalize a novel problem of \emph{graph-level extraction attacks}, where the adversary aims to reconstruct the underlying entity-relation graph of a GraphRAG system under a budgeted and black-box setting;  
(ii) We propose \textbf{AGEA}, the first agentic graph extraction attack framework for GraphRAG; 
(iii) Extensive experiments show that AGEA consistently outperforms baselines under identical query budgets, recovering up to 90\% of nodes and edges with high precision. Our findings demonstrate that modern GraphRAG pipelines can remain vulnerable to structured, long-horizon extraction attacks, underscoring significant privacy risks for graph-augmented LLM systems.

% \begin{itemize}
%     \item We identify and formalize the problem of \emph{graph-level extraction attacks} against GraphRAG systems, extending prior RAG leakage analysis from flat text retrieval to structured knowledge graphs.
%     \item We propose \textbf{AGEA}, the first agentic graph extraction attack framework tailored to GraphRAG, integrating novelty-guided exploration--exploitation, external graph memory, and a two-stage extraction pipeline with lightweight discovery and LLM-based verification.
%     \item We conduct extensive evaluations on medical, agriculture, and literary datasets across Microsoft GraphRAG and LightRAG systems, showing that AGEA consistently outperforms existing baselines under identical query budgets, recovering up to 90\% of nodes and edges with high precision.
%     \item Our findings demonstrate that modern GraphRAG pipelines remain highly vulnerable to structured, long-horizon extraction attacks, highlighting urgent privacy risks for graph-augmented LLM systems.
% \end{itemize}

