\section{Preliminaries}

% \jiahao{There is no motivation before the technical details of the proposed method. I think we should do the following (if we have time):
% \begin{itemize}
%     \item Add a preliminary section on GraphRAG and agents
%     \item Discuss the technical challenges of query-efficient attacks, summarize them at the end of the preliminary section
%     \item Make a clear connection between technical challenges and components of our framework
% \end{itemize}
% } \jiahao{Done}

%{\bf Notations.} 

Next, we introduce GraphRAG and then formalize our threat model for our privacy attack problem.
% for query-efficient graph extraction attack.

\subsection{Graph Retrieval-Augmented Generation}

% To enhance LLM responses with external knowledge, we start from a collection of source documents $\mathcal{D}=\{d_1,\ldots,d_N\}$ used to construct a retrieval database.
Given a collection of source documents $\mathcal{D}=\{d_1,\ldots,d_N\}$, GraphRAG~\cite{edge2024local,guo2024lightrag,jimenez2024hipporag} first construct a knowledge graph $\mathcal{G}=(\mathcal{V},\mathcal{E})$ from $\mathcal{D}$, where $\mathcal{V}$ is the set of nodes (entities) and $\mathcal{E}$ is the set of edges (relations) derived from $\mathcal{D}$. 
Given a user query $q$, the GraphRAG system retrieves a subgraph $\mathcal{G}_q=(\mathcal{V}_q,\mathcal{E}_q)$ from $\mathcal{G}$ (with $\mathcal{G}_q \subseteq \mathcal{G}$) and generates a natural-language response conditioned on the retrieved subgraph as $R = \mathrm{LLM}(q, \mathcal{G}_q)$. 
% \begin{align*}
% R = \mathrm{LLM}(q, \mathcal{G}_q).
% \end{align*}
In practice, retrieved entities and relations may carry textual attributes (e.g., descriptions) that are used as input context for generation.



\subsection{Threat Model} \label{sec:threat_model}

{\bf Attacker's Capability.}  We consider a strict \textit{black-box} setting. The attacker has no access to the internal components of the GraphRAG system, including the retriever, the underlying graph $\mathcal{G}$, and the base LLM parameters. The attacker can only interact with the system via queries and obtain the returned responses. Concretely, the attacker submits a sequence of queries $\{q^{(t)}\}_{t=1}^T$. At each round $t$, the attacker observes the response $
R^{(t)} = \mathrm{LLM}(q^{(t)}, \mathcal{G}_{q^{(t)}})$, 
where $\mathcal{G}_{q^{(t)}}$ denotes the (hidden) subgraph retrieved by the system for $q^{(t)}$.

\noindent{\bf Attacker's Goal.} The attacker aims to recover the system's internal graph $\mathcal{G}$ by adaptively crafting queries and extracting entities/relations from the responses $\{R^{(t)}\}_{t=1}^T$. We focus on query-efficient extraction: the attacker seeks high coverage of both $\mathcal{V}$ and $\mathcal{E}$ while using as few queries as possible.

\noindent{\bf Technical Challenges.} Our setting differs from prior studies that mainly demonstrate that GraphRAG can leak private content or structured facts~\cite{liu2025exposing}. Instead, we study whether an adversary can \emph{systematically reconstruct} the latent knowledge graph under a tight query budget. It is a challenging problem:  
\textbf{(i)} The attacker never observes the retrieved subgraph $\mathcal{G}_{q^{(t)}}$ directly and must infer structure from free-form responses, which can be incomplete or noisy. 
% Moreover, the same entity or relation may appear under different surface forms across rounds (e.g., ``NYC'' vs. ``New York City''), making cross-turn entity/relation merging non-trivial; 
\textbf{(ii)} It is non-trivial to balance \emph{coverage} and \emph{depth}: naive querying quickly becomes redundant as local neighborhoods saturate under limited queries. 


% \noindent{\bf Technical Challenges.} Our setting differs from prior studies that mainly demonstrate that GraphRAG can leak private content or structured facts~\cite{liu2025exposing}. Instead, we study whether an adversary can \emph{systematically reconstruct} the latent knowledge graph under a tight query budget. This is challenging for several reasons:
% \textbf{(i)} The attacker never observes the retrieved subgraph $\mathcal{G}_{q^{(t)}}$ directly and must infer structure from free-form responses, which can be incomplete or noisy. Moreover, the same entity or relation may appear under different surface forms across rounds (e.g., ``NYC'' vs. ``New York City''), making cross-turn entity/relation merging non-trivial.
% \textbf{(ii)} It is non-trivial to balance \emph{coverage} and \emph{depth}: naive querying quickly becomes redundant as local neighborhoods saturate under limited queries. \suhang{we should mention these challenges in the introduction concisely}
% These challenges motivate our agentic graph extraction framework in Section~\ref{sec:framework}.

 