% \section{Conclusion and Future Work}
% This paper studies privacy risks in GraphRAG under a budget-constrained black-box threat model, where an adversary seeks to reconstruct the hidden entity--relation graph. We propose AGEA, an agentic extraction attack that couples novelty-guided exploration--exploitation with a two-stage pipeline (discovery + LLM-based filtering). Across multiple datasets and two GraphRAG systems (M-GraphRAG and LightRAG), AGEA outperforms prior attacks under fixed query budgets, recovering large portions of the hidden graph with high precision. These results show that GraphRAG’s structured retrieval can enable long-horizon leakage and reconstruction of reusable relational structure.

% Future work includes measuring attribute leakage, testing more GraphRAG variants and construction choices~\cite{wang2026graphskill}, and developing defenses against multi-turn structured extraction, such as retrieval-time filtering, response sanitization, and traversal-aware monitoring~\cite{wang2026making,song2026subgraph}. Standardized graph-leakage benchmarks and reporting protocols would improve reproducibility and accelerate safer GraphRAG systems. More broadly, graph-based reasoning is already being explored beyond retrieval QA, including evidence-intensive fact-checking and multimodal reasoning settings~\cite{sengupta2025biomol,zhang2025correct,zhang2026mever}, suggesting that graph-level privacy and extraction risks may need to be studied beyond text-only GraphRAG systems.

% \section*{Limitations}
% \noindent\textbf{Dependence on structured outputs and parsing.}
% AGEA relies on eliciting structured responses from the victim GraphRAG system and then using regex-based parsing in Stage A to extract candidate entities and relations. If a system enforces paragraph-only responses, aggressively rewrites outputs, or applies prompting policies that suppress explicit entity--relation formatting, the reliability of candidate extraction may decrease. Although our Stage B filter mitigates some noise, AGEA remains partly dependent on the victim exposing enough structure in its responses for stable extraction.

% \noindent\textbf{Threat-model scope.}
% Our study focuses on a budgeted black-box extraction setting, where the attacker interacts with the system only through queries and responses under a fixed attack budget. We do not explicitly model deployment-time defenses such as query monitoring, rate limiting, query rewriting, response filtering, or adaptive detection of multi-turn extraction behavior. As a result, our findings should be interpreted as characterizing privacy risk under a clean black-box setting rather than providing a full evaluation of defense-aware attack--defense dynamics.

% \noindent\textbf{System and graph-construction coverage.}
% Our experiments cover two representative GraphRAG systems and several domain datasets, but extraction behavior may vary with the victim’s graph-construction pipeline, retrieval design, and corpus quality. In particular, prior work suggests that GraphRAG evaluation can be sensitive to knowledge-graph construction choices and dataset quality~\cite{zhang2025diagnosing}. Future work should test AGEA across a broader range of GraphRAG architectures, construction settings, and output-control policies to better understand how robust these leakage patterns are across deployments. More broadly, our study is limited to GraphRAG extraction and does not address other graph-specific privacy risks, such as those arising from graph unlearning procedures~\cite{zhang2024graph,zhang2026attack,zhang2026unlearning}.

% \noindent Despite these limitations, our study provides a systematic investigation of query-efficient graph extraction attacks against GraphRAG and shows that substantial privacy leakage can occur even under a strict query budget.

% \section*{Ethical Considerations}

% This work investigates privacy risks in GraphRAG systems by studying query-efficient graph extraction attacks. Because our goal is to characterize how structured knowledge (i.e., entities and relations) can be recovered through black-box interactions, we recognize that the techniques described in this paper have potential dual-use implications.

% The dual-use nature of our study aligns with prior work showing that LLMs can both enable and help detect harmful information operations such as disinformation, underscoring the importance of publishing attack analyses together with stronger defenses~\cite{lucas2023fighting}.

% Despite such risks, we nevertheless believe that publishing these findings is beneficial for the community. We intend to support responsible vulnerability research: by making the attack surface and failure modes explicit, especially those unique to graph-structured retrieval, we enable practitioners to design stronger mitigations (e.g., output controls and privacy-aware GraphRAG architectures) and to evaluate defenses against realistic adversaries. 

% To reduce the risk of harm, all experiments are conducted in a controlled setting using only publicly available data (e.g., GraphRAG-Bench~\cite{xiao2025graphrag}, Agriculture~\cite{zhou2025depth}) and do not involve any private, non-consensual, or newly collected sensitive information. We report results at an aggregate level and focus on measuring leakage trends and query efficiency rather than enabling targeted extractions of real individuals' data. Overall, our objective is to help build safer and more trustworthy GraphRAG deployments by encouraging privacy-by-design practices.

% We used AI-based writing assistants for language polishing (e.g., grammar and clarity). All research ideas, methods, experiments, and claims were developed by the authors, and we remain fully responsible for the content.


\section{Conclusion and Future Work}
This paper studies privacy risks in GraphRAG under a budget-constrained black-box threat model, where an adversary seeks to reconstruct the hidden entity--relation graph. We propose AGEA, an agentic extraction attack that combines novelty-guided exploration--exploitation with a two-stage pipeline (discovery + LLM-based filtering). Across multiple datasets and two GraphRAG systems (M-GraphRAG and LightRAG), AGEA outperforms prior attacks under fixed query budgets, recovering large portions of the hidden graph with high precision. These results show that GraphRAG’s structured retrieval can enable long-horizon leakage of reusable relational structure.

Future work includes measuring attribute leakage, testing more GraphRAG variants and construction choices~\cite{wang2026graphskill}, and developing defenses against multi-turn structured extraction, such as retrieval-time filtering, response sanitization, and traversal-aware monitoring~\cite{wang2026making,song2026subgraph}. Standardized graph-leakage benchmarks and reporting protocols would improve reproducibility and support safer GraphRAG systems. More broadly, graph-based reasoning is already being explored beyond retrieval QA, including evidence-intensive fact-checking and multimodal reasoning~\cite{sengupta2025biomol,zhang2025correct,zhang2026mever}, suggesting that graph-level privacy risks extend beyond text-only GraphRAG.

\section*{Limitations}
\noindent\textbf{Dependence on structured outputs and parsing.}
AGEA relies on eliciting structured responses from the GraphRAG system to enable regex-based parsing for candidate entities and relations extraction. If a system enforces paragraph-only responses, aggressively rewrites outputs, or suppresses explicit entity--relation formatting, extraction reliability may decrease. Although Stage B mitigates some noise, AGEA still depends on the victim exposing enough structure for stable extraction.

\noindent\textbf{Threat-model scope.}
Our study focuses on a budgeted black-box extraction setting, where the attacker interacts with the system only through queries and responses under a fixed budget. We do not model deployment-time defenses such as query monitoring, rate limiting, query rewriting, response filtering, or adaptive detection of multi-turn extraction behavior. Our findings therefore characterize privacy risk in a clean black-box setting rather than full defense-aware attack--defense dynamics.

\noindent\textbf{System and graph-construction coverage.}
Our experiments cover two representative GraphRAG systems and several domain datasets, but extraction behavior may vary with the victim’s graph-construction pipeline, retrieval design, and corpus quality. Prior work suggests that GraphRAG evaluation is sensitive to knowledge-graph construction choices and dataset quality~\cite{zhang2025diagnosing}. Future work should test AGEA across a broader range of architectures, construction settings, and output-control policies to assess the robustness of these leakage patterns. More broadly, our study focuses on GraphRAG extraction and does not address other graph-specific privacy risks, such as those arising from graph unlearning procedures~\cite{zhang2024graph,zhang2026attack,zhang2026unlearning}.

\noindent Despite these limitations, our study provides a systematic investigation of query-efficient graph extraction attacks against GraphRAG and shows that substantial privacy leakage can occur even under strict query budgets.
\section*{Ethical Considerations}

This work studies privacy risks in GraphRAG via query-efficient graph extraction attacks. We acknowledge the dual-use nature of these techniques, consistent with prior work showing that LLMs can both enable and mitigate harmful information use~\cite{lucas2023fighting}. 
We believe disclosing such risks is important for developing effective defenses. By characterizing the attack surface of graph-structured retrieval, our findings can inform mitigation strategies such as output controls and privacy-aware GraphRAG design.
All experiments are conducted in controlled settings using publicly available data (e.g., GraphRAG-Bench~\cite{xiao2025graphrag}, Agriculture~\cite{zhou2025depth}). We report only aggregate results and focus on leakage trends and query efficiency, without enabling targeted extraction of real individuals’ data.
We used AI-based tools for language polishing. All research ideas, methods, and conclusions are the authors’ own, and we take full responsibility for the content.

\section*{Acknowledgments}
This work was supported in part by U.S. NSF awards \#2114824 and \#2438810, the Army Research Office (ARO) under grant number W911NF-21-1- 0198, and the Cisco Faculty Research Award. 
Some experimental results were obtained using computational resources provided by CloudBank, supported through U.S. NAIRR award \#240336.

