Retrieval-augmented generation (RAG) and its graph-based extensions (GraphRAG) are effective paradigms for improving large language model (LLM) reasoning by grounding generation in external knowledge. However, most existing RAG and GraphRAG systems operate under static or one-shot retrieval, where a fixed set of documents is provided to the LLM in a single pass. In contrast, recent agentic search systems enable dynamic, multi-round retrieval and sequential decision-making during inference, and have shown strong gains when combined with vanilla RAG by introducing implicit structure through interaction.
This progress raises a fundamental question: \textit{can agentic search compensate for the absence of explicit graph structure, reducing the need for costly GraphRAG pipelines?}
To answer this question, we introduce RAGSearch, a unified benchmark that evaluates dense RAG and representative GraphRAG methods as retrieval infrastructures under agentic search. RAGSearch covers both training-free and training-based agentic inference across multiple question answering benchmarks. To ensure fair and reproducible comparison, we standardize the LLM backbone, retrieval budgets, and inference protocols, and report results on full test sets. Beyond answer accuracy, we report offline preprocessing cost, online inference efficiency, and stability. Our results show that agentic search substantially improves dense RAG and narrows the performance gap to GraphRAG, particularly in RL-based settings. Nevertheless, GraphRAG remains advantageous for complex multi-hop reasoning, exhibiting more stable agentic search behavior when its offline cost is amortized. Together, these findings clarify the complementary roles of explicit graph structure and agentic search, and provide practical guidance on retrieval design for modern agentic RAG systems.
The benchmark code and evaluation scripts are publicly available at \href{https://github.com/FanDongzhe123/RAGSearch}{https://github.com/FanDongzhe123/RAGSearch}.

% Retrieval-augmented generation (RAG) and its graph-based extensions (GraphRAG) represent two dominant approaches for grounding large language models with external knowledge. While GraphRAG introduces explicit structural bias through graph construction and traversal, it also incurs substantial offline preprocessing cost. At the same time, recent agentic search systems enable multi-round retrieval and sequential decision-making, raising a fundamental question: can agentic search compensate for the absence of explicit graph structure in standard RAG pipelines? To answer the question, we present RAGSearch, a unified benchmark that evaluates RAG and GraphRAG as retrieval infrastructures under multiple inference paradigms, including single-shot inference, training-free agentic search, and training-based agentic search. Our study covers six representative retrieval pipelines—vanilla dense RAG and five well-established GraphRAG methods—and evaluates them on multiple question answering benchmarks spanning single-hop and multi-hop reasoning. To ensure fair comparison, we standardize the LLM backbone, retrieval budgets, inference protocols, and evaluate on full test sets.
% Beyond answer accuracy, we report offline preprocessing cost, online inference efficiency, and stability under agentic control. \qyt{Our results show that agentic search substantially improves RAG and narrows the performance gap to GraphRAG, particularly under training-free settings. However, GraphRAG remains advantageous for complex multi-hop reasoning, providing more efficient and stable search behavior when its offline cost is amortized. These findings clarify the complementary roles of explicit graph structure and agentic reasoning, and provide practical guidance on when GraphRAG remains necessary in modern agentic retrieval systems.} The benchmark code can