% TR Foundational Research style template
\documentclass[logo, address]{trfr}

% Bibliography support
\usepackage{natbib}

% To allow colored text
\usepackage{xcolor}

%Including images in your LaTeX document requires adding
%additional package(s)
\usepackage{graphicx}

\usepackage{algorithm,algpseudocode}
\usepackage{algorithmicx}

\usepackage{multirow}

\usepackage{amssymb}

\usepackage{threeparttable}

\usepackage{hyperref}

\usepackage[most]{tcolorbox}
\usepackage{listings}

\usepackage{soul}
\definecolor{my_lightblue}{rgb}{0.85,0.95,1.0}
\sethlcolor{my_lightblue}

% If the title and author information does not fit in the area allocated, uncomment the following
%
%\setlength\titlebox{<dim>}
%
% and set <dim> to something 5cm or larger.

\title{Knowledge Graph-Assisted LLM Post-Training for Enhanced Legal Reasoning}

\abstract{
LLM post-training has primarily relied on large text corpora and human feedback, without capturing the structure of domain knowledge. This has caused models to struggle dealing with complex reasoning tasks, especially for high-stakes professional domains. In Law, reasoning requires deep understanding of the relations between various legal concepts, a key component missing in current LLM post-training. In this paper, we propose a knowledge graph (KG)-assisted approach for enhancing LLMs' reasoning capability in Legal that is generalizable to other high-stakes domains. We model key legal concepts by following the \textbf{IRAC} (Issue, Rule, Analysis and Conclusion) framework, and construct a KG with 12K legal cases. We then produce training data using our IRAC KG, and conduct both Supervised Fine-Tuning (SFT) and Direct Preference Optimization (DPO) with three state-of-the-art (SOTA) LLMs (30B, 49B and 70B), varying architecture and base model family. Our post-trained models obtained better average performance on 4/5 diverse legal benchmarks (14 tasks) than baselines. In particular, our 70B DPO model achieved the best score on 4/6 reasoning tasks, among baselines and a 141B SOTA legal LLM, demonstrating the effectiveness of our KG for enhancing LLMs' legal reasoning capability.
}

% Authors and affiliations
\author[1]{Dezhao Song}
\author[1]{Guglielmo Bonifazi}
\author[1,*]{Frank Schilder}
\author[1,2,*]{Jonathan Richard Schwarz}

\affiliation[1]{Thomson Reuters Foundational Research}
\affiliation[2]{Imperial College London}

% Equal contribution marker
\contribution[*]{Equal contribution}

% Correspondence email
\correspondence{\{first.last\}@thomsonreuters.com}

\begin{document}
\maketitle

\input{introduction}

\input{related_work}

\input{overview}

\input{data_generation}

\input{experiment}

\input{conclusion}

\input{limitation}

%\section*{Acknowledgments}

% Bibliography
\bibliographystyle{plainnat}
\bibliography{kg}

\appendix

\input{appendix/appendix_benchmark}

\newpage
\input{appendix/appendix_delta_stance}

\input{appendix/appendix_hyperparameter}

\newpage
\input{appendix/appendix_llama}

\newpage
\input{appendix/appendix_prompts}

\end{document}
