\section{Related Work}
\label{section:related_work}

\subsection{LLM-based KG Construction}
\label{section:related_work_kg_construction}

KG creation pipelines typically consist of two steps: Named Entity Recognition (NER) and Relation Extraction (RE). Prompting-based strategies have proven to be effective, addressing both tasks jointly \cite{DBLP:journals/corr/abs-2404-16130,guo2024lightrag} or separately \cite{jimenez2024hipporag,gutierrez2025from}. Compared to traditional methods, LLMs are also capable of extracting additional metadata, such as verbose entity descriptions or numerical scores measuring relation strength \cite{guo2024lightrag}.

%Furthermore, LLMs are capable of schema-free KG creation or easy adaptation to existing ones.
Focusing on KG quality, \citet{zhang2024extract} defined a three-stage solution to ground LLMs into existing KGs, or to canonicalize one derived via open extraction. \citet{DBLP:conf/acl/HanCBS24} trained small models for output quality verification and iteratively improving the quality of the original KG, while \citet{zhu2024llms} developed a multi-agent framework to guide this refinement process by integrating external knowledge.

\subsection{Graph-based LLM Reasoning}
\label{section:related_work_llm_reasoning}

Researchers have utilized LLMs and graphs to address complex reasoning scenarios \cite{pan2024unifying}. GraphRAG \cite{DBLP:journals/corr/abs-2306-16092} organizes text corpora as a KG, and reasons over community descriptions to answer queries. This enables LLMs to handle questions that require a general understanding of the corpus and inspired follow-up methods to explore structured representations to improve Retrieval Augmented Generation (RAG) pipelines \cite{peng2024graph, han2024retrieval}.

A recurring theme in several of these works is to present the retrieved information to LLMs in structured formats, e.g., triples or relational paths, which has improved reasoning fidelity and quality \cite{DBLP:conf/iclr/MaXJLQYMG25,sun2024thinkongraph,liu2024knowledge,wen2024mindmap}. Rather than using graphs for retrieving structured information, \citet{cheng2024structure} reformulate the input query as a graph, and propose a multi-stage prompting pipeline to reason over the input graph for query answering. The authors claimed that the method reflects how humans often approach complex problems.

In addition to fostering reasoning, graphs were also used to model the reasoning process itself. Both Tree-of-Thoughts \cite{yao2023tree} and Graph-of-Thoughts \cite{besta2024got} improved over the classical Chain-of-Thought idea that lacks the capability of expressing complex thought processes, such as backtracking on unpromising steps or combining ideas from different branches.

\subsection{KG-LLM Synergy in the Legal Domain}
\label{section:kg_llm_legal}

%In legal, researchers have proposed a series of ideas for graph-based modeling and how to combine KGs and LLMs.
\citet{tang2024caselink} represented legal cases and charges as nodes, and connected them using existing metadata, such as case-case citations and case-charge relationships. \citet{dhani2021similar} developed a more complex pipeline to extract entities and relations from Indian cases, judgments and laws using traditional NER and RE techniques for the purpose of finding similar cases. 

More recently, \citet{chen2024leverage} used an LLM to extract triples from Chinese cases and criminal law articles by following a pre-defined schema.
%, showing the effectiveness of KGs and LLMs other than Common Law.
Similar to our approach, \citet{tang2024casegnn++,tang2024casegnn} relied on an LLM to represent case legal issues and facts as a KG (though without considering precedents). This offered an initial, though partial, representation of a case via the IRAC framework.

While being effective in solving important tasks, \citet{HANNAH2025100843} showed that serious legal implications might arise from LLM responses, and proposed a KG-RAG solution to address potential legal concerns. Similarly, \citet{10.1145/3627673.3680268} combined KG and RAG to develop an Italian legislative platform to support law analysis, drafting, landscape identification and complexity monitoring. Finally, ChatLaw \cite{DBLP:journals/corr/abs-2306-16092} is a multi-agent system for legal consulting, and utilizes KGs in intermediate steps to assist answering user requests.

Instead of extracting specific entities (e.g., Person, Location, etc.), our work builds KGs that model key legal concepts (such as Facts and Rules). Also, different from existing methods that combine LLMs with graphs, our novelty lies in the use of graph structure for domain-specific LLM post-training. Finally, while previous approaches studied partial modeling of legal reasoning, our IRAC KG offers a more comprehensive coverage of the important legal reasoning components.
