\section{Related Works}
\subsection{LLM-powered Multi-Agent Systems} 

Recent studies introduce a surge of multi-agent systems to incentivize LLMs' swarm intelligence in complex scenarios. The communication topology occupies a central position in them and includes multiple structures. Among them, non-interactive systems organize agents parallelly without explicit communication, such as Mixture-of-Agents~\citep{wangmixture} and LLM-Debate~\citep{estornell2024multi}; Chain MAS arranges agents sequentially as a workflow, such as MetaGPT~\citep{hong2023metagpt} and ChatDev~\citep{qian2024chatdev}; Tree MAS works in a task-splitting mode with a chief node and hierarchical child nodes~\citep{yao2023tree}; Star MAS works in a task-assignment mode with a central node and multiple edge nodes, seen in AutoGen~\citep{wu2024autogen} and MiniGrid~\citep{zhou2024large}; Graph MAS, as the most general form, can represent all of above-posed topologies and are widely applied~\citep{langgraph,zhuge2024gptswarm,wu2024autogen}.


\subsection{Self-evolving Multi-Agent Systems} 
To improve efficiency, recent research interests shift towards ``self-evolving'' MAS~\citep{wang2025evoagentx,fang2025comprehensive}, which can contribute to fully-automated MAS customization for changing tasks. These studies characterize multi-agent communication topologies as graphs~\cite{liu2023dynamic,zhuge2024gptswarm,GDesigner} to organize and represent relationships between agents. Compared with conventional static communication topologies, they support task-aware~\citep{liu2023dynamic,zhuge2024gptswarm} or even query-aware~\citep{GDesigner,li2025assemble,zhang2025safesieve} dynamic communication topology customization. We categorize them into Spatial Evolving and Temporal Evolving MAS. For Spatial Evolving MAS, they mainly focus on the performance, robustness, efficiency, and redundancy~\citep{zhang2025safesieve} when customizing the topology. However, they pay little attention to temporal scheduling which is crucial in MAS with dialogue-wise varying resource demands. For Temporal Evolving MAS~\citep{zhangaflow,niu2025flow,lee2025confidence}, though they consider the temporal scheduling in different iterations, most of them neglect utilizing the collaborative capability of MAS inside each iteration. In this work, we propose \ourmethod, the first Spatio-Temporal Evolving MAS, which supports temporal scheduling for spatial communication topologies.