\section{Evaluation}%
\label{sec:evaluation}

After introducing our evaluation setup in Section~\ref{subsec:evaluation-setup}, we compare our approach with state-of-the-art approaches in Section~\ref{subsec:evaluation-best-approach}. In Sections~\ref{subsec:evaluation-ablation-analysis} and~\ref{subsec:evaluation-walk-variants}, we perform an ablation analysis to identify the components that contribute most towards our high performance. Section~\ref{subsec:evaluation-dataset-characteristics} studies the performance based on dataset characteristics. How the learned concepts evolve from generation to generation is exemplified in Section~\ref{subsec:evaluation-example}, and Section~\ref{subsec:effectiveness-over-runtime} investigates performance as a function of runtime.

\subsection{Evaluation Setup}%
\label{subsec:evaluation-setup}

Our evaluation was performed with SML-Bench~\citep{Westphal2019SML-Bench}, a benchmarking framework for structured machine learning.

\paragraph{Datasets and Learning Problems}

\input{figures/table-evaluation-datasets}

Table~\ref{tab:evaluation-datasets} gives an overview of the nine datasets we employ for our evaluation. In contrast to SML-Bench's original configuration~\citep{Westphal2019SML-Bench},
we added the Family dataset~\citep{Lehmann2009DL-Learner}, which is provided as part of DL-Learner and often used to evaluate structured machine learning approaches~\citep{Tran2017Parallel}.
Per dataset, the SML-Bench framework provides one learning problem, i.e., one set of positive and negative examples. For the Family dataset, the concept of an \texttt{Uncle} is to be learned.

\paragraph{Baselines}

We compare our novel approach EvoLearner with four baselines: DL-Learner (CELOE), DL-Learner (OCEL), Aleph, and SPaCEL\@. Except for SPaCEL, all approaches are part of the SML-Bench framework~\citep{Westphal2019SML-Bench}. CELOE and OCEL employ inductive logic programming with downward refinement operators with different heuristics. Aleph serves as an example of a bottom-up approach~\citep{Muggleton1995Inverse}. SPaCEL~\citep{Tran2017Parallel} employs a hybrid approach of upward and downward refinements. We also experimented with DL-FOIL~\citep{Fanizzi2008DL-FOIL,Fanizzi2018DLFoil,Rizzo2020DL-Foil}; however, it assumes the existence of a perfect solution, which covers all positive examples and none of the negative examples. Since almost none of the SML-Bench learning problems have such a perfect solution with a reasonable length, DL-FOIL did not terminate and we excluded it from our experiments. Additionally, we experimented with Metagol~\citep{Muggleton2013MetainterpretiveLA}. However, Metagol did not terminate within our timeout for any of the datasets, corroborating previous findings that it has problems with larger datasets and that finding a suitable set of metarules for each dataset is a challenging, unsolved task~\citep{Dumancic2020Comparative,Cropper2020Inductive}. Hence, we excluded it from our experiments.

\paragraph{Hyperparameters}
As outlined in Section~\ref{sec:approach}, we employ a population size of~800 with~200 generations, a tournament size of~7, a crossover probability of~90\%, a mutation probability of 10\%, and a static depth limit of 17.

\paragraph{Cross-validation and Evaluation Metrics}
As SML-Bench~\citep{Westphal2019SML-Bench}, we employ 10-fold cross-validation, i.e., all positive and negative examples for each learning problem are randomly shuffled and split into 10~folds. In each round, the examples of one fold are used as the validation set and the other folds are used as the training set. Finally, the performance on all validation folds is averaged. As commonly done~\citep{Westphal2019SML-Bench}, we evaluate the predictive performance of the approaches in terms of accuracy and $F_1$-measure, and the explainability in terms of concept length~\citep{Tran2017Parallel}. Following SML-Bench, we employ a timeout of 5~minutes per fold.

\paragraph{Reproducibility}
To ensure the reproducibility of our experiments, the code underlying our research is publicly available.%
\footnote{\url{https://github.com/dice-group/EvoLearner}}
It enables those who wish to follow up on our work to replicate the plots and performance values reported.
We implemented EvoLearner in Python~3.6.9 with the evolutionary framework DEAP~\citep{Fortin2012DEAP}~1.3.1  and the ontology framework Owlready2~\citep{Lamy2017OWL}~0.29. For evaluation, we employ SML-Bench~\citep{Westphal2019SML-Bench}~0.3.0, DL-Learner~\citep{Lehmann2009DL-Learner}~1.4.0, and the latest version of SPaCEL~\citep{Tran2017Parallel}. Our experiments were run on a machine with 32~GB memory and an Intel Core i7-9750H with 2.6~GHz.

\subsection{Evaluation of EvoLearner}%
\label{subsec:evaluation-best-approach}

\input{figures/table-evaluation-results}

Table~\ref{tab:evaluation-results} evaluates our EvoLearner approach on the benchmarking datasets and compares it with state-of-the-art baselines. Our approach outperforms each of the baselines on at least~7 out of~9 datasets in terms of accuracy and $F_1$-measure. In each of the 8~pairwise comparisons of EvoLearner with a baseline according to $F_1$-measure or accuracy, we can reject the null hypothesis that both approaches are equally good with $p < 0.05$ (according to the non-parametric Wilcoxon signed-rank test). Looking at the lengths of learned concepts, we find that our approach generates much shorter concepts than SPaCEL and slightly longer concepts than CELOE and OCEL on most datasets. A manual inspection revealed that \mbox{SPaCEL} generates overly verbose expressions with many redundant and unnecessary parts, whereas CELOE's and OCEL's concepts are often incomplete. In the following, we show example solutions found by EvoLearner for the \textit{Premier League} and \textit{Carcinogenesis} learning problems. In case of \textit{Premier League}, the objective is to find descriptions of soccer goalkeepers based on their statistics; for example, the concept of a goalkeeper can be characterized by the number of shots on the target conceded. In case of \textit{Carcinogenesis}, molecules causing cancer can be characterized by certain chemical structures. Another example is the solution~\eqref{eq:expected-solution} found by EvoLearner for the \texttt{Uncle} problem.

\medskip

\noindent
\emph{Premier League:}\quad\\
$\texttt{Player} \sqcap \exists \texttt{has\_action.}(\texttt{shots\_on\_target\_conceded} \geq \texttt{2})$

\medskip

\noindent
\emph{Carcinogenesis:}\quad\\
$(\texttt{drosophila\_slrl} = \texttt{true}) \ \sqcup \ (\texttt{amesTestPositive} = \texttt{true}) \ \sqcup$
$(\geq 4 \ \texttt{hasStructure.Halide}) \ \sqcup$
$(\texttt{chromaberr} = \texttt{false})$

\input{figures/table-ablation-analysis}

\subsection{Initialization and Data Properties}%
\label{subsec:evaluation-ablation-analysis}

To investigate the cause of EvoLearner's high performance, we perform an ablation study and investigate the following variants of EvoLearner: (1)~without random walk initialization, (2)~without data properties, and (3)~without both. Instead of our random walk initialization, we employ the \textsc{rampedHalfHalf} initialization method with a maximal depth of 6, which combines the \textsc{Full} and \textsc{Grow} methods and has been found to be one of the best default initialization methods~\citep{Koza1992GP}.

Table~\ref{tab:ablation-analysis} shows that both our novel initialization method and our support for data properties lead to an increase in performance on almost all datasets. For tackling the \textit{Hepatitis}, \textit{Mammographic}, \textit{Mutagenesis}, \textit{NCTRER} and \textit{Pyrimidine} learning problems, sufficient support for data properties and cardinality restrictions is crucial. Unsurprisingly, on the \textit{Lymphography} dataset, which does not contain any properties, neither our initialization nor support for data properties could boost performance. On \textit{Mutagenesis} and \textit{NCTRER}, we achieve an $F_1$-measure of $1.00$ with and without our initialization technique since the optimal solution only requires finding the suitable value for one data property.

\subsection{Variants of Biased Random Walks}%
\label{subsec:evaluation-walk-variants}

\input{figures/table-evaluation-random-walk-init}

We examined why the biased random walk method for initialization works so well by experimenting with different variants thereof: leaving out type or path information (see Section~\ref{subsec:initialization}). In
the first variant, we omitted Step (\ref{item1-rw}) from the random walk method, so we did not select a type during the initialization and only selected the paths afterward. For the second variant, we omitted Step (\ref{item2-rw}) and Step (\ref{item3-rw}) so the resulting concepts in the initial population only consisted of the selected type in Step (\ref{item1-rw}). Table~\ref{tab:random_walk_init_comparison}
shows that both type and path information are important to get the highest performance.  
However, path information was more important than type information, especially for \textit{Hepatitis} and \textit{Pyrimidine}. Note that the variant without types still outperforms the variant without random walks and the variant without paths is about as good.

\subsection{Dataset Characteristics}%
\label{subsec:evaluation-dataset-characteristics}

We observed that our random walk/bottom-up initialization starting at the ABox tends to be particularly good for datasets whose solutions require long class expressions and for datasets that contain many object properties in the TBox (Table~\ref{tab:evaluation-datasets} shows the number of object properties, Table~\ref{tab:evaluation-results} [bottom] the concept lengths, and Table~\ref{tab:evaluation-results} [top] the performance). This can be explained as follows: Top-down approaches randomly refining the top concept $\top$ have a hard time finding sensible concepts by chance if the class expressions are long and the TBox contains many object properties due to combinatorial explosion. On the other hand, our bottom-up initialization based on random walks only yields combinations of object properties that do appear in the ABox. As shown in Table~\ref{tab:ablation-analysis}, this effect is particularly pronounced on the datasets \textit{Carcinogenesis}, \textit{Family} and \textit{Hepatitis}. 

\subsection{Example of Emerging Concepts}%
\label{subsec:evaluation-example}

\input{figures/table-evaluation-example}

Table~\ref{tab:evaluation-example} provides an example of emerging concepts from generation to generation on the \textit{Uncle} learning problem. From each generation's population, the best concept according to the fitness function is shown. It can be seen that up to generation 11, concepts become more accurate on the training set while also becoming longer. Afterwards, concepts maintain their good accuracy while becoming shorter. The best concept is reached after 29 generations. This pattern of growing and shrinking concepts is typical and we observed it for many datasets and learning problems.

\input{figures/figure-runtime-effectiveness}

\subsection{Effectiveness Depending on Runtime}%
\label{subsec:effectiveness-over-runtime}

In Figure~\ref{fig:runtime-effectiveness}, we examine the relationship between performance and runtime. The time for loading the datasets is not taken into account. For EvoLearner, the time starts right before the calculation of the splits and the random-walk initialization; for SPaCEL and CELOE, time starts after the initialization of the search and before the start of the refinements; for Aleph, time starts immediately as per SML-Bench. After the random-walk initialization, EvoLearner achieves an $F_1$-measure of~0.83 averaged over all datasets. This number increases to~0.88 after the evolutionary algorithm has run for 5~seconds. Except for \textit{Carcinogenesis}, EvoLearner reaches 200 generations within the first 60 seconds, with further generations hardly increasing performance. A manual analysis revealed that for \textit{NCTRER} and \textit{Mutagenesis}, our initialization almost always generated an individual with the correct data property and split within the initial population. SPaCEL and CELOE initially predict \texttt{Thing}, yielding an $F_1$-measure of~0.65. SPaCEL finishes in under a second for most datasets, except for \textit{Carcinogenesis}, \textit{Lymphography} and \textit{Mammographic}. Therefore, performance hardly improves afterwards. CELOE struggles to improve on \textit{Carcinogenesis}, \textit{Lymphography}, \textit{Mammographic}, \textit{Mutagenesis} and \textit{NCTRER}. On \textit{Pyrimidine}, the performance of CELOE even decreases over time due to overfitting. The jump between 2 and 3 minutes is due to an increase in $F_1$-measure on \textit{Premier League}. Aleph does not provide partial solutions, and the jumps of average performance correspond to Aleph's solution to \textit{NCTRER} after about 10~seconds and Aleph's solution to \textit{Carcinogenesis} and \textit{Premier League} after about 40~seconds.
