\section{Discussion}%
\label{sec:discussion}

\paragraph{Open-world vs.\ Closed-world Reasoning.} Closed-world reasoners~\citep{Kroetzsch2012Description} assume every fact not explicitly stated to be true to be actually false. Open-world reasoners keep unspecified information open and require a logical consequence to be true in all conceivable states of the world. In this work, we employ a closed-world reasoner for the following reasons: (1)~Our baseline systems employ closed-world reasoning. (2)~
Closed-world reasoners may be less surprising to new users%
\footnote{\url{https://spinrdf.org/shacl-and-owl.html}}
~\cite{Ruttenberg2005Experience}.
(3)~Closed-world reasoners are a lot faster, allowing the evaluation of many more concepts in the same amount of time. Our code can be adapted to employ an open-world reasoner, which is available as part of the Owlready2 library~\cite{Lamy2017OWL}.

\paragraph{Datatypes.}
Our current implementation supports Booleans as well as numbers including double values and integers. Extending this to dates is straightforward as dates can be sorted, and thresholds can be computed in the same way as for numbers. An extension to strings can be realized by treating them as atomic concepts.

\paragraph{Initialization of Baselines}
Our initialization strategy is specifically tailored towards evolutionary algorithms and our crossover and mutation operators. Applying our initialization strategy to our baselines would lead to a significantly smaller search space since concepts that are more general than our initial concepts would not be found by downward refinement operators. We leave it to future work to develop novel initialization strategies specifically tailored to inductive logic programming with refinement operators.
