\section{Preliminaries} \label{preliminaries}

In this section, we first describe the underlying graph and graph exploration models in \S\ref{graph_classes} and \S\ref{graph_exploration} respectively.
After that we briefly describe the general idea of competitive analysis and online algorithms in \S\ref{competitive}.

\subsection{Graph Classes}\label{graph_classes}

We consider undirected weighted Graphs, $G=(V,E)$, where edge weights
will be denoted as $l(e)$ for an edge $e\in E$. Edge weights are nonzero
and nonnegative. We call the weight of an edge its length. We use
$d(v,w)$ to describe the shortest path between two nodes $v,w \in V$. The length
of a path is the sum of the lengths of all edges on that path. We consider
two graph classes: cycles and tadpole graphs, which are defined as followed:

\paragraph*{Cycle} A cycle $C=(V,E)$ is a connected graph, where each node in $V$ has degree 2.
We call $L = \sum_{e \in E}^{}l(e)$ the length of the cycle.

\paragraph*{Tadpole Graph} A tadpole graph $T=(V,E)$ is a graph, which consists of a cycle to which
a tail is attached. In a tadpole graph we denote the length of the cycle as $L_c$ and the length
of the tail with $L_t$. We call the cycle node with degree 3, to which the tail is attached, the intersection $v_i$.
The single node with degree 1 on the tail will be called the end of the tail $v_t$.

\subsection{Online Graph Exploration}\label{graph_exploration}
In the online graph exploration problem, all nodes of a given weighted graph $G=(V,E)$ have to be visited by an agent $a$, starting and ending on a specific node $s \in V$.
The graph is initially unknown, except for the starting node $s$ and its neighborhood $N(s)$. Whenever the agent traverses an edge to a yet unvisited node $v$, all
adjacent edges, as well as $N(v)$ is revealed. Nodes have labels and can be distinguished, but the labels do not provide any further information about the graph to the agent.
When the agent is located on some node $v$ and the exploration is not finished, it can either choose an edge $e$ adjacent to $v$, which it will traverse in $l(e)$ time,
or it can choose to wait on the current node while time progresses.\\
We consider graph exploration with $k \in \mathbb{N}$ agents $a_1,...,a_k$, for which we assume unlimited computational power and shared knowledge, meaning that as soon as any agent learns
something about the neighborhood of a node, all other agents instantly receive the same information.\\
A graph is considered explored, when each node in $V$ has been visited by any agent, and
all $k$ agents have returned to the starting node $s$. All agents move at identical speed, taking a time of $l(e)$ for traversing some edge $e$. When the exploration is finished, the time passed is denoted as $\mathcal{T}$, while the distance traversed by the
agent $a_i$ is denoted as $d(a_i)$. The goal of a graph exploration strategy, is to minimize the cost of the exploration. We consider two models for the cost of an exploration:

\paragraph*{Time Model} 
In the time model the cost of the exploration is the entire exploration time $\mathcal{T}$ taken until the last agent returns to $s$ after all nodes of the graph have been visited.

\paragraph*{Energy Model}
In the energy model the cost of the exploration is the maximum distance \linebreak$\max(d(a_1), ... ,d(a_k))$ traversed by any agent during the exploration of the graph.

\begin{figure}[H]
    \begin{center}
        \begin{tikzpicture}[node distance={15mm}, thick, main/.style = {draw, circle}] 
            \node[main, minimum size=0.5cm] (2) {}; 
            \node[main, minimum size=0.5cm] (3) [above right of = 2, above=-1.5em] {$_{v_i}$ }; 
            \node[main, minimum size=0.5cm] (4) [above left of = 3, above=-1.5em] {};
            \node[main, fill=gray!50, minimum size=0.5cm] (6) [right of = 3, right=-0.5em] {$_{s}$ };
            \node[main, minimum size=0.5cm] (7) [left of = 2, left=-0.5em] {$_{v_s}$ };
            \node[main, minimum size=0.5cm] (8) [left of = 4, left=-0.5em] {$_{v_\ell}$};
            \node[main, minimum size=0.5cm] (9) [right of = 6, right=-0.5em] {$_{v_t}$ };
            \draw (7) [bend left] to node[left] {$e_{mid}$} (8);
            \draw (2) [bend right] to node[right] {} (3);
            \draw (3) [bend right] to node[above right] {} (4);
            \draw (3) [] to node[above] {} (6);
            \draw (2) [] to node[below] {} (7);
            \draw (4) [] to node[above] {} (8);
            \path [red, thick, dashed, ->] (3) edge[out=90,in=45] node[above] {{$d_\ell$}} (8);
            \path [blue, thick, dashed, ->] (3) edge[out=270,in=315] node[below right] {{$d_s$}} (7);
            \path [olive, thick, dashed, ->] (6) edge[out=15,in=165] node[above] {{$d_t$}} (9);
            \path [violet, thick, dashed, ->] (6) edge[out=165,in=15] node[above] {{$d_i$}} (3);
            \draw (6) [] to node[above] {} (9);
        \end{tikzpicture} 
    \end{center}
    \caption[Tadpole example]{Tadpole Graph Example. The paths $p_\ell, p_s, p_i, p_t$ and the edges $e_{mid}$ and $e_{max}$ are~marked.}
    \label{Example}
\end{figure}

For any tadpole graph, we denote the longest edge of the cycle as $e_{max}$. If multiple edges share the highest length, one of these edges can be picked at random
to be $e_{max}$. We call the point on the cycle with exactly distance $L_c/2$ in both directions to either
the starting point $s$ (when $s$ in on the cycle), or the intersection $v_i$ (when $s$ is on the tail), the midpoint $m$ of the cycle. If $m$ falls onto an edge, this edge is
called $e_{mid}$. If $m$ falls onto a node, the node is called $v_{mid}$. In this case we consider $l(e_{mid}) = 0$.
We consider $e_{mid}=(v_l, v_s)$. If $e_{mid}$ does
not exist, we consider $v_l = v_s = v_{mid}$. 
We denote $p_l$ and $p_s$ with length $d_l$ and $d_s$ as edge-disjoint paths from $s$ (if $s$ is located on the cycle) or $d_i$ (if $s$ is located on the tail) to $v_l$ and $v_s$ respectively, 
where $p_l$ and $p_s$ combined contain all edges of the cycle except $(v_l, v_s)$. We always assume w.l.o.g that $d_s \leq d_l$.\\
The path $p_i$ with length~$d_i$ always denotes the shortest path from $s$ to $v_i$. 
The path $p_t$ with length~$d_t$ denotes the path from $v_i$ to $v_t$ when $s$ is located on the cycle. When $s$ is located on the tail, $p_t$ denotes the path from $s$
to $v_t$. An example of a tadpole graph and the labeled paths and edges is given in Figure \ref{Example}.

\subsection{Competitive Analysis}\label{competitive}
Algorithms where the input is revealed piece by piece instead of being known from the start are called \textit{online algorithms}. For the assessment of online algorithms,
their result gets compared to the optimal result that can be achieved by an algorithm which knows the whole input from the start. In our case, we compare the online
exploration strategies to the optimal paths that can be found when the entire graph is already known. For this we use the definition also used by Brandt et al.~\cite{Brandt2020}, but extend it
by adding the number of agents $k$ to the problem instance.

\paragraph*{Competitive Ratio} Let $opt(G,s,k)$ be the cost of an optimal (offline) solution
for a graph exploration instance, while $\onl_{A}(G,s,k)$ is the cost of a solution found by some online algorithm. We call $\frac{\onl_{A}(G,s,k)}{opt(G,s,k)}$ the \textit{competitive ratio}
for this given instance. Given a graph class $\mathcal{G}$ and a number of agents $k \in \mathbb{N}$, we say that an Algorithm $A$ is $c$-competitive for $\mathcal{G}$ and $k$, if $c$ is the supremum for
the competitive ratio of $A$ in all possible graph exploration instances $(G =(V,E) \in \mathcal{G}, s \in V, k)$. Note that by this definition, an algorithm cannot be less than $1$-competitive.\\
If an exploration strategy is
$c$-competitive for the time model, it is at most $c$-competitive for the energy model, since in an exploration that takes some time $\mathcal{T}$, no agent can traverse a distance further than $\mathcal{T}$,
while in the offline case the maximum distance traversed by any agent matches the general exploration time.