\section{ALE on Tadpole Graphs} \label{ale_tad}

In this section, we extend the \textit{ALE (Avoid-Longest-Edge) Algorithm} by Higashikawa et al.\ \cite{Higashikawa2012} to a strategy for tadpole graph exploration.
The \textit{ALE Algorithm} uses two agents to explore a cycle, by sending the agents clockwise and counterclockwise respectively,
moving only the agent that sees the edge with lower weight at a time. If both agents see edges with the same weight, the edge that is traversed is chosen at random. 
When all nodes have been visited, both agents have full knowledge of the graph and return to the start via their shortest paths. The \textit{ALE Algorithm} reaches a 
competitive ratio of $1.5$ on cycles in the time model.
We first show a competitive lower bound of $2$ for the exploration of tadpole graphs with $k\geq3$ agents for any \textit{ALE}-based exploration strategy.
We then prove that an exploration strategy based on the \textit{ALE Algorithm} is $3$-competitive when using $k=3$ agents and $2$-competitive when using $k=4$ agents 
on tadpole graphs in the time model. 

\paragraph*{Lower Bound}

We show that when starting on a node of the cycle, an adversary can
always hide the tail of the tadpole graph behind the initially seen, but most expensive edge of the tadpole graph, leading to a competitive lower bound
of $2$ for any \textit{ALE}-based exploration of tadpole graphs using at least $k\geq3$~agents.

\begin{theorem}[Lower bound of ALE]\label{AleLower}
    Given $k\geq3$ agents, a strategy that tries to avoid the longest edge of a given graph cannot have a competitive ratio of 
    less than two for the class of tadpole graphs.
\end{theorem}

\begin{figure}[H]
    \begin{center}
    \begin{tikzpicture}[node distance={15mm}, thick, main/.style = {draw, circle}, scale=0.5] 
        \node[main, fill=gray!50, minimum size=0.5cm] (2) {$_{s}$ }; 
        \node[main, minimum size=0.5cm] (3) [above right of = 2] {$_{c_2}$ }; 
        \node[main, minimum size=0.5cm] (4) [above left of = 3] {$_{c_1}$ };
        \node[main, minimum size=0.5cm] (6) [right of = 3, right=0.5em] {$_{t_1}$ };
        \draw (2) [bend left, dashed] to node[left] {$1$} (4);
        \draw (2) [bend right] to node[right] {$2\varepsilon$} (3);
        \draw (3) [bend right, dashed] to node[right] {$1 - 2\varepsilon$} (4);
        \draw (3) [dashed] to node[below] {$1 - 2\varepsilon$} (6);
    \end{tikzpicture} 
    \end{center}
    \caption[ALE is not $1.5$-competitive]{A graph in which ALE has a competitive ratio of $2$ for the time model. The dashed lines
    are paths, consisting entirely of edges with length $\varepsilon$.}
    \label{ALETad}
\end{figure}

\begin{proof}
    Consider how an optimal offline strategy, when given $k\geq3$ agents, takes time $2$ to explore the graph shown in Figure \ref{ALETad}, by sending two
    agents clockwise and counterclockwise to $c_1$ and back, as well as one agent on the shortest path to $t_1$ and back.\\
    Since the edge $(s,c_2)$ is the longest edge in the graph, any ALE strategy will send some number of agents clockwise around the graph, from
    $s$ to $c_2$. At this point, after $2-2\varepsilon$ time units have passed, the cycle is explored and the shortest way to complete the exploration, is to send
    some agent from $c_2$ to $t_1$ and back to $s$, leading to an exploration time of $4-4\varepsilon$ and a competitive ratio of $\frac{4-4\varepsilon}{2}$.
    The supremum for the competitive ratio on any graph like the one shown in Figure \ref*{ALETad} is $2$, having arbitrary small $\varepsilon>0$.
\end{proof}

\paragraph*{Upper Bound}

Having shown the lower bound of $2$ for $k\geq 3$ agents, we now show an exploration strategy that reaches this competitive ratio with a team of four agents,
while reaching a competitive ratio of $3$ with a team of three agents. The proof for this Theorem \ref{AleUpper} has been moved to the \hyperref[appendix]{Appendix}.


\begin{theorem}[ALE on tadpole graphs]\label{AleUpper}
    On tadpole graphs, using the ALE strategy, a team of three agents reaches a competitive ratio of $3$,
     while a team of four agents reaches the optimal competitive ratio of $2$ for the time model.
\end{theorem}
