% \begin{abstract}
% %RAG
% Retrieval-Augmented Generation (RAG) enhances the performance of LLMs across various tasks by retrieving relevant information from external sources, particularly on text-based data. 
% For structured data such as knowledge graphs, GraphRAG has been widely adopted to retrieve and aggregate information along graph structures. More recently, a growing body of work extends GraphRAG to general text-based settings by organizing unstructured text into graph representations, demonstrating potential benefits for reasoning and grounding.
% Despite these advances, existing applications of GraphRAG for text data are typically developed for specific tasks, datasets, and system designs, leading to highly heterogeneous evaluation settings. As a result, a clear understanding of the relative strengths, limitations, and trade-offs between RAG and GraphRAG remains lacking on widely used text-based benchmarks.
% In this paper, we conduct a systematic benchmark evaluation of RAG and GraphRAG on established tasks, including Question Answering and Query-based Summarization. We introduce a unified evaluation protocol that standardizes data preprocessing, retrieval configurations, and generation settings, enabling fair and reproducible comparisons across paradigms.
% Our results highlight the distinct strengths of RAG and GraphRAG across different tasks and evaluation perspectives. 
% Inspired by these observations, we investigate strategies to 
% integrate their strengths to improve downstream tasks. In addition, we provide an in-depth analysis of the limitations and failure modes of current GraphRAG approaches, and discuss open challenges and future directions for benchmarking retrieval-augmented generation systems.
% \end{abstract}

\begin{abstract}
Retrieval-Augmented Generation (RAG) improves large language models (LLMs) by retrieving relevant information from external sources and has been widely adopted for text-based tasks. For structured data, such as knowledge graphs, Graph Retrieval-Augmented Generation (GraphRAG) retrieves and aggregates information along graph structures. More recently, GraphRAG has been extended to general text settings by organizing unstructured text into graph representations, showing promise for reasoning and grounding.
Despite these advances, existing GraphRAG systems for text data are often tailored to specific tasks, datasets, and system designs, resulting in heterogeneous evaluation protocols. Consequently, a systematic understanding of the relative strengths, limitations, and trade-offs between RAG and GraphRAG on widely used text benchmarks remains limited.
In this paper, we present a comprehensive benchmark study comparing RAG and GraphRAG on established text-based tasks, including question answering and query-based summarization. We introduce a unified evaluation protocol that standardizes data preprocessing, retrieval configurations, and generation settings, enabling fair and reproducible comparisons. Our results highlight the distinct strengths of RAG and GraphRAG across different tasks and evaluation perspectives. 
Building on these findings, we explore selection and integration strategies that combine the strengths of both paradigms, leading to consistent performance improvements. We further analyze failure modes, efficiency trade-offs, and evaluation biases, and highlight key considerations for designing and evaluating retrieval-augmented generation systems.


\end{abstract}



