\section{Related Work}

\paragraph{Retrieval-Augmented Generation.}
RAG has become the standard approach for grounding LLMs in external knowledge \cite{lewis2021retrievalaugmentedgenerationknowledgeintensivenlp,gao2023retrieval}. Recent advances like Active Retrieval Augmented Generation \cite{jiang2023active} and R²AG \cite{ye2024r2ag} have introduced sophisticated retrieval strategies, but these systems assume static corpora without temporal or version constraints. Recent work confirms that standard RAG fails on outdated information \cite{ouyang2025hohdynamicbenchmarkevaluating}, achieving only 58\% accuracy on our versioned document benchmark.

\paragraph{Graph-Enhanced Retrieval.}
GraphRAG and its variants enhance retrieval through structured knowledge representations \cite{zhang2025surveygraphretrievalaugmentedgeneration}. While GraphRAG excels at multi-hop reasoning, systematic comparisons \cite{han2025ragvsgraphragsystematic} show it struggles with temporal dynamics. Our experiments confirm this limitation: GraphRAG achieves only 64\% overall accuracy on versioned documents and fails catastrophically (10\% accuracy) on implicit change detection, while requiring 16× more indexing tokens than our approach.

\paragraph{Temporal and Version-Aware Approaches.}
Existing temporal approaches address different challenges than versioned documents. Time-Aware Language Models \cite{dhingra2022timeaware} modify LM internals to handle facts that expire, but require retraining and cannot handle discrete version numbers. Temporal KGQA systems like CRONKGQA \cite{saxena2021temporal} answer questions over temporal knowledge graphs but assume pre-existing temporal structures rather than extracting version relationships from documents. TempRALM \cite{gade2024itstimeincorporatingtemporality} introduces time-sensitive retrieval but focuses on chronological grounding (e.g., "What happened in 2023?") rather than version-specific retrieval (e.g., "What changed in version 2.3?"). None of these systems handle version-to-version transitions essential for technical documentation.

\paragraph{Comparison with Existing Approaches.}
Table~\ref{tab:rag-comparison} summarizes how VersionRAG uniquely combines capabilities for versioned document QA. To our knowledge, this is the first system specifically designed for retrieval-augmented generation over versioned documents, achieving 90\% accuracy while requiring 97\% fewer tokens than GraphRAG. Additional related work is discussed in Appendix A.

\begin{table}[hb]
\centering
\small
\caption{Comparison of RAG approaches for version-specific retrieval requirements. VersionRAG is the only method that directly addresses versioned documents, distinct from more generic temporal retrieval methods.}
\resizebox{\columnwidth}{!}{%
\begin{tabular}{lcccccc}
\hline
\textbf{Method} & \makecell{Version\\Awareness} & \makecell{Change\\Tracking} & \makecell{Temporal\\Filtering} & \makecell{Graph\\Reasoning} & \makecell{Hybrid\\Retrieval} & \makecell{Efficient\\Indexing} \\
\hline
Standard RAG     & \xmark & \xmark & \xmark & \xmark & \xmark & \cmark \\
GraphRAG         & \xmark & \xmark & \xmark & \cmark & \cmark & \xmark \\
Time-Aware LM    & \xmark & \xmark & \cmark & \xmark & \xmark & N/A \\
CRONKGQA         & \xmark & \xmark & \cmark & \cmark & \xmark & \xmark \\
TempRALM         & \xmark & \xmark & \cmark & \xmark & \xmark & \cmark \\
\hline
\textbf{VersionRAG} & \cmark & \cmark & \cmark & \cmark & \cmark & \cmark \\
\hline
\end{tabular}
}
\label{tab:rag-comparison}
\end{table}
