\section{Dataset and Experimental Setup}
\label{sec:dataset}

To the best of our knowledge there currently does not exist a version-aware document QA dataset. We therefore construct a new benchmark dataset based on publicly available documentation and change logs of open-source software projects.
Our dataset VersionQA is publicly available for the community (\githuburl)

\subsection{VersionQA: A Versioned Document QA Dataset}

\paragraph{Dataset Construction.}
We create VersionQA, the first benchmark specifically designed for evaluating versioned document question answering. The dataset comprises 100 manually curated question-answer pairs across 34 technical documentation files totaling over 700 pages. Documents span four topics as shown in Table~\ref{tab:datasetoverview}: Apache Spark releases (6 changelog files), Bootstrap releases (6 changelog files), Node.js Assert module (13 documentation files across versions), and Node.js Errors (9 documentation files across versions). This mix of changelogs and versioned documentation enables evaluation of both explicit and implicit change detection capabilities.

\begin{table}[hb]
\centering
\small
\caption{VersionQA dataset composition with version ranges.}
\resizebox{\columnwidth}{!}{%
\begin{tabular}{llll}
\hline
Topic & Type & Files & Versions \\ \hline
Apache Spark & Changelog & 6 & 2.4.7 - 3.5.5\\
Bootstrap & Changelog & 6 & 5.2.3 - 5.3.5\\
Node.js Assert & Documentation & 13 & 11.15.0 - 23.11.0\\
Node.js Errors & Documentation & 9 & 15.14.0 - 23.11.0\\
\hline
\end{tabular}
}
\label{tab:datasetoverview}
\end{table}

\paragraph{Query Categories.}
Based on our query type taxonomy, we design six evaluation categories to comprehensively test version-aware reasoning capabilities. Table~\ref{tab:querycategories} shows the distribution and examples. \textit{Content Retrieval} (20 Q\&A pairs) tests basic information extraction. \textit{Content Retrieval Complex} (20 pairs) requires synthesizing multiple pieces of information. \textit{Content Retrieval Version-Specific} (20 pairs) tests precise version-aware retrieval (e.g., \textit{``What is the stability level of assert.CallTracker in Node.js version 20.19.0?''}). \textit{Version Listing \& Inquiry} (20 pairs) evaluates version metadata understanding. \textit{Change Retrieval Explicit} (10 pairs) tests retrieval of documented changes from changelogs. \textit{Change Retrieval Implicit} (10 pairs) requires detecting undocumented changes between versions (e.g., ``When was assert.deepEqual() removed?'').

\begin{table}[hb]
\centering
\small
\caption{Distribution of query categories in VersionQA. 60\% of queries require version-aware reasoning.}
\resizebox{\columnwidth}{!}{%
\begin{tabular}{lcc}
\hline
Category & Q\&A Pairs & Version-Sensitive \\ \hline
Content Retrieval & 20 & No \\
Content Retrieval Complex & 20 & No \\
Content Retrieval Version-Specific & 20 & Yes \\
Version Listing \& Inquiry & 20 & Yes \\
Change Retrieval (Explicit) & 10 & Yes \\
Change Retrieval (Implicit) & 10 & Yes \\
\hline
\end{tabular}
}
\label{tab:querycategories}
\end{table}

\subsection{Experimental Configuration}

\paragraph{Baseline Systems.}
We compare VersionRAG against two baselines representing different retrieval paradigms. \textit{Naive RAG} implements standard retrieval-augmented generation following \cite{gao2023retrieval}, chunking documents into 512-token segments and using text-embedding-3-small for embedding. It retrieves top-5 chunks based on cosine similarity without version awareness. \textit{GraphRAG} uses the official Neo4j implementation \cite{neo4j_graphrag_docs} with HybridCypherRetriever, combining vector search with graph traversal. It constructs knowledge graphs by extracting entities and relationships using LLMs but lacks explicit version modeling.

\paragraph{Language Models.}
We evaluate across three LLMs with varying capacities to assess robustness: Llama 3 8B (8,192 token context), GPT-4o Mini (128,000 token context), and DeepSeek-R1 70B (128,000 token context). All systems use OpenAI's text-embedding-3-small~\cite{openai2024embedding} for vector embeddings and the same LLM for both indexing and generation within each experimental configuration to ensure fair comparison.

\paragraph{Implementation Details.}
VersionRAG is implemented using Neo4j~\cite{neo4j2025} for graph storage and Milvus Lite~\cite{milvuslite2025} for vector database operations. Documents are chunked into 512-token segments with 50-token overlap. The DeepDiff library \cite{Dehpour_DeepDiff} performs line-level comparisons for implicit change detection. Few-shot prompting guides LLM behavior across all tasks without fine-tuning (see Appendix~\ref{app:implementation_details} for further details).

\paragraph{Evaluation Metrics.}
We measure accuracy as the proportion of correctly answered questions. Each answer is evaluated using GPT-4.1 as an LLM judge \cite{gu2025surveyllmasajudge}, comparing generated responses against ground truth. This automated evaluation is manually reviewed for all 100 questions to ensure reliability. While the dataset size precludes extensive statistical testing, the manual curation ensures high-quality evaluation across diverse query types.

\subsection{Resource Considerations}

All experiments were conducted using cloud APIs with costs tracked. Table~\ref{tab:indexingcosts} shows the dramatic efficiency difference: VersionRAG requires 186K input tokens versus GraphRAG's 2,970K tokens for indexing the same documents with DeepSeek-R1 70B, translating to \$0.17 versus \$6.67 in API costs and 25 minutes versus 5.2 hours processing time. This 97\% reduction in resource consumption makes VersionRAG practical for large-scale deployment on continuously evolving documentation.

\begin{table}[hb]
\centering
\footnotesize
\caption{Indexing resource consumption with DeepSeek-R1 70B.}
\begin{tabular}{lrrr}
\hline
Approach & Tokens [K] & Cost [\$] & Time \\ \hline
GraphRAG & 2,970 & 6.67 & 5h 12min \\
VersionRAG (ours) & 186 & 0.17 & 25min \\
\hline
\end{tabular}
\label{tab:indexingcosts}
\end{table}
