\section{Related Work}
\label{sec:related}

We divide the related works into three categories: (\romannumeral1) knowledge 
graph based recommendation, (\romannumeral2) temporal knowledge graph embedding
and (\romannumeral3)  temporal information in 
recommendation.


\subsection{Knowledge Graph Based Recommendation}

Existing studies on KG-based recommendation systems \cite{surveyRec} can be roughly grouped into two sub-categories: embedding-based methods and path-based
methods.

Embedding-based methods adopt a common general model, where the latent vector
$\boldsymbol{u}_i$ of each user $u_i$ and item embedding $\boldsymbol{v}_j$ can 
be
extracted from KGE, and the probability  of item $v_j$ being recommended to
user $u_i$ can be calculated by $\hat{y}_{i, j}=f\left(\mathbf{u}_{i},
\mathbf{v}_{j}\right)$. Note that $f(\cdot)$ can be either DNN, inner product,
or other scoring functions.  
%
For instance, \cite{CKE} proposed CKE, which uses TransE to unify the KG information in the CF framework.
%
Deep Knowledge-based Network (DKN) \cite{DKN} treats entity embeddings and word embeddings as different channels, where Kim CNN \cite{kimCNN} is used to combine them together for news recommendation.
\cite{KSR} uses a GRU network with a knowledge-enhanced key-value memory network, named KSR, to capture user preferences from the sequential interactions.
\cite{kgat} and \cite{kgin} employ the message passing mechanism of graph neural networks over KG to model the higher-order connections among users, entities, and items.


In the line of path-based methods, recommendations are made based on the connectivity patterns of the entity in user-item graph.
For example, \cite{mcrec} uses CNN to obtain each path instance's embedding.
%
\cite{kprn} proposed a knowledge-aware path recurrent network (KPRN) solution,
which constructs the extracted path sequence with both the entity embedding and
the relation embedding, and encodes the path sequence with an LSTM layer before
recommendation.  
%
RippleNet~\cite{ripplenet} combined embedding-based and path-based methods and
modeled users' preference propagation by their historical interests along the
path in the KG. 
%
Inspired by KG reasoning techniques~\cite{deeppath, multihop, gowalk}, PGPR~\cite{pgpr} performs reinforcement policy-guided path reasoning over
KG-based user-item interaction.
Inspired by such RL-based policy networks, CPR~\cite{RLconversa} models conversational recommendation as a path reasoning problem on a heterogeneous graph.
Different from PGPR which relies on sparse reward signal, ADAC~\cite{ADAC} adopts an Adversarial Actor-Critic model to achieve faster converge. 

These KG reasoning methods (\eg,~\cite{pgpr, ADAC, RLconversa}) can provide explainable reasoning paths while obtaining accurate recommendation results.
However, they do not use temporal information and may lead to inappropriate
recommendations.
Therefore, we propose \tkgrec, aiming to leverage temporal information for promoting explainable recommendation.


%\subsection{Squential Recommendation}
%Sequential recommendation captures patterns between consecutive user-item 
%interactions and predicts the successive item that the user is likely to 
%adopt. 
%A classic work is the FPMC model \cite{rendle2010fFPMC}, which integrates
%matrix factorization with Markov chains for modeling long-term perferences and 
%dynamic transitions of users.

\subsection{Temporal Knowledge Graph Embedding}


Existing studies on knowledge graph embedding research focus on static
knowledge graphs. A series of these models are variations of 
TransE~\cite{transE, transD,
transH, transR}. These models assume that facts are not changing with time, which is
obviously contrary to reality. 
%
Therefore, recent studies begin to take temporal information (\eg , fact
occurrence time, end time, \etc)
%
%\footnote{\hxie{what do you mean by ``fact \textit{occursSince} when \etc''}}
%
into consideration \cite{surveyKG}, which turns out to further improve the
performance of KG embedding.

There exist only a few studies on temporal knowledge graph (TKG) embedding. 
%
\cite{leblay} proposed TTransE by simply extending existing
embedding methods like TransE. TTransE adopts translational distance score
functions to learn associations between facts of a KG.
%and encode time information in entity-relation to low dimensional spaces. 
%
\cite{ma_embedding} generalized existing models for static
knowledge graphs to temporal knowledge graphs with a timestamp embedding. 
%
\cite{hyte} took a timestamp as a hyper-plane and projected
entities and relations to learn KG embedding. 

TKG embedding has to deal with two types of dynamics, namely,
entity dynamics and relation dynamics.

Entity dynamics refers to the fact that real-world events can
change the state of a given entity's state and therefore affect its
corresponding relations. 
%
\cite{knowevolve} modeled the occurrence of a fact as a
temporal point process, and used a novel recurrent network to learn the
representation of non-linearly evolving entities. 
%
\cite{contextTemporal} formulated the temporal scoping
problem as a state change detection problem and utilized the context to learn
the states and the state change vectors.

Relation dynamics refers to the fact that the relations
among entities in a knowledge graph may change over time. 
%
\cite{relation_dy} realized that there exist temporal
dependencies in relational chains following the timeline, for example,
$(P,\text{wasBornIn}, \_ )$ $ \rightarrow$ $ (P, $ $ \text{graduateFrom}$ $, $ $\_ ) $ $\rightarrow $ $(P, \text{workAt}, \_ ) $
$\rightarrow $ $(P,\text{diedIn}, \_ )$, and found that many facts are only
valid during a short time period. To solve that issue, the authors proposed two
time-aware KG completion models to incorporate the above two kinds of temporal
information.

%Numerous experiments demonstrate effectiveness of those TKG embedding methods
%over traditional KG embedding methods in different tasks, which illustrates
%the auxiliary role of temporal information in representation.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Although those TKG embedding methods achieve better
performance than traditional KG embedding methods, 
none of them have considered if only part of the facts is updated very frequently, which is common in recommendation
and dealed by our \tkgrec.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Temporal Information in Recommendation}

Temporal Information is important contextual information for providing users 
with an accurate prediction based on historical behaviors\cite{timeSurveyReview}.
\cite{yi2014beyond} finds that dwell time is an important factor to quantify how likely an item is relevant to a user.
\cite{liang2012time} uses the temporal information in micro-blogs in order to profile users' time-sensitive topic interests.
\cite{chang2017streaming} proposes sREC, which captures temporal dynamics of users and topics under steaming settings, to perform real-time recommendations.
\cite{seqInMusic} proposes CoSeRNN and leverages time context and device context for better music recommendation.
As for temporal patterns of user behaviors, \cite{timeMatters} and \cite{timeAwareSeq} discover ``absolute" and ``relative" time patterns and jointly learn those temporal patterns to model user dynamic preferences and predict future items.
\cite{heteTemporal} defines the periodic and evolving patterns of user preferences, and proposes a cascade of two encoders with an attention module to capture such temporal patterns.

Recently, KG-based methods achieve great success for many temporal tasks.
\cite{kerl} uses both sequence- and knowledge-level state representations to capture user preference with an induction network, and adopt a composite reward to capture both sequence-level and knowledge-level information for sequential recommendation.
\cite{KSR} uses GRU to capture the user’s sequential preference, and utilizes knowledge base information to model the user’s attribute-level preference.
\cite{huang2019explainable} designs EIUM, which represents KG with 
multi-modal fusion, and adopts a masked self-attention model to encode the user’s sequential interactions for capturing her dynamic interests.
Most of those methods with temporal information consider KG information as enhanced representation to assist sequential recommendation.
Our work differs from these works by modeling the statistical and structural 
temporal patterns between user-item interactions to construct TCKG, and propose time-aware path reasoning over the TCKG to make full use of the structural constraints in KG. It's inconvenient to utilize our \tkgrec\ to predict the next item task like other sequential recommendation methods, because the KG data is different from the sequence data. That is, we need to construct a dynamic edge MASK matrix on KG's adjacency matrix to avoid the next item $v$'s information and other items behind $v$ from influencing the training phase. We will leave this as our future work.
% If we superimpose T to predict the next item,
%Sequential recommendation captures patterns between consecutive user-item 
%interactions and predicts the successive item that the user is likely to 
%adopt. 
%A classic work is the FPMC model \cite{rendle2010fFPMC}, which integrates
%matrix factorization with Markov chains for modeling long-term perferences and 
%dynamic transitions of users.
% (5) Thank you for pointing out such interesting direction. The motivation of our reward function is mentioned in ans.(2). We haven't considered to take the user's recently interacted items v as the pre-known target items, and set the reward function as the similarity between the reasoning terminal item $\hat{v}$ and $v$. However, the KG data is different with sequence data. That is, we need to construct a dynamic edge MASK matrix on KG's adjacency matrix to avoid items $v$'s information and the other items behind v from influencing the training phase. We will leave this as our future work. \\
















