\section{Conclusion}
\label{sec:conclusion}

In this paper, we present \tkgrec, a novel 
time-aware path reasoning model for recommendation, which addresses the timeliness of
interpretation.
To the best of our knowledge, the \tkgrec\ method is the first work to
introduce time-aware path reasoning method into a recommendation
system and achieves significant performance improvement by leveraging the
temporal information.
%
%To the best of our knowledge, the \tkgrec\ method is the first work to
%introduce time-aware reasoning method into a recommendation
%system and achieves significant performance improvement by leveraging the
%temporal information.
%
%Our model consists of time-aware interaction relation extraction component, which 

Our model first uses time-aware interaction relation extraction component to
construct TCKGs for the
reasoning environment. Then the time-aware representation learning component encodes 
entities and relations to get proper
representation. Finally is the key time-aware reasoning component, which adopts a 
time-aware
personalized reasoner to explore temporal information assisted recommendation.
%
We also conduct extensive experiments on three real-world datasets to evaluate
the effectiveness of \tkgrec. Evaluation results demonstrate that \tkgrec\
outperforms the existing models on a set of widely used metrics.

For future work, we plan to evaluate \tkgrec\ using more datasets from other
product domains and other major online vendors, transform the training process 
to make it suitable for next item prediction,
% Change the training process to make it suitable for sequence recommendation
and extend our \tkgrec\ model
by leveraging the adversarial learning model to automatically shape rewards in
order to achieve more accurate recommendation results.  We also plan to combine
causal inferences with our model to achieve better interpretability.
