\section{Related Work}
\textbf{Reinforcement Learning for LLMs.}~~
Beyond early alignment-focused approaches such as RLHF~\citep{ziegler2019fine,stiennon2020learning,ouyang2022training,rafailov2024direct}, recent work studies Reinforcement Learning from Verifiable Rewards (RLVR), which leverages automatically checkable signals (e.g., correctness in math or code) to improve LLM capabilities~\citep{zeng2025simplerl}.
Within this setting, group-based RL has emerged as a strong alternative to classical actor-critic algorithms like PPO~\citep{schulman2017proximal}. Techniques such as GRPO~\citep{shao2024deepseekmath}, RLOO~\citep{kool2019buy,ahmadian2024back},
Dr.~GRPO~\citep{liu2025understanding}, DAPO~\citep{yu2025dapo}, and GSPO~\citep{zheng2025group} aggregate multiple rollouts for the same query and perform relative comparisons within the group, thereby avoiding explicit value-function learning.
RLVR has also been extended to agentic, multi-turn settings where LLMs act as automatic agents~\citep{zhou2024archer,bai2024digirl,feng2025towards,wang2025spa,zhang2025agent,feng2026agentocr}. GRPO-style training has been widely applied to tool use~\citep{qian2025toolrl,xue2025simpletir}, OS control~\citep{lai2025computerrl}, and gaming~\citep{wang2025ragen}.
Further variants refine group construction or objectives, such as GiGPO~\citep{feng2025group} and ARPO~\citep{dong2025agentic}.


\textbf{Reinforcement Learning for Multi-Agent LLMs.}~~
Recent RL post-training has expanded from single-agent scenarios to \emph{learning coordination} in role-specialized, multi-turn multi-agent systems. Self-play training (e.g., SPIRAL~\citep{liu2025spiral}, and MARSHAL~\citep{yuan2025marshal} use multi-turn dynamics to generate curricula and rewards with minimal manual labeling. However, these approaches are often confined to dyadic (two-agent) self-play scenarios. To ease deployment, Chain-of-Agents~\citep{li2025chain} distills multi-agent trajectories into a single agentic policy. Meanwhile, group-relative optimization has been extended to multi-agent settings~\citep{liu2025llm,chen2025heterogeneous,li2025flow,park2025maporl,wan2025rema,xue2025comas,mo2025multi,hong2025multi}, but these methods typically rely on heuristics and lack stability guarantees. \methodname{} distinguishes itself by theoretically identifying \emph{gradient-norm inflation} as the root cause of instability and proposing a simple yet rigorous agent-wise solution.


\textbf{Reinforcement Learning Infrastructure.}~~
As RL post-training scales, infrastructure has shifted toward optimizing the end-to-end \emph{rollout-train loop}, where throughput, scheduling, and variable-length generation dominate system efficiency. General-purpose stacks such as veRL~\citep{sheng2024hybridflow}, OpenRLHF~\citep{hu2024openrlhf}, ROLL~\citep{wang2025reinforcement}, slime~\citep{slime_github}, and AReaL~\citep{fu2025areal} increasingly provide modular pipeline abstractions and distributed execution to improve utilization under heavy sampling. As agentic use cases grow, frameworks increasingly emphasize multi-turn rollout and tool integration (e.g., verl-agent~\citep{feng2025group}, VerlTool~\citep{jiang2025verltool}, Agent-Lightning~\citep{luo2025agent}), with MARTI~\citep{marti2025} and PettingLLMs~\citep{zhao2025stronger} offering a practical multi-agent training interface. However, they either provide limited support for heterogeneous model assignments or lack a shared resource pool for efficient scheduling. Our \methodname{} addresses both to improve scalability and utilization in MAS post-training.

