

\section{Theoretical Analysis}
\label{sec:theory}

In this section, we provide a rigorous justification for \EHGRAG using the Latent Space Model (LSM) \cite{mao2024revisiting}. We demonstrate how constructing semantic hyperedges via BIRCH clustering explicitly bridges the gap between disjoint entities by strictly tightening the upper bound of their latent distance.

\subsection{Latent Space Modeling}
Following \cite{mao2024revisiting,sarkar2011theoretical}, we model the corpus graph $\mathcal{G}=(\mathcal{V}, \mathcal{E})$ in a $D$-dimensional latent Euclidean space $\mathbb{R}^D$. Each entity $v_i$ has a latent position $\mathbf{z}_i$ and an influence radius $r_i$. The probability of a link between entities $i$ and $j$ is governed by their latent distance $d_{ij} = \|\mathbf{z}_i - \mathbf{z}_j\|$:
\begin{equation}
    P(i \sim j \mid d_{ij}) = \frac{1}{1 + \exp(\alpha(d_{ij} - \tau))}
\end{equation}
where $\alpha > 0$ is a scaling factor. A smaller $d_{ij}$ implies a higher retrieval probability.

\subsection{The Semantic Gap in Structural Retrieval}
In purely structural RAG systems, links rely on explicit sentence co-occurrence. Let $\eta_{ij}^{str} = |\mathcal{N}_{str}(i) \cap \mathcal{N}_{str}(j)|$ be the number of structural common neighbors.
For semantically related but spatially disjoint entities (e.g., in different documents), we have $\eta_{ij}^{str} \to 0$. According to Proposition 1 in \cite{mao2024revisiting}, the latent distance $d_{ij}$ is loosely bounded:
\begin{equation}
    d_{ij} \le 2\sqrt{r_{ij}^{\max} - \left(\frac{\eta_{ij}^{str}/N - \epsilon}{V(1)}\right)^{2/D}}
\end{equation}
where $r_{ij}^{\max} = \max(r_i, r_j)$ and $V(1)$ is the unit hypersphere volume. As $\eta_{ij}^{str} \to 0$, the subtracted term vanishes, leaving $d_{ij}$ close to its maximum possible value $2\sqrt{r_{ij}^{\max}}$, resulting in $P(i \sim j) \to 0$. This mathematically quantifies the \textit{Semantic Gap}.

\subsection{Bridging via Clustering-Induced Hyperedges}
\EHGRAG overcomes this by utilizing BIRCH to construct semantic hyperedges.
\begin{definition}[Cluster-Induced Connectivity]
    Let $\mathcal{C} = \{C_1, \dots, C_K\}$ be the clusters generated by BIRCH. For a cluster $C_k$ with centroid $\mathbf{\mu}_k$ and threshold radius $T$, any entity $v_i \in C_k$ satisfies $\|\mathbf{x}_i - \mathbf{\mu}_k\| \le T$ in the embedding space. We construct a semantic hyperedge $e_{sem}^k$ connecting all $v \in C_k$.
\end{definition}

This construction transforms feature compactness into structural connectivity. We formalize this effect as a \textit{Feature Proximity (FP)} term $\beta_{ij}$, which acts as a "synthetic" common neighbor probability.

\begin{theorem}[Cluster-Tightened Distance Bound]
    For any two entities $i, j$ belonging to the same semantic hyperedge $e_{sem}^k$ (i.e., $i, j \in C_k$), the BIRCH clustering guarantees a feature proximity lower bound $\beta_{min} \propto \exp(-4T^2)$.
    Consequently, the latent distance $d_{ij}$ is tightly bounded by:
    \begin{equation}
    \begin{split}
        d_{ij} &\le 2\sqrt{r_{ij}^{\max} - \Delta_{sem}}, \\
        \text{where } \Delta_{sem} &= \left(\frac{\beta_{ij} + \mathcal{A}(r_i, r_j, d_{ij})}{V(1)}\right)^{2/D}.
    \end{split}
    \label{eq:cluster_bound}
    \end{equation}
    Here, $\mathcal{A}(\cdot)$ is the intersection volume of influence spheres, and $\beta_{ij}$ represents the probabilistic connection strength induced by the semantic cluster.
\end{theorem}

\begin{proof}
    We extend the proof from \cite{mao2024revisiting}. The existence of a semantic hyperedge $e_{sem}^k$ containing $i$ and $j$ introduces a direct path in the hypergraph.
    In the LSM, this is equivalent to injecting a non-zero feature proximity term $\beta_{ij}$ into the intersection volume.
    Since $i, j \in C_k$, by triangle inequality, their embedding distance $\|\mathbf{x}_i - \mathbf{x}_j\| \le 2T$.
    Mapping this feature distance to the connection probability space, we obtain $\beta_{ij} > 0$.
    
    Substituting the augmented volume $\mathcal{A}' = \beta_{ij} + \mathcal{A}(r_i, r_j, d_{ij})$ into the hypersphere packing bound:
    \begin{equation}
    \begin{aligned}
        \frac{\mathcal{A}'}{V(1)} & \le \left(r_{ij}^{\max} - \left(\frac{d_{ij}}{2}\right)^2\right)^{D/2} \\
        \implies d_{ij} & \le 2\sqrt{r_{ij}^{\max} - \left(\frac{\beta_{ij} + \mathcal{A}}{V(1)}\right)^{2/D}}
    \end{aligned}
    \end{equation}
    Critically, for disjoint entities where $\mathcal{A} \approx 0$, the term $\beta_{ij}$ (guaranteed by BIRCH clustering) ensures that the subtraction term $\Delta_{sem}$ is strictly positive.
    Since $f(x) = \sqrt{C - x}$ is monotonically decreasing, a larger $\beta_{ij}$ strictly decreases the upper bound of $d_{ij}$.
\end{proof}

\textbf{Implication:} Eq. \ref{eq:cluster_bound} proves that \EHGRAG guarantees a tighter latent distance bound than LinearRAG. Even if $\eta_{ij}^{str}=0$, the semantic term $\beta_{ij}$ forces the latent distance to shrink, thereby theoretically ensuring a higher retrieval probability for semantically similar entities.
\begin{table*}[!t]
\centering
\small
\renewcommand{\arraystretch}{1.3} 
\begin{tabularx}{\textwidth}{p{2.2cm}|X}
\toprule
\rowcolor{headergray} \textbf{Category} & \textbf{Content} \\ \midrule
\textbf{Question} & "Which film was released first, Aas Ka Panchhi or Phoolwari?" \\ \midrule
\textbf{Ground Truth} & Phoolwari (1946) \\ \midrule
\textbf{Support Context} & [Aas Ka Panchhi: 1961] $\leftrightarrow$ [Phoolwari: 1946] \\ \midrule

\rowcolor{baselinepink} \textbf{LinearRAG} & \textbf{Retrieved context (Top 5):} \\
\rowcolor{baselinepink} & 1) \xmark \ \textit{Shah Muhammad... Phulwarisharif}: ...born in Phulwarisharif, Bihar... (Location noise) \\
\rowcolor{baselinepink} & 2) \xmark \ \textit{Pyar Ka Bandhan}: ...is a 1963 Hindi film... \\
\rowcolor{baselinepink} & 3) \xmark \ \textit{Student of the Year}: ...released on 19 October 2012... \\
\rowcolor{baselinepink} & 4) \xmark \ \textit{Hum Dil De Chuke Sanam}: ...released internationally in 1999... \\
\rowcolor{baselinepink} & 5) \xmark \ \textit{Phool Aur Kaante}: ...began career with Phool Aur Kaante in 1991... \\
\rowcolor{baselinepink} & \textbf{Prediction:} \xmark \ Aas Ka Panchhi \\ \midrule

\rowcolor{proposelblue} \textbf{\EHGRAG} & \textbf{Retrieved context (Top 5):} \\
\rowcolor{proposelblue} & 1) \cmark \ \textbf{Aas Ka Panchhi (1961)} \& \textbf{Phoolwari (1946)}: ...Phoolwari is a 1946 film. Aas Ka Panchhi is a 1961 movie... \\
\rowcolor{proposelblue} & 2) \cmark \ \textit{Hum Dil De Chuke Sanam}: ...adaptation of Maitreyi Devi's novel... (Relatively irrelevant but correctly ranked) \\
\rowcolor{proposelblue} & 3) \xmark \ \textit{Vaibhavi Merchant}: ...choreography work in Bollywood films... \\
\rowcolor{proposelblue} & 4) \xmark \ \textit{Nitin Chandrakant Desai}: ...noted Indian art director... \\
\rowcolor{proposelblue} & 5) \cmark \ \textbf{Aas Ka Panchhi (1961)}: ...1961 Hindi movie produced by J. Om Prakash... \\
\rowcolor{proposelblue} & \textbf{Prediction:} \cmark \ Phoolwari \\ 
\bottomrule
\end{tabularx}
\caption{\textbf{Detailed Case Study comparison.} Our method (\EHGRAG) successfully retrieves the exact release years for both movies, while the Baseline is misled by geographic entities and recent film noise.}
\label{tab:detailed_case}
\end{table*}

\begin{table*}[!tbp]
\centering
\small
\begin{tabularx}{\textwidth}{l|l|X}
\toprule
\textbf{Category} & \textbf{Method} & \textbf{Key Characteristics} \\ \midrule
\textbf{Zero-shot LLM} & LLaMA3 (8B/13B), Qwen3-8B & Evaluates the internal knowledge of state-of-the-art open-source LLMs. \\
& GPT-3.5-turbo, GPT-4o-mini & Proprietary models used to establish a performance upper bound for zero-shot inference. \\ \midrule
\textbf{Standard RAG} & Vanilla RAG & Standard retrieval-augmented generation relying on vector similarity. \\ \midrule
\textbf{Graph-based RAG} & GraphRAG, KGP, G-retriever & Traditional GraphRAG methods that typically utilize LLMs for entity-relation triple extraction. \\
& RAPTOR & Builds tree-organized indices through recursive abstractive processing. \\ \midrule
\textbf{Lightweight RAG} & HippoRAG, HippoRAG2 & Neurobiologically inspired methods utilizing Personalized PageRank (PPR). \\
& LinearRAG & A state-of-the-art lightweight framework that models document structures directly via NER. \\
& E2GraphRAG, LightRAG & Recent efficient frameworks designed to streamline graph-based retrieval. \\
\bottomrule
\end{tabularx}
\caption{Comprehensive overview of baseline methods.}
\label{tab:baselines}
\end{table*}

\begin{table*}[t]
    \centering
    \small
    \resizebox{\linewidth}{!}{
    \begin{tabular}{l|cccc}
    \toprule
    \textbf{Hyperparameter} & \textbf{HotpotQA} & \textbf{2WikiMultiHop} & \textbf{MuSiQue} & \textbf{Medical} \\
    \midrule
    \textbf{NER Model} & \texttt{en\_core\_web\_trf} & \texttt{en\_core\_web\_trf} & \texttt{en\_core\_web\_trf} & \texttt{en\_core\_sci\_scibert} \\
    \textbf{Max Iterations ($T$)} & 3 & 3 & 5 & 3 \\
    \textbf{Pruning Threshold ($\epsilon$)} & 0.5 & 0.4 & 0.4 & 0.5 \\
    \textbf{Passage Ratio ($\lambda_1$)} & 1.5 & 0.05 & 2.0 & 1.5 \\
    \textbf{Sentence Number ($L$)} & 1 & 1 & 4 & 1 \\
    \textbf{Cluster Threshold ($D$)} & 100 & 100 & 100 & 100 \\
    \bottomrule
    \end{tabular}
    }
    \caption{Detailed hyperparameter settings for \EHGRAG across four benchmark datasets.}
    \label{tab:hyperparams}
\end{table*}
\section{Related Work}
\label{related-work}
\subsection{LLM-based GraphRAG via Triple Extraction}
Graphs serve as a natural and expressive representation for encoding relational knowledge, and recent advances in graph learning~\cite{song2021dynamic,song2024efficient,song2025ddfi,chendecoupled,luo2024fast,chen2023lsgnn} have significantly improved the ability to reason over such structured information. Building on this foundation, GraphRAG transforms unstructured text into structured Knowledge Graphs (KGs) to explicitly model entity relationships~\citep{zhang2025erarag,zhou2025depth,xiao2025graphragbenchchallengingdomainspecificreasoning,zhang2025survey,xiang2025use,mavromatis2024gnn}. Prominent frameworks like Microsoft's GraphRAG \cite{edge2024local} employ Large Language Models (LLMs) for Open Information Extraction (OpenIE) to construct entity-relation triples, subsequently using community detection (e.g., Leiden) to support global query answering. Similarly, RAPTOR \cite{sarthi2024raptor} builds tree-structured indices via recursive clustering.

However, these methods suffer from a construction bottleneck~\citep{edge2024local,sarthi2024raptor,jimenez2024hipporag}. The reliance on LLMs for triple extraction incurs prohibitive computational costs that scale polynomially with corpus size. Furthermore, rigid Named Entity Recognition (NER) often leads to \textit{Semantic Loss}—semantically related entities that do not physically co-occur or fail extraction remain disconnected, disrupting retrieval pathways.

\subsection{Lightweight Graph Construction}
To mitigate high costs, recent work explores lightweight strategies~\cite{huang2025ket,pan2024unifying,zhang2025adagcrag}. HippoRAG \cite{jimenez2024hipporag} and its successor \citep{gutiérrez2025hipporag2} leverage Personalized PageRank (PPR) on existing KGs to simulate associative memory. LinearRAG \cite{zhuang2025linearrag} introduces a tri-Graph architecture using lightweight tools to connect entities, sentences and passages, achieving high efficiency and outstanding QA performance on various datasets.

\paragraph{Positioning of \EHGRAG:} While the aforementioned methods reduce costs, they often overlook deep semantic correlations, relying primarily on physical textual co-occurrence. Our proposed \textbf{\EHGRAG} inherits the efficiency of lightweight construction (linear complexity) while introducing \textbf{Semantic Hyperedges}. By leveraging hypergraph topology, we explicitly resolve semantic disconnects without increasing construction overhead.


\subsection{Experimental Configuration}
\label{app:config}

All experiments were conducted on a high-performance computing server equipped with two Intel(R) Xeon(R) Platinum 8377C CPUs , theNVIDIA RTX 4090 GPU (24GB VRAM), and 512GB of RAM. Hyperparameters were tuned specifically for each dataset to handle varying reasoning complexities. The dataset-specific configurations are summarized in Table \ref{tab:hyperparams}.

\section{Case Study}
To intuitively demonstrate how \EHGRAG bridges the semantic gap, we present a qualitative analysis in Table \ref{tab:detailed_case} using a comparative query from 2WikiMultiHop. \EHGRAG utilizes semantic hyperedges to capture latent correlations. Even though the correct movie \textit{"Phoolwari"} (1946) does not share explicit structural neighbors with the query context, our clustering-based semantic construction successfully maps the query entity to the correct latent topic. This activates the relevant passage containing \textit{"Phoolwari is a 1946 film..."}, enabling the model to correctly identify that \textit{"Phoolwari"} (1946) was released before \textit{"Aas Ka Panchhi"} (1961). This case highlights \EHGRAG's robustness in filtering keyword noise and retrieving semantically aligned evidence.

\section{Baseline Descriptions}
We compare our method against two primary groups of baselines: Zero-shot LLM and RAG methods. The details are shown in Table~\ref{tab:baselines}.

\section{Dataset Descriptions}
\label{app:datasets}

We evaluate EHRAG on four benchmark datasets, including three multi-hop reasoning benchmarks and one domain-specific dataset:

\begin{itemize}[leftmargin=*]
    \item \textbf{HotpotQA}: A widely used multi-hop reasoning benchmark that requires finding and integrating evidence across multiple documents.
    \item \textbf{2WikiMultiHop}: This dataset frequently involves reasoning chains that require entity aliasing, such as linking synonymous but disjoint entities. It is characterized by having semantically disjoint entities and complex global dependencies.
    \item \textbf{MuSiQue}: A dataset comprised of multi-hop questions generated via single-hop question composition, testing deep logical integration.
    \item \textbf{Medical}: A domain-specific dataset from GraphRAG-Bench. We utilize the LLM-Acc metric for this dataset because the ground truth answers contain multiple statements, making Exact Match metrics (SubEM) less effective.
\end{itemize}


