 \section{Preliminaries}
\subsection{Backgrounds}

Given a corpus $\mathcal{C} = \{d_1, \dots, d_{|\mathcal{C}|}\}$ and a query $q$, retrieval-augmented generation (RAG) aims to retrieve relevant documents to support answer generation. While vanilla RAG relies on vector similarity, it often treats documents as independent units, struggling with complex queries that require multi-hop reasoning across interconnected information. To overcome this limitation, graph-based RAG structure the corpus into knowledge graphs to improving multi-step information propagation. However, traditional GraphRAG methods typically depend on LLMs to extract fine-grained entity-relation triples, which incurs prohibitive computational costs and latency. 

Recently, lightweight methods (e.g., LinearRAG) replace expensive relation extraction with Named Entity Recognition (NER), modeling relationships primarily through explicit structural co-occurrence. Despite their efficiency, these pairwise graph structures often fail to capture latent semantic correlations between spatially disjoint entities. To bridge this gap, we model the corpus as a hypergraph $\mathcal{H} = (\mathcal{V}, \mathcal{E})$, where the node set $\mathcal{V}$ consists of unique entities extracted via lightweight NER. Unlike simple edges, a hyperedge $e \in \mathcal{E}$ connects an arbitrary subset of entities ($e \subseteq \mathcal{V}$), enabling the unified modeling of both explicit structural inclusion (entities within a sentence) and implicit semantic grouping (entities within a semantic cluster). The hypergraph is always represented by an incidence matrix $\mathbf{H} \in \{0, 1\}^{|\mathcal{V}| \times |\mathcal{E}|}$, where $H(v, e) = 1$ indicates entity $v$ belongs to hyperedge $e$.

\subsection{Lightweight Node Extraction}

Efficient graph-based RAG uses lightweight Named Entity Recognition (NER) models (e.g., GLiNER or SpaCy) to extract entities directly from the raw text, thereby bypassing the computationally intensive relation extraction (RE) process. For each sentence $s_{i,j}$ in document $d_i$, we extract a set of entities $E_{i,j}$. The global node set $\mathcal{V}$ is the union of all unique entities: $\mathcal{V} = \bigcup_{d_i \in \mathcal{C}} \bigcup_{s_{i,j} \in d_i} E_{i,j}$. This process scales linearly with the corpus size, effectively avoiding the $\mathcal{O}(N^2)$ complexity associated with pairwise relation modeling.
