\subsection{Spatiotemporal Scene Graphs from Video}
Scene graphs encode objects as nodes and relationships as edges.
Recent work extends them temporally: SceneSayer~\cite{scenesayer2024eccv} predicts scene graph evolution, DriveLM~\cite{drivelm2024eccv} introduces graph-structured VQA for driving, and STEP~\cite{step2025cvpr} constructs spatio-temporal scene graphs for Video-LLMs.
In 3D, Lost~\&~Found~\cite{lostfound2025cvpr} builds dynamic 3D scene graphs from egocentric observations, FROSS~\cite{fross2025iccv} enables real-time 3D scene graph generation from monocular video, and 3DGraphLLM~\cite{3dgraphllm2025iccv} combines 3D scene graphs with LLMs for spatial understanding.
Our \textit{spatiotemporal knowledge graphs} combine the strengths of both families: from scene graphs we inherit fine-grained object-level detail with rich semantic descriptors and spatial relationships; from topological graphs we inherit the ability to cover large environments from monocular video without 3D reconstruction. By adding persistent object identity via LLM-based semantic association, our representation bridges these two paradigms in a way not explored in prior work.

\subsection{Persistent Memory from Egocentric Video}
Maintaining long-horizon memory from egocentric observations is critical for embodied agents.
VideoAgent~\cite{videoagent2024eccv} iteratively searches long videos using structured memory, AMEGO~\cite{amego2024eccv} constructs active memory representations, and Embodied VideoAgent~\cite{embodiedvideoagent2025iccv} integrates persistent scene memory with embodied sensor streams.
ReMEmbR~\cite{anwar2024remembr} builds retrieval-augmented spatio-temporal memory pairing visual observations with metric poses, while SNOW~\cite{snow2025arxiv} constructs 4D scene graphs with persistent object identity.
VL-KnG builds persistent memory through knowledge graphs rather than latent representations, enabling explicit, queryable, and interpretable scene memory that scales independently of video length.

\subsection{Vision-Language Navigation and Embodied QA}
Vision-language navigation (VLN)~\cite{wu2024vision, anderson2018vision} connects navigation with language instructions.
NavGPT-2~\cite{zhou2024navgpt} combines LLM reasoning with topological graphs, GSA-VLN~\cite{gsavln2025iclr} maintains persistent topological graph memory, and MobilityVLA~\cite{chiang2024mobility} builds topological graphs from demonstration videos for long-range navigation.
NWM~\cite{nwm2025cvpr} introduces navigation world models that predict future observations, while UniGoal~\cite{unigoal2025cvpr} unifies zero-shot goal navigation via scene graph representations.
In embodied QA, OpenEQA~\cite{majumdar2024openeqa} establishes a comprehensive benchmark for scene understanding from egocentric histories, and DAAAM~\cite{daaam2025arxiv} constructs 4D scene graphs for temporally grounded QA.
Our work addresses both navigation and QA through a unified knowledge graph representation.

\subsection{Environment Representation for VLN}
Several groups of methods can be found on the environment representation, both in the general case and in the VLN-specific case. Multimodal 3D-mapping methods like VLMaps \cite{huang2022visual} and ConceptFusion \cite{jatavallabhulaconceptfusion} extend commonly used in robotics 3D maps with multimodal embeddings, enabling natural language queries to the map. ConceptGraphs \cite{gu2024conceptgraphs} enhance this approach by constructing a multimodal scene graph, which is an example of the knowledge graph \cite{yudin2025m3dmap}, for advanced reasoning with LLM. In general, 3D graphs \cite{armeni20193d} are a popular way for scene representation, employed by methods like Hydra \cite{hughes2022hydra} and Clio \cite{maggio2024clio}. RoboHop \cite{garg2024robohop} makes a step towards getting free of expensive range sensing by constructing a topological graph based on segments extracted from the observed frames.
An alternative growing approach for range-less environment representations is image-based topological graphs \cite{shah2021ving}. The full images of the various locations in the environment are employed as nodes, and a traversability score between views is assigned to the edges. Compared to the scene graphs, topological graphs often cover larger areas, up to kilometers, but lack fine-grained details. LM-Nav \cite{shah2023lm} exploited CLIP-based retrieval to select image goals according to the navigation query, which are then passed to the learned local navigation policy. MobilityVLA \cite{chiang2024mobility} builds a topological graph using a demonstration tour video, and the same video is passed to a large VLM to identify a goal frame according to the query. Finally, ReMEmbR \cite{anwar2024remembr}, despite not focusing on topological graphs, provides a goal proposal by exploiting retrieval-augmented memory over previously visited frames, paired with metric poses.
Our proposed approach derives the best aspects of each group. It constructs a knowledge graph from the demonstration tour video in an efficient manner, capturing both global and local properties of the environment. This graph is passed to the LLM for question answering and goal frame proposal, which can finally be fed to the vision-only policy or classical range-based navigation system.

\subsection{Open-Vocabulary Scene Understanding}
Open-vocabulary approaches enable scene understanding without predefined categories.
ConceptGraphs~\cite{gu2024conceptgraphs} constructs open-vocabulary 3D scene graphs using foundation model features, OvSGTR~\cite{ovsgtr2024eccv} addresses open-vocabulary scene graph generation via transformers, and SceneGraphLoc~\cite{scenegraphloc2024eccv} leverages scene graphs for visual localization.
Unlike these methods requiring depth sensing or 3D reconstruction, VL-KnG operates on monocular RGB video, building open-vocabulary knowledge graphs using VLM-based detection and semantic relationship extraction.

\subsection{Graph-Based Retrieval and Reasoning}
GraphRAG~\cite{Han2024RetrievalAugmentedGW} has emerged as a powerful paradigm for structured retrieval and reasoning.
Vgent~\cite{vgent2025neurips} applies graph-based retrieval for long video understanding, and DAAAM~\cite{daaam2025arxiv} constructs 4D scene graphs from multi-modal sensor data for temporally grounded QA.
VL-KnG is distinguished by operating solely on monocular RGB video, constructing spatiotemporal knowledge graphs via LLM-based semantic association (not visual tracking or 3D reconstruction), and processing queries through Graph-based RAG~\cite{Han2024RetrievalAugmentedGW}---enabling explainable, training-free reasoning.
