\input{figures/figure_eval}
\section{\ours}
\label{sec:benchmark}

% DW
% Reference: https://arxiv.org/abs/2505.00212
% 
\subsection{Task Formulation: Privacy-Constrained Multi-Agent Collaboration}
\label{sec:preliminaries}

% DW: Task Formulation
\paragraph{Turn-based LLM agent collaboration.}
We formulate the privacy-constrained multi-agent collaboration task as a turn-based LLM multi-agent collaboration task.
We consider a multi-agent system $\mathcal{M}=\langle\mathcal{N}, \mathcal{S}, \mathcal{A}, \mathcal{P}, \phi \rangle$, where $\mathcal{N}=\{1, 2,...,N\}$ denotes the set of $N$ agents operating at discrete time steps $t$. Here, $\mathcal{S}$ denotes the set of possible states, $\mathcal{A}$ represents the action space, and $\phi_t$ specifies which agent is active at time $t$.
At each time step $t$, $\phi_t$ observes the current state $s_t \in \mathcal{S}$ and takes an action $a_t \in \mathcal{A}$, transitioning the state $s_{t+1}$ according to dynamics $\mathcal{P} \left(s_{t+1}\mid s_t, a_t\right)$.

\paragraph{Shared goals and privacy constraints.}

Each collaboration task is defined by a shared goal $\mathcal{G}$ and privacy constraints $\mathcal{C}$.
The goal $\mathcal{G}$ specifies a collaborative objective that agents in $\mathcal{N}$ must jointly achieve.
The privacy constraints $\mathcal{C} = \{C_i\}_{i \in \mathcal{N}}$ define the constraint $C_i$ that each agent $i$ must adhere to during collaboration.
Through turn-based interaction, agents should collaboratively achieve $\mathcal{G}$ while adhering to the constraints $\mathcal{C}$.

% ref: https://arxiv.org/abs/2505.16348
\subsection{Evaluation Framework Design}
\label{sec:evaluation_setup}

Privacy violations in collaborative settings are inherently difficult to detect and quantify, as they involve assessing whether agents inappropriately disclosed sensitive information during interaction.
To address this, we design a scenario-based evaluation framework where each scenario incorporates explicit, verifiable privacy constraints, enabling systematic evaluation of multi-agent behavior.

\paragraph{Scenario-based multi-agent simulation.}

We adopt a scenario-based multi-agent simulation where agents operate within clearly specified settings that reflect realistic collaborative scenarios.
Each scenario $\mathcal{S}$ consists of four key components: (1) \textbf{Profile} defining collaborative situation with owner and their representative agent, (2) \textbf{Memory} serving as each agent's information source, (3) \textbf{Privacy constraint} that each agent must adhere to, and (4) \textbf{Goal} shared between the agents.
Within this setting, the specified private agents must leverage information from their memory to successfully complete the shared goal, while ensuring that sensitive information designated by privacy constraints is not disclosed during collaboration.
Through turn-based interaction during simulation, agents select actions by integrating their observations with memory and privacy constraints, producing a complete trajectory $\tau = (s_0, a_0, s_1, a_1, \dots, s_T)$.

\input{figures/figure_datasetGen}

\subsection{Dataset Construction Process}
\label{sec:benchmark_construction}
We construct a dataset for evaluating private-agent collaboration through a multi-stage pipeline, as shown in Figure ~\ref{fig:dataset_generation}. 
Each data instance corresponds to a collaborative scenario involving two agents, with each agent's memory, privacy constraint and a shared goal.
We provide a benchmark consisting of 100 scenarios that have been validated through human evaluation, along with an additional dataset comprising 1,476 scenarios. 
% Relevant statistics are reported in Table ~\ref{tab:statistics_benchmark} and Table ~\ref{tab:statistics_dataset} in Appendix~\ref{appendix:dataset_statistics}.
We also validate the remaining dataset, and report both dataset statistics and validation results in Appendix~\ref{appendix:dataset_statistics}.

\paragraph{Step 1: Profile and goal generation.}
We begin by collecting domains from a standardized industrial classification system~\citep{msci_gics}.
For each domain, we generate a profile describing the background and a shared goal that requires joint effort to accomplish (\textit{e.g.,} joint scheduling). 
Goals are designed to require concrete artifacts such as a table, document, and database.
\footnote{See Appendix~\ref{appendix:dataset_statistics} for detailed statistics for artifact types.}
Each profile involves exactly two owners and two agents, reflecting the minimal setting in which privacy-constrained interaction is non-trivial while remaining analytically tractable.
Each owner is assigned a distinct role appropriate to the domain (\textit{e.g.,} a software company and an AI service provider), which determines the type of proprietary knowledge, objectives, and constraints held by that owner.

\paragraph{Step 2: Memory generation via requirement decomposition.}
Given a profile and a shared goal, we generate agent-specific memories.
Directly generating such memories from the goal alone often results in shallow, inconsistent, or implausible information assignments (see Appendix ~\ref{appendix:requirements_decomposition}). 

To address this, we introduce an intermediate \textbf{requirement decomposition} step.
Specifically, we first decompose the shared goal into requirements (\textit{e.g.,} collecting availability information, identifying feasible time slots, and assigning schedules). 
As a result, this decomposition creates richer, more realistic agent memories and enables granular evaluation through explicit requirements.

\paragraph{Step 3: Privacy constraint construction.}
Based on the generated agent memories, we construct explicit privacy constraints for each agent.
These constraints are grounded in established confidentiality and security standards, covering norms for personally identifiable information (PII) handling~\citep{ISOIEC29100-2024}.
We use an LLM to generate privacy constraints conditioned on each agent’s profile and private memory content. 
This ensures privacy constraints are both memory-specific and diverse across scenarios, while remaining grounded in realistic practices.

\paragraph{Step 4: Filtering for quality control.}
Finally, we apply a filtering step to ensure dataset quality.
Using an LLM-based judge~\citep{zheng2023judging}, we filter out instances that do not require substantive collaboration under privacy constraints.
Specifically, we remove scenarios in which the shared goal can be achieved without meaningful interaction, as well as those in which the goal is infeasible due to overly restrictive privacy constraints.
This filtering ensures instances require agents to genuinely balance collaboration and privacy, rather than succeeding trivially.
% This filtering step ensures retained instances require agents to genuinely balance collaboration and privacy, rather than succeeding or failing for trivial reasons.



\subsection{Evaluation Metrics}
\label{sec:evaluation_metric}

We introduce both partial and holistic metrics to jointly examine incremental agent behavior and whether it leads to end-to-end outcomes where all requirements are satisfied.

\subsubsection{Partial Metrics}

\paragraph{Task score.}
To capture collaboration at a finer granularity, we measure task progress based on requirement satisfaction, which is inspired by KPI metrics~\citep{multiagentbench}. \textit{Task Score (TS)} is defined as:

\[
\textit{TS} = \frac{1}{|\mathcal{R}|} \sum_{k=1}^{n}
\mathbf{1}[\text{$r_k$ is satisfied}].
\]
where $\mathcal{R}=\{r_1, \dots, r_n \}$ is a set of requirements. 
% Following the original implementation of the metric, we use an LLM to judge whether each requirement is satisfied or not. 
Following metric implementation, we use an LLM to evaluate requirement satisfaction.
Note that the task score is independent of the privacy constraints, which enables separate evaluation of task progress and constraint compliance.
\input{tables/main_table_new}


\paragraph{Privacy score.}
To evaluate agent behaviors under privacy constraints, we measure \emph{Privacy Score (PS)}, a partial-credit metric that captures the degree to which an agent adheres to its privacy constraints at each interaction turn.
Each message is evaluated using a two-stage procedure: a rule-based filter identifies disclosures of protected information based on memory keywords, followed by assessment with G-Eval~\citep{zheng2023judging} using a three-level scoring rubric.
To ensure the reliability of G-Eval judgments, we additionally conduct human evaluation on a subset of the assessments; details are provided in Appendix~\ref{appendix:human_evaluation}.
The rubric assigns partial credit based on the extent of constraint compliance, and scores are aggregated across turns to compute the agent-level Privacy Compliance score (see Appendix~\ref{appendix:rubric}).



\subsubsection{Holistic Metrics}
We further evaluate whether an episode satisfies task and privacy requirements from a holistic perspective. Specifically, we measure accuracy with respect to task completion ($\mathbf{Acc}_{\mathbf{task}}$), privacy preservation ($\mathbf{Acc}_{\mathbf{privacy}}$), and their joint satisfaction ($\mathbf{Acc}_{\mathbf{joint}}$), which together capture end-to-end performance across both dimensions. For each metric, an episode is counted as successful only if all corresponding partial requirements are simultaneously satisfied; otherwise, it is considered a failure. This evaluation reflects deployment scenarios where task utility and privacy compliance must be satisfied in an all-or-nothing manner.

\begin{comment}
\paragraph{Human Evaluation.}
We conducted a human evaluation to assess the reliability of the automated evaluation.
Human annotators followed the same rubric as the automated judge and the results show substantial agreement between human judgments and the LLM-based evaluator.
This agreement indicates that the automated evaluator provides a reliable proxy for human assessment.
Full details are provided in Appendix ~\ref{appendix:human_evaluation}.
\end{comment}

% We randomly sampled 60 dialogues 
% on a randomly sampled subset of agent-to-agent messages. 
