\section{Ablation Study}
\subsection{Effect on Privacy-Aware Prompting}
\label{sec:effect_privacy_aware_prompting}

To distinguish between inherent model limitations and the role of prompting, we examine how different ways of providing privacy-related instructions affect agent behavior under privacy constraints. Specifically, we consider two variations: (i) a baseline without explicit privacy-related instructions in the system prompt, and (ii) encouraging agents to use chain-of-thought reasoning about privacy constraints.

\input{tables/camera_ready/2_effect_of_prompts}

As shown in Table~\ref{tab:prompt_effect}, privacy performance drops substantially across all models without explicit privacy-related instructions. In contrast, encouraging step-by-step reasoning about privacy constraints does not consistently improve performance and may even reduce task accuracy. Overall, these results suggest that explicit instructions are necessary for maintaining privacy, but prompt-level interventions alone are insufficient to address the observed failures.



\subsection{Protocol Variation Analysis for Initiator Dominance}
\label{sec:initiator_dominance}

We examine whether the observed initiator dominance stems from multi-agent coordination under privacy constraints or from the fact that Agent A initiates the interaction and shapes the solution space. To evaluate this possibility, we introduce a protocol variation in which Agent B is explicitly instructed to propose and structure the solution space at the beginning of the interaction. This modification shifts the initiative from Agent A to Agent B while keeping all other components unchanged.

\input{tables/camera_ready/3_initiator_dominace}

Table~\ref{tab:initiator_dominance} reports that we do not observe a consistent performance advantage for Agent B under the modified protocol.
In most cases, performance remains similar or decreases, and the overall asymmetry persists. These results suggest that the dominance of the initiating agent cannot be fully explained by turn-taking artifacts alone, and instead reflects a more fundamental characteristic of multi-agent coordination under privacy constraints.