\appendix
\clearpage

\section*{Appendix}

\section{Tool Use Scenarios}
\label{appendix:tool_use_task}

\subsection{Tool Set}
\label{app:full_tool_set}
We source tools from publicly available MCP~\citep{anthropic2024modelcontextprotocol} servers, selecting those that support the generation of diverse artifacts such as documents, tables, code, and SQL queries. To ensure both efficiency and experimental stability, we first include the full set of tools provided by each selected MCP server and run simulations over a subset of sampled scenarios. Based on tool usage statistics observed during these simulations, we retain only the tools that are frequently invoked by agents, resulting in a curated tool set used in all experiments. The complete tool list is provided in Table~\ref{tab:tool-set}.


\subsection{Experiment Setup}
\label{app:experiment_setup}
All agents are instantiated using large language models that natively support tool calling. We chose four representative models: GPT-5.1, Llama-3.3-70B, Qwen-3-32B, and Ministral-3-14B-Instruct-2512~\citep{ministral3_14b}. During simulation, each agent may invoke tools up to 5 times per turn, with a maximum interaction length of 20 turns per episode. We adopt the same evaluation framework and metrics as in Table~\ref{tab:main_results}, except that we additionally provide the agents’ produced artifacts—such as documents, tables, or code—as supplementary evidence for evaluation.



\input{tables/tool_set_table}

\subsection{Experiment Result}
\subsubsection{Overall Performance with Tool Use}
We observed a substantially larger performance decline in task-related metrics within tool-use scenarios compared to settings without tool use (Table \ref{tab:tool_use_table}). Given that the primary distinction is the requirement for tool manipulation, these results suggest that task success is most heavily dictated by a model’s tool-use capability rather than other attributes.

At the same time, a closer examination of absolute performance reveals an additional challenge. While several models achieve moderate scores on partial metrics, the task accuracy remains consistently below 20\% across all models. This is because achieving a perfect execution is exceptionally difficult in sequential tool-use scenarios: even a single failure in the tool-call sequence can act as an irreversible point of failure, making recovery within a single episode nearly impossible. As a result, incorrect or incomplete executions tend to propagate through the interaction trajectory, ultimately leading to the low task accuracy observed in tool-augmented multi-agent interactions.
\input{tables/tool_use_table}

\subsubsection{Impact of Execution Errors}

\input{tables/tool_error_table}
To better understand the role of execution stability, we summarize the tool execution error rates for each model in Table~\ref{tab:error-rate}. GPT-5.1 exhibits relatively low execution errors, whereas LLaMA-3.3-70B and Qwen-3-32B show high error rates of around 40\%. Ministral-3-14B is significantly less stable, with execution failures occurring in roughly 80\% of all runs. During our experiments, we observed that these failures—often manifesting as consecutive tool-call errors, request timeouts, or empty responses frequently led to the premature termination of simulations before completion.

Consistent with this trend, excluding such error cases leads to notable improvements across all reported metrics (Table~\ref{tab:tool_use_table}). This confirms that execution failures substantially distort performance evaluation in tool-rich environments. More importantly, these errors systematically bias holistic evaluation by disproportionately penalizing models where early-stage failures preclude any opportunity for recovery. This effect is especially pronounced for joint metrics, where a single failed tool interaction, such as a timeout or a malformed call, can invalidate the entire sequence of otherwise correct reasoning in later turns.

\label{app:experiment_result}

\input{tables/camera_ready/4_quantitative_failure_modes}

\section{Quantitative Analysis for Failure Modes}
\label{appendix:failure_modes}

\paragraph{Early-stage privacy violations.}
We sample 720 episodes with zero Privacy Score and record the first turn at which a privacy violation occurs. As shown in Table~\ref{tab:early_privacy_violations}, 74.86\% (539/720) of violations occur within the first three turns (29.58\% at turn 1, 33.06\% at turn 2, and 12.22\% at turn 3).

\paragraph{Over-conservative abstraction.}
We randomly sample 100 episodes (50 range-type and 50 change-type) from 925 task-failure episodes for detailed inspection. We identify responses containing masking placeholders (e.g., \texttt{[TRUNCATED]}, \texttt{[Anonymized]}, \texttt{[REDACTED]}, \texttt{[MASKED]}). Manual review confirms 35 cases where masking removed necessary information, accounting for 35\% of the sampled task-failure episodes.

\paragraph{Privacy-induced hallucination.}
Using the same sampling protocol described above, we identify 41 cases (30 change-type and 11 range-type) in which agents altered scenario-grounded information under privacy constraints. LLM-as-a-judge verification confirms that these alterations were induced by privacy-related context, indicating that 41\% of the sampled task-failure episodes involve privacy-induced hallucination.


\section{Human Evaluation}
\label{appendix:human_evaluation}

To complement the automatic evaluation results, we conduct a human evaluation to assess qualitative aspects that are difficult to capture with automated metrics. We develop a lightweight annotation interface, illustrated in Figure~\ref{fig:interface}. We randomly sampled 80 dialogs, and authors with high English proficiency manually evaluated individual instances with respect to correctness and privacy compliance. Each evaluation instance was judged independently, based solely on the observable properties of the generated responses.

We analyzed the consistency between human judgments and automated scores by computing the Spearman rank correlation ($\rho$) between the human evaluation results and the corresponding automatic metrics. Specifically, we measured the correlation for the task score and the privacy score by analyzing evaluations for each task requirement and privacy constraint. The obtained coefficients are 0.870 and 0.901, respectively. These values indicate a strong positive correlation \citep{liu2023gevalnlgevaluationusing}, suggesting that the automatic evaluation metrics align reasonably well with human judgments for both task performance and privacy compliance.

\input{figures/CamReady_figure_humanEval_UI}
\input{tables/camera_ready/1_G-Eval_reliability}


% While individual-level variance remains, the overall ranking of model variants is preserved under both evaluation schemes.


\section{Dataset Statistics}
\label{appendix:dataset_statistics}
This appendix reports descriptive statistics of the generated scenarios.
We summarize the distribution of (i) the types of artifacts required by scenario goals, (ii) the number of requirements per scenario, and (iii) the number of memories per requirement and per scenario.

The benchmark consists of 100 scenarios and the additional dataset consists of a total of 1,476 scenario instances. Descriptive statistics for this benchmark are provided in this appendix.

Privacy constraints are not included in the statistical analysis, since they are generated in a fixed manner: for each scenario, exactly one privacy constraint is produced per agent, resulting in two privacy constraints per scenario by construction.

\paragraph{Validation on the additional dataset.}
The additional scenarios are generated using the same construction pipeline as the 100 human-validated benchmark instances. To verify that our main findings are not specific to the validated subset, we conduct experiments on a randomly sampled set of 150 additional scenarios from the larger dataset.

As shown in Table~\ref{tab:additional_dataset_performance}, the resulting performance trends closely match those reported in the main results. Across all models, \textsc{Acc\_joint} remains similar to the scores on the validated benchmark, with only small absolute differences.

\input{tables/camera_ready/6_additional_dataset_performance}
\input{tables/camera_ready/7_additional_dataset_spearman}


We further report Spearman correlation coefficients between the main benchmark results and the 150-sample results to quantify ranking stability. As shown in Table~\ref{tab:additional_dataset_correlation}, both task-score and privacy-score rankings remain strongly correlated across the two sets, suggesting that the comparative model trends are stable beyond the human-validated subset.

\input{tables/statistics_benchmark}
\input{tables/statistics_dataset}

\section{Effect of Requirements Decomposition}
\label{appendix:requirements_decomposition}

In our framework, goals specify desired outcomes rather than explicit construction processes. When memory generation is conditioned solely on such outcome-level goals—e.g., “construct a joint database”—we observe that multiple failure characteristics frequently arise within a single memory instance.

Specifically, outcome-conditioned generation may assume the existence of a fully integrated database without explicitly representing underlying requirements such as data source identification, schema compatibility, access constraints, or validation criteria. As a result, the generated memories are shallow due to missing requirement-level detail, inconsistent with realistic system development workflows, and often implausible given practical constraints. These failure characteristics commonly co-occur, reflecting a shared structural limitation rather than independent error types.

Requirement decomposition addresses this limitation by explicitly enumerating and structuring the necessary conditions that must be satisfied to achieve the desired outcome. By grounding memory generation in decomposed requirements rather than the outcome alone, the model produces representations that are more complete, internally consistent, and aligned with real-world constraints.

\section{Holistic Performance under Cooperative and Adversarial Partners}
\label{app:holistic_partner_results}

\input{tables/adversarial_result}


\section{Responsible NLP Research Checklist}

This appendix provides responses to the Responsible NLP Research Checklist required by ACL Rolling Review. The content below directly corresponds to the checklist items and reflects the design choices, data sources, and experimental procedures used in this paper.

\medskip
\noindent
\textbf{Limitations.}
The limitations of this work are explicitly discussed in the Limitations section of the paper. These include the minimal two-owner collaboration setting, the use of natural language privacy constraints evaluated by an LLM-based judge, fixed agent prompting and memory formulation, and the bounded interaction horizon. These design choices enable controlled analysis but may not capture all dynamics present in larger-scale or long-horizon deployments.

\medskip
\noindent
\textbf{Risks.}
This work studies privacy-aware multi-agent collaboration and therefore considers potential risks related to misuse of privacy-constrained coordination mechanisms, over-reliance on automated constraint enforcement, and misinterpretation of abstracted privacy constraints. These risks and broader impacts are discussed in the Ethical Considerations section.

\medskip
\noindent
\textbf{Use of scientific artifacts.}
This work uses existing large language models and publicly available standards and prior academic literature as scientific artifacts. All such models, frameworks, and references are properly cited in the main paper. No proprietary or restricted-access artifacts are used.

\medskip
\noindent
\textbf{Licenses and terms of use.}
All referenced models and external resources are used in accordance with their original licenses and terms of use. 
In particular, the GICS\textregistered{} framework is referenced solely for high-level domain categorization and terminology, and no proprietary index data, classification tables, or licensed datasets from MSCI are redistributed, stored, or used to generate derivative data. 
Similarly, ISO/IEC~29100 is cited for conceptual grounding and publicly accessible terminology only; the full standard text, extracts, or proprietary content are not redistributed or included. 
The study does not include any datasets or artifacts that violate licensing or usage restrictions.


\medskip
\noindent
\textbf{Personally identifiable information.}
This work does not use, collect, or release any personally identifiable information (PII). All scenarios, agent memories, interaction trajectories, and privacy constraints are synthetically generated. Privacy constraints are derived from publicly available standards and prior literature rather than from real user data.

\medskip
\noindent
\textbf{Artifact documentation.}
The benchmark construction process, scenario domains, agent memory generation, privacy constraint types, and evaluation metrics are documented in Sections~\ref{sec:benchmark} of the paper, with additional details provided in the appendices.

\medskip
\noindent
\textbf{Computational experiments.}
The evaluated models, interaction settings, and evaluation protocols are described in Section~\ref{sec:experiments}. Experimental results are reported using aggregate metrics over multiple interaction episodes. Human evaluation results and correlations with automated metrics are reported in Appendix~\ref{appendix:human_evaluation}.

\medskip
\noindent
\textbf{Human annotators.}
A human evaluation is conducted to assess the reliability of the automated privacy compliance metrics. Human annotators evaluate agent-generated messages based solely on observable outputs and a predefined rubric. The evaluation does not involve exposure to personal, sensitive, or distressing content, as all evaluated data is synthetically generated. Details of the evaluation protocol and rubric are provided in Appendix~\ref{appendix:human_evaluation}.

\medskip
\noindent
\textbf{Demographic information.}
Demographic attributes of annotators are not collected, as they are not required for the evaluation task and no human-subject data is analyzed beyond rubric-based judgments of synthetic content.

\medskip
\noindent
\textbf{Use of AI assistants.}
AI assistants are not used to generate experimental data, benchmark instances, or evaluation results. Any auxiliary tools used for editing or formatting do not affect the scientific claims or empirical findings of this paper.

\section{Prompts Used in the Experiments}
This section presents the full set of prompts used in our experiments. The prompts define how agent profiles, goals, and scenario-specific contexts are generated and instantiated across different experimental settings. All prompts are reported verbatim to ensure reproducibility and to facilitate future extensions or comparisons.

\label{appendix:prompts}

\subsection{Dataset Generation Prompt}
\label{appendix:dataset_generation}
We provide dataset generation prompts in 
Figure~\ref{fig:prompt_dataset_1}, Figure~\ref{fig:prompt_dataset_2}, Figure~\ref{fig:prompt_dataset_3}, Figure~\ref{fig:prompt_dataset_4-1}, and Figure~\ref{fig:prompt_dataset_4-2}.

\subsection{Task Evaluation Prompt}
\label{appendix:task_evaluation_prompt}
We provide task evaluation prompts in 
Figure~\ref{fig:prompt_task}.

\subsection{Privacy Evaluation Prompt}
\label{appendix:rubric}

We provide privacy evaluation prompts in 
Figure~\ref{fig:prompt_priv}.

\subsection{Privacy Evaluation Rubric}
\label{appendix:rubric}

Table~\ref{tab:privacy_rubric} summarizes the privacy evaluation rubric used in our benchmark. Privacy observance is evaluated at the level of individual information disclosure instances. Each instance is scored based solely on the observable properties of the disclosed information entity and its relationship to the applicable privacy constraint conditions.

\input{tables/privacy_rubric}


\input{prompts/dataset_step1}
\input{prompts/dataset_step2}
\input{prompts/dataset_step3}
\input{prompts/dataset_step4-1}
\input{prompts/dataset_step4-2}
\input{prompts/privacy_g_eval}
\input{prompts/task_g_eval}
\input{prompts/agent_a}