
Consider a scenario where $N_a$ robots are deployed in a 3D scene with multiple different assignments, each starting from an initial pose $g^i_0$, and aiming to answer the questions $q^i_{1:N_q}$ related to its assignments.
The objective is to maximize the success rate while minimizing the exploration time, with all answers required within a time horizon $T_\text{max}$.
Each robot knows all questions, including those assigned to others.
They can communicate via natural language messages, denoted $\zeta^i$, to exchange information.

Each robot $i\in N_a$ is equipped with cameras that, at each time step $t$, can provide the robot with an RGB image $I^i_{c,t}$ and a depth image $I^i_{d,t}$ of the local scene as observations. The pose (2D position and orientation) of each robot at each time step is denoted as $g^i_t$, with the poses of all robots collected into a set $G_t = \{g^i_t \mid i=1,...,N_a\}$. Each robot is equipped with a collision-free planner $\pi$ to navigate. Given the current pose $g^i_{t}$ and a target position, the planner $\pi$ determines the next feasible pose $g^i_{t+1}$, with a low-level controller transporting the robot to the planned pose at $t+1$. 

In this case, a multi-robot multi-task Embodied Question Answering (MM-EQA) problem is defined with a tuple $\xi:= (E, G_0, T_\text{max}, Q, Y)$, where $E$ is the 3D scene with dimensions $L \times W \times H$, which is discretized into a voxel map $M$ composed of cubes with a side length of $l$. $L$, $W$, and $H$ representing the length, width, and height of the voxel map $M$; $G_0 = \{g^i_0 \mid i=1,...,N_a\}$ is a set of initial poses of the robots, and $T_\text{max}$ is the maximum time horizon allowed for the robots to explore the scene and complete the task. Each robot $i$ is assigned with $N_q$ questions to answer. The set $Q = \{q^i_j \mid i=1,...,N_\text{a},j=1,...,N_\text{q}\}$ collects all the questions assigned to the robots, with $q^i_j$ being the $j^\mathrm{th}$ question assigned to the $i^\mathrm{th}$ robot. Each question is a multiple-choice question with four choices $\{\text{`A', `B', `C', `D'}\}$. The ground truth answers are denoted by the set $Y = \{a^i_j\in \{\text{`A', `B', `C', `D'}\} \mid i=1,...,N_a,j=1,...,N_q\}$. 
