\section{Experimental Results}
\label{sec:experiments}


To understand how MAC performs for enterprise usage, we choose three business domains to experiment with. For each domain, we set up a set of agents and tools. Then, we manually collect benchmarking data for each domain. In this report, we show experiments on thirty scenarios from each domain. This dataset is also publicly released for others to benchmark their own multi-agent systems (Section~\ref{sec:intro}). The three domains are as follows:
\begin{enumerate}
\item Travel planning: agents help user plan a trip, which includes booking flights, booking hotels, finding local events, getting information about the weather, etc.
\item Mortgage financing: agents help user with mortgage issues, e.g., submitting loan applications, querying information about properties, retrieving banking information, etc.
\item Software development: agents help user design, implement, test, review, and/or deploy code.
\end{enumerate}

The first two domains are conversational, whereas the third domain is more about automation and requires minimal interaction with user. For the agent profile design, we have made sure to cover the following conditions to showcase adoption of multi-agent collaboration for various developer setups:

\begin{enumerate}
\item Supervisor agents with and without tools: The supervisor agent for Mortgage has access to MortgageLoans tools, whereas the supervisor agents for other domains do not have tools.
\item Specialist agents with and without tools: Many specialist agents have their own set of tools. However, some specialist agents in Software do not have tools as they should have the capability to complete the tasks without them.
\item Agent hierarchy with depth more than one: In Software, the supervisor agent can call on Deploy agent, which can then call on Infrastructure agent and Application agent.
\end{enumerate}

\begin{table}[t]
    \caption{Dataset statistics, including average number of goals per scenario, average number of assertions per scenario, total number of action groups, and total number of APIs/tools.}
    \label{tab:dataset_stats}
    \centering
    \footnotesize
    \begin{tabular}{lrrrr}
    \toprule
     Dataset & Avg. Goals per Scenario & Avg. Assertions per Scenario & Action Groups & APIs/Tools \\
     \midrule
     Travel & 2.13 & 4.55 & 11 & 52 \\
     Mortgage & 1.91 & 3.99 & 10 & 35 \\
     Software & 1.69 & 7.47 & 2 & 4 \\
     \bottomrule
     \end{tabular}
\end{table}


Table~\ref{tab:dataset_stats} shows an overview of the statistics for the three datasets. Action groups refer to group of tools (e.g. ``BookFlight'' action group is a set of tools for searching flights, booking flights, getting flight details, etc.). Travel and Mortgage each have more than thirty tools, whereas Software has only two tools. Software tends to have more assertions on average than Travel and Mortgage. Appendix~\ref{app:agent_profiles} shows the agents for each domain and their associated action groups, which are the set of tools that the agents have access to.


