\subsection{Coordination Mode Experiments}

\begin{table}[t]
    \caption{End-to-end evaluation of Coordination Mode}
    \label{tab:coord_results}
    \centering
    \footnotesize
    \begin{tabular}{llrr}
    \toprule
    Setting & Dataset & Overall GSR & Supervisor GSR \\
    \midrule 
    \multirow{3}{*}{\shortstack[l]{Supervisor: Sonnet 3.5 (20241022) \\ Specialists: Sonnet 3.5 (20241022)}} & Travel & 0.90 & 0.90 \\
    & Mortgage & 0.90 & 0.93 \\
    & Software & 0.90 & 1.00 \\
    \midrule 
    \multirow{3}{*}{\shortstack[l]{Supervisor: Sonnet 3.5 (20241022) \\ Specialists: Sonnet 3.0}} & Travel & 0.87 & 0.90 \\
    & Mortgage & 0.90 & 0.97 \\
    & Software & 0.77 & 0.90 \\
    \midrule
    \multirow{3}{*}{\shortstack[l]{Supervisor: Sonnet 3.5 (20241022) \\ Specialists: Haiku 3.5}} & Travel & 0.80 & 0.87 \\
    & Mortgage & 0.83 & 0.90 \\
    & Software & 0.87 & 0.93 \\
    \midrule
    \multirow{3}{*}{Single-agent: Sonnet 3.5 (20241022)} & Travel & 0.60 & -- \\
    & Mortgage & 0.80 & -- \\
    & Software & 0.53 & -- \\
    \bottomrule
    \end{tabular}
\end{table}

\begin{table}[t]
    \caption{Latency Performance of Coordination Mode}
    \label{tab:coord_latency}
    \centering
    \footnotesize
    \begin{tabular}{llrr}
    \toprule
    Setting & Dataset & \shortstack[r]{Avg. communication \\overhead per turn (s)} & \shortstack[r]{Avg. user-perceived \\turn latency \\per session (s)} \\
    \midrule 
    \multirow{3}{*}{\shortstack[l]{Supervisor: Sonnet 3.5 (20241022) \\ Specialists: Sonnet 3.5 (20241022)}} & Travel & 13.75 & 31.46 \\
    & Mortgage & 13.39 & 24.42 \\
    & Software & 35.44 & 168.73 \\
    \midrule 
    \multirow{3}{*}{\shortstack[l]{Supervisor: Sonnet 3.5 (20241022) \\ Specialists: Sonnet 3.0}} & Travel & 15.43 & 42.12 \\
    & Mortgage & 15.97 & 29.90 \\
    & Software & 53.48 & 137.31 \\
    \midrule
    \multirow{3}{*}{\shortstack[l]{Supervisor: Sonnet 3.5 (20241022) \\ Specialists: Haiku 3.5}} & Travel & 12.95 & 23.98 \\
    & Mortgage & 11.03 & 18.13 \\
    & Software & 36.65 & 125.31 \\
    \midrule
    \multirow{3}{*}{Single-agent: Sonnet 3.5 (20241022)} & Travel & -- & 14.12 \\
    & Mortgage & -- & 9.12 \\
    & Software & -- & 52.61 \\
    \bottomrule
    \end{tabular}
\end{table}

We report the goal success metrics for coordination mode across a variety of settings in Table~\ref{tab:coord_results}. For evaluating the assertions, we leverage OpenAI’s GPT-4o model~\cite{gpt4o} for providing LLM-based judgements. The results demonstrate that multi-agent collaboration achieves the best overall GSR of 90\% across the three evaluated domains when the Claude 3.5 Sonnet (20241022) model~\cite{claude35} is utilized as both the supervisor agent and the specialist agents. 

We further examine the impact of using different agent models. Switching the specialist agent model from Claude 3.5 Sonnet  to Claude 3.0 Sonnet shows a significant regression in the performance for the Software development domain. This is also apparent when the specialist agent is switched to Claude 3.5 Haiku, as the performance in the Software domain is mostly recovered with this newer generation of models.

We also compare the performance of a single agent with the multi-agent collaboration approach. In this experiment, a single agent is given the tools from all specialist agents combined and is responsible for assisting the user. We reuse the assertions collected for the multi-agent setup but replace any mentions of specialist agents with supervisor agent (e.g. ``flight agent books tickets'' becomes ``travel agent books tickets''). For any assertions about inter-agent behaviors, we would replace mentions of the primary agent with ``user'' and mentions of the specialist agent with the supervisor agent (e.g. ``code agent implements code and delivers back to software agent'' becomes ``software agent implements code and delivers back to user'').  

In the single-agent setting, we observe an absolute regression of up to 37\%. MAC allows each specialist agent to be provided with instructions for the specific subset of tasks it is supposed to handle. This specialized task assignment may not be achievable by a single agent, which may struggle to manage the multitude of instructions required to complete the complex tasks. In the single-agent trajectories, we observe more hallucination in tool parameters and incorrect tool choice. 



We report the latency metrics for our experiments in Table~\ref{tab:coord_latency}. When using Claude 3.5 Sonnet (20241022) for both supervisor agent and specialist agents, the average communication overhead per turn ranges from 13.39s to 35.44s, with the Software domain showing significantly higher overhead due to its complexity. The Software domain consistently demonstrates higher latency metrics across all settings, with user-perceived turn latency reaching 168.73s compared to 31.46s for Travel and 24.42s for Mortgage domains. While the single-agent setting shows lower user-perceived latencies, this comes at the cost of reduced goal success rates as shown in the previous results. See Appendix~\ref{app:full} for full results on coordination mode.

We also performed ablation experiments with the payload referencing capability of the supervisor agent, which is discussed in more detail in Section \ref{sec:ablations-payload}.