\subsection{Agreement with Human Evaluation}




Throughout this report, we have used an LLM to provide automatic judgements on assertions. This has helped scale our experiments so that we can quickly prototype and develop improved multi-agent systems. What if we ask a human to judge conversation success purely from their own perspective without any reference to assertions? To understand how well assertion-based evaluation compares with human evaluation, we deliver a batch of ninety trajectories to human annotators during one of our milestone checkpoints. For each conversation, we ask three annotators to provide binary judgements on a different set of guidelines. During this human evaluation, they are never shown assertions or LLM judgements and only instructed to determine success and efficiency from their own judgements. Table~\ref{tab:human_instructions} show the instructions given to human annotators for each success metric.

After the human annotators finish their evaluation, the aggregated majority judgement is used to compare against LLM evaluations. Note that for this milestone, we use Claude 3.5 Sonnet (20240620) for supervisor agent and Sonnet 3.0 for specialist agents.  See Appendix~\ref{app:human_eval} for the automatic and human evaluation results for this set of experiments.  We then compute agreement between human and LLM judges. Since the judgements for automatic and human evaluation are binary, we use agreement ratio to measure alignment between human and automatic evaluation. The agreement ratio is the number of conversations with matching judgements (either both 1 or both 0) over the total number of conversations evaluated. 

\begin{table}[t]
    \caption{The instructions given to annotators when performing human evaluation of conversation trajectories. Note that humans do not judge assertions and only determine success purely from their own judgements.}
    \label{tab:human_instructions}
    \centering
    \footnotesize
    \begin{tabular}{p{2cm}p{10cm}}
    \toprule
    Metric & Human annotator instructions \\
    \midrule
    User GSR & Evaluate from user’s perspective, whether the conversation with the primary agent meets the user's goals and successfully address user's requests or not. \\
    System GSR & From the perspective of the environment, evaluate whether the actual impacts of all agent actions accurately address and resolve all of the user's stated tasks, requests, and expectations within that specific environment or context.  \\
    Supervisor GSR & Evaluate from user's perspective whether the primary agent has tried its best to help the User, regardless of whether task was completed or the agent actions correctly impacted the environment. \\
    \bottomrule
    \end{tabular}
\end{table}

\begin{table}[t]
    \caption{The agreement ratios between human annotators and assertion-based benchmarking on success metrics across 90 conversation trajectories.}
    \label{tab:human_agreement}
    \centering
    \footnotesize
    \begin{tabular}{lrrrr}
    \toprule
    Dataset & Overall GSR & Supervisor GSR & User-side GSR & System-side GSR \\
    \midrule 
    Travel & 0.93 & 0.87 & 0.93 & 0.93 \\
    Mortgage & 0.87 & 1.00 & 0.97 & 0.87 \\
    Software & 0.97 & 0.77 & 1.00 & 0.90 \\
    \bottomrule
    \end{tabular}
\end{table}

For success metrics, the agreement is generally above 85\% (Table~\ref{tab:human_agreement}). The only exception is on primary agent success for software, where the agreement is 77\%. Here, the automatic evaluation has overall GSR as 90\% but the human annotators only believe the supervisor agent is successful in 87\% of the conversations. On the trajectories where the humans disagree with LLM judgements, we observe a mix of mistakes from both ends. For some trajectories, the human evaluation would mark that supervisor agent has not make a mistake but LLM judge has captured when the supervisor agent repeatedly wanting to follow-up with the user rather than delegating tasks to sub-agents. There is also the reversed case where the LLM judge does not observe any issues with the supervisor agent but the human annotators detect that the supervisor agent neglects to conduct thorough code review with the Review agent.

%For efficiency metrics, the agreement was generally above 80\%, with the exception of forgetfulness and verbosity for Software. Here, the LLM judge was actually more strict and accurate than the human annotators. It was able to detect when the primary agent forgot the initial user requests. Since this is a task automation domain, it is important that the primary agent remembers the initial request to prevent further, unnecessary follow-ups. The initial user requests tend to be very long for this domain with code files and lists of requirements to be fulfilled. So, annotators might be more sidetracked and not spot the inefficiencies as easily.

