\section{Communication Mechanism Ablations}
\label{sec:ablations}

Section~\ref{sec:experiments} shows the main results of our approach with different models. In this section, we provide additional ablations to quantify the impact of MAC communication mechanisms. This includes experiments with and without payload referencing, as well as comparison with open-source frameworks.  The additional experiments provide more justification on the utility of MAC for enterprise applications.

\subsection{Impact of Payload Referencing}
\label{sec:ablations-payload}

\begin{table}[t]
    \caption{Impact of payload referencing on GSR and latency for Software}
    \label{tab:payload_ref}
    \centering
    \footnotesize
    \begin{tabular}{lrrrr}
    \toprule
     & \shortstack[r]{Overall \\ GSR} & \shortstack[r]{Avg. \\ communication \\ overhead per \\ turn (s)} & \shortstack[r]{Avg. \\ user-perceived \\ turn latency \\ per session (s)} & \shortstack[r]{Avg. \\ output \\ tokens per \\ communication} \\
    \midrule 
    With Payload Ref. & 0.90 & 35.44 & 168.73 & 373.77 \\
    Without Payload Ref. & 0.73 & 48.78 & 159.75 & 539.21 \\
    \bottomrule
    \end{tabular}
\end{table}

In Table~\ref{tab:payload_ref}, we report the results of an ablation experiment with Payload Referencing for Software domain with Claude 3.5 Sonnet (20241022) as the supervisor agent as well as specialist agents. This experiment reveals that payload referencing significantly improves both the efficiency as well as effectiveness of multi-agent collaboration, particularly in the code-heavy Software domain. The impact is most pronounced here as large code blocks are frequently exchanged between agents.

Enabling payload referencing results in a 23\% relative improvement in overall GSR as well as a 27\% relative reduction in the average communication overhead per turn. The latter can be attributed to a 30\% relative reduction in the average output tokens per communication of the supervisor agent, as it is able to leverage the payload referencing mechanism to more efficiently reduce the number of generated tokens required for sharing code blocks, while improving the goal success rate.

When enabling payload referencing, we also observe an increase in the average user-perceived turn latency. As this also includes the latency of the specialist agents, it suggests that the specialist agents operating for a smaller number of turns may be detrimental to the overall goal success.

In conclusion, payload referencing proves particularly valuable in domains such as Software, as it:

\begin{itemize}
    \item Enables precise referencing of payloads without expensive regeneration of tokens
    \item Reduces the likelihood of payload corruption during agent-to-agent transmission
    \item Maintains formatting and structure of the payload across agent communications
    \item Facilitates more efficient parallel inter-agent communication
\end{itemize}


Our experiments suggest that payload referencing is a crucial optimization for multi-agent systems, particularly in domains involving structured content exchange. The mechanism not only improves system performance metrics but also enhances the quality and reliability of agent interactions.

\subsection{Comparison with Task Automation Framework}
\begin{table}[t]
    \caption{Comparison with a widely adopted open-source framework for task automation (OSF). Note that the version of Sonnet 3.5 used below refers to an older version.}
    \label{tab:osf_results}
    \centering
    \footnotesize
    \begin{tabular}{llrr}
    \toprule
    Setting & Dataset & Overall GSR & Supervisor GSR \\
    \midrule 
    \multirow{3}{*}{\shortstack[l]{[MAC Coordination Mode] \\ Supervisor: Sonnet 3.5 (20240620) \\ Specialists: Sonnet 3.0}} & Travel & 0.87 & 0.90 \\
    & Mortgage & 0.90 & 0.97 \\
    & Software & 0.77 & 0.90 \\
    \midrule 
    \multirow{3}{*}{\shortstack[l]{[OSF] \\ Supervisor: Sonnet 3.5 (20240620) \\ Specialists: Sonnet 3.0}} 
    & Travel & 0.50 & 0.80 \\
    & Mortgage & 0.63 & 0.87 \\
    & Software & 0.40 & 0.63 \\
    \midrule
    \multirow{3}{*}{\shortstack[l]{[OSF] \\ Supervisor: GPT-4o (mini) \\ Specialists: GPT-4o (mini)}} 
    & Travel & 0.43 & 0.63 \\
    & Mortgage & 0.40 & 0.67 \\ 
    & Software & 0.33 & 0.77 \\
    \bottomrule
    \end{tabular}
\end{table}



We also conducted a comparative evaluation of our implementation against a widely adopted open-source framework (OSF) for task automation. The OSF implements multi-agent collaboration as a sequential task-automation workflow, wherein the supervisor agent receives a task from the user and is responsible for breaking it up into one-time sub-tasks for its sub-agents. However, as our evaluation is primarily based on more conversational back-and-forth between the specialist agents, the one-time task assignment may not be sufficient. Therefore, we also expanded the OSF to support multiple sub-agent interactions. The OSF also enables tool-use for its agents using ReAct-style prompting~\cite{yao2023react}, as opposed to native function-calling capability of our implementation. 

In Table~\ref{tab:osf_results}, we present a comparative analysis with the OSF. Due to the prompting style of the agents in the OSF, they tend to be highly verbose and utilize a much higher number of tokens. To constrain the experiment to a reasonable budget, we employ Claude 3.5 Sonnet (20240620) as the supervisor agent and Claude 3.0 Sonnet as the specialist agents. Since the original prompts in the OSF may have been optimized for GPT-4o (mini), as suggested by the defaults in the code implementation, we also report the performance of GPT-4o (mini) with the OSF in the conversational setting.