% \subsection{Structure-Guided Hyperedge Retrieval}

We introduce a hyperedge retrieval module that combines semantic matching with structural signals derived from the hypergraph.
The goal is to refine the retrieval process by favoring hyperedges whose entities are both relevant to the current query and structurally distinctive in the knowledge hypergraph.
Compared with prior retrieval schemes that primarily rely on semantic alignment between the query and candidate entities or hyperedges, our method re-scores candidate hyperedges using entity-level structural statistics computed from the hypergraph. 
This design encourages retrieval trajectories that are more compatible with the underlying hypergraph structure, while remaining grounded in semantic relevance.

% Let $\mathcal{H}=(V,E)$ denote the knowledge hypergraph, where $V$ is the set of entities and $E$ is the set of hyperedges.
At reasoning step $t$, the agent generates a query $\mathbf{q}_t$ for the retrieval.
We first extract the set of query entities, denoted by $\mathcal{V}(\mathbf{q}_t)$, and retrieve candidate hyperedges based on both semantic relevance and structural distinctiveness.

\paragraph{Entity-query semantic relevance.}
We measures how well each entity $v \in V$ semantically aligns with the current query $\boldsymbol{q}_t$, which is computed as:
\begin{equation}
    s_t\left(v\right) = \mathrm{sim}\!\left(\phi(v), \phi \left(\mathcal{V}\left(\mathbf{q}_t\right)\right)\right), \qquad \forall v \in V,
\end{equation}
where $\phi(v)$ denotes the embedding of entity $v$, and
\begin{equation}
    \phi\left(\mathcal{V}\left(\mathbf{q}_t\right)\right) = \frac{1}{\left\lvert \mathcal{V}\left(\mathbf{q}_t \right)\right\rvert} \sum_{u \in \mathcal{V}\left(\mathbf{q}_t \right)} \phi \left(u \right)
\end{equation}
is the aggregated embedding of the entities mentioned in the query.
The score $s_t(v)$ captures the semantic compatibility between entity $v$ and the current required information.

\paragraph{Structure-guided entity distinctiveness.}
Semantic similarity alone is often insufficient in hypergraphs, because highly frequent entities may receive large similarity scores even when they provide limited discriminative value for multi-hop retrieval.
To address this issue, we introduce an entity distinctiveness term that reflects how selectively an entity appears in hyperedges connected to the current query $\boldsymbol{q}_t$.

Assume that
\begin{equation}
    E(\mathbf{q}_t) = \{ e \in E \mid V_e \cap V(\mathbf{q}_t) \neq \emptyset \}
\end{equation}
is the set of hyperedges incident to at least one query entity, where $V_e$ denotes the entity set of hyperedge $e$.
For each entity $v \in V$, we define its query-conditioned distinctiveness as
\begin{equation}
    I_t(v) = \log \left(
    1 +
    \frac{\left|\{ e \in E(\mathbf{q}_t) \mid v \in V_e \}\right|}
         {\left|\{ e \in E \mid v \in V_e \}\right|}
    \right).
\end{equation}
This quantity becomes larger when $v$ appears relatively often in hyperedges related to the current query, but not ubiquitously throughout the entire hypergraph.
In this sense, $I_t(v)$ acts as a query-conditioned structural prior that downweights overly common entities and amplifies entities that are more informative for the current retrieval context.

\paragraph{Hyperedge re-scoring.}
Given a candidate hyperedge $e \in E$, we first normalize the semantic relevance of each entity within the hyperedge:
\begin{equation}
    \tilde{s}_t(v,e) =
    \frac{s_t(v)}{\sum_{u \in V_e} s_t(u)}, \qquad v \in V_e.
\end{equation}
This normalization reflects the relative semantic contribution of entity $v$ within hyperedge $e$, rather than using its global relevance score in isolation.

We then combine semantic relevance and structural distinctiveness to obtain the entity contribution score
\begin{equation}
    r_t(v,e) = \tilde{s}_t(v,e)\cdot I_t(v),
\end{equation}
and define the overall score of hyperedge $e$ as
\begin{equation}
    R_t(e) = \sum_{v \in V_e} r_t(v,e).
\end{equation}

Finally, we rank all candidate hyperedges by $R_t(e)$ and select the top-$k$ hyperedges:
\begin{equation}
    \mathcal{E}_t^{\mathrm{ret}} = \operatorname{TopK}_{e \in E}\, R_t(e).
\end{equation}
The retrieved fact set is then given by
\begin{equation}
    \mathcal{F}_t^{\mathrm{ret}}
    =
    \bigcup_{e \in \mathcal{E}_t^{\mathrm{ret}}}
    \{(e, V_e)\}.
\end{equation}
