\section{Related Work}
\label{sec:related}
% Our work on multi-agent confidence calibration is situated at the intersection of two rapidly developing research areas: uncertainty quantification (UQ) for LLM-based agents and confidence calibration for LLMs.


% \paragraph{Multi-agent LLM systems and correlated errors.}
% \textbf{(why the need the calibation for mulati agent system)}
% Composing LLMs into multi-agent systems has improved factuality, reasoning, and code synthesis~\citep{du2023improvingfactualityreasoninglanguage,hong2024metagptmetaprogrammingmultiagent,wu2023autogenenablingnextgenllm}. 
% These gains are often attributed to diversity among agents, but this diversity is limited when agents share training data, model families, alignment procedures, or prompting patterns. 
% Recent work shows that LLM errors can be correlated across models~\citep{estornell2026multillmdebate}, especially within the same model family~\citep{kim2025correlatederrorslargelanguage}, and that consensus is not always reliable evidence when agents share failure modes~\citep{denisovblanch2026consensusverificationcrowdwisdom}. 
% We build on this observation and ask how multi-agent confidence should be calibrated when failures are correlated by design. 
% Our answer is to model the dependency structure among agents directly, rather than treating agreement as independent evidence.

\paragraph{Multi-Agent Uncertainty Quantification.}
Existing uncertainty estimators for LLM panels often summarize the answer distribution with a scalar score~\citep{wang2023selfconsistencyimproveschainthought,kadavath2022languagemodelsmostlyknow,feng2025rethinkingllmuncertaintymultiagent,chen2026responsecountsquantifyinguncertainty,jiang2026discouq}.  
For example, DiscoUQ-LLM~\cite{jiang2026discouq} learns from disagreement features, while MATU~\cite{chen2026responsecountsquantifyinguncertainty} models uncertainty through tensor decomposition over multi-agent rollouts~\citep{jiang2026discouq, chen2026responsecountsquantifyinguncertainty}. These methods are useful when disagreement reflects uncertainty. 
However, disagreement can be misleading: benign diversity may cause under-confidence, while communication-induced agreement may cause over-confidence. \methodname{}  therefore conditions confidence on agent dependencies rather than disagreement alone.
% Vote share underlies majority voting and self-consistency~\citep{wang2023selfconsistencyimproveschainthought}. 
% Mean log-probability extends single-model confidence estimation to the panel setting~\citep{kadavath2022languagemodelsmostlyknow}. 
% Entropy-based methods, such as DiverseAgentEntropy~\citep{feng2025rethinkingllmuncertaintymultiagent}, use disagreement among agents as a black-box uncertainty signal. 





% However, our results show that this assumption can fail in two directions: benign diversity can make a reliable panel look uncertain, while communication can make an unreliable panel look confident. 
% CAGE-CAL therefore conditions confidence on the dependency structure that produced the disagreement, rather than on the disagreement level alone.

\paragraph{Multi-Agent Confidence Calibration.}

% such as Platt scaling~\cite{platt1999probabilistic}, isotonic regression~\cite{zadrozny2002transforming}  scaling-binning~\cite{kumar2019verified} 

% Confidence calibration aims to align a model's predicted probability with the true likelihood of correctness.

Existing work can be broadly grouped into three lines. The first line, \textit{Post-hoc plurality calibrators}~\cite{zhang2026agentic}, calibrates scalar uncertainty signals, such as vote share or entropy, using post-hoc methods~\cite{platt1999probabilistic,zadrozny2002transforming,kumar2019verified}.
% The first line, \textit{post-hoc scalar calibration}~\cite{zhang2026agentic}, applies post-hoc methods\cite{platt1999probabilistic,zadrozny2002transforming,kumar2019verified} such as scaling-binning~\cite{kumar2019verified} to scalar uncertainty scores such as vote share and entropy,
% but has been mainly studied in single-agent settings.
%%
The second line studies \textit{LLM-elicited confidence estimators}~\cite{lin2022teaching,yang2024confidence}, where LLMs are trained or prompted to report calibrated confidence. For example, LLM-Cal~\cite{lin2022teaching} fine-tunes an LLM to align verbalized confidence with empirical correctness. 
The third line develops \textit{trained calibrators}~\cite{li2025graph,jiang2026discouq,zhu2026demystifying}, which estimate final-answer correctness from confidence and disagreement features. For example, DiscoUQ-LLM~\cite{jiang2026discouq} uses logistic regression over vote confidence and hand-crafted disagreement features. 
Despite their effectiveness, these methods largely overlook communication-induced dependencies, heterogeneous LLM panels, and diverse communication topologies.





%SCollaborative
% Calibration (Collab Cal)~\cite{yang2024confidence} further performs post-hoc, training-free calibration by using multiple tool-augmented LLM agents to generate answers, verbalized confidence, and feedback through a simulated group deliberation process.
% However, these methods primarily rely on verbalized uncertainty or deliberative feedback, and do not explicitly model how communication topology induces dependencies among agents.
%%