\begin{abstract}

% 我们的方法怎么更好的用了外部的知识。为什么。

%  前面的废话太多
% Large Language Models (LLMs) have shown impressive performance across a variety of tasks, but remain vulnerable to hallucinations and factual errors, particularly in knowledge-intensive scenarios. Incorporating external knowledge from Knowledge Graphs (KGs) has proven effective for enhancing factual reasoning. However, most existing LLM-based KG reasoning methods assume complete KGs, which rarely holds in practice. 
% % 到这里才提出来，
% In real-world settings, missing triples or entities can severely disrupt the reasoning process. 
% % 上一句接下来说一下当下方法的问题 GOG
% % 技术方案不够具体，方案和如何解决确实问题有何联系
% % KG 本来就是用来增强 LLM 的，再用 LLM 来增强 KG 就不是那么合理了
% To tackle this challenge, we propose Debate over Mixed-knowledge (DoM), a Multi-Agent Debate (MAD) framework for question answering under Incomplete Knowledge Graphs (IKGQA). DoM integrates structured information from incomplete KGs with unstructured external text, leveraging a coordinated set of agents to decompose questions, retrieve complementary knowledge, and verify intermediate answers through debate. 
% % 为了更好的模拟正式场景下的 IKGQA，相比于之前的数据集的问题。我们为此构建了这样的数据集
% We further construct a new benchmark dataset, Incomplete Knowledge Graph WebQuestions (IKGWQ), by rebuilding QA pairs from CWQ and WebQSP using up-to-date external knowledge, introducing realistic missing triples and entities. Experiments on three datasets show that DoM consistently outperforms competitive baselines, achieving up to 13.6\% improvement on existing IKGQA benchmarks and 70.7\% relative gain on IKGWQ.



% Retrieval-Augmented Generation

Knowledge Graph Question Answering (KGQA) aims to improve factual accuracy by leveraging structured knowledge. However, real-world Knowledge Graphs (KGs) are often incomplete, leading to the problem of Incomplete KGQA (IKGQA). A common solution is to incorporate external data to fill knowledge gaps, but existing methods lack the capacity to adaptively and contextually fuse multiple sources, failing to fully exploit their complementary strengths.
To this end, we propose Debate over Mixed-knowledge (DoM), a novel framework that enables dynamic integration of structured and unstructured knowledge for IKGQA. Built upon the Multi-Agent Debate paradigm, DoM assigns specialized agents to perform inference over knowledge graphs and external texts separately, and coordinates their outputs through iterative interaction. It decomposes the input question into sub-questions, retrieves evidence via dual agents (KG and Retrieval-Augmented Generation, RAG), and employs a judge agent to evaluate and aggregate intermediate answers. This collaboration exploits knowledge complementarity and enhances robustness to KG incompleteness.
In addition, existing IKGQA datasets simulate incompleteness by randomly removing triples, failing to capture the irregular and unpredictable nature of real-world knowledge incompleteness. To address this, we introduce a new dataset, Incomplete Knowledge Graph WebQuestions, constructed by leveraging real-world knowledge updates. These updates reflect knowledge beyond the static scope of KGs, yielding a more realistic and challenging benchmark. Through extensive experiments, we show that DoM consistently outperforms state-of-the-art baselines.
\end{abstract}

% \begin{links}
%     \link{Code and Datasets}{github.com/liujilong0116/DoM}
    % \link{Extended version}{arxiv.com/xxxx/xxx}
% \end{links}

