\section{Appendix}

\subsection{A. Algorithm of DoM}
\input{algorithms/overview}



\subsection{B. Baseline Introduction}

\subsubsection{Prompt-based LLM Methods} \

\textbf{IO Prompt}~\cite{brown2020language}: Directly prompts the LLM to generate answers in a single step without step-by-step inference. We follow the code released by ToG~\cite{sun2023think}.

\textbf{CoT Prompt}~\cite{wei2022chain}: Enhances IO prompting with chain-of-thought reasoning before producing the final answer. We follow the code released by ToG~\cite{sun2023think}.

\subsubsection{Fine-tuned LLM-based Methods} \
~\input{figures/figure_3}

\textbf{ChatKBQA}~\cite{luo2024chatkbqa}: A semantic parsing-based KGQA model that fine-tunes an LLM to generate SPARQL queries from natural language questions. We directly use the evaluation results provided in GoG~\cite{xu2024generate}.

\textbf{RoG}~\cite{luo2024reasoning}: A retrieval-guided method that fine-tunes LLMs to perform step-by-step inference along pre-retrieved KG paths, aligning outputs with KG structure to improve factual accuracy. We directly use the evaluation results provided in GoG~\cite{xu2024generate}.

\subsubsection{Retrieval-Augmented Inference Frameworks} \

% \textbf{ToG}~\cite{sun2023think}: A training-free reasoning framework where LLMs act as agents to iteratively explore knowledge graphs through beam search. It supports multi-hop path-based inference with explicit reasoning traces, enables knowledge traceability and correction via external feedback, and is compatible with different LLMs and KGs without additional training cost.

\textbf{ToG}~\cite{sun2023think}: A training-free method using LLMs to perform multi-hop inference over KGs via beam search, with support for explicit path tracing and correction.

% \textbf{PoG}~\cite{tan2025paths}: A retrieval-augmented reasoning method that addresses multi-hop and multi-entity KGQA through dynamic path exploration. It improves reasoning faithfulness by pruning irrelevant paths using a three-stage strategy combining graph structure, LLM prompts, and pretrained encoders.

\textbf{PoG}~\cite{tan2025paths}: A retrieval-augmented method for multi-hop and multi-entity KGQA that improves faithfulness by dynamically pruning irrelevant paths using graph structure, LLM prompts, and pretrained encoders.

% \textbf{GoG}~\cite{xu2024generate}: A training-free approach designed for IKGQA. It integrates LLM internal knowledge with retrieved KG context by generating missing triples through a thinking-searching-generating framework, enhancing reasoning robustness in incomplete settings.

\textbf{GoG}~\cite{xu2024generate}: A training-free IKGQA method that enhances answer generation by inferring missing triples via a thinking-searching-generating framework combining KG context and LLM knowledge.

% 需要精简
\subsection{C. Comparison between DoM and GoG under GPT-series models}

\input{tables/gpt_4o_result}

Table~\ref{table:gpt_4o_result} presents a detailed comparison between DoM and GoG across three backbone models: DeepSeek-v3, GPT-3.5, and GPT-4o, evaluated on IKGWQ, CWQ (IKG-40\%), and WebQSP (IKG-40\%). From the results, we observe that DoM consistently achieves the best performance across all backbone models. Both GPT-4o and DeepSeek-v3 outperform GPT-3.5 across datasets, indicating their stronger reasoning capacity and knowledge coverage. However, an intriguing observation is that on the IKGWQ dataset, GPT-4o underperforms DeepSeek-v3 under both GoG and DoM frameworks, despite showing superior performance on CWQ and WebQSP. 

We attribute this phenomenon to the nature of IKGWQ, which is designed to reflect more realistic and challenging IKG scenarios. Unlike CWQ and WebQSP, which simulate KG incompleteness through predefined deletions that result in more predictable missing facts, IKGWQ introduces more diverse and up-to-date facts that are not aligned with existing KG structures, leading to higher uncertainty and more complex inference demands. 


While GPT-4o possesses powerful parametric knowledge, its strong generative capacity can sometimes introduce greater autonomy in reasoning trajectories, which may hinder performance in modular pipelines like GoG and DoM that rely on strict agent coordination and predictable intermediate steps. This issue is particularly evident in IKGWQ, where KG incompleteness is more complex and unpredictable, requiring consistent multi-turn interaction between agents. In contrast, CWQ and WebQSP adopt more patternized and constrained forms of incompleteness, where the inference paths tend to follow simpler and more regular structures. In such cases, GPT-4o's capabilities can be more effectively harnessed, leading to better performance. Meanwhile, DeepSeek-v3, though potentially less capable in terms of knowledge coverage, exhibits stronger consistency and alignment with structured multi-step inference workflows, making it more robust in IKGWQ.

% \subsection{D. Case Study}

\subsection{D. Manual Analysis}
\input{figures/manual_analysis}


To examine how DoM leverages both structured and unstructured knowledge sources, we manually analyzed correctly answered samples from CWQ and WebQSP under the IKG-40\% setting. As shown in Figure~\ref{fig:manual_analysis}, a small portion of correct answers were derived from the LLM’s internal knowledge when neither the KG nor external data provided sufficient evidence. Most correct predictions, however, involved complementary evidence from both the KG and RAG agents, highlighting the value of dual-path retrieval. Through the Multi-Agent Debate (MAD) paradigm, our method enables interactive inference across heterogeneous knowledge sources, allowing agents to compensate for each other’s limitations. 

To further illustrate how multi-agent debate enables complementary inference under KG incompleteness, we present a representative example from the IKGWQ dataset (Figure~\ref{fig:case_study}). The question is: \emph{Which film featuring Armie Hammer was selected for preservation in the National Film Registry?}

In this example, the critical triple \emph{(The Social Network, film\_registry\_preservation.film, National Film Registry)} is missing from the KG. During the first iteration, the KG Agent successfully identifies \emph{The Social Network} as a relevant film based on structured KG facts, while the RAG Agent fails to retrieve useful evidence from external data. In the second iteration, the KG Agent can no longer offer useful knowledge due to the missing triple, but the RAG Agent locates supporting information in retrieved text. Through iterative inference and integration by the Judge Agent, the system ultimately arrives at the correct answer.

This case highlights how DoM enables complementary inference across structured and unstructured knowledge. When one agent is hindered by missing information, the other compensates, enabling robust inference for IKGQA.