\section{Preliminaries}
\label{preliminaries}

% \subsection{Knowledge Graphs}


% A graph can be denoted as $\mathcal{G} = (\mathcal{V}, \mathcal{E})$ where $\mathcal{V}$ and $\mathcal{E}$ are the vertex set and the edge set respectively. Each $v_i$ $\in$ $\mathcal{V}$ can be associated with some feature information $\mathcal{X}_{v_i}$. For example, in an academic biology graph, $v_i \in \mathcal{V}$ are papers with features $x_i \in \mathcal{X}_{v_i}$ such as author, or publication venue, and $e_i \in \mathcal{E}$ represents papers that share 

% \subsection{\textcolor{blue}{Retrieval Augmented Generation (RAG)}}

% LLMs exhibit strong generative capabilities, but struggle with reasoning over factual knowledge, particularly in specialized domains such as scientific question answering. {\bf Retrieval Augmented Generation (RAG)} addresses this limitation by incorporating external retrieval mechanisms into the generation process. Instead of relying solely on parametric memory, RAG retrieves relevant information from an external knowledge source. Traditional RAG systems typically retrieve knowledge units based on semantic similarity using dense embeddings. This approach lacks structured reasoning capabilities and struggles with multi-hop reasoning with related facts or when the required information is dispersed throughout the knowledge base. {\bf GraphRAG} extends RAG by integrating {\bf knowledge graphs} as the retrieval backbone, leveraging their explicit relational structure to improve performance. 

% \subsection{Inference Time Scaling}


% Previous efforts to improve model performance have primarily focused on scaling up pretraining. However, recent studies, inspired by the success of reasoning models such as OpenAI-o1 and Deepseek r1, have demonstrated that performance can also be improved through {\bf inference-time scaling}. Two prominent paradigms for inference-time scaling have emerged: {\bf sequential scaling} and {\bf parallel scaling}.  

% {\bf Sequential scaling} conditions the model’s current computation on previous ones, often through a structured reasoning process, such as a long chain of thought. {\bf Parallel scaling} generates multiple responses in parallel and selects the most suitable one based on a predefined criterion (e.g. majority voting or best-of-N)
\subsection{Knowledge graphs}

We denote a knowledge graph as \( G = (V, E) \), where \( V \) is the set of nodes (entities) and \( E \) the set of edges (relations). Each node \( v_i \in V \) is associated with feature information \( X_{v_i} \), that may include textual content or metadata. For instance, in an academic domain-specific graph, nodes might represent research papers, with features including authorship, publication venue, or abstract text, while edges capture relationships such as co-authorship or citation links.

\subsection{Retrieval-augmented generation (RAG)}

Large Language Models (LLMs) demonstrate strong generative capabilities but often struggle with reasoning over factual knowledge, especially in specialized domains. Retrieval Augmented Generation (RAG) \citep{lewis2020retrieval} addresses this limitation by incorporating external information retrieval into the generation pipeline. Rather than relying solely on parametric memory, RAG retrieves relevant documents from an external knowledge source and conditions the model’s generation on this context.

RAG implementations typically use dense vector similarity \citep{fan2024surveyragmeetingllms, devlin-etal-2019-bert} to retrieve semantically related documents. While this is effective for recalling isolated facts, it struggles with structured or multi-hop reasoning, particularly when relevant information is distributed across multiple sources \citep{tang2024multihoprag}. GraphRAG \citep{edge2025localglobalgraphrag} extends RAG by using a knowledge graph as the retrieval backbone, allowing the model to leverage the explicit relational structure among entities to guide retrieval and enhance coherence in reasoning.

\subsection{Inference-time scaling}

Traditionally, model performance improvements have been achieved by scaling pretraining \citep{10.5555/3495724.3495883, hoffmann2022trainingcomputeoptimallargelanguage}. Recent studies have shown that allocating additional compute at test time \citep{uesato2022solvingmathwordproblems, 10.5555/3600270.3600548} can significantly improve performance on complex reasoning tasks. Inference-time scaling provides an orthogonal axis for performance improvement without modifying the model architecture.

Two primary paradigms of inference scaling are employed:

\begin{itemize}
    \item \textbf{Sequential Scaling:} The model performs step by step reasoning, with each inference step conditioned on the outputs from previous steps \citep{muennighoff2025s1simpletesttimescaling}. This enables the accumulation of intermediate insights, supporting deeper reasoning and iterative refinement.   

    \item \textbf{Parallel Scaling:} Multiple responses are generated independently \citep{brown2024largelanguagemonkeysscaling} in parallel, and a final output is selected using aggregation strategies such as majority voting or best-of-N. This method improves robustness and mitigates single-sample errors.
\end{itemize}

Our proposed method incorporates both sequential and parallel scaling into the GraphRAG framework, enabling large language models to perform efficient and effective multi-hop reasoning over structured knowledge graphs.
