% \section{Related work}

% \paragraph{Knowledge Graphs and GraphRAG.}
% Knowledge graphs represent entities and their relationships in a structured format, supporting logical reasoning and multi-hop inference. GraphRAG \citep{edge2025localglobalgraphrag} integrates knowledge graphs into the RAG framework by enabling retrieval based on graph structure rather than unstructured text. Recent works have explored using Graph Neural Networks (GNNs) as more sophisticated retrievers \citep{peng2024graphretrievalaugmentedgenerationsurvey}, and enabling LLMs to interact with these GNNs. \citep{9046288}.

% \paragraph{Chain-of-Thought and Inference Scaling.}
% Inference scaling allows LLMs to perform more effective reasoning by allocating more compute at test time. Researchers have shown that LLMs can learn to allocate more compute at test time through reinforcement learning on verifiable outcomes \citep{lambert2025tulu3pushingfrontiers}. Researchers have also explored utilizing more sophisticated parallel sampling strategies for LLMs such as Monte-Carlo Tree Search. 

% \paragraph{LLM-based Graph Traversal.}
% Recent efforts such as GraphCoT \citep{jin2024graph, jin2024largelanguagemodelsgraphs, he2024gretrieverretrievalaugmentedgenerationtextual} explore how LLMs can interact with knowledge graphs using iterative reasoning and function-based graph APIs. These methods show promise but have yet to incorporate inference-time scaling. Our work extends this line of research by combining structured traversal with inference-time compute allocation for improved accuracy and scalability.


\section{Related Work}

\paragraph{Knowledge Graphs and GraphRAG.}
Knowledge graphs represent entities and their relationships in a structured format, supporting logical reasoning and multi-hop inference. GraphRAG \citep{edge2025localglobalgraphrag} integrates knowledge graphs into the RAG framework by enabling retrieval based on graph structure rather than unstructured text. Recent works have explored using Graph Neural Networks (GNNs) as more sophisticated retrievers \citep{peng2024graphretrievalaugmentedgenerationsurvey, zhang2025surveygraphretrievalaugmentedgeneration}, and enabling LLMs to interact with these GNNs \citep{9046288, wu2025inference}. In addition, works like \citep{he2024gretrieverretrievalaugmentedgenerationtextual} explore methods for incorporating relational structure into retrieval pipelines. Other approaches focus on learning graph node embeddings to enhance retrieval fidelity \citep{devlin-etal-2019-bert}. ToolQA \citep{zhuang2023toolqa} demonstrates the effectiveness of structured tool interfaces, an idea conceptually aligned with function-based graph interaction. Despite these advancements, GraphRAG systems often struggle with the scalability of multi-hop traversal, motivating methods like our own.

\paragraph{Chain-of-Thought and Inference Scaling.}
Inference scaling allows LLMs to perform more effective reasoning by allocating more compute at test time. Researchers have shown that LLMs can learn to allocate more compute through reinforcement learning on verifiable outcomes \citep{lambert2025tulu3pushingfrontiers}. Techniques such as self-consistency \citep{wang2023selfconsistency}, Best-of-N sampling \citep{jinnai2025regularizedbestofnsamplingminimum}, and Tree-of-Thoughts \citep{yao2023tree} improve reasoning robustness and diversity. Recent frameworks like OpenAI o1 \citep{openai2024o1} and DeepSeek R1 \citep{deepseekai2025deepseekr1incentivizingreasoningcapability} demonstrate that test-time scaling can significantly enhance LLM capabilities without altering model weights. The use of budget forcing and controllable compute \citep{muennighoff2025s1simpletesttimescaling} has made it easier to balance cost-performance tradeoffs. Furthermore, Monte Carlo Tree Search strategies \citep{zhang2024rest} offer a path for combining structured planning with sampling-based scaling. Reinforcement learning techniques \citep{gulcehre2023reinforcedselftrainingrestlanguage} show potential for optimizing reasoning strategies in procedural tasks. Scaling laws for inference \citep{wu2025inference} provide theoretical support for compute-efficient design. These inference scaling techniques, while originally designed for symbolic or open-ended tasks, align naturally with the demands of structured graph traversal and motivate our framework’s design.

\paragraph{LLM-based Graph Traversal.}
Recent efforts such as GraphCoT \citep{jin2024graph} explore how LLMs can interact with knowledge graphs using iterative reasoning and function-based graph APIs \citep{jin2024largelanguagemodelsgraphs}. G-Retriever \citep{he2024gretrieverretrievalaugmentedgenerationtextual} focuses on the textual grounding of graph reasoning. Tool-use datasets such as ToolQA \citep{zhuang2023toolqa} and function-agent frameworks \citep{xi2023risepotentiallargelanguage} extend these capabilities to more general interaction settings. In-context learning strategies \citep{dong2024surveyincontextlearning} remain the dominant mechanism for teaching LLMs how to traverse structured environments. However, these methods struggle to generalize to unseen graph topologies. Techniques that enable self-reflection and correction \citep{uesato2022solvingmathwordproblems, 10.5555/3600270.3602070} can aid traversal fidelity. Our work extends this line by explicitly scaling inference compute and structuring the traversal process into reasoning-action-execution loops, allowing for deeper and more accurate reasoning across graph structures.
