\section{Dataset Details}
\label{appendix_dataset_detail}

The eight datasets used in our experiments are classic datasets that are widely employed to evaluate the performance of agent-based methods. Here, we provide an introduction to the eight datasets used in our experiments.

\textbf{GSM-IC.}  It is a grade-school math problem dataset derived from GSM8K ~\citep{cobbe2021training}.  For each problem in GSM8K, GSM-IC keeps the base problem description and adds to it one irrelevant sentence that does not affect the solution of the problem.

\textbf{MATH.} It is a math dataset containing challenging competition mathematics problems. Each of them has a full step-by-step solution.

\textbf{MMLU.} It contains 57 types of multiple-choice problems, such as elementary mathematics, US history, computer science, and so on. To acquire high performance on the MMLU datasset, models must possess extensive world knowledge and strong problem-solving ability.

\textbf{MMLU-pro.} It contains questions sourced from multiple origins, such as MMLU, TheoremQA, and SciBench. Moreover, it expands the option number of each problem from 4 to 10.

\textbf{GPQA.} It contains 448 graduate-level question-answering problems, covering knowledge in various fields such as biology, physics, and chemistry.

\textbf{ARC-C.} It contains complex questions on natural science, presented in the form of multiple-choice options.

\renewcommand{\dblfloatpagefraction}{.9}
\input{table/table_appendix_experiments}
\input{table/appendix_table_additional_token}

\textbf{LongBench.} It is a dataset designed to evaluate the long-context understanding capabilities of models. It encompasses six major categories of tasks, including single-document QA, multi-document QA, summarization, few-shot learning, code completion, and synthetic tasks.

\textbf{SQuAD.} It is a dataset used to evaluate the reading comprehension ability of models. The dataset requires models to answer different questions from given long texts.