%!TEX root = main.tex
\IEEEPARstart{T}{he} millimeter-wave (mmWave) bands have been considered by the 3rd Generation Partnership Project (3GPP) as one of the main reliefs to the explosive increase of the global mobile traffic, which is now posing big challenges to the access capacity provided by sub-6GHz communications.
Large bandwidths (several hundreds of MHz) and mainly-underutilized spectrum portions available at those high frequencies are the key enablers of a Gbps access throughput.
However, this potential comes at a cost of facing a harsh propagation environment characterized by very high path losses and weak, or even null, propagation through obstacles, including not only static buildings but also moving vehicles and pedestrians. While current antenna design technologies have shown to be effective in mitigating path losses through extremely directional arrays, there is very little they can do against random obstacle blockages. In practice, mmWave networks typically exhibit a coverage-limited behavior due to the presence of obstacles. Therefore, to guarantee a high-quality coverage, 5G mmWave access networks require base stations to be much more densely deployed than in traditional radio access networks. This may translate into high installation budgets for operators, which are mainly driven by costs to deploy wired (e.g., fiber) backhaul connections.

Aiming to provide a dense network deployment at minimal costs, 3GPP specifications have introduced in release 16 a new multi-hop wireless access architecture, named Integrated Access and Backhaul (IAB)\cite{3gpp15study}. The rationale is to place relay nodes, called IAB-nodes, in the service area of a mmWave base station (BS), called IAB-donor, and form a wireless multi-hop backhaul to forward data packets between the IAB-donor and user equipments (UEs). An example of such an IAB network scenario can be found in Fig.~\ref{fig:scenario}.
In recent years, regardless of technical challenges potentially posed, full-duplex IAB networks have been proposed in many works \cite{9770117,9363025} as a promising architecture for 5G NR paradigm\footnote{\begin{changed}3GPP has included the support for IAB simultaneous transmission and reception in Release 17 (3GPP TS 38.174 version 17.0.0 Release 17).\end{changed}}, which can considerably improve the spectral efficiency, compared with the commonly adopted half-duplex ones.
Self-backhauling is a peculiar aspect of IAB networks, where both radio access and backhaul links share the same radio resources and interfaces. Therefore, a proper radio resource allocation is essential to efficiently operate this network. In particular, since the adopted multiple access scheme is based on time-division multiple access (TDMA), the resource optimization must deal with routing paths and scheduling of directional transmissions along established links.


Studies on (joint) routing and scheduling in wireless multi-hop networks have appeared in the literature since early 2000s. It has been considered as a hard problem due to interference constraints and mainly solved resorting to optimization techniques that assume always-available links and static users \cite{yuan2018optimal}.
However, it is hard for these techniques to provide real-time solutions for dynamic mobile mmWave IAB networks.
Indeed, the optimal solution derived under ideal link conditions remarkably underperforms when facing the stochastic on-off link behavior caused by mobile users and the varying signal attenuation due to mobile obstacles.
In several cases, random link conditions can even eliminate all the advantages of a careful optimization.
The network could, in principle, be re-optimized periodically or every time it undergoes a change. However, it can induce huge computational costs and, most likely, not be practical, because a non-negligible amount of time is usually required to provide an optimal solution for a single network snapshot.
Therefore, flexible and adaptive solutions are required.

Given the above context, Reinforcement Learning (RL) techniques can play an important role thanks to their intrinsic adaptability to the environment behavior.
Indeed, an RL agent can automatically grasp relevant environment statistics by playing against the environment and eventually discover a strategy that can provide the best long-term reward.
However, several challenges need to be overcome if it is adopted.
First, access links are intermittently available due to UE mobility, which makes centralized single-agent RL (SARL) approaches infeasible. Indeed, their decision space is based on a set of potential concurrent transmissions (i.e., compatible links), which unfortunately changes as users randomly move around.
Second, randomly moving obstacles can dynamically cause different degrees of link attenuation, whose statistics must be learned.
Based on the above observations, random mobility patterns characterizing both UEs and obstacles typically generate local areas with local statistics that may vary across different network areas. To leverage such a scattered structure of the problem, multi-agent RL (MARL) techniques can be used to exploit multiple RL agents able to both make decisions based on local observations and coordinate with the other agents. This allows to split a single, complex, and high-dimensional problem -- which would otherwise be intractable -- into several, cooperative, and low-dimensional tasks.

In this article, we address the joint flow routing and link scheduling problem in mmWave IAB networks, coordinating both access and backhaul transmissions to maximize the downlink throughput perceived by UEs.
We provide an adaptive MARL-based framework that supports real-time operations and takes into account (1) physical constraints, including link interference, duplexing modes (i.e., full-duplex, half-duplex), hardware limitations, etc., (2) the amount of data cached in IAB-nodes' buffers, to avoid multi-hop flow starvation, (3) randomly moving 3D blocking obstacles, to reduce stochastic signal attenuation of mmWave communications to the full extent, and (4) randomly moving UEs, to dynamically adapt to changing access layouts.

Our contributions are summarized as follows:
\begin{itemize}
    \item By harnessing the distributed nature of the issue, we introduce an approach based on MARL that partitions a significantly intricate combinatorial resource allocation problem into numerous smaller tasks overseen by collaborative agents. This facilitates real-time execution of resource allocation operations that adjust to network conditions.
	\item The proposed approach can coordinate the interference among concurrent backhaul and access links, promptly monitor and refill IAB-node buffers to prevent downstream access transmission starvation, adjust transmission beams to serve mobile UEs, and adapt to intermittent blockages caused by randomly moving 3D obstacles.
	\item We develop distinct versions of our approach tailored for scenarios where all IAB-nodes operate either in full duplex (FD) or half duplex (HD) mode.
        \item We propose an online training framework that considers system-level aspects, particularly the challenges related to message exchange and coordination encountered in its practical application to mmWave IAB networks.
        \item We conduct extensive numerical experiments to evaluate the performance of the proposed approach and demonstrate how it can outperform the baselines.
\end{itemize}

