\section{Safety and Security}  
The interaction between agents during collaboration requires extensive information sharing to provide sufficient context for solving tasks. These conversations are facilitated by protocols specifically designed for multi-agent communication. However, the method, volume, and nature of information exchange introduce new challenges related to security, privacy, and system robustness.

The modular and flexible design of \sys enables systematic exploration of these challenges. Its configurability allows us to easily construct attack scenarios, while its modularity supports the creation of adversarial agents with diverse capabilities across different environments. Furthermore, its observability enables implementing and measuring Attack Success Rate (ASR) metrics.

% \subsection{Alignment}

\subsection{Unsafe and Insecure Characteristics}

A successful multi-agent design requires system and collaboration strategies with characteristics unique to a MAS, which adversaries can exploit to construct a range of attacks. Such attacks, leveraging these and other MAS-specific features, may have catastrophic effects on the system as the compromise propagates through multiple interactions. 

\pbe{Agent actions can serve secondary objectives.} 
In a collaborative environment, agents typically assume that the actions of others are intended to optimize the global objective. However, verifying that an agent’s actions are not instead serving a secondary, unintentional or adversarial, objective may not be feasible. This creates unique challenges, as a large number of potential secondary objectives can be pursued through actions that still appear valid. The ulterior motive can range from targeting a specific goal or agent to misaligning and affecting the performance of the entire system.

\pbe{Extended agentic capabilities.} 
To take actions and retrieve necessary information, agents must rely on external tools, extending their capabilities. These tools can be leveraged for both active attacks, where the adversary modifies the interaction to carry out the attack, and passive attacks, where the adversary observes the interaction to infer information. While multi-agent poisoning has been studied in limited contexts, such as poisoning via web-retrieved content~\citep{lee2024prompt}, the growing scale and complexity of MAS systems—and their increasing reliance on heterogeneous tool sets—introduce novel challenges.

\pbe{Communication protocol vulnerabilities.}
MASs are dependent on communication protocols for effective collaboration. These underlying protocols connect agents to one another and, in many cases, to central platforms that coordinate their interactions~\citep{dang2025multi, bhatt2025should}. As these protocols rapidly evolve and form the core of modern MASs, it becomes essential to study the novel attack vectors that emerge from their integration.

\subsection{Exploring Attack Vectors}

The characteristics specified in the previous section motivate us to explore novel attack vectors to test the Confidentiality, Integrity and Availability (CIA) of MASs. We use these attack vectors to understand the security and privacy implications of MASs and to motivate future research. 


\pbe{Confidentiality. Can agents keep a secret?}
To evaluate confidentiality, we examine whether agents preserve private information communicated by a previous agent when interacting with a subsequent one. In this setup, the second agent is instructed to elicit the personal information shared earlier, while the queried agent receives a system prompt explicitly stating that it should not reveal private information about any other agent. Our findings show that the \textit{agent nevertheless discloses the information, despite being prompted not to}.

\pbe{Integrity. What actions lead to misalignment?}
To evaluate integrity, we examine misalignment by determining which actions, and the minimum number of actions, must be altered by an adversary during collaboration. We investigate two scenarios: an adversarial agent part of the collaboration and an external adversary capable of poisoning communication. The adversarial agent is restricted to modifying messages on its blackboard and communicating its own preferences, whereas the external adversary can target any agent, action, or blackboard. Our results indicate that (1) \textit{a single adversarial agent is sufficient to misalign the entire system}, and (2) \textit{an external adversary can induce misalignment in one shot with access to a single planning round, though multiple shots are required to improve efficacy}.

\pbe{Availability. How easily does context overflow?}
In collaborative settings, agents expend significant tokens and maintain extensive context windows to retain the history of prior interactions, which informs future decisions. We were  able to carry out the availability attacks at only a fraction of the cost required for completing the underlying task. These findings suggest that \textit{MASs are particularly vulnerable to context overflow attacks, with attack costs diminishing as additional agents participate}.
