\section{Experiments}
To evaluate the performance of the attacks, we first measure the joint-utility of the agents on the three given tasks. We use difference in utility as the primary measure of misalignment success, since misalignment impacts the ability of the agent to contribute to the joint goal. We measure privacy by comparing the actual private information to the retrieved information with LLM-as-a-judge. We assign a accuracy score of 100\% if the LLM states the retrieved information is fully accurate, 50\% if it is partially accurate, and 0\% if it is inaccurate. We report the context overflow attack success rate (ASR) by measuring the number of times, out of 30 seeded runs, the attack causes an API error.

\subsection{Driving Use Cases}

We adopt three instruction-augmented DCOPs~\citep{mahmud2025collab, mahmud2025distributed} that span environments generated from synthetic and real-world data. Each environment holds a ground-truth joint-utility function and a well-defined action space.

\pbe{Meeting Scheduling.} Meeting Scheduling is a partially-generated real-world environment where agents are attendees; decision variables are meetings \(\mathcal{X}=\{x_m\}\) with discrete slots \(\mathcal{D}_{x_m}=\{0,\ldots,9\}\) (1-hour blocks). Each meeting has an \emph{owner} (one of its attendees). The context \(c\) provides a per-meeting mode \(\{\textsc{Physical},\textsc{Zoom}\}\) and building coordinates for physical meetings. For each agent \(i\), \(I_i\) specifies (a) preferred slots \(P_{i,m}\subseteq\{0,\ldots,9\}\) for each meeting \(m\) they attend, and (b) a strict priority \(\pi_i(m)\in\mathbb{N}\) over their meetings. Optionally, \(I_i\) includes a visual panel that \emph{mirrors} the textual fields: a graph-based campus map (nodes are buildings placed at coordinates from \(c\), edges labeled by integer minute distances) and a simple 10-slot strip per meeting highlighting the agent’s preferred slots \(P_{i,m}\); the visual adds no scoring fields beyond what \(P_{i,m}\) and \(c\) already convey. For the joint-utility score, Meeting ranges from $[0, \infty]$ with a higher score being more successful.

\pbe{Personal Assistant.} PersonalAssistant is a fully synthetic environment where each agent \(i\) chooses an outfit \(x_i\) from a wardrobe; an outfit is object that contains following attributes \((\text{article}, \text{color}, \text{optional image})\).
The interaction graph induces color-based factors:
unary \textsc{PREF\_COLOR}/\textsc{AVOID\_COLOR} and pairwise \textsc{MATCH\_COLOR}/\textsc{NOT\_MATCH\_COLOR}.
Only \emph{color} affects scoring (articles/images are presentation only). \(I_i\) is text specifying the agent’s color likes/dislikes and neighbor cues (e.g., “match Alice,” “do not match Bob”) and the description of the outfits in the wardrobe. An optional \emph{visual panel} mirrors the text description of the wardrobe: a per-agent collage of their wardrobe options. For the joint-utility score, PersonalAssistant ranges from $[0,1]$ with a higher score being more successful.


\pbe{Smart-Home Assistant.} SmartHome is fully generated with real-world meter data where agents are smart-home assistants (one per home). Each home has several tasks; for each task the agent selects a start time \(x_{h,j}\) from its \emph{allowed-start} set. The context \(c\) provides a time-varying sustainable capacity profile \(S[t]\). When aggregate demand exceeds \(S[t]\) at slot \(t\), the excess is supplied by the main—unsustainable—grid. A single high-arity factor couples all homes through this main-grid draw. For each home \(h\), \(I_h\) enumerates its tasks with energy \emph{consumption} (kW), \emph{duration} (slots), and the \emph{allowed} start times used by the scorer. An optional visual panel \emph{mirrors} the same information: a top bar chart of \(S[t]\) over the horizon and, below, per-task horizontal segments marking allowed start windows. For the joint-utility score, SmartHome ranges from $[-\infty, 0]$ with a higher score being more successful.


\subsection{Experimental Setup}
In our experiments, we use seeded, randomized configurations of each environment, varying transition dynamics, factor graph initialization, number of agents, preferences, and constraints. To exhibit complex communication, we simulate 6 agents for PersonalAssistant, 10 agents for Meeting, and 8 agents for SmartHome.


\subsection{Experiments}

Table~\ref{tab:baselines} reports the normalized joint objective value, $F_{\textsc{POST}}$ across three models and three DCOP domains, which we use as the baseline for our attack experiments in Table~\ref{tab:CIA_results}. We normalize $F$ using min-max normalization by using the lowerbound over the minimum possible scores for each seed instance and the upperbound over the maximum possible scores where min and max values are obtained using search. We find that smaller models such as OpenAI GPT-4.1-nano are often unable to assign actions to all their agent-owned variables (e.g., meeting time slots, outfit, or energy time slots), causing incomplete evaluations which are filtered out in the calculation of the joint-utility values.

To study the different attacks, we adopt GPT-4.1-mini as our primary model and focus on meeting scheduling for evaluations. We evaluate communication poisoning under varying numbers of poisoning shots to analyze the correlation between increased poisoning and misalignment. Our results show that in the privacy attack, the adversary was able to query the model and retrieve details with 100\% accuracy. We also successfully conducted context overflow attacks with 100\% accuracy. This shows MASs can be highly vulnerable to privacy and availability attacks. 

% We find that smaller models such as OpenAI GPT-4.1-nano are often unable to assign actions to all their agent-owned variables (e.g., meeting time slots, outfit, or energy time slots), causing incomplete evaluations which are filtered out in the calculation of the joint utility values. This inability to assign actions, biases some of the joint utility values resulting in OpenAI GPT-4.1-nano spuriously outperforming larger models as depicted in the SmartHome environment with $7/30$ successfully completed runs compared to the $29/30$ for GPT-4.1-mini and $30/30$ for GPT-4.1.

Although we consistently observe a decrease in utility under adversarial agent and communication poisoning attacks, the reduction is not significant—indicating that while these attacks succeed, their impact remains relatively weak. However, we do observe that increasing the number of shots leads to higher attack efficacy, showing a clear correlation between poisoning percentage and attack success.
%% Unnormalized
% \begin{table*}[t]
%   \centering
%   \small
%   \setlength\tabcolsep{6pt}
%   \renewcommand{\arraystretch}{1.0}
%   % \begin{adjustbox}{width=.95\textwidth,center}
%   \begin{tabular}{@{}lccc@{}}
%     \toprule
%     \textbf{Model} &
%     \textsc{Meeting $\uparrow$} &
%     \textsc{SmartHome $\uparrow$} &
%     \textsc{PersonalAssistant $\uparrow$} \\
%     \midrule
%     OpenAI GPT-4.1
%       & $63.17 \pm 5.18$
%       & $-194.87 \pm 109.44$
%       & $0.58 \pm 0.28$ \\
%     \midrule
%     OpenAI GPT-4.1-mini
%       & $62.33 \pm 5.76$
%       & $-198.59 \pm 187.94$
%       & $0.61 \pm 0.15$ \\
%     \midrule
%     OpenAI GPT-4.1-nano
%       & $56.6 \pm 8.07$
%       & $-139.96 \pm 187.94$
%       & $0.58 \pm 0.13$ \\
%     \bottomrule
%   \end{tabular}
%   % \end{adjustbox}
%   \caption{Joint-utility value across different models and environments.}
%   \label{tab:baselines}
% \end{table*}

%% Normalized based on global max min across instances
\begin{table*}[t]
  \centering
  \small
  \setlength\tabcolsep{6pt}
  \renewcommand{\arraystretch}{1.0}
  % \begin{adjustbox}{width=.95\textwidth,center}
  \begin{tabular}{@{}lccc@{}}
    \toprule
    \textbf{Model} &
    \textsc{Meeting $\uparrow$} &
    \textsc{SmartHome $\uparrow$} &
    \textsc{PersonalAssistant $\uparrow$} \\
    \midrule
    OpenAI GPT-4.1
      & $83.1 \pm 8.1$
      & $66.2 \pm 22.4$
      & $58.0 \pm 28.0$ \\
    \midrule
    OpenAI GPT-4.1-mini
      & $81.8 \pm 9.0$
      & $65.4 \pm 38.4$
      & $61.0 \pm 15.0$ \\
    \midrule
    OpenAI GPT-4.1-nano
      & $72.8 \pm 12.6$
      & $77.4 \pm 38.4$
      & $58.0 \pm 13.0$ \\
    \bottomrule
  \end{tabular}
  % \end{adjustbox}
  \caption{Normalized joint-utility value, $F_{\textsc{base}}$, across instruction-augment DCOPs and models ordered by model size.}
  \label{tab:baselines}
\end{table*}



% \begin{table}[t]
%   \centering
%   \small
%   \setlength\tabcolsep{6pt}
%   \renewcommand{\arraystretch}{1.0}
%   % \begin{adjustbox}{width=.95\textwidth,center}
%   \begin{tabular}{@{}lccc@{}}
%     \toprule
%     \textbf{Model} &
%     \textsc{Meeting} &
%     \textsc{SmartHome} &
%     \textsc{PersonalAssistant} \\
%     \midrule
%     OpenAI GPT-4.1
%       & $60.4 \pm 12.02$
%       & $-202.38 \pm 102.78$
%       & $0.52 \pm 0.28$ \\
%     \midrule
%     OpenAI GPT-4.1-mini
%       & $62.30 \pm 6.16$
%       & $-204.22 \pm 103.68$
%       & $0.63 \pm 0.16$ \\
%     \midrule
%     OpenAI GPT-4.1-nano
%       & $55.63 \pm 7.50$
%       & $-124.33 \pm 123.70$
%       & $0.53 \pm 0.16$ \\
%     \bottomrule
%   \end{tabular}
%   % \end{adjustbox}
%   \caption{Adversarial Agent}
%   \label{tab:untargeted}
% \end{table}

% \begin{table*}[t]
%   \centering
%   \small
%   \setlength\tabcolsep{6pt}
%   \renewcommand{\arraystretch}{1.0}
%   % \begin{adjustbox}{width=.95\textwidth,center}
%   \begin{tabular}{@{}lcccc@{}}
%     \toprule
%     \textbf{Category} &
%     \textbf{Attack} &
%     \textbf{Metric} &
%     Value &
%     $F_{\textsc{post}}$ \\
%     \midrule
%     Confidentiality
%       & Information leakage
%       & Correctness (\%)
%       & 100\%
%       & - \\
%     \midrule
%     \multirow{4}{*}{Integrity}
%       & Adversarial agent
%       & \multirow{4}{*}{Utility Diff.}
%       & $+0.03$
%       & $62.30 \pm 6.17$ \\
%       & Com. poisoning (1-shot)
%       &
%       & $+0.63$
%       & $61.7 \pm 4.96$ \\
%       & Com. poisoning (2-shot)
%       &
%       & $+0.73$
%       & $61.6 \pm 5.67$ \\
%       & Com. poisoning (3-shot)
%       &
%       & $+1.73$
%       & $60.6 \pm 3.44$ \\
%     \midrule
%     Availability
%       & Context overflow
%       & ASR (\%)
%       & 100\%
%       & - \\
%     \bottomrule
%   \end{tabular}
%   % \end{adjustbox}
%   \caption{Performance of Confidentiality, Integrity and Availability attacks on schedule meeting task using GPT-4.1-mini.}
%   \label{tab:CIA_results}
% \end{table*}


%% Normalized with global max min
\begin{table*}[t]
  \centering
  \small
  \setlength\tabcolsep{6pt}
  \renewcommand{\arraystretch}{1.0}
  % \begin{adjustbox}{width=.95\textwidth,center}
  \begin{tabular}{@{}lcccc@{}}
    \toprule
    \textbf{Category} &
    \textbf{Attack} &
    \textbf{Metric} &
    Value &
    $F_{\textsc{post}}$ \\
    \midrule
    Confidentiality
      & Information leakage
      & Correctness (\%)
      & 100\%
      & - \\
    \midrule
    \multirow{4}{*}{Integrity}
      & Adversarial agent
      & \multirow{4}{*}{Utility Diff.}
      & $+0.1$
      & $81.7 \pm 9.6$ \\
      & Com. poisoning (1-shot)
      &
      & $+1.0$
      & $80.8 \pm 7.8$ \\
      & Com. poisoning (2-shot)
      &
      & $+1.2$
      & $80.6 \pm 8.9$ \\
      & Com. poisoning (3-shot)
      &
      & $+2.7$
      & $79.1 \pm 5.4$ \\
    \midrule
    Availability
      & Context overflow
      & ASR (\%)
      & 100\%
      & - \\
    \bottomrule
  \end{tabular}
  % \end{adjustbox}
  \caption{Performance of Confidentiality, Integrity and Availability attacks on schedule meeting task using GPT-4.1-mini.}
  \label{tab:CIA_results}
\end{table*}

% \begin{table}[t]
%   \centering
%   % \small
%   \setlength\tabcolsep{6pt}
%   \renewcommand{\arraystretch}{1.0}
%   % \begin{adjustbox}{width=.95\textwidth,center}
%   \begin{tabular}{@{}lccc@{}}
%     \toprule
%     \textbf{Model} &
%     \textsc{Meeting} &
%     \textsc{SmartHome} &
%     \textsc{PersonalAssistant} \\
%     \midrule
%     OpenAI GPT-4.1
%       & $+2.77$ & $+7.51$ & $+0.06$ \\
%     OpenAI GPT-4.1-mini
%       & $+0.03$ & $+5.63$ & $-0.02$ \\
%     OpenAI GPT-4.1-nano
%       & $+0.97$ & $-15.63$ & $+0.05$ \\
%     \bottomrule
%   \end{tabular}
%   % \end{adjustbox}
%   \caption{Adversarial Agent. The higher the number, the more successful the attack.}
%   \label{tab:untargeted}
% \end{table}


% \begin{table*}[t]
%   \centering
%   \small
%   \setlength\tabcolsep{6pt}
%   \renewcommand{\arraystretch}{1.0}
%   % \begin{adjustbox}{width=.95\textwidth,center}
%   \begin{tabular}{@{}lcccc@{}}
%     \toprule
%     \textbf{Category} &
%     \textbf{Attack} &
%     \textbf{Metric} &
%     Value &
%     $F_{\textsc{post}}$ \\
%     \midrule
%     Confidentiality
%       & Information leakage
%       & Correctness (\%)
%       & 100\%
%       & - \\
%     \midrule
%     \multirow{4}{*}{Integrity}
%       & Adversarial agent
%       & \multirow{4}{*}{Utility Diff.}
%       & $62.33 \pm 5.76$
%       & $62.30 \pm 6.17$ \\
%       & Com. poisoning (1-shot)
%       &
%       & $62.33 \pm 5.76$
%       & $61.7 \pm 4.96$ \\
%       & Com. poisoning (2-shot)
%       &
%       & $62.33 \pm 5.76$
%       & $61.6 \pm 5.67$ \\
%       & Com. poisoning (3-shot)
%       &
%       & $62.33 \pm 5.76$
%       & $60.6 \pm 3.44$ \\
%     \midrule
%     Availability
%       & Context overflow
%       & ASR (\%)
%       & 100\%
%       & - \\
%     \bottomrule
%   \end{tabular}
%   % \end{adjustbox}
%   \caption{ss}
%   \label{tab:CIA_results}
% \end{table*}




