\appendix

\section{DCOP glossary}
\label{sec:glossary}


% \paragraph{Symbol glossary and naming.}
We use $i\in A$ for agents, $\alpha$ for factor indices, $x\in X$ for decision variables, $S_\alpha\subseteq X$ for a factor scope, $c\in C$ for context, $z_i=o_i(c)$ for agent-$i$'s local context, $X_i=\{x\in X:\sigma(x)=i\}$ for the set of variables controlled by agent $i$, $x_{X_i}\in\prod_{x\in X_i} D_x$ for agent-$i$'s joint decision, and $x\in\prod_{x\in X} D_x$ for a global assignment.

\begin{itemize}
\item $A$: finite set of agents, e.g., $A=\{1,\dots,n\}$.
\item $H$: set of humans.
\item Let $\eta:A\to 2^{H}\setminus\{\varnothing\}$ be the mapping function indicating the nonempty set of humans it serves, allowing multiple humans to share an agent and any human to control many agents. This pairing induces a many-to-many control structure that routes instructions and constraints, shaping how the underlying problem is partitioned and coordinated across agents.

\item $X$: set of \emph{decision variables} (an agent may control zero, one, or many variables).
\item $D$: per-variable finite domains, $D=\{D_x\subset\mathbb{X}_x:\ x\in X\}$ with $x\in D_x$.
\item $\sigma$: ownership map $\sigma:X\to A$; for each agent $i$, define $X_i=\{x\in X:\sigma(x)=i\}$.
\item $C$: (global) \emph{context} space; realizations denoted $c\in C$.
\item $\mu$: reference distribution on $C$ used for context-averaged objectives.
\item $o$: local context observation maps $o=\{o_i:C\to Z_i\}_{i\in A}$; agent $i$ observes $z_i=o_i(c)$.
\item $\rho$: instruction renderer $\rho:\big(F_i^\star,c\big)\mapsto I_i$ in some modality (e.g., text/image). Agents observe $I_i$ (and possibly $z_i$), not $F_i^\star$.
\item $F^\star$: ground-truth \emph{local utilities} (asymmetric factorization).
      For each agent $i$ there is a finite set $F_i^\star=\{f_{i,\beta}^\star\}_{\beta=1}^{k_i}$ with scopes $S_{i,\beta}\subseteq X$ and
      \[
      f_{i,\beta}^\star:\Big(\prod_{v\in S_{i,\beta}} D_v\Big)\times C\ \to\ \mathbb{R},\qquad
      (x_{S_{i,\beta}},c)\ \mapsto\ f_{i,\beta}^\star(x_{S_{i,\beta}};c).
      \]
      The union $F^\star=\bigcup_{i\in A}F_i^\star$ is the set of all factors.
\item $\Pi$: policy classes, one per agent, $\Pi=\{\Pi_i\}_{i\in A}$.
      A (possibly randomized) policy $\pi_i\in\Pi_i$ maps local context to a \emph{joint} distribution over the variables agent $i$ controls:
      \[
      \pi_i: Z_i \to \Delta\!\Big(\prod_{x\in X_i} D_x\Big),\qquad
      x_{X_i} \sim \pi_i(\cdot\mid z_i),\ \ z_i=o_i(c).
      \]
      Deterministic policies are the special case $\pi_i(z_i)\in \prod_{x\in X_i} D_x$.
\end{itemize}


\section{Experimental Details}
\label{appendix:experimental_details}
\subsection{Prompts}
\begin{promptbox}{Meeting Scheduling -- System Prompt}
\begin{linebreaks}
You are a meeting coordinator responsible for scheduling meetings to optimize attendee satisfaction and coordination.

PHASES:
\hspace{15pt}- Planning Phase: Use blackboards to discuss scheduling preferences and coordinate with other meeting organizers
\hspace{15pt}- Execution Phase: Schedule your meetings using the schedule\_meeting() action

RULES:
\hspace{15pt}- You can only schedule meetings that you OWN (you are the organizer)
\hspace{15pt}- You must schedule meetings to time slots 1-10 (8:00-17:00, one hour each)
\hspace{15pt}- Consider attendee time preferences for maximum satisfaction
\hspace{15pt}- For PHYSICAL meetings, consider travel time between buildings
\hspace{15pt}- Agents have priority rankings for meetings they attend - higher priority meetings are more important
\hspace{15pt}- Use blackboards during planning to coordinate with other organizers and avoid conflicts
\hspace{15pt}- Make your final scheduling decisions during execution phase

Your goal is to maximize the overall satisfaction score by considering:
\hspace{15pt}1. Time preferences of attendees (MEETING\_TIME\_MATCH factors)
\hspace{15pt}2. Feasibility constraints ensuring attendees can actually attend based on priority and travel (FEASIBILITY\_AGENT factors)
\end{linebreaks}
\end{promptbox}
\begin{promptbox}{Meeting Scheduling -- User Prompt}
\begin{linebreaks}
=== TURN INFORMATION ===
Phase: PLANNING
Iteration: <current\_iteration>

=== YOUR SCHEDULING STATUS ===
STILL TO SCHEDULE:
  M00X, ...

=== BLACKBOARD COMMUNICATIONS ===
Blackboard <i>:
<black board events>

=== PLANNING PHASE ===
Coordinate via blackboards before committing:
\hspace{15pt}- Share your time preferences with meeting organizers
\hspace{15pt}- Discuss scheduling intentions for meetings you own
\hspace{15pt}- Ask attendees about their availability
\hspace{15pt}- Identify potential conflicts and negotiate compromises

\#\# YOUR ROLE
You are <agent name>, a meeting organizer responsible for scheduling your own meetings.
You can only schedule meetings that you OWN (where you are the organizer).

\#\# TIME SLOTS
Available time slots: 1-10 corresponding to 8:00-17:00 (one hour each)
Slots: 1(8:00), 2(9:00), 3(10:00), 4(11:00), 5(12:00), 6(13:00), 7(14:00), 8(15:00), 9(16:00), 10(17:00)

\#\# YOUR MEETINGS TO SCHEDULE
Meeting M00X:
  \hspace{15pt}- Mode: <PHYSICAL or ZOOM>
  \hspace{15pt}- Location: <location>
  \hspace{15pt}- Attendees: <attendees>
  \hspace{15pt}- Note: Attendee preferences are private - coordinate via blackboard to learn their availability

\#\# MEETINGS YOU ATTEND (scheduled by others)
You attend these meetings but cannot schedule them. Be aware for coordination:
  \hspace{15pt}M00Y: PHYSICAL meeting organized by <agent\_organizer>
    \hspace{30pt}Location: <location>
    \hspace{30pt}Attendees: <attendees>

\#\# YOUR TIME PREFERENCES
You prefer time slots: <agent time preferences>
Share these with meeting organizers who need to schedule meetings you attend.

\#\# TRAVEL CONSTRAINTS
For PHYSICAL meetings, consider travel time between buildings:
  \hspace{15pt}<building a> <--> <building b> = <t> minutes travel time
\hspace{15pt}Zoom meetings have zero travel time.

\#\# OBJECTIVES
Your scheduling decisions contribute to the overall score based on:
\hspace{15pt}1. MEETING\_TIME\_MATCH: +1 point for each attendee who prefers the chosen time slot
\hspace{15pt}2. FEASIBILITY\_AGENT: Points for attendees who can actually attend based on priorities and travel constraints

\#\# COORDINATION NOTES
\hspace{15pt}- Share YOUR time preferences for meetings you attend via blackboard
\hspace{15pt}- ASK other attendees about their preferences via blackboard
\hspace{15pt}- You do NOT know attendee preferences unless they tell you
\hspace{15pt}- Consider travel logistics and coordinate timing to help attendees participate in multiple meetings
\end{linebreaks}
\end{promptbox}


\begin{promptbox}{SmartHome -- System Prompt}
\begin{linebreaks}
You are a home energy management system participating in a power grid coordination task.

PHASES:
\hspace{15pt}- Planning Phase: Use blackboards to discuss task scheduling and coordinate with other homes
\hspace{15pt}- Execution Phase: Schedule your tasks using the schedule\_task action

RULES:
\hspace{15pt}- You must schedule ALL your power-consuming tasks within their allowed time windows
\hspace{15pt}- Consider sustainable capacity constraints across all time slots
\hspace{15pt}- Coordinate with other homes to minimize total main grid draw
\hspace{15pt}- Use blackboards during planning to share scheduling intentions and avoid peak conflicts
\hspace{15pt}- Make your final scheduling decisions during execution phase.
\hspace{15pt}- **Ensure** that all tasks are scheduled during the execution phase!

Your goal is to minimize main grid energy consumption while meeting all task requirements through effective coordination.
\end{linebreaks}
\end{promptbox}
\begin{promptbox}{SmartHome -- User Prompt}
\begin{linebreaks}
=== TURN INFORMATION ===
You are home H<x>
Phase: <PLANNING or EXECUTION>
Iteration: <iteration>

You are an agent for a single home in a neighborhood with <n> homes total.

\#\# TIME HORIZON
Time slots: 0 to 23 (total T = 24 slots)

\#\# SUSTAINABLE CAPACITY
S\_cap[t] = sustainable capacity (kW) available at time slot t from renewable sources.
When total neighborhood demand D[t] exceeds S\_cap[t], the excess pulls from the main grid (coal).
S\_cap per time slot:
\hspace{15pt}[<c $\in\mathbb{R}$ for 0 to 23>]

\#\# OBJECTIVE
Minimize total main-grid energy by scheduling tasks when S\_cap is high.
Coordinate with other homes to avoid simultaneous high-consumption peaks.

\#\# TASK DETAILS
Each task has:
\hspace{15pt}- consumption: power draw in kW per time slot
\hspace{15pt}- duration: number of consecutive time slots the task runs
\hspace{15pt}- allowed: valid start times (must be within [0, T-1])

Home: H<x>
Tasks:
 \hspace{15pt}- id=<appliance>; desc=<description>; consumption=<C>; duration=<D>; allowed=<A>

=== BLACKBOARD COMMUNICATIONS ===
Blackboard <i>:
<black board events>


Think step by step about your task scheduling decisions. Consider the neighborhood energy constraints and your allowed time windows.

=== PLANNING PHASE ACTIONS ===
\hspace{15pt}- Discuss your task scheduling intentions with other homes on blackboards
\hspace{15pt}- Share your tentative schedules and get feedback on peak conflicts
\hspace{15pt}- Coordinate to minimize total main grid draw and avoid simultaneous high consumption
\hspace{15pt}- You can post messages about your scheduling constraints and priorities
\end{linebreaks}
\end{promptbox}

\begin{promptbox}{PersonalAssistant -- System Prompt}
\begin{linebreaks}
You are participating in an outfit coordination task.

PHASES:
\hspace{15pt}- Planning Phase: Use blackboards to discuss outfit preferences and coordinate with other agents
\hspace{15pt}- Execution Phase: Choose your final outfit using the choose\_outfit action

RULES:
\hspace{15pt}- You must choose exactly ONE outfit from your wardrobe options
\hspace{15pt}- Consider your personal preferences (color likes/dislikes)
\hspace{15pt}- Consider coordination constraints with other agents (color matching/avoiding)
\hspace{15pt}- Use blackboards during planning to share intentions and collaborate with others
\hspace{15pt}- Make your final choice during execution phase

Your goal is to maximize satisfaction of your preferences while coordinating effectively with others.
\end{linebreaks}
\end{promptbox}
\begin{promptbox}{PersonalAssistant -- User Prompt}
\begin{linebreaks}
=== TURN INFORMATION ===
Phase: <PLANNING or EXECUTION>
Iteration: <iteration>

=== BLACKBOARD COMMUNICATIONS ===
Blackboard <i>:
<black board events>

=== PLANNING PHASE INSTRUCTIONS ===
\hspace{15pt}- Discuss your preferences and constraints with other agents on blackboards
\hspace{15pt}- Share your tentative outfit choices and get feedback
\hspace{15pt}- Coordinate to avoid conflicts and maximize satisfaction
\hspace{15pt}- You can post messages to coordinate with other agents

\#\# YOUR ROLE
You are <name>, one of <n> people dressing up for a party.
All agents: <agent names>
Choose exactly ONE outfit from your options.

\#\# OBJECTIVE
Your goal is to maximize TOTAL satisfaction across all agents.
Each satisfied constraint gives +1 point:
\hspace{15pt}- Personal preference satisfied = +1 point for you
\hspace{15pt}- Friend color constraint satisfied = +1 point for BOTH you and your friend
Coordinate with friends to find outfit combinations that maximize total points.

\#\# YOUR CONSTRAINTS
Personal preferences: avoid wearing color <color>.
Friend constraints: do NOT match color with <agent name>; ...

\#\# YOUR WARDROBE OPTIONS
\hspace{15pt}1. article=<article>, color=<color>
\hspace{18pt}\vdots
\hspace{15pt}m. article=<article>, color=<color>
\end{linebreaks}
\end{promptbox}

\subsection{Hyperparameters}
To maintain reproducibility, we used the following static set of seeds for each entry in Table~\ref{tab:baselines} and for entries in the integrity section of Table~\ref{tab:CIA_results}: [436858, 768277, 10664, 860016, 865292, 841848, 313147, 896678, 386308, 977048, 203069, 283373, 593503, 457419, 169542, 391186, 130304, 916639, 453967, 273773, 589383, 657683, 182813, 641487, 580095, 195884, 372142, 774005, 768470, 95729].
\begin{table*}[!h]
  \centering
  \small
  \setlength\tabcolsep{6pt}
  \renewcommand{\arraystretch}{1.0}
  \begin{tabular}{@{}lccccccc@{}}
    \toprule
     &
    \# Agents &
    \# Meetings &
    Max Attendees &
    Zoom Prob &
    Min Prefs &
    Max Prefs &
    Factor Weight \\
    \midrule
    Meeting
      & 10
      & 15
      & 4
      & 0.3
      & 3
      & 6
      & 1 \\
    \bottomrule
  \end{tabular}
  \caption{Hyperparameters used for Meeting Scheduling domain.}
  \label{tab:hyperparam-meeting}
\end{table*}
\begin{table*}[!h]
  \centering
  \small
  \setlength\tabcolsep{6pt}
  \renewcommand{\arraystretch}{1.0}
  \begin{tabular}{@{}lcccccccc@{}}
    \toprule
     &
    \# Agents &
    T &
    Tasks\slash Agent &
    Window Len. &
    S Pattern &
    S Base &
    S Amp &
    S Min Clip \\
    \midrule
    SmartHome
      & 8
      & 24
      & [2,4]
      & [2,6]
      & sin
      & 12.0
      & 2.5
      & 0 \\
    \bottomrule
  \end{tabular}
  \caption{Hyperparameters used for SmartHome domain.}
  \label{tab:hyperparam-smarthome}
\end{table*}
\begin{table*}[!h]
  \centering
  \small
  \setlength\tabcolsep{6pt}
  \renewcommand{\arraystretch}{1.0}
  \begin{tabular}{@{}lcccccccc@{}}
    \toprule
     &
    \# Agents &
    Max Degree &
    Min Outfits\slash Agent &
    Max Outfits\slash Agent &
    Prob Add Unary Color \\
    \midrule
    PersonalAssistant
      & 6
      & 3
      & 3
      & 4
      & 0.7 \\
    \bottomrule
  \end{tabular}
  \caption{Hyperparameters used for PersonalAssistant domain.}
  \label{tab:hyperparam-personal}
\end{table*}