\todo{[review C6.1] this conclusion near-paraphrases the abstract sentence by sentence (4 of 6 sentences overlap, including the headline "the best harness is the combination..."); rewrite as (a) one-sentence restatement + (b) the three forward directions in \S5.4 with the highest-leverage one named explicitly.}What is the best harness for cybersecurity AI? We answer this question by measuring the per-challenge solve sets of five LLM agent scaffolds (\texttt{CSI::Claude}, \texttt{CSI::Codex}, \texttt{CSI::Mistral}, \texttt{CSI::GCAI}, \texttt{CSI::CAI}) on the 33 sanctioned cybench challenges with a single fixed model, \aliasmini{}. The best individual scaffolds solve $15/33$ (\texttt{CSI::Claude} and \texttt{CSI::Codex}, tied); the four-scaffold union solves $17/33$. A fifth scaffold (\texttt{CSI::Mistral}, $10/33$), tested independently, contributes one exclusive solve (\texttt{crushing}). No single scaffold dominates: each of four scaffolds contributes exactly one exclusive solve that no other reaches, while \texttt{CSI::GCAI} contributes none.

The answer is that the best harness is not any single scaffold but their \emph{combination}. Scaffold heterogeneity, embodied as structurally different orchestration patterns wrapping the same model, is a structural lever toward cybersecurity superintelligence. The lever is consistent with the heuristic-injection posture of prior G-CTR work \cite{mayoralvilches2025gametheoretic} but operates one level higher in the stack, on the agent population rather than on the agent's reasoning loop.

We validated this answer by deploying a blackboard-based multi-scaffold architecture under which the four heterogeneous scaffolds run in parallel against the same target and exchange typed findings via a shared substrate. The blackboard solves $19/33$ ($57.6\%$), exceeding the union ceiling of $17/33$ for the first time. The best harness for cybersecurity AI is the combination of heterogeneous scaffolds under a carefully designed multi-agent protocol, not the optimisation of any single one.

\section*{Acknowledgements}
This work has been funded by the European Innovation Council (GA 101161136).
