\subsection{Reading of the empirical result}\label{sec:reading}

Three observations from Section~\ref{sec:results} are worth restating. First, the \emph{exclusive-solve table} is concentrated rather than diffuse: \texttt{CSI::CAI} accounts for four of the seven exclusive solves, \texttt{CSI::GCAI} for two, \texttt{CSI::Claude} for one, \texttt{CSI::Codex} for none. Second, the \emph{best individual scaffold has zero unique value}: every challenge \texttt{CSI::Codex} captures is also captured by another scaffold, so removing it from the four-scaffold ensemble leaves the union unchanged. Third, the \emph{frugal Pareto frontier} is not anchored by the strongest individual scaffold but by the cheapest one: \texttt{CSI::CAI} alone is Pareto-optimal at the low-cost end and is present in every Pareto-optimal subset.

These observations together support a counter-intuitive design rule: when adding a scaffold to a multi-scaffold ensemble, prefer the scaffold whose architecture is most structurally distant from the ones already included, even if that scaffold underperforms on raw solve count. \texttt{CSI::GCAI}, the weakest individual scaffold, is the one the optimal $k=3$ ensemble cannot drop, because its one-shot reasoning regime captures challenges that the iterative tool-loop scaffolds (\texttt{Claude}, \texttt{Codex}) systematically miss.

\subsection{Threats to validity}\label{sec:threats}

\paragraph{Single model.} The whole study runs against \aliasmini{}. We do not know whether the same exclusive-solve geometry would hold against a frontier model with broader pretraining; it is plausible that frontier models smooth over scaffold differences, in which case the lower-bound payoff of heterogeneity shrinks. The hypothesis we advance, however, predicts the opposite for harder benchmarks: under capability stretch, scaffold heterogeneity should matter more, not less.

\paragraph{Single benchmark.} We measure on cybench, which is biased toward Jeopardy-style challenges with a clear flag. The complementarity geometry on multi-host scenarios (e.g.\ MHBench), where the agent must persist state across machines, could differ.

\paragraph{Single run per scaffold per challenge.} We did not run pass@$k$ within scaffolds. The non-overlapping exclusive-solve set could in principle be partially recovered by re-running the dominated scaffold with a different temperature or seed. Prior work on G-CTR \cite{mayoralvilches2025gametheoretic} reports a $5.2\times$ reduction in behavioural variance under guidance, which suggests that without guidance, intra-scaffold variance is non-trivial. We therefore consider the blackboard result of $57.6\%$ a \emph{lower bound} on multi-scaffold coverage, not a fixed point.

%\paragraph{Cost extraction.} Two of the per-scaffold costs are extracted from a growing proxy JSONL log that is shared across scaffold runs. We cap raw per-attempt costs at $\$200$ to reject the obvious accumulator artefacts (values $>\$900$ on $<2$ minute runs). This cap is conservative for the tool-loop scaffolds, which can legitimately spend $\$80$ to $\$120$ on a $2$-hour very-hard challenge. The reported total costs in Table~\ref{tab:scoreboard} are therefore lower bounds on the true cost.

%\paragraph{Infrastructure fragility.} The two infrastructure fixes mentioned in Section~\ref{sec:harness} (Mono-wrapper guard and host-side image pre-pull) recovered six otherwise-invalidated challenges. The unfixed harness silently invalidates results, which is a more dangerous failure mode than a hard error; any reproduction of the experiment should apply the equivalent guards before instrumentation.

\subsection{Connection to the prior work and to the next step}\label{sec:connection}

G-CTR \cite{mayoralvilches2025gametheoretic} inserted a single human-style heuristic, namely game-theoretic reasoning about attacker/defender effort, into a single-agent loop. The present work extends the bio-inspired posture to a different cognitive lever, namely the heterogeneity of the agent population itself, and provides the empirical lower bound that justifies the lever. The natural composition is a multi-scaffold ensemble in which each scaffold is also using a different LLM model. The next one would be to explore ensembles that are G-CTR-guided; under that composition the closed-loop digest of one scaffold becomes a candidate item on the blackboard of the others. We leave this compositions to follow-up work.
