Cybersecurity AI is being shaped by a small number of agent scaffolds, the orchestration layers that wrap a Large Language Model (LLM) into a tool-using offensive practitioner. PentestGPT \cite{deng2024pentestgpt,mayoral2025offensive} introduced the LLM-in-the-loop pattern in 2023, Cybersecurity AI (CAI) \cite{mayoral2025cai} demonstrated practitioner-level results in early 2025, and recent work on Generative Cut-the-Rope (G-CTR) \cite{mayoralvilches2025gametheoretic} inserted a game-theoretic human heuristic into the agent's reasoning loop, doubling success on a 44-run cyber-range benchmark. These advances all share a single design assumption: \emph{one scaffold per agent}, optimised end-to-end against a target benchmark.

However, scaffolds are not interchangeable wrappers. They differ in how the model commits to actions (one-shot vs.\ iterative), in the granularity of their tool registry (free shell vs.\ constrained API), in how they manage context, and in whether they impose hard cost or turn caps. Each of these choices steers the LLM through a different region of the solution space. This raises the central research question of this work: \emph{what is the best harness for cybersecurity AI?} A natural sub-question follows: \emph{when several scaffolds are run on the same challenge with the same model, do they fail and succeed on the same items, or on different items?} If they fail and succeed on different items, scaffolds are complementary, and the best harness is not any single scaffold but their combination.


Human discovery in security, as in science, is rarely the work of a uniformly trained team. Reverse engineers, web exploitation specialists, cryptanalysts, and binary exploitation researchers approach the same target through different mental models, and the breakthroughs that count are typically produced by the intersection of those models rather than by any single expert. We extend this observation, already used in agent design via game-theoretic guidance in G-CTR \cite{mayoralvilches2025gametheoretic}, to the scaffold layer itself. Our working hypothesis is that, given the probabilistic nature of LLMs and the empirically large variance in scaffold behaviour, \emph{heterogeneity of scaffolds is a structural lever toward cybersecurity superintelligence}, not an engineering inefficiency to be optimised away.

To test this hypothesis, we built Cybersecurity SuperIntelligence (CSI), a meta-scaffold that unifies heterogeneous agent harnesses under a common orchestration layer. CSI wraps any LLM-driven scaffold (Claude Code, Codex, Mistral Vibe, a one-shot GCAI generator, or the CAI framework) behind a uniform benchmark harness, local routing proxy, and blackboard-based multi-agent architecture, enabling controlled comparison and parallel composition of structurally different scaffolds against the same model and challenge suite.

Using CSI, we answer this question empirically. Holding the model fixed at \aliasmini{}, no single scaffold is the best harness: across the 33 cybench challenges the best individual scaffold solves $15/33$ ($45.5\%$), the four-scaffold union solves $17/33$ ($51.5\%$), and a blackboard architecture in which heterogeneous scaffolds exchange findings reaches $19/33$ ($57.6\%$). The best harness for cybersecurity AI is therefore not any single scaffold but the \emph{combination} of structurally heterogeneous scaffolds under a multi-agent protocol.

In sum, this paper makes the following contributions:

\begin{enumerate}[leftmargin=*,nosep]
  \item \textbf{Empirical complementarity.} A controlled study that holds the model fixed at \aliasmini{} and runs structurally heterogeneous scaffolds on the same challenges under the same per-challenge budget, instrumenting their per-item agreement to test whether scaffolds fail and succeed on the same or on different items.
  \item \textbf{A generative minimalistic scaffold (GCAI).} \texttt{CSI::GCAI}, a $\sim\!1{,}400$-line generative scaffold derived from CAI that can be rapidly customised for domain-specific use cases, offered as a compact, auditable blueprint that is an alternative to production-grade agent frameworks.
  \item \textbf{Blackboard multi-agent architecture.} A parallel-race architecture with a blackboard that lets heterogeneous scaffolds exchange typed findings, turning the measured complementarity into coverage beyond the union of independent runs.
\end{enumerate}
