\section{Steering LLMs for Cultural Alignment}
\label{sec:methods}


We present an overview of our tested strategies for improving cultural alignment in Figure \ref{fig:main_figure}. We first adapt existing approaches as \textbf{1) Single-LLM} (\S \ref{method:single_llm}) and propose \textbf{2) Multi-LLM Collaboration}-based approaches (\S \ref{method:multi_llm}). All prompts are in Appendix \ref{appendix:prompts}.


\subsection{Single-LLM}
\label{method:single_llm}
% \paragraph{Single Model.}
% We evaluate LLMs with two levels of cultural contextualization: with and without the relevant social norm to the story (\textit{rule-of-thumb}) in the prompt.

\paragraph{Self-Reflection.}
Previous studies have shown that LLMs can evaluate their outputs and learn from their own feedback \cite{kadavath2022language, reflexion, pan2023automatically, renze2024selfreflectionllmagentseffects}. Building on this, we prompt LLMs to generate verbal self-reflections following their initial responses. Specifically, given the country, rule-of-thumb, and story as input, we prompt an LLM $\mathcal{M}$ to 1) generate an initial decision $\hat{y}_0^\mathcal{M}$ by evaluating the cultural adaptability of the given scenario, 2) generate a rationale for their decision $f^\mathcal{M}$, and 3) incorporate this as additional context to make a final decision $\hat{y}_f^\mathcal{M}$.

% \mc{Use notations consistent with those used for debate throughout to formalize the process.}

% \subsection{Selective Model}
% \label{method:selective model}
% Stories from different cultures may not benefit uniformly from a single model, as the best-performing model often varies across cultures. To explore the potential of \textbf{multi-LLM collaboration}, we theoretically evaluate an approach that combines the strengths of multiple LLMs by routing queries based on ground truth labels. Specifically, given two LLMs, $\mathcal{M}_1$ and $\mathcal{M}_2$, predictions for each culture are assigned to the LLM with higher mean accuracy. For instance, if $\mathrm{Acc}(\mathcal{M}_1) > \mathrm{Acc}(\mathcal{M}_2)$ for entries related to South Korean culture $\mathcal{C}_{sk}$, then $\mathcal{M}_1$ handles all predictions for $\mathcal{C}_{sk}$. While this approach is not directly comparable to other methods, as it relies on access to gold labels, it provides a theoretical upper bound and motivates for other forms of multi-LLM collaboration strategies (\S \ref{method:multi-agent debate}).


\subsection{Multi-LLM Collaboration}
\label{method:multi_llm}
On one hand, adapting a single LLM to reflect on its own generations poses challenges such as confirmation bias and hallucination, which can lead to unreliable self-evaluation \cite{feng-etal-2024-dont, liang-etal-2024-encouraging}. On the other hand, LLMs often exhibit varying knowledge coverage, with the potential to complement each other due to differences in training data distributions and alignment processes \cite{yu2023kola, du2023improving, bansal2024llm}. We tap into this \textit{knowledge complementarity} through one common form of multi-LLM collaboration, debate \cite{irving2018ai}, where two LLM-based agents debate and collaboratively evaluate the given scenario.


\paragraph{Debate-Only.}
Given the same inputs as in \S \ref{method:single_llm}, two LLM agents, $\mathcal{M}_1$ and $\mathcal{M}_2$, independently generate their initial decisions, $\hat{y}_0^{\mathcal{M}_1}$ and $\hat{y}_0^{\mathcal{M}_2}$ respectively. Each agent then provides feedback, $f^{\mathcal{M}_1}$ and $f^{\mathcal{M}_2}$ to the discussant's initial decision. We exchange the feedback, and each agent incorporates the feedback along with their initial decisions to arrive at their final decisions, $\hat{y}_f^{\mathcal{M}_1}$ and $\hat{y}_f^{\mathcal{M}_2}$. For $i=1$ and $j=2$ (and vice versa):

\begin{equation}
\begin{split}
    \hat{y}_f^{\mathcal{M}_i} &= \mathcal{M}_i(\hat{y}_0^{\mathcal{M}_i}, \hat{y}_0^{\mathcal{M}_j}, f^{\mathcal{M}_i}, f^{\mathcal{M}_j}) \\
\end{split}
\end{equation}
If their final decisions are identical, we use it as the aggregated decision, regardless of its correctness. Otherwise, we employ a judge LLM, $\mathcal{M}_j$, to summarize and synthesize the debate history into a final decision \cite{feng-etal-2024-dont, li-etal-2024-llms-speak}.

%     \hat{y}_f^{\mathcal{M}_2} &= \mathcal{M}_2(\hat{y}_0^{\mathcal{M}_1}, \hat{y}_0^{\mathcal{M}_2}, f^{\mathcal{M}_1}, f^{\mathcal{M}_2})


\begin{equation}
\begin{split}
    \mathcal{M}_j(\hat{y}_0^{\mathcal{M}_1}, \hat{y}_0^{\mathcal{M}_2}, f^{\mathcal{M}_1}, f^{\mathcal{M}_2},
    \hat{y}_f^{\mathcal{M}_1}, \hat{y}_f^{\mathcal{M}_2}) \rightarrow \hat{y}_f^{\mathcal{M}_j}
\end{split}
\end{equation}

\paragraph{Self-Reflect+Debate.}
LLMs may exhibit varying preferences when responding to feedback. To account for this, we extend the Debate-Only setup by agents making choices during their turn: (A) self-reflection, where they generate reflection $r^{\mathcal{M}_i}$ on their previous output, or (B) debate, where they generate feedback $f^{\mathcal{M}_i}$ in response to the discussant's opinion. Formally, if $\mathcal{M}_1$ chooses (A) self-reflection and $\mathcal{M}_2$ chooses (B) debate, the updated decision for $i=1$ and $j=2$ (and vice versa) is:

\begin{equation}
\begin{split}
    \hat{y}_f^{\mathcal{M}_i} &= \mathcal{M}_i(\hat{y}_0^{\mathcal{M}_i}, \hat{y}_0^{\mathcal{M}_j}, r^{\mathcal{M}_1}, f^{\mathcal{M}_2}) \\
\end{split}
\end{equation}
We use the judge LLM if their final decisions differ. Note that in both multi-LLM setups, $\mathcal{M}_1$ and $\mathcal{M}_2$ are \textit{exchangeable}, as each agent has symmetrical access to the same information.

% We provide a broader action space to enable LLMs make more informed decisions by leveraging both their internal parametric knowledge and the external information presented in the prompt.\zk{Any citations?}

% These options are presented in a multiple-choice format. To mitigate position bias \cite{orderofoptions} and address potential inconsistencies in LLM choices, the process is repeated twice, alternating the order of the options.