\section{Analysis}
\label{sec:analysis}

\definecolor{darkpurple}{RGB}{245, 66, 155}
\definecolor{bblue}{RGB}{66, 141, 245}
\definecolor{darkgreen}{RGB}{107, 201, 60}


\subsection{Decision Dynamics}
\label{sec:decision_dynamics}

% \mc{From the Sankey chart, I don't understand whether this aggregates responses from all models or only a subset of models? Given that models have different behavior, are we losing ifnormation if they are all lumped together?}
% \zk{The current visualization aggregates responses for all models -- I show the results for each LLM / LLM combinations in Appendix C.4.}

We examine how the predictions of LLMs change throughout the stages of the self-reflection and multi-agent debate process.  For self-reflection, we capture two key phases of LLM behavior: \textcolor{darkpurple}{\textbf{1)}} how initial model decisions change and \textcolor{darkgreen}{\textbf{2)}} how these contributes to final accuracy improvements. For multi-agent debate, since we consider both LLM agents simultaneously, we additionally capture \textcolor{bblue}{\textbf{3)}} how disagreed individual final accuracies are aggregated based on the judge LLM's decisions. We aggregate results from all LLMs or LLM combinations and illustrate the dynamics in Figure \ref{fig:sankey_chart}. 

% Detailed results for each LLMs are provided in Appendix \ref{appendix:detailed_dynamics}.

In the self-reflection setup (Figure \ref{fig:sankey_chart} (a)), LLMs occasionally change their correct initial decisions to incorrect ones, despite this occurs less frequently than cases where incorrect initial decisions are corrected. This results in higher rates of final correct decisions (62.5\% $\rightarrow$ 65.3\%). During both the Debate-Only (Figure \ref{fig:sankey_chart} (b)) and the Self-Reflect+Debate setup (Figure \ref{fig:sankey_chart} (c)), LLMs mostly show disagreed initial decisions (\textit{Mixed}). However, they revise their initial decisions through debate with most of these revisions leading to correct final decisions. Additionally, we find that cases where both LLMs change their correct initial decisions to incorrect ones, or vice versa, are rare. 

Taken together, the debate process itself provides unique benefits, significantly increasing correct final decision rates from 29.5\% to 63.7\% for Debate-Only and from 29.2\% to 56.7\% for Self-Reflect+Debate (\textcolor{darkpurple}{\textbf{1}} $\rightarrow$ \textcolor{darkgreen}{\textbf{2}}). Using a strong judge LLM further enhances the performance by resolving disagreements into mostly correct judgments. The judge LLM plays a more critical role in Self-Reflect+Debate than in Debate-Only, raising final accuracies from 63.7\% to 76.3\% for Debate-Only and from 56.7\% to 75.6\% for Self-Reflect+Debate (\textcolor{darkgreen}{\textbf{2}} $\rightarrow$ \textcolor{bblue}{\textbf{3}}). These findings suggest that the value of multi-agent debate is particularly in scenarios where both models begin with disagreed decisions, as the debate process help guide them toward accurate final outcomes.

% \mc{one take-away from the chart is that the judge plays a more important role in self-reflect+debate than in debate only (comparing correct predictions in green vs. blue)}
% \zk{Addressed!}


\subsection{When do LLMs Agree/Disagree?}
\label{sec:llms_disagree}

\paragraph{Label Group.}
We analyze the decision dynamics by categorizing them based on the ternary ground truth label groups, as detailed in Appendix \ref{appendix:decision_dynamics_label}. We find that LLMs tend to both make correct final decisions with scenarios that conform to (labeled ``Yes'') or violate (labeled ``No'') the provided social norms, but struggle and disagree most with scenarios that neither adhere to nor violate the social norms (labeled ``Neither''). This is consistent with previous findings on inherent agreement biases within LLMs \cite{perez2022discovering, huang2024trustllm}. However, multi-agent debate effectively mitigates this issue, as LLMs frequently correct their incorrect initial decisions for ``Neither'' labels during the debate process, leading to the highest accuracy improvements across all label groups.

% Judge LLM benefits scenarios where the LLMs show disagreements & in Neither scenarios -> that's why the benefit is larger for Self-Reflect+Debate than Debate-Only (SR+D has higher mixed results for Neither

\paragraph{Cultural Group.}
We further assess improvements per cultural group defined by the Inglehart-Welzel cultural map (Appendix \ref{appendix:decision_dynamics_culture}). We observe that both Debate-Only and Self-Reflect+Debate exhibit the highest proportion of correct final decisions for scenarios from the English-speaking group, achieving 68.0\% and 61.7\% respectively. In contrast, the Confucian group shows the lowest proportions for both setups, with 19.1\% for Debate-Only and 18.8\% for Self-Reflect+Debate. Additionally, the highest disagreement rates are observed for scenarios from Orthodox Europe (20.5\% in Debate-Only) and African-Islamic groups (27.8\% in Self-Reflect+Debate).

% \mc{Are there patterns in the questions that both models get wrong? or right? or disagree on? There might be potential artifacts or difficulty differences in the dataset that lead to agreement or disagreement independently of the model used.}

\subsection{Cultural Group Parity}
\label{sec:cultural_group_parity}
We observe that multi-agent debate improve average accuracies \---\ but are these improvements consistent across different cultures? To address this, we analyze cultural group parities for each method, aggregated across all LLMs (or LLM combinations), as shown in Table \ref{tab:cultural_group_parity}. Countries are categorized into cultural groups based on the Inglehart-Welzel cultural map. We calculate parity premiums for each cultural group relative to the English-speaking group, which has the highest mean accuracy across all methods, as expected given previous evidence of LLM bias towards Western-centric content \cite{normad, naous-etal-2024-beer}. We show that Debate-Only (\textbf{D}) achieves the closest average parity premiums to 1 (0.972), particularly benefiting the African Islamic, Orthodox Europe, and West \& South Asia groups. This also holds when compared to the judge LLM (\textsc{Gemma-2-27b}, \textbf{J}), which achieve a parity score of 0.964. Notably, the best-performing LLM combinations in both Debate-Only (\textsc{Gemma-2}+\textsc{Aya-23}, \textbf{G+A}) and in Self-Reflect+Debate (\textsc{Gemma-2}+\textsc{EXAONE-3}, \textbf{G+E}) outperforms the cultural parity of the judge LLM by parity score of 0.994 and 0.986, respectively. 
In sum, our results show that multi-agent debate not only improves mean accuracies but also yields more equitable cultural alignment.% especially for underrepresented regions.\mc{unclear what underrepresented means in this context}


\input{table/cultural_group_parity}


 % \mc{I still don't undetrsatnd what models are included in the table and in the discussion. Is this across all models or for one model combination? If we can show that models that improve or approach the accuracy of the judge are also better in terms of parity, then it helps make a much stronger argument for debating.}

% \zk{This is aggregated result across all llms and llm combinations -- this is for both Figure 2 and Table 3. I added this information in each of their caption. I also added two best-performing variants from Debate-only and Self-Reflect+Debate (G+A and G+E in Table 3 and show they outperfom judge LLM in terms of parity.}
 

% \mc{Probably not worth doing now, but for talk/posters in the future, it would be nice to visualize results in maps.}


% \zk{Removed case study subsection for now, will add if space allows}


% \subsection{Case study}
% \label{sec:case_studies}


% We present one trajectory example of a successful debate (Debate-Only) to illustrate how two LLM agents generate their initial decisions, provide feedback to the discussant, and arrive at their final decisions. Figure \ref{fig:case_study_1} demonstrates a scenario where both agents initially made incorrect decisions but changed to reach correct final decisions. In this case, the rule-of-thumb is irrelevant to the story (labeled ``Neither''), but \textsc{SeaLLM-3} initially responds with ``Yes'' since it fails to consider the connection between the rule-of-thumb and the story. \textsc{LLaMA-3} responds as ``No'' despite understanding the irrelevance. During the debate, \textsc{LLaMA-3} provides feedback to \textsc{SeaLLM-3}, emphasizing the importance of considering the rule of relevance, which successfully shifts both agents' final decisions to ``Neither''. Additional case studies covering all variations in decision dynamics are provided in Appendix \ref{appendix:detailed_case_studies}.

% \input{figure/case_studies/main_w_c_c}

% The second example, shown in Figure \ref{fig:case_study_2}, demonstrates a scenario where both agents initially made correct decisions but later changed to incorrect ones. In this scenario, Sarah's action contradicts the rule-of-thumb (labeled ``No''), and both \textsc{InternLM-2.5} and \textsc{Yi-1.5} initially respond correctly as ``No''. However, during the debate, both agents hallucinate that the rule-of-thumb is irrelevant to the story, leading them to incorrectly change their final decisions to ``Neither''. This example highlights the importance of well-calibrated debates, as hallucinations from one agent can mislead the other, resulting in incorrect outcomes. Additional case studies covering various decision dynamics are provided in Appendix \ref{appendix:detailed_case_studies}.

% \input{figure/case_studies/main_c_c_w}
