\section{Preliminaries}
\label{sec:preliminaries}

%\paragraph{Task and agents.}
We consider a task instance $x\in\mathcal{X}$ with ground-truth label $y^\star\in\mathcal{Y}$ drawn from an unknown distribution $\mathcal{D}$. A debate is conducted by $n\geq 2$ agents indexed by $[n]=\{1,\ldots,n\}$. Each agent $i$ is a stochastic inference-time policy $\pi_{\theta_i}(\cdot\mid x,o_i)$ that maps the task instance and a local observation $o_i$ to a distribution over outputs.
%\paragraph{Per-agent state and debate state.}
At the end of each round $r$, every agent $i$ exposes a structured tuple
%\begin{equation*}
    \(\xi_i^{(r)}=\big(y_i^{(r)},\,c_i^{(r)},\,r_i^{(r)}\big)\),
%\end{equation*}
where $y_i^{(r)}\in\mathcal{Y}$ is the current answer, $c_i^{(r)}\in\{1,\ldots,5\}$ is the self-reported confidence on an ordinal scale, and $r_i^{(r)}$ is the accompanying chain-of-thought reasoning. In parallel, the router maintains an accumulated \emph{influence} statistic $\rho_i^{(r)}\in[0,1]$ that summarizes how often agent $i$'s prior critiques have been adopted by its downstream targets; its update rule is given in Section~\ref{sec:method}. The \emph{debate state} observable to the router at the start of round $r$ is
%\begin{equation*}
    \(s_r=\big\{\big(\xi_i^{(r-1)},\rho_i^{(r-1)}\big)\big\}_{i\in[n]}\).
%\end{equation*}

\paragraph{Role graph.}
%We distinguish \emph{roles} from \emph{agents}. 
Let
%\begin{equation*}
    $G_0=(V_0,E_0)$, $V_0=[n]$,
%\end{equation*}
be a directed base role graph that fixes a sparse communication pattern. 
An edge $(u\!\to\!v)\in E_0$ permits the agent occupying role $v$ to observe messages produced by the agent occupying role $u$. A role-to-agent assignment is a bijection $\pi\in S_n$, where $\pi(u)$ is the agent occupying role $u$. The induced agent-level communication graph is
\begin{align*}
    G(\pi) &= ([n],\,E(\pi)),\\
    E(\pi) &= \{(\pi(u)\!\to\!\pi(v)):(u\!\to\!v)\in E_0\}.
\end{align*}
By construction, every $G(\pi)$ preserves the per-agent in-degree of $G_0$, so the assignment $\pi$ only relabels which concrete agent occupies each role and yields a candidate sparse communication graph rather than an arbitrary subset of edges.
Since every role has in-degree $k$, the base graph has
\(
    m := |E_0| = nk
\)
directed edges. Every candidate graph $G(\pi)$ therefore satisfies
$|E(\pi)|=m$.

\paragraph{Round-based debate.}
A debate proceeds for $R$ rounds. At the start of round $r$, the round-$r$ communication graph $G^{(r)}=G(\pi_r)$ is selected as a state-aware function of $s_r$; the specific selection rule is given in Section~\ref{sec:method}. After $R$ rounds, the protocol returns $\hat{y}=\mathrm{Agg}\big(\{y_i^{(R)}\}_{i\in[n]}\big)$, where $\mathrm{Agg}$ is the aggregation rule (we use majority vote).