\section{Evaluation}
\label{sec:evaluation}

In this section, we present the evaluation of our approach. We start by providing an overview of the experimental setup, including the datasets, the baselines, evaluation measures, hyperparameter settings, and implementation details. Afterward, we compare our agent to two baselines on the binary causal question answering task. Next, we conduct an ablation analysis to evaluate the effectiveness of the different components of our approach and evaluate the effects of initial supervised learning. The code and data to reproduce our results are publicly available.%
\footnote{\url{https://github.com/ds-jrg/causal-qa-rl}}\textsuperscript{,}\footnote{\url{https://doi.org/10.5281/zenodo.10683046}}


\input{tables/datasets}

\subsection{Experimental Setup}
\label{subsec:experimental-setup}
\paragraph{Datasets} As causality graph, we employ CauseNet~\cite{Heindorf2020Causenet}. As ques\-tion-answering datasets, we employ subsets of causal questions from MS MARCO~\cite{Nguyen2016MSMARCO} and SemEval~\cite{Hendrickx2010SemEval, SharpCausalQAEmbeddings2016}. To extract binary causal question from MS MARCO we extended an extraction mechanism from \citet{Heindorf2020Causenet} by including additional causal cue words~\cite{Girju2002CausalCue}. SemEval was curated by \citet{SharpCausalQAEmbeddings2016} by selecting a subset of 1730 word pairs from the semantic relation classification benchmark SemEval 2010 Task 8~\cite{Hendrickx2010SemEval}. Among the 1730 word pairs, there are 865 causal pairs and 865 non-causal pairs, i.e., the dataset is balanced, whereas MS MARCO is imbalanced. The first three columns of Table~\ref{table-evaluation-datasets} show the original numbers of training, validation, and test questions of both datasets. However, as discussed in Sections~\ref{subsec:approach-description} and \ref{sec:pseudocode-training}, for training our reinforcement learning agent, we remove negative questions and questions where either the cause or effect cannot be found in CauseNet. The ``E. Train'' column shows the number of questions effectively available for learning when combining the training and validation sets. That leaves us with 1350 questions for MS MARCO and 812 questions for SemEval. Each causal question contains one cause and one effect. On average, a causal question has a length of 30.2 characters and 4.6 words (averaged over the training, validation, and test splits of both datasets after filtering). For testing question answering, we use both positive and negative questions regardless of whether the cause/effect can be mapped to CauseNet. If a cause or effect cannot be found in CauseNet, the question is answered with ``no''. Further details regarding Causenet and our dataset construction are given in Sections~\ref{sec:causenet} and \ref{sec:dataset} in the appendix, respectively.


\paragraph{Baselines}
We compare our agent with two kinds of baselines: (1)~breadth-first search (BFS) on CauseNet and (2)~direct question answering with language models. BFS performs an exhaustive search in the graph up to a certain depth and serves as a strong baseline. However, it must be noted that BFS can be applied effectively only to binary causal questions. Moreover, it needs to traverse many nodes in the graph whereas our reinforcement learning agent visits much fewer nodes. As a second baseline, we use UnifiedQA-v2~\cite{Khashabi2020UnifiedQA, Khashabi2022UnifiedQA2} and OpenAI's GPT-v4~\cite{OpenAI2023GPT4}. UnifiedQA-v2 is a text-to-text language model based on the T5 architecture~\cite{Raffel2020T5} and achieved state-of-the-art performance on multiple datasets. We chose UnifiedQA-v2 because it was used by the CausalQA~\cite{Bondarenko2022CausalQA} benchmark for their evaluation. Its input consists of a question and additional contextual information as shown in Figure~\ref{fig:graph-example}. We experimented with three variants of UnifiedQA-v2:
(1)~with an empty context (UnifiedQA-v2),
(2)~with causal triples as context (UnifiedQA-v2-T) as done by \cite{DalalCausalQAEnhancing2021, DalalCausalQAISWC2021},
(3)~by using the provenance data available in CauseNet along paths from the cause to the effect (UnifiedQA-v2-P).
For (2),~all triples from CauseNet are obtained where the cause in the question matches the cause in CauseNet and the effect in the question matches the effect in CauseNet.
For (3),~we take advantage of the additional meta-information available in CauseNet~\cite{Heindorf2020Causenet}. For each causal pair, CauseNet contains the original sentence from which the pair was extracted. Given a question $q$ and a path $(e_1, \dots, e_n)$ our agent found for that question, we extract the original sentence for each causal pair $(e_i, e_{i+1})$, with $0 \leq i < n$, on the path $p$. We concatenate the sentences for all paths and all pairs therein and input the sequence into the language model as context. For the GPT-v4 baseline, we use the prompt ``Answer binary causal questions with 'Yes' or 'No''' and experiment with the three variants, too.

\paragraph{Evaluation Measures}
We evaluate our agent for binary question answering using the standard classification measures accuracy, $F_1$-score, precision, and recall. Additionally, we evaluate our agent and the BFS baselines w.r.t. the number of unique nodes (entities) that are visited per question on average.

\paragraph{Hyperparameter Optimization}
We optimized hyperparameters using Optuna~\cite{Akiba2019Optuna} on the validation sets and subsequently retrained on the combined training and validation sets. We trained each agent for 2000 steps with a batch size of 128 and a learning rate of 0.0001. The hidden dimension of the feedforward heads was set to 2048. Additionally, we set the discount factor $\gamma$ to $0.99$ and the $\lambda$ parameter of GAE to $0.95$~\cite{Schulman2016GAE}. The weight $\beta$ for the entropy regularization was set to 0.01. During supervised learning, we used 300 training steps, a batch size of 64, and a supervised ratio $\alpha$ of 0.8. Moreover, we used a beam width of 50.

\paragraph{Implementation Details}
We used the AdamW~\cite{Loshchilov2019AdamW} optimizer with gradient norm clipping~\cite{Pascanu2013Clip} at a value of 0.5. As knowledge graph we used CauseNet-Precision~\cite{Heindorf2020Causenet} and to embed the entities and questions we used GloVe embeddings~\cite{Pennington2014Glove}.
We also experimented with BERT~\cite{Devlin2018BERT}, RoBERTa~\cite{Liu2019Roberta}, and E5~\cite{Wang2022E5}, but this did not lead to improved results in terms of accuracy and $F_1$-score.
For the UnifiedQA-v2 baseline, we chose the \textit{base} model~\cite{Khashabi2020UnifiedQA, Khashabi2022UnifiedQA2}. All experiments were run on an NVIDIA A100 40GB. Additional details can be found in our GitHub repository (URL see above).

\subsection{Evaluation of the RL Agent}
\label{subsec:evaluation-approach}

\input{tables/evaluation}

The last column of Table~\ref{table-evaluation}, compares the number of visited nodes by our approach with a brute-force BFS. Our approach visits less than 30 nodes per question on average whereas a BFS visits over 3,000 nodes to answer binary questions with 3 or 4 hops. Thus, our approach effectively prunes the search space by 99\%. The fact that the number of nodes visited by BFS barely increases from 3 to 4 hops can be attributed to the topology of CauseNet.

The first columns of Table~\ref{table-evaluation} compare the question-answering performance of our agent with the BFS and the language models UnifiedQA-v2 and GPT-v4. Our agent consistently achieves a high precision above or around 0.9. In terms of precision, our agent outperforms BFS, comes close to GPT-v4 on MS MARCO, and outperforms GPT-v4 on SemEval. In terms of recall, BFS achieves a slightly higher recall than our agent, and UnifiedQA-v2 and GPT-v4 achieve an even higher recall. The accuracy of BFS and our agent is higher on SemEval than on MS MARCO.

Unlike language models, our graph-based approach yields high-precision and verifiable answers as for each edge on a path, we can provide its original source on the web. Our recall is naturally lower than BFS as BFS performs an exhaustive search and positively answers a question if it can find a path, whereas our agent drastically prunes the search space and hence, occasionally misses a path. The fact that language models have an even higher recall can be explained two-fold: On the one hand, causality graphs such as CauseNet are extracted from text documents on the web and are not complete, thus lowering recall. On the other hand, UnifiedQA-v2 shows a strong tendency to provide the answer ``yes'' instead of ``no'', thus increasing recall (see Table~\ref{table-confusion-table} in appendix). This works particularly well on the MS MARCO dataset that is skewed towards positive questions (85\% positive, 15\% negative) and less so on SemEval which is balanced at around 50\%. The fact that the accuracy of BFS and our agent is higher on SemEval than on MS MARCO is mainly due to false positives. BFS and our agent default to a ``no'' answer when cause or effect cannot be linked to the causality graph, which leads to 21 false negatives on SemEval (out of 173 predictions) and 80 false negatives on MS MARCO (out of 263 predictions).

Comparing varying number of hops of our agent and the BFS, we can observe that additional hops increase recall while decreasing precision. The best trade-off in terms of $F_1$-score and accuracy is achieved for 4 hops on MS MARCO and 2 or 3 hops on SemEval. On SemEval, the precision of BFS drops from 0.937 in the 2-hop setting to 0.750 in the 3-hop setting due to the introduction of many false positives through inverse edges.%
\footnote{The results of BFS 3-Hop on SemEval are improved when not using inverse edges. However, using inverse edges improves the results for all other configurations. Thus, we included them in the graph as they also improve the performance of our agent, as shown in the ablation study in Section~\ref{subsec:ablation-study}.} In contrast, our agent mitigates this problem by pruning the search space and avoiding paths leading to wrong answers, still achieving a precision of 0.930. Compared to BFS, our agent has several advantages:
(1)~it prunes the search space and decreases the number of visited nodes by around 99\%,
(2)~it can avoid false positives introduced by inverse edges and errors in CauseNet as shown above,
(3)~it can be extended to open-ended causal questions as discussed in Section~\ref{sec:discussion}.

Moreover, as described in Section~\ref{subsec:experimental-setup}, we experimented with providing triples (UnifiedQA-v2-T) from CauseNet as additional context to the language model as well as providing paths found by our agent (UnifiedQA-v2-P). The results indicate that UnifiedQA-v2-T slightly outperforms the vanilla UnifiedQA-v2 without context as well as UnifiedQA-v2-T with triples. Adding context to GPT-v4 did hardly improve results.


\subsection{Ablation Study}
\label{subsec:ablation-study}

\input{tables/ablation-study}

In our ablation study in Table~\ref{table-ablation}, we investigate the performance impact of the components of our approach. We try out the following configurations:
(1)~without supervised learning, i.e., we run Algorithm~\ref{alg:algorithm} directly and train the policy and value network with 
policy gradients from scratch,
(2)~without Actor-Critic, we remove the critic and only run the 
REINFORCE algorithm,
(3)~we remove the beam search and use 
greedy decoding to only sample the most probable path,
(4)~without inverse edges in the graph,
(5)~without LSTM only using the two feedforward networks.

Overall, beam search has the biggest impact on performance. When beam search is exchanged for greedy decoding, the accuracy drops from 0.460 to 0.293 on MS MARCO and from 0.769 to 0.613 on SemEval. Notably, greedy decoding slightly increases the precision on MS MARCO and does reach a precision of 1.0 compared to the 0.943 of beam search on SemEval. Thus, the number of false positives decreases when only using the most probable path. Supervised learning has the second highest impact and we analyze it in more detail below. Next, the Actor-Critic algorithm only has a minor impact with a difference of around 0.02-0.03 points accuracy on both datasets. Similarly, the removal of inverse edges results in a slight decrease in overall performance but an increase in precision on the SemEval dataset to 1.0. That is because the removal of inverse edges reduces the probability of finding false positives, as discussed in Section~\ref{sec:discussion}. Using a feedforward network instead of an LSTM slightly decreases performance, too. We attribute this to the fact that a pure feedforward network can only encode a single node whereas an LSTM can capture a broader context of a node, namely the previously visited nodes on the path. In future work, inspired by \citet{Almasan2022DeepRL}, we would like to capture an even larger context of nodes (e.g., 1-hop or 2-hop neighborhood) by employing a graph neural network (GNN).

\input{figures/supervised-accuracy-full}


\subsection{Effects of Supervised Learning}
\label{subsec:effects-supervised}

We compare the performance of the agent when using different numbers of supervised training steps. Figure~\ref{figure-supervised} shows the accuracy of the agent on the SemEval~\cite{SharpCausalQAEmbeddings2016} test set depending on the number of reinforcement learning training steps. Each of the three runs was bootstrapped with a different number of supervised training steps. Thus, at step 0, we can see the accuracy directly after supervised learning without any training via reinforcement learning. We observe that the run with 100 steps is significantly worse than the runs with 200 and 300 steps. It starts at around 0.67 directly after supervised learning and increases to around 0.72. Whereas the difference between 200 to 300 steps is already a lot smaller. Both start between 0.72 and 0.73 and follow similar trajectories afterward to reach an accuracy of around 0.76 after 2000 reinforcement learning steps. To maintain the clarity of the figures, we did not include a run with 400 steps, but the trend of diminishing returns on the number of supervised steps continues. This suggests that increasing the number of supervised steps beyond 300 does not improve performance. Likewise, we observed similar results on the MS MARCO~\cite{Nguyen2016MSMARCO} dataset.


\input{figures/supervised-paths-entropy}

Moreover, Figure~\ref{figure-supervised-entropy} illustrates the number of unique paths explored during training on the left and the mean entropy of the action distribution of the policy network on the right. Notably, with an increasing number of supervised steps, the entropy of the policy network drops significantly. Hence, the number of explored paths during reinforcement learning also decreases as shown on the left in Figure~\ref{figure-supervised-entropy}. These findings indicate that supervised learning effectively establishes a strong foundation for the reinforcement learning agent. For example, an agent trained with 300 supervised steps only explores 21.6\% of the paths of an agent without any supervised steps at the start. Accordingly, the agent trained with 300 supervised steps can exploit the knowledge acquired during supervised learning to follow better paths. In contrast, the agent without any supervised learning steps requires more exploration and fails to achieve the same performance, as shown in Table~\ref{table-ablation}.

\label{subsec:examples}
