\newpage
\section{Introduction}

Causal question answering addresses the problem of determining the causal relations between given causes and effects~\cite{KayeshCausalTransfer2020, DalalCausalQAEnhancing2021}. This involves examining \emph{whether} a causal relation exists and \emph{how} causal relations can be explained in terms of intermediate steps. Examples of such questions include \textit{``Does pneumonia cause anemia?''} and \textit{``How does pneumonia cause death?''} Nowadays, the necessity to answer causal questions arises in various domains. For example, users often seek answers to causal questions from virtual assistants like Alexa or from search engines~\cite{Nguyen2016MSMARCO, Heindorf2020Causenet}. Reasoning via chains of causal relations is crucial for argumentation~\cite{Walton2007Dialog, Habernal2018Argumentation} and automated decision-making~\cite{HassanzadeshCausalQA2019, KayeshCausalTransfer2020, Heindorf2020Causenet}, too, e.g., to arrive at better answers and to gain a deeper understanding.

The literature started to introduce approaches for causal question answering~\cite{SharpCausalQAEmbeddings2016, HassanzadeshCausalQA2019, KayeshCausalTransfer2020, DalalCausalQAISWC2021}. However, they lack explanations and verifiability of their answers. Only recently, the introduction of CauseNet~\cite{Heindorf2020Causenet}, a large-scale knowledge graph (KG) with causal relations between noun phrases and with context information, provides new opportunities to build effective, verifiable causal question answering systems that we exploit in this work.

Inspired by the successful application of reinforcement learning to KGs on different tasks such as link prediction~\cite{Xiong2017DeePpath}, fact-checking~\cite{Das2018Minerva}, conversational question answering~\cite{Kaiser2021Reinforcement}, and multi-hop reasoning~\cite{Wan2021GaussianPath}, in this paper, we explore whether we can model the \emph{causal question answering task} as a sequential decision problem over a causality graph. We train a reinforcement learning agent that learns to walk over the graph to find good inference paths to answer binary causal questions. We implement the agent via the Synchronous Advantage Actor-Critic (A2C) algorithm~\cite{Mnih2016A2C} and use generalized advantage estimation (GAE)~\cite{Schulman2016GAE} to compute the advantage. To address the challenge of a large action space, we bootstrap the agent with a supervised learning procedure~\cite{Xiong2017DeePpath} where the agent receives expert demonstrations to understand what good paths look like.

We evaluate our approach both on causal questions from SemEval~\cite{Hendrickx2010SemEval} as well as a novel dataset constructed from the MS MARCO~\cite{Heindorf2020Causenet, Nguyen2016MSMARCO} dataset, which consists of questions asked to search engines. While the latter is skewed to questions with the answer ``yes'', the former is balanced and contains an equal number of questions that are to be answered with ``yes'' or ``no''. Our evaluation demonstrates that on both datasets, our agent can effectively prune the search space, considering only a small number of nodes per question---on average, less than 30 nodes per question. For comparison, a breadth-first search (BFS) visits over 3,000 nodes per question. Furthermore, our agent minimizes false positives achieving a precision of 0.89, whereas BFS achieves a precision of only 0.75 and the language model UnifiedQA~\cite{Khashabi2020UnifiedQA, Khashabi2022UnifiedQA2} only a precision of 0.5. Our experiments confirm that bootstrapping the agent via supervised learning establishes a strong foundation decreasing uncertainty and accelerating the learning process. The paths found by our agent can be used to explain the relations between cause and effect, including the option to report the original source of the causal relation~\cite{Heindorf2020Causenet}.

To summarize our contributions:
(1)~We introduce the first reinforcement learning approach for causal question answering on KGs;
(2)~we introduce a supervised learning procedure for causal question answering to handle the challenge of the large action space and sparse rewards and accelerate the learning process;
(3)~we introduce a new causal question dataset.
