\section{Limitations and Future Work}\label{sec:future_work}

There are several avenues for improving and extending our grokking-based approach to multi-hop reasoning. While our proof-of-concept experiments on 2WikiMultiHopQA provide promising evidence, there remain important open questions regarding data complexity, interpretability, and resource feasibility.

\paragraph{Datasets and Benchmarks.}
Our results demonstrate that Transformer grokking can be induced on real-world datasets such as 2WikiMultiHopQA. Nevertheless, a broader spectrum of \emph{challenging} reasoning benchmarks could illuminate the true scope and boundaries of our method. For instance, tasks requiring longer reasoning chains, specialized domain knowledge (e.g., biomedical), or \emph{temporal} reasoning may reveal nuanced constraints that do not emerge in standard Wikipedia-based QA.

\paragraph{Analysis and Explainability.}
Although we observe emergent generalization circuits, the precise \emph{mechanics} of how these circuits form remains only partially understood. Future work can:
\begin{itemize}
    \item \textbf{Quantify factual drift:} Investigate how adding synthetic (hallucinated) facts impacts the model’s factual consistency and other downstream metrics.
    \item \textbf{Mechanistic interpretability:} Extend the logit-lens or attention-probing analyses of \citet{wang_grokked_2024} to more complex, real-world tasks. Doing so may reveal how sub-networks handle shifting knowledge distributions -- particularly if a separate memory module is involved.
\end{itemize}

\paragraph{Factuality.}
A key question is how synthetic data (some of it intentionally or accidentally hallucinated) affects the model’s factual accuracy. While our experiments show that moderate amounts of non-factual data can \emph{bolster} generalization, we acknowledge potential risks:
\begin{itemize}
    \item \textbf{Distortion of real-world knowledge:} Without careful filtering, hallucinations might overwrite or obscure genuine facts.
    \item \textbf{Factual fragility:} Certain tasks (e.g., medical or legal reasoning) demand rigorous correctness, making any factual drift untenable.
\end{itemize}
As a partial solution, we envision more sophisticated \emph{constraint-based} data augmentation that preserves core factuality while still boosting the inferred-to-atomic ratio \(\phi\). Investigating such hybrid strategies is an intriguing direction for future work.

\paragraph{Scope.}
We expanded the scope from contrived toy problems to large-scale, factual datasets derived from Wikipedia. However, there remain many open questions:
\begin{itemize}
    \item \textbf{Non-Wikipedia Domains:} Would the same grokking dynamics hold in domain-specific corpora (e.g., arXiv papers, biomedical literature, or news articles)?
    \item \textbf{Other Reasoning Paradigms:} Beyond factual QA, it is unknown whether a generalizing circuit would also yield improvements on commonsense or moral reasoning tasks, where the inference rules are less formally grounded.
\end{itemize}

\paragraph{Feasibility.}
Finally, we note that training large Transformer architectures for extended periods, as required by grokking, can be prohibitively expensive. Techniques to reduce this overhead, such as those described by \citet{lee_grokfast_2024}, are essential. Concretely, future work might explore:
\begin{itemize}
    \item \textbf{Scaling Laws:} Determining how model size, dataset size, and ratio \(\phi\) collectively influence training cost.
    \item \textbf{Accelerated Convergence:} Applying curriculum learning or specialized optimizers that shorten the “memorization phase” and expedite the onset of generalization.
    \item \textbf{Pre-training:} Pre-trained models can facilitate grokking by leveraging prior knowledge, improving performance, and accelerating the transition from memorization to generalization. Since they already encode fundamental patterns (e.g., linguistic or mathematical rules), they might require less training time to achieve generalization.
\end{itemize}

\vspace{0.5em}
\noindent
In summary, while we establish the efficacy of grokking for multi-hop factual QA, there is ample room to refine, extend, and \textbf{better explain} these emergent capabilities. We hope our work can serve as a foundation for future explorations into more powerful, transparent, and efficient forms of implicit reasoning in large language models.
