% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
%
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{pgfplots}
\usepackage{makecell}
\usepackage{multirow}
\usepackage{bbm}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{adjustbox}
% \usepackage{marvosym}

\pgfplotsset{compat=1.18}

\usepackage[misc]{ifsym}
\pagenumbering{gobble}

%
\begin{document}
%
\title{Harnessing Diverse Perspectives: A Multi-Agent Framework for Enhanced Error Detection in Knowledge Graphs}
%
\titlerunning{A Multi-Agent Framework for Enhanced Error Detection in KGs}
%
\author{Yu Li\inst{1}\and
Yi Huang\inst{2} \textsuperscript{(\Letter)} \and
Guilin Qi\inst{1} \textsuperscript{(\Letter)} \and
Junlan Feng\inst{2} \and
Nan Hu\inst{1} \and
Songlin Zhai\inst{1} \and \\
Haohan Xue\inst{1} \and
Yongrui Chen\inst{1} \and
Ruoyan Shen\inst{1} \and
Tongtong Wu\inst{3}}
%
\authorrunning{Y. Li et al.}
%
\institute{Southeast University, Nanjing, China\\
\email{\{yuli\_11, gqi, nanhu, songlin\_zhai, thex1ay, yongruichen, ry\_shen\}@seu.edu.cn}\\
\and
China Mobile Research Institute, China\\
\email{\{huangyi, fengjunlan\}@chinamobile.com}
\and
Monash University, Australia\\
\email{tongtong.wu@monash.edu}
}
%

\maketitle             
%
\setcounter{footnote}{0}
\begin{abstract}
Knowledge graphs are widely used in industrial applications, making error detection crucial for ensuring the reliability of downstream applications. 
% 
Existing error detection methods often fail to effectively utilize fine-grained subgraph information and rely solely on fixed graph structures, while also lacking transparency in their decision-making processes, which results in suboptimal detection performance.
% 
In this paper, we propose a novel Multi-Agent framework for Knowledge Graph Error Detection (MAKGED) that utilizes multiple large language models (LLMs) in a collaborative setting. 
% 
By concatenating fine-grained, bidirectional subgraph embeddings with LLM-based query embeddings during training, our framework integrates these representations to produce four specialized agents. These agents utilize subgraph information from different dimensions to engage in multi-round discussions, thereby improving error detection accuracy and ensuring a transparent decision-making process.
%
Extensive experiments on FB15K and WN18RR demonstrate that MAKGED outperforms state-of-the-art methods, enhancing the accuracy and robustness of KG evaluation. 
For specific industrial scenarios, our framework can facilitate the training of specialized agents using domain-specific knowledge graphs for error detection, which highlights the potential industrial application value of our framework.
Our code and datasets are available at \url{https://github.com/kse-ElEvEn/MAKGED}.
% \footnote{This research was funded by Southeast University-China Mobile Research Institute Joint Innovation Center }.

\keywords{Large Language Models  \and Knowledge Graph \and Multi-Agent}
\end{abstract}
%

\input{section/introduction}

\input{section/related_work}

\input{section/problem_statement}

\input{section/method}

\input{section/experiment}

\input{section/conclusion}

\section{Acknowledgments}
This work is partially supported by National Nature Science Foundation of China under No. U21A20488, and is funded by Southeast University-China Mobile Research Institute Joint Innovation Center. We thank the Big Data Computing Center of Southeast University for providing the facility support on the numerical calculations in this paper.

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{reference}
%

\end{document}
