Large language models (LLMs)~\citep{qwen2025qwen25technicalreport,guo2025deepseek,comanici2025gemini} have achieved remarkable success across a wide range of natural language processing tasks.
However, they often suffer from hallucination, generating plausible yet factually incorrect outputs, in knowledge-intensive settings.
Retrieval-augmented generation (RAG) addresses this limitation by generating outputs using external knowledge sources.
Beyond conventional RAG over unstructured text chunks, GraphRAG~\citep{luo2025graph,sun2023thinkongraph,luo2025hypergraphrag} organizes knowledge as entity--relation graphs, enabling retrieval over structured evidence and supporting multi-hop reasoning across interconnected facts.

Recently, reinforcement learning~(RL)-based agentic GraphRAG frameworks~\citep{luo2025graph} have been proposed to enable LLMs to iteratively interact with the knowledge graph over multiple steps, retrieve evidence, and refine their reasoning trajectories to arrive at final answers.
However, existing RL-based agentic GraphRAG frameworks still exhibit a fundamental mismatch between graph-structured reasoning and the way retrieval and learning are actually carried out.
In retrieval, they largely rely on contextual similarity, retrieving evidence that appears semantically relevant to the question but may fail to capture the relational structure required for multi-hop graph reasoning.
In post-training, they are typically optimized with sparse outcome-level rewards, which provide supervision only at the end of a trajectory, determined solely by whether the final answer is correct.
Such delayed feedback makes credit assignment difficult and limits effective learning in complex multi-step retrieval settings.
These two issues are tightly coupled: when retrieval is not structure-aware, the agent is more likely to explore noisy or disconnected evidence trajectories and under sparse final rewards, it receives little signal about why such a trajectory failed or which retrieval step is responsible, making it difficult to learn policies that progressively construct coherent reasoning paths. 
In other words, effective agentic GraphRAG requires not only retrieving evidence that is relevant, but retrieving evidence that is \emph{structurally supportive} of downstream reasoning, and not only rewarding final correctness, but rewarding intermediate decisions based on how much they contribute to reasoning progress.
As a result, existing RL-based GraphRAG remains only weakly aligned with the compositional and relational nature of graph-grounded reasoning.


To address these limitations, we propose \textbf{HyperGraphPro}, a progress-aware reinforcement learning framework for multi-turn graph retrieval-augmented generation in multi-hop knowledge-intensive tasks.
Our HyperGraphPro consists of two key components: structure-guided retrieval and progress-based stepwise policy optimization.
First, we introduce a \textbf{structure-guided hypergraph retrieval} mechanism, which jointly leverages semantic relevance and structural proximity in the knowledge graph to retrieve subgraphs that are not only contextually relevant but also structurally coherent.
Second, we present a \textbf{progress-based stepwise policy optimization} strategy, which provides dense supervision over intermediate reasoning steps by assessing the action of each step according to its contribution to reasoning progress, rather than relying solely on the correctness of the final answer.
Together, these components align both retrieval and policy learning with the compositional nature of graph-based reasoning.


We evaluate HyperGraphPro on multiple knowledge-intensive question answering benchmarks and show that it consistently outperforms both conventional GraphRAG methods and RL-based agentic baselines.
These results demonstrate the importance of incorporating graph structure into retrieval and of providing step-level learning signals for multi-step reasoning over graph-based knowledge.

Our contributions are threefold:
\begin{itemize}
    \item We propose a \textbf{structure-guided hypergraph retrieval}, which jointly exploits semantic relevance and hypergraph structural proximity for improved subgraph retrieval in multi-hop question answering.
    \item We introduce a \textbf{progress-aware stepwise optimization}, a dense supervision strategy that assesses each retrieval action based on the contribution to reaching the final answer and connectivity between reasoning steps.
    \item We demonstrate that \textbf{HyperGraphPro} achieves the best performance among GraphRAG and RL-based agentic frameworks on multi-hop question answering benchmarks.
\end{itemize}