% ============================================================
\section{Case Study}
\label{app:case_study}
% ============================================================

We present several examples illustrating how \system's
calibration prevents memory corruption that baselines
fail to catch.

\textbf{Case 1: HotpotQA (MemBank + MacNet).}
The task asks: \emph{``Were the directors of `Jaws'
and `E.T.' born in the same city?''}  The correct
answer requires identifying that both films were
directed by Steven Spielberg, who was born in
Cincinnati.

\begin{tcolorbox}[colback=gray!5, colframe=gray!60,
  title={\small Round 2: Contributor $a_3$ proposes
  $\Delta_t$}, fonttitle=\bfseries\small,
  boxrule=0.4pt, arc=1.5mm]
\small
\texttt{memory\_entry}: ``The director of Jaws is
Steven Spielberg (born in Cincinnati). The director
of E.T. is \textbf{Tobe Hooper} (born in Austin).
Therefore, they were born in different cities.''
\end{tcolorbox}

\noindent
Agent $a_3$ hallucinates the director of E.T.\
as Tobe Hooper (who directed \emph{Poltergeist}, a
common confusion).  The entry is fluent and
well-structured.

\begin{tcolorbox}[colback=blue!3, colframe=blue!40,
  title={\small \system\ calibration},
  fonttitle=\bfseries\small, boxrule=0.4pt,
  arc=1.5mm]
\small
\textbf{$\rho_{\text{detect}}$}: The embedding of
$\Delta_t$ lands in a dense region near existing
Spielberg entries, yielding $\hat{r}_k / \bar{r} =
1.42$ (above threshold) $\Rightarrow$
$\rho_{\text{detect}} = 0.31$.\\[3pt]
\textbf{$\rho_{\text{align}}$}: Auditor $a_1$'s
intercepted query \texttt{``director of E.T.''}
retrieves \texttt{``Steven Spielberg directed E.T.
(1982)''} from $\mathcal{M}_t$. After merging
$\Delta_t$, the top-1 result flips to the
hallucinated entry, giving $d_{\text{RBO}} = 0.87$
$\Rightarrow$ $\rho_{\text{align}} = 0.18$.\\[3pt]
\textbf{Composite}: $\rho = \sqrt{0.31 \times 0.18}
= 0.24 < \rho^* = 0.52$. \textbf{Rejected.}
\end{tcolorbox}

\begin{tcolorbox}[colback=red!3, colframe=red!40,
  title={\small Baseline failures},
  fonttitle=\bfseries\small, boxrule=0.4pt,
  arc=1.5mm]
\small
\textbf{LLM Audit}: The auxiliary LLM scores the
entry as plausible (Tobe Hooper is a real director;
the sentence is grammatically correct and
well-reasoned). Score: 0.78 $\Rightarrow$
\textbf{Committed.}  Subsequent agents retrieve the
false entry and answer ``different cities.''\\[3pt]
\textbf{PPL Filter}: Perplexity of the entry is 12.3,
well below the adaptive threshold of 18.5 (the entry
uses common vocabulary and natural syntax).
$\Rightarrow$ \textbf{Committed.}  Same downstream
error.
\end{tcolorbox}

\noindent
\textbf{Why \system\ succeeds.}  The hallucinated
entry is locally plausible: it names a real director,
uses correct grammar, and provides a coherent
reasoning chain.  LLM Audit and PPL Filter, which
evaluate entries in isolation, cannot detect the
error.  \system\ catches it through
$\rho_{\text{align}}$: the entry contradicts existing
evidence in $\mathcal{M}_t$ (``Spielberg directed
E.T.''), causing a large retrieval disruption when
an auditor's intercepted query surfaces the conflict.
The geometric mean $\sqrt{\rho_{\text{detect}} \cdot
\rho_{\text{align}}}$ ensures the entry is rejected
even though $\rho_{\text{detect}}$ alone ($0.31$) is
ambiguous.

\textbf{Case 2: ALFWorld (G-Memory + MacNet).}
The task is: \emph{``Put a hot mug in the cabinet.''}
The correct action sequence is: find mug $\to$ pick
up mug $\to$ go to microwave $\to$ heat mug $\to$ go
to cabinet $\to$ put mug in cabinet.

\begin{tcolorbox}[colback=gray!5, colframe=gray!60,
  title={\small Round 4: Contributor $a_5$ proposes
  $\Delta_t$ (3 new edges)}, fonttitle=\bfseries\small,
  boxrule=0.4pt, arc=1.5mm]
\small
\texttt{edge\_1}: (\texttt{mug\_1}, \texttt{located\_in},
\texttt{cabinet\_2})\\
\texttt{edge\_2}: (\texttt{mug\_1}, \texttt{state},
\texttt{hot})\\
\texttt{edge\_3}: (\texttt{cabinet\_2},
\texttt{contains}, \texttt{mug\_1})
\end{tcolorbox}

\noindent
Agent $a_5$ prematurely commits the goal state to
memory \emph{before} executing the heating step.
At this point in the episode, the mug has been picked
up but not yet heated: the agent skipped the
microwave step due to a planning error.

\begin{tcolorbox}[colback=blue!3, colframe=blue!40,
  title={\small \system\ calibration},
  fonttitle=\bfseries\small, boxrule=0.4pt,
  arc=1.5mm]
\small
\textbf{$s_{\text{local}}$(edge\_2)}: The node
\texttt{mug\_1} has existing edges
\texttt{(mug\_1, state, picked\_up)} and
\texttt{(mug\_1, located\_in, countertop\_1)}.
Adding \texttt{(mug\_1, state, hot)} requires a
\texttt{heat} action edge, which is absent
$\Rightarrow$ $s_{\text{local}} = 0.12$.\\[3pt]
\textbf{$s_{\text{path}}$(edge\_1)}: BFS from
\texttt{mug\_1} to \texttt{cabinet\_2} finds no
existing path (the mug is currently on the
countertop, not near any cabinet) $\Rightarrow$
$s_{\text{path}} = 0.0$.\\[3pt]
\textbf{$\rho_{\text{detect}}$}: $\alpha_t \cdot
0.12 + (1 - \alpha_t) \cdot 0.0 = 0.05$.\\[3pt]
\textbf{$\rho_{\text{align}}$}: Auditor $a_2$ is
walking path \texttt{countertop\_1 $\to$ mug\_1 $\to$
picked\_up}. The sampled edge \texttt{edge\_1}
(\texttt{mug\_1 $\to$ cabinet\_2}) is not reachable
from $a_2$'s path endpoints via compatible
relations $\Rightarrow$ $\rho_{\text{align}} = 0.21$.\\[3pt]
\textbf{Composite}: $\rho = \sqrt{0.05 \times 0.21}
= 0.10 < \rho^* = 0.48$. \textbf{Rejected.}
\end{tcolorbox}

\begin{tcolorbox}[colback=red!3, colframe=red!40,
  title={\small Baseline failure},
  fonttitle=\bfseries\small, boxrule=0.4pt,
  arc=1.5mm]
\small
\textbf{PPL Filter}: All three edges use standard
relation types and entity names. Perplexity of the
serialised edge text is 8.1 (below threshold 15.2).
$\Rightarrow$ \textbf{All three edges committed.}\\[3pt]
\textbf{Downstream effect}: Agents $a_1$--$a_4$ in
subsequent rounds retrieve \texttt{(mug\_1, state,
hot)} and \texttt{(mug\_1, located\_in, cabinet\_2)},
concluding the task is already complete.  The episode
terminates with \texttt{score = 0} because the mug
was never actually heated.
\end{tcolorbox}

\noindent
\textbf{Why \system\ succeeds.}  The premature goal
state is \emph{locally valid}, wherein each edge uses
correct entity names and relation types, and the
serialised text has low perplexity.  PPL Filter
passes all three edges.  \system\ catches the error
through two complementary signals.  First,
$s_{\text{local}}$ detects that the \texttt{state:
hot} edge lacks a prerequisite \texttt{heat} action
in \texttt{mug\_1}'s neighborhood.  Second,
$s_{\text{path}}$ finds no existing path from
\texttt{mug\_1} to \texttt{cabinet\_2}, revealing
that the agent has not navigated to the cabinet.
The combination produces $\rho = 0.10$, far below
$\rho^*$, preventing the premature commit from
corrupting downstream agents' planning.

\textbf{Case 3: LoCoMo (MemBank + MacNet).}
The task asks: \emph{``Where does Alice work now?''}
based on a long conversation where session~3 mentions
``Alice moved to Boston in March'' and session~7
mentions ``Alice started a new job at a tech company
in April.''  The correct answer is Boston.

\begin{tcolorbox}[colback=gray!5, colframe=gray!60,
  title={\small Round 3: Contributor $a_2$ proposes
  $\Delta_t$ with high confidence},
  fonttitle=\bfseries\small, boxrule=0.4pt,
  arc=1.5mm]
\small
\texttt{memory\_entry}: ``Based on my analysis, Alice
currently works in \textbf{San Francisco}.  Many tech
companies are headquartered in San Francisco, and
Alice started a new job at a tech company, so this is
the most likely location.  \textbf{Confidence: very
high.}''
\end{tcolorbox}

\noindent
Agent $a_2$ fabricates a plausible-sounding inference
from its pre-trained parametric bias (``tech company''
$\to$ ``San Francisco'').  The entry explicitly
asserts high confidence, which influences other
agents.

\begin{tcolorbox}[colback=gray!5, colframe=gray!60,
  title={\small Auditor behaviour: sycophantic
  agreement}, fonttitle=\bfseries\small,
  boxrule=0.4pt, arc=1.5mm]
\small
\textbf{Auditor $a_1$}: Has previously retrieved
``Alice moved to Boston'' but does not raise a
conflict.  Its intercepted query is
\texttt{``Alice job location''}.\\[3pt]
\textbf{Auditors $a_3$--$a_5$}: Have no strong prior
about Alice's location.  Their intercepted queries
are generic: \texttt{``Alice new job''},
\texttt{``Alice work''},
\texttt{``Alice tech company''}.\\[3pt]
\textbf{Result}: No auditor explicitly challenges
$a_2$'s assertion.  Under a vote-based system,
$\Delta_t$ would be committed unanimously.
\end{tcolorbox}

\begin{tcolorbox}[colback=blue!3, colframe=blue!40,
  title={\small \system\ calibration},
  fonttitle=\bfseries\small, boxrule=0.4pt,
  arc=1.5mm]
\small
\textbf{$\rho_{\text{detect}}$}: The embedding of
``Alice works in San Francisco'' has moderate density
in the memory manifold (tech/job entries are common)
$\Rightarrow$ $\rho_{\text{detect}} = 0.61$.\\[3pt]
\textbf{$\rho_{\text{align}}$}: \system\ samples
$a_1$'s intercepted query \texttt{``Alice job
location''} and computes top-$k$ retrieval before and
after merging $\Delta_t$.
\emph{Before}: top-1 is \texttt{``Alice moved to
Boston in March''}.
\emph{After}: top-1 flips to \texttt{``Alice works in
San Francisco''}, displacing the Boston entry.
$d_{\text{RBO}} = 0.82$.\\
For $a_3$'s query \texttt{``Alice new job''}: top-1
was \texttt{``Alice started a new job at a tech
company in April''}, which does not mention a city.
After merging, top-1 becomes the San Francisco entry.
$d_{\text{RBO}} = 0.71$.\\[3pt]
Weighted average: $\rho_{\text{align}} = 1 - 0.74 =
0.26$.\\[3pt]
\textbf{Composite}: $\rho = \sqrt{0.61 \times 0.26}
= 0.40 < \rho^* = 0.51$. \textbf{Rejected.}
\end{tcolorbox}

\begin{tcolorbox}[colback=red!3, colframe=red!40,
  title={\small Why baselines fail},
  fonttitle=\bfseries\small, boxrule=0.4pt,
  arc=1.5mm]
\small
\textbf{LLM Audit}: The auxiliary LLM reads
``tech company $\to$ San Francisco'' as a plausible
inference.  The entry is well-structured, confident,
and factually coherent in isolation.  Score: 0.81
$\Rightarrow$ \textbf{Committed.}\\[3pt]
\textbf{PPL Filter}: Perplexity is 9.7 (well below
threshold 17.3).  The entry uses common vocabulary
and natural reasoning patterns.  $\Rightarrow$
\textbf{Committed.}\\[3pt]
\textbf{Vote-based audit}: All five auditors would
approve---$a_1$ defers to $a_2$'s stated confidence
despite holding conflicting evidence, and
$a_3$--$a_5$ have no basis to disagree.
$\Rightarrow$ \textbf{Committed unanimously.}
\end{tcolorbox}

\noindent
\textbf{Why \system\ succeeds.}
This case illustrates the core failure mode that
\system\ is designed to prevent: a confident
contributor overwhelms uncertain or sycophantic
auditors, and the erroneous entry passes any
vote-based or isolated check.  \system\ bypasses
this failure entirely because it \emph{never uses
auditor votes}.  Instead, it intercepts $a_1$'s
query \texttt{``Alice job location''} and
\emph{independently} measures how $\Delta_t$
disrupts retrieval.  The key signal is that $a_1$'s
existing top-$k$ already contains ``Alice moved to
Boston''---a direct contradiction that $\Delta_t$
displaces.  This contradiction is invisible to
LLM~Audit (which never sees $\mathcal{M}_t$),
invisible to PPL~Filter (which only checks surface
statistics), and invisible to vote-based schemes
(because $a_1$ chose not to raise it).  \system's
$\rho_{\text{align}}$ detects it structurally:
high $d_{\text{RBO}}$ on $a_1$'s query means the
proposed entry overwrites existing evidence, which
is precisely the manipulation pattern the zero-trust
game is designed to catch
(Section~\ref{ssec:equilibrium}).