% This must be in the first 5 lines to tell arXiv to use pdfLaTeX, which is strongly recommended.
\pdfoutput=1
% In particular, the hyperref package requires pdfLaTeX in order to break URLs across lines.

\documentclass[11pt]{article}

% Change "review" to "final" to generate the final (sometimes called camera-ready) version.
% Change to "preprint" to generate a non-anonymous version with page numbers.
\usepackage[final]{acl}

% Standard package includes
\usepackage{times}
\usepackage{latexsym}

% For proper rendering and hyphenation of words containing Latin characters (including in bib files)
\usepackage[T1]{fontenc}
% For Vietnamese characters
% \usepackage[T5]{fontenc}
% See https://www.latex-project.org/help/documentation/encguide.pdf for other character sets

% This assumes your files are encoded as UTF8
\usepackage[utf8]{inputenc}

% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

% This is also not strictly necessary, and may be commented out.
% However, it will improve the aesthetics of text in
% the typewriter font.
\usepackage{inconsolata}

%Including images in your LaTeX document requires adding
%additional package(s)
\usepackage{multirow}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{bbm}
\usepackage{graphicx}
\usepackage{float}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{mathrsfs}
\renewcommand{\algorithmiccomment}[1]{\hfill $\triangleright$ #1}

% If the title and author information does not fit in the area allocated, uncomment the following
%
%\setlength\titlebox{<dim>}
%
% and set <dim> to something 5cm or larger.

\title{CortexDebate: Debating Sparsely and Equally for Multi-Agent Debate}

% Author information can be set in various styles:
% For several authors from the same institution:
% \author{Author 1 \and ... \and Author n \\
%         Address line \\ ... \\ Address line}
% if the names do not fit well on one line use
%         Author 1 \\ {\bf Author 2} \\ ... \\ {\bf Author n} \\
% For authors from different institutions:
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \And  ... \And
%         Author n \\ Address line \\ ... \\ Address line}
% To start a separate ``row'' of authors use \AND, as in
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \AND
%         Author 2 \\ Address line \\ ... \\ Address line \And
%         Author 3 \\ Address line \\ ... \\ Address line}

% \author{First Author \\
%   Affiliation / Address line 1 \\
%   Affiliation / Address line 2 \\
%   Affiliation / Address line 3 \\
%   \texttt{email@domain} \\\And
%   Second Author \\
%   Affiliation / Address line 1 \\
%   Affiliation / Address line 2 \\
%   Affiliation / Address line 3 \\
%   \texttt{email@domain} \\}

\author{
 \textbf{Yiliu Sun\textsuperscript{1}},
 \textbf{Zicheng Zhao\textsuperscript{1}},
 \textbf{Sheng Wan\textsuperscript{2*}},
 \textbf{Chen Gong\textsuperscript{3*}}
\\
 \textsuperscript{1}School of Computer Science and Engineering, Nanjing University of Science and \\Technology, Nanjing, China.
 \\
 \textsuperscript{2}College of Artificial Intelligence, Nanjing Agricultural University, Nanjing, China.
\\
\textsuperscript{3}School of Automation and Intelligent Sensing, Shanghai Jiao Tong University, \\Shanghai, China.
\\
 \small{
   \textbf{Correspondence:} \href{wansheng315@hotmail.com}{wansheng315@hotmail.com}; \href{chen.gong@sjtu.edu.cn}{chen.gong@sjtu.edu.cn}.
 }
}

\newcommand{\ZC}[1]{\textcolor{cyan}{ZC: #1}}
\newcommand{\WS}[1]{\textcolor{red}{WS: #1}}

\begin{document}
\maketitle
\begin{abstract}
    Nowadays, single Large Language Model (LLM) struggles with critical issues such as hallucination and inadequate reasoning abilities. To mitigate these issues, Multi-Agent Debate (MAD) has emerged as an effective strategy, where LLM agents engage in in-depth debates with others on tasks. However, existing MAD methods face two major issues: (a) \textit{too lengthy input contexts}, which causes LLM agents to get lost in plenty of input information and experiences performance drop; and (b) \textit{the overconfidence dilemma}, where self-assured LLM agents dominate the debate, leading to low debating effectiveness. To address these limitations, we propose a novel MAD method called ``CortexDebate''. Inspired by the human brain's tendency to establish a sparse and dynamically optimized network among cortical areas governed by white matter, CortexDebate constructs a sparse debating graph among LLM agents, where each LLM agent only debates with the ones that are helpful to it. To optimize the graph, we propose a module named McKinsey-based Debate Matter (MDM), which acts as an artificial analog to white matter. By integrating the McKinsey Trust Formula, a well-established measure of trustworthiness from sociology, MDM enables credible evaluations that guide graph optimization. The effectiveness of our CortexDebate has been well demonstrated by extensive experimental results across eight datasets from four task types.
\end{abstract}


\input{introduction}
\input{related_work}
\input{preliminaries}
\input{approach}
\input{experiments}
\input{conclusion}
\input{limitations}

% \section{Document Body}

% \subsection{Footnotes}

% Footnotes are inserted with the \verb|\footnote| command.\footnote{This is a footnote.}

% Bibliography entries for the entire Anthology, followed by custom entries
%\bibliography{anthology,custom}
% Custom bibliography entries only
\bibliography{custom}

\appendix

\input{appendix/appendix_dataset_detail}
\input{appendix/supplementary_results}
\input{appendix/additional_experiment}
\input{appendix/performance_investigation}
\input{appendix/evaluation_strategy}
\input{appendix/cortexdebate_prompt}
\input{appendix/appendix_baseline_introduction}
\input{appendix/algorithm}

\end{document}
