\input{Tables/main_table}
\input{Tables/komodis_table}

\input{Tables/retrieval_table}
\input{Tables/supp_human_eval}
\input{Tables/ablation}
\input{Tables/llama_table}

In this section, we evaluate the effectiveness of the proposed DialogGSR on knowledge graph{\textendash}grounded dialog generation.
We first introduce the two datasets~(OpenDialKG~\cite{moon2019opendialkg} and KOMODIS~\cite{galetzka2020corpus}), and the experimental setup and metrics.
Then, we demonstrate the effectiveness of DialogGSR on the two benchmark datasets.
Lastly, we provide ablation studies, and analyses of our DialogGSR. 

\subsection{Datasets}
% \label{supp:datasets}
\textbf{OpenDialKG} is an open-domain dialog dataset, which consists of 15K dialogs with 91K turns and 1.12M triplets from Freebase knowledge graph~\cite{bast2014easy}.
The knowledge graph has 1,190,658 triplets, 100,813 entities, and 1,358 relations.
There are 49\% of the turns having gold knowledge triplets.
Following \cite{galetzka2020corpus}, we randomly split the samples into train~(70\%), validation~(15\%), and test~(15\%) sets.
We evaluate the response generation and retrieval performance of our DialogGSR with other baselines using OpenDialKG dataset.

\noindent\textbf{KOMODIS} is a closed-domain dialog dataset that consists of 7.5k dialogs with 103k turns and the corresponding KG, which contains 88K triplets.
Following \cite{moon2019opendialkg,kang2022knowledge,galetzka2020corpus}, we randomly split the dialogs into train~(70\%), validation~(15\%), and test~(15\%) sets for KOMODIS dataset, too.
With KOMODIS dataset, we evaluate the response generation performance of our DialogGSR with other baselines following \cite{kang2022knowledge,galetzka2021space}.