








\section{DISTANCE-THRESHOLD COLLISIONS}
\label{sec:packing}

Our analysis has centered on a partition-based collision model, a useful abstraction for systems with predefined operational zones. This section demonstrates the modularity of our framework by showing how it naturally extends to a more physically-motivated model where collisions are governed by proximity. 

In the distance-threshold model, a collision occurs if any two players' actions $X_t^{(j)}$ and $X_t^{(j')}$ are within a distance $\rho > 0$ of each other. To handle this, we reduce the problem to our existing framework. We first discretize the space $\X$ into a set of ``safe centers" $\{z_1, \dots, z_M\}$ that form an $r$-packing with $r > \rho$. We then associate each center $z_i$ with a ``safe ball" $B_i$ of radius $\sigma < (r-\rho)/2$. By construction, any two points chosen from two different safe balls are guaranteed to be separated by a distance greater than $\rho$, making inter-ball collisions impossible.

Our entire multi-phase protocol (Phase I - III) can then be applied directly, treating the family of safe balls $\{B_i\}$ as if they were the cells of the partition. Players identify, seat themselves upon, and perform optimization within these balls. The performance guarantees translate directly, with regret measured against the optimal assignment to these safe balls, $\OPT_{\pack}(r,\sigma,N)$.

\begin{theorem}[Regret in the Distance-Threshold Model]
\label{thm:packing}
When applied to a set of safe balls derived from an $r$-packing, our protocol's expected total regret is bounded by an expression identical in form to that in Theorem \ref{thm:global}, with the partition parameters $(K, h)$ replaced by the packing parameters $(M, \sigma)$.
\end{theorem}

\section{A MINIMAX LOWER BOUND}
\label{sec:lower}

Having established upper bounds for the regimes above, we now record a lower bound on the unavoidable horizon dependence. The following result shows that no decentralized algorithm can improve on the single-player exponent $T^{(d+1)/(d+2)}$. In particular, it matches the dominant $T$-dependence attained by our upper bound in the consensus regime, showing that decentralization and collisions do not worsen the core statistical difficulty of the problem.

\begin{theorem}[Minimax Lower Bound]
\label{thm:lower}
For the decentralized multi-player bandit problem in a partition-based collision model, for any decentralized algorithm, there exists an $L$-Lipschitz mean-reward function such that the expected regret is bounded below by:
\[
\EE[R_{\cont}(T)] \ge c \cdot N (Lh)^{\frac{d}{d+2}} T^{\frac{d+1}{d+2}},
\]
where $c$ is a constant depending only on dimension $d$.
\end{theorem}

The proof relies on a standard reduction from the well-established lower bound for finite-armed bandits \citep{lattimore2020bandit,bubeck2012regret}. We construct a challenging reward function that embeds $N$ independent, hard, finite-armed bandit problems into $N$ disjoint cells.










\section{CONCLUSION}
\label{sec:conclusion}
We have introduced and provided the first end-to-end solution for the cooperative, decentralized multi-player stochastic bandit problem in continuous domains with hard collisions. Our central contribution is a modular, multi-phase protocol that requires no communication between players. The key insight is to decouple the problem into a horizon-independent coordination stage and a horizon-dependent learning stage. A crucial innovation is our maxima-directed identification phase, which performs a localized search to avoid systemic biases inherent in simpler center-based discretizations. Our analysis culminates in a near-optimal, gap-free regret bound of $\tilde{O}(T^{(d+1)/(d+2)})$, which matches the single-player minimax rate for Lipschitz bandits in the consensus regime. Our analysis assumes a fixed known number of synchronous players and a common known upper bound on the Lipschitz constant. Extending the framework to unknown smoothness, asynchronous starts, changing player populations, or delayed feedback remains an interesting direction for future work.
