\section{END-TO-END REGRET GUARANTEES}
\label{sec:global_guarantees}

With the components of our multi-phase protocol established, we combine them to get end-to-end performance guarantees. Our main result is that the significant upfront cost of decentralized coordination is carefully managed to ensure that the long-term performance is dictated by the optimal rate of single-agent learning. We build to this conclusion by first presenting a clean result for well-separated problem instances, and then stating our main guarantee that holds for any instance.

\subsection{Global Regret Under a Reward Gap}

Our first result quantifies the performance of the protocol in an ideal setting where the top-$N$ cells are clearly better than the rest. This scenario is formalized by the $\varepsilon$-uniqueness condition (Definition \ref{def:eps-uniq}), which assumes a sufficiently large ``reward gap" between the $N$-th best cell and the $(N+1)$-th best cell. When this gap exists, Phase II is guaranteed to lead to consensus, where all players identify the exact same set of top-$N$ cells. This allows for a seamless transition into seating and optimization.


\begin{theorem}[Global Regret with Consensus]
\label{thm:global}
Assume the $\varepsilon$-uniqueness condition holds (i.e., a sufficient reward gap exists). For any horizon $T$, the expected total regret is bounded by:
\begin{equation}
\label{eq:global-regret-bound}
\begin{aligned}
\EE[R_{cont}(T)] &\le \underbrace{N(T_0 + T_1) + c_{MC}N^2}_{\text{Coordination Cost}} \\
&\quad + \underbrace{c_d N (Lh)^{\frac{d}{d+2}} T^{\frac{d+1}{d+2}}}_{\text{Learning Cost}} + \delta_{sys}T,
\end{aligned}
\end{equation}
where $c_{MC}$ and $c_d$ are universal constants.
\end{theorem}

The theorem isolates the architecture of the protocol: an upfront coordination term followed by the standard single-player Lipschitz learning term. When \(\delta_{sys}\) is treated as a fixed confidence parameter, \(T_0\) and \(T_1\) are independent of \(T\). If one instead chooses \(\delta_{sys}=\delta_{sys}(T)\) to make the failure contribution \(\delta_{sys}T\) negligible in expectation, then the Phase~I/II radii inherit only extra logarithmic dependence on \(T\); equivalently, the coordination term becomes polylogarithmic in \(T\) rather than strictly horizon-independent. See Appendix~F, Remark (i) for details.




\subsection{A Gap-Free Guarantee}

The true strength of a decentralized protocol lies in its ability to perform well without favorable structural assumptions. A natural and challenging scenario arises when the reward gap is small or even zero, making the top-$N$ cells statistically indistinguishable from the next best. In this ``gap-free" setting, consensus is no longer guaranteed; different players might identify slightly different (but still high-quality) sets of target cells.

Our main result shows that our algorithm is robust to this challenge. This is achieved by running the protocol in epochs of doubling length ($T_k=2^k$), with the precision $\varepsilon_k$ recalibrated for each epoch. This standard ``doubling trick" \citep{cesa-bianchi2006prediction} allows the algorithm to control regret from potential sub-optimality without knowing the reward gaps or the horizon $T$ in advance. Our result relies on two additional ingredients, namely, public coverage/scheduling property together with a benign near-optimality-dimension condition. We state the resulting guarantee here and defer the formal assumptions and proof to Appendix~G. 

\begin{corollary}[Epochic, Gap-Free Global Regret]\label{cor:epochic-gapfree}
By running the multi-phase protocol in epochs, with precision $\varepsilon_k \propto 2^{-k/(d+2)}$ for epoch $k$, the algorithm achieves, for any $L$-Lipschitz reward function and any horizon $T$, an expected total regret of
\[
\EE[R_{\cont}(T)] \le \tilde{O}\left(N(Lh)^{\frac{d}{d+2}} T^{\frac{d+1}{d+2}}\right).
\]
\end{corollary}

Appendix~G also gives a fully gap-free single-shot baseline that holds without these additional assumptions, albeit with a weaker horizon exponent.

The above result demonstrates that by dynamically adapting the precision of the identification phases, our algorithm robustly achieves the minimax optimal regret rate without requiring any separation between the values of good and bad cells. The costs of repeated coordination in each epoch are controlled and are ultimately subsumed by the dominant learning cost.
