

\section{PHASE III: OPTIMIZATION WITHIN CELLS}
\label{sec:phase3}

With the completion of Phase II, the multi-agent coordination problem is solved. Each player is now the sole occupant of a distinct cell. For the remainder of the horizon, $T' = T - T_0 - T_1 - T_{MC}$, the problem decouples entirely into $N$ independent, single-player bandit problems. Collisions are no longer a concern, and each player's objective is simply to cultivate the maximum possible reward from within their own cell.

Each player must now solve a standard Lipschitz bandit problem over their assigned domain $C_j$. A provably near-optimal and standard approach for this task is an epoch-based, discretize-and-explore algorithm like Zooming \citep{Kleinberg}. In each epoch, they create a grid of points within their cell, with the grid resolution becoming finer over time.

The performance of such single-player strategies is well-established in the bandit literature \citep{bubeck2012regret,slivkins2019introduction}. The regret incurred by each player is known to follow the classical minimax rate for a $d$-dimensional Lipschitz problem.

\begin{proposition}[In-Cell Regret]
\label{prop:in-cell}
The expected regret for any player $j$ during the Phase III optimization within their cell $C_j$ over a duration of $T'$ rounds is bounded by:
\[
\EE\big[R_{\mathrm{in}}^{(C_j)}(T')\big] \;\le\; c_d\, (Lh)^{\frac{d}{d+2}} (T')^{\frac{d+1}{d+2}} + c'_d,
\]
where $c_d$ and $c'_d$ are constants that depend only on the dimension $d$.
\end{proposition}

The total regret from Phase III is the sum of these individual regrets across all $N$ players. This term represents the primary, horizon-dependent component of our overall regret bound. 
