\section{PRELIMINARIES} \label{sec:prelims}

We build upon three established areas in sequential decision-making: the stochastic multi-armed bandit problem, its extension to continuous arms via the Lipschitz assumption, and the multi-player variant with collisions. We briefly review each to establish notation and context.

\subsection{Stochastic Multi-Armed Bandits}
The canonical multi-armed bandit (MAB) problem involves a single player sequentially choosing from a set of $K$ discrete actions, or ``arms". At each time step $t$, the player selects an arm $i_t \in \{1, \dots, K\}$ and receives a stochastic reward drawn from an unknown distribution with mean $\mu_i$. The player's goal is to maximize the cumulative expected reward over a horizon $T$. Performance is measured by the cumulative regret, defined as the expected difference between the reward from always playing the single best arm and the reward accumulated by the player's policy:
\[
R(T) = T \cdot \mu^* - \sum_{t=1}^T \EE[\mu_{i_t}],
\]
where $\mu^* = \max_{i \in \{1,\dots,K\}} \mu_i$. Minimizing regret requires balancing the exploration of arms to learn their mean rewards with the exploitation of the arm that currently seems best.

\subsection{Lipschitz Bandits in Continuous Domains}
When the set of actions is a continuous domain, such as $\X = [0,1]^d$, the problem becomes intractable without further assumptions, as there are infinitely many arms to explore. The Lipschitz bandit model introduces structural smoothness. The unknown mean-reward function $\mu: \X \to [0,1]$ is assumed to be $L$-Lipschitz with respect to a norm, typically the Euclidean norm $\|\cdot\|_2$:
$$
|\mu(x) - \mu(y)| \le L \|x - y\|_2 \quad \text{for all } x, y \in \X.
$$
This condition ensures that the mean rewards of nearby points are similar, allowing an algorithm to generalize from a finite number of samples to the entire space. This structure makes the problem tractable, and algorithms for this setting can achieve near-optimal regret that scales as $\tilde{O}(T^{(d+1)/(d+2)})$, where the exponent depends on the dimension $d$ of the action space.

\subsection{Cooperative Multi-Player Bandits and Collisions}
In the multi-player MAB setting, $N$ players simultaneously choose from a common set of arms. We focus on the cooperative goal, where the objective is to maximize the sum of rewards across all players. A central challenge is handling collisions. In the "hard collision" model, if two or more players select the same arm (or region) in the same round, all colliding players receive zero reward. This creates an incentive for players to coordinate on distinct, high-value arms.

A simple and effective communication-free protocol for this coordination task is known as Musical Chairs. Once a set of $N$ high-quality arms has been identified, the players must assign themselves to these arms without conflict. In the Musical Chairs protocol, each unassigned player repeatedly samples an arm uniformly from the target set. If a player lands on an arm that no one else chose in that round, they "seat" there and play that arm for the remainder of the game. This process continues until all players are seated. A crucial aspect of our analysis considers the practical implementation where players do not know which of the $N$ target arms are already occupied, making their sampling choices over the full set of $N$ target arms.
