
\section*{Checklist}


\begin{enumerate}

  \item For all models and algorithms presented, check if you include:
  \begin{enumerate}
    \item A clear description of the mathematical setting, assumptions, algorithm, and/or model. [Yes]
    \item An analysis of the properties and complexity (time, space, sample size) of any algorithm. [Yes]
    \item (Optional) Anonymized source code, with specification of all dependencies, including external libraries. [Not Applicable]
  \end{enumerate}

  \item For any theoretical claim, check if you include:
  \begin{enumerate}
    \item Statements of the full set of assumptions of all theoretical results. [Yes]
    \item Complete proofs of all theoretical results. [Yes]
    \item Clear explanations of any assumptions. [Yes]     
  \end{enumerate}

  \item For all figures and tables that present empirical results, check if you include:
  \begin{enumerate}
    \item The code, data, and instructions needed to reproduce the main experimental results (either in the supplemental material or as a URL). [Yes]
    \item All the training details (e.g., data splits, hyperparameters, how they were chosen). [Yes]
    \item A clear definition of the specific measure or statistics and error bars (e.g., with respect to the random seed after running experiments multiple times). [Yes]
    \item A description of the computing infrastructure used. (e.g., type of GPUs, internal cluster, or cloud provider). [Yes]
  \end{enumerate}

  \item If you are using existing assets (e.g., code, data, models) or curating/releasing new assets, check if you include:
  \begin{enumerate}
    \item Citations of the creator If your work uses existing assets. [Not Applicable]
    \item The license information of the assets, if applicable. [Not Applicable]
    \item New assets either in the supplemental material or as a URL, if applicable. [Not Applicable]
    \item Information about consent from data providers/curators. [Not Applicable]
    \item Discussion of sensible content if applicable, e.g., personally identifiable information or offensive content. [Not Applicable]
  \end{enumerate}

  \item If you used crowdsourcing or conducted research with human subjects, check if you include:
  \begin{enumerate}
    \item The full text of instructions given to participants and screenshots. [Not Applicable]
    \item Descriptions of potential participant risks, with links to Institutional Review Board (IRB) approvals if applicable. [Not Applicable]
    \item The estimated hourly wage paid to participants and the total amount spent on participant compensation. [Not Applicable]
  \end{enumerate}

\end{enumerate}

\clearpage
\appendix
\thispagestyle{empty}
\onecolumn
\aistatstitle{Supplementary Material:\\ Multi-Agent Lipschitz Bandits}




\input{rel-work-appendix}


\section*{Appendix B: Proofs for Phase I}
\label{app:phase1}

We collect here the proofs of Lemmas~\ref{lem:counts} and~\ref{lem:means} and Proposition~\ref{prop:phase1-brackets}. Throughout, probabilities and expectations are taken with respect to all sources of randomness (players' exploration, collision process, and reward noise). We begin by restating the standing assumptions, notation, and two identities that are used repeatedly.

\paragraph{Standing assumptions and notation.}
\begin{itemize}
    \item The action domain is $\X=[0,1]^d$, partitioned into $\Pcal=\{C_1,\ldots,C_K\}$, where each $C\in\Pcal$ is a (closed) axis-aligned hypercube of side length $h$; the cells have disjoint interiors and cover $\X$. For each $C\in\Pcal$, we denote by $x_C$ its geometric center and by
    \[
        D_h \;:=\; h\sqrt{d}
    \]
    the Euclidean diameter of any such cell. (Boundary cells may be smaller; using $D_h$ is conservative and simplifies the presentation.)
    \item The unknown mean-reward function $\mu:\X\to[0,1]$ is $L$-Lipschitz w.r.t.\ $\|\cdot\|_2$:
    \[
        |\mu(x)-\mu(y)| \;\le\; L\|x-y\|_2\qquad\forall x,y\in\X.
    \]
    \item In Phase~I, at each round $t\in[T_0]$ and for each player $j\in[N]$ independently, a cell $C_t^{(j)}$ is sampled uniformly from $\Pcal$; the player probes the cell center $x_{C_t^{(j)}}$.
    \item A collision occurs in cell $C$ at round $t$ if at least two players sample $C$ in that round. If player $j$ is the unique occupant of $C$ at round $t$, a noisy reward $Y_t^{(j)}$ with mean $\mu(x_C)$ is observed; otherwise a null symbol $\bot$ is observed and no reward is recorded.
    \item We analyze the standard bounded-reward model: whenever a reward is observed, $Y_t^{(j)}\in[0,1]$ with $\mathbb E[Y_t^{(j)}\mid C_t^{(j)}=C,\ \text{no collision}]=\mu(x_C)$. This implies the centered noise is $\sigma$-sub-Gaussian with $\sigma\le\tfrac12$.
    \item Players observe whether a collision occurred (via $\bot$). The collision/missingness process depends only on the independent exploration choices and is independent of the reward noise.
\end{itemize}

\paragraph{Two basic identities.}
\begin{enumerate}
\item[(i)] \textbf{Single-round success probability.} For a fixed player $j$ and cell $C\in\Pcal$, the probability that $j$ samples $C$ and no other player samples $C$ in the same round is
\begin{equation}
\label{eq:pK}
p_K \;:=\; \frac{1}{K}\Bigl(1-\frac{1}{K}\Bigr)^{N-1}.
\end{equation}
\emph{Proof.} $\Pr[C_t^{(j)}=C]=1/K$ by uniform sampling; for each other player $j'\neq j$, $\Pr[C_t^{(j')}\neq C]=1-1/K$ independently; multiply over $N-1$ players.

\item[(ii)] \textbf{Center vs.\ maximum (Lipschitz geometry).} For any cell $C\in\Pcal$,
\begin{equation}
\label{eq:center-max-bracket}
\mu(x_C)\ \le\ \mu^\ast(C)\ \le\ \mu(x_C) + \frac{L}{2}D_h \;=\; \mu(x_C) + \frac{Lh\sqrt d}{2}.
\end{equation}
\emph{Proof.} For any $x\in C$, $\|x-x_C\|_2\le D_h/2$, hence $\mu(x)\le \mu(x_C)+L\|x-x_C\|_2\le \mu(x_C)+\tfrac L2 D_h$. Taking $\sup_{x\in C}$ yields the RHS; the LHS is trivial since $\mu^\ast(C)=\sup_{x\in C}\mu(x)\ge \mu(x_C)$.
\end{enumerate}

\medskip

We write $U_j(C,t):=\mathbf 1\{\,\text{player $j$ is the unique occupant of cell $C$ at round $t$}\,\}$. The success count over Phase~I is
\[
o_{j,C}(T_0)\;:=\;\sum_{t=1}^{T_0} U_j(C,t).
\]
When $o_{j,C}(T_0)\ge 1$, the empirical mean at the cell center is
\[
\widehat\mu^{(0)}_j(C)\;:=\;\frac{1}{o_{j,C}(T_0)}\sum_{t=1}^{T_0} U_j(C,t)\,Y_t^{(j)};
\]
For $o_{j,C}(T_0)=0$, we define $\widehat\mu^{(0)}_j(C):=0$ (this choice is harmless because $\mu(x_C)\in[0,1]$ and our confidence radius below will be $\ge 1$ in that case). We recall the Phase~I radii from the main text:
\begin{equation}
\label{eq:phase1-radius}
r^{(0)}_{j}(C) \;:=\; \sqrt{\frac{\beta_0}{2\,\max\{1,o_{j,C}(T_0)\}}}, 
\qquad
\beta_0 \;:=\; \log\!\frac{4 N K (T_0+1)}{\delta_{I}},
\end{equation}
and
\begin{equation}
\label{eq:phase1-brackets-def}
\LCB^{(0)}_j(C) \;:=\; \widehat{\mu}_{j}^{(0)}(C) - r^{(0)}_{j}(C),
\qquad
\UCB^{(0)}_j(C) \;:=\; \widehat{\mu}_{j}^{(0)}(C) + r^{(0)}_{j}(C) + \frac{L h\sqrt{d}}{2}.
\end{equation}


\subsection*{B.1\quad Success counts under collisions (Lemma~\ref{lem:counts})}

\begin{lemma}[Restatement of Lemma~\ref{lem:counts}]
Fix $\eta\in(0,1)$. With probability at least $1-\delta_{I}/2$, simultaneously for all $j\in[N]$ and $C\in \Pcal$,
\[
(1-\eta)\,T_0 p_K \;\le\; o_{j,C}(T_0) \;\le\; (1+\eta)\,T_0 p_K.
\]
\end{lemma}

\begin{proof}
Fix $j\in[N]$ and $C\in\Pcal$. By the sampling protocol, across rounds $t=1,\ldots,T_0$ the random variables $\{C_t^{(j)}\}_{t=1}^{T_0}$ are i.i.d., and for each fixed round the choices $\{C_t^{(j')}\}_{j'=1}^N$ are mutually independent. Therefore, for this fixed $(j,C)$, the indicators $\{U_j(C,t)\}_{t=1}^{T_0}$ are i.i.d.\ Bernoulli$(p_K)$ with $p_K$ given by~\eqref{eq:pK}. Consequently,
\[
o_{j,C}(T_0)=\sum_{t=1}^{T_0} U_j(C,t)\ \sim\ \mathrm{Bin}\!\left(T_0,p_K\right).
\]
Let $\mu:=\mathbb E[o_{j,C}(T_0)]=T_0 p_K$. The two-sided multiplicative Chernoff bound for binomial variables states that for any $\eta\in(0,1)$,
\[
\Pr\!\left(\,\big|o_{j,C}(T_0)-\mu\big|>\eta\mu\,\right)\ \le\ 2\exp\!\left(-\frac{\eta^2 \mu}{3}\right)
\;=\; 2\exp\!\left(-\frac{\eta^2 T_0 p_K}{3}\right).
\]
Applying a union bound over all $N$ players and all $K$ cells yields
\[
\Pr\!\left(\,\exists (j,C)\in [N]\times \Pcal:\ \big|o_{j,C}(T_0)-T_0 p_K\big|>\eta T_0 p_K \,\right)
\ \le\ 2 N K \exp\!\left(-\frac{\eta^2 T_0 p_K}{3}\right).
\]
Hence, if $T_0$ is chosen to satisfy
\begin{equation}
\label{eq:T0-prereq-counts}
2 N K \exp\!\left(-\frac{\eta^2 T_0 p_K}{3}\right)\ \le\ \frac{\delta_I}{2}
\quad\Longleftrightarrow\quad
T_0 \ \ge\ \frac{3}{\eta^2 p_K}\,\log\!\frac{4 N K}{\delta_I},
\end{equation}
then the claimed event holds with probability at least $1-\delta_I/2$. This is precisely the prerequisite on $T_0$ used later (see \S\ref{sec:choice-T0}).
\end{proof}


\subsection*{B.2\quad Anytime concentration for center means (Lemma~\ref{lem:means})}

\begin{lemma}[Restatement of Lemma~\ref{lem:means}]
With probability at least $1-\delta_{I}/2$, simultaneously for all $j\in[N]$ and $C\in \Pcal$,
\[
\big|\widehat{\mu}_j^{(0)}(C) - \mu(x_C)\big| \;\le\; r^{(0)}_{j}(C),
\qquad
r^{(0)}_{j}(C) \;=\; \sqrt{\frac{\beta_0}{2\,\max\{1,o_{j,C}(T_0)\}}},\ \ 
\beta_0 \;=\; \log\!\frac{4 N K (T_0+1)}{\delta_{I}} .
\]
\end{lemma}

\begin{proof}
Fix $(j,C)$ and let $n:=o_{j,C}(T_0)$. Condition on the sigma-field generated by all exploration choices and collisions, and on the realized value of $n$. 

Conditional on $n$, and because the reward noise is independent of the exploration/collision process (see assumptions), the $n$ observed rewards associated with $(j,C)$ are i.i.d., lie in $[0,1]$, and have mean $\mu(x_C)$. Denote their average by $\widehat\mu^{(0)}_j(C)$ (for $n=0$ we keep the convention $\widehat\mu^{(0)}_j(C)=0$).

\underline{Case $n\ge 1$.} Hoeffding's inequality for $[0,1]$-bounded i.i.d.\ variables yields, for any $\epsilon>0$,
\[
\Pr\!\left(\,\big|\widehat\mu^{(0)}_j(C)-\mu(x_C)\big|>\epsilon \ \middle|\ o_{j,C}(T_0)=n\right)\ \le\ 2\exp\!\left(-2 n \epsilon^2\right).
\]
Choosing $\epsilon=\sqrt{\beta_0/(2n)}$ gives
\begin{equation}
\label{eq:cond-failure}
\Pr\!\left(\,\big|\widehat\mu^{(0)}_j(C)-\mu(x_C)\big|>\sqrt{\beta_0/(2n)} \ \middle|\ o_{j,C}(T_0)=n\right)\ \le\ 2 e^{-\beta_0}.
\end{equation}

\underline{Case $n=0$.} Then $\widehat\mu^{(0)}_j(C)=0$ by definition. Since $\mu(x_C)\in[0,1]$, the event
\[
\left\{\ \big|\widehat\mu^{(0)}_j(C)-\mu(x_C)\big|>\sqrt{\beta_0/2}\ \right\}
\]
is \emph{impossible} whenever $\sqrt{\beta_0/2}\ge 1$. With our choice $\beta_0=\log\!\frac{4NK(T_0+1)}{\delta_I}$ and global budget $\delta_I\le \delta_{\rm sys}<1/4$, we have
\[
\beta_0 \ \ge\ \log\!\frac{4\cdot 1\cdot 1\cdot 2}{1/4} \;=\; \log(32) \;>\; 2,
\]
so indeed $\sqrt{\beta_0/2}>1$ and the $n=0$ failure probability equals $0$.

Let $E_{j,C}$ be the (unconditional) failure event for this $(j,C)$, namely
\[
E_{j,C} \;:=\; \left\{\ \big|\widehat{\mu}_j^{(0)}(C)-\mu(x_C)\big|\ >\ \sqrt{\frac{\beta_0}{2\,\max\{1,o_{j,C}(T_0)\}}}\ \right\}.
\]
By the law of total probability and the discussion above,
\[
\Pr(E_{j,C})
\;=\; \sum_{n=0}^{T_0} \Pr\!\left(E_{j,C}\ \middle|\ o_{j,C}(T_0)=n\right)\Pr\!\left(o_{j,C}(T_0)=n\right)
\;\le\; \sum_{n=1}^{T_0} 2 e^{-\beta_0}\,\Pr\!\left(o_{j,C}(T_0)=n\right)
\;\le\; 2 e^{-\beta_0}.
\]
Finally, apply a union bound over all players and cells:
\[
\Pr\!\left(\exists (j,C)\in[N]\times\Pcal:\ E_{j,C}\right)
\ \le\ 2 N K\, e^{-\beta_0}
\ =\ \frac{2 N K}{\frac{4 N K (T_0+1)}{\delta_I}}
\ =\ \frac{\delta_I}{2(T_0+1)}
\ \le\ \frac{\delta_I}{2}.
\]
Hence, with probability at least $1-\delta_I/2$, the desired deviation bound holds simultaneously for all $(j,C)$, i.e., the lemma.
\end{proof}





\subsection*{B.3\quad Phase-I maxima brackets (Proposition~\ref{prop:phase1-brackets})}

\begin{proposition}[Restatement of Proposition~\ref{prop:phase1-brackets}]
On an event of probability at least $1-\delta_{I}$, simultaneously for all $j\in[N]$ and $C\in \Pcal$,
\[
\LCB^{(0)}_j(C) \;\le\; \mu^\ast(C) \;\le\; \UCB^{(0)}_j(C),
\]
with $\LCB^{(0)}_j,\UCB^{(0)}_j$ as in~\eqref{eq:phase1-brackets-def}.
\end{proposition}

\begin{proof}
By Lemma~\ref{lem:means}, on an event $\mathcal E_{\text{means}}$ of probability at least $1-\delta_I/2$, we have for all $(j,C)$
\[
\mu(x_C)\ \in\ \Bigl[\widehat\mu^{(0)}_j(C)-r^{(0)}_j(C),\ \widehat\mu^{(0)}_j(C)+r^{(0)}_j(C)\Bigr].
\]
Combining this with ~\eqref{eq:center-max-bracket} gives, for every $(j,C)$,
\[
\widehat{\mu}_j^{(0)}(C) - r^{(0)}_j(C) \;\le\; \mu^\ast(C) \;\le\; \widehat{\mu}_j^{(0)}(C) + r^{(0)}_j(C) + \frac{L}{2}D_h,
\]
which is exactly $\LCB^{(0)}_j(C)\le \mu^\ast(C)\le \UCB^{(0)}_j(C)$ by~\eqref{eq:phase1-brackets-def}. Thus, the validity holds on $\mathcal E_{\text{means}}$.

For later phases we also record the success-count event $\mathcal E_{\text{counts}}$ of Lemma~\ref{lem:counts}, which holds with probability at least $1-\delta_I/2$ provided $T_0$ satisfies~\eqref{eq:T0-prereq-counts}. While $\mathcal E_{\text{counts}}$ is not needed for the validity of the intervals, it controls their \emph{width}. On the intersection
\[
\mathcal E_I \;:=\; \mathcal E_{\text{means}} \cap \mathcal E_{\text{counts}},
\]
the bracket validity still holds, and by a union bound
\[
\Pr(\mathcal E_I)\ \ge\ 1 - \frac{\delta_I}{2} - \frac{\delta_I}{2} \ =\ 1-\delta_I.
\]
This proves the proposition as stated.
\end{proof}



\subsection*{B.4\quad Choice of $T_0$ and bracket precision}
\label{sec:choice-T0}

We record explicit (mild) lower bounds on the Phase~I budget $T_0$ that guarantee both Lemma~\ref{lem:counts} and a desired bracket accuracy.

\paragraph{Prerequisite for Lemma~\ref{lem:counts}.}
As shown in~\eqref{eq:T0-prereq-counts}, for any fixed $\eta\in(0,1)$ it suffices to take
\begin{equation}
\label{eq:T0-Lemma1}
T_0 \ \ge\ \frac{3}{\eta^2 p_K}\,\log\!\frac{4 N K}{\delta_I}.
\end{equation}

\paragraph{Uniform accuracy target.}
Fix $\alpha\in(0,1)$. On $\mathcal E_{\text{counts}}$ we have $o_{j,C}(T_0)\ge (1-\eta)T_0 p_K$ for all $(j,C)$. Using~\eqref{eq:phase1-radius},
\[
r^{(0)}_j(C) \ \le\ \sqrt{\frac{\beta_0}{2(1-\eta)T_0 p_K}},
\qquad \beta_0=\log\!\frac{4NK(T_0+1)}{\delta_I}.
\]
Therefore a sufficient condition for $r^{(0)}_j(C)\le \alpha$ uniformly over $(j,C)$ on $\mathcal E_{\text{counts}}$ is
\begin{equation}
\label{eq:T0-accuracy-implicit}
T_0 \ \ge\ \frac{\beta_0}{2\alpha^2(1-\eta)\,p_K}.
\end{equation}

\paragraph{A convenient consolidated choice.}
Since $\beta_0\ge \log\!\frac{4NK}{\delta_I}$ (as $T_0+1\ge 1$), the single implicit requirement
\begin{equation}
\label{eq:T0-consolidated}
T_0 \ \ge\ \frac{\beta_0}{p_K}\cdot \max\!\left\{ \frac{1}{\alpha^2},\ 12 \right\}
\qquad\text{with }\ \beta_0=\log\!\frac{4 N K (T_0+1)}{\delta_{I}}
\end{equation}
implies both~\eqref{eq:T0-Lemma1} (taking $\eta=\tfrac12$ so that $\tfrac{3}{\eta^2}=12$) and~\eqref{eq:T0-accuracy-implicit} (since $\frac{1}{2(1-\eta)}=1$ for $\eta=\tfrac12$). The dependence on $T_0$ inside $\beta_0$ is benign and monotone; any $T_0$ large enough to satisfy~\eqref{eq:T0-consolidated} is acceptable. In our subsequent analysis we only need the validity of the Phase~I brackets (which already holds under Lemma~\ref{lem:means}); the accuracy parameter $\alpha$ can thus be taken moderate.




\bigskip




\section*{Appendix C: Proof Details for Phase II}
\label{app:phase2}

Throughout this appendix we condition on the Phase~I clean event $\mathcal E_I$ from Appendix~B:
(i) all Phase~I brackets are valid for all players and cells; and
(ii) the Phase~I count concentration holds when invoked.
We keep the Phase~II failure budget $\delta_{II}\in(0,1/4)$ and allocate it explicitly across events.

\paragraph{Standing assumptions and notation (Phase II).}
\begin{itemize}
\item As in Appendix~B, observed rewards lie in $[0,1]$. Hence the centered noise is $\sigma$-sub-Gaussian with $\sigma\le \tfrac12$, and Hoeffding-type concentration bounds apply.
\item \textbf{Collision observability} Players observe a collision bit (null symbol $\bot$). The missingness process (collisions) depends only on the independent exploration choices and is independent of the reward noise. We will condition on counts of successful observations without affecting noise distributions.
\item \textbf{Active sets (safe elimination).} For player $j$, let $\theta^{(0)}_j$ be the $N$-th order statistic of $\{\LCB^{(0)}_j(C):C\in\Pcal\}$, and define
\begin{equation}
\label{eq:active-set-def}
\Sact^{(0)}_j \;:=\; \Bigl\{\,C\in \Pcal \,:\, \UCB^{(0)}_j(C)\ \ge\ \theta^{(0)}_j \Bigr\}.
\end{equation}
We will show that on $\mathcal E_I$ the active set is  {safe} and has size at least $N$ for every player.
\item \textbf{Probe nets.} For each cell $C$, fix an $\eta$-net $Z_C\subset C$ built as an axis-aligned grid of spacing $s:=\eta/\sqrt d$ in each coordinate. Then for every $x\in C$ there exists $z\in Z_C$ with $\|x-z\|_\infty\le s/2$ and hence $\|x-z\|_2\le (s/2)\sqrt d=\eta/2<\eta$. Its cardinality satisfies
\begin{equation}
\label{eq:Pmax}
|Z_C|\ \le\ \Bigl(2+\frac{h\sqrt d}{\eta}\Bigr)^{\!d}
\ \le\ c_d\,\Bigl(1+\frac{h}{\eta}\Bigr)^{\!d}
\ \le\ c'_d\,\Bigl(1+\Bigl(\frac{h}{\eta}\Bigr)^{\!d}\Bigr)
\ \le\ C_d\,\Bigl(\frac{h}{\eta}\Bigr)^{\!d},
\end{equation}
where $c_d:=(2+\sqrt d)^{d}$ and $C_d:=\max\{c_d,2^d\}$ is an absolute constant depending only on $d$. For simplicity we use the conservative bound $|Z_C|\le C_d (h/\eta)^d$ below.
Define $P_{\max}:=\max_{C\in\Pcal}|Z_C|$, so $P_{\max}\le C_d (h/\eta)^d$.
\item \textbf{Phase II sampling protocol (fixed for $T_1$ rounds).}
At each round $t=1,\dots,T_1$, independently across rounds and players:
\begin{enumerate}
\item Player $j$ samples a cell $C_t^{(j)}$ uniformly from $\Sact^{(0)}_j$.
\item Given $C_t^{(j)}$, player $j$ samples a probe $Z_t^{(j)}$ uniformly from $Z_{C_t^{(j)}}$ and probes $Z_t^{(j)}$.
\item A collision in a cell $C$ occurs if at least two players select any probes in the same $C$ at round $t$.
A probe is successful if no other player selects cell $C$ in that round.
\end{enumerate}
The active sets $\{\Sact^{(0)}_j\}$ and nets $\{Z_C\}$ are fixed throughout Phase~II.
\item \textbf{Counting notation.} For a triple $(j,C,z)$ with $C\in \Sact^{(0)}_j$ and $z\in Z_C$, define the per-round success indicator
\[
V_{j,C,z}(t)\ :=\ \mathbf 1\{\, C_t^{(j)}=C,\ Z_t^{(j)}=z,\ \text{and no other player selects }C\text{ at round }t\,\},
\]
and total successes $s_{j,C,z}(T_1):=\sum_{t=1}^{T_1} V_{j,C,z}(t)$.
Let
\[
\NumProbes \ :=\ \sum_{j=1}^N\ \sum_{C\in \Sact^{(0)}_j}\ |Z_C|
\quad\text{and}\quad
M_{act} \ :=\ \max_{j\in[N]} |\Sact^{(0)}_j|.
\]
\end{itemize}

\subsection*{C.1.\; Safe active sets (size and completeness)}

\begin{lemma}[Active-set safety and size]\label{lem:active-safety}
On $\mathcal E_I$, for every player $j$:
\begin{enumerate}
\item $|\Sact^{(0)}_j|\ \ge\ N$;
\item every true top-$N$ cell belongs to $\Sact^{(0)}_j$, i.e., if $T^\star$ denotes the set of $N$ cells with the largest $\mu^\ast(\cdot)$ values, then $T^\star\subseteq \Sact^{(0)}_j$.
\end{enumerate}
\end{lemma}

\begin{proof}
On $\mathcal E_I$, $\LCB^{(0)}_j(C)\le \mu^\ast(C)\le \UCB^{(0)}_j(C)$ for every $C$.

Let $\mu^\ast_{(1)}\ge\cdots\ge \mu^\ast_{(K)}$ be the sorted cell maxima and $T^\star$ the set of corresponding cells with ranks $1$ to $N$.

Since each $\LCB^{(0)}_j(C)\le \mu^\ast(C)$, the $N$-th LCB order statistic satisfies
$\theta^{(0)}_j \le \mu^\ast_{(N)}$.

For any $C\in T^\star$, we have $\UCB^{(0)}_j(C)\ge \mu^\ast(C)\ge \mu^\ast_{(N)}\ge \theta^{(0)}_j$,
hence $C\in \Sact^{(0)}_j$ by \eqref{eq:active-set-def}.

Therefore $T^\star\subseteq \Sact^{(0)}_j$ and $|\Sact^{(0)}_j|\ge |T^\star|=N$.
\end{proof}

\subsection*{C.2.\; Coverage: uniform lower bound on per-round probe success}

\begin{lemma}[Per-round success probability]\label{lem:q-lower}
Under the Phase~II protocol and Lemma~\ref{lem:active-safety}, for every triple $(j,C,z)$ and every round $t$,
\[
\Pr\bigl[V_{j,C,z}(t)=1\bigr]\ \ge\ q_{M_{act},\eta}
\quad\text{with}\quad
q_{M_{act},\eta}\ :=\ \frac{1}{M_{act}\,P_{\max}}\left(1-\frac{1}{N}\right)^{N-1},
\]
where $P_{\max}:=\max_C |Z_C| \le C_d (h/\eta)^d$.
\end{lemma}

\begin{proof}
Fix $(j,C,z)$ and $t$.

Player $j$ picks $C$ with probability $1/|\Sact^{(0)}_j|\ge 1/M_{act}$ and, given $C$, picks $z$ with probability $1/|Z_C|\ge 1/P_{\max}$.

For each other player $k\neq j$, either $C\notin \Sact^{(0)}_k$ (so $\Pr(C_t^{(k)}=C)=0$) or $C\in \Sact^{(0)}_k$ and then
$\Pr(C_t^{(k)}=C)=1/|\Sact^{(0)}_k|\le 1/N$ by Lemma~\ref{lem:active-safety}.

Independence across players implies
\[
\Pr\bigl[\text{no other player selects }C\bigr]\ \ge\ \Bigl(1-\frac{1}{N}\Bigr)^{N-1}.
\]

Multiplying completes the proof.
\end{proof}

\begin{lemma}[Phase-II Probe Coverage]\label{lem:coverage}
Let $b\in\mathbb N$ and $T_1\in\mathbb N$ satisfy
\[
b \ \ge\ 4\log\frac{2\,\NumProbes}{\delta_{II}}
\qquad\text{and}\qquad
T_1 \ \ge\ \frac{2b}{q_{M_{act},\eta}}.
\]
Then, with probability at least $1-\delta_{II}/2$, every triple achieves at least $b$ successes:
\[
\min_{(j,C,z)}\ s_{j,C,z}(T_1)\ \ge\ b.
\]
\end{lemma}

\begin{proof}
For any fixed triple, $\{V_{j,C,z}(t)\}_{t=1}^{T_1}$ are i.i.d.\ Bernoulli with success probability $q_{j,C,z}:=\Pr[V_{j,C,z}(t)=1]\ge q_{M_{act},\eta}$ by Lemma~\ref{lem:q-lower}. 

Thus
$\mathbb E[s_{j,C,z}(T_1)]=T_1 q_{j,C,z}\ge 2b$.

By the Chernoff lower-tail bound with $\lambda=\tfrac12$,
\[
\Pr\bigl[s_{j,C,z}(T_1)< b\bigr]\ \le\ \exp\!\Bigl(-\frac{\mathbb E[s_{j,C,z}(T_1)]}{8}\Bigr)\ \le\ e^{-b/4}.
\]

A union bound over all $\NumProbes$ triples gives
$\Pr\bigl(\exists (j,C,z): s_{j,C,z}(T_1)< b\bigr)\le \NumProbes\, e^{-b/4}\le \delta_{II}/2$ by the choice of $b$.
\end{proof}

\subsection*{C.3.\; Uniform probe accuracy}

\begin{lemma}[Uniform probe accuracy]\label{lem:probe-accuracy}
Let
\[
\beta_1\ :=\ \log\frac{4\,\NumProbes}{\delta_{II}}
\qquad\text{and}\qquad
r_1\ :=\ \sqrt{\frac{\beta_1}{2b}}.
\]
On the event of Lemma~\ref{lem:coverage} (so $s_{j,C,z}(T_1)\ge b$ for all triples), we have
\[
\Pr\!\left[\ \exists (j,C,z):\ \big|\widehat\mu_j(C,z)-\mu(z)\big|> r_1\ \right]\ \le\ \frac{\delta_{II}}{2},
\]
where $\widehat\mu_j(C,z)$ is the empirical mean over the $s_{j,C,z}(T_1)$ successful observations at $(j,C,z)$.
Equivalently, with probability at least $1-\delta_{II}/2$,
\[
\big|\widehat\mu_j(C,z)-\mu(z)\big|\ \le\ r_1
\qquad\text{simultaneously for all }(j,C,z).
\]
\end{lemma}

\begin{proof}
Fix $(j,C,z)$. Condition on $s:=s_{j,C,z}(T_1)\ge b$ and on the exploration/collision sigma-field.

By our assumption on the collisions, the $s$ observed rewards at $(j,C,z)$ are i.i.d.\ in $[0,1]$ with mean $\mu(z)$.
For any $n\ge b$, Hoeffding yields
\[
\Pr\!\left(\big|\widehat\mu_j(C,z)-\mu(z)\big|>\sqrt{\beta_1/(2n)}\ \middle|\ s=n\right)\ \le\ 2e^{-\beta_1}.
\]

Hence, by the law of total probability restricted to $n\ge b$,
\[
\Pr\!\left(\big|\widehat\mu_j(C,z)-\mu(z)\big|>r_1\ \middle|\ s\ge b\right)\ \le\ 2e^{-\beta_1}.
\]

A union bound over the $\NumProbes$ triples yields the claim with the chosen $\beta_1$.
\end{proof}

\begin{remark}[Anytime variant (not used in parameterization)]
\label{rem:anytime}
If one prefers a radius that adapts to the realized count, set
$\beta_1^{\mathrm{any}}:=\log\frac{4\,\NumProbes\,(T_1+1)}{\delta_{II}}$
and $r^{\mathrm{any}}(s):=\sqrt{\beta_1^{\mathrm{any}}/(2\max\{1,s\})}$.
Then, by the same Hoeffding+\;law-of-total-probability argument and a union bound over $n\in\{1,\dots,T_1\}$,
\[
\Pr\!\left(\ \exists (j,C,z):\ \big|\widehat\mu_j(C,z)-\mu(z)\big|> r^{\mathrm{any}}(s_{j,C,z}(T_1))\ \right)\ \le\ \frac{\delta_{II}}{2}.
\]
We do not use this form below; our fixed-$b$ parameterization already yields the target width with fewer log factors.
\end{remark}

\subsection*{C.4.\; Refined maxima brackets}

For player $j$ and active cell $C\in \Sact^{(0)}_j$, define
\begin{equation}
\label{eq:phase2-brackets-def}
\LCB^{(1)}_j(C)\ :=\ \max_{z\in Z_C}\bigl\{\widehat\mu_j(C,z)-r_1\bigr\},
\qquad
\UCB^{(1)}_j(C)\ :=\ \max_{z\in Z_C}\bigl\{\widehat\mu_j(C,z)+r_1\bigr\} + L\eta.
\end{equation}

\begin{proposition}[Refined Maxima Brackets]\label{prop:refined-bracket}
On the intersection of the events in Lemmas~\ref{lem:coverage} and~\ref{lem:probe-accuracy} (probability at least $1-\delta_{II}$), simultaneously for all players $j$ and active cells $C\in \Sact^{(0)}_j$,
\[
\LCB^{(1)}_j(C)\ \le\ \mu^\ast(C)\ \le\ \UCB^{(1)}_j(C)
\quad\text{and}\quad
\UCB^{(1)}_j(C)-\LCB^{(1)}_j(C)\ \le\ 2r_1 + L\eta.
\]
\end{proposition}

\begin{proof}
Work on the event of Lemma~\ref{lem:probe-accuracy}. 

For any $z\in Z_C$,
$\mu(z)\in [\widehat\mu_j(C,z)-r_1,\ \widehat\mu_j(C,z)+r_1]$.

Taking maxima over $z\in Z_C$ gives
\[
\max_{z\in Z_C}\mu(z)\ \in\ \left[\ \max_{z\in Z_C}\bigl(\widehat\mu_j(C,z)-r_1\bigr),\ \max_{z\in Z_C}\bigl(\widehat\mu_j(C,z)+r_1\bigr)\ \right].
\]

By the $\eta$-net property and $L$-Lipschitzness, $\mu^\ast(C)\in [\,\max_{z\in Z_C}\mu(z),\ \max_{z\in Z_C}\mu(z)+L\eta\,]$.

Combining yields the validity and the width bound stated.
\end{proof}

\subsection*{C.5.\; Selecting the top-$N$ cells: gap-free $\varepsilon$-optimality and consensus}

Recall that each player $j$ selects the $N$ cells with the largest $\LCB^{(1)}_j(C)$
(breaking ties by a fixed public ordering), and denote the selected set by $S^{(j)}_\varepsilon$.

\begin{theorem}[Gap-Free $\varepsilon$-Optimality]\label{thm:gapfree-safety}
Let $\varepsilon>0$. If Phase~II parameters are such that $2r_1+L\eta\le \varepsilon$,
then on the intersection of the events in Lemmas~\ref{lem:coverage} and~\ref{lem:probe-accuracy} (probability at least $1-\delta_{II}$), for every player $j$ and every $C\in S^{(j)}_\varepsilon$,
\[
\mu^\ast(C)\ \ge\ \mu^\ast_{(N)} - \varepsilon.
\]
\end{theorem}

\begin{proof}
On the event of Proposition~\ref{prop:refined-bracket}, for any true top-$N$ cell $C^\star$ we have
$\LCB^{(1)}_j(C^\star)\ge \mu^\ast(C^\star)-\varepsilon\ge \mu^\ast_{(N)}-\varepsilon$.

Let $\theta^{(1)}_j$ be the $N$-th order statistic of $\{\LCB^{(1)}_j(C):C\in \Sact^{(0)}_j\}$; since $T^\star\subseteq \Sact^{(0)}_j$ (Lemma~\ref{lem:active-safety}) and there are $N$ cells with LCB at least $\mu^\ast_{(N)}-\varepsilon$, we have $\theta^{(1)}_j\ge \mu^\ast_{(N)}-\varepsilon$.

If $C\in S^{(j)}_\varepsilon$, then $\LCB^{(1)}_j(C)\ge \theta^{(1)}_j$, and validity gives
$\mu^\ast(C)\ge \LCB^{(1)}_j(C)\ge \mu^\ast_{(N)}-\varepsilon$.
\end{proof}

\begin{definition}[$\varepsilon$-Uniqueness at the Top-$N$]\label{def:eps-uniq}
A mean function $\mu$ is $\varepsilon$-unique at the top-$N$ if there exists a unique set $S^\dagger\subset \Pcal$ of size $N$ such that
\[
\min_{C\in S^\dagger} \mu^\ast(C) \ \ge\ \max_{C\notin S^\dagger} \mu^\ast(C) + 2\varepsilon.
\]
\end{definition}

\begin{lemma}[Consensus under $\varepsilon$-Uniqueness]\label{lem:consensus}
Assume $\varepsilon$-uniqueness at the top-$N$ and that all refined brackets have width at most $\varepsilon$ and contain $\mu^\ast(C)$.
Then $S^{(j)}_\varepsilon = S^\dagger$ for all $j\in[N]$.
\end{lemma}

\begin{proof}
For any $C_{\rm good}\in S^\dagger$ and $C_{\rm bad}\notin S^\dagger$,
\[
\LCB^{(1)}_j(C_{\rm good})\ \ge\ \mu^\ast(C_{\rm good})-\varepsilon\ \ge\ \mu^\ast(C_{\rm bad})+\varepsilon\ \ge\ \LCB^{(1)}_j(C_{\rm bad}),
\]
using $\varepsilon$-uniqueness and $\LCB^{(1)}_j(C_{\rm bad})\le \mu^\ast(C_{\rm bad})$.
Thus the $N$ largest LCBs are attained exactly on $S^\dagger$ (ties do not change this inclusion).
\end{proof}

\subsection*{C.6.\; Parameter choices and complexity bounds}

We summarize our parameter choices ensuring width $\le \varepsilon$ with probability at least $1-\delta_{II}$.

\paragraph{Cardinalities and probabilities.}
By \eqref{eq:Pmax} and Lemma~\ref{lem:active-safety},
\[
\NumProbes\ =\ \sum_{j=1}^N \sum_{C\in \Sact^{(0)}_j} |Z_C|
\ \le\ N\,M_{act}\,P_{\max}
\ \le\ N\,M_{act}\,C_d\Bigl(\frac{h}{\eta}\Bigr)^{\!d}.
\]
Lemma~\ref{lem:q-lower} gives
\[
q_{M_{act},\eta}\ \ge\ \frac{1}{M_{act}\,P_{\max}}\left(1-\frac{1}{N}\right)^{N-1}
\ \ge\ \frac{1}{M_{act}\,C_d}\left(\frac{\eta}{h}\right)^{\!d}\left(1-\frac{1}{N}\right)^{N-1}.
\]

\paragraph{Concrete schedule for a target $\varepsilon>0$.}
Choose
\[
\eta\ =\ \frac{\varepsilon}{2L},\qquad
\beta_1\ =\ \log\frac{4\,\NumProbes}{\delta_{II}},\qquad
b\ \ge\ \max\!\left\{\, 4\log\frac{2\,\NumProbes}{\delta_{II}},\ \frac{8\,\beta_1}{\varepsilon^2}\,\right\},
\]
so that $2r_1+L\eta \le \varepsilon$, where $r_1=\sqrt{\beta_1/(2b)}$.
Then, using Lemma~\ref{lem:coverage} and the bound on $q_{M_{act},\eta}$,
\[
T_1 \ \ge\ \frac{2b}{q_{M_{act},\eta}}
\ \le\ \frac{2\,b\,M_{act}\,P_{\max}}{\left(1-\frac{1}{N}\right)^{N-1}}
\ \le\ \frac{2\,b\,M_{act}\,C_d}{\left(1-\frac{1}{N}\right)^{N-1}}
\left(\frac{h}{\eta}\right)^{\!d}.
\]
With $\eta=\varepsilon/(2L)$ and $b=\Theta\!\big(\beta_1/\varepsilon^2 + \log(\NumProbes/\delta_{II})\big)$ we obtain
\[
T_1 \ =\ O\!\left(
\frac{M_{act}\,(Lh)^d}{\varepsilon^{d+2}}\cdot
\Bigl[\beta_1 + \log\frac{\NumProbes}{\delta_{II}}\Bigr]
\right),
\qquad
\NumProbes \ \le\ O\!\Big(N\,M_{act}\,(Lh/\varepsilon)^d\Big).
\]
Thus the Phase~II budget $T_1$ is independent of the horizon $T$ and scales (up to polylog factors) as
\[
T_1 \ =\ \tilde O\!\Big(M_{act}\,(Lh)^d\,\varepsilon^{-(d+2)}\Big).
\]
If desired, one may replace $M_{act}$ by $K$ using $M_{act}\le K$ for a looser but simpler bound.
\medskip

\noindent\textbf{Failure budget aggregation.}
By Lemmas~\ref{lem:coverage} and~\ref{lem:probe-accuracy}, the intersection of the coverage and uniform-accuracy events holds with probability at least $1-\delta_{II}$. Proposition~\ref{prop:refined-bracket} and Theorem~\ref{thm:gapfree-safety} are stated on this intersection. Lemma~\ref{lem:consensus} is a deterministic consequence of the refined brackets and $\varepsilon$-uniqueness.

\medskip

\noindent\textbf{Remarks.}
(i) The constant $L\eta$ in \eqref{eq:phase2-brackets-def} can be tightened to $L\eta/2$ using the $\eta/2$ covering radius; we keep $L\eta$ for simplicity and monotonicity with respect to $\eta$.
(ii) If one prefers an anytime-in-$n$ accuracy with an adaptive radius, use Remark~\ref{rem:anytime}; this modifies $\beta_1$ to include a $\log(T_1\!+\!1)$ factor without changing asymptotics in $\varepsilon$.
(iii) The protocol fixes active sets during Phase~II; allowing adaptive shrinking would require re-deriving $q_{M_{act},\eta}$ or freezing a lower bound on $|\Sact^{(0)}_j|$ throughout the phase.







\bigskip

\section*{Appendix D: Proof Details for Phase II$\tfrac{1}{2}$ (Musical Chairs)}
\label{app:mc}

We now provide proofs for the Musical Chairs (MC) seating phase.

We know that Phase II concluded such that all players share the same $N$-cell target set (e.g., because the $\epsilon$-uniqueness condition holds). The analysis below is conditioned on this event.

There are $N$ target cells and $N$ players. At the start of the phase, all players are unseated.
In each round, every unseated player independently samples a cell uniformly at random from the $N$-cell target set.
If exactly one unseated player chooses a currently unoccupied cell, that player becomes seated at that cell and remains seated thereafter.
If a cell is chosen by two or more unseated players, or by any unseated player together with an already seated player, a collision occurs at that cell and all players who chose it obtain zero reward in that round (the seated player remains seated).

Let $U_t\in\{0,1,\dots,N\}$ be the number of unseated players at the start of round $t$.
Then exactly $N-U_t$ cells are occupied (by seated players) and exactly $U_t$ cells are free.
Define the  {drift} at state $u$ by
\begin{equation}
\label{eq:mc-drift-def}
\Delta(u)\ :=\ \EE\!\left[\,U_t-U_{t+1}\ \middle|\ U_t=u\,\right],
\end{equation}
i.e., the expected number of newly seated players in a round when $u$ players are currently unseated.

\subsection*{D.1.\; Drift formula and basic bounds}

\begin{lemma}[Exact drift and a uniform lower bound]
\label{lem:mc-drift}
For every $u\in\{1,\dots,N\}$,
\begin{equation}
\label{eq:mc-drift}
\Delta(u)\ =\ \frac{u^2}{N}\left(1-\frac{1}{N}\right)^{u-1}
\ \ \ge\ \ \frac{u^2}{e\,N}.
\end{equation}
\end{lemma}

\begin{proof}
When $u$ players are unseated, there are $u$ free cells. 

Fix a particular free cell.


The probability that  {exactly one} of the $u$ unseated players chooses this cell equals
$u\cdot \tfrac{1}{N}\cdot (1-\tfrac{1}{N})^{u-1}$: choose which unseated player (there are $u$ choices), that player picks the cell with probability $1/N$, and each of the remaining $u-1$ unseated players avoids it with probability $(1-1/N)$, independently.

Each free cell with exactly one chooser yields exactly one newly seated player, and free cells are disjoint, so by linearity of expectation over the $u$ free cells we obtain
\[
\Delta(u)\ =\ u\cdot \Bigl[u\cdot \tfrac{1}{N}\cdot (1-\tfrac{1}{N})^{u-1}\Bigr]\ =\ \frac{u^2}{N}\left(1-\frac{1}{N}\right)^{u-1}.
\]

For the lower bound, $(1-1/N)^{u-1}\ge (1-1/N)^{N-1}\ge e^{-1}$ for all $N\ge 1$, yielding $\Delta(u)\ge u^2/(eN)$.
\end{proof}

\begin{lemma}[Monotonicity of the drift]
\label{lem:mc-drift-monotone}
The function $u\mapsto \Delta(u)$ is strictly increasing on $\{1,2,\dots,N\}$.
\end{lemma}

\begin{proof}
For $u\in\{1,\dots,N-1\}$,
\[
\frac{\Delta(u+1)}{\Delta(u)}
\ =\ \frac{(u+1)^2}{u^2}\cdot \left(1-\frac{1}{N}\right)
\ =\ \left(1+\frac{1}{u}\right)^2\left(1-\frac{1}{N}\right).
\]

Since $u\le N-1$, we have $1+\frac{1}{u}\ \ge\ 1+\frac{1}{N-1}\ >\ 1$ and hence
\[
\left(1+\frac{1}{u}\right)^2\left(1-\frac{1}{N}\right)
\ \ge\ \left(1+\frac{1}{N-1}\right)^2\left(1-\frac{1}{N}\right)
\ =\ \frac{N^2}{(N-1)^2}\cdot \frac{N-1}{N}
\ =\ \frac{N}{N-1}\ >\ 1.
\]

Thus $\Delta(u+1)>\Delta(u)$.
\end{proof}

\subsection*{D.2.\; Expected seating time}

We now prove that the expected number of rounds to seat all players is linear in $N$.

\begin{theorem}[Expected seating time]
\label{thm:mc-time-app}
Let $T_{MC}:=\inf\{t\ge 1: U_t=0\}$ be the (a.s. finite) stopping time at which all players are seated.
Then
\[
\EE[T_{MC}]\ \le\ \sum_{u=1}^{N}\frac{1}{\Delta(u)}\ \le\ \frac{e\pi^2}{6}\,N,
\]
and in particular $\EE[T_{MC}]=O(N)$.
\end{theorem}

\begin{proof}
Define the potential
\[
V(u)\ :=\ \sum_{v=1}^{u}\frac{1}{\Delta(v)},\qquad u\in\{0,1,\dots,N\}.
\]
Note that $V(0)=0$ and $V$ is finite and nondecreasing.

Let $Y_t:=U_t-U_{t+1}\in\{0,1,\dots,U_t\}$ denote the number of newly seated players in round $t$.

Fix $t$ and condition on $U_t=u>0$. Using the definition of $V$,
\[
V(U_t)-V(U_{t+1})\ =\ V(u)-V(u-Y_t)\ =\ \sum_{k=0}^{Y_t-1}\frac{1}{\Delta(u-k)}.
\]

By Lemma~\ref{lem:mc-drift-monotone}, $\Delta(\cdot)$ is increasing, so $1/\Delta(\cdot)$ is decreasing. 

Therefore
\[
V(U_t)-V(U_{t+1})\ \ge\ Y_t\cdot \frac{1}{\Delta(u)}.
\]

Taking conditional expectations and using the definition of the drift \eqref{eq:mc-drift-def},
\[
\EE\!\left[\, V(U_t)-V(U_{t+1}) \ \middle|\ U_t=u \,\right]
\ \ge\ \frac{\EE[Y_t\mid U_t=u]}{\Delta(u)}\ =\ \frac{\Delta(u)}{\Delta(u)}\ =\ 1.
\]

Taking expectations and summing over $t=0,1,\dots,T_{MC}-1$, we obtain (by the tower property; no optional-stopping theorem is required)
\[
\EE\!\left[\,V(U_0)-V(U_{T_{MC}})\,\right]
\ =\ \sum_{t=0}^{\infty} \EE\!\left[\,\mathbf 1\{t<T_{MC}\}\cdot \bigl(V(U_t)-V(U_{t+1})\bigr)\,\right]
\ \ge\ \sum_{t=0}^{\infty} \EE\!\left[\,\mathbf 1\{t<T_{MC}\}\,\right]
\ =\ \EE[T_{MC}].
\]
Since $U_0=N$ and $V(0)=0$, we have $\EE[T_{MC}]\le V(N)=\sum_{u=1}^{N}\frac{1}{\Delta(u)}$.

Finally, using Lemma~\ref{lem:mc-drift}, $\Delta(u)\ge u^2/(eN)$, hence
\[
\sum_{u=1}^{N}\frac{1}{\Delta(u)}\ \le\ eN \sum_{u=1}^{N}\frac{1}{u^2}\ \le\ \frac{e\pi^2}{6}\,N,
\]
which proves the claim.
\end{proof}

\subsection*{D.3.\; Seating-phase regret}

We evaluate the expected regret accumulated during the seating phase, measured against the per-round benchmark of obtaining $N$ unit-normalized rewards (one per target cell). 

\begin{corollary}[Seating-phase regret: a simple bound]
\label{cor:mc-regret}
Let $R_{MC}$ denote the cumulative regret incurred during the seating phase.
Then
\[
\EE[R_{MC}]\ \le\ N \cdot \EE[T_{MC}]\ \le\ \frac{e\pi^2}{6}\,N^2,
\]
so in particular $\EE[R_{MC}]=O(N^2)$. The bound is independent of the overall horizon $T$.
\end{corollary}

\begin{proof}
In each round, the per-round benchmark is at most $N$ (one unit per cell), and actual reward is nonnegative. Therefore the instantaneous regret is at most $N$.

By Linearity of expectation on the random-time sum,
\[
\EE[R_{MC}] \ =\ \EE\!\left[\sum_{t=1}^{T_{MC}} \text{regret}_t\right]
\ \le\ \EE\!\left[\sum_{t=1}^{T_{MC}} N\right]\ =\ N\,\EE[T_{MC}],
\]
and the claim follows from Theorem~\ref{thm:mc-time-app}.
\end{proof}

\begin{remark}[Sharper regret bound]
\label{rem:mc-regret-sharp}
The $O(N^2)$ bound is conservative. One can show $\EE[R_{MC}]=O(N\log N)$ as follows.
In a round with $u$ unseated players:
\begin{itemize}
\item The expected number of occupied cells that are hit by at least one unseated player is at most
$(N-u)\bigl(1-(1-1/N)^u\bigr)\ \le\ (N-u)\cdot \frac{u}{N}\ \le\ u$,
so expected regret contributed by  {occupied} cells is $\le u$ (each such collision zeros that cell’s reward).
\item Among the $u$ free cells, the expected number that are  {not} uniquely chosen by exactly one unseated player is
$u\left[1 - u\cdot \tfrac{1}{N}\cdot (1-\tfrac{1}{N})^{u-1}\right]\ \le\ u$,
so expected regret from  {free} cells is also $\le u$.
\end{itemize}

Thus $\EE[\text{regret}_t\mid U_t=u]\le 2u$. 

Summing over the seating phase,
\[
\EE[R_{MC}]\ \le\ 2\,\EE\!\left[\sum_{t=0}^{T_{MC}-1} U_t\right].
\]

Define the potential $G(u):=\sum_{v=1}^{u}\frac{v}{\Delta(v)}$. 

By the same drift argument as in Theorem~\ref{thm:mc-time-app}, one shows
$\EE\!\left[\sum_{t< T_{MC}} U_t\right]\ \le\ G(N)=\sum_{v=1}^{N}\frac{v}{\Delta(v)}$.

Using $\Delta(v)\ge v^2/(eN)$ gives $\sum_{v=1}^{N}\frac{v}{\Delta(v)}\le eN \sum_{v=1}^{N}\frac{1}{v}\le eN(1+\ln N)$.

Therefore $\EE[R_{MC}]=O(N\log N)$. We keep Corollary~\ref{cor:mc-regret} in the main text for simplicity, as it is horizon-independent and sufficient for our overall bounds.
\end{remark}


\bigskip



\section*{Appendix E: Proof of Proposition~\ref{prop:in-cell} (In-Cell Regret)}
\label{app:in-cell}

We prove the standard minimax rate for a single player optimizing within a fixed cell.
Throughout this appendix, rewards are bounded in $[0,1]$ (consistent with Appendix~B), and $\mu$ is $L$-Lipschitz on the hypercube cell $C\subset\mathbb R^d$ of side length $h$ in the Euclidean norm.

\paragraph{Reduction to the unit cube.}
Let $\phi:[0,1]^d\to C$ be the affine bijection $\phi(x')=x_0+h\,x'$ that maps the unit cube onto $C$ (for some cell origin $x_0$).
Define $\mu'(x'):=\mu(\phi(x'))$ for $x'\in[0,1]^d$.
Then, for any $x',y'\in[0,1]^d$,
\[
|\mu'(x')-\mu'(y')|
\;=\;
|\mu(\phi(x'))-\mu(\phi(y'))|
\;\le\; L\, \|\phi(x')-\phi(y')\|_2
\;=\; L h\, \|x'-y'\|_2.
\]
Thus $\mu'$ is $L'$-Lipschitz on $[0,1]^d$ with $L':=Lh$.

\paragraph{Known minimax rate on the unit cube.}
For the $d$-dimensional Lipschitz bandit on $[0,1]^d$ with Lipschitz constant $L'$, there exist algorithms (e.g., the Zooming algorithm \citep{Kleinberg}) whose expected regret over any horizon $T'\ge 1$ satisfies
\begin{equation}
\label{eq:unit-cube-rate}
\EE\big[R_{[0,1]^d}(T')\big]
\;\le\;
c_d\,(L')^{\frac{d}{d+2}}\, (T')^{\frac{d+1}{d+2}} + c'_d,
\end{equation}
where $c_d,c'_d$ depend only on $d$.
This result is classical; see, e.g., Kleinberg et al. \citep{Kleinberg} or Slivkins \citep{slivkins2019introduction}.

\paragraph{Combining.}
Applying \eqref{eq:unit-cube-rate} to $\mu'$ and substituting $L'=Lh$ gives
\[
\EE\big[R_{\mathrm{in}}^{(C)}(T')\big]
\;\le\;
c_d\,(Lh)^{\frac{d}{d+2}}\,(T')^{\frac{d+1}{d+2}} + c'_d,
\]
which is exactly Proposition~\ref{prop:in-cell}.
\qed

\medskip

\noindent\textbf{Remarks.}
(i) The proof above is intentionally short: it isolates the $h$-dependence via rescaling and then cites a standard unit-cube result. If desired, one may instantiate a concrete algorithm (e.g., Zooming) and track constants; this does not affect the rate or the $(Lh)^{d/(d+2)}$ dependence.
(ii) If one prefers finite-armed baselines, an epochic discretize-and-explore scheme on grids of mesh $\asymp (Lh)^{2/(d+2)}\,2^{e/(d+2)}$ per coordinate also yields the same rate by balancing exploration and discretization errors; we omit these routine details.


\section*{Appendix F: Global Regret Bounds (Theorem~\ref{thm:global})}
\label{app:global}

We assemble the end-to-end bound and reconcile expectation-level failure terms with the main-text statement. Throughout, per-round reward is in $[0,1]$ for each player; thus the per-round system benchmark (sum of the top-$N$ cell maxima) is at most $N$.

\subsection*{F.1.\; Clean event and failure budgeting}

Let $\mathcal{E}_I$ and $\mathcal{E}_{II}$ be the Phase~I and Phase~II success events as defined in Appendices~B and~C, respectively (valid brackets and coverage/accuracy).
Set
\[
\delta_{I}\ =\ \delta_{II}\ =\ \frac{\delta_{sys}}{2N}.
\]
By union bounds across players and cells (already accounted for in Appendices~B and~C), we have
\[
\Pr(\mathcal{E}_I)\ \ge\ 1-\frac{\delta_{sys}}{2N},
\qquad
\Pr(\mathcal{E}_{II})\ \ge\ 1-\frac{\delta_{sys}}{2N}.
\]
Define the global clean event $\mathcal E:=\mathcal E_I\cap \mathcal E_{II}$ for which
\begin{equation}
\label{eq:clean-event-budget}
\Pr(\mathcal E)\ \ge\ 1-\frac{\delta_{sys}}{N}.
\end{equation}
We write $R_{\cont}(T)$ for the total regret up to time $T$ and decompose its expectation by indicators of $\mathcal E$:
\[
\EE[R_{\cont}(T)]
\;=\;
\EE\big[R_{\cont}(T)\,\mathbf 1\{\mathcal E\}\big]
+\EE\big[R_{\cont}(T)\,\mathbf 1\{\mathcal E^c\}\big].
\]
Since per-round regret is at most $N$, we have
\begin{equation}
\label{eq:failure-expectation}
\EE\big[R_{\cont}(T)\,\mathbf 1\{\mathcal E^c\}\big]
\ \le\ N T \,\Pr(\mathcal E^c)
\ \le\ \delta_{sys}\, T,
\end{equation}
which matches the main-text term.

\subsection*{F.2.\; Identification and seating terms (conditioned on $\mathcal E$)}

Condition on $\mathcal E$. During Phase~I and Phase~II, each round contributes at most $N$ to regret:
\begin{equation}
\label{eq:phaseI-II}
\EE\!\left[R_{I}(T_0)+R_{II}(T_1)\,\big|\,\mathcal E\right] \ \le\ N(T_0+T_1).
\end{equation}
We assume the $\varepsilon$-uniqueness condition of Definition~\ref{def:eps-uniq} (main text) in Theorem~\ref{thm:global}, which guarantees that all players identify the same $N$ cells (Lemma~\ref{lem:consensus} in Appendix~C).
Musical Chairs (Appendix~D) is then run on this fixed set; its randomness is independent of reward noise used to define $\mathcal E$.
Therefore,
\begin{equation}
\label{eq:mc-condition}
\EE\!\left[R_{MC}(T_{MC})\,\big|\,\mathcal E\right]
\ =\ \EE\!\left[R_{MC}(T_{MC})\right]
\ \le\ c_{MC}\,N^2,
\end{equation}
for an absolute constant $c_{MC}$ (Appendix~D).

\subsection*{F.3.\; In-cell term and end-to-end bound}

On $\mathcal E$, the Phase~III processes are collision-free and decoupled across players.
For any player $j$, Proposition~\ref{prop:in-cell} gives
\[
\EE\!\left[R_{\mathrm{in}}^{(C_j)}(T^{(j)}_{\mathrm{in}})\,\big|\,\mathcal E\right]
\ \le\ c_d\,(Lh)^{\frac{d}{d+2}}\,(T^{(j)}_{\mathrm{in}})^{\frac{d+1}{d+2}} + c'_d
\ \le\ c_d\,(Lh)^{\frac{d}{d+2}}\,T^{\frac{d+1}{d+2}} + c'_d,
\]
and summing over $j\in[N]$,
\begin{equation}
\label{eq:phaseIII-sum}
\sum_{j=1}^N \EE\!\left[R_{\mathrm{in}}^{(C_j)}(T^{(j)}_{\mathrm{in}})\,\big|\,\mathcal E\right]
\ \le\ c_d\,N\,(Lh)^{\frac{d}{d+2}}\,T^{\frac{d+1}{d+2}} + N c'_d.
\end{equation}
Combining \eqref{eq:failure-expectation}, \eqref{eq:phaseI-II}, \eqref{eq:mc-condition}, and \eqref{eq:phaseIII-sum} yields
\[
\EE[R_{\cont}(T)]
\ \le\ N(T_0+T_1) + c_{MC}N^2 + c_d\,N\,(Lh)^{\frac{d}{d+2}}\,T^{\frac{d+1}{d+2}} + N c'_d + \delta_{sys} T.
\]
Absorbing the additive $Nc'_d$ into the (horizon-independent) coordination constant completes the proof of Theorem~\ref{thm:global}.
\qed

\medskip

\noindent\textbf{Remarks.}
(i) The term $N(T_0+T_1)+c_{MC}N^2$ is strictly horizon-independent only when $\delta_{sys}$ is fixed. If one instead sets $\delta_{sys}=\delta_{sys}(T)$, e.g.\ $\delta_{sys}=1/T$ or $\delta_{sys}=1/(NT)$, so that the explicit failure contribution is $O(1)$ in expectation, then the dependence on $T$ enters only through the logarithms in the Phase~I/II radii and therefore changes the bound only by additional polylogarithmic factors.
(i) The quantity \(N(T_0+T_1)+c_{MC}N^2\) is strictly horizon-independent only when \(\delta_{sys}\) is treated as a fixed confidence parameter. If one instead chooses \(\delta_{sys}=\delta_{sys}(T)\) (for example \(\delta_{sys}=O(1/T)\)) so that the failure contribution \(\delta_{sys}T\) is \(O(1)\) in expectation, then the Phase~I/II radii acquire additional \(\log T\) factors, and so do \(T_0\) and \(T_1\). Thus, in the expected-regret view the coordination term is best understood as polylogarithmic in \(T\), rather than strictly \(T\)-independent. These logarithmic factors are absorbed into \(\tilde O(\cdot)\).
(ii) The proof above uses only consensus (from $\varepsilon$-uniqueness) to run MC on a fixed target set; no other structural gap is used in Phase~III.








\section*{Appendix G: Gap-Free Analysis—Consensus, Baselines, Limits, and a Conditional Epochic Recovery}
\label{app:gapfree}

This section gives a complete treatment of the gap-free regime referenced in Section~\ref{sec:global_guarantees}. Our goals are:
\begin{enumerate}
\item to formalize a communication-free public dither mechanism that guarantees consensus among players in Phase~II selection and to prove it correct with safe constants;
\item to provide fully general guarantees that hold without extra assumptions on the instance: a single-shot gap-free bound and a restart lower bound showing that restarting global identification each epoch is too costly under the Phase~II sampling analyzed in Appendices~B-D;
\item to state and prove a conditional epochic recovery theorem under an extra assumption compared to Phase~II (a public coverage/scheduling property).
\end{enumerate}

Throughout this appendix, we use the failure budgeting of Appendix~F so that the contribution of failure events to expected regret is at most $\delta_{\text{sys}}T$.



\subsection*{G.1.\; Communication-free consensus via a public dither with a guaranteed gap}
\label{subsec:public-dither}

In the gap-free regime, the refined LCBs $\{\LCB^{(1)}_j(C)\}_C$ produced in Phase~II can differ slightly across players, potentially leading to different top-$N$ sets. We enforce consensus without communication by adding a public deterministic \emph{dither} (randomness) $\xi(C)$ to the LCBs before ranking cells. Crucially, we ensure a minimum pairwise gap in $\xi$ so that the dither dominates cross-player LCB fluctuations for every pair of cells.

\paragraph{Internal vs.\ external precision and probe budget.}
Fix a target external precision $\varepsilon_{\text{main}}>0$ for the selection of $N$ cells at the end of Phase~II. Internally, Phase~II refines brackets to width
\[
\varepsilon_{\mathrm{int}}:=\frac{\varepsilon_{\text{main}}}{4},
\]
i.e., for all cells $C$ and all players $j$,
\[
\UCB^{(1)}_j(C)-\LCB^{(1)}_j(C)\ \le\ \varepsilon_{\mathrm{int}}.
\]
This is achieved in Appendix~C by choosing an $\eta$-net (probe spacing $\eta$) and a per-probe success budget $b$ so that $2r_1+L\eta\le \varepsilon_{\mathrm{int}}$, where $r_1=\sqrt{\beta_1/(2b)}$ and $\beta_1$ is the usual anytime log factor.\footnote{See Appendix~C (coverage lemma and anytime concentration), where we use law-of-total-probability removal of conditioning and an anytime union bound across the random counts $s\ge b$ to obtain uniform-in-time concentration at each probe.}

\paragraph{Public dither with a guaranteed minimum gap.}
Let $\{C_1,\dots,C_K\}$ be the cells in a fixed public order (e.g., lexicographic). Set
\[
\eta_{\mathrm{dit}}:=\frac{3\,\varepsilon_{\text{main}}}{4},
\qquad
\xi(C_m):=\frac{m-1}{K-1}\,\eta_{\mathrm{dit}},\quad m=1,\dots,K.
\]
Thus the minimum pairwise dither gap is $\Delta_\xi:=\eta_{\mathrm{dit}}/(K-1)$. 

We increase the per-probe success budget $b$ by a constant (in $T$) factor so that
\begin{equation}
\label{eq:dither-gap-dominates}
4r_1\ \le\ \Delta_\xi\ =\ \frac{\eta_{\mathrm{dit}}}{K-1}.
\end{equation}
(Equivalently, we reduce $r_1$ by a constant factor; this changes Phase~II constants but not rates in~$T$.) Each player ranks cells by the public \emph{score}
\[
\mathrm{Score}_j(C):=\LCB^{(1)}_j(C)+\xi(C)
\]
and selects the $N$ cells with largest Scores (ties broken lexicographically).

\begin{lemma}[Consensus and $\varepsilon_{\text{main}}$-optimality with public dither]
\label{lem:dither-consensus}
On the Phase~II accuracy event (Appendix~C) with bracket width $\le \varepsilon_{\mathrm{int}}$ for all cells, the public dither rule above ensures, with the same high probability:
\begin{enumerate}
\item \textbf{Consensus:} All players select the same top-$N$ set $S^{\mathrm{dit}}$.
\item \textbf{$\varepsilon_{\text{main}}$-optimality:} Every $C\in S^{\mathrm{dit}}$ satisfies $\mu^\ast(C)\ge \mu^\ast_{(N)}-\varepsilon_{\text{main}}$.
\end{enumerate}
\end{lemma}

\begin{proof}
(\emph{Consensus.}) On the Phase~II accuracy event, for any cell $C$ and players $j,k$,
\(
|\LCB^{(1)}_j(C)-\LCB^{(1)}_k(C)|\le 2r_1.
\)
Hence for any pair $(C,C')$,
\[
\sup_{j,k}\Big|\big(\LCB^{(1)}_j(C)-\LCB^{(1)}_j(C')\big)
-\big(\LCB^{(1)}_k(C)-\LCB^{(1)}_k(C')\big)\Big|
\le 4r_1.
\]
By construction $|\xi(C)-\xi(C')|\ge \Delta_\xi\ge 4r_1$ for  {every} pair $(C,C')$ (eq.~\eqref{eq:dither-gap-dominates}). Therefore, the sign of
\[
\big(\LCB^{(1)}_j(C)-\LCB^{(1)}_j(C')\big)+\big(\xi(C)-\xi(C')\big)
\]
is the same for all $j$, i.e., all players induce the same total order by $\mathrm{Score}_j(\cdot)$ and select the same top-$N$ set.

( {$\varepsilon_{\text{main}}$-optimality.}) Let $\theta^{\mathrm{dit}}$ be the $N$-th largest Score. For any true top-$N$ cell $C^\ast$,
$\LCB^{(1)}_j(C^\ast)\ge \mu^\ast(C^\ast)-\varepsilon_{\mathrm{int}}\ge \mu^\ast_{(N)}-\varepsilon_{\mathrm{int}}$ and $\xi(C^\ast)\ge 0$; hence $\theta^{\mathrm{dit}}\ge \mu^\ast_{(N)}-\varepsilon_{\mathrm{int}}$. For any selected $C$,
\[
\mu^\ast(C)\ \ge\ \LCB^{(1)}_j(C)\ \ge\ \theta^{\mathrm{dit}}-\xi(C)\ \ge\ \mu^\ast_{(N)}-(\varepsilon_{\mathrm{int}}+\eta_{\mathrm{dit}})\ =\ \mu^\ast_{(N)}-\varepsilon_{\text{main}}.\qedhere
\]
\end{proof}

\paragraph{Data reuse across epochs.}
Unless stated otherwise, we assume Phase~II reuses all probe data across epochs; we do not restart identification. Union over $K_{\text{ep}}=\Theta(\log T)$ epochs adds an extra $\log K_{\text{ep}}$ into the radii’s $\beta$, which is absorbed by $\tilde O(\cdot)$.

\subsection*{G.2.\; A fully general, single-shot gap-free guarantee}
\label{subsec:single-shot}

We first prove a gap-free guarantee that requires  {no} structural assumptions beyond Lipschitzness. Phase~I and Phase~II are run once at precision $\varepsilon$; then we apply Lemma~\ref{lem:dither-consensus} to select a common $N$-cell set, seat via Musical Chairs (Appendix~D), and run Phase~III (Appendix~E).

\begin{proposition}[Single-shot, gap-free baseline]
\label{prop:gap-free-single-shot}
For any $L$-Lipschitz mean on $[0,1]^d$ and horizon $T$, there exists a choice of $\varepsilon$ such that
\[
\EE[R_{\cont}(T)]\ =\ \tilde O\!\Big(N\, (K(Lh)^d)^{\frac{1}{d+3}}\, T^{\frac{d+2}{d+3}}\Big)\ =\ \tilde O\!\Big(N\, L^{\frac{d}{d+3}}\, T^{\frac{d+2}{d+3}}\Big),
\]
using $K=\lceil 1/h\rceil^d$ and $K h^d\in[1,2^d)$, whence $K(Lh)^d=\Theta(L^d)$. The $\tilde O(\cdot)$ hides logarithmic factors in $N,K,1/\delta_{\text{sys}}$.
\end{proposition}

\begin{proof}
On the clean event (Appendix~F), the Phase~II time at target width $\varepsilon$ satisfies (Appendix~C)
\[
T_1(\varepsilon)\ =\ \tilde O\!\big(M_{\mathrm{act}}(Lh)^d\,\varepsilon^{-(d+2)}\big),
\]
and in the worst case $M_{\mathrm{act}}\le K$. Each identification round contributes at most $N$ regret, hence
$R_{\mathrm{ID}}=\tilde O\!\big(NK(Lh)^d\,\varepsilon^{-(d+2)}\big)$. 

By Lemma~\ref{lem:dither-consensus}, Phase~III suboptimality is $R_{\mathrm{Sub}}\le N\varepsilon T$, while in-cell learning is $R_{\mathrm{Learn}}=\tilde O\!\big(N (Lh)^{\frac{d}{d+2}} T^{\frac{d+1}{d+2}}\big)$ (Appendix~E). 

Balancing $R_{\mathrm{ID}}$ and $R_{\mathrm{Sub}}$ gives $\varepsilon^\star\asymp (K(Lh)^d/T)^{1/(d+3)}$ and
\[
R_{\mathrm{ID}}+R_{\mathrm{Sub}}\ =\ \tilde O\!\Big(N\, (K(Lh)^d)^{\frac{1}{d+3}}\, T^{\frac{d+2}{d+3}}\Big).
\]
Since $\frac{d+2}{d+3}>\frac{d+1}{d+2}$ for $d\ge 1$, this dominates $R_{\mathrm{Learn}}$; adding the $O(N^2)$ seating constant and the $\delta_{\text{sys}}T$ failure contribution yields the claim.
\end{proof}

\subsection*{G.3.\; Why restart-style epochic identification fails}
\label{subsec:restart-fail}

We formalize that restarting Phase~II at each epoch (instead of reusing data) incurs linear identification overhead in worst-case Lipschitz instances.

\begin{proposition}[Lower bound for restart-style epochic identification]
\label{prop:epochic-lb}
Suppose that at the start of each epoch $k$ (of length $T_k$) the algorithm recomputes Phase~II brackets to width $\varepsilon_k$ by running the collision-censored sampling of Phases~I/II afresh, without reusing earlier probe data. Then for worst-case $L$-Lipschitz instances and any epoch schedule with $\sum_k T_k=T$,
\[
\EE\Big[\sum_k R_{\mathrm{ID}}^{(k)}\Big]\ =\ \Omega(NT).
\]
\end{proposition}

\begin{proof}
By Appendix~C (coverage and probe-level anytime bounds), achieving width $\varepsilon_k$ requires
\[
\Omega\!\big((Lh)^d\,\varepsilon_k^{-(d+2)}\big)
\]
rounds (up to logs), since the per-round success probability scales as $q_{M_{\mathrm{act}},\eta}\asymp 1/(M_{\mathrm{act}}P(\eta))$ with $M_{\mathrm{act}}\asymp K$ and $P(\eta)\asymp (Lh/\varepsilon_k)^d$ in the worst case. 

Each identification round contributes at most $N$ regret, so $R_{\mathrm{ID}}^{(k)}=\Omega\!\big(N(Lh)^d\,\varepsilon_k^{-(d+2)}\big)$. 

Balancing $N\varepsilon_k T_k$ and $N(Lh)^d\,\varepsilon_k^{-(d+2)}$ yields $\varepsilon_k\asymp T_k^{-1/(d+2)}$ and $\varepsilon_k^{-(d+2)}\asymp T_k$, hence $\sum_k R_{\mathrm{ID}}^{(k)}=\Omega\!\big(N(Lh)^d \sum_k T_k\big)=\Omega(NT)$ (absorbing $(Lh)^d$ into the constant if $h$ is fixed).
\end{proof}

\paragraph{Remark (data reuse).}
Proposition~\ref{prop:epochic-lb} targets  {restart} epochic identification. If Phase~II aggregates probe data across epochs (our default), the incremental work per epoch is smaller; however, without further structure (next section) the cumulative identification overhead remains too large to be dominated by the Phase~III learning term in the worst case.

\subsection*{G.4.\; Conditional epochic recovery under a public coverage/scheduling property}
\label{subsec:conditional-recovery}

We now state a proof of the rate in the main text. Given the negative result in the previous subsection, we require an additional condition (public coverage/scheduling) for Phase~II that is orthogonal to the reward statistics and can be viewed as a systems-level assumption.
We want to emphasize that this was not assumed in Appendices~B-D (which used uniform randomization over active cells and probes with collision censorship).

\begin{assumption}[Public stratified coverage for Phase~II]
\label{ass:coverage}
In any epoch with probe spacing $\eta$ and per-cell probe count $P(\eta)$, there exists a public, communication-free schedule with the following properties:
\begin{enumerate}[label=(\alph*)]
\item For each active probe $(C,z)$, there is a publicly known set $\mathcal{R}(C,z)$ of rounds with $|\mathcal{R}(C,z)|=\Theta(P(\eta))$ per $P(\eta)$-length block, and in each $t\in\mathcal{R}(C,z)$ exactly one player samples $z$ in $C$ and no other player samples any point in $C$; i.e., the per-round success probability for $(C,z)$ is $\Omega(1)$ on its scheduled rounds.
\item Across the epoch, the schedule assigns $O(1)$ such $(C,z)$ per round per player (constant load), enabling parallelism without collisions.
\end{enumerate}
\end{assumption}

\paragraph{Near-optimality (zooming) dimension.}
We use the standard instance-complexity notion: there exist $d^{*}\in[0,d]$ and $C>0$ such that $\X_\varepsilon:=\{x:\mu^{*}-\mu(x)\le \varepsilon\}$ can be covered by at most $C\,\varepsilon^{-d^{*}}$ Euclidean balls of radius $\Theta(\varepsilon/L)$ (see Kleinberg et al. \citep{Kleinberg}).

\begin{lemma}[Active-cell count under $d^{*}$]
\label{lem:Mact-dstar}
If $\X_\varepsilon$ admits a cover by $O(\varepsilon^{-d^{*}})$ balls of radius $c\,\varepsilon/L$ with $c\,\varepsilon/L\le h/4$, then the number of partition cells that intersect $\X_\varepsilon$ satisfies $M_{\mathrm{act}}(\varepsilon)=O(\varepsilon^{-d^{*}})$. For the finitely many coarser $\varepsilon$, the bound holds up to a constant factor absorbed in $\tilde O(\cdot)$.
\end{lemma}

\begin{proof}
Each ball of radius $c\,\varepsilon/L\le h/4$ intersects $O(1)$ cells; there are $O(\varepsilon^{-d^{*}})$ balls.
\end{proof}

\begin{proposition}[Per-epoch identification under Assumption~\ref{ass:coverage} and $d^{*}$]
\label{prop:per-epoch-coverage}
Fix an epoch with target width $\varepsilon_k$. Under Assumption~\ref{ass:coverage} and near-optimality dimension $d^{*}$, the number of successful probe  {samples} is $\tilde O(\varepsilon_k^{-(d^{*}+2)})$; since the per-probe success probability on scheduled rounds is $\Omega(1)$, the number of  {rounds} is also $\tilde O(\varepsilon_k^{-(d^{*}+2)})$ (up to logarithmic factors).
\end{proposition}

\begin{proof}
By Lemma~\ref{lem:Mact-dstar}, the number of probes is $O(\varepsilon_k^{-d^{*}})$. 

Each probe needs $b=\Theta(\varepsilon_k^{-2})$ successful samples to reach noise radius $O(\varepsilon_k)$ by the anytime concentration used in Appendix~C. 

Assumption~\ref{ass:coverage}(a)--(b) guarantees $\Omega(1)$ success probability for each probe on its scheduled rounds and constant load per round, hence the round budget is $\tilde O(\varepsilon_k^{-d^{*}}\cdot \varepsilon_k^{-2})$.
\end{proof}

\begin{theorem}[Conditional epochic, gap-free recovery]
\label{thm:conditional-epochic}
Assume $d^{*}\le d-1$ and Assumption~\ref{ass:coverage}. Run epochs of lengths $T_k=2^k$ with precisions $\varepsilon_k\propto 2^{-k/(d+2)}$, reuse all data across epochs, and use public dither (Lemma~\ref{lem:dither-consensus}). Then
\[
\sum_{k} \EE\big[R_{\mathrm{ID}}^{(k)}\big]\ =\ \tilde O\!\Big(N\,T^{\frac{d^{*}+2}{d+2}}\Big),
\]
which is dominated by the Phase~III learning term $\tilde O\!\big(N(Lh)^{\frac{d}{d+2}}T^{\frac{d+1}{d+2}}\big)$ when $d^{*}\le d-1$. Consequently, the main-text epochic gap-free corollary holds under Assumption~\ref{ass:coverage}.
\end{theorem}

\begin{proof}
By Proposition~\ref{prop:per-epoch-coverage}, per-epoch identification rounds are $\tilde O(\varepsilon_k^{-(d^{*}+2)})$, hence the identification regret is $N$ times this. 

With $\varepsilon_k\propto 2^{-k/(d+2)}$, summing a geometric series over $K_{\text{ep}}=\Theta(\log T)$ epochs yields $\tilde O\!\big(N\,T^{\frac{d^{*}+2}{d+2}}\big)$. 

Since $d^{*}\le d-1$, we have $\frac{d^{*}+2}{d+2}\le \frac{d+1}{d+2}$, so identification is dominated by Phase~III learning (Appendix~E). 

Add the $O(N^2)$ seating constant and the $\delta_{\text{sys}}T$ failure contribution (Appendix~F). 

Reusing probe data across epochs adds at most a $\log K_{\text{ep}}$ factor in the radii, absorbed by~$\tilde O(\cdot)$.
\end{proof}








\bigskip






\section*{Appendix H: Distance-Threshold Collisions via Packing Reduction}
\label{app:packing}

This appendix provides a reduction from the distance-threshold collision model to the partition-style analysis used in the main text. The regret comparator in Theorem~\ref{thm:packing} is the packing-based benchmark $\OPT_{\pack}(r,\sigma,N)$; without additional geometric covering assumptions, we do not claim a uniform comparison to the best $\rho$-separated assignment.

\subsection*{H.1.\; Setup and notation}

Fix a collision threshold $\rho>0$. Let $Z=\{z_1,\dots,z_M\}\subset \X$ be an  {$r$-packing}, i.e., $\|z_i-z_{i'}\|_2\ge r$ for all $i\ne i'$, with some $r>\rho$. We assume
\begin{equation}
\label{eq:packing-feasible}
M=|Z|\ \ge\ N,
\end{equation}
which is necessary both for the comparator $\OPT_{\pack}(r,\sigma,N)=\sum_{m=1}^N \nu^\ast_{(m)}$ and for seating $N$ players on distinct balls.

Fix a radius $\sigma$ with
\begin{equation}
\label{eq:sigma-safe}
0<\sigma<\frac{r-\rho}{2}.
\end{equation}
Define the  {safe balls} $B_i:=\{x\in\X:\|x-z_i\|_2\le\sigma\}$ (balls are implicitly clipped to $\X$). For a Lipschitz mean $\mu$, let $\nu_i^\ast:=\sup_{x\in B_i}\mu(x)$ and let $\nu_{(1)}^\ast\ge\cdots\ge \nu_{(M)}^\ast$ be the sorted values. The packing-based one-round benchmark is
\[
\OPT_{\pack}(r,\sigma,N)\ :=\ \sum_{m=1}^N \nu_{(m)}^\ast.
\]

\begin{lemma}[Collision safety across safe balls]
\label{lem:packing-safety}
If $\sigma$ satisfies \eqref{eq:sigma-safe}, then for any $i\ne i'$ and any $x\in B_i$, $x'\in B_{i'}$, we have $\|x-x'\|_2>\rho$. Hence inter-ball collisions are impossible.
\end{lemma}

\begin{proof}
Triangle inequality and $r$-packing: $\|x-x'\|_2 \ge \|z_i-z_{i'}\|_2-\|x-z_i\|_2-\|x'-z_{i'}\|_2 \ge r-2\sigma>\rho$.
\end{proof}

\subsection*{H.2.\; Reduction to the partition model}

We treat the index family $\{B_1,\dots,B_M\}$ as a ``virtual partition.” The multi-phase protocol (Phases I–III and II$\tfrac{1}{2}$) is run  {verbatim} with the following substitutions:
\begin{itemize}
\item \textbf{Phase I (coarse identification).} Each round, a player samples a ball index $I\in[M]$ uniformly and probes its center $z_I$ (or any fixed representative in $B_I$). The per-round success probability for a given $(\text{player},\text{ball})$ is
\[
p_M\ :=\ \frac{1}{M}\Bigl(1-\frac{1}{M}\Bigr)^{N-1},
\]
identical to the cell-based $p_K$ with $K$ replaced by $M$. The coarse brackets mirror Appendix~B with $K\mapsto M$ and with the ball geometry:
\[
\LCB^{(0)}_j(B_i)\ =\ \widehat\mu^{(0)}_j(z_i)-r^{(0)}_j(B_i),
\qquad
\UCB^{(0)}_j(B_i)\ =\ \widehat\mu^{(0)}_j(z_i)+r^{(0)}_j(B_i)+L\,\sigma,
\]
since $\mu^\ast(B_i)\le \mu(z_i)+L\max_{x\in B_i}\|x-z_i\|_2=\mu(z_i)+L\sigma$.
\item \textbf{Phase II (local peek).} For each active ball $B_i$, instantiate an internal $\eta$-net $Z_\eta(B_i)$; standard volumetric arguments give $|Z_\eta(B_i)|\le C_d\,(\sigma/\eta)^d$. All Phase‑II lemmas (coverage, anytime accuracy, refined brackets) from Appendix~C carry through with the replacements $K\mapsto M$, $h\mapsto \sigma$, $D_h\mapsto D_\sigma:=2\sigma$.
\item \textbf{Phase II$\tfrac{1}{2}$ (seating).} Musical Chairs is unchanged. By Lemma~\ref{lem:packing-safety}, once one player is seated per ball, inter-ball collisions cannot occur.
\item \textbf{Phase III (within-ball optimization).} With players uniquely assigned to balls, the processes decouple. Rescaling a ball of radius $\sigma$ to the unit ball multiplies the Lipschitz constant by $\sigma$; by Appendix~E, the in-ball regret over $T'$ rounds satisfies
\[
\EE\!\left[R_{\mathrm{in}}^{(B_i)}(T')\right]\ \le\ c_d\,(L\sigma)^{\frac{d}{d+2}}\,(T')^{\frac{d+1}{d+2}}+c'_d.
\]
\end{itemize}

\subsection*{H.3.\; Regret bound (proof of Theorem~\ref{thm:packing})}

Combining Phase~I/II identification costs, the seating cost (Appendix~D), and the sum of in-ball regrets (Appendix~E) exactly as in Appendix~F yields
\[
\EE[R_{\cont}(T)]
\ \le\
\underbrace{N(T_0+T_1)}_{\text{identification}}
\ +\ 
\underbrace{c_{MC}N^2}_{\text{seating}}
\ +\
\underbrace{c_d\,N\,(L\sigma)^{\frac{d}{d+2}}\,T^{\frac{d+1}{d+2}}}_{\text{learning}}
\ +\ \delta_{sys}T,
\]
where $T_1=\tilde O\!\big(M\,(L\sigma)^d\,\varepsilon^{-(d+2)}\big)$ (Appendix~C.6 with $K\mapsto M$ and $h\mapsto \sigma$). This is identical in form to Theorem~\ref{thm:global} after the substitutions $(K,h)\mapsto (M,\sigma)$.

\begin{remark}[Comparator choice]
\label{rem:pack-vs-true}
We compare to $\OPT_{\pack}(r,\sigma,N)$ by design. Uniformly relating the true $\rho$-separated optimum to $\OPT_{\pack}(r,\sigma,N)$ would require a  {covering} guarantee in addition to packing; without it, the two comparators need not be close. Even with coverage radius $O(r)$, the model-mismatch term per round can be $\Omega(NL r)$, which is not negligible for fixed $r$.
\end{remark}










\section*{Appendix I: Minimax Lower Bound}
\label{app:lower}

We prove Theorem~\ref{thm:lower}. The ingredients are: (i) a standard $\Omega(\sqrt{K\tau})$ minimax lower bound for  {finite-armed} stochastic bandits, and (ii) an $L$-Lipschitz embedding of $K'=\Theta(m^d)$ ``arms” within each of $N$ distinct cells, with a cone-shaped spike at one grid point.

\subsection*{I.1.\; Finite-armed minimax lower bound (cited)}
For every $K\ge 2$ and $\tau\ge K$, there exists a universal constant $c>0$ such that
\begin{equation}
\label{eq:finite-lb}
\inf_{Alg}\ \sup_{\nu}\ \EE_{\nu}\!\left[\sum_{t=1}^{\tau} (\mu^\ast-\mu(A_t))\right]\ \ge\ c\,\sqrt{K\,\tau},
\end{equation}
where the supremum is over all product reward distributions with means in $[0,1]$. See, e.g., Slivkins \citep{slivkins2019introduction}.

\subsection*{I.2.\; Proof of Theorem~\ref{thm:lower}}

Partition $[0,1]^d$ into $K=\lceil 1/h\rceil^d$ hypercubes $\Pcal=\{C_1,\dots,C_K\}$ of side $h$. Assume
\[
K=\lceil 1/h\rceil^d\ \ge\ N,
\]
and select $N$ distinct cells $\{C_{i_1},\dots,C_{i_N}\}$. Within each chosen cell $C_{i_j}$, place a regular grid $G$ of resolution $m$ per coordinate; neighboring grid points are at Euclidean distance $h/m$. Let $K'=(m+1)^d$ be the number of grid points in $G$.

For $\theta=(\theta_1,\dots,\theta_N)$ with $\theta_j\in\{1,\dots,K'\}$, define a Lipschitz mean $\mu_\theta$ as follows. In each chosen cell $C_{i_j}$, let $g_{j,\theta_j}\in G$ be the selected “spike” grid point and set
\[
\mu_\theta(x)\ :=\
\max\!\Big\{\tfrac{1}{2},\ \tfrac{1}{2}+\Delta\ -\ L\,\|x-g_{j,\theta_j}\|_2\Big\},
\qquad x\in C_{i_j},
\]
and set $\mu_\theta(x)\equiv\tfrac{1}{2}$ for $x$ in all other cells. Since $x\mapsto \|x-g\|_2$ is 1-Lipschitz and $\max(\cdot,\cdot)$ preserves Lipschitz constant, we have $\mu_\theta\in\mathcal L(L)$. At the spike $g_{j,\theta_j}$, the value is $1/2+\Delta$; at any other grid point $g\neq g_{j,\theta_j}$, the value is at most $1/2+\Delta - L(h/m)$, hence the spike arm is uniquely optimal.

Let $\OPT_{\cont}(\Pcal,N)$ be the per-round partition benchmark. In our construction, exactly the $N$ chosen cells attain maximum $1/2+\Delta$ and all others have maximum $1/2$, so
\[
\OPT_{\cont}(\Pcal,N)\ =\ \sum_{j=1}^{N} \Big(\tfrac{1}{2}+\Delta\Big)\ =\ N\Big(\tfrac{1}{2}+\Delta\Big).
\]

Consider the product prior over $\theta$ in which each $\theta_j$ is independent and uniform over the $K'$ grid points in $C_{i_j}$. By Yao’s minimax principle, the minimax expected regret is bounded below by the Bayes expected regret under this prior. Rewards and choices decouple across the $N$ special cells, and the per-round benchmark is additive across cells; therefore the Bayes expected regret equals the sum of the $N$ per-cell Bayes regrets. Each per-cell problem is a $K'$-armed stochastic bandit with rewards in $[0,1]$ and horizon $T$, so by \eqref{eq:finite-lb} the per-cell Bayes (hence minimax) regret is $\Omega(\sqrt{K' T})$. Summing over cells,
\[
\EE_{\mu_\theta}\!\left[R_{\cont}(T)\right]\ \ge\ c\,N\,\sqrt{K' T}\ \asymp\ c\,N\,m^{d/2}\,\sqrt{T}.
\]

Finally, choose parameters to ensure bounded rewards (take $\Delta\le 1/6$) and to match the worst-case finite-armed scaling under the $L$-Lipschitz constraint. Set
\[
\Delta\ =\ c_0\,\frac{L h}{m}\quad\text{with}\quad c_0\in(0,1/2],
\]
so that the spike height is consistent with the grid spacing and the gap at the nearest other grid point is at least $\Delta/2$. Optimizing the lower bound in $m$ (subject to $m\ge 2$ and $\Delta\le 1/6$) yields
\[
m\ \asymp\ (L h)^{\frac{2}{d+2}}\,T^{\frac{1}{d+2}},
\]
and hence
\[
\EE_{\mu_\theta}\!\left[R_{\cont}(T)\right]\ \gtrsim\ N\,(L h)^{\frac{d}{d+2}}\,T^{\frac{d+1}{d+2}}.
\]
Taking the supremum over $\theta$ concludes the proof of Theorem~\ref{thm:lower}.
\qed

\medskip

\noindent\textbf{Remarks.}
(i) Disjointness of cells suffices; ``non-adjacent” is inessential since collisions are intra-cell only.  
(ii) The same construction applies to the distance-threshold model by embedding spikes in $N$ safe balls of a packing (Appendix~H); at most one non-colliding observation per ball per round is possible, and the $N$-fold lower bound follows identically.






\input{experiments}



\section*{Appendix K: Parameter Summary}
\label{app:param-summary}

Table~\ref{tab:param-summary} collects the main quantities used in Phases I and II and the sufficient choices proved in Appendices~B and~C.

\begin{table}[h]
\centering
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{|p{0.16\linewidth}|p{0.28\linewidth}|p{0.46\linewidth}|}
\hline
Quantity & Meaning & Sufficient choice / scaling used in the analysis \\
\hline
\(p_K\) & Phase-I per-round success probability for a fixed (player, cell) pair & \(p_K=\frac{1}{K}\left(1-\frac{1}{K}\right)^{N-1}\) \\
\hline
\(\alpha\) & Target Phase-I center-estimation radius & User-chosen coarse accuracy level \\
\hline
\(T_0\) & Phase-I budget & It suffices that \eqref{eq:T0-consolidated} holds; equivalently \(T_0=\tilde O(p_K^{-1}\alpha^{-2})\) for fixed \(\alpha\) and fixed failure budget \\
\hline
\(\eta\) & Phase-II probe-net resolution & For target final maxima accuracy \(\varepsilon\), choose \(\eta=\varepsilon/(2L)\) \\
\hline
\(P_{\max}\) & Maximum number of probe points in one active cell & \(P_{\max}\le C_d (h/\eta)^d\) \\
\hline
\(\NumProbes\) & Total number of active probe triples \((j,C,z)\) & \(\NumProbes \le N M_{act} P_{\max}\) \\
\hline
\(b\) & Required successful samples per active probe & Choose \(b \ge \max\!\left\{4\log\frac{2\NumProbes}{\delta_{II}}, \frac{8\beta_1}{\varepsilon^2}\right\}\), where \(\beta_1=\log\frac{4\NumProbes}{\delta_{II}}\) \\
\hline
\(q_{M_{act},\eta}\) & Phase-II per-round success probability lower bound for a probe triple & \(q_{M_{act},\eta} \gtrsim \frac{1}{M_{act}}\left(\frac{\eta}{h}\right)^d \left(1-\frac{1}{N}\right)^{N-1}\) \\
\hline
\(T_1\) & Phase-II budget & \(T_1 \ge 2b/q_{M_{act},\eta}\), hence \(T_1=\tilde O\!\big(M_{act}(Lh)^d\varepsilon^{-(d+2)}\big)\) \\
\hline
\(\delta_I,\delta_{II}\) & Phase-wise failure budgets & Chosen so that \(\delta_I+\delta_{II}\le \delta_{sys}\); if \(\delta_{sys}\) depends on \(T\), the resulting \(T_0,T_1\) gain only extra logarithmic factors \\
\hline
\end{tabular}
\caption{Summary of the main design parameters and sufficient choices. The displayed bounds are sufficient choices used in the proofs, not optimized minima.}
\label{tab:param-summary}
\end{table}


