\documentclass[sigconf]{acmart}
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}


\copyrightyear{2026}
\acmYear{2026}
\setcopyright{cc}
\setcctype{by-nc-nd}
\acmConference[WWW '26]{Proceedings of the ACM Web Conference 2026}{April 13--17, 2026}{Dubai, United Arab Emirates}
\acmBooktitle{Proceedings of the ACM Web Conference 2026 (WWW '26), April 13--17, 2026, Dubai, United Arab Emirates}
\acmPrice{}
\acmDOI{10.1145/3774904.3792589}
\acmISBN{979-8-4007-2307-0/2026/04}



\usepackage{comment}
\usepackage{enumitem}
\usepackage{multirow}


\usepackage{algorithm}
\usepackage{algpseudocode}  %
\usepackage{amsmath}        %
\acmSubmissionID{rfp3241}
\settopmatter{printacmref=true}

\begin{document}

\title{GraphRAG-R1: Graph Retrieval-Augmented Generation with Process-Constrained Reinforcement Learning}

\newcommand{\methodname}{GraphRAG-R1}
\newcommand{\RLName}{Rollout Retrieval Enhanced GRPO}
\newcommand{\rlname}{rollout retrieval enhanced GRPO}
\newcommand{\RewardName}{Process-Constrained Reward}
\newcommand{\rewardname}{process-constrained reward}



\author{Chuanyue Yu}
\orcid{0009-0004-7818-9808}
\affiliation{
  \institution{Nankai University}
   \city{Binhai New Area}
  \state{Tianjin}
  \country{China}
}
\email{yuchuanyue@mail.nankai.edu.cn}

\author{Kuo Zhao}
\orcid{0009-0003-9033-2112}
\affiliation{
  \institution{Nankai University}
   \city{Binhai New Area}
  \state{Tianjin}
  \country{China}
}
\email{zhaokuo@mail.nankai.edu.cn}

\author{Yuhan Li}
\orcid{0000-0003-1324-5819}
\affiliation{
  \institution{HKUST Guangzhou}
   \city{Guangzhou}
   \state{Guangdong} 
  \country{China}
}
\email{yuhanli98@gmail.com}

\author{Heng Chang}
\orcid{0000-0002-4978-8041}
\authornote{Project co-leader.}
\affiliation{
  \institution{Huawei Technologies Ltd}
  \city{Haidian District}
  \state{Beijing}
  \country{China}
}
\email{changh.heng@gmail.com}

\author{Mingjian Feng}
\orcid{0009-0007-0345-762X}
\affiliation{
  \institution{Nankai University}
  \city{Binhai New Area}
  \state{Tianjin}
  \country{China}
}
\email{fengmingjian@mail.nankai.edu.cn}

\author{Xiangzhe Jiang}
\orcid{0009-0007-4243-9029}
\affiliation{
  \institution{Nankai University}
  \city{Binhai New Area}
  \state{Tianjin}
  \country{China}
}
\email{jiangxiangzhe@mail.nankai.edu.cn}

\author{Yufei Sun}
\orcid{0009-0001-9778-9575}
\affiliation{
  \institution{Nankai University}
   \city{Binhai New Area}
  \state{Tianjin}
  \country{China}
}
\email{yufei_sun@sina.com}

\author{Jia Li}
\orcid{0000-0002-6362-4385}
\affiliation{
  \institution{HKUST Guangzhou}
  \city{Guangzhou}
  \state{Guangdong} 
  \country{China}
}
\email{jialee@hkust-gz.edu.cn}

\author{Yuzhi Zhang}
\orcid{0000-0002-6729-925X}
\authornotemark[1]
\affiliation{
  \institution{Nankai University}
   \city{Binhai New Area}
  \state{Tianjin}
  \country{China}
}
\email{zyz@nankai.edu.cn}

\author{Qingyun Sun}
\orcid{0000-0003-1930-3848}
\affiliation{
  \institution{Beihang University}
  \city{Haidian District}
  \state{Beijing}
  \country{China}
}
\email{sunqy@buaa.edu.cn}

\author{Jianxin Li}
\orcid{0000-0001-5152-0055}
\affiliation{
  \institution{Beihang University}
  \city{Haidian District}
  \state{Beijing}
  \country{China}
}
\email{lijx@buaa.edu.cn}

\author{Ziwei Zhang}
\orcid{0000-0003-2451-843X}
\authornotemark[1]
\authornote{Corresponding author.}
\affiliation{
  \institution{Beihang University}
  \city{Haidian District}
  \state{Beijing}
  \country{China}
}
\email{zwzhang@buaa.edu.cn}



\renewcommand{\shortauthors}{Chuanyue Yu et al.}

\begin{abstract}
Graph Retrieval-Augmented Generation (GraphRAG) has shown great effectiveness in enhancing the reasoning abilities of Large Language Models (LLMs) by leveraging graph structures for knowledge representation and modeling complex real-world relationships. However, existing GraphRAG methods still face significant bottlenecks when handling complex problems that require multi-hop reasoning, as  %
their query and retrieval phases are largely based on pre-defined heuristics and do not fully utilize the reasoning potentials of LLMs.  
To address this problem, we propose \methodname, an adaptive GraphRAG framework by training LLMs with process-constrained outcome-based reinforcement learning (RL) to enhance the multi-hop reasoning ability. Our method can decompose complex problems, autonomously invoke retrieval tools to acquire necessary information, and perform effective reasoning.
Specifically, we utilize a modified version of Group Relative Policy Optimization (GRPO) that supports rollout-with-thinking capability to train the model. Next, we design two process-constrained reward functions. To handle the shallow retrieval problem, we design a Progressive Retrieval Attenuation (PRA) reward to encourage essential retrievals. Then, to handle the over-thinking problem, we design a Cost-Aware F1 (CAF) reward to balance the model performance with computational costs. 
We further design a phase-dependent training strategy, containing three training stages corresponding to cold start and these two rewards. These stages empower GraphRAG with format following, behavior shaping, and smartness optimization abilities, respectively.
Lastly, our method adopts a hybrid graph-textual retrieval to improve the reasoning capacity.
Extensive experimental results demonstrate that \methodname~significantly boosts LLM capabilities in solving complex reasoning problems compared to state-of-the-art GraphRAG methods on both in-domain and out-of-domain datasets. Furthermore, our framework can be flexibly integrated with various existing retrieval methods, consistently delivering performance improvements.









\end{abstract}

\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10010147.10010178.10010187</concept_id>
       <concept_desc>Computing methodologies~Knowledge representation and reasoning</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
   <concept>
       <concept_id>10010147.10010257</concept_id>
       <concept_desc>Computing methodologies~Machine learning</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
 </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computing methodologies~Knowledge representation and reasoning}
\ccsdesc[500]{Computing methodologies~Machine learning}

\keywords{Reinforcement Learning, GraphRAG, Knowledge Graph}

\maketitle
\newcommand\webconfavailabilityurl{https://doi.org/10.5281/zenodo.18349146}
\ifdefempty{\webconfavailabilityurl}{}{
\begingroup\small\noindent\raggedright\textbf{Resource Availability:}
The source code has been made publicly available at \url{https://doi.org/10.5281/zenodo.18349146} and can also be accessed via the project repository: \url{https://github.com/ycygit/GraphRAG-R1}. The model weights are available at \url{https://doi.org/10.57967/hf/7629} and \url{https://huggingface.co/yuchuanyue/GraphRAG-R1}.
\endgroup
}
\input{1-Intro}
\input{2-RelatedWork}
\input{3-Method}
\input{4-Exp}
\input{5-Conclusion}


\begin{acks}
This work was supported in part by the National Natural Science Foundation of China (No. 92570113, 62472018), the Natural Science Foundation of Tianjin (No. 24JCQNJC02170), and the Tianjin Science and Technology Plan Project (No. 24HHXCSS00001).
\end{acks}

\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}


\appendix

\input{6-Appendix}

\end{document}
