\documentclass[runningheads]{llncs}

\usepackage[T1]{fontenc}
\usepackage{graphicx}

\usepackage{fancyhdr}
\fancypagestyle{plain}{%
  \fancyhf{}%
  \fancyfoot[L]{\small International Semantic Intelligence Conference (ISIC), Germany, 2025}%
  \fancyfoot[R]{\thepage}%
  \renewcommand{\headrulewidth}{0pt}%
  \renewcommand{\footrulewidth}{0pt}%
}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[L]{\small International Semantic Intelligence Conference (ISIC), Germany, 2025}
\fancyfoot[R]{\thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}





\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{soul}
\usepackage{xcolor}
\usepackage{booktabs}

\usepackage{listings}
%\usepackage{xcolor}
\usepackage[dvipsnames,svgnames,x11names,table]{xcolor}

\usepackage{comment}
\usepackage[pdfstartview={XYZ null null 1.2}]{hyperref}
\usepackage[numbers]{natbib}
\lstset{
  basicstyle=\ttfamily\small,
  columns=fullflexible,
  keepspaces=true,
  upquote=true,
  showstringspaces=false,
  showspaces=false,
  keywordstyle=\bfseries\color{Blue},
  commentstyle=\itshape\color{Gray},
  stringstyle=\color{OliveGreen},
  numberstyle=\scriptsize\color{Gray},
  stepnumber=1,
  numbersep=5pt,
  backgroundcolor=\color{Gray!10},
  frame=single,
  breaklines=true,
  tabsize=2,
  captionpos=b
}

\renewcommand{\lstlistingname}{Code Block}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}


\usepackage{xurl}
\urlstyle{same} 
\usepackage{hyperref}
\begin{document}

\title{Interpretable Question Answering with Knowledge Graphs}

\author{
Kartikeya Aneja\inst{1,3}%\orcidID{0000-1111-2222-3333} 
\and
Manasvi Srivastava\inst{2,3}%\orcidID{1111-2222-3333-4444}
\and 
Subhayan Das\inst{4}%\orcidID{2222--3333-4444-5555}
\and
Nagender Aneja\inst{5}%\orcidID{2222--3333-4444-5555}
}
%
\authorrunning{K. Aneja et al.}

\institute{
Department of Electrical and Computer Engineering, University of Wisconsin-Madison, Madison, USA \email{kaneja@wisc.edu}
\and
Department of Computer Science, Banasthali Vidyapeeth, Rajasthan, India \email{manasvisrivastava26@gmail.com}
\and
Ansyst Consulting, Gurgaon, India
\and
Huawei Ireland Research Center, Dublin, Ireland \email{subhayan.das@h-partners.com}
\and
Bradley Department of Electrical and Computer Engineering, Virginia Tech, Blacksburg, VA, USA \email{naneja@vt.edu}
}
%
\maketitle              % typeset the header of the contribution
%

\thispagestyle{plain}


\begin{abstract}
This paper presents a question answering system that operates exclusively on a knowledge graph retrieval without relying on retrieval augmented generation (RAG) with large language models (LLMs). Instead, a small paraphraser model is used to paraphrase the entity relationship edges retrieved from querying the knowledge graph. The proposed pipeline is divided into two main stages. The first stage involves pre-processing a document to generate sets of question-answer (QA) pairs. The second stage converts these QAs into a knowledge graph from which graph-based retrieval is performed using embeddings and fuzzy techniques. The graph is queried, re-ranked, and paraphrased to generate a final answer. This work includes an evaluation using LLM-as-a-judge on the CRAG benchmark, which resulted in accuracies of 71.9\% and 54.4\% using LLAMA-3.2 and GPT-3.5-Turbo, respectively.

\keywords{Knowledge Graph  \and Question Answering \and RAG}
\end{abstract}

\input{text}

\bibliographystyle{IEEEtranN}
\bibliography{refs}


\end{document}
