\vspace{-1em}
\section{Results}
\vspace{-1em}
\textbf{Effectiveness of Adversarial Attacks.}

Figure \ref{fig:main_results} reports ARIA scores across attacks, models, and system configurations. Prompt-based attacks (DPI and Impersonation) are consistently the most effective, with Impersonation reaching 82\% in Swarm and DPI 81\% in Magentic-one. Impersonation succeeds largely because agents prioritize instructions from perceived authorities, even when malicious. The success of IPI attack largely depends on the configuration, ranging from average 27.4\% in Magentic-one to 56.4\% in Roundrobin. Agent-based attacks show mixed effectiveness, Byzantine agent attack achieves high attack success scores, while Colluding agents attack is less successful, with only 2–16\% success. However, in the colluding agents attack, there are several instances where only one agent successfully completes the malicious task while the other fails, resulting in a lower overall score. We explore this further in Table \ref{tab:collu_half_success}.

Prompt-level attacks yield similar ARIA scores across open- and closed-source models, indicating model-agnostic vulnerability. For IPI, closed-source models like Gemini-2.0-Flash and GPT-4o tend to be more resilient than open-source models. For example, in the Magentic One configuration, the average ARIA-4 is 15.6\% for closed-source models compared to 39.2\% for open-source models. Similarly, for RoundRobin configuration, closed-source models achieve 37.6\% versus 75.2\% for open-source models.  


\input{fig/main_results}

\textbf{Impact Across Configurations.} Table \ref{tab:ers} shows that CrewAI configurations yield higher safety scores compared to their AutoGen counterparts. Interestingly, the decentralized sequential setup in CrewAI attains an average safety score of 35.98\%, closely matching the 37.09\% observed in the orchestrator-based configurations. This improvement can be attributed to the design choice of assigning tasks to individual agents upfront, rather than dynamically during execution. In contrast, orchestrator-based setups, while effective, introduce a single point of failure that can undermine overall safety if compromised.

\textbf{Robustness under Adversarial and Benign Conditions.} A robust multi-agent LLM system must balance safety under adversarial conditions with utility in benign tasks. We capture this trade-off using the ERS metric. As shown in Table \ref{tab:ers}, GPT models consistently attain high ERS values across configuratiosn, indicating both strong safety and reliable performance. Notably, Llama-3.1-8B achieves competitive ERS in the CrewAI setup, largely due to its higher refusal rates. Overall, ERS provides a concise metric to evaluate and compare multi-agent systems, guiding the selection of models and configurations that are both safe and effective.



