\vspace{-1em}
\section{Discussion}
\vspace{-1em}
Our results reveal several insights into the vulnerabilities of multi-agent LLM systems, which we discuss below. Additional illustrative examples are provided in Appendix \ref{sec:case_study}.\\
\textbf{Attacks are consistently effective across components.} Figure \ref{fig:main_results} shows that state-of-the-art models remain vulnerable to adversarial attacks at multiple levels including the user prompt, the environment, and agent configuration. These vulnerabilities persist across models and frameworks. 



\textbf{Agents often comply with explicitly malicious tasks.} Even when inputs are explicitly malicious, such as instructions to perform harmful tasks, the refusal rates remain low, consistent with the findings of \citet{andriushchenko2025agentharmbenchmarkmeasuringharmfulness}. Instead of rejecting these requests, agents frequently proceed with execution, indicating that current safety mechanisms fail to trigger reliably in multi-agent settings.

\textbf{Agents execute tasks they recognize as harmful.} We also observe some cases where an agent acknowledges that the requested action may be malicious, but nevertheless proceeds to execute it. For example, in one experiment, an agent flagged a request to delete all quiz records as potentially malicious. Despite this recognition, it still executed the deletion. 


\textbf{Conversation trajectories are easy to manipulate.} We find that it is surprisingly easy to alter the trajectory of the conversation using lightweight injections, either through tool outputs or agent responses. Even small fragments of misleading or malicious content were enough to derail task execution. Interestingly, while orchestrator-based configurations achieve the overall high ERS, they also introduce a single point of failure. 

These findings show that multi-agent LLM systems not only inherit vulnerabilities from individual agents but also exhibit emergent risks unique to collaborative settings. Mitigating these threats requires layered defenses at the agent, orchestration, and backbone model levels to ensure safe deployment in real-world applications.


\input{table/ers}