\begin{table*}
\centering
\caption{Ablation study: effect of the width of shared dense layer-only models. Width $n\times$ represent the width of $W_h$ is $nd$, i.e.,  $W_h \in \Re^{nd\times d}$}
\label{table7}
\begin{tabular}{cccc|ccc}
\hline
 & \multicolumn{3}{c}{\textbf{FB15k-237}} & \multicolumn{3}{c}{\textbf{WN18RR}}\\
 \hline
 \textbf{Methods} &
 \textbf{MRR} &
 \textbf{HIT@10} &
 \textbf{HIT@1} &
 \textbf{MRR} &
 \textbf{HIT@10} &
 \textbf{HIT@1} \\
 \hline
 Width 1 $\times$ (baseline) & .336 & .515  & .246 & .437 & .503 & .402\\
 \hline
 Width 50 $\times$ & .348 \textbf{(+.012)} & .532 \textbf{(+.017)} & .258 \textbf{(+.012)} & .471 \textbf{(+.034)} & .537 \textbf{(+.034)}& .439 \textbf{(+.037)}\\
 Width 100 $\times$ & .349 \textbf{(+.013)} & .531 \textbf{(+.016)} & .260 \textbf{(+.014)} & .475 \textbf{(+.038)} & .543 \textbf{(+.04)}  & .441 \textbf{(+.039)}\\
 Width 200 $\times$ & .347 \textbf{(+.011)} & .529 \textbf{(+.014)} & .258 \textbf{(+.012)} & \textbf{.476} \textbf{(+.039)}& \textbf{.545} \textbf{(+.042)}& \textbf{.443} \textbf{(+.041)}\\
 Width 300 $\times$ & .347 \textbf{(+.011)} & .529 \textbf{(+.014)} & .257 \textbf{(+.011)} & .462 \textbf{(+.025)} & .525 \textbf{(+.022)} & .431 \textbf{(+.029)}\\
 \hline
  ComDensE & \textbf{.356 (+.02)}  &  \textbf{.536 (+.021)} & \textbf{.265 (+.019)} & .473 \textbf{(+.036)}  & .538 \textbf{(+.035)} & .440 \textbf{(+.038)}\\
  \hline
\end{tabular}
%}
\end{table*}

\begin{table*}
\centering
\caption{Ablation study: effect of the depth of shared dense layer-only models. Depth-$m$ denote the depth $m$ of common dense layer.}
\label{table8}
\begin{tabular}{cccc|ccc}
\hline
 & \multicolumn{3}{c}{\textbf{FB15k-237}} & \multicolumn{3}{c}{\textbf{WN18RR}}\\
 \hline
 \textbf{Methods} &
 \textbf{MRR} &
 \textbf{HIT@10} &
 \textbf{HIT@1} &
 \textbf{MRR} &
 \textbf{HIT@10} &
 \textbf{HIT@1} \\
 \hline
 Depth-1 (baseline) & .336 & \textbf{.515}  & .246 & \textbf{.437} & \textbf{.503} & \textbf{.402}\\
 \hline
 Depth-2 & \textbf{.338} \textbf{(+.002)} & \textbf{.515} & \textbf{.250} \textbf{(+.004)} & .426 \textbf{(-.011)} & \textbf{.503} & .380 \textbf{(-.022)}\\
 Depth-3 & .328 \textbf{(-.008)} & .499 \textbf{(-.016)} & .242 \textbf{(-.004)} & .446 \textbf{(+.009)} & .510 \textbf{(+.007)} & .369 \textbf{(-.033)}\\
 Depth-4 & .313 \textbf{(-.023)} & .478 \textbf{(-.037)} & .230 \textbf{(-.016)} & .382 \textbf{(-.055)} & .491 \textbf{(-.012)} & .320 \textbf{(-.082)}\\
 Depth-5 & .301 \textbf{(-.035)} & .460 \textbf{(-.055)} & .220 \textbf{(-.026)} & .339 \textbf{(-.098)} & .465 \textbf{(-.038)} & .273 \textbf{(-.129)}\\
 \hline
  ComDensE & \textbf{.356 (+.02)}  &  \textbf{.536 (+.021)} & \textbf{.265 (+.019)} & \textbf{.473 (+.036)}  & \textbf{.538 (+.035)} & \textbf{.440 (+.038)}\\
 \hline
\end{tabular}
%}
\end{table*}

\section{Ablation Study}
This section conducted ablation study associated with ComDensE. Since ComDensE combines both relation-aware and shared dense layer, we studied models in which some of the layer is removed or changed. Specifically, we considered the following configurations:
\begin{itemize}
		\item Shared dense layer only with varying widths
		\item Shared dense layer only with varying depths
		\item Different relation-aware encoding functions
	\end{itemize}
	
\subsection{Shared dense layer only: Effects of Widths}
We evaluated ComDensE only containing the shared dense layer, i.e., removing the relation-aware dense layer. We adjusted the shape of the shared dense layer in order to see if the model can outperform original ComDensE. We first explored the effects of the width of shared dense layer. Note that, increasing the width of dense layer is equivalent to increasing the number of kernels in CNN. As in Table \ref{table7}, the optimal widths are roughly $100d$ and $200d$ respectively for FB15k-237 and WN18RR models. Thus, it appeared that increasing the number of filters indefinitely does not help. In most cases, ComDensE outperformed other configurations, whereas in WN18RR, ComDensE was slightly worse, while the performance gap was quite small.

\subsection{Shared dense layer only: Effects of Depths}
Next, we also considered shared dense layer only and evaluated the effect of increasing network depth. We increased the number of layers in the shared network where the depth is in $\{2, 3, 4, 5\}$. In general, increasing the depth enhances expressive power of the model, while it did not apply to our experiments. Table \ref{table8} illustrates that link prediction performance aggravates with increasing depth. Thus, we concluded that the width of ComDensE is the only important design parameter than the depth in order to obtain a better representation of KGs.

\subsection{Different relation-aware encoding functions}
This experiment considers the effect of different relation-aware encoding functions $\Omega_r$. We tested a simple ``translation-only'' function such that
\begin{equation}
\Omega_r(x) = x + v_r
\label{eq9}
\end{equation}
where $v_r \in \Re^{d}$ is the learnable relation-specific vectors. The results and comparison with ConvE were illustrated in Table \ref{table10}. Note ``translation-only'' $\Omega_r$ does not provide any heterogeneous interaction between embedding components. However, the link prediction performance was better than ConvE on both FB15k-237 and WN18RR. This demonstrated that the inductive bias from relation-awareness enhances the link prediction performance. However, the results in Table \ref{table10} are worse than ComDensE, which shows that promoting the heterogeneous interactions~\cite{vashishth2020interacte} among the embedding components is crucial.

\begin{table}[h]
\centering
\caption{Prediction performance when $\Omega_r$ is ``translation only'' function, i.e., vector addition. (+,-) denote the performance difference from ConvE~\cite{dettmers2018convolutional}}
\label{table10}
\begin{tabular}{c|c|c}
\hline
\multicolumn{3}{c}{\textbf{vector add operation}}\\
\hline
 & \textbf{FB15k-237} & \textbf{WN18RR}\\
 \hline
 \textbf{MRR} & .344 (+.019) & .460 (+.030) \\
 \textbf{HIT@10} & .527 (+.026) & .522 (+.002) \\
 \textbf{HIT@1} & .253 (+.016) & .428 (+.028)\\
\hline
\end{tabular}
\end{table}