%% This is a skeleton file to create IEEE style Bibliography list. There is a guide added "create-manual-bib-entry.txt" to manually create popular types of references such as PhD thesis, website, unpublished work etc.
%%
%% Modified by K. Reaz( kahn.reaz@ieee.org)
%% Support sites:
%% http://www.ieee.org/

%%***********************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or implied; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk and can modify as s/he wants.

%%***********************************************************

%package list
\documentclass[a4paper,conference]{IEEEtran}
\usepackage{graphicx}

\begin{document}
\title{ComDensE : Combined Dense Embedding of Relation-aware and Common Features for Knowledge Graph Completion}


% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Minsang Kim\textsuperscript{\rm 1,\rm 2},  Seungjun Baek\textsuperscript{\rm 2}}
Email: kmswin7@gmail.com, sjbaek@korea.ac.kr\\
\textsuperscript{\rm 1}Kakao Enterprise, \textsuperscript{\rm 2}Korea University
}

\maketitle

\begin{abstract}
Real-world knowledge graphs (KG) are mostly incomplete. The problem of recovering missing relations, called KG completion, has recently become an active research area. Knowledge graph (KG) embedding, a low-dimensional representation of entities and relations, is the crucial technique for KG completion. Convolutional neural networks in models such as ConvE, SACN, InteractE, and RGCN achieve recent successes. This paper takes a different architectural view and proposes ComDensE which combines relation-aware and common features using dense neural networks. In the relation-aware feature extraction, we attempt to create relational inductive bias by applying an encoding function specific to each relation. In the common feature extraction, we apply the common encoding function to all input embeddings. These encoding functions are implemented using dense layers in ComDensE. ComDensE achieves the state-of-the-art performance in the link prediction in terms of MRR, HIT@1 on FB15k-237 and HIT@1 on WN18RR compared to the previous baseline approaches. We conduct an extensive ablation study to examine the effects of the relation-aware layer and the common layer of the ComDensE. Experimental results illustrate that the combined dense architecture as implemented in ComDensE\footnote{ https://github.com/kmswin1/ComDensE} achieves the best performance.
\end{abstract}
\IEEEpeerreviewmaketitle


\input{intro}

\input{related}

\input{method}

\input{experiment}

\input{results}

\input{ablation}

\input{conclusion}

\bibliographystyle{IEEEtran}
\bibliography{paper}

\end{document} 