\begin{abstract}
The financial domain poses unique challenges for knowledge graph (KG) construction at scale due to the complexity and regulatory nature of financial documents. Despite the critical importance of structured financial knowledge, the field lacks large-scale, open-source datasets capturing rich semantic relationships from corporate disclosures. We introduce an \textbf{open-source, large-scale financial knowledge graph dataset built from the latest annual SEC 10-K filings of all S\&P 100 companies} - a comprehensive resource designed to catalyze research in financial AI.

We propose a robust and generalizable knowledge graph (KG) construction framework that integrates intelligent document parsing, table-aware chunking, and schema-guided iterative extraction with a reflection-driven feedback loop. Our system incorporates a comprehensive evaluation pipeline, combining rule-based checks, statistical validation, and LLM-as-a-Judge assessments to holistically measure extraction quality. We support three extraction modes-single-pass, multi-pass, and reflection-agent-based allowing flexible trade-offs between efficiency, accuracy, and reliability based on user requirements. Empirical evaluations demonstrate that the reflection-agent-based mode consistently achieves the best balance, attaining a 64.8\% compliance score against all rule-based policies (CheckRules) and outperforming baseline methods (single-pass \& multi-pass) across key metrics such as precision, comprehensiveness, and relevance in LLM-guided evaluations.

The utility of our KG pipeline is demonstrated through its flexible extraction modes, coupled with a multi-faceted evaluation methodology. By releasing a high-quality, thoroughly evaluated dataset along with a comprehensive KG construction \& evaluation framework, we aim to advance transparency, reproducibility, and innovation in financial KG research. \textbf{The dataset is publicly available at:} \url{https://anonymous.4open.science/r/KG-Financial-Datasets-SP-100-529B/README.md}

\textbf{Keywords:} Knowledge Graphs, Financial Data, SEC Filings, Natural Language Processing, Information Extraction, LLMs
\end{abstract}