\section{Conclusion and Future Work}
In this work, we democratize the access to a reliable financial knowledge graph (KG) triples by releasing an open-source dataset constructed from SEC 10-K filings of all the S\&P 100 companies.
Given the universal and utilitarian nature of SEC 10-K filings, we believe that this open-source dataset will empower developers and researchers to build robust, finance-specific applications, advancing transparency and innovation in the financial domain. 

Our pipeline demonstrates that reliable KG triples can be generated using relatively compact language models (<100B parameters) without costly fine-tuning, provided a robust evaluation and normalization framework is in place—an important consideration for regulated industries where trust and auditability are paramount. This motivated our development of a holistic novel framework for evaluating our KG construction pipeline and it's results. 

We are currently pursuing the below enhancements to further broaden the impact and flexibility of our approach. 

\textbf{Schema-Free KG Construction and Self-Improvement:} Inspired by the Extract-Define-Canonicalize (EDC) paradigm~\cite{zhang2024extract}, we are developing a schema-free pipeline capable of creating schemas from scratch and iteratively refining existing ones. This is particularly valuable for private financial data sources where schema requirements are unknown. Our evaluation results demonstrate that pre-configured schemas may not capture all nuances within financial data, necessitating a schema discovery and improvement pipeline. It would be interesting to compare the results of closed vs. open schema frameworks in terms of coverage and performance degradation. Careful processing \& retrieval of expanded schemas is critical for efficient instruction following during inference.

\textbf{Temporal Knowledge Graphs for Thematic Investing:} Building on recent advances in financial temporal KGs~\cite{li2024findkg}, we plan to enrich our dataset with time-aware features to enable structured event timelines and causal reasoning. Our approach will incorporate temporal annotations capturing the evolution of financial relationships—market events, regulatory changes, and corporate developments—across various time horizons. Temporal KGs can enhance explainability for signal generation for market movements and offer actionable insights for traders and risk managers.

    \textbf{Enhanced LLM-as-a-Judge Evaluation Methodology:} Several factors warrant consideration when interpreting the results of LLM-as-a-judge approach. First, our use of Qwen3-32B without reasoning capabilities may not capture the full potential of more sophisticated reasoning models. Second, the extrinsic validation by using diverse LLM families is necessary to assess cross-model reliability and can help normalize the biases inherent in using a specific model family.
    
\textbf{Table-Aware Serialization for Improved Extraction:}\\
    We observed that smaller language models exhibit conservative extraction behavior from markdown-formatted tables missing semantic relationships despite structured data availability. A dedicated table-aware serialization module could significantly enhance knowledge graph coverage and completeness, particularly for quantitative financial metrics and their inter relationships.

We have used the underlying KG for essential downstream applications, such as question answering, proactive recommendations by integrating real-time news feeds with the structured KG. The promising results highlight the broad applicability of our KG for real-world financial use cases and can be explored at scale. 

Looking ahead, we are making a concerted effort to not only augment our pipeline with above enhancements but also expand our KG triple dataset to include all the S\&P 500 companies with data from the last 10 years of annual SEC 10-K filings, significantly broadening the scope and temporal coverage of our financial KG. We hope to catalyze further research and practical adoption of knowledge graphs in the financial sector and beyond. 
