\section{Evaluation} 
Evaluating knowledge graph construction requires overcoming limitations of traditional metrics that rely on simplistic or single-dimensional measures, especially when comprehensive ground-truth annotations are unavailable \citep{choi2025kgc}. To address this, we propose a holistic evaluation framework integrating complementary methodologies:

\subsection{CheckRules}
Knowledge graph construction systems often suffer from inconsistent entity normalization and schema violations, leading to redundant representations and semantic ambiguity. A critical issue arises from abstract entity references that lack semantic clarity: pronouns like "the company", "we", "our", or "it" create ambiguous nodes that cannot be properly linked or reasoned upon. For instance, in a financial document about Apple Inc., the same corporate entity may be represented as "Apple Inc.", "the company", "we", or the standardized ticker "AAPL", creating artificial multiplicity and semantic confusion that degrades graph quality and downstream reasoning capabilities.

To address these systematic issues, \textbf{CheckRules} evaluates each extracted triple against a set of rules:
\begin{itemize}
    \item \textbf{Subject Reference}: Identifies and flags abstract entity references (e.g., "the company", "we", "our", "it") that lack semantic specificity (e.g., "AAPL" for Apple Inc.).
    \item \textbf{Entity Length Constraint}: Limits entity names to maximum 5 words to prevent verbose representations.
    \item \textbf{Entity Schema Compliance}: Ensures extracted entities types adhere to a predefined schema.
    \item \textbf{Relationship Schema Compliance}: Ensures extracted relationship adhere to a predefined schema.
\end{itemize}

Each extracted triple is individually evaluated against these rules. For a triple \(t\) with \(R\) rules, the CheckRules score is:
\begin{equation}
    CR(t)=\frac{1}{R}\sum_{i=1}^{R}\phi_i(t)
\label{eq:check_rules}
\end{equation}
where \(\phi_i(t)\in\{0,1\}\) indicates compliance. 

\begin{table}[h]
\centering
\caption{CheckRules scores for different extraction modes }
\label{tab:checkrules_individual}
\begin{tabularx}{\columnwidth}{l|XXX}
\hline
\textbf{Rule(\textuparrow)} & \small \textbf{Single Pass (\%)} & \small \textbf{Multi Pass (\%)} & \small \textbf{Reflection (\%)} \\
\hline
Subject Reference & 99.9 & \textbf{100.0} & \textbf{100.0} \\
Entity Length Constraint & 68.2 & \textbf{79.5} & 78.0 \\
Entity Schema Compliance & 95.9 & 96.6 & \textbf{98.1} \\
Rel. Schema Compliance & 64.6 & 62.0 & \textbf{84.2} \\
\hline
\end{tabularx}
\end{table}



\begin{table}[h]
\centering
\caption{Proportion of valid triples with increasingly strict criteria}
\label{tab:checkrules_aggregate}
\begin{tabularx}{\columnwidth}{l|XXX}
\hline
\textbf{Metric (\textuparrow)} & \textbf{Single Pass (\%)} & \textbf{Multi Pass (\%)} & \textbf{Reflection (\%)} \\
\hline
At least 1 rule & 100.0 & 100.0 & 100.0 \\
At least 2 rules & 99.1 & 99.4 & \textbf{99.8} \\
At least 3 rules & 87.3 & 90.8 & \textbf{95.6} \\
At least 4 rules & 42.3 & 47.3 & \textbf{64.8} \\
\hline
\end{tabularx}
\end{table}

While \autoref{tab:checkrules_individual} identifies specific compliance bottlenecks, \autoref{tab:checkrules_aggregate} quantifies the proportion of triples considered valid under increasingly strict criteria. The results show that company references and entity-type compliance are consistently handled across all modes. However, relationship-schema compliance lags behind, indicating the need for further refinements of the predefined schema\cite{wadhwa2023revisiting}. Notably, the Reflection paradigm substantially improves compliance, particularly concerning entity naming length and relationship schema rules. \\
The second table indeed confirms this by highlighting Reflection's notable performance advantage at higher compliance thresholds. 

\subsection{Local Extraction Efficiency}

To assess extraction effectiveness and comprehensiveness, we compute Coverage Ratios, quantifying diversity and completeness across entities, entity types, and relationships. Specifically, we measure the proportion of unique entities and entity types relative to total extracted elements (Entity Coverage Ratio, ECR; Type Coverage Ratio, TCR), and evaluate schema utilization through normalized coverage ratios (TCR-N, RCR-N). Similar computations for relationships yield Relationship Coverage Ratios (RCR, RCR-N). 

\begin{table}[htbp]
\centering
\caption{Local Extraction Efficiency scores across different extraction modes}
\label{tab:coverage_assessment}
\begin{tabularx}{\columnwidth}{l|XXX}
\hline
\textbf{Metric (\textuparrow)} & \textbf{Single Pass (\%)} & \textbf{Multi Pass (\%)} & \textbf{Reflection (\%)} \\
\hline
Triples (per chunk) & 13.3 & 12.4 & \textbf{15.8} \\
ECR & 0.30 & 0.31 & \textbf{0.53} \\
TCR & 0.09 & 0.10 & \textbf{0.27} \\
TCR-N & 0.13 & 0.13 & \textbf{0.18} \\
RCR & 0.21 & 0.22 & \textbf{0.38} \\
RCR-N & 0.13 & 0.13 & \textbf{0.14} \\
\hline
\end{tabularx}

\end{table}

\autoref{tab:coverage_assessment} highlights a clear performance hierarchy, with Reflection consistently outperforming Single Pass and Multi Pass across all coverage metrics. Reflection generates more triples per chunk and achieves substantially higher entity, type, and relationship coverage, indicating a richer and more diverse extraction of semantic content. Normalized ratios (TCR-N, RCR-N), although improved by Reflection, it still suggests the underutilization of schema and highlights possible avenue for schema-design improvements and better alignment with extracted data.

\subsection{Global Semantic Diversity}

To quantify semantic diversity within the dataset, we analyze the distribution of extracted entities, types, and relationships using information-theoretic measures. Given frequency distributions $\mathbf{p} = \{p_1, p_2, \ldots, p_n\}$ where $p_i$ represents the normalized frequency of element $i$ in the extracted set, we compute Shannon Entropy \cite{shannon1948mathematical}, which provides insights into overall diversity by measuring the balance or skewness of distributions across extracted elements: 

\begin{equation}
H(X) = -\sum_{i=1}^{n} p_i \log_2 p_i
\end{equation} 

In addition, Schema-Normalized Entropy contextualizes diversity within the predefined schema:

\begin{equation}
H_{\text{norm}}(X) = \frac{H(X)}{\log_2 |S|}
\end{equation}
where $|S|$ is the total number of elements defined in the schema. 

Furthermore, Rényi Entropy \cite{renyi1961measures}, with parameter $\alpha = 2$, emphasizes concentration on frequent or rare elements:
\begin{equation}
H_2(X) = -\log_2 \left(\sum_{i=1}^{n} p_i^2\right)
\end{equation}

For each extraction method, we compute these measures on three distributions: 
(1) entity frequencies $\mathbf{p}_E$, (2) entity type frequencies $\mathbf{p}_T$, and (3) relationship frequencies $\mathbf{p}_R$, aggregated across all document chunks.

\begin{table}[htbp]
\renewcommand{\arraystretch}{1.3}
\centering
\caption{Entropy scores across different extraction modes}
\label{tab:diversity_profiling}
\begin{tabularx}{\columnwidth}{l|XXX}
\hline
\textbf{Metric} & \textbf{Single Pass} & \textbf{Multi Pass} & \textbf{Reflection} \\
\hline
\multicolumn{4}{l}{\textit{Shannon Entropy}} \\
\hline
Entity & 7.5383 & 7.2845 & 7.1779 \\
Entity Type & 3.0290 & 2.9835 & 2.8665 \\
Relationship & 5.5438 & 5.6116 & 4.3164 \\
\hline
\multicolumn{4}{l}{\textit{Normalized Schema Entropy}} \\
\hline
Entity Type & 0.6607 & 0.6507 & 0.6252 \\
Relationship & 1.1412 & 1.1552 & 0.8885 \\
\hline
\multicolumn{4}{l}{\textit{Rényi Entropy ($\alpha = 2$)}} \\
\hline
Entity & 2.8619 & 2.5883 &  2.4574 \\
Entity Type & 2.1312 & 2.0851 & 1.9877 \\
Relationship & 3.6355 & 3.5691 & 2.6814\\
\hline
\multicolumn{4}{l}{\textit{Normalized Schema Rényi Entropy ($\alpha = 2$)}} \\
\hline
Entity Type & 0.4648 & 0.4548 & 0.4335 \\
Relationship & 0.7484 & 0.7347 & 0.5520 \\
\hline
\end{tabularx}
\end{table}

\autoref{tab:diversity_profiling} reveals a clear trade-off between extraction completeness and variety. The Reflection method achieves the highest coverage but exhibits the lowest entropy across all dimensions. This result demonstrates that Reflection intentionally reduces diversity to yield a more compact, connected, and navigable graph consistent with predefined extraction rules. Given the significant improvement of Reflection on complementary metrics, this reduction in entropy is well within the acceptable range. Future work will monitor entropy drift and adapt the Reflection rules when diversity falls below the predefined threshold. All extraction methods exhibit moderate schema-normalized entropy, suggesting that the current ontology effectively captures core semantic categories in the corpus, while retaining room for schema enhancement to accommodate greater semantic detail.
\subsection{Comparative Evaluation: LLM-as-a-Judge}
The absence of benchmark ground truth triples for knowledge graph evaluation necessitates an alternative evaluation approach. We leverage LLMs as comparative judges to assess:
\begin{itemize}
\item \textbf{Precision}: Assesses the clarity, specificity, and uniqueness of the extracted triples.
\item \textbf{Faithfulness}: Measures the factual accuracy and grounding of the triples within the source text.
\item \textbf{Comprehensiveness}: Evaluates how completely the generated triples capture the core informational content of the source text. 
\item \textbf{Relevance}: Determines the contextual alignment of triples with the main topics and themes of the source text.
\end{itemize}

This methodology enables ground truth-agnostic metrics that provide relative comparative evaluations rather than absolute measurements, circumventing the need for predefined reference datasets.
According to recent findings \cite{chen2024not, sui2025stop}, Chain-of-Thought (CoT) reasoning \cite{wei2022chainofthought} can underperform in linear, fast, and intuitive tasks, potentially introducing unnecessary complexity and overthinking. Consequently, we adopt a prompting strategy similar to that used by Lopez et al. \cite{lopez2023can}, employing direct instructions without intermediate reasoning steps. In this approach, the model initially commits to a judgment and subsequently provides an explanation. This aligns with cognitive insights indicating that post-hoc rationalization can offer improved human interpretability compared to reasoning that precedes commitment \cite{vamvourellis2025reasoning}.
In our evaluation, we utilized the Qwen3-32B model without reasoning prompts and set the temperature parameter to 0.1.\\

\begin{table}[H]
\centering
\caption{LLM as a Judge Score for various extraction modes}
\begin{tabularx}{\columnwidth}{l|XXX}
\hline
\textbf{Metric (\textuparrow)} & \textbf{Single Pass (\%)} & \textbf{Multi Pass (\%)} & \textbf{Reflection (\%)} \\
\hline
Precision & 22.3 & 38.6 & \textbf{39.1} \\
Faithfulness & \textbf{40.1} & 24.4 & 35.5 \\
Comprehensiveness & 36.3 & 15.6 & \textbf{48.1} \\
Relevance & 34.6 & 28.1 & \textbf{37.3} \\
\hline
\end{tabularx}
\label{tab:llm_judge_results}
\end{table}

To ensure the reliability of our comparative evaluations, we implement a robustness assessment protocol. For each three-way comparison on chunk $c_{ij}$ and metric $\mu$, we conduct $n_{\text{votes}} = 3$ independent evaluations:

\begin{equation}
    \mathcal{V}\mu(c{ij}) = \{J_\mu^{(k)}(c_{ij}, \mathcal{T}{ij}^{(m_1)}, \mathcal{T}{ij}^{(m_2)}, \mathcal{T}{ij}^{(m_3)})\}{k=1}^{3}
\end{equation}

where $k$ represents the $k$-th independent vote. In cases where the votes do not reach consensus, we request a fourth decisive vote.

\begin{table}[h]
\centering
\caption{Consistency across the three LLM as a Judge runs}
\begin{tabularx}{\columnwidth}{l|X}
\hline
\textbf{Metric (\textuparrow)} & \textbf{Agreement (\%)} \\
\hline
Precision         & 82.1 \\
Faithfulness      & 81.3 \\
Comprehensiveness & 86.7 \\
Relevance         & 83.7 \\
\hline
\end{tabularx}
\label{tab:judge_agreement}
\end{table}
\autoref{tab:llm_judge_results} reveals nuanced performance patterns across extraction modes. The reflection mode outperforms other modes in precision, comprehensiveness, and relevance, whereas the single-pass mode excels in faithfulness. This dichotomy underscores a fundamental trade-off between comprehensiveness of extraction and factual grounding.
The reflection mode's relatively lower faithfulness score, despite greater comprehensiveness, suggests increased triple generation potentially exceeds source-constrained accuracy boundaries. 
% This observation aligns with recent findings that Chain-of-Thought reasoning can introduce unnecessary complexity in linear tasks \cite{chen2024not, sui2025stop}, potentially leading to over-extraction beyond source material boundaries. 
Moreover, \autoref{tab:judge_agreement} suggests an inverse correlation, where lower agreement is indicative of higher contextual uncertainty.

% While the internal agreement metrics (>80\% across all dimensions) demonstrate measurement consistency, establishing reliable comparative evaluations requires further refinement through judge model calibration and extrinsic validation via multiple LLM families.






