\section{Related Work}
In this section, we provide details on existing research that has been happening in the realm of Knowledge Graph Construction with a focus on the financial domain. 

\textbf{Knowledge Graph Construction:} 
Knowledge graph construction (KGC) has traditionally followed a pipeline architecture composed of discrete subtasks such as entity recognition \cite{zukov2018neural, martins2019joint} and relation classification \cite{zeng2014relation, zeng2015distant}, often relying on supervised learning with domain-specific annotations. However, the recent success of LLMs in information extraction tasks \cite{li2023evaluating} highlights a paradigm shift toward prompt-based strategies for robust knowledge graph construction.

Recent work has leveraged large language models (LLMs) for zero and few-shot extraction using iterative prompting strategies. \citet{carta2023iterative} propose a zero-shot pipeline using GPT-3.5, where a sequence of prompts progressively identifies entities, types them, extracts relations, and resolves co-references without supervision or external knowledge bases. \citet{jiang2025ras} introduce the Retrieval-And-Structuring (RAS) framework, which alternates between query planning, retrieval, and triple extraction to incrementally construct task-specific mini-KGs, outperforming standard RAG methods. These approaches complement interactive designs like ChatIE \cite{wei2023chatie}, which frames triple extraction as a multi-turn QA task. Collectively, they underscore the emergence of modular, prompt-driven workflows for scalable KG construction with LLMs.

\textbf{Normalization and Schema Canonicalization} : 
While open information extraction (OIE) methods enable large-scale triples extraction, they often produce unstandardized and semantically redundant outputs. Without canonicalization, multiple surface-level variations of the same relation (e.g., \textit{supplies}, \textit{is supplier of}) can coexist in the knowledge graph, introducing ambiguity and reducing its utility for downstream tasks.
Traditional approaches depend on whether a target schema is available: alignment-based methods use lexical resources like WordNet, while schema-free methods such as CESI \cite{vashishth2018cesi} cluster relations using embeddings and external signals. However, clustering often over-generalizes, merging distinct semantics. The recent Extract-Define-Canonicalize (EDC) framework \cite{zhang2024extract} offers a more robust, LLM-native alternative. It extracts triples, defines schema candidates in context, and canonicalizes them using LLM-generated definitions and reasoning-avoiding brittle heuristics or external ontologies.

\textbf{Financial Knowledge Graphs:}
Early work on financial knowledge graphs (KGs) focused on extracting structured event representations from unstructured news. \citet{benetka2017financial} jointly extract all attributes of economic transactions as quintuples, aggregating information across multiple mentions to build unified event-centric graphs. Subsequent efforts, such as \citet{elhammadi2020pipeline}, combined semantic role labeling, dependency parsing, and domain-specific dictionaries to construct high-precision financial KGs from news. More recently, \citet{li2024findkg} introduced FinDKG, a dynamic, time-varying financial KG generated from news using a fine-tuned LLM pipeline, systematically extracting entities and relations as event quadruples. Collectively, these works highlight the evolution from rule-based and supervised pipelines to LLM-driven, schema-flexible approaches for building robust financial knowledge graphs.

Building upon these foundations, we present an open-source, large-scale financial knowledge graph constructed exclusively from SEC 10-K filings of all S\&P 100 companies. Our work addresses key limitations in existing approaches: while previous financial KGs focused on news-based event extraction, we target the most authoritative financial documents (SEC filings) with comprehensive schema-guided extraction, establishing new benchmarks for financial KG construction and evaluation.

