\section{Detailed Experimental Settings}\label{sec:exp_settings_appendix}

\stitle{Hardware configurations.} We conduct all the experiments on an AWS EC2 g5.16xlarge instance with 1 NVIDIA A10 GPU (24GB memory), 64-core vCPUs, 256G memory and 2TB NVMe SSD storage. For LLM service, we use AWS bedrock API with Claude-3.5-sonnet~\cite{claude} and Deepseek-R1~\cite{deepseekr1} models.

\stitle{Baselines and models.} We compare \name{} against existing GraphRAG methods discussed in \autoref{sec:intro}. To ensure a fair and clear comparison, we categorize baselines based on their adopted graph traversal methods and select one representative from each category, despite minor differences in other modules. For instance, since both MS\_GraphRAG and LightRAG use BFS to retrieve all one-hop neighbors, we select MS\_GraphRAG as the representative method. Similarly, for traversal methods that invoke LLMs at each step, we compare with Graph-CoT instead of ToG. Additionally, since RoG requires fine-tuning an LLM to generate faithful reasoning paths, we instead prompt the LLM with the graph schema to avoid instruction tuning. For recent methods that require training of the retriever, such as G-retriever~\cite{gretriever} and SubgraphRAG~\cite{gnnrag}, we do not include them in this experiment since they can not be applied in general GraphRAG workloads where questions do not have ground-truth labels. We also include the baseline, named Cypher, which directly generates cypher queries using the LLM without the guidance of our proposed question pattern taxonomy and any further optimizations built upon it to show the necessity of our adaptive prompting. For \name{}, we set the $k$ in top-$k$ shortest paths to 10, which means that we only take the top-10 reasoning paths satisfying the optional constraints in the question. For consistency, we use the Claude-3.5-sonnet~\cite{claude} as the underlying LLM service for \name{} and all baselines, both for categorization and generation.

\stitle{Evaluation metric.} Since most of the graph question patterns do not have a single definitive answer as discussed in~\autoref{sec:question_categorization}, we assess the generation quality using win rates determined by LLM judgments. We evaluate responses from four perspectives: \textit{Comprehensiveness}, \textit{Diversity}, \textit{Empowerment}, and \textit{Directness}, and then let the LLM determines the \textit{Overall Winner} considering all criteria, following previous approaches~\cite{ms_graphrag, lightrag}. Full prompts for these criteria are provided in \autoref{sec:criteria_appendix}. As each question is judged across multiple baselines and thus there could be multiple high-qualty responses, we prompt the LLM to allow multiple winners for each criterion, leading to total win rates exceeding 100\%. In addition to win rates, we report \textit{F1-score} and \textit{Deepseek-R1} for $\langle s, p, * \rangle$ and $\langle s, p, * \rangle+ \langle s, p, * \rangle$ questions, which we have automatically labeled ground-truth answers. We use the strong open-weight reasoning model Deepseek-R1~\cite{deepseekr1} for judgment. Meanwhile, we measure end-to-end response latency and token usage to evaluate the computational efficiency.