\section{Related Work}
\label{sec:related work}



% \clearpage
In this section, we summarize the related work and discuss their connections to our model.
Firstly, we introduce the two lines of work on the KG completion task: multi-hop reasoning and KG embedding.


The \textbf{multi-hop reasoning} task focuses on learning logical multi-hop paths reasoned from KG.
% Multi-hop reasoning task can be formulated as a search process, in which the search agent traverses a logical multi-hop path to find the missing tail entity in KG, based on the known head entity and relation.
The multi-hop reasoning models distill deep information from paths thereby generating further directly interpretable results.
\cite{lao2011random,das2016chains,jiang2017attentive,yin2018recurrent}
% ,~\cite{}
% ,~\cite{}, and~\cite{} 
predicted the missing relations of incomplete triples based on pre-computed paths. 
\cite{Xiong2018DeepPath} firstly adopted the RL framework to improve the reasoning performance. 
% finds paths between the head and tail entities based on RL framework and predicts the missing relations.
% Our work is devised to find the missing entities, which are orthogonal to the aforementioned models predicting missing relation in a complementary manner.
% As for finding a missing entity, 
The task of finding a missing entity is orthogonal to the prediction of the missing relation in a complementary manner.
\cite{das2017go} used the history path to facilitate the search agent finding the missing entity
% effectively 
and \cite{LinEMNLP2018} optimized the reward function of RL framework based on \cite{das2017go}.
% MINERVA~\cite{das2017go} uses the history path to facilitate the search agent to find the missing entity effectively.
% MultiHop~\cite{LinEMNLP2018} optimizes the reward function of RL framework based on MINERVA.
\cite{lv-etal-2019-adapting} adopted the meta learning framework for multi-hop reasoning over few-shot relations.
% However, these works neglect the long distance reasoning scenarios, their performance declines significantly as the distance increases.
These works are conditioned in short distance scenarios, and tend to rapidly lose effectiveness as the distance increases. In contrast, we propose a general model which can be sufficiently utilized in both the short and long distance reasoning scenarios.



The \textbf{KG embedding} task is another line of work carried to alleviate the incompleteness of KG.
Embedding-based models project KGs in the embedding space and estimate the likelihood of each triple using scoring functions.
% , through learning a scoring function to indicate the predicted probability.
% learn global latent representations for entities and relations in continuous
% vector space and estimate the likelihood of each triple (e s ,r,e d ) by using a scoring function ψ(e s ,r,e d ).
% TransE~\cite{bordes2013translating}, based on translation assumption, considers that two entities can be connected by relation with low error. TransH~\cite{wang2014knowledge}, TransR~\cite{lin2015learning}, and TransD~\cite{ji2016knowledge} are the variants of TransE. 
\cite{bordes2013translating,wang2014knowledge,lin2015learning,ji2016knowledge} defined additive scoring functions based on the translation assumption.
% namely, two entities can be connected by the relation with the lowest error.
\cite{yang2014embedding,trouillon2017complex} defined multiplicative scoring functions based on linear map assumption.
Moreover, recent models introduce special neural networks like neural tensor network~\cite{NIPS2013_tensor}, convolution neural network~\cite{Dettmers2018Convolutional} and graph convolutional network~\cite{nathani-etal-2019-learning}.
% For example, neural tensor networks in~\cite{NIPS2013_tensor}, convolution neural network in~\cite{Dettmers2018Convolutional} and graph convolutional network in~\cite{nathani-etal-2019-learning}.
Due to the neglection of deep information within multi-hop paths, the results of the embedding-based models lack interpretability, which is critical for KG-related applications. 
However, embedding-based models are less sensitive to the reasoning distance because they learn KG structure from the global perspective.
Thus, we take advantage of this strength to learn the global knowledge from graph structure and retain the interpretability by reasoning from the history paths. 
% However, it is critical to understand how models behave when exposed to real-world data, especially for KG-related applications.


%\vspace{-1mm}

Secondly, we discuss the community research on long distance reasoning scenarios.
% Nevertheless, t
% There are studies that focus on long distance reasoning scenarios in other natural language processing applications.
% For example, in conversational reasoning task,
\cite{tuan-etal-2019-dykgchat} formed a transition matrix for reasoning over six-hop path in KG for the conversational reasoning task.
It is however not suitable for large-scale KGs, because the matrix multiplication requires large calculation space.
\cite{wang2019explainable} proposed a long-term sequential pattern to encode long distance paths
% and estimate the recommendation confidence 
for the recommendation task.
Because there is no real reasoning process for the long distance paths, it is not suitable for the KG completion.
To summary, we are the first to study long distance reasoning scenarios in the KG completion.
We propose a general model that tackles both short and long distance reasoning scenarios and works effectively on large-scale KGs.



%\clearpage

