
\documentclass{article} % For LaTeX2e
\usepackage{iclr2025_conference,times}

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

\usepackage{hyperref}
\usepackage{url}
\usepackage{xspace}
\usepackage{adjustbox}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{tcolorbox}
\tcbuselibrary{listingsutf8}
\usepackage{float}
\usepackage{wrapfig} 
\usepackage{floatflt} 
\usepackage{graphicx}
\usepackage{mdframed}
\usepackage{lipsum} % 
\usepackage{tablefootnote}
\usepackage{subcaption}

\newcommand{\ML}[1]{{\color{teal}M.L.:[#1]}}
\newcommand{\pan}[1]{{\color{blue}Pan:[#1]}}
\newcommand{\siqi}[1]{{\color{red}Siqi:[#1]}}


\newcommand{\proj}{SubgraphRAG\xspace}

\title{Simple is Effective: The Roles of Graphs and Large Language Models in Knowledge-Graph-Based Retrieval-Augmented Generation}

\author{Mufei Li$^{*}$, Siqi Miao$^{*}$, Pan Li \\\
Georgia Institute of Technology \\
\texttt{\{mufei.li, siqi.miao, panli\}@gatech.edu} \\
\footnotesize{$^{*}$Equal contribution.}}

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
\begin{document}

\maketitle

\begin{abstract}

Large Language Models (LLMs) demonstrate strong reasoning abilities but face limitations such as hallucinations and outdated knowledge. Knowledge Graph (KG)-based Retrieval-Augmented Generation (RAG) addresses these issues by grounding LLM outputs in structured external knowledge from KGs. However, current KG-based RAG frameworks still struggle to optimize the trade-off between retrieval effectiveness and efficiency in identifying a suitable amount of relevant graph information for the LLM to digest. We introduce \proj, extending the KG-based RAG framework that retrieves subgraphs and leverages LLMs for reasoning and answer prediction. Our approach innovatively integrates a lightweight multilayer perceptron (MLP) with a parallel triple-scoring mechanism for efficient and flexible subgraph retrieval while encoding directional structural distances to enhance retrieval effectiveness. The size of retrieved subgraphs can be flexibly adjusted to match the query's needs and the downstream LLM's capabilities. This design strikes a balance between model complexity and reasoning power, enabling scalable and generalizable retrieval processes. Notably, based on our retrieved subgraphs, smaller LLMs like Llama3.1-8B-Instruct deliver competitive results with explainable reasoning, while larger models like GPT-4o achieve state-of-the-art accuracy compared with previous baselines—all without fine-tuning. Extensive evaluations on the WebQSP and CWQ benchmarks highlight \proj's strengths in efficiency, accuracy, and reliability by reducing hallucinations and improving response grounding. Our implementation is available at \href{https://github.com/Graph-COM/SubgraphRAG}{https://github.com/Graph-COM/SubgraphRAG}.
\end{abstract}


\input{intro}
\input{preliminaries}
\input{approach}
\input{experiment}
\input{conclude}

\bibliography{iclr2025_conference,GraphRAG_ref}
\bibliographystyle{iclr2025_conference}


\input{appendix}

\end{document}
