\section{Related Work}

Combination of large language models (LLMs) and knowledge graphs (KGs) has recently received considerable attention, aiming to address their respective limitations: LLM`s sensitivity to hallucinations and incomplete reasoning versus KG`s fragmentary coverage and static ontology. In this section, we will briefly review several representative methods to enhance reasoning over KGs, illustrating distinct pathways toward modeling external memory for personalized LLM agents and implementing information search.

PersonalAI 1.0 (PAI-1)~\cite{11479299} represents a systematic exploration of KG storage and retrieval approaches for personalized LLMs. By presenting a flexible graph-based memory framework, it bridges the gap between dense vector similarity retrieval and structured memory representations. This study underscores the necessity of dynamic retrieval interfaces, emphasizing multiple traversal mechanisms such as BeamSearch and WaterCircles. However, its focus on memory representation leaves room for improvement concerning scalability and applicability to open-domain tasks. Think-on-Graph (ToG)~\cite{DBLP:conf/iclr/SunXTW0GNSG24} introduces a tight coupling (LLM $\bigotimes$ KG) paradigm, enabling direct participation of LLMs in graph reasoning processes. ToG exploits the advantages of multi-hop reasoning paths and improves the responsiveness and interpretability of reasoning outcomes. Nonetheless, its dependence on KG's integrity and relevance limits its adaptability to evolving domains and dynamic user requirements.  Reasoning on Graphs (RoG)~\cite{luo2024rog} addresses the hallucination problem by employing a planning-retrieval-reasoning framework. It grounds LLM-generated reasoning steps onto verified KG-derived paths, ensuring faithfulness and interpretability. Though successful in certain KGQA settings, its reliance on manual annotations restricts broader applicability. 

Debat on Graph (DoG)~\cite{ma2025debate} proposes an iterative interactive reasoning framework that combines simplified question transformations and debating among multi-role LLMs. This method excels in addressing overly complex and noisy paths, though its computational overhead might impede scalability. Pyramid-Driven Alignment (PDA)~\cite{Li2024AnEP} applies the Pyramid Principle to organize reasoning hierarchies derived from LLMs and KGs. By generating deductive knowledge and recursively unlocking KG reasoning capabilities, PDA achieves high accuracy on multi-hop reasoning tasks. However, its dependency on precise hierarchical organization complicates generalization to diverse contexts. Finally, Pseudo-Graph Generation \& Atomic Knowledge Verification (PG\&AKV)~\cite{PGAKV2025} emphasizes generalizability across KGs and open-ended question answering. It constructs pseudo-triples to fill knowledge gaps, followed by verification against actual KG triples. While this resolves certain issues around hallucination, its reliance on additional LLM computation adds latency.

In contrast, PAI-2 contributes a holistic enhancement by integrating dynamic planning mechanism into graph-traversal procedure. By focusing on iterative subgraph traversals and query refinement, PAI-2 improves factual correctness and reduces hallucinations. Its distinctive features include a carefully balanced fusion of structured and unstructured data retrieval, informed by LLM-driven reasoning. This approach promises broader applicability across diverse benchmarks and contexts, positioning itself as a significant leap forward in personalized LLM agents equipped with knowledge graphs.


% TODO