
The goal of dialog generation is to generate an informative and appropriate response given an input dialog.
Pretrained Language Models~(PLMs) have demonstrated promising performance on the dialog generation~\cite{roberts2019exploring,touvron2023llama,achiam2023gpt}.
However, they often generate irrelevant, factually incorrect, or hallucinatory responses since the generation process heavily depends on the internal parameters of the language models~\cite{lewis2020retrieval,shuster2021retrieval}.
To mitigate these issues, several studies~\cite{wang2020improving,zhao2020low} have explored knowledge-grounded dialog generation models, which incorporate external knowledge to generate more factually accurate responses.
Some approaches utilize unstructured texts such as Wikipedia articles~\cite{dinan2019wizard} and internet web pages~\cite{ghazvininejad2018knowledge} while others~\cite{moon2019opendialkg,galetzka2021space,tuan2022towards,kang2022knowledge} leverage structured knowledge graphs~(KGs) to capture both the relational and semantic information for grounding dialog responses.

{
Many existing knowledge graph{\textendash}grounded dialog generation models~\cite{tuan2022towards,kang2022knowledge} employ encoder-based retrieval methods.
They encode the dialog history into a single vector and then use it on another encoder~(\eg,~bi-encoder) to retrieve relevant triplets from the KG.
However, this approach can lead to an information bottleneck due to the limited capacity of a single vector to represent long and complex multi-turn dialogs~\cite{humeau2020poly,de2021autoregressive,lee2022generative}.
Moreover, these methods~\cite{galetzka2021space,tuan2022towards,kang2022knowledge} often rely on separate models, such as graph neural networks (GNNs), to encode the knowledge graphs, which limits the integration of natural language comprehension capabilities of PLMs.
}

Recent studies~\cite{lee2022generative,sun2023generative} have addressed the information bottleneck issue by applying generative retrieval methods, which cast retrieval as an autoregressive generation process to facilitate direct interactions between query context and knowledge paragraphs.
Despite this progress, most generative retrieval works focus solely on natural language-based knowledge, employing conventional token representations and decoding strategies, which do not fully capture the structure and properties of knowledge graphs.

{To address the aforementioned issues, we propose \textbf{Dialog} Generation model with \textbf{G}enerative \textbf{S}ubgraph \textbf{R}etrieval~(\textbf{DialogGSR}), which integrates generative subgraph retrieval with response generation. 
Our proposed method adopts two key graph-specialized techniques: (1) a structure-aware knowledge graph linearization for effective graph representation and (2) graph-constrained decoding for valid subgraph retrieval.}
\textcolor{black}{Our knowledge graph linearization approach introduces a small set of special token embeddings to account for both the structural positioning of knowledge entities and the reverse relationships between them. By self-supervising these special tokens using a knowledge graph reconstruction loss, the method effectively represents the knowledge graph.}
The graph-constrained decoding facilitates autoregressively retrieving the knowledge considering the graph structural information, thus generating valid and relevant knowledge subgraphs.
Since DialogGSR utilizes pretrained language models for both subgraph retrieval and dialog generation, it leverages the pretrained language models' internal knowledge in both tasks.

We evaluate DialogGSR on two KG{\textendash}grounded dialog generation datasets: OpenDialKG~\cite{moon2019opendialkg} and KOMODIS~\cite{galetzka2020corpus}.
Our proposed method shows the best performance on both benchmark datasets.

Our contributions are three-fold as follows:
\begin{itemize}
    \item We propose Dialog generation with Generative Subgraph Retrieval~(DialogGSR), which retrieves the relevant knowledge subgraphs by generating their token sequences. 
    \item We design knowledge graph linearization for effective graph representations and graph-constrained decoding for retrieving valid and relevant subgraphs.
    \item We show the state-of-the-art response generation performance on two benchmark datasets, OpenDialKG and KOMODIS.
\end{itemize}