\section{\benchmarkname: A Benchmark for GraphRAG with Diverse Questions}\label{sec:benchmark}

In this section, we first introduce the knowledge graphs used in \benchmarkname, then discuss how we generate concrete graph questions and paraphrase them into flexible expressions.

% \stitle{Benchmark Overview.}

\stitle{Data collection.} We utilize knowledge graphs from the public graph reasoning benchmark GRBench~\cite{graphcot}, which contains 10 knowledge graphs spanning 5 general domains: academia, e-commerce, literature, healthcare, and legal, collected from various public sources. In \benchmarkname{}, we select 3 out of the 10 graphs—specifically from the academia~\cite{academia}, literature~\cite{literature}, and e-commerce~\cite{e-commerce} domains. Detailed statistics of the selected knowledge graphs are provided in \autoref{sec:dataset_appendix}.

\stitle{Question generation.} Following principles used in prior benchmarks~\cite{cwq, graphcot, grailqa, cypherbench}, we generate initial fixed-form questions by randomly selecting entities that meet specific constraints and populating predefined question templates. Specifically, we design 73 well-crafted question templates across all three knowledge graphs, covering both basic and nested question patterns with varying levels of complexity. Each template is paired with a manually written Cypher query to retrieve entities that ensure the resulting questions are valid and answerable. In particular, inspired by the diverse complexity of $\langle s, p, * \rangle$ questions seen in recent KGQA benchmarks~\cite{cwq, graphq, grailqa, graphcot}, our templates include questions requiring multi-hop reasoning, with relation paths ranging from 1 to 5 hops. For higher-order relations, we carefully validate the semantics to avoid generating unrealistic or nonsensical questions. As a result, we generate 400 initial questions per knowledge graph, covering a broad range of patterns and complexities—yielding a total of 1,200 questions across the entire benchmark. The question templates are described in detail in \autoref{sec:question_template_appendix}.

% Existing GraphQA benchmarks~\cite{webqsp, cwq, hotpotqa} primarily focus on the $\langle s, p, * \rangle$ question type, as only these questions have ground-truth answers available for evaluation. To comprehensively assess the performance of existing methods across a diverse range of graph questions, we introduce a new GraphRAG benchmark that encompasses all four question types discussed above, utilizing manually designed question templates. Specifically, we generate 80 questions for each question type by randomly selecting entities and populating the corresponding templates, resulting in a total of 320 questions per knowledge graph.

\stitle{Partial answer annotation.} Most questions in \benchmarkname{} do not have gold-standard ground truth answers, and LLM-based judgment is the common practice for evaluation~\cite{ms_graphrag, fast_graphrag}. Nevertheless, we identify that ground truth can be provided for specific question types—namely, $\langle s, p, * \rangle$ and $\langle s, p, * \rangle + \langle s, p, * \rangle$ questions. For these templates, we manually author additional Cypher queries that, when populated with the selected entities during question generation, retrieve the corresponding answers. These ground truth answers enable quantitative evaluation using standard metrics such as \textit{F1-score} and \textit{Hit}, thereby strengthening the rigor of our benchmark assessment.

\stitle{Question paraphrasing.} As noted in existing KGQA benchmarks~\cite{cwq, graphq, grailqa, graphcot, cypherbench}, template-based question generation often results in fixed and repetitive phrasing, which limits linguistic diversity. To address this, we follow the strategy adopted by recent benchmarks~\cite{graphcot, cypherbench} and use an LLM (Claude-3.5-Sonnet~\cite{claude}) to paraphrase each initial question into four distinct variants. We then randomly select one of these paraphrased versions as the final question presented in \benchmarkname{}.

% Previous benchmarks~\cite{cwq,graphq,grailqa} involve extensive human-labor efforts to rephrase the generated question into flexible expressions (e.g., manual paraphrasing by employed annotators or crowd-sourcing platforms like Amazon Mechanical Turk~\cite{mturk}). 