\section{List of Hyperparameters}\label{appsec:hyperparams}


\begin{table*}[!h]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\textbf{Algorithm} & \textbf{Parameter} & \textbf{CartSafe} & \textbf{Stag-Hunt} & \textbf{Centipede} & \textbf{EPGG} & \textbf{Markov Stag-Hunt} \\
\hline\hline
\multirow{9}{*}{\textbf{DQN}} & Epochs & 1 & x & 1 & x & x \\
\cline{2-7}
& $\gamma$ & 0.9 & x & 0.99 & x & x \\
\cline{2-7}
& Buffer size & 10000  & x & 512 & x & x \\
\cline{2-7}
& Batch size & 128 & x & 128& x & x \\
\cline{2-7}
& lr & 0.001 & x & 0.001 & x & x \\
\cline{2-7}
& $\epsilon$-decay & 0.99996 & x & 0.9972 & x & x \\
\cline{2-7}
& $\epsilon_{min}$ & 0.01 & x & 0.01 & x & x \\
\cline{2-7}
& $\alpha$ & $\{1.0,5.0\}$ & x & 1.0 & x & x \\
\cline{2-7}
& $\tau$ & 1.0 & x & 1.0 & x & x \\
\hline\hline
\multirow{9}{*}{\textbf{PPO}} & Epochs & 10  & 10 &  10 & 10 & 10 \\
\cline{2-7}
& $\gamma$ & 0.9 & 0.99 & 0.99 & 0.99 & 0.99 \\
\cline{2-7}
& Buffer size & 400 & 50 & 100 & 50 & 100 \\ % update timestep
\cline{2-7}
& $\epsilon$-clip & 0.1 & 0.1 & 0.15 & 0.1 & 0.1 \\
\cline{2-7}
& lr (actor) & 0.001 & 0.001 & 0.001 & 0.001 & 0.001 \\
\cline{2-7}
& lr (critic) & 0.001 & 0.001 & 0.001 & 0.001 & 0.001 \\
\cline{2-7}
& VF coef 0.5 & 0.5 & 0.5 & 0.5 & 0.5 & 0.5 \\
\cline{2-7}
& S coef 0.01 & 0.01  & 0.01 & 0.01 & 0.01 & 0.01 \\
\cline{2-7}
& $\alpha$ & $\{0.5,1.0,2.0\}$  & 1.0 & 1.0 & 1.0 & 1.0 \\
\hline
\end{tabular}
\caption{Hyperparameters for experiments. }
\label{table:hyperparams}
\end{table*}


Table~\ref{table:hyperparams} describes the hyperparameters used in the underlying RL algorithms for all independent MARL experiments. The hyperparameters are:
\begin{itemize}
    \item \textbf{Epochs:} The number of epochs that the neural networks are trained per training call.
    \item {$\mathbf{\gamma}$:} The discount factor.
    \item \textbf{Buffer size:} The number of latest steps (states and actions taken) contained in the history buffer.
    \item \textbf{Batch size:} (DQN) The batch size sampled from the buffer per training epoch.
    \item \textbf{lr/lr (actor)/lr (critic):} Learning rate for Q network (DQN), actor/critic networks (PPO). All networks were optimised via Adam \citep{kingma2014adam}, with all other hyperparameters left as in PyTorch's default implementation \citep{paszke2019pytorch}.
    \item \textbf{$\epsilon$-decay:} (DQN) $\epsilon$-decay factor $\delta$ for $\epsilon$-greedy exploration according to the following formula, where $t$ is the number of exploration steps taken so far:
    \begin{equation}
        \epsilon\leftarrow\delta^t
    \end{equation}
    \item \textbf{$\epsilon_{min}$:} (DQN) Minimum value of $\epsilon$ for $\epsilon$-greedy exploration.
    \item \textbf{$\tau$:} (DQN) Exploration factor for softmax exploration.
    \item \textbf{VF coef:} (PPO) Value-function loss coefficient.
    \item \textbf{S coef:} (PPO) Entropy loss coefficient.
    \item \textbf{$\epsilon$-clip}: (PPO) Clipped policy update ratio range. 
    \item \textbf{$\alpha$:} Safety penalty coefficient (cf.\ Definition~3.3 and \citet{yang2023safe}'s Definition 5.1).
\end{itemize}
Additionally, all DQN agents used neural networks with 2 hidden layers of 64 neurons each with a ReLU activation in between each layer, and all PPO agents used the same for actor and critic networks, except using the hyperbolic tangent instead of ReLU between layers.
