\input{Figure_tex/temp.tex}

\subsection{Generative Retrieval}

Retrieving relevant information from a large corpus such as a text corpus or a knowledge base is crucial in many tasks~\cite{ChenFWB17,ThorneVCM18,lewis2020retrieval,IzacardG21}.
Recent studies~\cite{de2021autoregressive,bevilacqua2022autoregressive,wang2022neural,lee2022generative,lee2023contextualized} have demonstrated that generative retrieval models can be more effective than conventional encoder-based retrieval models. %\cite{KarpukhinOMLWEC20, WuPJRZ20, ZhaoXBD21}. 
They cast retrieval tasks as generation tasks, where relevant sequences are generated rather than retrieved given input queries.
Several studies~\cite{chen2022gere,thorne2022data,lee2022generative,yu2023generate,xu-etal-2023-unsupervised,luo2024reasoning} have shown the effectiveness of generative retrieval in various knowledge-intensive natural language processing tasks.
Motivated by these works, we propose a generative subgraph retrieval model with knowledge graph linearization and graph-constrained decoding for effective graph representation and generation.

\subsection{Knowledge-Grounded Dialog Generation}
% Diet version
Many language generation approaches leverage pretrained language models (PLMs)~\cite{radford2019language,devlin2018bert,roberts2019exploring,thoppilan2022lamda,touvron2023llama,achiam2023gpt}, showing strong performance.
However, they often suffer from the hallucination issue~\cite{duvsek2018findings,balakrishnan2019constrained,duvsek2020evaluating}, which generates plausible but factually wrong responses since they rely on the models' internal parameters.
To address this problem, recent works~\cite{moon2019opendialkg,dinan2019wizard,lian2019learning,park2023relation} have proposed to augment the models with external knowledge sources.
This approach is effective in generating factually accurate responses in various language generation tasks~\cite{fernandes2018structured,huang2020knowledge,yasunaga2021qa,yu2022jaket,zhang2022greaselm}.
% Regarding dialog generation, various works incorporate external knowledge into the generation, where the knowledge is in the form of structured knowledge graphs~\cite{moon2019opendialkg,zhou2021earl,zhou2018commonsense,tuan2019dykgchat,zhang2019grounded}.
Regarding dialog generation, various works incorporate external knowledge graph into the generation~\cite{moon2019opendialkg,zhou2018commonsense,tuan2019dykgchat,zhang2019grounded,zhou2021earl}. 
% More related works?
%Several works have been proposed for conditioning response generation on the knowledge graphs~\cite{tuan2019dykgchat,zhang2019grounded,zhou2021earl}.
For instance, Space Efficient~\cite{galetzka2021space} proposes an efficient method to encode knowledge triplets.
% EARL~\cite{zhou2021earl} learns generalized representations of knowledge graph entities.
RHO~\cite{ji2022rho} generates responses with the dialog history and knowledge graph represented by graph embedding methods~(\eg, TransE \cite{NIPS2013_1cecc7a7}).
% It directly uses gold knowledge, which is practically inapplicable, thereby difficult to fairly compare with the other approaches.
DiffKG~\cite{tuan2022towards} uses a graph reasoning encoder on top of sparse matrices for graph representations.
SURGE~\cite{kang2022knowledge} applies GNNs to retrieve context-relevant subgraphs. 
Different from these works, our work autoregressively retrieves the context-relevant subgraphs and then generates knowledge-grounded dialogs without separate knowledge graph modules.