\section{Discussion}
\label{sec:discuss}
We acknowledge that the scope of our evaluation is limited, specifically targeting the graph exploration domain in the broader landscape of data science workflows while focusing on an industrial setting. Moreover, all the case study participants were employed at a single company. 
While we believe the observed practices
exist widely in industry and academia, the choice of participants inevitably impacted the generalizability of the findings due to organizational norms, policies, and infrastructures. Additional studies could explore \system's usage benefits and limitations in diverse settings.
Even so, the observed usage benefits and limitations of case studies highlight several opportunities for improvement. 
% While participants appreciated the freedom of customizing data operations that helped accommodate ephemeral and ever-evolving objectives within their exploratory analysis, there were suggestions for adding more features by default. This tension indicates the inherent trade-off between user empowerment and user-friendliness. We are conducting participatory design studies within \company to identify features that could be added as built-in functionalities of the widgets. The study also aims to identify additional components for supporting new workflows within the graph construction and serving platform. To improve the comprehension of a widget's features, we plan to implement a \emph{describe} method to explain component definitions, \ie their data types, supported interactions and their corresponding data operations, and the scope of the shared actions. 

% One of the key strengths of the \system framework is the capability to compose task-oriented widgets by combining components. Therefore, a possible research direction can be to investigate various component authoring strategies --- for example, via declarative specification (\eg by leveraging the grammar of interactive graphics~\cite{satyanarayan2016vega}) or using direct manipulation-based (\eg Lyra~\cite{satyanarayan2014lyra}).
% Graphileon~\cite{graphileon} is a graph-driven dashboard development environment that uses a graph database to store user-interface components (\eg Networks, Tables, Forms) in nodes. Events modeled as relations define the interactions and data flows between the UI components. Future research may explore such view composition strategies for \system widgets.
% Moreover, as highlighted in the case studies, interaction on the interface, even with specific tasks and goals, may lead to a large number of events being recorded. As a result, the history view may become challenging to use due to perceptual scalability limitations~\cite{liu2013immens, bendre2019faster, rahman2021noah}. Future versions of \system can enhance the history view to support typical exploratory data analysis operations such as search and filter.

% \todo{What are takeaways and lessons learned.}

\stitle{Graph semantics and generalizability.} In this work, we incrementally added new components and interactions based on feedback from participatory sessions. As \system is adopted more and more within \company, continuous addition of graph visualizations, composite interfaces, and data operations would be required. However, these additions should not be arbitrary and practices should be enforced to ground their design on existing graph visualization and graph task taxonomy research. One intriguing aspect of \system framework is its potential for generalizing to other domains beyond graphs, which has already been demonstrated with the table widgets. Supporting a new domain can be achieved by adding data management capabilities for the corresponding domain such as tables, text, and image. Similar to graphs, enabling exploratory analysis in other domains would require modeling the domain-specific semantics. 

\stitle{Addressing the layout gap.}
While not directly a limitation of \system, the linear layout of notebooks may attenuate the benefits afforded by \system. \system attempts to bridge the layout gap by enabling multiple coordinated visualization and resizable panes. Even so, as the analytic session progresses, the number of widgets added may increase. Future studies may explore benefits of approaches such as split panes for coding and visualization (similar to B2~\cite{wu2020b2} and Leam~\cite{rahman2020leam}) or sticky views such as StickyLand~\cite{wang2022stickyland}, in the context of \system widgets.

%To this end, the TypeScript-based design of the front-end components offers promise --- domain semantics can be infused in the component design by enforcing type constraints on the variables and component renderers.
