\documentclass[10pt,a4paper]{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{float}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage{mathptmx}
\usepackage{listings}


\title{Advancing Multi-Agent Systems Through Model Context Protocol: Architecture, Implementation, and Applications}

\author{Naveen Krishnan}

\date{\today}

\begin{document}

\maketitle

\begin{abstract}
Multi-agent systems represent a significant advancement in artificial intelligence, enabling complex problem-solving through coordinated specialized agents. However, these systems face fundamental challenges in context management, coordination efficiency, and scalable operation. This paper introduces a comprehensive framework for advancing multi-agent systems through Model Context Protocol (MCP), addressing these challenges through standardized context sharing and coordination mechanisms. We extend previous work on AI agent architectures by developing a unified theoretical foundation, advanced context management techniques, and scalable coordination patterns. Through detailed implementation case studies across enterprise knowledge management, collaborative research, and distributed problem-solving domains, we demonstrate significant performance improvements compared to traditional approaches. Our evaluation methodology provides a systematic assessment framework with benchmark tasks and datasets specifically designed for multi-agent systems. We identify current limitations, emerging research opportunities, and potential transformative applications across industries. This work contributes to the evolution of more capable, collaborative, and context-aware artificial intelligence systems that can effectively address complex real-world challenges.
\end{abstract}
\section{Introduction}
\input{section1_introduction}

\section{Theoretical Foundations}
\input{section2_theoretical_foundations}

\section{The Model Context Protocol (MCP)}
\input{section3_model_context_protocol}

\section{Multi-Agent System Architecture with MCP}
\input{section4_multi_agent_system_architecture}

\section{Advanced Context Management Techniques}
\input{section5_advanced_context_management}

\section{Implementation Case Studies}
\input{section6_implementation_case_studies}

\section{Evaluation Methodology and Results}
\input{section7_evaluation_methodology}

\section{Challenges and Future Directions}
\input{section8_challenges_future_directions}

\section{Conclusion}
\input{section9_conclusion}


\end{document}
