\documentclass[11pt]{article}

\usepackage[preprint]{acl}

\usepackage{times}
\usepackage{latexsym}


\usepackage[T1]{fontenc}

\usepackage[utf8]{inputenc}

\usepackage{microtype}
\usepackage{inconsolata}

\usepackage{graphicx}

\usepackage{booktabs}

\usepackage{multirow}

\usepackage{pifont}
\usepackage{xcolor}
\newcommand{\cmark}{\textcolor{green!60!black}{\ding{51}}} %
\newcommand{\xmark}{\textcolor{red}{\ding{55}}}            %


\usepackage{tikz}




\usepackage{amssymb}

\usepackage{makecell}

\usepackage{booktabs}



\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=.6pt] (char) {#1};}}


\usepackage{soul}
\usepackage{xcolor}
\definecolor{highlightgray}{gray}{0.9} %
\sethlcolor{highlightgray}


\newcommand{\githuburl}{\url{https://github.com/danielhuwiler/versionrag}}



\title{VersionRAG: Version-Aware Retrieval-Augmented Generation for Evolving Documents}



\author{
Daniel Huwiler \quad Kurt Stockinger \quad Jonathan Fürst \\
Zurich University of Applied Sciences, Switzerland \\
\texttt{daniel.huwiler@proton.me, kurt.stockinger@zhaw.ch, jonathan.fuerst@zhaw.ch}
}



\begin{document}
\maketitle


\begin{abstract}
Retrieval-Augmented Generation (RAG) systems fail when documents evolve through versioning—a ubiquitous characteristic of technical documentation. Existing approaches achieve only 58-64\% accuracy on version-sensitive questions, retrieving semantically similar content without temporal validity checks.
We present VersionRAG, a version-aware RAG framework that explicitly models document evolution through a hierarchical graph structure capturing version sequences, content boundaries, and changes between document states. During retrieval, VersionRAG routes queries through specialized paths based on intent classification, enabling precise version-aware filtering and change tracking.
On our VersionQA benchmark—100 manually curated questions across 34 versioned technical documents—VersionRAG achieves 90\% accuracy, outperforming naive RAG (58\%) and GraphRAG (64\%). VersionRAG reaches 60\% accuracy on implicit change detection where baselines fail (0-10\%), demonstrating its ability to track undocumented modifications. Additionally, VersionRAG requires 97\% fewer tokens during indexing than GraphRAG, making it practical for large-scale deployment. Our work establishes versioned document QA as a distinct task and provides both a solution and benchmark for future research.
\end{abstract}

\input{sections/01-intro}
\input{sections/02-related}
\input{sections/03-versionrag}
\input{sections/04-dataset-setup}
\input{sections/05-results}
\input{sections/06-conclusion}


\section*{Limitations}

While VersionRAG demonstrates strong performance on versioned document QA, several limitations constrain its applicability:

\paragraph{Dataset Scale and Diversity.}
Our evaluation uses 100 manually curated question-answer pairs across 34 documents. While manual curation ensures high quality and diverse query types, this scale limits statistical testing and fine-grained error analysis. The dataset focuses exclusively on technical documentation (Node.js, Apache Spark, Bootstrap). Generalization to other domains with different versioning conventions (legal documents with amendment structures, medical guidelines with approval stages, scientific papers with revision rounds) remains unexplored and may require domain-specific adaptations.

\paragraph{Change Detection Limitations.}
VersionRAG achieves 60\% accuracy on implicit change detection—our most challenging task. The DeepDiff-based comparison may miss subtle semantic changes that don't manifest as clear textual differences (e.g., a security implication from changing default values). Additionally, smaller LLMs like Llama 3 8B produce 42\% fewer change nodes than larger models, directly linking change detection quality to model capacity. Production systems requiring high precision for compliance or security-critical change tracking may find this insufficient.

\paragraph{Version Extraction Requirements.}
The system assumes documents contain extractable version information in their first pages and maintain consistent structure across versions. Documents with version information embedded in filenames only, irregular formatting, or versioning schemes that don't follow semantic conventions (e.g., date-based versions, code names) may fail during indexing. The sequential processing of versions also cannot capture complex dependencies between non-adjacent versions (e.g., a feature deprecated in v2.0 but reimplemented differently in v4.0).

\paragraph{Model and Infrastructure Dependencies.}
Performance degrades significantly with model size: query classification accuracy drops from 92\% (DeepSeek-R1 70B) to 76\% (Llama 3 8B), directly impacting downstream retrieval. This creates deployment challenges for resource-constrained environments. Infrastructure requirements include both a graph database (Neo4j) and vector store (Milvus), increasing operational complexity compared to pure vector-based solutions. The system also requires 186K tokens for indexing our 34-document test collection—while 97\% less than GraphRAG, this still represents substantial API costs for organizations with thousands of documents.

\paragraph{Temporal Reasoning Gaps.}
While VersionRAG handles discrete version numbers effectively, it cannot reason about continuous temporal aspects within versions. Questions like "What features were added in Q3 2023?" require mapping calendar time to version releases, which our current system does not support. Similarly, questions about development velocity ("How quickly are deprecations typically resolved?") or version lifecycle patterns are beyond the current scope.

\paragraph{Error Propagation.}
The pipeline architecture means errors compound: misclassified queries (8\% error rate) lead to incorrect retrieval paths, version extraction errors affect all downstream processing, and incorrect change detection permanently impacts the graph structure. Unlike end-to-end learned systems, these errors cannot be corrected through backpropagation, requiring manual intervention or complete reindexing to fix.

\section*{Ethical Considerations}

\paragraph{Environmental Impact.}
While VersionRAG reduces computational costs by 97\% compared to GraphRAG, the indexing process still requires substantial LLM API calls (186K tokens for our 34-document collection). Organizations should consider the environmental impact of processing large document repositories and explore batch processing or caching strategies to minimize redundant computations.

\paragraph{Fairness and Bias.}
VersionRAG's performance depends heavily on the underlying LLM's capabilities, inheriting any biases present in these models. Our evaluation focused on English technical documentation; performance may vary significantly for other languages or domains. The system's 92\% query classification accuracy with large models versus 76\% with smaller models could create disparities in service quality based on available computational resources.

\paragraph{Data Privacy.}
Versioned documents often contain sensitive information about deprecated features, security vulnerabilities, or internal changes. While VersionRAG processes documents locally after initial LLM-based indexing, organizations must carefully consider which documents to include and ensure appropriate access controls on the resulting knowledge graph.

\paragraph{Transparency and Accountability.}
The system's 10\% error rate, particularly in change detection, could lead to incorrect technical decisions if users over-rely on its outputs. We recommend clearly communicating confidence levels and providing source attribution for all retrieved information. The version-aware graph structure actually enhances accountability by maintaining clear provenance for all information.

\paragraph{Broader Impacts.}
Improved access to versioned documentation could democratize technical knowledge and reduce barriers for developers working with evolving systems. However, it might also enable more sophisticated attacks if applied to security documentation. We encourage responsible deployment with appropriate access controls and monitoring.


\paragraph{AI Assistants In Research Or Writing}
We have used GPT-5, Gemini 2.5 pro and Claude Opus 4.1 to help us refine our writing. All final text in the paper has been verified by the authors.

\bibliography{custom}

\appendix
\onecolumn
\input{sections/appendix}

\end{document}
