% Discussion - fragment file, included via \input{sections/discussion}
% Does not contain \section{} header; \section{Discussion}\label{sec:discussion} is defined in main.tex

This section discusses design implications derived from the system's design and evaluation (\S\ref{sec:design-implications}), clinical integration considerations (\S\ref{sec:clinical-integration}), and limitations (\S\ref{sec:limitations}).

\subsection{Design Implications and Responses to Research Questions}\label{sec:design-implications}

\paragraph{Implication 1: Diagnosis as Explanation. Progressive Visualization Builds Trust (RQ2)}
The system's real-time progressive KG updating transforms the diagnostic process itself into an explanatory tool: users observe how candidate syndromes narrow across interaction rounds, understanding the basis behind each follow-up question. The diagnosis-treatment dual-chain visualization further enables users to trace reasoning paths from symptoms to syndrome patterns and onward to treatments, making conclusions traceable and verifiable. This design implies that health informatics systems should treat the diagnostic process, not merely the final decision, as the core object of visualization\cite{24,35}. A transparent reasoning process is an important factor for building trust\cite{40}, although transparency alone is not sufficient to address all user risks and must be complemented by contextualized usage guidelines\cite{41}. Evaluation confirmed that this approach produced a large effect improvement across all five trust dimensions.

\paragraph{Implication 2: Soft Scaffold, Hard Boundary. KG Constraints and Multi-Round Interaction Synergy (RQ1)}
Our system uses the KG simultaneously as a ``soft scaffold'' guiding interaction and a ``hard boundary'' constraining outputs. At the interaction level, the information gain-driven follow-up strategy selects the most discriminative symptoms within the candidate space, transforming diagnosis into a natural dialogue requiring only 2 to 3 follow-up rounds\cite{11,12}. At the constraint level, the LLM handles flexible symptom extraction on the input side, while the KG constrains the output space to validated syndrome-symptom associations on the output side, reducing the risk of hallucinated diagnostic conclusions\cite{25,64,44,45}. This complementary architecture addresses the respective limitations of KG-only rigidity and LLM-only unreliability.

\paragraph{Implication 3: Heterogeneous Modality Division. Multimodal Presentation Lowers Cognitive Barriers (RQ3)}
Different modalities serve different cognitive functions: text conveys logical reasoning, images convey intuitive understanding, and 3D models convey spatial localization\cite{67,Baxter2025}. This division enables differentiated information access: patients grasp treatment essentials through intuitive images, physicians consult detailed formula compositions and KG reasoning paths, and students use interactive 3D models for acupoint localization\cite{30,69}. Evaluation confirmed that the multimodal plan significantly reduced cognitive load compared to text-only presentation, with acupoint localization showing the most pronounced improvement.

\subsection{Clinical Integration Considerations}\label{sec:clinical-integration}

The system should function as a decision-support tool embedded within physicians' existing workflows, with final decisions made by licensed physicians. Deployment requires professional training, informed consent regarding AI involvement, and data privacy compliance\cite{7,8,14}.

\subsection{Limitations}\label{sec:limitations}

We identify the following limitations of the current system:

\begin{enumerate}
  \item \textbf{Limited KG Coverage}: The knowledge graph covers 241 syndrome patterns, but TCM literature documents over 1000 types; rare syndromes and regional differentiation systems (e.g., Lingnan medicine) remain excluded.
  \item \textbf{Lack of Large-Scale User Study}: Evaluation relied on the LLM-as-a-Judge framework with limited sample sizes ($N=25$--$30$), which may exhibit systematic biases. A controlled user study with practitioners remains necessary for validating clinical utility.
  \item \textbf{LLM Content Reliability}: Although KG constraints reduced non-standardized outputs by 32\%, treatment plans may still contain inaccurate recommendations. The system currently lacks a human-AI collaborative review mechanism for physician oversight.
  \item \textbf{No Real Clinical Validation}: Evaluation used retrospective CEMRs data without prospective validation in real clinical settings. A prospective clinical trial is necessary to assess real-world performance.
\end{enumerate}

\subsection{Conclusion}\label{sec:conclusion}

This paper presented a knowledge graph-driven TCM visual diagnostic system that addresses three interrelated challenges in AI-assisted syndrome differentiation: opaque reasoning, passive interaction, and simplistic treatment presentation. By combining progressive KG visualization with LLM-based symptom extraction, the system makes diagnostic reasoning transparent and interactive while constraining outputs to validated medical knowledge. Evaluation demonstrated substantial trust improvements (Cohen's $d=1.82$) and reduced cognitive load through multimodal treatment plans. KG constraints also reduced non-standardized LLM outputs by 32\%. These results suggest that structured knowledge constraints can complement generative AI capabilities in clinical decision support. Current limitations include reliance on automated evaluation with limited sample sizes and incomplete KG coverage. Future work will prioritize prospective clinical validation with practitioners and patients, expanded syndrome coverage, and EHR integration to support real-world deployment.
