% Results - fragment file, included via \input{sections/results}
% Contains the full content of the evaluation chapter

\subsection{Evaluation Strategy}\label{sec:eval-strategy}

This paper focuses on overall system design and interaction experience rather than algorithmic peak performance.
We adopted a four-pronged evaluation strategy:
(1)~\textbf{Technical accuracy verification}: quantitative syndrome differentiation accuracy on a clinical dataset, compared against mainstream large language models;
(2)~\textbf{Case study}: a complete diagnostic workflow demonstrating how design decisions operate together (presented in Supplementary Information Section~S3);
(3)~\textbf{System capability assessment}: response time and rendering performance analysis;
(4)~\textbf{LLM-as-a-Judge automated evaluation}: paired comparison evaluations assessing trust, cognitive load, and reference credibility to quantify each design decision's effect.
All evaluation data were de-identified, and no real patient interactions were involved.

\subsection{RQ1: Syndrome Differentiation Accuracy}\label{sec:eval-accuracy}

\paragraph{Dataset}
We used the CEMRs dataset containing 2,000 de-identified Chinese electronic medical records covering 147 unique syndrome pattern labels drawn from real clinical settings.

\paragraph{Comparison Methods}
To illustrate the benefit of knowledge graph constraints, we compared against two baselines:
(1)~DeepSeek R1\cite{58}, a general-purpose large language model with strong reasoning capabilities;
(2)~HuatuoGPT-Vision\cite{62}, a medical domain-specific model fine-tuned on medical corpora.
This comparison aims to demonstrate the effect of knowledge graph constraints, not to claim comprehensive superiority.

\paragraph{Results and Analysis}
Table~\ref{tab:accuracy-comparison} presents the Top-1 syndrome differentiation accuracy on the CEMRs dataset.

\begin{table}[pos=tbp]
  \centering
  \caption{Syndrome Differentiation Accuracy Comparison on the CEMRs Dataset}
  \label{tab:accuracy-comparison}
  \begin{tabular}{lc}
    \toprule
    \textbf{Method} & \textbf{Top-1 Accuracy} \\
    \midrule
    Our System & \textbf{47.11\%} \\
    DeepSeek R1 & 19.76\% \\
    HuatuoGPT-Vision & 11.23\% \\
    \bottomrule
  \end{tabular}
\end{table}

Several contextual factors inform these results.
The dataset contains 147 fine-grained syndrome labels (far exceeding the 10--20 coarse-grained categories in common benchmarks), and cases come from real clinical records with inherent noise such as colloquial language and ambiguity.

After introducing knowledge graph constraints, non-standardized outputs decreased by approximately 32\% compared to unconstrained LLMs, indicating that the knowledge graph constrains the generation space and reduces non-standard outputs, though hallucination cannot be eliminated entirely.

\paragraph{Reproducibility Statement}
Due to privacy restrictions, the CEMRs dataset cannot be publicly released. We provide 160 de-identified sample cases (\texttt{public\_dataset.json}) with complete prompt templates for independent validation.

\subsection{RQ2: Effect of Knowledge Graph Enhancement on Trust}\label{sec:eval-rq1-trust}

Using the LLM-as-a-Judge approach, we generated diagnostic results with and without knowledge graph enhancement for 30 CEMRs cases.
A large language model simulating target users performed paired comparison evaluations across five trust dimensions: diagnostic transparency, evidence traceability, reasoning confidence, information completeness, and trust level.
Each dimension was tested using the Wilcoxon signed-rank test with Benjamini--Hochberg correction.
Table~\ref{tab:rq1-trust} summarizes the paired trust evaluation results.

\input{paper_tables/rq1_trust_table}

Knowledge graph enhancement produced significant improvements across all five dimensions (all $p_{\mathrm{adj}}<0.001$), with an overall Cohen's $d=1.82$.
\textbf{Information completeness} showed the largest effect ($d=2.18$), indicating that structured knowledge graph presentation substantially enhanced users' perception of diagnostic information coverage.
\textbf{Evidence traceability} followed ($d=1.73$), reflecting clearer reasoning paths through graph visualization.
\textbf{Reasoning confidence} had the smallest effect ($d=0.87$), still within the large effect range, possibly because this dimension involves deeper cognitive judgment.

\subsection{RQ3.1: Effect of Multimodal Plans on Cognitive Load}\label{sec:eval-rq3a-cognitive}

We generated text-only plans (Plan~A) and multimodal plans (Plan~B, with 3D acupoint models and AI-generated illustrations) for 30 cases, evaluated by a large language model simulating non-specialist users.
Five cognitive dimensions were assessed; cognitive load was reverse-scored (higher = lower load, positive $\Delta$ = Plan~B advantage).
Table~\ref{tab:rq3-cognitive} reports the cognitive load comparison.

\input{paper_tables/rq3_cognitive_load}

Four of five dimensions reached statistical significance ($p_{\mathrm{adj}}<0.001$).
\textbf{Acupoint localization} showed the most pronounced improvement ($\Delta=+1.87$, $r=1.00$), directly reflecting the 3D bronze figure model's advantage for spatial localization.
\textbf{Action confidence} ($\Delta=+0.70$, $r=0.91$) and \textbf{language comprehension} ($\Delta=+0.50$, $r=0.88$) also improved significantly.
\textbf{Preparation clarity} showed a positive trend ($\Delta=+0.27$) but did not reach significance after correction ($p_{\mathrm{adj}}=0.053$).
Overall cognitive load improved significantly ($\Delta=+0.60$, $r=0.90$), confirming that multimodal plans effectively reduced cognitive load.

\subsection{RQ3.2: Effect of References on Evidence Credibility}\label{sec:eval-rq3c-refs}

Paired comparison evaluations of plans with and without references were conducted across 30 cases; five were excluded due to invalid reference URLs, yielding 25 valid cases.
Five dimensions were assessed: source credibility, evidence verifiability, information confidence, comprehension support, and overall evidence quality.
Table~\ref{tab:rq3_references} reports the reference credibility evaluation.

\input{paper_tables/rq3_references}

Plans with references scored 4.21 overall, significantly higher than 2.95 without ($\Delta=+1.27$); four of five dimensions reached significance ($p_{\mathrm{adj}}<0.001$).
\textbf{Evidence verifiability} had the largest effect (Cohen's $d=1.98$), indicating that references transformed recommendations from unverifiable assertions into traceable evidence-based information.
\textbf{Overall evidence quality} ($d=1.55$) and \textbf{source credibility} ($d=1.52$) also showed large improvements.
\textbf{Comprehension support} did not reach significance ($p_{\mathrm{adj}}=0.317$, $d=-0.20$), aligning with expectations: references primarily enhance traceability and credibility rather than plan comprehensibility.

Beyond these quantitative evaluations, we conducted illustrative case studies across representative clinical scenarios to validate the system's end-to-end diagnostic workflow, covering patient self-assessment, physician-assisted diagnosis, and TCM education contexts.
Full case study results are presented in the Supplementary Information (Section~S3).

\subsection{System Performance and Limitations}\label{sec:eval-limitations}

\paragraph{System Performance}
At the engineering level, the system demonstrated good response efficiency: the average response time per interaction round was under 30 seconds,
the frontend ECharts knowledge graph visualization update rendered within 200ms, and the overall interaction fluency met real-time dialogue requirements.

\paragraph{Limitations}
The system has several limitations, including knowledge graph syndrome coverage, evaluation scale, LLM output reliability, dataset external validation, and cross-language applicability. These limitations are discussed in detail in Section~\ref{sec:limitations}.
