\section{Model Training and Inference Details}
\label{section:hyperparameter}

We adopted Transformers \cite{DBLP:conf/emnlp/WolfDSCDMCRLFDS20}, DeepSpeed\footnote{https://github.com/deepspeedai/DeepSpeed}, Liger Kernel \cite{DBLP:journals/corr/abs-2410-10989} and Transformer Reinforcement Learning (TRL)\footnote{https://github.com/huggingface/trl} for training. Table \ref{table:hyperparameter} shows the detailed training hyperparameters. We did not conduct any parameter search; instead, we followed industry best practices to set the important parameters.

One ml.p4de.24xlarge instance has eight A100 GPUs, and each GPU has 80GB GPU RAM. For Llama-3.1-70B-Instruct, we employed three and four instances for SFT and DPO respectively; for Llama-3\_3-Nemotron-Super-49B-v1\_5, we utilized two and three instances for SFT and DPO respectively; for Qwen3-30B-A3B-Instruct-2507, we adopted one and two instances for SFT and DPO respectively.

In terms of training time, for Qwen3-30B-A3B-Instruct-2507, Llama-3\_3-Nemotron-Super-49B-v1\_5 and Llama-3.1-70B-Instruct, it needed 13, 2.5 and 3.5 hours for SFT respectively, and took 6, 2 and 2.5 hours for DPO respectively. For all model training, we trained for five epochs, and used our development set (Section \ref{section:evaluation_kg_generation}) for model selection. All our model training is fully reproducible. In total, our model training consumed 320 GPU hours.

We also employed SGLang\footnote{https://github.com/sgl-project/sglang} for inference; due to its non-reproducible nature, we ran each inference twice and reported the average. On our evaluation benchmarks, a single inference run can take up to 70 minutes (the COLIEE benchmark in Appendix \ref{section:appendix_benchmark}). We ran all inferences on a single instance. All our evaluations consumed a total of 480 GPU hours.

These libraries are open-source, and the base models are available from Hugging Face\footnote{https://huggingface.co/models}. The only proprietary artifact we use is Sonnet 3.5. All use of these artifacts are consistent with their intended use.

\begin{table}[ht]
  \centering
  \begin{tabular}{lcr}
    \hline
    \textbf{Hyperparameter} & \textbf{SFT} & \textbf{DPO} \\ \hline
    Learning rate & 1e-6 & 5e-7 \\
    Scheduler & \multicolumn{2}{c}{linear} \\
    Effective batch size & 384 & 192 \\
    Optimizer & \multicolumn{2}{c}{Adam} \\
    Attention & \multicolumn{2}{c}{FA2} \\
    Liger Kernel & Yes & No \\
    Model precision & \multicolumn{2}{c}{bfloat16} \\
    Gradient & \multicolumn{2}{c}{\multirow{2}{*}{Yes}} \\
    checkpointing & \\
    DeepSpeed & \multicolumn{2}{c}{Zero-3 without offload} \\
    Hardware & \multicolumn{2}{c}{ml.p4de.24xlarge} \\ 
    Training Data Size & 13.5K & 5.3K \\ \hline
  \end{tabular}
  \caption{\label{table:hyperparameter}
    Model training hyperparameters. SFT and DPO represent Supervised Fine-Tuning and Direct Preference Optimization respectively. \textit{Effective batch size} includes gradient accumulation.
  }
\end{table}