\section*{Limitations}
Of course our work has several limitations. First, constrained by GPU resources, our experiments are primarily conducted with LLMs up to 72B parameters and embedding models up to 4B parameters—though these sizes are practical for most developers and small-to-medium enterprises for local deployment. Second, the evolving query and sub-graph refinement components increase inference latency, typically 2–3× slower than baseline methods, making our approach more suitable for accuracy-critical applications where sacrificing speed for improved knowledge fidelity is acceptable. Third, the same mechanisms result in longer context inputs, which demand larger GPU memory capacity for efficient processing.
These limitations could be mitigated through model distillation, optimized graph traversal algorithms, and dynamic context pruning techniques in future improvement.
% Future work will explore three promising directions for further advancement. 
% First, we plan to extend our multi-agent evolving framework to support larger-scale and more complex knowledge-intensive tasks, such as programming assistance, financial analysis, and clinical decision-making.
% % by enhancing the coordination mechanisms and scalability of the MACER architecture. 
% Second, we aim to generalize our method from text to multimodal reasoning, integrating audio, image, and video modalities to construct a world model that bridges textual knowledge with perceptual grounding. 
% Third, inspired by human cognitive science and brain science, we will explore novel architectures that combine parametric memory with large language models to unify memory and reasoning in a seamless framework, enabling more efficient knowledge retention and tool-use capabilities akin to human intelligence.

\section*{Ethical Considerations}
This research focuses on improving the technical performance of knowledge-enhanced language models. This work utilizes only public benchmark datasets and adheres to strict reproducibility standards. While our framework improves text generation capability, we acknowledge potential risks of generating misleading content and note that performance may reflect biases inherent in base models. We follow the ACL ethical guidelines when conducting the research in this paper.

\section*{Information About Use Of AI Assistants}
In the preparation of this work, the author used AI-assisted technology (specifically, large language models such as GPT-5 and Deepseek-V3) exclusively for text refinement purposes. The AI was employed to assist in proofreading, correcting grammatical errors, and polishing linguistic expressions to improve the clarity and readability of the manuscript.