\paragraph{GraphRAG.}
GraphRAG extends the conventional RAG paradigm by structuring retrieved knowledge as entities and relations, thereby providing stronger support for multi-hop reasoning and knowledge-intensive QA. Early GraphRAG methods~\cite{GraphRAG,RAPTOR} typically construct knowledge graphs with entities as nodes and relations as edges. Recent works~\cite{LightRAG,LinearRAG,HippoRAG,HippoRAG2} further enhance the representation power of GraphRAG by incorporating richer graph structures (e.g., HyperGraph), thereby improving evidence organization and multi-hop reasoning over complex knowledge, typically with the support of large-scale LLMs. Meanwhile, another line of work explores GraphRAG systems~\cite{Graph-R1, GraphSearch, GraphRAG-R1} that rely on smaller models, whose reasoning capabilities are enhanced through RL. In this study, we focus on the setting where GraphRAG frameworks are paired with large and costly LLMs, which often incurs substantial computational cost and still relies on a fixed retrieval infrastructure.

\paragraph{LLM Routing.}
Current LLM routing frameworks aim to select appropriate generator models from a candidate pool according to query complexity. Existing studies have explored both predictive model routing~\cite{KNNRouter, graphrouter} and multi-round routing strategies over candidate LLMs, including RL-based approaches such as Router-R1~\cite{Router-R1} that interleave internal reasoning with dynamic model selection and response aggregation. However, these methods focus solely on routing among generator LLMs. In contrast, our setting requires joint routing over both GraphRAG frameworks and generator LLMs, which introduces a substantially larger and more complex action space.

% \paragraph{Agentic Search LLMs.} To mitigate the limitations of single-shot retrieval, recent works~\cite{Search-o1,GraphSearch,GraphSearchjiajin} has explored agentic paradigms in which LLMs iteratively conduct multi-round search and reasoning, progressively collecting evidence for complex tasks. More recently, with the emergence of reinforcement learning methods such as GRPO~\cite{GRPO}, some studies~\cite{Graph-R1,Search-R1,GraphRAG-R1} have moved beyond training-free designs and explored learnable search policies, where multi-turn search behavior is optimized with rule-based reward signals.

