
\section{Experiments}
\subsection{Experimental Setup}
\label{sec:setup}

We conduct experiments on three challenging and complementary benchmarks: \textbf{MMLU} \citep{hendrycks2020measuring}, \textbf{GSM8K} \citep{cobbe2021training}, and \textbf{GPQA} \citep{reinGPQAGraduateLevelGoogleProof2023}. The PPO-based topology controller of RUMAD is exclusively trained on the MMLU dev dataset, leveraging its broad coverage of multi-domain reasoning tasks. Table~\ref{tab:hyperparameters} summarizes the training hyperparameter settings used throughout our experiments. For evaluation, we report results on the MMLU test set as well as on GSM8K (arithmetic reasoning) and GPQA (graduate-level science QA). Notably, for GSM8K and GPQA, we apply RUMAD controller in a zero-shot transfer setting without any further fine-tuning, directly assessing the generalization capability of the learned communication policy.

% \begin{table}[t]
% \centering
% \caption{Training hyperparameters used for the PPO-based topology controller of RUMAD.}
% \begin{tabular}{ccc}
% \toprule
% {\color[HTML]{000000} \textbf{Symbol}} & \textbf{Description} & {\color[HTML]{000000} \textbf{Value}} \\ \midrule
% $d_h$ & Hidden layer dimension & 128 \\
% $\alpha$ & Learning rate & $1\times10^{-4}$ \\
% $\gamma$ & Discount factor & 0.99 \\
% $\lambda$ & GAE parameter & 0.95 \\
% $\varepsilon$ & Policy clipping threshold & 0.20 \\
% $c_1$ & Value loss coefficient & 0.01 \\
% $c_2$ & Budget penalty coefficient & 0.01 \\
% $E$ & Update epochs per rollout & 1\\
% $b$ & Batch size per update & 10 \\
% $L$ & Rollout length & 10 \\
% \bottomrule
% \end{tabular}%
% \label{tab:hyperparameters}
% \end{table}

\begin{table}[t]
% \setlength{\tabcolsep}{1.3mm}
\centering
\caption{Performance of RUMAD and baselines across three evaluation datasets. Token cost is calculated as average of each topic debated. (6,6) is general mark of MAD systems indicating 6-agent, 6-round configuration. RUMAD significantly reduces token cost with comparable or improved accuracy. S-MAD with different structures are denoted as * (Star) and o (Ring). Since RUMAD is trained upon MMLU dev partition, MMLU test partition is used for evaluation. RUMAD evaluated upon GPQA-main and GSM8K is zero-shot migrated, without any finetuning with new datasets. RUMAD shows superior cross-domain generality. \protect\newtext{Note: All baseline accuracies are measured under identical 4-bit quantization and 0-shot settings for a fair comparison.}} 
\begin{tabular}{llccc}
\toprule
\textbf{Task} & \textbf{Method} (6,6) & \textbf{ACC} & \textbf{\makecell[c]{Token Cost\\(k/task)}} & \textbf{\makecell[c]{Cost\\Saving}} \\
\midrule
\multirow{7}{*}{MMLU}
 & \textbf{RUMAD$_{B=12}$} & 68\% & \textbf{11.43} & \textbf{-81.74\%} \\
 & \textbf{RUMAD$_{B=18}$} & \textbf{68\%} & 22.46 & -64.11\% \\
 & MAD & 49\% & 62.58 & N/A \\
 & S-MAD$_*$ & 61\% & 33.32 & -46.75\% \\
 & S-MAD$_\circ$ & 54\% & 31.70 & -49.34\% \\
 & GD & 53\% & 32.17 & -48.59\% \\
 & S$^2$MAD & 46\% & 25.36 & -58.48\% \\
\midrule
\multirow{7}{*}{GPQA}
 & \textbf{RUMAD$_{B=12}$} & 32\% & \textbf{19.53} & \textbf{-66.21\%} \\
 & \textbf{RUMAD$_{B=18}$} & \textbf{35\%} & 33.39 & -42.24\% \\
 & MAD & 30\% & 57.80 & N/A \\
 & S-MAD$_*$ & 30\% & 36.37 & -37.08\% \\
 & S-MAD$_\circ$ & 34\% & 38.59 & -33.24\% \\
 & GD & 34\% & 26.05 & -54.93\% \\
 & S$^2$MAD & 28\% & 23.26 & -59.76\% \\
\midrule
\multirow{7}{*}{GSM8K}
 & \textbf{RUMAD$_{B=12}$} & 86\% & \textbf{10.46} & \textbf{-86.40\%} \\
 & \textbf{RUMAD$_{B=18}$} & \textbf{89\%} & 17.28 & -77.53\% \\
 & MAD & 88\% & 76.90 & N/A \\
 & S-MAD$_*$ & 83\% & 39.38 & -48.78\% \\
 & S-MAD$_\circ$ & 70\% & 37.82 & -50.81\% \\
 & GD & 84\% & 29.76 & -61.30\% \\
 & S$^2$MAD & 70\% & 30.51 & -60.32\% \\
\bottomrule
\end{tabular}
\label{tab:performance}
\end{table}

To maximize the heterogeneity and dynamic interactions within the debate, we instantiate a diverse agent pool comprising three different LLM models: \textbf{LLaMA-3.1-8B-Instruct} \citep{touvron2023llama}, \textbf{ChatGLM-4-9B} \citep{glm2024chatglm}, and \textbf{Deepseek-Math-7B-Instruct} \citep{guo2025deepseek}. Each architecture is represented by two agents, forming a six-member debate group per trial. \newtext{For each agent, there are 4 non-similar agents and 1 similar agent.} This multi-architecture composition is designed to capture a spectrum of reasoning styles and knowledge bases. 

For computational efficiency and scalability, all LLMs are deployed using \newtext{\textbf{4-bit groupwise quantization (Q4\_K\_M)}} with mixed precision. Embedding model used for RUMAD to compute similarity among texts, defined in Equation~\ref{eq:similarity}, is \textbf{Nomic-Embed-v1} \citep{nussbaumNomicEmbedTraining2025}. This configuration enables concurrent inference of all agents on a single NVIDIA GeForce RTX 3090 GPU, facilitating systematic ablation and large-scale evaluation. \newtext{Thus, an efficiency-focused \textbf{0-shot, 4-bit} setup is crucial for fair baseline comparison. For instance, the LLaMA-3.1-8B-Instruct is officially reported with 69.4\% accuracy on MMLU under \textbf{5-shot, bf16-precision} conditions, while actually achieving 57.9\% under \textbf{0-shot, 4-bit} setting.} 

We benchmark RUMAD primarily against MAD, a fully-connected debate protocol that omits both visibility control and prompt structuring, thereby preserving complete information exchange among all agents throughout the discussion. In addition, we evaluate against S-MAD, GD, and S$^2$-MAD using each method’s reported optimal configuration. 

Our evaluation focuses on two key metrics: (1) solution \textbf{accuracy} across diverse problem categories, and (2) computational \textbf{efficiency} as measured by total token consumption. And we evaluate generality of RUMAD by comparing its performance across different benchmarks. Scripts for training and evaluating, along with RUMAD PPO checkpoint weight files, will be provided in supplementary files.

\subsection{Results and Analysis}
\label{sec:main_result}
As shown in Table~\ref{tab:performance}, our proposed RUMAD framework achieves a substantial reduction in communication cost while maintaining, or even enhancing, answer accuracy across all evaluated benchmarks. On both MMLU and GSM8K, RUMAD reduces average token usage per task by over 80\% compared to the fully connected MAD baseline, yet achieves much better accuracy (e.g., 68\% vs 49\% on MMLU). RUMAD also provides best token cost saving on GPQA, while higher accuracy is available if assigned more communication budget (12 to 18 times per round). This demonstrates the efficacy of reinforcement learning-based dynamic topology control of RUMAD in identifying and preserving the most informative agent interactions under tight communication budgets. The results highlight that significant efficiency gains are attainable without sacrificing group reasoning performance.

\paragraph{\textbf{$B$ as configurable prior budget}} A salient advantage of our framework lies in the explicit budget parameter $B$ utilized in budget loss defined in Equation~\ref{eq:Loss_budget}, which directly governs the maximum expected communication load per round. By adjusting $B$, practitioners can specify a clear prior on resource consumption, aligning debate efficiency with practical deployment constraints. Our results show that even at relatively low budget levels (e.g., $B=12$ for six agents), the controller learns to allocate communication judiciously, maintaining high accuracy with a fraction of the original token cost.

We configured a comparison with $B=18$, indicating user prior preference is communication of 3 times per agent per round in identical 6-agent system. RUMAD is capable to allocate this budget adaptively and get higher accuracy performance on all benchmarks, with corresponding trade-off on token-cost. This interpretability and controllability of $B$ enhances the usability of our approach in real-world multi-agent systems. As we can see, on MMLU tasks, $B=12$ budget is sufficient for RUMAD to coordinate debate and achieve comparable accuracy with $B=18$ budget (68.30\% vs 68.48\%), while on GPQA and GSM8K, RUMAD utilize more budget to provide better performance.

\newtext{As defined in Equation~\ref{eq:Loss_budget}, $B$ acts as a \textbf{training-time prior} via the loss function, encouraging the policy to internalize a preference for sparsity, rather than a \textbf{hard constraint at inference} applied to scheduler. Utilization of $B$ provides better alignment of human prior preference without increasing cost of hyperparameter tuning.}

\paragraph{\textbf{RUMAD zero-shot generality}} We observe that the RUMAD controller, trained solely on the MMLU development set, generalizes robustly to out-of-domain benchmarks such as GPQA and GSM8K in a zero-shot setting. It's notable that MMLU is single-choice task while GSM8K needs arithmetic answers. Despite no exposure to these domains during training, RUMAD maintains competitive accuracy and cost savings, underscoring the generality and transferability of the learned communication policy. \newtext{This strong out-of-domain performance also serves as key evidence of \textbf{hyperparameter robustness}. The same model trained on MMLU under reward model with parameter$\alpha_k, \beta_k$ transferred directly to GSM8K and GPQA without modification, indicating the learned policy is not brittle or overfitted to the training domain, a common concern with complex reward structures.} This result suggests that our method is not tightly coupled to any single task distribution or agent type, facilitating practical deployment across diverse collaborative reasoning scenarios.

\begin{table}[t]
\setlength{\tabcolsep}{1.3mm}
\centering
\caption{\newtext{Ablation study of RUMAD's key components. We report accuracy (ACC, \%) and average token cost (TC,  in k/task). The best result for each metric is in \textbf{bold}. We set $B=12$ for all variants.}}
\begin{tabular}{lcccccc}
\toprule
\multirow{2.5}{*}{\textbf{Ablation Module}} & \multicolumn{2}{c}{\textbf{MMLU}} & \multicolumn{2}{c}{\textbf{GPQA}} & \multicolumn{2}{c}{\textbf{GSM8K}} \\
\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7}
 & \textbf{ACC} & \textbf{TC} & \textbf{ACC} & \textbf{TC} & \textbf{ACC} & \textbf{TC} \\
\midrule
\textbf{RUMAD} & 68.3 & \textbf{11.4} & \textbf{31.9} & \textbf{19.5} & \textbf{86.4} & \textbf{10.5} \\
$\beta$ distribution & 65.1 & 18.7 & 29.2 & 28.7 & 84.5 & 17.2 \\
w/o $R_{ep}$ & 66.9 & 15.6 & 31.0 & 24.4 & 85.1 & 14.3 \\
w/o $R_{t}$ & 67.2 & 22.2 & 30.1 & 32.6 & 86.0 & 20.2 \\
w/o agent activation & 65.4 & 51.9 & 31.7 & 67.5 & 86.1 & 45.0 \\
w/o $\mathcal{L}_\mathrm{budget}$ & \textbf{70.0} & 17.4 & 27.7 & 26.8 & 85.8 & 15.6 \\
\bottomrule
\end{tabular}
\label{tab:ablation}
\end{table}

\subsection{\newtext{Ablation Study}}
\label{sec:ablation}
\newtext{We conduct a comprehensive ablation study to investigate the contribution of each key component of RUMAD. To ensure a fair comparison, all variants are trained exclusively on the MMLU dev dataset and operate under a consistent 6-agent, 6-round configuration. The results, summarized in Table~\ref{tab:ablation}, are evaluated on MMLU, GPQA, and GSM8K, reporting both accuracy and average token cost. The findings demonstrate that each module is integral to the model's performance, and the full RUMAD framework achieves the best overall trade-off between accuracy and efficiency.}

\newtext{\paragraph{\textbf{Change to $\beta$ distribution}} RUMAD models agent connections using a Gaussian distribution to avoid overfitting. Replacing this with a $\beta$ distribution results in a significant performance drop: accuracy falls across all benchmarks (e.g., 68.3\% to 65.1\% on MMLU), and the token cost substantially increases, underscoring the superior modeling capability of the Gaussian parameterization.}

\newtext{\paragraph{\textbf{Ablation of $R_{ep}$ and $R_t$}} Our two-tier reward system is critical for balancing immediate and long-term goals. It combines the per-round reward $R_{t}$ with an episode reward $R_{ep}$ applied only at the final round. In thew/o $R_{ep}$ variant, we replace the final round's $R_{ep}$ with the standard $R_{t}$, which causes a notable drop in accuracy and a $\sim$37\% increase in token cost on MMLU (11.4k to 15.6k). Conversely, in the w/o $R_{t}$ variant, we broadcast the final $R_{ep}$ value to all preceding rounds. This results in a severe impact on efficiency, nearly doubling the token cost. This highlights that both reward signals are necessary for learning an efficient policy.}

\newtext{\paragraph{\textbf{Ablation of agent activation}} The agent activation mechanism is paramount for efficiency. It conditionally decides if an agent generates a new response, enabling true communication sparsification. Removing it (w/o agent activation) means that even with efficient pruning of communication edges, all agents are still forced to generate a new response in every round. This inability to dynamically silence agents causes a catastrophic increase in token cost (e.g., a $\sim$4.5x increase on MMLU), while accuracy also suffers. This confirms that dynamic agent activation, not just edge pruning, is the primary driver of RUMAD's token savings.}

\newtext{\paragraph{\textbf{Ablation of $\mathcal{L}_\mathrm{budget}$}} The budget loss $\mathcal{L}_\mathrm{budget}$ acts as a crucial regularizer for both efficiency and generalization. Without it, the controller fails to converge to an efficient policy, incurring higher token costs. Interestingly, while this variant achieves higher accuracy on the in-domain MMLU task (70.0\%), its performance drops significantly on the out-of-domain benchmarks GPQA (27.7\% vs. 31.9\%) and GSM8K (85.8\% vs. 86.4\%). This strongly suggests that $\mathcal{L}_\mathrm{budget}$ not only enforces efficiency but also guides the RL algorithm to learn more generalizable communication strategies.}

\begin{table}[t]
% \setlength{\tabcolsep}{1.3mm}
\centering
\caption{\newtext{Scalability analysis with varying agent numbers. We report Accuracy (ACC) and average Token Cost (TC, k/task) on MMLU and GSM8K.}}
\label{tab:scaling}
\begin{tabular}{cccccc}
\toprule
\multirow{2.5}{*}{\textbf{Agents} ($N$)} & \multirow{2.5}{*}{\textbf{Budget} ($B$)} & \multicolumn{2}{c}{\textbf{MMLU}} & \multicolumn{2}{c}{\textbf{GSM8K}} \\
\cmidrule(lr){3-4} \cmidrule(lr){5-6}
 & & \textbf{ACC} & \textbf{TC} & \textbf{ACC} & \textbf{TC} \\
\midrule
3 & 6 & 66.6\% & 2.3 & 85.0\% & 2.0 \\
6 & 12 & 68.3\% & 11.4 & 86.4\% & 10.5 \\
6 & 18 & 68.5\% & 22.5 & \textbf{88.6\%} & 17.3 \\
9 & 18 & \textbf{70.3\%} & 17.6 & 88.5\% & 15.9 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{\newtext{Scalability Analysis}}

\newtext{We investigate RUMAD's scalability and robustness by evaluating its performance across varying agent group sizes ($N \in \{3, 6, 9\}$) and budgets ($B \in \{6, 12, 18\}$), with results summarized in Table~\ref{tab:scaling}. For a fair comparison, all hyperparameters except $B$ (e.g., learning rate, reward coefficients) are kept identical, demonstrating the model's robustness.
}

\newtext{First, the results demonstrate a clear positive correlation between the number of agents and reasoning performance. When scaling the agent count $N$ and communication budget $B$ proportionally ($N \in \{3, 6, 9\}$ while $B=2 \times N$), we observe consistent improvements in accuracy—rising from 66.6\% to 70.3\% on MMLU and from 85.0\% to 88.5\% on GSM8K. This trend indicates that RUMAD effectively harnesses the increased diversity and collective intelligence of larger groups. While the token cost naturally increases with the number of agents, the framework remains efficient relative to the performance gains.}

\newtext{A more compelling insight emerges when scaling the agent pool under a fixed budget. By increasing the agent count from $N=6$ to $N=9$ while keeping the budget at $B=18$, we observe a simultaneous increase in MMLU accuracy (68.5\% $\to$ 70.3\%) and a significant decrease in token cost for both benchmarks (e.g., 22.5k $\to$ 17.6k on MMLU). This counter-intuitive result strongly demonstrates the adaptability of our RL controller. Given a larger pool of agents, the controller learns to allocate its fixed budget more judiciously, selecting a more specialized or diverse subset of agents to participate. This intelligent selection leads to a more efficient path to the solution, enhancing performance while reducing redundant communication.}

\newtext{Across experiments upon different swarm, RUMAD shows stable ability to find a more efficient and accurate policy without requiring extensive hyperparameter tuning. It suggests RUMAD learns a generalizable communication policy rather than overfitting to a specific setup, highlighting its hyperparameter insensitivity and flexibility for deployment in diverse environments.}
