\section{Analysis of Computation Cost}
\label{appendix:computation_cost}

\subsection{Comparison of Time Consumption}
\begin{table*}[t]
\centering
\caption{Computational cost comparison across datasets between Graph-based methods. The best EM score of each dataset are marked in \textbf{bold}. ToG-3 achieves the best accuracy with efficient indexing and justified inference cost. }
\label{tab:computation_cost}
\scriptsize
\begin{tabular}{lccccccc}
\toprule
Dataset & Method & \multicolumn{3}{c}{Graph Statistics} & Indexing & Inference & Avg. \\
 & & Entities & Relations & Communities & Time (h) & Time (s/q) & EM \\
\midrule
\multirow{4}{*}{HotpotQA}
 & ToG-3 & 37,358 & 30,987 & 5,041 & 12.5 & 17.13 & \textbf{0.645} \\
 & HippoRAG-2 & 92,145 & 22,047 & - & 11.2 & 4.85 & 0.612 \\
 & GraphRAG & 94,376 & 73,265 & 10,981 & 15.8 & 8.91 & 0.337 \\
 & LightRAG & 94,578 & 76,157 & - & 12.1 & 6.54 & 0.308 \\
\midrule
\multirow{4}{*}{2WikiMultihopQA} 
 & ToG-3 & 19,311 & 21,077 & 3,417 & 8.2 & 15.07 & \textbf{0.527} \\
 & HippoRAG-2 & 48,251 & 11,540 & - & 7.6 & 4.12 & 0.491 \\
 & GraphRAG & 50,556 & 37,840 & 6,261 & 10.3 & 7.45 & 0.439 \\
 & LightRAG & 50,177 & 37,995 & - & 7.8 & 5.23 & 0.420 \\
\midrule
\multirow{4}{*}{Musique}
 & ToG-3 & 32,842 & 39,134 & 6,258 & 9.7 & 13.34 & \textbf{0.291} \\
 & HippoRAG-2 & 112,270 & 26,581 & - & 10.1 & 4.92 & 0.212 \\
 & GraphRAG & 106,042 & 83,139 & 9,407 & 13.2 & 9.37 & 0.109 \\
 & LightRAG & 94,621 & 75,923 & - & 10.3 & 7.12 & 0.082 \\
\midrule
\multirow{4}{*}{Average}
 & ToG-3 & 29,837 & 30,399 & 4,905 & 10.13 & 15.18 & \textbf{0.474} \\
 & HippoRAG-2 & 84,222 & 20,056 & - & 9.63 & 4.63 & 0.438 \\
 & GraphRAG & 83,658 & 64,748 & 8,883 & 13.10 & 8.58 & 0.295 \\
 & LightRAG & 79,792 & 63,358 & - & 10.06 & 6.30 & 0.270 \\
\bottomrule
\end{tabular}
\end{table*}
The Table~\ref{tab:computation_cost} reveal a consistent accuracy-efficiency trade-off across all datasets. 
We observed that during the indexing phase, GraphRAG required the longest processing time, averaging 13.10 hours. This is primarily due to its need to extract a large number of triplets and generate community summaries. In comparison, both ToG-3 and LightRAG showed similar indexing times, at 10.13 and 10.06 hours respectively. Although ToG-3 also involves community summary generation, it constructs the graph more efficiently by extracting fewer relational structures during graph initialization compared to both LightRAG and GraphRAG.
While LightRAG achieve faster inference times, they suffer from lower accuracy due to redundant graph elements or simpler retrieval mechanisms. 
While HippoRAG-2 achieves competitive performance and faster inference speed, it still falls short of the EM scores attained by ToG-3.
GraphRAG's expensive two-stage indexing yields suboptimal results despite longer processing times. 
ToG-3 demonstrates an effective balance: its efficient heterogeneous graph construction produces refined knowledge bases across all datasets, and while its multi-agent reasoning requires higher inference time, this cost is directly justified by its best performance on all benchmarks, making it ideal for quality-sensitive applications requiring reliable reasoning capabilities.
Note that the reranker model is relatively small and reduces the input length to the LLM, thus having minimal impact on inference time.
Detailed token consumption for graph construction and inference across different methods are provided in Appendix.\ref{appendix:token_consumption}.

\subsection{Comparison of Token Consumption}
\label{appendix:token_consumption}
Our proposed ToG-3 framework achieves a more favorable balance between inference efficiency and performance. As shown in Table~\ref{tab:token_consumption}, compared to GraphRAG, ToG-3 saves approximately 60\% of token consumption during the graph construction phase (an average of 5.03 vs. 12.82 million tokens), which benefits from the dynamic graph construction mechanism that avoids the overhead of pre-building large-scale static knowledge graphs. Although ToG-3's average inference token consumption per sample (72.1 tokens) is higher than that of GraphRAG (32.3 tokens) and LightRAG (23.1 tokens), this increased inference overhead is the necessary cost for achieving precise multi-hop reasoning—our multi-agent evolution mechanism effectively decomposes complex questions and focuses on critical evidence through deep iterative query and sub-graph evolution, ultimately translating into superior answer quality (as demonstrated by the performance gains in Table~\ref{tab:ablation_studies}). This design trade-off indicates that ToG-3 achieves higher overall efficiency and accuracy by shifting computational resources from the expensive pre-construction phase to the targeted reasoning phase. Note that, since LLM inference speed is comparable across methods, token consumption is directly proportional to the primary time overhead.

\begin{table*}[t]
\centering
\caption{Comparison of token consumption for graph construction and inference across different methods.M means Millions.}
\label{tab:token_consumption}
\begin{tabular}{lcc}
\toprule
\textbf{Method} & \textbf{Avg. Graph Construction Tokens} & \textbf{Avg. Inference Tokens per Sample} \\
\midrule
ToG-3 & 5.03M & 72.1 \\
GraphRAG & 12.82M & 32.3 \\
LightRAG & 4.92M & 23.1 \\
HippoRAG-2 & 5.01M & 20.6 \\
\bottomrule
\end{tabular}
\end{table*}
