\section{Experiment}
This section presents the experimental design and methodology employ to evaluate \toolname. We first describe the constructed datasets, followed by an introduction to the baseline approaches. Subsequently, we detail the performance metrics and experimental configuration utilized in our evaluation.

\subsection{Dataset}
\label{sec:dataset}
We construct a comprehensive dataset to evaluate \toolname, comprising six highly-rated GitHub projects, each featuring both Java and C\# implementations. Following the established methodology of Methods2Test~\cite{tufano2022methods2test}, we extract Java-C\# translation pairs that include corresponding test cases. All unit tests within each project are executed to ensure their functionality and correctness. Detailed statistics for each project are provided in Table~\ref{tab:dataset}.

\begin{table}[htbp]
  \centering
  \caption{The statistics of the constructed dataset}
  \resizebox{.65\linewidth}{!}{%
    \begin{tabular}{l|cc} 
    \toprule
    \textbf{Project} & \textbf{Star} & \makecell{\textbf{\# Focal Method}\\\textbf{(Java / C\#)}} \\ 
    \midrule
    \textbf{\href{https://github.com/apache/lucene}{lucene}} & 2.9k & 113/114 \\
    \textbf{\href{https://github.com/apache/poi}{poi}} & 2.0k & 229/291 \\ 
    \textbf{\href{https://github.com/eclipse-jgit/jgit}{jgit}} & 0.2k & 134/140 \\ 
    \textbf{\href{https://github.com/itext/itext-java}{itext}} & 2.1k & 67/35 \\ 
    \textbf{\href{https://github.com/quartz-scheduler/quartz}{quartz}} & 6.5k & 42/25 \\ 
    \textbf{\href{https://github.com/apache/rocketmq-clients}{rocketmq-clients}} & 0.4k & 42/50 \\ 
    \bottomrule
    \end{tabular}
  }
  \label{tab:dataset}%
\end{table}%

\subsection{Baselines}
To evaluate the effectiveness of \toolname, we selected UniTrans~\cite{yang2024exploring} and PLTranslation~\cite{pan2024lost} as comparison benchmarks. Both UniTrans and PLTranslation represent traditional LLM-based code translation approaches that utilize test cases to validate translated code and iteratively refine translations based on test feedback. Additionally, we include the No Agent approach as a baseline, wherein the LLM directly translates the source function without any iterative refinement process.

\subsection{Evaluation Metrics}
Consistent with previous research~\cite{yang2024exploring,pan2024lost,yin2024rectifier}, we employ compile rate and pass rate as evaluation metrics. A piece of code is considered compilable if it successfully passes the compiler's syntactic and semantic checks, and correct if it additionally passes all associated test cases. The compile rate and pass rate are formally defined as the proportion of all generated functions that are compilable and functionally correct, respectively.

\subsection{Experimental Settings}
We implemented \toolname using Python, leveraging the LangChain API to interface with the relevant models, including Llama 3.1 8B and 70B~\cite{grattafiori2024llama}, Qwen2.5 7B and 72B~\cite{yang2025qwen3}, GPT4o-mini~\cite{hurst2024gpt}, and DeepSeek V3~\cite{liu2024deepseek}. We adhere to established best practice guidelines in designing our prompts. For baseline comparisons, we adapt their prompts to ensure applicability to repository-aware translation scenarios and guarantee fair performance evaluation.