\section{Introduction}

As software systems continue to evolve in scale and complexity, repository-aware code translation has emerged as a critical enabler for legacy system modernization and cross-platform development. Despite substantial advances in code translation research, existing approaches exhibit fundamental limitations when applied to repository-aware scenarios. Early approaches such as rule-based systems~\cite{nguyen2013lexical,chen2018tree} struggled with complex syntactic structures and lacked the adaptability required for diverse programming contexts, while Recurrent Neural Networks (RNN)-based models~\cite{dong2016language,yin2017syntactic,yin2018tranx} demonstrated limited effectiveness in handling repository-aware context. Furthermore, prompt designs employed in existing methods~\cite{khan2024xcodeeval,macedo2024exploring,pan2024lost,yang2024exploring} are typically simplistic and static, failing to adapt dynamically to varying repository contexts.

Recent Large Language Model (LLM)-based approa-ches~\cite{lano2024using,nitin2024spectra,pan2308understanding,yin2024rectifier} have demonstrated substantial improvements in translation quality, yet they remain constrained by insufficient contextual understanding and limited adaptability to real-world repository scenarios. Most prior work has concentrated primarily on isolated functions or small code snippets, systematically overlooking the global dependencies and complex invocation relationships that characterize large-scale software repositories.

Traditional static analysis techniques~\cite{ou2024repository,wang2024repotransbench}, including call graphs and program dependency graphs, pose significant interpretation challenges for LLMs and frequently introduce redundant or irrelevant information, thereby constraining their practical effectiveness. Furthermore, prompt designs employed in existing methods~\cite{khan2024xcodeeval,macedo2024exploring,pan2024lost,yang2024exploring} are typically simplistic and static, failing to adapt dynamically to varying repository contexts and consequently yielding suboptimal translation outcomes. Error correction strategies predominantly rely on test case execution results without providing actionable guidance or comprehensive context for effective issue resolution~\cite{pan2024lost,yang2024exploring}.

These fundamental limitations underscore the critical need for more flexible, context-aware, and adaptive solutions specifically tailored for repository-aware code translation. To address these challenges, we propose \toolname, a novel multi-agent LLM framework for repository-aware code translation. \toolname systematically decomposes the complex repository-aware translation task into specialized subtasks: retrieving semantically similar functions, collecting relevant contextual information, and performing iterative code generation and refinement. Each subtask is handled by a dedicated agent with domain-specific expertise.

The RAG Agent employs advanced retrieval-augmented generation techniques to identify and retrieve functions from the repository that exhibit semantic similarity to the source function. The Context Agent autonomously invokes specialized tools to incrementally gather necessary contextual information, focusing on the most relevant components for effective code translation. The Refine Agent performs the actual translation process based on the source function, target function signature, and comprehensive information collected by the RAG and Context Agents. Additionally, it executes test cases to collect execution feedback, reflects systematically on the output to generate targeted suggestions for error correction, and strategically re-invokes tools to acquire context specifically required for effective error resolution.

To ensure comprehensive agent understanding of current tasks and workflows, we design a dynamic and adaptive prompting scheme. The prompt architecture incorporates both static and dynamic components strategically. The static components include essential elements such as Goals, Guidelines, and Examples, which clarify task objectives, establish fundamental principles, and demonstrate basic workflows. The dynamic components encompass Gathered Context, Input, and Last Command, enabling agents to adapt their tool invocation strategies based on specific inputs and previously collected contextual information.

To evaluate the effectiveness of our approach comprehensively, we constructed a dataset of hundreds of Java-C\# translation pairs from six popular open-source projects on GitHub and conducted extensive experiments to assess \toolname's performance on repository-aware code translation tasks. The experimental results demonstrate that \toolname significantly outperforms baseline approaches in both compile and pass rates. Specifically, the average compile rate improved substantially from 26.07\%–30.47\% to 55.34\%, while the pass rate increased from 18.59\%–28.16\% to 45.84\%. Compared to baseline approaches, the functions successfully translated by \toolname almost completely encompass those translated by the three baseline methods while additionally achieving 90 more successful translations. We also conducted detailed analysis of error types for functions that \toolname failed to translate and found that most errors were compilation-related.

Our main contributions are summarized as follows:

\textbf{A. Multi-Agent Repository-Aware Translation Framework:} \toolname introduces a novel multi-agent LLM framework that systematically decomposes repository-aware code translation into specialized subtasks, enabling more accurate and context-aware translations.

\textbf{B. Dynamic Context Retrieval and Adaptive Prompting:} Our approach leverages advanced retrieval-augmented generation and dynamic prompt construction techniques, allowing agents to efficiently gather relevant context and adapt effectively to complex repository scenarios.

\textbf{C. Comprehensive Empirical Evaluation:} We conduct extensive experiments on real-world Java-C\# repositories, demonstrating that \toolname significantly outperforms state-of-the-art baseline approaches in both compile and pass rates.