\section{Conclusion}
\label{sec:conclusion}

We have proposed \OurApproach{}, a novel approach for complex KGQA using message passing, which sets the new state-of-the-art results on the LC-QuAD benchmark for complex question answering.
We have shown that \OurApproach{} is scalable and can be successfully applied to very large KGs, such as DBpedia, which is one of the biggest cross-domain KGs.
\OurApproach{} does not require supervision in the answer inference phase, which helps to avoid overfitting and to discover correct answers missing from the benchmark due to the limitations of its construction.
Moreover, the answer inference process can be explained by the extracted subgraph and the confidence score distribution.
\OurApproach{} requires only a handful of hyper-parameters to model confidence thresholds in order to stepwise filter partial results and trade off recall for precision.

% what we found;
\OurApproach{} is built on a basic assumption of considering edges as undirected in the graph, which proved reasonable and effective in our experiments.
The error analysis revealed that, in fact, symmetric edges were often missing in the KG, i.e., the decision on the order of entities in KG triples is made arbitrarily and is not duplicated in the reverse order.
However, there is also a (small) subset of relations, e.g., hierarchy relations, for which relation direction is essential.
% \todo[inline]{AP: IMHO, this next sentence could be thin ice, and while it is ok to mention it before in the evaluation, I wouldn't repeat/stress it in the conclusions, since this is essentially arguing that everything can be learned if enough data is available, sure, but in fact this directionality is maybe something where you rule-based heuristics in the parsing would actually work better.}
% We argue that these relations are underrepresented in the existing benchmark which will cause supervised approaches trained to detect relation direction to overfit the training data.

% what are the implications;
% \if0
Question answering over KGs is hard due to (1)~ambiguities stemming from question interpretation, (2)~inconsistencies in knowledge graphs, and (3)~challenges in constructing a reliable benchmark, which motivate the development of robust methods able to cope with uncertainties and also provide assistance to end-users in interpreting the provenance and confidence of the answers.
% we overcome the query building and showed very powerful maximize optimise for recall tune precision prune based on modeling query structure additional constraints on the walk 
% \fi

% what are the limitation;
\OurApproach{} is not without limitations. 
It is designed to handle questions where the answer is a subset of entities or an aggregate based on this subset, e.g., questions for which the expected answer is a subset of properties in the graph, are currently out of scope.
An important next step is to use \OurApproach{} to improve the recall of the benchmark dataset by complementing the answer set with missing answers derived from relaxing the dataset assumptions.
Recognizing relation directionality is an important direction for future work, which requires extending existing benchmark datasets and the addition of more cases where an explicit order is required to retrieve correct answers.
Another direction is to improve predicate matching, which is the weakest component of the proposed approach as identified in our ablation study.
Finally, unsupervised message passing can be adopted for other tasks that require uncertain reasoning on KGs, such as knowledge base completion, text entailment, summarization, and dialogue response generation.
% improve relation detection is the next bottleneck consider all increase recall implicit no lexical match
