\section{Dataset Details}
\label{app:datasets}

We evaluate our proposed framework on seven datasets spanning mathematical reasoning, general knowledge, expert knowledge reasoning, and factual correctness.

\subsection{Mathematical Reasoning Tasks}
\begin{itemize}
    \item \textbf{GSM8K}~ \cite{cobbe2021gsm8k}: A benchmark consisting of high-quality, linguistically diverse grade school math word problems. We randomly sampled 300 questions from the test set for evaluation. This dataset serves as a baseline to assess the model's capability in basic multi-step reasoning.
    \item \textbf{MATH500}~ \cite{lightman2023lets}: A rigorous subset of the MATH dataset, containing 500 challenging problems uniformly sampled across seven subjects. Unlike GSM8K, MATH500 requires complex problem-solving skills and domain-specific knowledge.
    \item \textbf{AIME 2024-2025}~ \cite{aime2024,aime2025}: The American Invitational Mathematics Examination (AIME) represents the pinnacle of high-school mathematical competitions. We utilize problems from the 2024 and 2025 exams to test the model's performance on extremely hard, out-of-distribution reasoning tasks.
\end{itemize}

\subsection{General Knowledge Tasks}
\begin{itemize}
    \item \textbf{MMLU}~ \cite{hendrycks2020measuring}: The Massive Multitask Language Understanding benchmark covers 57 subjects across STEM, the humanities, and social sciences. We randomly sampled 300 questions to assess the breadth of the model's world knowledge.
\end{itemize}

\subsection{Expert Knowledge Reasoning Tasks}
\begin{itemize}
    \item \textbf{GPQA}~\cite{rein2023gpqa}: The Graduate-Level Google-Proof Q\&A benchmark is a challenging multiple-choice dataset designed to evaluate expert-level scientific knowledge and reasoning. Questions are authored by domain experts in biology, physics, and chemistry, and are specifically designed to be difficult even for those with internet access (hence ``Google-proof''). We use the GPQA Main subset, which contains 448 questions spanning biology, physics, and chemistry. Standard accuracy is used as the evaluation metric.
\end{itemize}

\subsection{Factual Correctness Tasks}
\begin{itemize}
    \item \textbf{Biography}~ \cite{du2023improving}: We randomly selected 100 figures to evaluate hallucination mitigation. The evaluation protocol follows the methodology proposed in the SoM paper.
\paragraph{Special Evaluation details}
    For each figure, an independent LLM acts as a \textbf{judge} to compare the generated biography against reference facts claim-by-claim. For each fact, the judge determines whether the generated biography is consistent with the fact and assigns one of three labels:
    \begin{itemize}
        \item \textbf{yes}: The fact is explicitly stated or clearly implied.
        \item \textbf{no}: The fact is missing or contradicts the biography.
        \item \textbf{uncertain}: The biography is too vague to determine consistency.
    \end{itemize}

    The metric calculates accuracy based only on facts labeled as ``yes'' or ``no'', ignoring ``uncertain'' cases:
    \begin{equation}
        \text{Accuracy}_{\text{Yes/No}} = \frac{N_{\text{yes}}}{N_{\text{yes}} + N_{\text{no}}}
    \end{equation}
    This metric reflects the model's accuracy when it provides explicit factual statements.
\paragraph{Component-Based Agent Allocation for Biography Generation}

For the Biography benchmark, we adopt a component-based agent allocation strategy,
denoted as allocate\_component, to structure multi-agent generation.
Instead of asking agents to generate a full biography independently, we first decompose
a biography into a small number of semantically distinct components (depends on number of agents),
such as core research focus, major contributions, and professional roles.

Each agent is assigned exactly one component and is instructed to generate content
only for that component.
Generation proceeds in multiple rounds: agents first produce initial component drafts,
and then refine their own components by referencing others for context,
while being prohibited from introducing new facts outside their responsibilities.

After all rounds, the generated components are merged into a single biography through
a lightweight integration step that removes duplication and ensures coherence,
without adding any new information.
\end{itemize}
