\section{Baseline Implementations}
\label{app:baselines}

To demonstrate the effectiveness of DynaDebate, we compare it against a comprehensive set of baselines.
\vspace{-4pt}
\subsection{Single-Agent Strategies}
\begin{itemize}
    \item \textbf{Chain-of-Thought (CoT)}~\cite{wei2022chain}: The standard prompting approach where the model is instructed to ``think step by step'' before generating the final answer.
    \item \textbf{CoT-SC (Self-Consistency)}~\cite{wang2022self}: An ensemble strategy that samples $k$ distinct reasoning paths and determines the final answer by a majority vote.
    \item \textbf{Self-Refine}~\cite{madaan2023self}: An iterative feedback mechanism where a single agent generates an initial output, critiques its own reasoning, and then refines the answer based on self-generated feedback.
\end{itemize}

\subsection{Multi-Agent Frameworks}
\begin{itemize}
    \item \textbf{MAD (Multi-Agent Debate)}~\cite{liang2023encouraging}: This method is implemented by inducing divergent results through participants with different personas: an Affirmative participant (``Angel'') and a Negative participant (``Devil'') provide answers to a Judge participant. The Judge is responsible for managing the process and deriving the final solution. The Judge possesses additional autonomy and can terminate the debate early if satisfied with the answer.
    \item \textbf{SoM (Society of Mind)}~\cite{du2023improving}: This framework proposes a multi-agent decision (MAD) approach where multiple agents achieve efficient collaboration by passing answers to one another. The method allows for the summarization of answers before adding them to the history record, enabling agents to call upon this condensed information in subsequent rounds.
    \item \textbf{DMAD}~\cite{liu2025breaking}: \textbf{Diversified Multi-Agent Debate (DMAD)} is a novel and robust framework designed to guide agents in employing diverse reasoning methods. It aims to break thinking stereotypes and patterns, thereby enhancing overall reasoning performance.
\end{itemize}
