\begin{abstract}
Multi-turn, multi-agent LLM game evaluations often exhibit substantial run-to-run variance. In long-horizon interactions, small early deviations compound across turns and are amplified by multi-agent coupling. This biases win rate estimates and makes rankings unreliable across repeated tournaments. Prompt choice worsens this further by producing different effective policies. We address both instability and underperformance with \textbf{\NAME{}} (\textbf{Me}mory-augmented \textbf{MO}del context optimization), a self-play framework that optimizes inference-time context by coupling \textbf{retention} and \textbf{exploration}. Retention maintains a persistent memory bank that stores structured insights from self-play trajectories and injects them as priors during later play. Exploration runs tournament-style prompt evolution with uncertainty-aware selection via \textsc{TrueSkill}, and uses prioritized replay to revisit rare and decisive states. Across five text-based games, \NAME{} raises mean win rate from \textbf{25.1\%} to \textbf{49.5\%} for GPT-4o-mini and from \textbf{20.9\%} to \textbf{44.3\%} for Qwen-2.5-7B-Instruct, using $2,000$ self-play games per task. Run-to-run variance also drops, giving more stable rankings across prompt variations. These results suggest that multi-agent LLM game performance and robustness have substantial room for improvement through context optimization. \NAME{} achieves the largest gains in negotiation and imperfect-information games, while RL remains more effective in perfect-information settings.
\end{abstract}

