\paragraph{Two-Player Multi-Turn Markov Game.}
We formalize the setting as a two-player, turn-based, zero-sum, partially observable Markov game $(S, A, O, P, \Omega, \rho)$, where $S$ is the state space, $A$ is the action space where each action is a complete model response, $O$ is the observation space, $P{:}\, S \times A \to \Delta(S)$ governs transitions, $\Omega{:}\, S \to O$ maps states to partial observations, and $\rho{:}\, S_{\text{term}} \to \{-1, 0, 1\}$ assigns win/draw/loss at terminal states. Players alternate turns; a trajectory $\tau = (s_0, a_0, \ldots, s_H)$ terminates after $H$ steps with outcome $r_0(\tau) = \rho(s_H)$ for Player~0.


\paragraph{Prompt and Memory as Game Context.}
We define \emph{context} as all information that conditions the model before and during play. Let $c=(q,M)$, where $q$ is the instruction prompt, including role and system text fixed at game start,
and $M$ is the memory injected at inference time without weight updates. $M$ consists of structured, reusable insights distilled from past self-play trajectories.
In \NAME{}, $M$ is drawn from a persistent memory bank $\mathcal{B}_{\text{mem}}$ that accumulates across
optimization iterations, and each game instance may use a subsampled memory $M\subseteq \mathcal{B}_{\text{mem}}$.

\paragraph{Full-Context Evaluation.}
\label{RSE}
We evaluate each method over $n$ independent runs of its full context-optimization pipeline, each producing a final context $c^*$ that is evaluated on a fixed game suite $\mathcal{G}$. For each game, we play multiple rounds against a fixed opponent pool, swapping first-move order to reduce bias (opponents use the reference contexts in Appx.~\ref{appendix: basepromptexample}). Let $x_r$ denote the run-level performance, defined as the mean win rate averaged over all games, opponents, and rounds. We report the mean performance across runs, $\mathrm{mean}(x_1,\ldots,x_n)$, together with the relative standard error $\mathrm{RSE}(\%) = 100 \times \frac{\mathrm{std}(x_1,\ldots,x_n)}{\mathrm{mean}(x_1,\ldots,x_n)\sqrt{n}}$, where lower RSE indicates greater run-to-run stability.
