\section{Introduction}\label{sec:intro}

Multi-agent LLM systems have risen as a powerful paradigm, exemplified by frameworks such as CAMEL, AutoGen, and MetaGPT \cite{autogen, metagpt, camel}, demonstrating promising performance in crucial domains, including coding, mathematical problem-solving, and collaborative decision-making.

Despite their advancements, the performance of multi-agent LLM systems is highly sensitive to adversarial and low-performing agents. 
Particularly, a subset of compromised team members with adversarial behavior can corrupt the system’s collective output. The susceptibility of LLM agents to persuasive inputs further amplifies this risk, potentially leading to incorrect group consensus. 
Although prior studies have highlighted this vulnerability \cite{psysafe, multiagent-debate-attack, MALLM-survey-2}, existing solutions are predominantly limited to specific, predefined architectures. These approaches and the related work are further discussed in Appendix~\ref{app:related}.

To the best of our knowledge, the literature lacks a general framework that enables users to design {\em robust multi-agent systems resilient to adversarial influence} while minimizing the impact of such attacks without the need to eliminate an agent.

In this paper, we fill this research gap by proposing an {\em adversary-resistant} multi-agent LLM system based on {\em credibility scoring.}

Specifically, we model the query-answering process as an iterative cooperative game, where a team of agents is formed to find the answer to a given query. The team members may have different roles and communicate based on the team's topology to finalize their individual answers, which are then aggregated into the system's answer to the query.

Instead of equally trusting all agents, our system follows a credibility-score aware aggregation strategy that weighs each agent's individual output proportional to their trustworthiness.
The credibility scores reflect the collective performance of each agent in answering the previous queries and are learned on the fly during the lifetime of the system.

For each query, the team receives a reward (or gets penalized) based on the quality of the generated output.
In order to fairly distribute the reward among the team members, we introduce the {\em contribution scores}, with larger values reflecting a larger impact of an agent in the generated output.
We propose two approaches based on Shapley values and LLM-as-Judge for measuring the contribution scores.
At the end of each round, the credibility scores are updated by distributing the reward to the agents proportional to their contribution. 

Our system has a unique ability to tolerate adversary-majority settings, a more extreme case than the typically considered settings that assume the adversaries are in the minority. We emphasize a critical yet under-explored challenge: when adversaries constitute more than 50\% of the agents, honest agents must either exert disproportionate influence or possess superior capabilities to avoid being outvoted or manipulated. 

Our approach is applicable across different team structures and integration mechanisms for existing methods. It empowers users to 
minimize the impact of low-performing and malicious agents within the teams with various formations and communications topologies. By leveraging this adaptability, our method enhances the resilience of multi-agent systems, ensuring more robust and reliable cooperation of the agents. 
We conduct comprehensive experiments on various tasks, benchmark datasets, and settings to evaluate our system.
Our experiment results verify the effectiveness of credibility scoring, 
demonstrating the ability of our system in detecting and minimizing the effect of the adversary agents, even for the adversary-majority settings.
\vspace{-0.5mm}
\paragraph{Paper Organization:} 
We first introduce the concepts and provide an overview of our system in Section~\ref{sec:overview}. Next in Section~\ref{sec:team}, we discuss the composition details of a team of agents, followed by the explanation of the credibility-score aware aggregation of the team outputs in Section~\ref{sec:agg}. 
We then conclude our technical discussions in Section~\ref{sec:tech-details} by explaining how the credibility scores are gradually learned in our system.
The experimental evaluations are provided in Section~\ref{sec:experiments}, followed by the concluding remarks and a discussion of our system's limitations in Sections~\ref{sec:conclusion} and~\ref{sec:limitations}.