\section{Limitations}
\label{sec:limitations}

Our study advances multi-agent LLM coordination through Credibility Scores (CrS), yet several important limitations must be acknowledged.

\paragraph{Limited Evaluation Domains.}
Our evaluation focused exclusively on four benchmarks: MMLU, GSM8K, MATH, and ResearchQA. While these datasets collectively assess reasoning, coding, and factual question-answering capabilities, they do not encompass dialogue interactions, vision-language tasks, or real-time communication scenarios. Consequently, the generalizability of our findings to other contexts is limited.

\paragraph{Judge Dependence.}
The effectiveness of the CrS mechanism critically relies on the capabilities of the evaluator (judge). We observed significant performance degradation when employing weaker judges (e.g., LLaMA3.2 compared to GPT-4oMini). In such cases, Contribution Scores become noisy and lead to reduced accuracy (see Section~\ref{sec:exp:judge}). Future research could mitigate this sensitivity by developing self-calibrating judges or employing ensembles of judges.

\paragraph{Synthetic Adversaries.}
Our adversarial agents were explicitly instructed to exhibit adversarial behaviors and typically became easier to influence after multiple rounds of interaction. However, real-world adversaries, whether human actors or LLMs specifically fine-tuned for deceptive behaviors, may exhibit more sophisticated and unpredictable patterns. Such advanced adversaries could potentially evade detection or mitigation through CrS.

\paragraph{Computational and Cost Overheads.}
The computation of Shapley-like CrS scales quadratically with the number of agents involved, posing significant computational challenges. Each communication round necessitates two API calls to an external judge—one to evaluate the group's final response and another to review the interaction logs and compute Contribution Scores. These repeated calls incur substantial financial costs, limiting our ability to experiment with more powerful judges such as GPT-4o. This constraint particularly impacts tasks like HumanEval, where judge proficiency significantly influences reward calculation accuracy. Additionally, as the number of agents and communication links increases, interaction logs lengthen, triggering token-compression mechanisms. Such compression introduces additional latency and may result in the loss of critical context, further exacerbating evaluation inaccuracies. Exploring cost-effective approximations or more efficient evaluation techniques represents valuable avenues for future research.