% \eat{\section{What Is The Story?}


% Given a collection of off-the-shelf Large Language Model (LLM) agents, consider the challenge of selecting a subset of agents to form a team capable of completing a specific task. Your knowledge of these models is limited to their general performance metrics, which may not accurately reflect how well individual agents collaborate with others. Furthermore, there are no predefined guidelines for designing the team architecture.

% When constructing such an architecture, users typically seek both high performance and reliability. An effective architecture should not only excel in task performance but also minimize adversarial effects, especially in scenarios where some agents may be compromised or behave maliciously.

% To address this challenge, we propose a method that empowers users to make informed decisions when selecting standard agents and designing their communication strategies, facilitating the development of robust and efficient teams of LLM agents.

% Through experiments, we demonstrate that our method enhances the performance of previously studied architectures and state-of-the-art approaches.
% }

\section{Team of Agents}\label{sec:team}

In this section, we explain the key components in the formation of a team of agents, including the topology and the gent roles.
\vspace{-0.5mm}
\paragraph{Agent Roles.}
In a multi-agent LLM system all team members may be assigned to the same task~\cite{DyLAN, div-think-llms}, or they may have different roles aligned with their specific expertise or subtasks \cite{CoA, MA-LLM-topo}. 
Another important consideration is the agents' adaptability: whether they can learn, adapt, or modify their strategies over time by updating internal parameters. 
These aspects have been explored in varying degrees across existing research. For instance, Alfonso et al.~\cite{multiagent-debate-attack} demonstrated that models could be influenced to alter their behavior in ways that ultimately degrade overall system performance. Such interference may occur through direct manipulation of agents' individual contributions or deceptive communication tactics \cite{multiagent-debate-attack}. Further details about incentives and adversarial behavior of LLM agents is discussed in Appendix~\ref{app:behavior}.

Therefore, establishing robust mechanisms to mitigate adversarial threats is essential to maintaining the integrity and reliability of multi-agent collaborations.
A major benefit of our systems is the {\bf robustness against adversarial agents}.
Specifically, allocating the agents with credibility scores, our system gradually penalizes the agents with adversarial behaviors (see Section~\ref{sec:tech-details}).
In Section~\ref{sec:experiments}, we demonstrate that our system can tolerate {\em even more than half} of the agents being adversary.


\paragraph{Communication Structure (Topology).}
The topology of a multi-agent system defines the arrangement and interconnections among agents, effectively determining which agents can directly communicate. This structure can be conceptualized as a graph, where each node represents an agent, and each edge represents a direct communication link between two agents. 
Previous research has investigated various topological arrangements from (a) {\em no connection} to (b) {\em fully-connected} structures, including (c) {\em chain}, (d) {\em ring}, (e) {\em hierarchical}, and (f) {\em randomly-connected} networks~\cite{MoA, resilience, MA-LLM-topo, DyLAN}. 
The choice of topology significantly impacts both scalability and robustness of the multi-agent system. For example, fully connected topologies facilitate rapid consensus due to their direct communication paths, yet they exhibit vulnerability when faced with adversarial agents or limited network resources~\cite{multiagent-debate-attack}. Conversely, sparse topologies, such as ring or chain structures, lower communication overhead but might be more susceptible to localized adversarial influence, potentially compromising subsets of agents \cite{multi-agent-sys}. 
% Therefore, selecting an appropriate topology requires carefully balancing efficiency, scalability, and resistance to adversarial conditions.

Our system is flexible to the choice of communication structures:
we assume each agent first drafts a candidate solution (\emph{local inference}). Then, during the 
{\em peer interaction} phase, the agents optionally exchange information according to the \emph{communication graph} prescribed by the topology.




