\begin{abstract}
    Long-horizon personalization requires dialogue assistants to retrieve user-specific facts from extended interaction histories.
    In practice, many relevant facts often have low semanticsimilarity to the query under dense retrieval.
    Standard Retrieval-Augmented Generation (RAG) and GraphRAG systems are still largely retrospective: they rely on embedding similarity to the query or on fixed graph traversals, so they often miss facts that matter for the user's needs but lie far from the query in embedding space.
    Inspired by \emph{prospection}, the human ability to use imagined futures as cues for recall, we introduce \textbf{Prospection-Guided Retrieval (PGR)}, which decouples retrieval from how memories are stored.
    Given a user query, PGR first expands the goal into a short Tree-of-Thought (ToT) or linear chain of plausible next steps, and uses these steps as retrieval probes rather than relying on the original query alone.
    The facts retrieved by these probes are then used to personalize the next round of prospection, enabling PGR to uncover additional memories that become relevant only after the simulation is grounded in the user's history.
    We also introduce \textbf{MemoryQuest}, a challenging multi-session benchmark in which each query is annotated with $3$--$5$ dated reference facts subject to a low query--reference similarity constraint.
    Across $1{,}625$ queries spanning $185$ user profiles from 3 publicly available datasets, PGR-TOT substantially improves retrieval, including nearly 3x recall on MemoryQuest over the strongest baseline.
    In pairwise LLM-as-judge comparisons against baselines, PGR-generated responses are preferred on $89$--$98\%$ of queries, with blinded human annotations on held-out subsets showing the same trend.
    Overall, the results demonstrate that explicit prospection yields large gains in long-horizon retrieval and response quality relative to similarity-only baselines.
\end{abstract}