\section{Benchmark Dataset: MemoryQuest}
\label{sec:dataset}

The need for \textbf{MemoryQuest} stems from the complexity of real-world assistant usage, where interactions span months and disparate tasks like travel booking or event planning. In these settings, a single query often depends on a ``thread'' of chronologically consistent facts that evade simple semantic search. Most existing benchmarks are limited to single sessions or lack logical evolution over time. Furthermore, retrieval tasks are often ``semantically easy,'' allowing standard RAG to succeed via keyword overlap. \textbf{MemoryQuest} provides a necessary stress-test for long-term memory, requiring the synthesis of multiple, semantically distant memories buried across a multi-domain history.


\subsection{Gap Analysis and Comparison}
Prior datasets target complementary aspects of long-term memory but lack the combination of temporal grounding and semantic difficulty required for proactive retrieval:

\squishlist
    \item \textbf{Single Session or Temporal Inconsistency:} \emph{LongMemEval}~\cite{wu2024longmemevalbenchmarkingchatassistants} and \emph{MSC}~\cite{xu-etal-2022-beyond} focus on evidence within continuous logs. Unlike \emph{LoCoMo}~\cite{maharana2024evaluating}, which uses event graphs, or \emph{MSC}, which lacks explicit dates, \emph{MemoryQuest} provide a dated, multi-session history requiring retrieval of $3$--$5$ distinct memories spread across disparate task domains.
    \item \textbf{Semantic Retrieval Bias:} In \emph{PersonaMem}~\cite{jiang2025personamem} and \emph{ImplexConv}~\cite{li2025implexconv}, evidence is often semantically similar to the query. \emph{MemoryQuest} enforces a \textbf{similarity bottleneck}, pairing queries with required facts filtered for low semantic overlap.
    \item \textbf{Lack of Fine-Grained Evidence:} \emph{MemoryQuest} provides dated, atomic facts. This enables precise, independent evaluation of both the \textbf{retrieval policy} and the \textbf{generation model}.
\squishend


\subsection{Dataset Construction Pipeline}
MemoryQuest is built on \emph{PersonaLens} profiles~\cite{zhao-etal-2025-personalens}, providing demographics across 20 domains. We generate \emph{in-situ} queries involving planning and follow-through rather than standalone factoid prompts via a three-step pipeline:

\paragraph{Step 1: Query Generation.} 
An LLM generates candidate queries, each including a query date, reasoning, and 3--5 \textbf{required references}. We retain candidates with average query--reference cosine similarity $\gamma \le 0.3$ and keep at most $n_q \le 15$ queries per user, prioritizing those with the lowest similarity scores.

\paragraph{Step 2: Timeline Synthesis.} 
For each query, an LLM builds a chronologically ascending timeline of 5--10 events, starting shortly before the earliest required-reference date. Each required reference is embedded in exactly one timeline event, while remaining events are persona-grounded \textbf{filler} chats for a realistic multi-domain conversation history.

\paragraph{Step 3: Dialogue Expansion.} 
Each timeline event is expanded into a multi-turn conversation (5--30 turns) via an LLM, conditioned on user demographics and domain summaries for logical continuity. A separate memory-extraction step (Section~\ref{sec:pgr-memory}) converts these logs into the structured fact store used at test time.

\paragraph{Scope and Generalizability.}
MemoryQuest is intentionally designed as a challenging stress-test for semantically indirect long-term personalization. The $\gamma \le 0.3$ filter selects queries whose required references have low embedding similarity to the query, creating a setting where direct single-query retrieval is expected to be challenging. We therefore do not present MemoryQuest as representative of all retrieval workloads; rather, it targets an important subset of assistant interactions: under-specified requests that require recovering temporally distributed, personalized evidence from long histories. To assess whether PGR's benefits extend beyond this constructed setting, we also evaluate on ImplexConv \cite{li2025implexconv} and PersonaMem \cite{jiang2025personamem}, two independently published benchmarks with different construction procedures and task objectives, where PGR improves retrieval recall over all baselines and achieves strong response-level win rates.
