\section{Method}
\label{sec:method}

We introduce \textbf{\system{}}, a training-free \underline{Con}versational \underline{Sens}or F\underline{us}ion framework that performs multimodal sensing via structured, role-specialized multi-agent collaboration (Figure~\ref{fig:overview}). \system{} comprises four defined agent roles: (i)~\textbf{\textit{modality agents}}, each specialized to a single sensor modality and responsible for producing task-relevant semantic interpretations; (ii)~a \textbf{\textit{semantic fusion agent}} that integrates modality-agent outputs into a holistic prediction by reasoning over cross-modal semantic evidence; (iii)~a \textbf{\textit{statistical fusion agent}} that reasons over a fixed prediction anchored to a majority-vote consensus of modality-level predictions, providing robustness against prior-driven knowledge bias; and (iv)~a \textbf{\textit{hybrid fusion agent}} that arbitrates between the outputs of the semantic and statistical fusion agents. By explicitly balancing knowledge-grounded and consensus-grounded reasonings, the hybrid fusion agent produces the final prediction. 

\subsection{Modality Agents}
\label{sec:method_modality_agents}

\system{} instantiates a set of \textbf{modality agents} $\{A^{\text{mod}}_1, A^{\text{mod}}_2, \ldots, A^{\text{mod}}_N\}$, where each agent $A^{\text{mod}}_i$ is assigned to a single sensor modality $m_i$ and is responsible for producing a task-relevant semantic interpretation of that modality under the query $T$. Each agent receives a modality-conditioned prompt $(m_i, T)$ and outputs (i)~a modality-specific prediction $\hat{y}_i \in \mathcal{Y}$ and (ii)~a rationale $r_i$ that explicitly grounds the prediction in evidence. This modularization isolates modality-level reasoning, reducing cross-modal interference within the prompt and preserving complementary evidence that may otherwise be diluted under joint prompting.

\subsection{Fusion Agents}
\label{sec:method_fusion_agents}

To reach a final prediction, \system{} aggregates the outputs of the modality agents, $\{(\hat{y}_i, r_i)\}_{i=1}^N$. As discussed in Section~\ref{sec:motivation}, semantic and statistical aggregation paradigms exhibit complementary strengths and distinct failure modes. To balance these trade-offs, we define a \emph{hybrid fusion} approach comprising three fusion agents.

\noindent \textbf{Semantic Fusion Agent ($A^{\text{fuse}}_{\text{sem}}$).} It implements a \textit{knowledge-grounded aggregation} that synthesizes semantic evidence across modality-agent outputs 
$\{(\hat{y}_1, r_1), \ldots, (\hat{y}_N, r_N)\}$ using the LLM's prior knowledge.
It represents a semantic inductive bias that emphasizes cross-modal coherence, causal plausibility, and high-level domain knowledge when forming an aggregated hypothesis.

\noindent  \textbf{Statistical Fusion Agent ($A^{\text{fuse}}_{\text{stat}}$).} It implements a \textit{consensus-grounded aggregation} by anchoring its reasoning to a fixed majority-voted prediction $\hat{y}_{\text{vote}} = \arg\max_{c \in \mathcal{Y}} \sum_{i=1}^{N} \mathbf{1}[\hat{y}_i = c]$. Rather than generating a new prediction, it produces a rationale that justifies this statistical consensus, representing a complementary inductive bias that prioritizes robustness to individual agent errors and suppresses prior-driven knowledge bias. In our framework, majority voting is used as a simple representative form of agreement-based aggregation.

\noindent  \textbf{Hybrid Fusion Agent ($A^{\text{fuse}}_{\text{hyb}}$).} We formalize hybrid fusion as an instance-wise arbitration between two complementary inductive biases: $(\hat{y}_{\text{sem}}, r_{\text{sem}}) = A^{\text{fuse}}_{\text{sem}}(\{(\hat{y}_i, r_i)\}_{i=1}^N)$ and $(\hat{y}_{\text{stat}}, r_{\text{stat}}) = A^{\text{fuse}}_{\text{stat}}(\{(\hat{y}_i, r_i)\}_{i=1}^N)$. The hybrid fusion agent $A^{\text{fuse}}_{\text{hyb}}$ performs instance-wise arbitration: $(\hat{y}, r) = A^{\text{fuse}}_{\text{hyb}}\big((\hat{y}_{\text{sem}}, r_{\text{sem}}), (\hat{y}_{\text{stat}}, r_{\text{stat}})\big)$ which selects between two complementary aggregation hypotheses grounded in (i) semantic reasoning and (ii) statistical consensus as a \textit{coordinator} role.

Unlike prior methods that rely only on knowledge-grounded reasoning, the hybrid fusion agent is additionally exposed to statistically grounded reasoning. This design introduces a complementary, data-driven perspective into the decision process, allowing \system{} to maintain robustness under sensor failure via semantic coherence, while simultaneously mitigating knowledge bias by taking account of statistical stability. %Full prompt templates are provided in Appendix~\ref{sec:appendix_prompts}.
