\section{Dataset Details}
\label{sec:appendix_dataset}

\input{tables/datasets}
\input{tables/features}

\noindent \textbf{Overview.} Table~\ref{tab:datasets} summarizes the tasks and sensor modalities for each dataset. The datasets include five to eleven modalities per task, covering 12 distinct sensor types collected from diverse devices and body locations, demonstrating broad diversity in sensing configurations.

\noindent \textbf{Data Preprocessing.} Following the protocols established in the original publications~\citep{wesad, sleepedf, actionsense, mmfit, pamap2}, raw sensor data were segmented using sliding windows. To prevent data leakage between few-shot examples and target samples, we employed non-overlapping windows (where step size equals window size). For WESAD, we focused on three affective states: baseline, stress, and amusement. For SleepEDF, we utilized the standard sleep stages (W, N1, N2, N3, and REM), excluding infrequent classes. In ActionSense, we grouped the labels into five high-level categories (spreading, peeling/slicing, jar operations, wiping, and tableware tasks) following the categorization in \citet{actionsense}; ``pouring'' was excluded due to insufficient samples. We utilized data from both the left and right armbands. For MMFit, we excluded data from the left smartphone due to sample sparsity. For PAMAP2, we selected 12 of the 18 original activity classes (e.g., walking, cycling, ironing) that provided sufficient sample density.

\input{tables/round0_results}

\noindent \textbf{Feature Extraction.} Features were extracted according to dataset-specific guidelines or established signal processing methods~\citep{wesad, sleepedf_features}, as summarized in Table~\ref{tab:features}. To evaluate system robustness against sensor failure, we simulated 10\%, 30\%, and 50\% modality dropout rates by randomly masking sensor streams with zeros prior to feature extraction. Detailed task descriptions, class definitions, and feature extraction procedures were stored as metadata and dynamically parsed into the LLM prompts to provide environmental context.

\noindent \textbf{Data Split.} We split each dataset into an example set (for 1-shot in-context learning) and a test set to prevent data leakage. We adopt a within-subject split strategy, assuming each user provides a single data instance per class with minimal effort. Sensor data such as EEG exhibit substantial inter-subject domain shift~\citep{eegdomainshift, domainshift}, which even remains an open challenge in the sensing community. Since LLMs are highly sensitive to in-context examples, cross-subject examples can incur significant performance variance. As our primary goal is to analyze \textit{multimodal fusion behavior} under controlled conditions, we adopt within-subject calibration to isolate fusion effects from confounding domain-shift factors.

\noindent \textbf{Data Subsampling.} Due to the high token cost of processing heavy sensor feature sequences with multiple LLMs (\texttt{gpt-oss-20B}, \texttt{gpt-oss-120B}, \texttt{Llama-3.1-8B-Instruct}, and \texttt{Llama-4-Scout-17B-16E}) and multi-agent baselines that require iterative debate rounds, we evaluate \system{} on balanced dataset subsets. We sample 50 instances per class for WESAD, SleepEDF, and ActionSense (datasets with $<$10 classes), and 30 instances per class for MMFit and PAMAP2 (datasets with $\geq$10 classes), resulting in test sets of 150–360 samples per task. Subsampling was performed uniformly while preserving the original class and subject distributions, and the same subsets were used across all baselines to ensure fair comparison. This strategy was adopted solely to make comparison across methods computationally feasible under identical budgets, rather than as a requirement of the proposed framework.

We construct a single maximally large and diverse test split for each dataset to maximize sample coverage under limited computational budgets. Since \system{} is training-free and deterministic (temperature$=0$ for all methods except Self-Consistency), the main source of randomness arises from dataset subsampling. We therefore report standard deviations using 1,000-iteration bootstrap resampling to estimate variance over samples. This evaluation protocol is adopted to prioritize broad benchmark coverage with multiple tasks and sensors, rather than to restrict statistical rigor.

\begin{table*}
\centering
\renewcommand{\arraystretch}{1.0}
\smaller
\begin{tabularx}{0.96\textwidth}{LD@{\hspace{6pt}}D@{\hspace{6pt}}D@{\hspace{6pt}}D@{\hspace{6pt}}D@{\hspace{6pt}}D}
\toprule
Method & WESAD & SleepEDF & ActionSense & MMFit & PAMAP2 & Avg. \\
\midrule
\rowcolor{gray!15}
\multicolumn{7}{l}{\textit{Single-agent} baselines} \\
\rowcolor{white}
Single Agent & 0.787 \scalebox{0.8}{$\pm$ 0.034} & 0.498 \scalebox{0.8}{$\pm$ 0.033} & 0.569 \scalebox{0.8}{$\pm$ 0.032} & 0.772 \scalebox{0.8}{$\pm$ 0.043} & 0.493 \scalebox{0.8}{$\pm$ 0.019} & 0.624 \scalebox{0.8}{$\pm$ 0.015} \\
$+$ Self-Consistency & 0.779 \scalebox{0.8}{$\pm$ 0.034} & 0.513 \scalebox{0.8}{$\pm$ 0.032} & 0.537 \scalebox{0.8}{$\pm$ 0.031} & 0.859 \scalebox{0.8}{$\pm$ 0.021} & 0.491 \scalebox{0.8}{$\pm$ 0.019} & 0.636 \scalebox{0.8}{$\pm$ 0.013} \\
$+$ Self-Refine & 0.617 \scalebox{0.8}{$\pm$ 0.095} & 0.536 \scalebox{0.8}{$\pm$ 0.032} & 0.501 \scalebox{0.8}{$\pm$ 0.055} & 0.734 \scalebox{0.8}{$\pm$ 0.052} & 0.492 \scalebox{0.8}{$\pm$ 0.018} & 0.576 \scalebox{0.8}{$\pm$ 0.025} \\
\midrule
\rowcolor{gray!15}
\multicolumn{7}{l}{\textit{Modality agents} $+$ multi-agent debate baselines} \\
\rowcolor{white}
$+$ Debate & 0.904 \scalebox{0.8}{$\pm$ 0.025} & 0.569 \scalebox{0.8}{$\pm$ 0.031} & 0.609 \scalebox{0.8}{$\pm$ 0.031} & 0.956 \scalebox{0.8}{$\pm$ 0.012} & 0.494 \scalebox{0.8}{$\pm$ 0.018} & 0.706 \scalebox{0.8}{$\pm$ 0.011} \\
$+$ MAD & 0.843 \scalebox{0.8}{$\pm$ 0.031} & 0.532 \scalebox{0.8}{$\pm$ 0.030} & 0.592 \scalebox{0.8}{$\pm$ 0.031} & 0.960 \scalebox{0.8}{$\pm$ 0.011} & 0.509 \scalebox{0.8}{$\pm$ 0.018} & 0.687 \scalebox{0.8}{$\pm$ 0.011} \\
$+$ CMD & 0.896 \scalebox{0.8}{$\pm$ 0.025} & 0.553 \scalebox{0.8}{$\pm$ 0.033} & 0.607 \scalebox{0.8}{$\pm$ 0.031} & 0.963 \scalebox{0.8}{$\pm$ 0.011} & 0.493 \scalebox{0.8}{$\pm$ 0.018} & 0.703 \scalebox{0.8}{$\pm$ 0.011} \\
$+$ ReConcile & 0.884 \scalebox{0.8}{$\pm$ 0.027} & 0.535 \scalebox{0.8}{$\pm$ 0.031} & 0.595 \scalebox{0.8}{$\pm$ 0.031} & 0.942 \scalebox{0.8}{$\pm$ 0.014} & 0.507 \scalebox{0.8}{$\pm$ 0.018} & 0.692 \scalebox{0.8}{$\pm$ 0.011} \\
\midrule
\rowcolor{gray!15}
\multicolumn{7}{l}{\textit{Modality agents} $+$ fusion agents (ours)} \\
\rowcolor{white}
$+$ Semantic Fusion & 0.821 \scalebox{0.8}{$\pm$ 0.032} & 0.553 \scalebox{0.8}{$\pm$ 0.031} & 0.600 \scalebox{0.8}{$\pm$ 0.031} & 0.963 \scalebox{0.8}{$\pm$ 0.011} & 0.482 \scalebox{0.8}{$\pm$ 0.018} & 0.684 \scalebox{0.8}{$\pm$ 0.012} \\
$+$ Statistical Fusion & 0.925 \scalebox{0.8}{$\pm$ 0.022} & 0.573 \scalebox{0.8}{$\pm$ 0.031} & 0.598 \scalebox{0.8}{$\pm$ 0.030} & 0.959 \scalebox{0.8}{$\pm$ 0.011} & 0.475 \scalebox{0.8}{$\pm$ 0.018} & 0.706 \scalebox{0.8}{$\pm$ 0.011} \\
\textbf{\system{}} & 0.877 \scalebox{0.8}{$\pm$ 0.027} & 0.581 \scalebox{0.8}{$\pm$ 0.031} & 0.611 \scalebox{0.8}{$\pm$ 0.031} & 0.966 \scalebox{0.8}{$\pm$ 0.011} & 0.488 \scalebox{0.8}{$\pm$ 0.018} & 0.705 \scalebox{0.8}{$\pm$ 0.011} \\
\bottomrule
\end{tabularx}
\caption{Comparison of \system{} with baseline methods in terms of macro-F1.}
\label{tab:main_f1_results}
\end{table*}

\section{Results in Macro-F1}
\label{sec:appendix_f1score}

Table~\ref{tab:main_f1_results} reports the main results in terms of macro-F1. Since the evaluated datasets are class-balanced, the macro-F1 results show trends similar to the accuracy results in Table~\ref{tab:main_results}.

\section{Multi-Agent Debate Performance without Iterative Rounds}
\label{sec:appendix_round0}

In our main experiments, multi-agent debate baselines (Debate, MAD, CMD, ReConcile) employ two additional iterative rounds to refine initial predictions. These additional rounds incur substantially higher token cost than \system{}. Without these iterative rounds, Debate and CMD reduce to majority voting, equivalent to our statistical fusion agent, while MAD reduces to an LLM judge, equivalent to our semantic fusion agent. ReConcile differs by applying confidence-weighted voting.

To compare performance under comparable token budgets with \system{}, we evaluate all baselines without iterative debate rounds. Table~\ref{tab:round0_results} reports the results. Debate and CMD exhibit identical performance to statistical fusion, and MAD mirrors semantic fusion, as expected. ReConcile shows reduced accuracy (71.0\%) when iterative refinement is removed, performing $1.3\%$ lower than \system{}. Overall, \system{} consistently outperforms debate-based baselines under equal token cost, demonstrating that its hybrid fusion achieves superior accuracy without relying on expensive iterative deliberation.

\section{Comparison to Supervised Models}
\label{app:supervised_fusion}

While \system{} is designed as a training-free framework, we compare it to a supervised baseline to provide an upper-bound reference. We evaluate a Linear Discriminant Analysis (LDA) classifier, following prior multimodal fusion work~\citep{wesad}, using the same feature representations provided to the LLM prompts. For each dataset, we train LDA on 60\% of the samples without overlap with the test set. Table~\ref{tab:supervised_vs_consensus} reports the results.

\begin{table}[t]
\centering
\renewcommand{\arraystretch}{1.0}
\begin{tabular}{lcc}
\toprule
Dataset & Supervised & \system{} \\
\midrule
WESAD       & 0.903 \scalebox{0.8}{$\pm$ 0.032} & 0.880 \scalebox{0.8}{$\pm$ 0.029} \\
SleepEDF    & 0.829 \scalebox{0.8}{$\pm$ 0.004} & 0.600 \scalebox{0.8}{$\pm$ 0.031} \\
ActionSense & 0.917 \scalebox{0.8}{$\pm$ 0.013} & 0.611 \scalebox{0.8}{$\pm$ 0.031} \\
MMFit       & 0.999 \scalebox{0.8}{$\pm$ 0.004} & 0.967 \scalebox{0.8}{$\pm$ 0.010} \\
PAMAP2      & 0.944 \scalebox{0.8}{$\pm$ 0.010} & 0.558 \scalebox{0.8}{$\pm$ 0.026} \\
Avg.        & 0.918 \scalebox{0.8}{$\pm$ 0.013} & 0.723 \scalebox{0.8}{$\pm$ 0.026} \\
\bottomrule
\end{tabular}
\caption{Comparison between a supervised model and \system{} in terms of accuracy. The supervised model is trained on the same feature representations, while \system{} operates in a training-free setting.}
\label{tab:supervised_vs_consensus}
\end{table}

The supervised baseline achieves strong performance by leveraging labeled training data. Although \system{} operates without task-specific training or retraining, it still performs strongly on selected datasets, including WESAD and MMFit. This suggests that \system{} can be useful in deployment settings where labeled data are limited or training is infeasible.

\begin{table*}
\centering
\renewcommand{\arraystretch}{1.0}
\smaller
\begin{tabularx}{0.96\textwidth}{LD@{\hspace{6pt}}D@{\hspace{6pt}}D@{\hspace{6pt}}D@{\hspace{6pt}}D@{\hspace{6pt}}D}
\toprule
Method & WESAD & SleepEDF & ActionSense & MMFit & PAMAP2 & Avg. \\
\midrule
Single-Agent & 0.780 \scalebox{0.8}{$\pm$ 0.033} & 0.512 \scalebox{0.8}{$\pm$ 0.033} & 0.544 \scalebox{0.8}{$\pm$ 0.031} & 0.907 \scalebox{0.8}{$\pm$ 0.017} & 0.578 \scalebox{0.8}{$\pm$ 0.026} & 0.664 \scalebox{0.8}{$\pm$ 0.028} \\
Semantic Fusion & 0.833 \scalebox{0.8}{$\pm$ 0.030} & 0.536 \scalebox{0.8}{$\pm$ 0.032} & 0.556 \scalebox{0.8}{$\pm$ 0.031} & 0.963 \scalebox{0.8}{$\pm$ 0.011} & 0.564 \scalebox{0.8}{$\pm$ 0.026} & 0.691 \scalebox{0.8}{$\pm$ 0.026} \\
Statistical Fusion & 0.913 \scalebox{0.8}{$\pm$ 0.023} & 0.528 \scalebox{0.8}{$\pm$ 0.032} & 0.616 \scalebox{0.8}{$\pm$ 0.031} & 0.980 \scalebox{0.8}{$\pm$ 0.008} & 0.542 \scalebox{0.8}{$\pm$ 0.025} & 0.716 \scalebox{0.8}{$\pm$ 0.024} \\
\system{} & 0.860 \scalebox{0.8}{$\pm$ 0.028} & 0.528 \scalebox{0.8}{$\pm$ 0.032} & 0.580 \scalebox{0.8}{$\pm$ 0.031} & 0.967 \scalebox{0.8}{$\pm$ 0.010} & 0.561 \scalebox{0.8}{$\pm$ 0.026} & 0.699 \scalebox{0.8}{$\pm$ 0.025} \\
\bottomrule
\end{tabularx}
\caption{Performance under additive white Gaussian noise (AWGN) at 10 dB SNR. Results show that \system{} preserves similar relative performance trends to the clean setting under moderate sensor corruption.}
\label{tab:noise_results}
\end{table*}

\section{Robustness to Noise}
\label{app:noise_robustness}

To assess robustness under sensor corruption that may arise in practical deployments, we evaluate \system{} under Additive White Gaussian Noise (AWGN) at 10 dB SNR. Table~\ref{tab:noise_results} reports the results. Overall, the performance trends remain similar to the main results in Table~\ref{tab:main_results}, with limited degradation under additional noise. We interpret this robustness as stemming from two factors: first, the feature-based prompting relies on statistical and frequency-domain descriptors that remain informative under moderate perturbation; second, our hybrid fusion mechanism mitigates the impact of noisy modalities by aggregating complementary evidence across agents. These results support the practical applicability of \system{} in noisy environments.

\section{Prompt Templates}
\label{sec:appendix_prompts}

We provide the detailed prompts used in the single-agent baseline and \system{} for the SleepEDF~\citep{sleepedf} dataset. We present the \texttt{SYSTEM} and \texttt{USER} prompts for each specialized agent. To maintain brevity, recurring content or dataset-specific parameters are represented as placeholders (e.g., \texttt{<classes>}).

\noindent \textbf{Single-Agent Baseline.} The system prompt assigns the agent's role and details the task context. The user prompt provides a one-shot example and the multimodal features. It mandates a structured JSON output to facilitate automated parsing of the agent's reasoning.

\begin{promptbox}{\texttt{System prompt}}
You are multimodal sensing agent that solves a sensing task.
You have the following information about the task: \\
\textbf{Task}: Classify the user's sleep stage: \texttt{<classes>}, based on physiological signals collected from wearable sensors. \\
\textbf{Classes}: \texttt{<description of the classes>} \\
You will receive sensor features from multiple modalities, and you have the following information about the modality:
\{\texttt{<modality 1>}: \{"Data collection": \texttt{<data collection protocol>}, "Feature extraction": \texttt{<feature extraction methods>}\}, \texttt{<modality 2>}: ..., \textit{(repeated for all modalities)}\} \\ \\
Your goal is to analyze the features and provide a reasoned answer using your knowledge.
\end{promptbox}

\begin{promptbox}{\texttt{User prompt}}
You have received sensor features from multiple modalities: \\
\textbf{Examples:} \\
Sensor values might not always align with your inherent knowledge due to differences in data collection or processing. So, we included a few labeled examples to help your interpretation: \\
\textit{Example of} \texttt{<class 1>}: \\
  - \texttt{<feature name>}: \texttt{<value>} \\
  - \textit{(repeated for all modality features)} \\
\textit{Example of} \texttt{<class 2>}: ... \\
\textit{(repeated for all examples)} \\
\textbf{Current sample features}: ... \\ \\
Please provide your answer for the task among \texttt{<classes>} and the reasoning for your answer.
Note that the sensor features might be wrong due to the data collection or processing.
You can evaluate the quality of the features by checking the examples you have. \\ \\
Respond in the following strict JSON format: \{"REASON": "<Reasoning for the answer>", "ANSWER": "<Answer among \texttt{<classes>}>"\} \\
Do not include any additional text outside of the JSON.
\end{promptbox}

\noindent \textbf{Modality Agents.} We provide a modality agent prompt for \texttt{EEG-Pz-Oz} in the SleepEDF dataset. This agent has a modality-specific role while using the same task template as the single-agent baseline. It follows the same user prompt structure as the single-agent baseline; the only difference is that it includes only the \texttt{EEG-Pz-Oz} features instead of the full multimodal feature set.

\begin{promptbox}{\texttt{System prompt}}
You are EEG-Pz-Oz agent that solves a sensing task.\\
\texttt{<task description prompt>}
\end{promptbox}

\begin{promptbox}{\texttt{User prompt}}
You have received sensor features from EEG-Pz-Oz modality: \\
\texttt{<modality-specific example prompt>} \\
\texttt{<modality-specific sample prompt>} \\ \\
\texttt{<instruction prompt>} \\
\texttt{<formatting prompt>}
\end{promptbox}

\noindent \textbf{Semantic Fusion Agent.} We assign the role of a fusion agent and instruct it to aggregate multiple outputs from the modality agents to solve the task. The outputs from all modality agents are merged and passed to the prompt. It is then instructed to generate a final output based on its own knowledge and expertise.

\begin{promptbox}{\texttt{System prompt}}
You are a fusion agent that solves a multimodal sensing task based on interpretations from multiple sensing agents. \\
\texttt{<task description prompt>} \\ \\
You will receive reasonings and answers from multiple agents based on their interpretations of different modalities.
Your goal is to provide a final reasoned answer for the task.
\end{promptbox}

\begin{promptbox}{\texttt{User prompt}}
You have received responses from multiple sensing agents:\\
\{"EEG-Fpz-Cz": \texttt{<modality agent output>}, "EMG-submental": ..., \textit{(repeated for all modality agents)}\} \\ \\
Using your own knowledge and expertise, analyze the reasonings and answers and provide a final reasoned answer. \\
\texttt{<formatting prompt>}
\end{promptbox}

\noindent \textbf{Statistical Fusion Agent.} The statistical fusion agent shares the same system prompt as the semantic fusion agent but utilizes a distinct user prompt. It is provided with the \texttt{<majority-voted answer>} and tasked with justifying this consensus by identifying potential failure modes in the dissenting modality agents.

\begin{promptbox}{\texttt{User prompt}}
You have received responses from multiple sensing agents:\\
\texttt{<responses from modality agents>} \\ \\
You are on the side that the correct answer is \texttt{<majority-voted answer>} which is the majority answer.
Based on the given reasonings and answers, provide a final reasoned answer for the task. \\ \\
For agents who provided different answers from \texttt{<majority-voted answer>}, explain why their reasoning is likely affected by noise or unreliable signal interpretation. 
Stay consistent with the position that the correct answer is likely \texttt{<majority-voted answer>}. \\
\texttt{<formatting prompt>}
\end{promptbox}

\noindent \textbf{Hybrid Fusion Agent.} The hybrid fusion agent is guided by a system prompt that assigns it the role of a coordinator for reconciling the outputs of the fusion agents. It is provided with (i) the modality agents' outputs and (ii) the responses from both semantic and statistical fusion agents. Its task is to evaluate these responses and provide the final consolidated output.

\begin{promptbox}{\texttt{System prompt}}
You are a coordinator agent that solves a multimodal sensing task based on interpretations from multiple sensing agents. \\
\texttt{<task description prompt>} \\ \\
You will receive reasonings and answers from multiple agents, each interpreting different modalities, as well as two fusion agents that have already aggregated these responses in different ways.
Your goal is to coordinate the responses from the fusion agents and provide a final reasoned answer for the task.
\end{promptbox}

\begin{promptbox}{\texttt{User prompt}}
You have received the following information. \\
1. Original responses from individual modality agents: \\
\texttt{<responses from modality agents>} \\ \\
2. Responses from fusion agents: \\
\texttt{<response from the semantic fusion agent>} \\
\texttt{<response from the statistical fusion agent>} \\ \\
Your task is to determine the responses from the fusion agents and provide a final reasoned answer for the task. \\
\texttt{<formatting prompt>}
\end{promptbox}

\section{Qualitative Analysis}
\label{sec:appendix_outputs}

We present outputs from the single-agent baseline and \system{} to illustrate the collaborative decision-making process, using examples from the SleepEDF dataset.

\noindent \textbf{Single-Agent Baseline.} In this example, the ground-truth label is REM, but the single-agent baseline incorrectly predicts N2. While the agent performs plausible reasoning on the spectral features, it fails to integrate the subtle respiratory cues that output REM from light sleep.

\begin{promptbox}{\texttt{LLM response} (Sinlge-agent)}
\{"REASON": "The ratio of (delta+theta) to (alpha+beta) for both Fpz-Cz (9.34) and Pz-Oz (3.75) falls between the typical values for wakefulness ($\approx6.1$ and 1.5) and stage N2 ($\approx10.6$ and $4.5$). The delta power (86.75) is higher than in N1 but much lower than in deep sleep (N3). Alpha and beta powers are lower than in N1/N2 but higher than in wakefulness, indicating a transition toward sleep. The k‑complex power and EMG activity are low, suggesting a lighter sleep stage. EOG shows many large eye movements and a high slow‑movement ratio, which is more consistent with wake or N1 rather than REM. Overall, the feature pattern best matches stage N2, the intermediate sleep stage.", "ANSWER": "N2"\}
\end{promptbox}

However, when isolating the respiration data via a specialized modality agent, the correct stage is identified:

\begin{promptbox}{\texttt{LLM response} (Respiration modality agent)}
\{"REASON": "The current sample shows an inhale duration longer than exhale (ratio 1.39) and an inhale mean of 2.49 s versus exhale mean of 1.79 s, which aligns with the REM example where the inhale is longer than the exhale (ratio 1.33). Other REM characteristics—such as a relatively high respiration rate ($\sim$13 breaths/min), moderate duration ($\sim$4.6 s), and moderate stretch—are also reflected in the current data. In contrast, the other stages (W, N1, N2, N3) all have inhale/exhale ratios below 1 and different mean durations. Therefore, the most consistent match is REM.", "ANSWER": "REM"\}
\end{promptbox}

\noindent \textbf{Semantic Fusion Agent.} In the previous example, while several modality agents provides incorrect classifications, the EEG-Pz-Oz and respiration agents correctly identify the REM stage. The semantic fusion agent successfully resolves this cross-modal conflict by prioritizing the high-fidelity evidence correct modality agents.

\begin{promptbox}{\texttt{LLM response} (Semantic fusion agent)}
\{"REASON": "The most reliable indicator of sleep stage is the EEG. While the frontal channel (Fpz-Cz) shows a high (delta+theta)/(alpha+beta) ratio typical of N2, the posterior channel (Pz-Oz) displays a ratio (3.75) that lies between the typical REM value ($\approx$2.6) and the N2 value ($\approx$4.5), and its other features (lower alpha/beta, lower variance) are more consistent with REM than with deeper stages. The respiratory pattern shows an inhale/exhale ratio $>$1 and a respiration rate ($\sim$13 breaths/min) characteristic of REM. EMG amplitude is low compared with wakefulness, which aligns with REM muscle atonia, although it is not as low as would be seen in deep sleep. EOG indicates a high slow‑movement ratio, but this can be influenced by sensor noise and is not a definitive marker for N3. Considering the stronger evidence from EEG (posterior channel) and respiration, the overall pattern points to REM sleep. Therefore the most plausible classification is REM.", "ANSWER": "REM"\}
\end{promptbox}

However, the semantic fusion agent is susceptible to prior-knowledge bias, where it may over-rely on a single modality output even when it is incorrect. For example, in an N1 stage sample, we observed a case where the respiration agent incorrectly suggested N2; despite the majority of other agents correctly identifying N1, the semantic agent erroneously followed the respiration agent.

\begin{promptbox}{\texttt{LLM response} (Semantic fusion agent)}
\{"REASON": "The most reliable signals for sleep staging are the EEG and respiration measures. Both EEG channels report low-amplitude, low-power activity, which is inconsistent with deep sleep (N3) that would show high-amplitude slow waves, and also inconsistent with REM, which would typically show characteristic sawtooth activity and higher dynamic range. The EOG channel's lack of large eye movements rules out REM and is compatible with both light and intermediate stages, but does not distinguish N1 from N2. The respiration data shows a moderate stretch ($\approx 2.2 \times 10^9$L), a respiration rate of 13.4 bpm, and exhale/inhale durations around 2.2 s---values that fall squarely within the typical range for stage N2 and are less compatible with the lower volume, longer duration pattern of N3 or the shorter, higher-rate pattern of REM. The EMG signal is intermediate between wakefulness and deeper stages, again pointing to a transitional stage rather than deep sleep. Given that the majority of modalities (EEG, respiration, EMG) lean toward an intermediate sleep stage and the EOG does not provide evidence for REM, the most consistent classification is stage N2.", "ANSWER": "N2"\}
\end{promptbox}

\noindent \textbf{Statistical Fusion Agent.} To mitigate semantic errors, the statistical fusion agent provides a complementary perspective by anchoring its reasoning to the majority consensus. In the aforementioned failure case, it identifies that the majority of modality agents point to N1 and provides a justification for why dissenting agents are likely erroneous.

\begin{promptbox}{\texttt{LLM response} (Statistical fusion agent)}
\{"REASON": "The two modalities that are most directly linked to sleep stage classification—central EEG (Fpz‑Cz) and submental EMG—both point to light sleep (N1). The Fpz‑Cz feature vector shows low‑amplitude, low‑power characteristics (high variance relative to N1, low delta power, low delta/theta ratio, and an alpha/beta ratio close to the N1 mean) that match the prototypical N1 profile far better than any other stage. The submental EMG is in the intermediate activity range between wakefulness and deeper stages, with mean and standard deviation values, percentiles, and peak statistics that align with published N1 values. These two signals are the gold standards for distinguishing wake, N1, N2, N3, and REM, so their agreement strongly supports an N1 classification. The other modalities provide weaker or conflicting evidence. The EOG horizontal channel, while showing low rapid‑movement power and high slow‑movement power, also exhibits an unusually high dynamic range and a very low difference variance, which are typical of measurement artifacts or electrode misplacement. Because eye‑movement activity is only one component of REM and N3, relying on it alone can misclassify light sleep as deep sleep. The EEG‑Pz‑Oz channel indicates REM based on low dynamic range and sawtooth power, yet its (delta+theta)/(alpha+beta) ratio is intermediate and the alpha/beta ratio is higher than the REM prototype, suggesting noise or cross‑talk from the adjacent frontal channel. Finally, the respiratory signal suggests N2 due to moderate breath duration and volume, but respiration alone is a poor discriminator between N2 and N3 and is highly variable across individuals. Given the central EEG and EMG consensus and the known unreliability of single‑modality cues in isolation, the most reliable conclusion is that the subject is in the N1 stage.", "ANSWER": "N1"\}
\end{promptbox}

\noindent \textbf{Hybrid Fusion Agent.} The hybrid fusion agent then evaluates these competing reasoning paths. In the previous example, it follows the statistical consensus. 

\begin{promptbox}{\texttt{LLM response} (Hybrid fusion agent)}
\{"REASON": "The most reliable evidence comes from the central EEG (Fpz‑Cz) and submental EMG, both of which are the gold standards for distinguishing sleep stages. The Fpz‑Cz channel shows low‑amplitude, low‑power activity with variance and delta power values that match the prototypical N1 profile far better than any other stage. The submental EMG is in the intermediate activity range between wakefulness and deeper stages, with mean, standard deviation, and peak statistics that align closely with published N1 values. These two signals agree on light sleep (N1). Other modalities provide conflicting or weaker cues: the Pz‑Oz channel suggests REM but its intermediate (delta+theta)/(alpha+beta) ratio and higher alpha/beta ratio point to noise; the EOG horizontal channel indicates minimal rapid eye movements, which is typical of both N1 and N2 and not decisive; the respiration signal is consistent with N2 but respiration alone is a poor discriminator. Given the consensus of the most reliable modalities and the known unreliability of single‑modality cues in isolation, the most robust conclusion is that the subject is in the N1 stage.", "ANSWER":"N1"\}
\end{promptbox}