


\documentclass[11pt]{article}

% Change "review" to "final" to generate the final (sometimes called camera-ready) version.
% Change to "preprint" to generate a non-anonymous version with page numbers.
\usepackage[final]{acl}

% Standard package includes
\usepackage{times}
\usepackage{latexsym}
\usepackage{booktabs}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{amsthm}
\usepackage{xspace}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newcommand{\EHGRAG}{EHRAG\xspace}


\usepackage[utf8]{inputenc}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{pifont}
\usepackage[table]{xcolor} 
\usepackage{enumitem}

\newcommand{\cmark}{\ding{52}}
\newcommand{\xmark}{\ding{56}}


\definecolor{headergray}{HTML}{EFEFEF}
\definecolor{baselinepink}{HTML}{FFF0F0}
\definecolor{proposelblue}{HTML}{F0F7FF}


% For proper rendering and hyphenation of words containing Latin characters (including in bib files)
% For Vietnamese characters
% \usepackage[T5]{fontenc}
% See https://www.latex-project.org/help/documentation/encguide.pdf for other character sets

% This assumes your files are encoded as UTF8
\usepackage{microtype}
\usepackage{inconsolata}
\usepackage{graphicx}



\title{\EHGRAG: Bridging Semantic Gaps in Lightweight GraphRAG via Hybrid Hypergraph Construction and Retrieval}


\author{
  Yifan Song\textsuperscript{1}, \;
  Xingjian Tao\textsuperscript{1}, \;
  Zhicheng Yang\textsuperscript{1}, \;
  Yihong Luo\textsuperscript{2}, \;
  and Jing Tang\textsuperscript{1,2}\thanks{Corresponding Author: Jing Tang.} \\
  \textsuperscript{1}The Hong Kong University of Science and Technology (Guangzhou) \\
  \textsuperscript{2}The Hong Kong University of Science and Technology \\
  \texttt{ysong853@connect.hkust-gz.edu.cn}, \;
  \texttt{jingtang@ust.hk}
}


\begin{document}
\maketitle
\begin{abstract}

Graph-based Retrieval-Augmented Generation (GraphRAG) enhances LLMs by structuring corpus into graphs to facilitate multi-hop reasoning. While recent lightweight approaches reduce indexing costs by leveraging Named Entity Recognition (NER), they rely strictly on structural co-occurrence, failing to capture latent semantic connections between disjoint entities. To address this, we propose \textbf{\EHGRAG}, a lightweight RAG framework that constructs a hypergraph capturing both structure and semantic level relationships, employing a hybrid structural-semantic retrieval mechanism. Specifically, \EHGRAG constructs structural hyperedges based on sentence-level co-occurrence with lightweight entity extraction and semantic hyperedges by clustering entity text embeddings, ensuring the hypergraph encompasses both structural and semantic information. For retrieval, \EHGRAG performs a structure-semantic hybrid diffusion with topic-aware scoring and personalized pagerank (PPR) refinement to identify the top-k relevant documents. Experiments on four datasets show that \EHGRAG outperforms state-of-the-art baselines while maintaining linear indexing complexity and zero token consumption for construction. Code is available at \url{https://github.com/yfsong00/EHRAG}.
\end{abstract}
\begin{sloppy}
\input{content/Intro}
\input{content/Preliminaries}
\input{content/Methods}
\input{content/Experiments}
%\input{content/RelatedWork}
\input{content/Conclusion}
\end{sloppy}

\section*{Limitations}
Despite achieving state-of-the-art performance with linear indexing complexity, EHRAG remains sensitive to several key hyperparameters, such as the cluster size $D$ and the decay factor $\gamma$, which may necessitate specific tuning for different datasets. Furthermore, while semantic hyperedges effectively bridge disjoint entities, the framework's reliance on the quality of initial entity extraction and text embeddings could potentially introduce structural noise in extremely specialized domains.

\section*{Acknowledgements}
This work is partially supported by National Key R\&D Program of China under Grant No. 2023YFF0725100, by the National Natural Science Foundation of China (NSFC) under Grant No. 62402410, by Guangdong Provincial Project (No. 2023QN10X025), by Guangdong Basic and Applied Basic Research Foundation under Grant No. 2023A1515110131, by Guangzhou Municipal Education Bureau (No. 2024312263), by Nansha District Project (No. 2023ZD022), and by HKUST(GZ) Kunpeng\&Ascend Center of Cultivation.

\bibliography{custom}

\clearpage

\appendix

\input{content/Appendix}

\end{document}
