
\documentclass{article} % For LaTeX2e
\usepackage{iclr2026_conference,times}

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{amsthm}
\usepackage{multirow}
\usepackage{mathtools}
\usepackage{tikz,lipsum,lmodern}
\usepackage[most]{tcolorbox}
\usepackage[table]{xcolor}
\usepackage{array}
% \usepackage[moderate, tracking = normal]{savetrees}
% \usepackage{amsfonts}
\usepackage{dsfont}
\usepackage{microtype}
\usepackage{graphicx}
% \usepackage{subfigure}
\usepackage[skip=4pt]{caption}
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{wrapfig} 
\usepackage{rotating}
% \usepackage{pdflscape}
% \usepackage{float}
% \usepackage{placeins}

% for textcolor
% \usepackage{xcolor}


% \title{TAMAS: Investigating Security
% Risks in Multi-Agent LLM Systems}

\title{TAMAS: Benchmarking Adversarial \\ Risks in Multi-Agent LLM Systems}

% Authors must not appear in the submitted version. They should be hidden
% as long as the \iclrfinalcopy macro remains commented out below.
% Non-anonymous submissions will be rejected without review.

% \author{Antiquus S.~Hippocampus, Natalia Cerebro \& Amelie P. Amygdale \thanks{ Use footnote for providing further information
% about author (webpage, alternative address)---\emph{not} for acknowledging
% funding agencies.  Funding acknowledgements go at the end of the paper.} \\
% Department of Computer Science\\
% Cranberry-Lemon University\\
% Pittsburgh, PA 15213, USA \\
% \texttt{\{hippo,brain,jen\}@cs.cranberry-lemon.edu} \\
% \And
% Ji Q. Ren \& Yevgeny LeNet \\
% Department of Computational Neuroscience \\
% University of the Witwatersrand \\
% Joburg, South Africa \\
% \texttt{\{robot,net\}@wits.ac.za} \\
% \AND
% Coauthor \\
% Affiliation \\
% Address \\
% \texttt{email}
% }

\author{Ishan Kavathekar$^{1*}$
Hemang Jain$^{1*}$
Ameya Rathod$^{1}$\\
\textbf{Ponnurangam Kumaraguru}$^{1}$
\textbf{Tanuja Ganu}$^{2}$\\
$^{1}$International Institute of Information Technology, Hyderabad\\
$^{2}$Microsoft Research, India} 


% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.
% \author{Ishan Kavathekar}

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
\begin{document}


\maketitle

\begingroup
\renewcommand\thefootnote{}\footnotetext{$^{*}$ Authors contributed equally.}%
\addtocounter{footnote}{-1}%
\endgroup

\begin{abstract}
Large Language Models (LLMs) have demonstrated strong capabilities as autonomous agents through tool use, planning, and decision-making abilities, leading to their widespread adoption across diverse tasks. As task complexity grows, multi-agent LLM systems are increasingly used to solve problems collaboratively. However, safety and security of these systems remains largely under-explored. Existing benchmarks and datasets predominantly focus on single-agent settings, failing to capture the unique vulnerabilities of multi-agent dynamics and co-ordination. To address this gap, we introduce \textbf{T}hreats and \textbf{A}ttacks in \textbf{M}ulti-\textbf{A}gent \textbf{S}ystems (\textbf{TAMAS}), a benchmark designed to evaluate the robustness and safety of multi-agent LLM systems. TAMAS includes five distinct scenarios comprising 300 adversarial instances across six attack types and 211 tools, along with 100 harmless tasks. We assess system performance across ten backbone LLMs and three agent interaction configurations from Autogen and CrewAI frameworks, highlighting critical challenges and failure modes in current multi-agent deployments. Furthermore, we introduce Effective Robustness Score (ERS) to assess the tradeoff between safety and task effectiveness of these frameworks. Our findings show that multi-agent systems are highly vulnerable to adversarial attacks, underscoring the urgent need for stronger defenses. TAMAS provides a foundation for systematically studying and improving the safety of multi-agent LLM systems. Code is available at \url{https://github.com/microsoft/TAMAS}.
\end{abstract}

\input{sections/1.Introduction}
\input{sections/2.RelatedWorks}
\input{sections/3.ExperimentalSetup}
\input{sections/4.Results}
\input{sections/5.Discussion}
\input{sections/6.Conclusion}


\bibliography{iclr2026_conference}
\bibliographystyle{iclr2026_conference}

\appendix
\input{sections/7.Appendix}


\end{document}
