\section{Related Work}
\label{relate}

Deep multi-agent reinforcement learning algorithms have witnessed significant advances in recent years. COMA~\cite{foerster2018counterfactual}, MADDPG~\cite{lowe2017multi}, PR2~\cite{wen2019probabilistic}, and DOP~\cite{wang2021off} study the problem of policy-based multi-agent reinforcement learning. They use a (decomposed) centralized critic to calculate gradients for decentralized actors. Value-based algorithms decompose the joint value function into individual utility functions in order to enable efficient optimization and decentralized execution. VDN~\cite{sunehag2018value}, QMIX~\cite{rashid2018qmix}, and QTRAN~\cite{son2019qtran} progressively expand the representation capabilities of the mixing network. QPLEX~\cite{wang2020qplex} implements the full IGM class~\cite{son2019qtran} by encoding the IGM principle into a duplex dueling network architecture. Weighted QMIX~\cite{rashid2020weighted} proposes weighted projection to decompose any joint action-value functions. There are other works that investigate into MARL from the perspective of coordination graphs~\cite{guestrin2002coordinated, guestrin2002multiagent, bohmer2020deep}, communication~\cite{singh2019learning, mao2020neighborhood, wang2020learning}, and role-based learning~\cite{wang2020roma, wang2021rode}.

\textbf{Knowledge sharing in MARL} From IQL~\cite{tan1993multi} to QPLEX, many works focus on designing mixing network structures and have provided promising empirical and theoretical results. For these works, experience sharing among agents has been an important component. Learning from others is one essential skill engraved in humans' genes to survive in society. Based on the relationship between teachers and students in human society, a series of research work hopes each agent can learn from others or selectively share its knowledge with others~\cite{zhu2019q,liang2020parallel,fu2020auto}. But it is challenging to specify knowledge in practice, let alone deciding what to share or learn. SEAC~\cite{christianos2020shared} partially solves this problem by sharing trajectories only for off-policy training. NCC~\cite{mao2020neighborhood} maintains cognition consistency by representation alignment between neighbors. \citet{roy2020promoting} force each agent to predict others' local policies and adds a coach for group experience alignment. \citet{christianos2021scaling} group agents during pre-training and force agents in the same group to use one policy. In this paper, we do not try to let agents choose whether to learn or share experiences. Our neural network structure shown in Fig.~\ref{fig:model} can balance group coordination and diversity by gradient backpropagation. 


\textbf{Diversity} In single-agent settings, diversity emerges for exploration or solving sparse reward problems. Existing methods such as curiosity-driven algorithms~\cite{pathak2017curiosity,burda2018exploration,badia2020never,badia2020agent57} or maximising mutual information~\cite{eysenbach2018diversity,sharma2020dynamics,campos2020explore} have shown great promise. When encouraging diversity in MARL settings, agents' coordination must be considered. Several recent works study this problem, such as MAVEN~\cite{mahajan2019maven}, EITI \& EDTI~\cite{wang2020influence}, and EOI~\cite{jiang2020emergence}. MAVEN learns a diverse ensemble of monotonic approximations with the help of a latent space to explore. EITI and EDTI consider pairwise mutual influence to encourage the interdependence between agents. EOI combines the gradient from the intrinsic value function (IVF) and the total Q-function to train each agent's local Q-function. In this paper, we encourage agents to explore unique trajectories by optimizing the mutual information between agent's identity and trajectory. Moreover, we propose a novel network structure to enable experience sharing or consensus, which combines all agents' rare ideas, while still maintain independent action-value functions for each agent to behave differently when necessary. Our approach considers the trade-off relationship between knowledge sharing and diversity, and learns to establish a balance and leverage their advantages for joint task solving. 

% ROMA~\cite{wang2020roma} introduces the role concept into MARL and enables adaptive shared learning among agents. However, agents with similar observations have the risk of being forced to behave the same due to role assignments.
%Experiment results in Section~\ref{experiment} demonstrate that our approach can achieve diversity quickly while achieving outstanding performance in super complex multi-agent problems that need cooperation.