\begin{abstract}
Knowledge graphs (KGs) capture knowledge in the form of  {\em head--relation--tail} triples and are a crucial component in many AI systems. There are two important reasoning tasks on KGs: (1) single-hop knowledge graph completion, which involves predicting individual links in the KG; and (2), multi-hop reasoning, where the goal is to predict which KG entities satisfy a given logical query. Embedding-based methods solve both tasks by first computing an embedding for each entity and relation, then using them to form predictions. However, existing scalable KG embedding frameworks only support single-hop knowledge graph completion and cannot be applied to the more challenging multi-hop reasoning task. Here we present {\em \modellong (\modelshort)}, the first general framework for both single-hop and multi-hop reasoning in KGs. Using a \emph{single machine} \modelshort can perform multi-hop reasoning in Freebase KG (86M entities, 338M edges), which is 1,500$\times$ larger than previously considered KGs. The key to \modelshort's runtime performance is a novel bidirectional rejection sampling that achieves a square root reduction of the complexity of online training data generation. Furthermore, \modelshort exploits asynchronous scheduling,  overlapping CPU-based data sampling, GPU-based embedding computation, and frequent CPU--GPU IO. \modelshort increases throughput (\ie, training speed) over prior multi-hop KG frameworks by 2.2$\times$ with minimal GPU memory requirements (2GB for training 400-dim embeddings on 86M-node Freebase) and achieves near linear speed-up with the number of GPUs.  Moreover, on the simpler single-hop knowledge graph completion task \modelshort achieves comparable or even better runtime performance to state-of-the-art frameworks on both single GPU and multi-GPU settings.
\end{abstract}