% !TEX root = main.tex


\subsection{Further optimization of \modelshort}
\label{sec:more_opt}


In addition to the above optimized system design for \modelshort, there are several other important optimization that further speeds up the training, which we highlight below.


\textbf{Sharing negative samples.}
Although with the asynchronous design we can overlap the embedding R/W with GPU computation, it is still important to keep the size of memory exchange small. Inspired by \citet{zheng2020dgl}, we share the negative answers among the queries in a mini-batch. Each mini-batch data is formatted as $\rbr{\Ncal, \cbr{(q_i, \Vcal_{q_i}, \Acal_{q_i}}_{i=1}^M, Mask}$, where $\Ncal \subset \Vcal$ are the shared negative answers for all queries. $Mask \in \cbr{0, 1}^{M \times |\Ncal|}$ is an indicator matrix. $Mask_{i, j}$ specifies whether the $j$-th entity in $\Ncal$ is a negative sample for $q_i$. 

This sharing trick also favors our bi-directional rejection sampler, as by nature it is the sample-and-check process, with the only adaptation that all the queries in the same mini-batch share the support of negative sampling proposal. 

\textbf{Customized CUDA distance kernel.}
Given $M$ queries and negative answer candidates $\Ncal$, the computation of $M \times |\Ncal|$ pairs of distances is model dependent. While generally distances like inner-product or L2 can be implemented with efficient matrix multiplication, geometries designed for multi-hop reasoning like box or beta distribution requires more complicated distance metrics like KL divergence. We provide a generic interface to parallelize the computation with customized CUDA kernel, which also enables the operation fusion to reduce GPU memory consumption.


\textbf{Scheduled structure sampling. }
Since we have the synchronized gradient update for $\theta_D$ at each step, it is important to balance the computation among worker processes. One aspect is the query tree structures sampled in each mini-batch. Some of the simple structures like 1-hop question can be computed very fast, while others like conjunctions with negations need not only multi-hop computation, but also involve dense neural network calculation. To balance the workload, we make the sampler $\Dcal_w$ of each worker $w$ to sample queries of the same structure in each mini-batch, by synchronizing the random seed at beginning. Note that we only make the query structure same, not the actual instantiated query.
