
\section{Planning and Reasoning Graph \texorpdfstring{\emojiplantitle}{Planning and Reasoning Graph}}
\label{sec-reasonplan}

A planning or reasoning graph characterizes the inherent logical flow among different entities, where entities typically represent concrete planning or reasoning substeps, and edges denote their logical relations. For the planning graph~\cite{shen2024hugginggpt, zhuangtoolchain}, a common example is a set of API tools used to achieve certain goals, where nodes represent actions, and edges denote their relational dependencies. For reasoning graphs, a notable example is the recent proposed chain/tree/graph of thoughts techniques~\cite{besta2024graph, wei2022chain, yao2024tree} where each node represents a decision-making thinking step connected by the reasoning flow. The dependency constraint and reasoning flow in the planning/reasoning graphs can be naturally represented as relational knowledge, which forms the foundation for GraphRAG in fulfilling planning/reasoning tasks. This section reviews GraphRAG for the planning and reasoning graph~\cite{besta2024graph, lin2024graph, madaan2021could, saha2021explagraphs, sakib2024consolidating, shen2024hugginggpt, shen2023taskbench, song2023llm, song2023restgpt, wu2024can, wei2022chain, xu2024p, yao2024tree, zhao2024large, zhuangtoolchain, hao2023reasoning}.


\subsection{Application Tasks}
The representative tasks conducted on planning and reasoning graphs are summarized as follows:
\begin{itemize}[leftmargin=*]
    \item \textbf{Sequential Plan Retrieval}~\cite{shen2024hugginggpt, shen2023taskbench, song2023restgpt, wu2024can, zhao2024large}:
    As one of the most frequently encountered tasks, plan retrieval aims to retrieve the plan of steps or tools in the format of subgraphs to complete user queries. For example, given the user query "Please generate an image where a girl is reading a book, and her pose is the same as the boy in "example.jpg," then please describe the new image with your voice.", the retrieved final plan from the global plan graph would be "Post Detection" $\rightarrow$ "Pose-to-Image" $\rightarrow$ "Image-to-Text" $\rightarrow$ "Text-to-Speech."

    \item \textbf{Naturalistic Asynchronous Planning}~\cite{lin2024graph}: In contrast to plan retrieval, which considers only dependency constraints among plans, incorporating time constraints introduces a greater challenge. Naturalistic Asynchronous Planning aims to produce a plan that meets dependency requirements and optimizes task completion efficiency, using time summation, time comparison, and constrained reasoning. For example, a user might request, "To make calzones, here are the steps and times required; please calculate the optimal plan for completion." An efficient plan would execute "roll dough," "add filling," and "fill dough" sequentially, with "preheat oven" in parallel, and then conclude with "bake."


    \item \textbf{Structured Commonsense Reasoning}~\cite{saha2021explagraphs}: Given a belief and an argument, structured common sense reasoning aims to infer the stance and generate/retrieve the corresponding commonsense explanation graph that explains the inferred stance. 

    \item \textbf{Defeasible Inference}~\cite{madaan2021could}: Defeasible Inference is a mode of reasoning in which, given a premise, a hypothesis may be weakened or overturned in light of new evidence. A prominent approach is to support defeasible inference through argumentation by constructing inference graphs.

    \item \textbf{Tool Usage}~\cite{zhuang2023toolchain, hao2023reasoning}: Instructing LLMs to use external tools for complex real-world problems has gained increasing importance. Recent research has explored advanced planning strategies to enhance LLMs' tool-use intelligence. Notably, two approaches employ A* search~\cite{zhuang2023toolchain} and Monte Carlo Tree Search~\cite{hao2023reasoning}, both utilizing graph-structured reasoning to adaptively retrieve the next tool based on the LLM's internal evaluations and environmental feedback. These methods enable dynamic tool retrieval, refining the model's problem-solving precision and flexibility.

    \item \textbf{Embodied Planning}~\cite{song2023llm, xu2024p}: Embodied planning tasks in Embodied AI involve guiding agents to perform sequences of actions based on natural language instructions and visual cues in simulated or real-world environments. These tasks, such as organizing or cleaning, challenge agents due to ambiguous instructions, limited task-specific knowledge, sparse feedback, and complex, variable action spaces.
\end{itemize}


\subsection{Reasoning and Planning Graph Construction}
Most existing methods for constructing reasoning and planning graphs begin by analyzing relational dependencies and subsequently adding edges based on these hard-coded rules. Therefore, rather than limiting our focus to reviewing this only rule-based construction method, we review various dependency categories used for edge addition.

\begin{itemize}[leftmargin=*]
    \item \textbf{Resource Dependency}~\cite{shen2023taskbench, song2023restgpt, wu2024can}: This dependency is defined as the shared resources among different actions/decisions. For example, two tools are connected if the output of one tool matches the input of the other, enabling a seamless transition from one process to another. The decision to add edges in existing graph construction methods is made by checking whether one node's input matches another node's output (e.g., plans, tools, or some other abstract processes).
    

    \item \textbf{Temporal Dependency}~\cite{shen2023taskbench}: This relation ensures that the sequence of events follows certain orders within the planning and reasoning process. For example, connections in some collected datasets denote the successive order between two APIs for daily life.


    \item \textbf{Inclusive Dependency}~\cite{ma2024harec}: The dependency described indicates that two connected nodes belong to the same category or environment. For example, cobblestones and birdhouses are both part of the category of garden decorations~\cite{wang2024knowledge2}. Hypergraphs can effectively capture such belonging relationships where one entity belongs to multiple environments~\cite{feng2019hypergraph}. Furthermore, these dependencies often form hierarchical structures, where "grandparent" entities encompass "parent" entities, which in turn encompass their "children." As the depth of the hierarchy increases, the space of possible dependencies grows exponentially, presenting a significant computational challenge. To address this, many previous works have proposed encoding such hierarchies in hyperbolic space~\cite{ma2024harec, liu2019hyperbolic, zhang2024hierarchical}. To the best of our knowledge, no prior research has explored inclusive dependencies in RAG systems.
    

    \item \textbf{Causual Dependency}~\cite{lin2024graph}: This dependency indicates the cause-and-effect logic within the graph, where one action/decision causes the trigger of another action/decision. A long-standing example is the casual graph to encode assumptions about the data-generating process.


    \item \textbf{Analogy Dependency}~\cite{yu2023thought, yuan2023analogykb}: This dependency underscores analogical reasoning, where relationships take the form "A is to B as C is to D." By recognizing and leveraging such dependency, humans build on existing knowledge to forge new insights across domains. A powerful historical example is the discovery of Coulomb's Law, inspired by the analogy between gravitational forces affecting celestial bodies and electrical forces between charged particles~\cite{priestley1775history}.
\end{itemize}

While resource-dependent and causal relations involve a sequentially structured relation (former step/tool/decision leads to the later step/tool/decision), they are inherently different. For instance, if Tool A generates a report in PDF format and Tool B is designed to extract data from PDF files, Tool A and B share resource dependency because the output of Tool A (the PDF) matches the input of Tool B. However, this connection does not imply a direct cause-and-effect relationship between the two tools, i.e., using Tool A would not necessarily cause us to use Tool B.


 


\subsection{Retriever}
Retrievers for handling tasks on reasoning and planning graphs are often modeled as graph traversers. The query or task instruction locates the initial seeding nodes to initialize the graph traversal; then a traversal expands the graph's scope either until a preset budget is exhausted or specific criteria are met. A core step throughout is selecting the most relevant neighbors from all potential candidates. Based on the criterion for neighborhood selection, retrievers fall into two main categories: embedding-based methods, which prioritize neighbors based on embedding similarity, and heuristic-based methods, which use local and global reward functions to determine neighbor importance.


\begin{itemize}[leftmargin=*]
\item \textbf{Embedding-based}: \citet{wu2024can} decompose the query, subsequently perform the embedding similarity match between the concatenated subquery with the current retrieved task API and each of the existing APIs, and then select the top one from the existing neighboring APIs. It explores the strategy of training and the one without training. 


\item \textbf{Heuristic-based}: Compared to embedding-based methods, which rely on dedicated training data for mapping, heuristic-based methods define rules to guide the graph retriever effectively\cite{zhao2024large, zhuangtoolchain, hao2023reasoning}. \citet{zhuangtoolchain} model tool planning as a tree search algorithm, incorporating A* search to adaptively retrieve the most promising tool for subsequent use based on accumulated and anticipated costs. Both cost functions are heuristically designed, drawing on prior literature and practical insights.


\item \textbf{Thought Propagation Retrieval}~\cite{yu2023thought}: Given an input problem, thought propagation retrieval prompts LLMs to propose a set of analogous problems, and then applies established prompting techniques, like Chain-of-Thought (CoT), to derive solutions. The aggregation module subsequently consolidates solutions from these analogous problems, enhancing the problem-solving process for the original input.
\end{itemize}

\subsection{Organizer}
The current GraphRAG literature on planning and reasoning graphs generally omits organizer mechanisms, as the retrieval process alone achieves sufficient precision, eliminating the need for reranking. Unlike document or knowledge graphs, which typically apply one-shot embedding-based similarity retrieval to select the top-K relevant content~\cite{wu2024stark}, planning and reasoning graphs use a multi-round embedding similarity process integrated with reasoning steps, enhancing plan fidelity. Moreover, reward-based retrieval involves a sophisticated search that further boosts accuracy. Together, these high-quality strategies reduce the need for fine-grained reranking or filtering.


\subsection{Generator}
Most existing GraphRAG approaches for reasoning and planning tasks either output the retrieved plan directly or integrate it into the LLM for downstream solution generation. For instance, \citet{wu2024can} outputs the retrieved graph-structured plan as the final result, while \citet{shen2024hugginggpt} compiles executed results from expert tools to generate the response. Similarly, after constructing a tool invocation graph, \citet{shen2023taskbench} directly prompts the LLM to generate the parameters, and \citet{lin2024graph} leverages the LLM to produce asynchronous plans based on task dependencies, time, and graph constraints. Notably, most of these works focus on fusing textual information, primarily using different graph structure formats (e.g., adjacency matrix, adjacency list, edge list, CSR) presented in textual form.




\subsection{ Resources and Tools}

We summarize the useful resources and tools for GraphRAG on planning and reasoning graphs. 

\subsection{Data Resources}
\begin{itemize}[leftmargin=*]
    \item \textbf{Hugging Face}\footnote{\href{https://github.com/microsoft/JARVIS}{https://github.com/microsoft/JARVIS}}~\cite{shen2023taskbench}: Hugging Face offers a wide array of AI models covering multi-modality tasks in language, vision, audio, video, and more. Each task corresponds to a tool node that handles specific input and output. If tools A and B are connected, the output type of A must match the input type of B. Thus, edges in the Hugging Face plan graph represent the resource-dependent relation. \cite{shen2023taskbench} firstly collects the tool repository and builds a tool graph with a collection of tools and their dependencies. Then, to generate each question, they sample a subgraph from the tool graph in the three basic formats: node, chain, and directed acyclic graph (DAG), each of which embodies a specific pattern for tool invocation. After that, the sampled subgraph is sent to LLMs to synthesize user instructions and populate the parameters for the tool subgraphs. At last, LLM-based and rule-based self-critic mechanisms are used to check and filer out the generated instruction to guarantee quality.

    \item \textbf{Multimedia}\footnote{\href{https://github.com/microsoft/JARVIS}{https://github.com/microsoft/JARVIS}}~\cite{shen2023taskbench}: Unlike the AI-focused tools of Hugging Face, multimedia tools serve a broader range of user-centric tasks such as file downloading and video editing. The edges remain consistent with the Hugging Face domain and the tool connections denote the resource-dependent relation similar to Hugging Face. The construction of Multimedia is similar to Hugging Face.
    
    \item \textbf{Daily Life APIs}\footnote{\href{https://github.com/microsoft/JARVIS}{https://github.com/microsoft/JARVIS}}~\cite{shen2023taskbench}: Daily life services, including web search and shopping, can also be viewed as tools for specific tasks. The dependencies among these APIs are primarily temporal, meaning that two daily life APIs are connected if one follows the other in sequence. The construction of Daily Life APIs is mostly similar to Hugging Face except that the edges are constructed manually because of the scarcity of publically available APIs.

    \item \textbf{RestBench}\footnote{\href{https://restgpt.github.io/}{https://restgpt.github.io/}}~\cite{song2023restgpt, wu2024can}: A dataset consisting of multiple APIs to address complex real-world user instructions in two scenarios: TMDB movie database and Spotify music player. The TMDB movie database offers RESTful APIs encompassing information about movies, TVs, actors, and images. Spotify Music Player provides API endpoints to retrieve content metadata, receive recommendations, create and manage playlists, and control playback. For RestBench, \cite{song2023restgpt} employed NLP experts to brainstorm instructions for different combinations of APIs and correspondingly annotate the gold API solution path for each instruction. Two additional experts are further employed to thoroughly verify the solvability of each instruction and the correctness of the corresponding solution path. To adapt RestBench into a graph-structured dataset, \cite{wu2024can} treats each API as a unique task node, modeling their relationships through two key dimensions: (1) categorical association and (2) resource dependencies. For instance, APIs offering movie-related functionalities, such as retrieving movie details or recommending films, are grouped under the 'movie' category, while APIs focused on person-related tasks, like searching for actors, are classified under the 'person' category. Additionally, if two APIs share a common parameter (e.g., movie-id), a link is established to represent resource dependency. To further enhance semantic distinction, GPT-4 is prompted to assign a unique name and detailed functional description to each API. 


    \item \textbf{AsyncHow}\footnote{\href{https://github.com/fangru-lin/graph-llm-asynchow-plan}{https://github.com/fangru-lin/graph-llm-asynchow-plan}}~\cite{lin2024graph}: A curated dataset consisting of 1.6K data points for asynchronous planning. Each data point comprises a user instruction specifying tasks with their basic execution constraints, represented by a directed acyclic graph (DAG). In these DAGs, nodes denote actions, and edges represent ordering constraints. Each edge carries a weight indicating the time required to complete the preceding action and transition to the next. Additionally, edges also signify causal links, meaning an action can only proceed if all preceding linked actions are completed. To construct this dataset, we first collected planning tasks from WikiHow~\cite{koupaee2018wikihow}. LLMs were then used for preprocessing, time annotation, and step dependency annotation. Specifically, plans containing optional steps, irrelevant tasks, or those lacking quantifiable duration were filtered out. The GPT-3.5 is used to estimate the time duration for each step, and the GPT -4 is used to annotate step dependencies using the DOT language. To generate natural language questions with execution constraints, ten trivially different but plausible templates were used to paraphrase the graph-structured dot language into human-understandable texts. The optimal time duration for a plan was calculated by determining the longest path within the DAG representation of the workflow.

    

    \item \textbf{EXPLAGRAPHS}\footnote{\href{https://github.com/swarnaHub/ExplaGraphs}{https://github.com/swarnaHub/ExplaGraphs}}~\cite{saha2021explagraphs}: Give the initially collected triplets consisting of belief, argument, and stance, the commonsense explanation graphs are constructed through a generic create-verify-refine iterative framework. Firstly, annotators construct a commonsense-augmented explanation graph that explicitly explains the stance. Each graph comprises 3-8 facts, each of which is a triplet with two concepts as entities connected by their relations. The graphical representation allows us to automatically perform in-browser checks for structural constraints, thereby guaranteeing the structural correctness of the graph. To further ensure the semantic correctness of the constructed graph, annotators reason through the graph to infer the stance based solely on the belief and the explanation graph. Finally, for incorrect graphs, another annotator refines them either by adding a new fact, removing an existing one, or replacing an existing fact.

    \item \textbf{GSM8K}\footnote{\href{https://github.com/openai/grade-school-math}{https://github.com/openai/grade-school-math}}~\cite{cobbe2021training}: The GSM8K dataset is a collection of 8.5K high-quality, linguistically diverse math word problems designed to assess multi-step reasoning for question answering. These grade school-level problems, solvable by a bright middle school student, require between 2 and 8 steps, primarily using basic arithmetic operations ($+, -, \times, \div$) without needing concepts beyond early Algebra. Solutions are presented in natural language to facilitate general applicability, offering insight into the reasoning processes of large language models. This format highlights how models handle structured, step-by-step reasoning in response to real-world math problems.


    \item \textbf{PrOntoQA}\footnote{\href{https://github.com/asaparov/prontoqa}{https://github.com/asaparov/prontoqa}}~\cite{saparov2022language}: PrOntoQA is a question-answering dataset that provides examples featuring chains-of-thought to outline the reasoning needed for correct answers. The sentences are syntactically simple and well-suited for semantic parsing, making it valuable for formal analysis of predicted reasoning chains from large language models like GPT-3.
    
\end{itemize}


\subsubsection{Tools}
\begin{itemize}[leftmargin=*]
    \item \textbf{ToolBench}\footnote{\href{https://github.com/sambanova/toolbench}{https://github.com/sambanova/toolbench}}~\cite{shen2023taskbench}: Recent studies on software tool manipulation with LLMs primarily depend on closed model APIs (e.g., OpenAI), as there remains a significant performance gap between these proprietary models and available open-source LLMs. To investigate the underlying causes of this discrepancy and to advance the capabilities of open-source LLMs—particularly in tool manipulation—a benchmark named ToolBench has been developed. ToolBench includes a range of diverse software tools designed for real-world tasks and provides an accessible infrastructure for directly evaluating each model’s execution success rate.
\end{itemize}