\section{Scientific Graph \texorpdfstring{\emojiscititle}{Scientific Graph}}
\label{sec-sci}
Scientific graphs refer to graph-structured data used in domains such as drug discovery~\cite{wangretrieval,huanginteraction,liu2024moleculargpt} and biomedicine~\cite{yang2024kg, liu2024drak,delile2024graph,jiang2024hykge,byambasuren2019preliminary,wen2023mindmap}, both of which are common application areas for GraphRAG. Therefore, in this section, scientific graphs specifically refer to molecular graphs and medical graphs.

In recent years, significant progress has been made in the development of artificial intelligence for science~\cite{abramson2024accurate,jumper2021highly,thirunavukarasu2023large,madani2023large}. Machine learning (ML) and deep neural network technologies are increasingly driving scientific discovery from experimental data. Notably, generative models such as Large Language Models (LLMs) have achieved remarkable success in working with scientific graph data, including molecular graphs and biomedical graphs. In molecular graphs, for example, atoms serve as nodes, while chemical bonds represent edges, capturing the structure of molecules. AI technologies can handle both prediction and generation tasks on these graphs, driving advancements in fields like drug discovery.

Despite the impressive capabilities of generative models like LLMs, several challenges still hinder their applications to scientific domains. One of the most prominent challenges is the lack of domain-specific expertise. In fields like drug discovery, molecule generation is crucial, yet traditional generative models often struggle with producing incorrect or scientifically invalid structures. In medical question-answering (QA) tasks, incorrect answers, hallucinations, and limited interpretability are frequently encountered. To address these challenges, recent works have proposed leveraging external knowledge databases to enhance generation via GraphRAG. GraphRAG improves accuracy by retrieving relevant scientific graphs from extensive databases to guide the generation or answering process. This approach ensures scientific validity by incorporating known valid graph structures, leverages existing knowledge for practical applications, and accelerates the generation process by narrowing the search space.

\subsection{Application Tasks}

Scientific graphs are beneficial for a wide range of tasks. In this subsection, we will review some representative tasks where scientific graphs can play a significant role. 

\begin{itemize}[leftmargin=*]
\item \textbf{Molecule generation:} Molecule generation refers to the process of creating or designing new molecular structures, often using generative models~\cite{wangretrieval,huanginteraction}. It plays a crucial role in fields like drug discovery. The use of scientific graphs, especially molecular graphs, can enhance the rationality and accuracy of generated molecular structures in molecular generation. Typically, an inquiry such as a molecule is given to retrieve the most relevant molecular structures to guide molecular generation. 

\item \textbf{Molecule property prediction:} Molecule property prediction refers to the use of computational methods to estimate the physical, chemical, or biological properties of molecules based on their structure~\cite{liu2024moleculargpt}. 
It has proven highly effective in accelerating the drug discovery process while significantly reducing associated costs. The use of scientific graphs, especially molecular graphs, can enhance the accuracy of prediction. To achieve this, a query molecule is provided, and similar molecules are identified as demonstrations to improve the prediction.

\item \textbf{Question answering:} Question answering (QA) in the scientific domain refers to the use of computational methods to provide accurate and context-specific answers to scientific questions~\cite{yang2024kg, jiang2024hykge, wen2023mindmap, li2024dalk, jeong2024improving,wu2024medical,soman2024biomedical}. This involves retrieving or generating information from scientific literature, databases, or other resources to address complex, domain-specific queries, such as "After meals, I feel a bit of stomach reflux. What medication should I take for it?" In graghRAG, the scientific literature is usually converted into a knowledge graph to provide a basis for answering questions or to enrich the query.
\end{itemize}


\subsection{ Scientific Graph Construction}
In GraphRAG, the choice and construction of data sources are crucial and typically include both public and private datasets. Public datasets are often derived from widely recognized resources, such as molecular databases like PubChem~\cite{kim2019pubchem}, ChEMBL~\cite{gaulton2012chembl}, and ZINC~\cite{irwin2005zinc}, as well as biomedical literature and data sources like PubMed~\cite{lu2011pubmed} and ClinicalTrials~\cite{zarin2011clinicaltrials}. These datasets provide a broad foundation of information across various domains, offering reliable and authoritative references for the model. 
On the other hand, private datasets contain user-specific information, such as medical records from hospitals or confidential clinical trial data~\cite{wu2024medical}. These datasets are highly confidential and unique, enabling GraphRAG models to offer personalized and proprietary knowledge support. 


For chemistry, molecules can be represented in four main forms: 1D SMILES (Simplified Molecular Input Line Entry System)~\cite{wangretrieval,liu2024moleculargpt}, 2D molecular graphs~\cite{luo2021predicting}, 3D molecular graphs with coordinates~\cite{huanginteraction}, and text captions describing molecular structures~\cite{delile2024graph}.
1D SMILES is a linear string generated through depth-first search (DFS) on the molecular graph, following specific rules.
2D molecular graphs represent atoms as nodes and bonds as edges, visually showing the connectivity of atoms.
3D molecular graphs incorporate spatial coordinates for each atom, reflecting the molecule’s structure in three-dimensional space, which is crucial for tasks such as molecular docking and reaction prediction.
Text captions, on the other hand, provide a natural language description of the molecular structure, which can be used in tasks that involve textual data interpreting chemical structures from text. Scientific graphs can typically be constructed as follows:

\begin{itemize}[leftmargin=*]
\item \textbf{Text-based construction}: Text-based graph construction is the most commonly used method, which can transform textual scientific knowledge into knowledge graphs. \citet{delile2024graph} believe that text captions suffer from issues of information redundancy and imbalance. By constructing text as a knowledge graph, it is possible to rebalance the retrievable information and reduce redundancy.
Building a knowledge graph typically involves two key steps:

\begin{itemize}[leftmargin=*]
    \item {\it Entity Extraction:} This step involves identifying and extracting key entities from the text, such as domain-specific terms (e.g., chemical compounds, genes).

    \item {\it Relationship Extraction:} After identifying the entities, the next step is to extract the relationships between these entities, determining how they are linked in the given context (e.g., "A is related to B"). This step forms the structural backbone of the knowledge graph.
\end{itemize}

\item \textbf{SMILES-based construction}:
Many chemical databases store data in analytical descriptor formats such as SMILES  ~\cite{wang2022retrieval}. To model graphs, SMILES representations need to be transformed into graph structures.
SMILES-based construction utilizes a library such as RDKit~\cite{landrum2013rdkit} to read the SMILES notation, create a molecular object, and extract atomic and bonding information to construct a 2D graph. Each atom in the molecule is represented as a node, and each bond is represented as an edge between nodes. The atoms carry features such as atom type, degree, charge, and aromaticity, while the bonds can include bond type (single, double, etc.) and whether they are part of a ring.

\item \textbf{3D graph construction}:
\citet{huanginteraction} introduce IRDIFF, an interaction-based retrieval-augmented 3D molecular diffusion model designed for target-specific molecule generation. For pretraining, PMINet is utilized to capture interactive structural context information with binding affinity signals, leveraging the PDBbind v2016 dataset. This dataset offers 3D protein structures and a substantial set of experimentally validated protein-ligand complexes. These protein structures are primarily obtained via techniques like X-ray crystallography, nuclear magnetic resonance (NMR), or cryo-electron microscopy, containing detailed atomic coordinates, bond angles, and secondary structure information.
\end{itemize}

\subsection{Retriever}
The retriever is responsible for locating relevant information based on the input query. In GraphRAG, this information typically consists of graph-structured data.  The retriever can be roughly classified as heuristic-based retriever and deep learning-based retriever.
 


\begin{itemize}[leftmargin=*]
    \item \textbf{Heuristic-based retriever:} A heuristic-based retriever employs predefined rules, algorithms, and heuristics to identify and retrieve relevant knowledge from graph-structured data sources. Heuristic-based retrieval can be categorized into several types as below:
    
    \begin{itemize}[leftmargin=*]
        \item \textit{Similarity-based retriever:} \citet{wangretrieval} retrieve exemplar molecules based on their similarity to the input molecule, using cosine similarity as the metric. MindMap~\cite{wen2023mindmap} encodes the entities from the query and the external knowledge graph into dense embeddings using BERT, and then retrieves the entity set with the highest similarity scores.
    
        \item \textit{Matching-based retriever:} A matching-based method provides an alternative approach, enabling LLMs to generate evidence-based responses by leveraging comprehensive private data. Specifically, \citet{wu2024medical} identify the most relevant graph through a top-down matching process. Once the relevant content is identified, the LLM generates an intermediate response with its assistance, enhancing both the transparency and interpretability of the results.

        \item \textit{Knowledge graph-based retriever:} A knowledge graph-based method can effectively identify and retrieve the necessary information to respond to a query. \citet{pelletier2024explainable,li2024dalk} use named entity recognition and relation extraction to connect user queries with relevant entities in the knowledge graph, thereby uncovering interpretable and actionable insights from existing biomedical knowledge. This approach significantly enhances the transparency and utility of predictive models. \citet{delile2024graph} map the text chunks to the knowledge graph, then utilize graph distances to find the chunks most relevant to the user's question. In addition,  this work introduces a scoring metric that balances the data by giving each concept mapped along the shortest path an equal opportunity. This metric prioritizes text chunks based on both their recency and their impact. HyKGE~\cite{jiang2024hykge} first queries the LLM to generate a hypothetical output and extracts entities from both the output and the query. Then, HyKGE retrieves reasoning chains between any two anchor entities in an existing knowledge graph, such as CMeKG~\cite{byambasuren2019preliminary} and CPubMed-KG, and feeds the reasoning chains along with the query into the LLM. KG-Rank~\cite{yang2024kg} identifies entities within the query and retrieves the related triples or sub-graphs from the KG to gather factual information.

        \item \textit{Fusion-based retriever:} \citet{soman2024biomedical} begins by retrieving the relevant node in the knowledge graph based on vector similarity to the query's entity. Then, it retrieves the context triples (Subject, Predicate, Object) linked to this node within the knowledge graph.
    \end{itemize}

\item \textbf{Deep Learning-based Retriever:}
Deep learning-based retrievers can extract relevant knowledge to guide the generation process, such as the generation of molecules or proteins. Specifically, \citet{huanginteraction} uses a pre-trained protein-molecule interaction network
named PMINet to extract interactive structural context information between the target protein and ligands in the reference pool to guide the generation of target-aware ligands. \citet{jeong2024improving}
utilize the off-the-shelf MedCPT retriever, a tool specifically tailored for retrieving documents in response to biomedical queries, capable of retrieving up to ten relevant pieces of evidence for each input. DALK~\cite{li2024dalk} filters out noise and retrieves the most relevant knowledge by utilizing the ranking capabilities of LLMs.
\end{itemize}

\subsection{Organizer}
Basically, there are two types
of the organizer: embedding-based and query-based organizers according to how the retrieved knowledge is utilized.


\begin{itemize}[leftmargin=*]
    \item \textbf{Query-based organizer.} The simplest and most direct organizer is a query-based organizer, which integrates the retrieved information with input queries to generate responses. Specifically, HyKGE~\cite{jiang2024hykge} enhances the reasoning process by incorporating external knowledge into the large language model. In this framework, the retrieved reasoning chains are fed into the LLM alongside the original query. This enables the model to ground its responses in structured, contextually relevant information, improving both the accuracy and depth of the generated output. \citet{wu2024medical} prompt the LLM to answer the question by providing the retrieved entity names and their relationships in a concatenated form. This approach involves retrieving relevant entities and the relationships between them from an external knowledge source and structuring this information as a cohesive input for the LLM. DALK~\cite{li2024dalk} integrates the query and retrieves knowledge and then feeds it into LLMs for reasoning and getting the predicted answer. Similarly, KG-Rank~\cite{yang2024kg} combines the re-ranked triplets with the task prompt and inputs them into LLMs for answer generation. In contrast to the methods mentioned above, \citet{soman2024biomedical} begin with context pruning. Specifically, this approach refines the retrieved context by selecting only the most semantically relevant elements needed to answer the query promptly. The input prompt is then combined with this pruning-aware information, producing an enriched prompt that is fed into the LLM for text generation. \citet{delile2024graph} develop a data rebalancing mechanism to ensure that each entity relevant to a question has an equal opportunity of being represented while also highlighting recent significant discoveries. This rebalanced knowledge is then combined with the query prompt and provided as input to the LLM.

    \item \textbf{Embeding-based organizer.} Embedding-based organizer integrates the retrieved information with input embedding to generate responses. Specifically, \citet{wangretrieval} uses a lightweight, trainable standard cross-attention mechanism to fuse the embedding of the input molecule and the retrieved example molecules. Similarly, \citet{huanginteraction} uses a trainable cross-attention mechanism to fuse the enhanced embeddings of the retrieved example ligands and the generated molecules.  

\end{itemize}
\subsection{Generator}

The generator is a core component of the GraphRAG model and is responsible for producing the final output by integrating retrieved evidence with the input data.
Generators can be broadly classified into three categories according to the type of generated models they use: transformer-based generators, diffusion model-based generators, and large language models-based generators. 

\begin{itemize}[leftmargin=*]
    \item \textbf{Transformer-based generator:} RetMol~\cite{wangretrieval} utilizes the Megatron version of the molecule generative model Chemformer for drug discovery. Specifically,  the Chemformer model is a Transformer-based model that can be efficiently applied to tasks in chemistry.

    \item \textbf{Diffusion-based generator:} \citet{huanginteraction} introduce a novel interaction-based retrieval-augmented diffusion model (IRDIFF) for structure-based drug design. Specifically, IRDIFF is able to generate molecules that bind strongly to the target pocket by utilizing protein-molecule interaction data between reference proteins and the target protein to guide the diffusion model.

    \item \textbf{LLM-based generator:} Some approaches leverage large language models, such as LLaMA2, LLaMA3, GPT-4, and Gemini, etc~\cite{wu2024medical,jeong2024improving,pelletier2024explainable,liu2024moleculargpt,li2024dalk,soman2024biomedical}. For instance, MedGraphRAG~\cite{wu2024medical} utilizes GraphRAG to improve the answering capabilities of models such as LLaMA2, LLaMA3, Gemini, and GPT-4 for medical question answering. MolecularGPT~\cite{liu2024moleculargpt} utilizes GraphRAG to improve GPT-3's predictive capabilities for molecular property prediction. DALK~\cite{li2024dalk} employs GraphRAG to boost GPT-3.5-turbo's ability to answer questions related to Alzheimer’s Disease. HyKGE~\cite{jiang2024hykge} utilizes GraphRAG to enhance the medical question-answering capabilities of GPT-3.5 and Baichuan13B.
\end{itemize}

\subsection{Resources and Tools}
In this section, we provide an overview of common data sources and tools utilized in graph RAG systems within the scientific domain, along with a brief description of each project.
\subsubsection{Data Resources}
The public datasets are commonly from well-known resources, such as molecular databases: 

\begin{itemize}[leftmargin=*]
\item \textbf{PubChem}~\cite{kim2019pubchem}: PubChem encompasses a wide range of chemical data, including 2D and 3D structures, chemical and physical properties, bioactivity, pharmacology, toxicology, drug targets, metabolism, safety guidelines, associated patents, and scientific literature. Most of its entries pertain to small molecules, with a primary emphasis on those containing fewer than 100 atoms and 1,000 bonds.

\item \textbf{ChEMBL}~\cite{gaulton2012chembl}: It is an openly accessible database containing detailed information on drugs, drug-like small molecules, and their bioactivity. This curated resource stands out for its comprehensive coverage of the drug discovery process, encompassing data on more than 2.2 million compounds and over 18 million records documenting their effects on biological systems.
ChEMBL provides insights into the interactions between small molecules and their protein targets, along with data on how these compounds influence cellular and organismal functions. It also includes information on ADMET (absorption, distribution, metabolism, excretion, and toxicity) profiles. The database stores two-dimensional structures, calculated molecular properties (such as logP, molecular weight, and Lipinski’s Rule of Five parameters), and bioactivity data like binding affinities and pharmacological effects.

\item \textbf{ZINC}~\citep{irwin2005zinc}: The ZINC dataset is a curated collection of commercially available chemical compounds designed specifically for virtual screening purposes. It offers over 230 million purchasable compounds in 3D formats that are ready for docking, as well as more than 750 million compounds available for analog searches. Each molecule is adjusted to biologically relevant protonation states and is annotated with properties such as molecular weight, calculated LogP, and rotatable bonds. The library includes vendor and purchasing details, making it compatible with several widely used docking software programs. Compounds are provided in multiple protonation states and tautomeric forms within certain constraints, and some formats even offer multiple conformations per molecule. The ZINC database is available for free download~\footnote{\href{http://zinc.docking.org}{http://zinc.docking.org}} in multiple common file formats, including SMILES, mol2, 3D SDF, and DOCK flexibase.
\end{itemize}

There are also biomedical data sources as below:
\begin{itemize}[leftmargin=*]
    \item \textbf{PubMed}~\cite{lu2011pubmed}: PubMed is a freely accessible database that primarily houses the MEDLINE collection, containing references and abstracts in life sciences and biomedicine. Managed by the United States National Library of Medicine (NLM) within the National Institutes of Health, PubMed is part of the Entrez retrieval system. As of May 23, 2023, PubMed contains over 35 million citations and abstracts, with records dating back to 1966 and selectively to 1865, and a few even to 1809. On this date, approximately 24.6 million records include abstracts, and 26.8 million provide links to full-text articles, with around 10.9 million available freely. In the last decade (up to December 31, 2019), PubMed added nearly one million new records annually on average.
    
    \item \textbf{ClinicalTrials}~\cite{zarin2011clinicaltrials}: ClinicalTrials is a global registry and database that provides information on clinical studies funded by both private and public sources. Managed by the U.S. National Library of Medicine, this resource includes a summary of each study's protocol, and for some studies, results are available in a tabular format. Users can search studies by criteria such as study status, condition or disease, country, and other keywords. Continuously updated, the database now includes over 300,000 research studies conducted across all U.S. states and in more than 200 countries worldwide.

    \item  \textbf{Open-source medical KGs}: CMeKG (Clinical Medicine Knowledge Graph)~\footnote{\href{https://cmekg.pcl.ac.cn/}{https://cmekg.pcl.ac.cn/}}, CPubMed-KG (Large-scale Chinese Open Medical  Knowledge Graph)~\footnote{\href{https://cpubmed.openi.org.cn/graph/wiki}{https://cpubmed.openi.org.cn/graph/wiki}} and Disease-KG (Chinese disease Knowledge Graph)~\footnote{\href{https://github.com/nuolade/disease-kb}{https://github.com/nuolade/disease-kb}} are open-source medical knowledge graphs that consolidate a vast amount of medical text data, covering areas such as diseases, medications, symptoms, and diagnostic treatments. The combined knowledge graph includes 1,288,721 entities and 3,569,427 relations.
\end{itemize}

\subsubsection{Tools}
\begin{itemize}[leftmargin=*]
    \item \textbf{RDKit}~\cite{landrum2013rdkit}: RDKit is open-source toolkit for cheminformatics. RDKit has several key features: it can process chemical structures by reading and writing various file formats, such as SMILES, InChI, and Mol files. It generates multiple types of molecular fingerprints, enabling chemical structure comparison and similarity searches. RDKit also provides algorithms for calculating molecular similarity and supports the representation and processing of chemical reactions, including the identification of reactants and products. Although it does not offer molecular docking capabilities on its own, RDKit can be integrated with other docking tools. Additionally, RDKit supports machine learning algorithms, allowing for pattern recognition in chemical data and the construction of predictive models.
    \item \textbf{CADRO}: The Common Alzheimer’s and Related Dementias Research Ontology (CADRO)~\footnote{\href{https://iadrp.nia.nih.gov/about/cadro}{https://iadrp.nia.nih.gov/about/cadro}} is employed to extract a subset of Alzheimer’s disease (AD)-related samples from the medical QA datasets for evaluation. CADRO organizes terms into a three-tiered classification system with eight main categories and multiple subcategories focused on AD and related dementias, containing frequently used terminologies or keywords in the field. From CADRO, users obtain a list of AD-related keywords most relevant to the medical QA datasets.

\end{itemize}
