\section{Related Work}

\subsection{Multi-Agent Debate}
Multi-Agent Debate can be seen as an extension of chain-of-thought (CoT) reasoning in LLMs. \citet{CoT} tried to elicit complex multi-step reasoning in LLMs using chain-of-thought prompting, finding that having the model reason step-by-step through a difficult problem led to significant gains on logical reasoning tasks when compared to zero-shot LLM performance. Methods such as self-refine \citep{madaan2023selfrefine} built upon CoT by having language models repeatedly provide feedback for their own outputs, which was then used to iteratively improve LLM generations, a technique that improved generation quality over a variety of tasks.

Many recent works have extended this latter method to a multi-agent debate setting, with the aim of further improving model factuality and reasoning capabilities. By having multiple instances of an LLM play different roles in a debate over how to best answer a question, such methods further improve over the results achieved by self-refine and similar methods. \citet{cohen2023lm} uses an instance of ChatGPT to act as a ``cross-examiner'' of another ChatGPT instance's claims by repeatedly asking follow-up questions, motivated by the idea that a language model is more likely to generate inconsistent outputs when it is hallucinating. They find that cross-examination leads to significant improvements over CoT on factuality benchmarks. \citet{chan2023chateval}, similarly motivated by group brainstorming discussions, introduce a multi-agent referee team (ChatEval) to evaluate models on natural language generation tasks. Finally, \citet{reconcile} find that debate between multiple LLMs outperforms both single- and multi-agent debate that only leverage instances of a single LLM.

\subsection{Red Teaming LLMs}
The emergent capabilities of LLMs have also led to concerns about irresponsible usage and the potential for harmful behavior, such as generating offensive or toxic outputs \citep{gehman2020}. To address such safety concerns in dialog settings, during the training and instruction fine-tuning stage, the model is also trained to be \textit{aligned} to ethical standards and responsible output, where it recognizes potentially harmful conversation and refuse to reply harmful and sensitive content. However, recent work has discovered that even fine-tuned models remain sensitive to adversarial prompts.

\citet{ganguli2022red} attempts to red team LLMs of different scales and model types with human crowdworkers, observing that LLMs not explicitly trained to minimize harmlessness are still prone to attacks regardless of scale, and released the full dataset of attempted attacks with detailed experiment methodology. \citet{perez2022red} explores red teaming a target language model with another language model in a dialog setting, attempting to uncover weaknesses and harms of the target LM automatically. Similarly, \citet{shah2023scalable} automatically red-team models by searching for personas that might generate harmful continuations to a given prompt and adding this persona to an adversarial prompt.

\citet{wei2023jailbroken} find that state of the art LLMs are prone to adversarial attacks through prompt construction. \citet{zou2023universal_adv_attacks}~further develops a universal adversarial attack prompt generation framework by training an attack suffix on multiple prompts and models. A model with safety alignment can be also further tuned on uncensored and unfiltered data to unlearn safety concerns and generate harmful output at high response rate and high generation quality~\cite{uncensored}, with potentially very simple LoRA fine-tuning and a low budget~\cite{uncensored2023lora}. In Section~\ref{sec:method} we discuss our adversarial prompt design to attack different LLM agents, and compare output toxicity of model variants with different training and fine-tuning approaches. This line of research calls for a deeper analysis of model reliability and approaches to ensure model harmlessness at training and inference time.

% \zhen{Do we add a short paragraph for evaluation of output toxicity?} <- idt we need to, they mostly just use a similar model or human eval