\section{Introduction}
\label{sec:introduction}

Large Language Models (LLMs) have recently demonstrated strong reasoning capabilities, achieving impressive performance on tasks such as mathematics, programming, and tool use~\cite{guo2025deepseek,yang2025qwen3,liu2025deepseek}. Reinforcement Learning with Verifiable Rewards (RLVR) plays a crucial role in enabling these capabilities by leveraging tasks with automatically checkable outcomes to provide reliable supervision for scaling reasoning. To further enhance LLM performance, a growing line of work~\cite{wang2022self, xiong2025llava,wang2025llava,zheng2025parallel} studies test-time scaling strategies to further improve the reasoning ability of LLMs. Among these approaches, collaborative reasoning~\cite{du2023improving,liang2024encouraging} through Multi-Agent Debate (MAD) has emerged as a promising paradigm: multiple LLM agents propose solutions to a shared question and iteratively update their answers in response to their peers~\cite{choi2025debate,yi2025debate}. 
% This process mirrors human deliberation, where groups challenge assumptions and aggregate diverse perspectives to solve difficult problems~\cite{toktobekov2025llm}.

Despite this promise, effective methodologies for preparing reasoning models for MAD interaction remain underexplored. Existing RLVR methods typically train LLMs to reason and then solve problems within single trajectories, failing to explicitly prepare them for collaborative environments where they must process diverse rationales. This mismatch between training and inference can limit LLM effectiveness in MAD settings~\cite{choi2025debate,kumaran2025overconfidence,li2025off}. Furthermore, recent attempts to train debate behaviors typically optimize the entire multi-agent systems, significantly increasing both training costs and deployment complexity~\cite{liao2025marft,liu2025llm,marti2025,li2025advancing}. These limitations highlight the need for a framework that produces a \emph{single} LLM capable of both independent problem-solving and productive collaboration in MAD.
% Moreover, it is unclear whether performance gains stem from genuine debate-driven revision or simply from ensembling effects like majority voting~\cite{choi2025debate}, particularly when peers present confident but conflicting trajectories~\cite{kumaran2025overconfidence,li2025off}.

In this work, we develop a theoretical analysis that clarifies why debate can help and when its benefits saturate. Inspired by the Dirichlet Compound Multinomial (DCM) framework of \citet{choi2025debate}, we model multi-agent debate as Bayesian belief updating and recover their key implication that standard MAD induces a martingale over each agent’s belief in the correct answer. We then extend this framework by explicitly disentangling the contributions of majority voting and agents’ \emph{private critique} in MAD, and show that improving agents’ private critique can improve overall MAD performance. Building on this insight, we propose \emph{Self-Debate Reinforcement Learning} (\SDRL{}), a learning paradigm that enables a single model to learn from its own reasoning conflicts, effectively preparing it for both standalone problem-solving and multi-agent interactions. Given a prompt, \SDRL{} first samples multiple candidate solutions from the current policy and evaluates them using verifiable rewards. \SDRL{} then constructs debate pairs by selecting different candidates from these initial solutions, forcing the model to confront divergent reasoning trajectories. Conditioned on a debate pair, the model generates second-round responses that deliberate over both candidates to produce a final answer. Finally, \SDRL{} jointly optimizes both the initial and second-round responses under verifiable rewards. This joint objective encourages the model to produce accurate first-pass solutions while also learning when and how to revise its reasoning during debate-style interaction, enabling a single trained model to serve as a highly competent agent within MAD.

Overall, our \textbf{contributions} can be summarized as follows:
\begin{enumerate}[itemsep=6pt, parsep=0pt, topsep=1pt]
    \item We introduce a theoretical framework that disentangles the contributions of debate and majority voting in the MAD paradigm, and we identify improving agents’ private critique as a key driver of debate gains.
    \item We propose \emph{Self-Debate Reinforcement Learning} (\SDRL{}), a training framework that equips a \emph{single} reasoning model with both independent problem-solving ability and collaborative debate skills by jointly optimizing both objectives.
    \item Extensive experiments across multiple reasoning benchmarks demonstrate that \SDRL{} consistently enhances multi-agent debate performance while simultaneously strengthening single-agent accuracy.
\end{enumerate}
