\section{Methodology}
\label{methodology}

We propose Self-Debate Reinforcement Learning (\SDRL{}), an online reinforcement learning framework that trains a \emph{single} policy to improve both (i) single-agent reasoning and (ii) \emph{private critique} required by Multi-Agent Debate (MAD). Section~\ref{subsec:single_agent_reasoning} introduces how \SDRL{} uses verifiable rewards to train the model for single-agent reasoning. Section~\ref{subsec:debate_ability} introduces how \SDRL{} equips a single model with the private critique ability to discriminate between different opinions during debate interactions.

\subsection{Single-agent reasoning}
\label{subsec:single_agent_reasoning}

To improve the model’s reasoning ability in the single-agent setting, \SDRL{} follows the GRPO framework~\cite{shao2024deepseekmath} and optimizes the policy using verifiable rewards. For each prompt $q$, \SDRL{} samples $n$ independent responses  $\{o_i\}_{i=1}^n \sim \pi_\theta(\cdot \mid q)$ from the current policy and assigns a sparse outcome reward $r_j \in \{+1,-1\}$ based on the correctness of the final answer. We then compute advantages for each response using Eq.~\ref{eq:advantage}. To prepare candidate responses for debate training, we follow DAPO~\cite{yu2025dapo} to oversample prompts and filter out those whose responses yield zero advantages. This ensures that each prompt has responses corresponding to different final answers, capturing diverse opinions and reasoning trajectories.

\begin{algorithm}[t]
\footnotesize
\caption{Self-Debate Reinforcement Learning (\SDRL{})}
\label{alg:sdrl}
\vspace{-0.4em}
\begin{algorithmic}[1]
\Require Policy $\pi_\theta$, prompt set $\mathcal{D}=\{q_i\}_{i=1}^N$, initial rollouts $n$, debate rollouts $n_d$, training steps $K$
\Ensure Updated policy $\pi_{\theta_{\mathrm{updated}}}$

\For{$t=1,\dots,K$}
  \State Sample mini-batch $\mathbf{q}\subseteq\mathcal{D}$ and initialize $\mathbf{B}\leftarrow\emptyset$
  \For{each $q\in\mathbf{q}$}
    \State Sample initial rollouts $\{o_i\}_{i=1}^n\sim\pi_\theta(\cdot\mid q)$ and compute advantages $\{A_i\}_{i=1}^n$
    \State $\mathbf{B}\leftarrow \mathbf{B}\cup\{(q,\{o_i\}_{i=1}^n,\{A_i\}_{i=1}^n)\}$
    \State Select debate pair $(o^1,o^2)$ from $\{o_i\}_{i=1}^n$ and construct debate prompt $q_d$
    \State Sample debate rollouts $\{o_j^d\}_{j=1}^{n_d}\sim\pi_\theta(\cdot\mid q_d)$ and compute advantages $\{A_j^d\}_{j=1}^{n_d}$
    \State $\mathbf{B}\leftarrow \mathbf{B}\cup\{(q_d,\{o_j^d\}_{j=1}^{n_d},\{A_j^d\}_{j=1}^{n_d})\}$
  \EndFor
  \State Update $\pi_\theta$ using the RL optimizer on $\mathbf{B}$
\EndFor
\State \Return $\pi_{\theta_{\mathrm{updated}}}$
\end{algorithmic}
\vspace{-0.3em}
\end{algorithm}

\subsection{Debate training}
\label{subsec:debate_ability}

To improve the model's private critique ability, \SDRL{} constructs debate contexts that expose the policy to conflicting reasoning trajectories. Producing a correct final answer in these contexts requires the model to exercise private critique by distinguishing reliable reasoning from flawed trajectories. Given the initial rollout set for a prompt $q$, we construct a debate pair by selecting two responses from the candidate response pool, which is formed from the first-round responses generated for single-agent reasoning. Selecting two responses to form a debate pair is a computationally efficient design choice that induces the fundamental private critique behavior and generalizes to settings with more candidate responses.

\textbf{Debate pair construction.}
Let $\mathcal{O}(q)=\{o_i\}_{i=1}^n$ denote the initial rollouts, which we use as the candidate pool, and let $a(o_i)$ be the extracted final answer of rollout $o_i$.
\SDRL{} constructs a debate pair $\mathcal{P}(o^1, o^2)$ by selecting two candidates from $\mathcal{O}(q)$ using one of two pairing rules:
\begin{enumerate}
    \item \emph{Random pairing}. It samples two rollouts uniformly from $\mathcal{O}(q)$.
    This induces a broad distribution of pair diversity.
    Some pairs exhibit genuine disagreement, while others share the same final answer but differ in their reasoning trajectories, which can provide useful training signals for confirmation rather than unconditional revision.
    \item \emph{Frequency-based pairing}. It first identifies the most common answer $a_1$ and the second most common answer $a_2$ in $\{a(o_i)\}_{i=1}^n$.
    This rule more consistently exposes the model to the dominant competing beliefs expressed by its current policy, yielding sharper disagreement instances and therefore requiring stronger private critique ability.
\end{enumerate}
 We evaluate both constructions and use the same downstream prompting and optimization for either choice. 

\textbf{Debate prompt formulation.}
Given a selected pair $\mathcal{P}(o^1, o^2)$, we build a debate prompt $q_d$ by serializing the two candidate responses into a two-turn conversation, and then prompt the model to deliberate over both responses and produce a final answer. The detailed conversation format and prompt template are shown in the Appendix. For \emph{frequency-based pairing}, we randomize the order of $a_1$ and $a_2$ to prevent positional heuristics. Since the most common answer $a_1$ typically has a higher probability of being correct, always placing $a_1$ as the first response in $q_d$ could encourage the model to select the first-position answer rather than perform critical analysis of the underlying reasoning trajectories.
