\section{Introduction}

Large language model (LLM) agents are moving from passive text generation to interactive systems that reason, call tools, maintain state, and delegate subtasks \cite{xu2026theagentcompany}. Multi-agent LLM systems decompose complex workflows into multiple specialized, interacting agents, often combining role-specific reasoning, tool use, memory, human oversight, routing, and guardrail components~\cite{wu2023autogenenablingnextgenllm}.

This decomposition is attractive because it promises modularity, specialization, and auditable division of responsibility. A finance assistant, for example, can route a transfer request through separate checks before a constrained decision engine approves or rejects the action.

The same modularity changes the security problem. In a single-agent setting, evaluation often asks whether the agent follows a malicious instruction, resists prompt injection, or avoids an unsafe tool call \cite{ruan2024identifying, liu2024formalizing}. In a multi-agent setting, the more important question is how failures propagate. A locally plausible change (e.g. a modified account identifier, downgraded risk score, biased shared summary, or delayed memory trigger) may look bounded where it is inserted. After routing, evidence reuse, inter-agent agreement, tool side effects, veto logic, and final aggregation, the same perturbation can become a wrong transfer approval, missed compliance violation, corrupted portfolio recommendation, or unsafe customer-facing action. The security object is therefore the full execution trace.
% , not only the input prompt or final answer.

This risk is not hypothetical. A recent incident involving an AI coding agent reportedly began with a staging-environment credential mismatch and ended with deletion of production data and backups through a single API mutation \citep{jer2026}. This was not a standard jailbreak. It was an orchestration failure: a locally understandable action, broad tool authority, weak confirmation, and stateful infrastructure interacted to produce irreversible harm. Similar dynamics arise when one agent's output is treated as evidence by others, shared context makes independent agents agree in the wrong direction, or memory carries a perturbation into future decisions.

Existing agent-security benchmarks have moved beyond static refusal tests. AgentDojo, AgentHarm, Agent Security Bench, SEC-bench, and SafePro evaluate prompt injection, tool use, harmful requests, software-security tasks, and professional-domain safety \cite{debenedetti2024agentdojo, andriushchenko2025agentharm, zhang2025agent, lee2026secbench, zhou2026safepro}. Multi-agent and persistence benchmarks such as TAMAS, Who's the Mole?, and memory-poisoning studies examine collusion, malicious agents, intention hiding, and persistent state corruption \citep{kavathekar2025tamas,xie2025s,sunil2026memory}. These works are important, but they mainly measure attack success, blocking, task completion, or final harmfulness. They do not directly measure how harm spreads from targeted components to non-targeted components across a trace. This matters because the most successful attack, the most harmful attack, and the most amplified attack need not be the same.

We introduce \proposed, a trace-first methodology and framework for studying local-to-global harm amplification in multi-agent LLM systems. Rather than treating compromise as a single malicious prompt or unsafe tool call, \proposed~evaluates whether bounded perturbations to agents, shared context, memory, or intermediate observations are amplified by orchestration. For each query, \proposed~compares paired clean and perturbed executions under the same database seed and records router decisions, specialist outputs, tool calls, memory reads and writes, guard events, oracle logs, final decisions, latency, and token cost. This separates three questions often conflated in agent security: whether an attack bypassed defenses, how much malicious impact it produced, and how far harm propagated beyond the targeted component.

The central metric is harm amplification, defined as the ratio between global trace harm and local targeted harm. Local harm measures the deviation contributed by attacked agents or corrupted channels; global harm measures the deviation accumulated over all participating agents. A high amplification factor indicates that the architecture converts a bounded local perturbation into broader system-level damage. We report this with attack success rate, safe and malicious impact, stealth, benign utility, latency, and normalized token cost, exposing security-utility trade-offs.
% that ASR alone hides.

We study four vulnerability regimes: single-specialist compromise, multi-agent collusion, shared-context failure, and temporal or memory-persistent failure. These regimes test whether harm arises from one perturbed role, mutually reinforcing deviations, biased shared evidence, or delayed stateful triggers. They expose different risks: single-specialist compromise gives the clearest amplification signal, shared-context failure yields the highest attack success, and temporal persistence produces the largest malicious impact. We instantiate \proposed~in a finance-oriented seven-agent system with a ReAct-style~\cite{yao2022react} router, simulated side effects, resettable state, and a deterministic decision gate.

Our contributions are:
\begin{enumerate}[nosep]
    \item We formulate local-to-global harm amplification as a multi-agent security failure mode.
    \item We define paired-trace metrics for local/global harm, amplification, attack success, impact, stealth, benign utility, latency, and cost.
    \item We implement a configurable HARP evaluation harness for specialist compromise, collusion, shared-context corruption, and temporal or memory-persistent attacks.
    \item We characterize four vulnerability regimes across twelve scenarios and five defense settings.
    \item We instantiate \textsc{IntegrityGuard} as a reference trace-level defense and analyze its security-utility-cost trade-offs.
\end{enumerate}

