% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
\input{commands}

% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
\usepackage{color}
\renewcommand\UrlFont{\color{blue}\rmfamily}
% \urlstyle{rm}
%
\begin{document}
%
\title{Generalized Information Gathering Under Dynamics Uncertainty}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Fernando Palafox\inst{1}\orcidID{0009-0005-0836-4663} \and
Jingqi Li\inst{1}\orcidID{0000-0002-3731-3807} \and
Jesse Milzman\inst{2}\orcidID{0000-0003-4937-8912} \and
David Fridovich-Keil \inst{1}\orcidID{0000-0002-5866-6441}}
%
\authorrunning{F. Palafox et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{University of Texas at Austin, Texas, USA\\ \email{\{fernandpalafox,dfk\}@utexas.edu, jingqi.li@austin.utexas.edu} \and
DEVCOM Army Research Laboratory, New York, USA \\
\email{jesse.m.milzman.civ@army.mil}}
%
\maketitle              % typeset the header of the contribution
%

%===============================================================================

\begin{abstract}
    An agent operating in an unknown dynamical system must learn its dynamics from observations. 
    Active information gathering accelerates this learning, but existing methods derive bespoke costs for specific modeling choices: dynamics models, belief update procedures, observation models, and planners. 
    We present a unifying framework that decouples these choices from the information-gathering cost by explicitly exposing the causal dependencies between parameters, beliefs, and controls. 
    Using this framework, we derive a general information-gathering cost based on Massey's directed information \cite{massey1990causality} that assumes only Markov dynamics with additive noise and is otherwise agnostic to modeling choices. 
    We prove that the mutual information cost used in existing literature is a special case of our cost. 
    Then, we leverage our framework to establish an explicit connection between the mutual information cost and information gain in linearized Bayesian estimation, thereby providing theoretical justification for mutual information-based active learning approaches. 
    Finally, we illustrate the practical utility of our framework through experiments spanning linear, nonlinear, and multi-agent systems.
    \keywords{Information gathering  \and Dynamics uncertainty \and Sequential decision making}
\end{abstract}

\input{intro}

\input{related}

\input{problem}

\input{experiments}

\input{conclusion}

\begin{credits}
\subsubsection{\ackname} We would like to thank Brett Barkley for formatting advice. This research was sponsored by the Army Research Laboratory under cooperative agreement number W911NF-25-2-0021, and by the National Science Foundation under grant number 2409535.

\end{credits}

\bibliographystyle{splncs04}
\bibliography{example}  % .bib

\end{document}
