\section{Related Work}
\label{sec:related}

\textbf{Information Gathering Under Dynamics Uncertainty.}
The problem of selecting actions that lead towards informative observations is typically formalized by defining a distribution (referred to as ``belief'') over the unknown dynamics parameters and maximizing Shannon's mutual information~\cite{shannon1948mathematical,cover1999elements} between parameters and observations, with abundant literature in the areas of Bayesian experimental design~\cite{rainforth2024modern} and active learning~\cite{settles2009active,cohn1994improving,zhan2022comparative}.
These approaches address which observations are informative, and they often assume the ability to directly select or sample observations. 
In contrast, we focus on embodied agents operating in dynamical systems where observations cannot be chosen directly but emerge from the system's state evolution. Therefore, the agents must plan control sequences that steer the system through state space regions that yield informative observations.

Approaches to this problem have modeled the unknown dynamics with Gaussian processes~\cite{sukhija2023optimistic, buisson2020actively, krause2007nonmyopic, krause2008near, zimmer2018safe}, Koopman operators~\cite{abraham2019active}, physics-based models~\cite{vantilborgh2025dual}, and neural networks~\cite{davydov2024first, lew2022safe, palafox2025info}.
Unlike these existing works, which derive bespoke information-gathering costs tailored to specific dynamics models or belief update procedures, our framework requires only the minimal structural assumption of Markov dynamics with additive noise.
We also make no assumptions about the specific dynamics model type or belief updating procedure, e.g., a Bayesian filter.
To this end, we derive a general information-gathering cost based on directed information~\cite{massey1990causality}, and in Theorem~\ref{thm:mi_special_case} prove that mutual information, the cost most commonly used in the literature, is a special case of our formulation.

\textbf{Belief-Space Planning and Dual Control.}
Closely related to our work is the literature on belief-space planning, partially observable Markov decision processes (POMDPs)~\cite{kaelbling1998planning, platt2010belief, van2012motion, van2016motion, patil2015scaling}, and dual control~\cite{feldbaum1960dual,mesbah2018stochastic}.
These approaches primarily address \emph{state} uncertainty, whereas we focus on \emph{dynamics} uncertainty.
The theoretical difficulty of belief-space planning is well-documented: the nonlinearity of Bayesian belief updates makes exact solutions intractable even for simple systems~\cite{klenske2016dual, bar1974dual, wittenmark1995adaptive}.

We reference the literature on belief-space planning because it faces the same computational difficulties as us: uncertainty propagation is challenging, and existing approaches derive information gathering solutions specific to particular dynamics models and belief updating procedures.
Our framework addresses this by explicitly exposing causal dependencies between beliefs, controls, and observations, allowing us to derive a general information-gathering cost that can be instantiated for different dynamics models and belief updating procedures without requiring problem-specific derivations.

\textbf{Multi-Agent Information Gathering.}
Our framework naturally extends to information gathering for a single agent operating within a multi-agent environment.
The problem of uncertainty in multi-agent interactions is explored in the literature on Bayesian games~\cite{harsanyi1967games,osborne2004introduction,shoham2008multiagent}.
Most of this work focuses on optimal decision-making under fixed uncertainty; few works directly examine how to actively \emph{reduce} that uncertainty.
An exception is the literature on deception~\cite{hespanha2000deception, rostobaya2023deception, xu2016modeling, fuchs2012sequential, vurankaya2025deceptive, palafox2024smooth}, which examines how agents strategically manipulate opponents' beliefs in adversarial settings. 
These works focus on controlling what others learn about the ego agent, whereas we focus on how the ego agent can actively learn about others. 
Additionally, we address continuous-state, continuous-action multi-agent dynamical systems with explicit dynamics parameter learning.

In multi-agent robotic applications, information-gathering actions have been explored in autonomous driving~\cite{sadigh2016information, hu2024active, knaup2024active, knaup2025dual, gadginmath2025active, wang2023active, sagheb2025unified}, drone racing~\cite{schwarting2021stochastic}, and pursuit-evasion games~\cite{krusniak2025online}.
These methods build upon belief-space planning for POMDPs~\cite{kaelbling1998planning, platt2010belief, van2012motion, van2016motion, patil2015scaling, gmytrasiewicz2004interactive}, where agents reason about how uncertainty will evolve to select controls that reduce it~\cite{taylor2021active}.
In this work, we consider scenarios where an ego agent actively reduces uncertainty about other agents' parameters. 
Our contribution in the multi-agent setting is demonstrating that our general framework applies directly to multi-agent settings without requiring multi-agent-specific derivations.