\section{Limitations and Future Work}
\label{sec:limitations}

\textbf{Compute and sample efficiency.} \abbrev{} is compute-intensive: each 5-round run requires 80 RL trainings per seed, totaling roughly 40 GPU-hours per environment in our setup. LLM inference is comparatively small (36 requests per debate round; Appendix~\ref{app:compute_budget}), while wall-clock time is dominated by simulator training. We reduce simulator load by skipping thesis training and parallelizing across GPUs, but scaling to larger design spaces will require more sample-efficient evaluation via early stopping, learned surrogates, or shared policy initialization.

\textbf{Simulator dependence and sim-to-real.} All experiments are conducted in simulation using Brax. Learned rewards and morphologies may exploit simulator artifacts and may not transfer to real robots without additional constraints. Extending \abbrev{} to sim-to-real settings will require robustness objectives (e.g., domain randomization), manufacturability constraints, and hardware-in-the-loop evaluation.

\textbf{Scope and design space.} We demonstrate \abbrev{}'s effectiveness on five MuJoCo locomotion tasks using 3 search seeds and 5 final evaluation runs. Manipulation tasks and integration with quality-diversity methods (e.g., MAP-Elites) are natural extensions that could further characterize when debate-driven co-design is most effective. Our parametric design space (fixed XML template with editable parameters) ensures validity and stable training, although exploring topology changes with stronger geometry validators is a promising direction for future work.

\textbf{Proprietary LLM dependence.} Our main experiments use GPT-5.2. Open-weight DeepSeek runs remain above the Default baseline on Ant and Swimmer (Appendix~\ref{app:open_weight_backbones}), but do not match GPT-5.2. API behavior can also shift between model versions, so we report prompts and exact model identifiers for the main experiments.

\textbf{Benchmark familiarity.} MuJoCo locomotion tasks are widely documented, so LLM backbones may have seen related XMLs, reward code, or design heuristics during pretraining. This caveat tempers novelty and out-of-distribution claims, although the within-protocol co-design interaction does not depend on novelty alone.

\textbf{Single-metric archive selection.} The judge panel provides multi-objective feedback during exploration, but the archive selects candidates using a single scalar metric (cumulative distance from origin). The two operate at different stages: judges steer what to change next round, and the metric decides which candidate to keep. The ablation confirms that judges improve Pareto hypervolume even though selection is scalar (Figure~\ref{fig:ablation_and_diversity_all}). Reconciling multi-objective feedback with multi-objective selection (e.g., Pareto archives), and selecting judges per-environment based on preliminary evaluation (adaptive panel), are concrete directions for future work.

\textbf{Comparison scope.} We position \abbrev{} against LLM-based morphology and reward methods, including RoboMorph for morphology-only search, Eureka for reward-only search, and RoboMoRe for co-design, as well as black-box morphology optimization. The empirical baseline suite focuses on methods that can be evaluated under the same fixed-topology, per-candidate-RL protocol as \abbrev{}. The claim is therefore scoped to joint morphology--reward co-design under this protocol, not strict superiority over all robot co-design formulations.
