\section{Related Work}


\textbf{Knowledge Graph Error Detection: } 
Knowledge graph error detection~\cite{survey} includes methods based on explicit and implicit evidence.

\textbf{Explicit Evidence :} These methods evaluate the credibility of triples using direct evidence from the graph, such as paths and subgraphs. For example:
%
Shi et al.~\cite{shi} used graph traversal to extract meta-paths and calculate path weights.
Lin et al.~\cite{lin} applied graph pattern mining with metrics like support and confidence. However, these methods may struggle with incomplete knowledge graphs and underutilize contextual information.

\textbf{Implicit Evidence :} These methods use embedding models to map entities and relations into vector spaces for credibility evaluation. 
%
CKRL~\cite{CKRL} optimized triple credibility by considering local and global factors during embedding learning.
KGTtm~\cite{kgttm} combined random walks and embeddings, using MLP for scoring. Recent methods also use pre-trained language models and contrastive learning:
KG-BERT~\cite{kg-bert} enriches semantic representations with pre-trained models.
SeSICL~\cite{sesicl}, StAR~\cite{star}, and CCA~\cite{cca} align textual and structural representations via contrastive learning. These methods improve performance but rely on fixed graph structures, limiting adaptability to new or unseen structures.


\noindent\textbf{Multiple LLM-based Agent System: } 
Multi-Agent systems such as CAMEL
~\cite{camel}, have gained significant attention for simulating complex interactions among intelligent agents. These systems coordinate multiple LLM agents to tackle complex tasks, particularly in NLP evaluation.
% 
For example, ChatEval \cite{chateval} uses a multi-agent jury to explore the impact of communication strategies on evaluating open-ended questions and traditional NLG tasks, while MATEval \cite{mateval} involves agents collaborating to evaluate story texts, enhancing the evaluation process through multi-agent interaction.