In this work, we addressed the limited semantic modeling capability in existing dexterous grasp synthesis methods and introduced OmniDexVLG, a multimodal semantic-guided framework that explicitly incorporates grasp taxonomy, contact semantics, and functional affordance into the grasp generation process. 
This enables the synthesis of more semantically consistent and structurally diverse dexterous grasp poses under natural language instructions.

To support fine-grained semantic supervision, we proposed OmniDexDataGen, a comprehensive grasp data generation pipeline that integrates taxonomy-driven topological configuration sampling, functional-affordance-aware contact point sampling, taxonomy-aware differential force closure grasp sampling, and physics-based optimization. This framework produces dexterous grasp samples that cover a broad range of semantic categories and contact structures. 

Furthermore, we developed OmniDexReasoner, a dexterous grasp semantic inference module that leverages large multimodal model reasoning together with RAG and CoT mechanisms to decode latent grasp intentions embedded in language and task context, enabling automatic and reliable semantic annotation.

We conducted extensive ablation studies to evaluate the contribution of each proposed component. The functional-affordance-aware contact sampler effectively prevents semantically invalid grasps—particularly on large-scale objects—and enhances both the validity and diversity of functional affordance distributions. The taxonomy-aware DFC sampler enriches grasp diversity across semantic dimensions by encouraging varied grasp types and contact configurations. Within OmniDexReasoner, RAG improves contextual grounding across multi-agent reasoning, while CoT enhances discrimination among semantically similar grasp types. Together, these mechanisms substantially improve grasp taxonomy inference accuracy and stability.

Comprehensive simulation and real-world experiments demonstrate that OmniDexVLG outperforms existing approaches in terms of grasp diversity, contact distribution quality, semantic consistency, and generalization across functional tasks, validating the effectiveness of the proposed multi-semantic modeling paradigm for dexterous grasp generation.

In future work, we plan to extend our framework to support task-chained language instructions and continuous manipulation trajectories, enabling more complex and semantically grounded robotic manipulation capabilities.