\begin{abstract}
Compositional spatiotemporal reasoning often requires a system to invoke multiple heterogeneous specialists, such as geometric, temporal, topological, and trajectory agents.
A central question is how such a system should route among specialists when execution does not simply succeed or fail, but fails in qualitatively different ways.
Existing tool-augmented and multi-agent LLM systems typically leave this routing decision implicit in language generation, making recovery ad hoc, difficult to interpret, and hard to optimize. This paper presents \starname{} (\textbf{S}patio-\textbf{T}emporal \textbf{A}gent \textbf{R}outer), a failure-aware routing framework that externalizes inter-agent control as a state-conditioned transition policy over the current agent, task type, and typed execution status.
At the center of \starname{} is an agent routing matrix that combines expert-specified nominal routes with recovery transitions learned from execution traces.
Because the matrix conditions on distinct failure states, the router can respond differently to malformed outputs, missing dependencies, and tool--query mismatches, rather than collapsing them into a generic retry signal.
Specialists execute through a tool-grounded \emph{extract--compute--deposit} protocol and write intermediate results to a shared blackboard for downstream fusion. Results prove that retaining unsuccessful traces during training enlarges the support of the routing policy on error states, enabling recovery transitions that success-only training cannot represent.
Across three spatiotemporal benchmarks and eight backbone LLMs, \starname{} improves over multiple baselines with the clearest gains on queries whose execution deviates from the nominal routing path.
Router-specific ablations and recovery analyses further show that typed failure-aware routing, rather than specialist composition alone, is a key factor for these improvements.
\end{abstract}