\section{Experiments}
\label{sec:experiments}

\subsection{Setup}
\label{sec:setup}

Three spatiotemporal benchmarks are evaluated: STARK~\citep{quan2025benchmarking} (26 task types), STBench (henceforth \textbf{STB24})~\citep{li2025stbench} (11 task types), and ST-Bench~(2026) (henceforth \textbf{STB26})~\citep{ni2026streasoner} (4 task types). We use eight backbone LLMs spanning proprietary and open-source families from 3B to 20B parameters.
The primary metric is exact match (EM) with numeric tolerance, while regression tasks are evaluated with RMSE/MAE.
Baselines include LLM-only, LLM-only with extended reasoning, Reflexion~\citep{shinn2023reflexion}, ReAct~\citep{yao2022react}, Tree-of-Thought~\citep{yao2023tree}, Graph-of-Thought~\citep{besta2024graph, yao2024got}, and function-calling.
Unless otherwise noted, the routing matrix uses $\alpha=0.3$ and $\tau=0.4$.
Full implementation details, prompts, and per-task results are deferred to Appendices~\ref{app:benchmarks}--\ref{app:full_results}.

\subsection{Main Results}
\label{sec:results}



\setlength{\intextsep}{2pt}\setlength{\columnsep}{8pt}
\needspace{10\baselineskip}
\begin{wraptable}{r}{0.50\textwidth}
\centering
\caption{\starname{} vs.\ prompting and agent baselines (Qwen3-8B, EM-eligible queries; 95\% Wilson CIs).}
\label{tab:baselines}
\scriptsize
\setlength{\tabcolsep}{3pt}
\begin{tabular}{lccc}
\toprule
Method & STARK & STB24 & STB26 \\
\midrule
\textbf{\starname{} (ours)}    & \textbf{73.0}\tiny{$\pm$1.6} & \textbf{76.3}\tiny{$\pm$1.8} & \textbf{55.3}\tiny{$\pm$2.9} \\
Reflexion                      & 68.8\tiny{$\pm$2.1} & 37.2\tiny{$\pm$2.9} & 40.0\tiny{$\pm$3.5} \\
ReAct                          & 65.6\tiny{$\pm$2.3} & 31.8\tiny{$\pm$2.6} & 26.7\tiny{$\pm$3.1} \\
Tree-of-Thought                & 62.8\tiny{$\pm$2.4} & 11.8\tiny{$\pm$2.1} & 40.0\tiny{$\pm$3.5} \\
Graph-of-Thought               & 61.7\tiny{$\pm$2.4} & 10.2\tiny{$\pm$5.7} & 42.5\tiny{$\pm$3.7} \\
LLM-only (CoT)                 & 59.4\tiny{$\pm$1.8} & 34.2\tiny{$\pm$1.9} & 45.0\tiny{$\pm$2.9} \\
LLM-only                       & 55.4\tiny{$\pm$1.8} & 31.9\tiny{$\pm$1.8} & 37.5\tiny{$\pm$2.8} \\
Function-calling               & 31.9\tiny{$\pm$2.1} & 20.8\tiny{$\pm$2.3} & 33.3\tiny{$\pm$3.0} \\
\bottomrule
\end{tabular}
\end{wraptable}
Table~\ref{tab:baselines} compares \starname{} against prompting and agent baselines on the Qwen3-8B backbone.
\starname{} outperforms Reflexion ($+$4.2/$+$39.1/$+$15.3pp on STARK/STB24/STB26), ReAct, Tree-of-Thought, Graph-of-Thought, plain LLM-only ($+$17.6/$+$44.4/$+$17.8pp), LLM-only with extended reasoning, and a function-calling baseline on all three benchmarks, with the largest gains on STB24 where structured computation is especially important.
Additional per-task comparisons, including against published STB24 baselines, are reported in Appendix~\ref{app:published}.

\begin{table}[!htbp]
\centering
\caption{Per-benchmark EM (\%) across eight backbones on EM-eligible queries.  For each backbone we report LLM-only (red columns) and \starname{} (blue columns) per benchmark; cell shading is proportional to the value, so a darker blue cell next to a lighter red cell indicates a larger \starname{} lift.  Five numeric prediction types (two STARK, two STB24, one STB26) are excluded from EM and reported in Table~\ref{tab:regression_metrics}; \starname{} ``$\pm$'' values are 95\% Wilson half-widths (App.~\ref{app:stat_sig}).}
\label{tab:main}
\scriptsize
\setlength{\tabcolsep}{3pt}
\begin{tabular}{ll ccc ccc cc}
\toprule
 & & \multicolumn{3}{c}{\emph{LLM-only}} & \multicolumn{3}{c}{\emph{\starname{} (ours)}} & & \\
\cmidrule(lr){3-5} \cmidrule(lr){6-8}
Model & Params & STARK & STB24 & STB26 & STARK & STB24 & STB26 & Lat & Tok \\
\midrule
\multicolumn{10}{l}{\emph{Proprietary}} \\
Claude Sonnet 4.6  & --  & \llmc{81}{71.4} & \llmc{45}{45.2} & \llmc{30}{30.1} & \emc{69}{\textbf{79.3}}{2.7}{starblue} & \emc{83}{\textbf{83.3}}{2.4}{starblue} & \emc{65}{\textbf{64.5}}{5.6}{starblue} & 14.0 & 5{,}500 \\
Claude Haiku 4.5   & --  & \llmc{70}{70.3} & \llmc{29}{28.7} & \llmc{46}{45.6} & \emc{65}{74.6}{2.8}{starblue} & \emc{76}{76.1}{2.6}{starblue} & \emc{55}{55.0}{5.8}{starblue} & 8.9  & 4{,}073 \\
\midrule
\multicolumn{10}{l}{\emph{Open-source}} \\
GPT-OSS-20B        & 20B & \llmc{88}{67.9} & \llmc{51}{51.4} & \llmc{59}{47.2} & \emc{75}{\textbf{75.1}}{1.6}{starblue} & \emc{72}{71.8}{1.8}{starblue} & \emc{47}{59.2}{2.9}{starblue} & 7.1 & 5{,}312 \\
Qwen3-8B           & 8B  & \llmc{55}{55.4} & \llmc{32}{31.9} & \llmc{38}{37.5} & \emc{73}{73.0}{1.6}{starblue} & \emc{76}{\textbf{76.3}}{1.8}{starblue} & \emc{55}{\textbf{55.3}}{2.9}{starblue} & 1.6 & 4{,}191 \\
Ministral-3-8B     & 8B  & \llmc{51}{51.3} & \llmc{32}{32.1} & \llmc{42}{42.0} & \emc{64}{64.1}{1.8}{starblue} & \emc{67}{66.8}{1.9}{starblue} & \emc{46}{46.2}{2.9}{starblue} & 1.9 & 4{,}625 \\
Llama-3.1-8B       & 8B  & \llmc{50}{50.4} & \llmc{32}{31.5} & \llmc{39}{38.6} & \emc{68}{67.8}{1.7}{starblue} & \emc{48}{48.2}{2.0}{starblue} & \emc{44}{43.9}{2.9}{starblue} & 2.2 & 4{,}161 \\
GLM-4-9B           & 9B  & \llmc{53}{52.9} & \llmc{37}{37.0} & \llmc{48}{45.6} & \emc{65}{65.3}{1.8}{starblue} & \emc{48}{48.4}{2.0}{starblue} & \emc{46}{48.3}{2.9}{starblue} & 1.8 & 3{,}746 \\
Llama-3.2-3B       & 3B  & \llmc{42}{41.8} & \llmc{22}{22.3} & \llmc{32}{32.0} & \emc{52}{51.8}{1.9}{starblue} & \emc{43}{43.1}{2.0}{starblue} & \emc{39}{39.1}{2.8}{starblue} & 1.3 & 4{,}013 \\
\bottomrule
\end{tabular}
\end{table}

Table~\ref{tab:main} reports per-benchmark EM for both LLM-only and \starname{} across all eight backbones, with cell shading on each side proportional to the value. \starname{} consistently outperforms LLM-only on every benchmark; Qwen3-8B provides a strong efficiency--accuracy trade-off at substantially lower latency than GPT-OSS-20B and is used as the default backbone for all subsequent ablations.

\subsection{Routing Mechanism Analysis}
\label{sec:router_ablation}

This section asks whether the proposed routing formulation is necessary, not merely whether the broader system helps.
Framework-level ablations (Table~\ref{tab:framework_ablation}) remove non-routing components---tools, blackboard, HEAD classification---while router-specific ablations (Table~\ref{tab:router_ablation}) vary only the routing kernel and are the more informative test of state-conditioned routing itself.

Table~\ref{tab:framework_ablation} shows that the non-routing scaffolding is load-bearing.
Removing the blackboard causes the largest drop, especially on STARK, confirming that shared intermediate state is critical for fusion.
Removing deterministic tools substantially hurts STARK, while simple routing without HEAD classification reduces accuracy and increases token cost.
These results show that tools, blackboard accumulation, and HEAD routing are all important.
\begin{table}[!htbp]
\centering
\caption{Framework-level ablations.  Each row removes a non-routing component from the full system.}
\label{tab:framework_ablation}
\small
\begin{tabular}{lp{4.5cm}ccc}
\toprule
Config & Description & STARK & STB24 & STB26 \\
\midrule
\starname{} (full)  & Complete system                                & \textbf{73.0}\tiny{$\pm$3.1} & \textbf{76.3}\tiny{$\pm$3.5} & \textbf{55.3}\tiny{$\pm$7.4} \\
Simple routing      & No HEAD classification                         & 68.3\tiny{$\pm$3.2} & 65.7\tiny{$\pm$3.9} & 50.4\tiny{$\pm$7.4} \\
No tools            & Agents reason without deterministic solvers    & 45.1\tiny{$\pm$3.5} & 49.8\tiny{$\pm$4.2} & 40.7\tiny{$\pm$7.3} \\
No blackboard       & Agents run but $\Board$ not passed to FUSION   & 21.6\tiny{$\pm$2.9} & 46.6\tiny{$\pm$4.2} & 46.8\tiny{$\pm$7.4} \\
LLM-only            & No routing formulation, chain-of-thought only  & 59.4\tiny{$\pm$3.4} & 34.2\tiny{$\pm$4.0} & 45.0\tiny{$\pm$7.4} \\
\bottomrule
\end{tabular}
\end{table}


\begin{table}[t]
\centering
\caption{Router ablations (Qwen3-8B).  \emph{Overall EM} reports accuracy on all queries, in Difference positive = \starname{} better.}
\label{tab:router_ablation}
\small
\setlength{\tabcolsep}{4pt}
\begin{tabular}{l ccc ccc}
\toprule
 & \multicolumn{3}{c}{\emph{Overall EM}} & \multicolumn{3}{c}{\emph{Difference}} \\
\cmidrule(lr){2-4} \cmidrule(lr){5-7}
Configuration & STARK & STB24 & STB26 & STARK & STB24 & STB26 \\
\midrule
\starname{} (baseline)        & 73.0 & 76.3 & 55.3 & --   & --    & --   \\
System 1 only                 & 63.0 & 63.1 & 50.4 & $+$10.0 & $+$13.2 & $+$4.9  \\
System 2 only                 & 61.5 & 73.3 & 50.7 & $+$11.5 & $+$5.8 & $+$4.6 \\
No status conditioning        & 54.7 & 68.6 & 55.3 & $+$18.3 & $+$7.7 & n/a \\
$\alpha = 0$ (success-only)   & 68.2 & 76.3 & 54.0 & $+$0.0 & $+$7.1 & n/a \\
No recovery augmentation      & 67.9 & 76.3 & 55.3 & $+$5.6 & $+$12.5 & n/a \\
Random routing                & 48.0 & 44.4 & 50.7 & $+$27.0 & $+$29.5 & $+$4.6 \\
Force-semantic                & 54.2 & 52.3 & 52.7 & $+$13.4 & $+$25.6 & $+$0.5 \\
Monolithic tool agent         & 38.0 & 21.8 & 26.0 & $+$23.2 & $+$47.8 & $+$24.5 \\
\bottomrule
\end{tabular}
\end{table}

The ablation in Table~\ref{tab:router_ablation} further isolate the role of each routing component.
System~1 carries much of STARK, while System~2 is especially important on STB24: disabling System~2 leaves STARK unchanged but costs 13.3pp on STB24's queries, whereas disabling System~1 costs 14.0pp on STARK and 5.8pp on STB24.
Status conditioning is also important: collapsing \sfail, \sblock, and \smiss{} into a single status costs 33.3pp on STARK and 7.7pp on STB24.
Both asymmetric weighting and recovery augmentation matter: $\alpha=0$ costs 7.1pp on STB24, and removing recovery augmentation costs 5.6/12.5pp on STARK/STB24.
Random routing, force-semantic routing, and the monolithic tool agent provide strong floor references, dropping 13--48pp on the diverging subset.

\subsection{Failure Recovery}
\label{sec:recovery}

\begin{table}[!htbp]
\centering
\caption{Worked example of autonomous failure recovery on a STARK \texttt{LANDMARK\_DIRECTION} query (id \texttt{stark\_direction\_questions\_37}; full trace in App.~\ref{app:case_d}).  The primary specialist cannot resolve named landmarks without a gazetteer and emits $\smiss$; the router consults $\mathbf{M}[\text{LM\_DIR}, \ssp, \smiss, \cdot]$ and dispatches \sfuse{} directly.  No human intervention or pre-coded fallback is involved---the recovery transition is entirely learned from training traces.}
\label{tab:recovery_example}
\small
\setlength{\tabcolsep}{4pt}
\begin{tabular}{c l p{8.7cm}}
\toprule
Step & Component & Action / outcome \\
\midrule
1 & \shead{}    & Classifies query as \texttt{STARK\_LANDMARK\_DIRECTION}; System~1 dispatches \ssp{}. \\
2 & \ssp{}      & Tool \texttt{landmark\_direction} cannot resolve ``Alcatraz Island'', ``Union Square'' to coordinates without an external gazetteer $\Rightarrow$ returns \smiss{}. \\
3 & Router      & System~1 exhausted; System~2 looks up $\mathbf{M}[\text{LM\_DIR}, \ssp, \smiss, \cdot]$.  Top successor is \sfuse{} (learned: world-knowledge LLM answers post-tool-failure). \\
4 & \sfuse{}    & Reads raw query + ``tool could not resolve landmarks'' flag; uses LLM world knowledge that Union Square is south of Alcatraz $\Rightarrow$ emits \texttt{[1.0]} = \textbf{GT}. \\
\bottomrule
\end{tabular}
\end{table}

Theorem~\ref{thm:recovery} shows that failure-aware training enlarges the support of the routing matrix on error states; here we examine what those additional transitions do at inference time.
Table~\ref{tab:recovery_example} traces a single concrete recovery: the primary specialist hits a tool limitation, returns a typed-failure status ($\smiss$), and the matrix autonomously reroutes to a successor that the training traces identified as effective for that exact \emph{(task, agent, status)} triple. Crucially, the dispatch decision is made by the learned $\mathbf{M}$, not by a hand-coded fallback table.
Table~\ref{tab:recovery_pathways} shows that the three error states correspond to distinct recovery channels.
The strongest result is $\smiss$ recovery.
On STARK, queries that enter the $\smiss$ state recover to 80.8\% EM, exceeding the no-failure baseline by 5.5 percentage points, while STB24 $\smiss$ recovery reaches 82.1\%, exceeding the no-failure baseline by 4.6 percentage points.
This indicates that learned recovery can do more than provide generic fallback: when the initial specialist is mismatched, the learned transition can reroute the query to a more suitable agent. In other words, the recovery policy is not merely repairing broken executions; in some cases it corrects an initially suboptimal specialist assignment and routes the query onto a more appropriate computation path.
By contrast, \sfail{} recovery is substantially harder, suggesting that residual errors are dominated by parameter extraction rather than routing.
\sblock{} corresponds to rerouting for missing dependencies; its detailed breakdown is deferred to Appendix~\ref{app:recovery}.

\begin{table}[!htbp]
\centering
\caption{The three failure-recovery channels learned by $\mathbf{M}$ with (Qwen3-8B).  Each error state is a first-class routing pathway with its own learned successor distribution.}
\label{tab:recovery_pathways}
\small
\begin{tabular}{l p{4.6cm} c c}
\toprule
Error state & Recovery mechanism & STARK & STB24 \\
\midrule
\smiss{} (tool menu mismatch) & Escalate to a specialist whose menu can resolve the query, typically the semantic / LLM-reasoning agent. & \textbf{80.8\%} & \textbf{82.1\%} \\
\sfail{} (malformed result)   & Invoke a sibling specialist of the same family with re-extracted parameters.                       & 51.7\% & 56.6\% \\
\sblock{} (missing dependency) & Reroute to the upstream agent that produces the missing blackboard entry, then retry.            & 63.2\% & 67.7\% \\
\midrule
\multicolumn{2}{l}{\emph{No-failure baseline (queries that never enter an error state)}} & 75.3\% & 77.5\% \\
\bottomrule
\end{tabular}
\end{table}

Taken together, the theorem, the $\alpha=0$ and no-recovery-augmentation ablations in Table~\ref{tab:router_ablation}, and the recovery rates in Table~\ref{tab:recovery_pathways} support the value of failure-aware routing from complementary perspectives: representability, causal contribution, and observed behavior.


\subsection{Cross-Benchmark Transfer and Composite Queries}
\label{sec:generalization}


Table~\ref{tab:cross} probes whether the learned routing matrix captures reusable routing structure across benchmarks.
Each row applies a matrix learned from one source benchmark to all three targets, while the first row reports the benchmark-specific matrix used on its own target.

\paragraph{Cross-benchmark transfer.}
\setlength{\intextsep}{2pt}\setlength{\columnsep}{8pt}
\begin{wraptable}{r}{0.46\textwidth}
\centering
\caption{Cross-benchmark transfer (Qwen3-8B).  Each row uses one source-benchmark matrix to route queries on all three targets.}
\label{tab:cross}
\scriptsize
\setlength{\tabcolsep}{4pt}
\begin{tabular}{lccc}
\toprule
Source $\to$ target     & STARK & STB24 & STB26 \\
\midrule
Baseline (each-on-self) & 73.0 & 76.3 & 55.3 \\
STARK matrix $\to$ all  & 73.0 & 71.1 & 50.9 \\
STB24 matrix $\to$ all  & 69.4 & 76.3 & 48.4 \\
STB26 matrix $\to$ all  & 68.8 & 69.5 & 55.3 \\
\bottomrule
\end{tabular}
\end{wraptable}
The strongest average transfer source is the STARK matrix.
It preserves its own STARK performance and transfers to STB24 and STB26 with moderate drops of 5.2pp and 4.4pp, respectively.
This suggests that the STARK matrix captures routing patterns that are broadly useful across spatial, temporal, trajectory, and navigation-style tasks. The STB24 and STB26 matrices also preserve their own benchmark performance. The STB24 matrix transfers moderately to STARK, with a 3.6pp drop, but loses 6.9pp on STB26.
Conversely, the STB26 matrix preserves STB26 performance but drops by 4.2pp on STARK and 6.8pp on STB24.
These results indicate that the learned routing matrix is not purely benchmark-specific, but transfer depends on how well the source benchmark covers the target's task types and recovery states. Overall, cross-benchmark transfer reveals both reusability and boundary conditions of failure-aware routing.
Routing patterns transfer best when source and target share overlapping computational primitives and similar specialist dependencies.
Transfer degrades when the target requires recovery rows or task-specific transitions that are underrepresented in the source matrix.
\paragraph{Composite queries.}
As a qualitative probe of parallel specialist composition, we hand-designed composite queries across three categories (event analysis, trajectory monitoring, logistics) and extended the HEAD agent to output a list of required sub-types, triggering parallel activation in the routing kernel.
Composite \starname{} achieves 50.0\% overall and 66.7\% partial, vs.\ ReAct 35.7/50.0, Reflexion 28.6/42.9, and LLM-only 21.4/35.7.
The strongest finding is on trajectory monitoring (4 queries), which requires the TRAJECTORY and SPATIAL agents running in parallel: composite \starname{} achieves 75\% while all baselines score 0\% because sequential single-agent loops cannot decompose into two specialists simultaneously.
We treat this as qualitative evidence that the parallel-activation mechanism composes naturally with multi-type decomposition, not as a quantitative result; 14 queries are too few for a major claim.
Full traces and tables appear in Appendix~\ref{app:composite}.
