

% \vspace{-2mm}
\section{Introduction}
\vspace{-1mm}




\input{tables/motivation}



% Introduction structure:
% (1) Motivation: rapid adoption of LLM-based multi-agent frameworks and evidence that architectural design dominates system performance (Table 1).
% (2) Limitations of prior work: existing benchmarks evaluate isolated capabilities and fail to capture framework-level architectural effects.
% (3) Our approach: a unified architectural taxonomy and MAFBench as a standardized execution layer integrating existing benchmarks.
% (4) Contributions: taxonomy, evaluation infrastructure, empirical findings, and design automation.

Multi-agent systems built on large language models (LLMs), often referred to as LLM-based agents or agentic AI systems,
~\cite{NEURIPS2024_fa54b0ed,
proagentcooperativeagent,
githubissuemultiagentllm,
qian-etal-2024-chatdev,
jin-etal-2024-agentreview}
have emerged as a widely adopted abstraction for constructing complex intelligent applications
~\cite{omar2025chatty, he2025llm,
githubissuemultiagentllm,
qian-etal-2024-chatdev}. Consequently, a growing ecosystem of multi-agent LLM frameworks has emerged to support the rapid development of these systems~\cite{langgraph2025, crewai2025, wu2024autogen, openaiagents2025, vezhnevets2023generative, touzel2024simulation}. These frameworks are software systems that define architectural abstractions for orchestrating LLM-driven agents, managing memory and tool access, and governing task execution and coordination. Despite their widespread adoption, the system-level consequences of framework-level architectural design choices remain poorly understood. As shown by our study in Table~\ref{tab:motivation}, architectural choices across orchestration, memory, planning, specialization, and coordination can drive large variation in latency, throughput, accuracy, and task success under identical models and tasks. These results indicate that system behavior in multi-agent settings is governed primarily by framework architecture rather than LLM quality alone. Table~\ref{tab:github-stats-updated} summarizes representative and widely used multi-agent LLM frameworks across different architectural paradigms.

Prior work has examined individual aspects of multi-agent intelligence, including tool use~\cite{mialon2023gaiabenchmarkgeneralai, nguyen2024dynasaur, guo2024stabletoolbench, shi2025retrievalmodelsarenttoolsavvy}, memory and retrieval~\cite{hu2025memoryagentbench, hsieh2024ruler, li2018towards, xu2024detectiveqa, zhong2023mquake}, and collaborative reasoning~\cite{coordinationcollaborativereasoning}. These benchmarks are designed to isolate and measure \emph{single capabilities}, and they do so effectively. However, none is intended to characterize the behavior of multi-agent frameworks, which integrate multiple capabilities and impose architectural constraints on how those capabilities interact. In practice, frameworks differ less in the capabilities they expose than in how those capabilities are orchestrated, constrained, and executed through framework-level design decisions. As a result, execution overhead, scalability, and failure modes are shaped by interactions among capabilities within a shared framework structure rather than by any capability in isolation. 
Existing benchmarks vary widely in format, assumptions, and evaluation protocols. As a result, applying them uniformly across heterogeneous frameworks is challenging and often requires substantial re-engineering.
Consequently, meaningful systematic comparison requires integrating complementary benchmarks to explain why systems built on the same models can exhibit markedly different performance and cost under controlled, large-scale deployments.


To address this gap, we introduce an architectural taxonomy that systematically characterizes multi-agent LLM frameworks along fundamental dimensions, including control flow, agent abstraction, communication, memory, and execution semantics. This taxonomy serves as the conceptual backbone of our analysis, enabling systematic comparison across systems. Building on this taxonomy, we introduce \textbf{MAFBench}\footnote{\vspace{-2mm}\faGithub\ \href{https://github.com/CoDS-GCS/MAFBench}{https://github.com/CoDS-GCS/MAFBench}}, a standardized evaluation suite that integrates established, domain-relevant benchmarks within a unified execution pipeline. Rather than proposing new benchmarks, MAFBench aligns execution and measurement protocols to isolate the impact of framework-level design choices, such as orchestration, memory abstraction, and communication structure, across both single-agent and multi-agent settings. 
We fix the underlying LLM to control for model effects and attribute observed differences to the framework architecture. Planning, however, is evaluated across multiple LLMs, as its behavior is inherently model-dependent. This methodology enables controlled, framework-level comparison while preserving the semantics of each benchmark.


% \vspace{2mm}
\noindent\textbf{Contributions.}
Our primary contribution is a unified methodology for understanding, evaluating, and guiding the design of multi-agent LLM systems. Our main technical contributions are:

\begin{itemize}[leftmargin=4mm]
\item An architectural taxonomy for systematically comparing multi-agent LLM frameworks by decomposing them along fundamental architectural dimensions. The taxonomy identifies orthogonal dimensions spanning control flow, agent abstraction, communication, memory, and execution semantics.\shorten

\item \textbf{MAFBench}, a standardized evaluation suite that integrates existing benchmarks within a unified execution and scoring pipeline for framework-level comparison.

\item A comprehensive empirical study across representative multi-agent LLM frameworks using MAFBench, demonstrating that framework-level architectural decisions, rather than model quality alone, govern performance, scalability, and cost under controlled execution settings.

\item Concrete architectural design principles that translate our empirical findings into actionable guidance for developing multi-agent LLM systems, and identify current gaps and promising future research directions.
\end{itemize}


\input{tables/All_Frameworks}

The remainder of the paper is organized as follows. Section~\ref{sec:taxonomy_analysis} presents the proposed architectural taxonomy, and Section~\ref{sec:benchmark_collection} describes MAFBench and its unified evaluation pipeline. Section~\ref{sec:eval} reports experimental results, followed by empirically grounded architectural design principles in Section~\ref{sec:design_principles}. Section~\ref{sec:future_work} discusses future directions motivated by observed system-level limitations, and Section~\ref{sec:conclusion} concludes the paper.
