


\newpage

\section{Appendix: Concordia Experiment Analysis for Framework Overhead}
\label{sec:concordia_appendix}




To better understand the unique behavior of the Concordia multi-agent simulation framework, we conducted a controlled run on the trivial query \emph{``What is 2+2?''}. The goal here was not to measure accuracy or efficiency per se, but to expose why Concordia transforms even simple questions into long, narrative-driven interactions and to illustrate the type of logs it produces.

\paragraph{Why Concordia Behaves This Way.}  
Unlike lightweight orchestration frameworks, Concordia is built as a role-play simulation engine. Every query is automatically embedded in a dramatic environment, narrated by a \emph{Game Master}, and passed through a structured observation–action–resolution loop. Even when only one agent is present, Concordia enforces the following pipeline: (i) the Game Master wraps the input in a simulated scene, producing a rich observation; (ii) the agent must respond with an \texttt{ActionSpec}, which is intended as a structured declaration of intent but is often realized by the LLM as verbose narrative text; (iii) the Game Master resolves the action into an event, again embedding it in a descriptive story; and (iv) Concordia logs the entire exchange in both plain text and full HTML transcript form. These requirements explain why a simple arithmetic prompt is converted into multi-turn narrative role-play with dramatically inflated output size and latency.

\paragraph{Log Example.}  
The following excerpt from our controlled run shows how a single numeric query was processed:  

\begin{tcolorbox}[colback=gray!5,colframe=black!40,title={Concordia Log}]
\scriptsize
\begin{verbatim}
[Entity: TestAgent] Observation:
  TestAgent finds themselves in a dimly lit room, 
  surrounded by walls lined with charts and equations.
  A worn wooden table in the center holds a sheet 
  that reads "What is 2+2?" ...

[Entity: TestAgent] Action:
  TestAgent leans forward, studying the curious creature ...
  and pondering the question "What is 2+2?".

[GameMaster] Resolution:
  Event: TestAgent leaned forward in their chair, 
  intently studying the curious creature before them. 
  They spoke: "Hello there ..." and then considered "2+2".

[GameMaster] Final transcript (HTML log):
  <!DOCTYPE html>
  <html> ...
\end{verbatim}
\end{tcolorbox}

\paragraph{Analysis and Conclusion.}
This log illustrates Concordia’s core design principles and their performance impact. Even when no complex reasoning is required, the framework enforces multiple orchestration layers, including \emph{narrative wrapping} of inputs into fictional scenarios, \emph{ActionSpec enforcement} that requires structured outputs despite verbose LLM responses, \emph{mandatory Game Master resolution} to validate and finalize actions, and \emph{automatic transcript generation} that produces extensive HTML logs. These mechanisms ensure consistency in interactive simulations but make every run verbose and computationally heavy, even for trivial tasks. As a result, a simple query such as \emph{``What is 2+2?''} triggers a multi-stage narrative and substantial logging, reflecting a deliberate focus on narrative fidelity over efficiency. While valuable for studying interactive agent coordination, this design explains Concordia’s high orchestration overhead and poor suitability for latency-sensitive scenarios.
