


\vspace{-2mm}
\subsection{Specialization Benchmarks}
\label{subsec:bench_specialization}

Specialization in LLM-based agents refers to activating domain-relevant reasoning through textual conditioning rather than external knowledge acquisition. We examine whether role descriptions, explicit planning, or expert methodological guidance better structure the domain-specific reasoning encoded in the model. Using machine learning tasks from CatDB~\cite{catdb}, we measure behavioral differences under controlled conditions with fixed data and models.


\noindent\textbf{Benchmark Structure and Conditioning Variants.}
The benchmark comprises five public machine learning datasets spanning regression, binary, and multiclass classification (Table~\ref{tab:datasets}). Each dataset is evaluated under three conditioning strategies. \emph{Role-based prompting} assigns a professional identity in the task description. \emph{Planning-based conditioning} inserts an intermediate step in which the LLM generates a high-level solution plan before code generation. \emph{Expert-guided conditioning} injects methodological instructions reflecting data-science workflows. These variants isolate the effects of identity framing, reasoning structure, and procedural guidance.

\noindent\textbf{Evaluation Setup.}
MAFBench provides a unified specialization evaluation pipeline that isolates the architectural impact of behavioral conditioning. Task structure, data loading, model execution, and metric computation are standardized to ensure consistent semantics. Conditioning strategy is the only experimental variable; models, inputs, and prompts remain fixed. Model parameters and execution limits are centrally configured for reproducibility and cost control. Results are logged using a shared schema capturing performance and runtime across runs.



\input{tables/Benchmark_Specialization}
