\section{Multi-Agent Design Principles}
\label{sec:design_principles}

This section distills results from Section~\ref{sec:eval} into actionable, architecture-level design principles for multi-agent LLM systems. Each principle is grounded in controlled empirical evidence, showing how execution interfaces and architectural structure, not model capability, govern performance, robustness, cost, and scalability.


\smallskip
\noindent\textbf{Principle 1: Orchestration overhead is the dominant scalability constraint.}
\emph{Keep orchestration shallow; add coordination only when strictly required.} Section~\ref{sec:framework-overhead} shows that latency and throughput are governed by framework execution structure even for trivial workloads. Direct LLM calls incur minimal cost, while graph-based and role-based frameworks introduce systematic overhead from mandatory scheduling, state propagation, and control layers. GABM-style execution amplifies this effect, producing orders-of-magnitude higher latency and throughput collapse due to persistent interaction loops and environment-mediated state updates. These effects arise from orchestration semantics rather than task complexity or model behavior. As a result, deeper orchestration directly limits scalability independent of model quality.
\emph{Design implication:} for latency- or throughput-sensitive production systems, favor lightweight orchestration and avoid multi-round coordination or environment-style execution unless extended multi-step interaction is essential.

\smallskip
\noindent\textbf{Principle 2: Memory must be architected around task semantics, not context size.}
\emph{Choose memory architecture based on task needs; never rely on larger context windows.}
Section~\ref{subsec:memoryagentbench} shows that memory behavior is governed by architectural design rather than available context. Retrieval-first architectures consistently dominate factual recall and long-range reasoning by isolating relevant evidence and preventing uncontrolled history growth. Accumulation-based memory degrades as unfiltered interaction history expands, even under large context budgets. In-session learning requires retaining recent history in context, but achieves its strongest and most stable performance under bounded hybrid designs that filter accumulated signals through retrieval. No single memory architecture performs well across all competencies, and increasing context length never compensates for missing architectural mechanisms. Selective Forgetting fails universally because current frameworks lack explicit memory editing and dependency-aware deletion.
\emph{Design implication:} use retrieval-first memory for recall and long-range reasoning tasks, bounded accumulation for in-session learning, and never replace architectural memory control with larger context windows.

\smallskip
\noindent\textbf{Principle 3: Planning should be permissive; rigid schemas should be exceptional.}
\emph{Allow free-form planning by default; enforce structure only when proven safe.}
Section~\ref{subsec:planning_results} shows that introducing a planning stage generally improves or preserves reasoning accuracy when plans are generated freely in natural language. In contrast, schema-constrained planning is a primary source of failure and overhead. For local open models, strict formats frequently convert correct reasoning into execution failures through high parsing error rates. Even for stronger remote models, constrained planning introduces substantial runtime cost and produces inconsistent accuracy, sometimes degrading performance when structured plans interfere with downstream reasoning. These failures arise from interface constraints rather than from planning itself.
\emph{Design implication:} treat planning as a flexible reasoning layer by default, and apply structured enforcement only selectively for high-capability models with carefully validated integration.

% \smallskip
\noindent\textbf{Principle 4: Specialization should be procedural; role labels should be secondary.}
\emph{Encode expertise as workflows, not as role names.}
Section~\ref{sec:specialization} shows that assigning professional roles does not activate domain-specific reasoning. Planning-based conditioning stabilizes behavior but does not yield consistent performance gains, indicating that intermediate reasoning steps alone do not induce expertise. In contrast, expert-guided procedural conditioning consistently delivers large improvements by enforcing explicit solution workflows that structure how the model processes data and decisions. Role labels may still support lightweight routing or delegation between agents, but they do not activate latent knowledge encoded in model parameters.
\emph{Design implication:} implement specialization through reusable procedural templates that enforce domain-specific reasoning workflows, not through role metadata or prompt rewording.\shorten

\smallskip
\noindent\textbf{Principle 5: Coordination is governed by communication topology, not by agent intelligence.}
\emph{Design communication structure explicitly; more interaction cannot fix bad topology.}
Section~\ref{sec:Coordination_section} shows that coordination success and scalability are determined by communication topology rather than by increasing interaction rounds, tokens, or runtime. For local coordination tasks, limited-hop, neighbor-based topologies achieve the highest success rates, with scale-free graphs offering strong success--cost trade-offs through efficient information routing. Sparse graphs with long paths fail to support global agreement as networks scale, even under large interaction budgets. Only dense broadcast-style connectivity consistently enables system-wide consensus. These effects arise from architectural information-flow constraints rather than agent reasoning capability. \emph{Design implication:} treat communication topology as a first-class architectural decision, since poor interaction structure cannot be fixed by additional rounds, prompts, or model capacity.\shorten

\smallskip
\noindent\textbf{Principle 6: System interfaces dominate multi-agent behavior.}
\emph{Engineer robustness and scalability through interfaces, not prompts.}
Across Section~\ref{sec:eval}, performance limits consistently arise from framework execution semantics and interface design rather than from task difficulty or interaction budget. Orchestration determines baseline latency and throughput. Memory behavior follows retrieval and accumulation semantics. Rigid planning schemas convert valid reasoning into execution failures. Role-based conditioning fails to induce specialization. Communication topology governs coordination success and scalability. These results show that multi-agent behavior is shaped by how frameworks structure interaction and control flow. \emph{Design implication:} engineer efficiency and scalability through architectural interfaces, because poor execution structure cannot be compensated by additional rounds, tokens, or prompt refinement.\shorten 


