\section{Future Directions}
\label{sec:future_work}

This section outlines promising research directions motivated by the system-level limitations identified in our evaluation.

\smallskip
\noindent\textbf{Single-Agent Foundations.}  
Our results suggest that core agent capabilities must move beyond prompt-level heuristics toward persistent architectural components with principled control. Recent work explores adaptive memory systems that continuously update, link, and refine stored knowledge to improve long-horizon reasoning~\cite{kang2025memory,xu2025mem}. While effective at consolidation and retrieval, these systems lack explicit mechanisms for controlled forgetting, dependency-aware revision, contradiction resolution, and guarantees on memory growth and stability.  
%
Planning interfaces should likewise evolve into robust execution stages with lightweight validation and supervision, rather than relying on brittle schema enforcement or heavy orchestration. Recent work on automated specialist discovery further shows how agents can acquire persistent domain expertise through architectural search and experience-driven updates~\cite{vuautomated}. However, these approaches do not address how procedural knowledge should be versioned, audited, reverted, or validated against downstream failures, nor how conflicting or obsolete expertise should be safely revised. Designing specialized agents with explicit lifecycle management, correctness guarantees, and long-term stability remains an open challenge.\shorten


\smallskip
\noindent\textbf{Multi-Agent Coordination.}
The strong dependence of coordination success on communication topology suggests treating connectivity as an adaptive system component rather than a fixed framework choice. Recent work learns task-specific graph structures via reinforcement learning or input-conditioned selection to improve coordination~\cite{leong2025amas,li2025adaptive}. These methods show that no single topology is optimal across tasks and that dynamic structure selection can improve accuracy. However, they typically operate over predefined candidate graphs or offline-optimized structures, and do not provide runtime guarantees on convergence, stability, or cost as agent populations scale.  
%
Future frameworks should support online topology reconfiguration guided by explicit coordination objectives, bounded communication cost, and correctness-aware adaptation across interaction rounds. Developing principled mechanisms for dynamic connectivity control with scalability guarantees remains an open systems challenge.\shorten

\smallskip
\noindent\textbf{Multi-Agent System Automation.}
The architectural trade-offs exposed by MAFBench indicate that multi-agent system design should shift from manual framework engineering toward automated optimization. Future platforms should translate high-level task requirements into concrete orchestration, memory, planning, specialization, and coordination architectures, guided by empirical performance profiles and deployment constraints.  
%
We introduce \textbf{ORCA}\footnote{\vspace{-2mm}\faGithub\ \url{https://github.com/CoDS-GCS/ORCA}}, a step toward fully automating multi-agent system construction from high-level task descriptions. ORCA selects and configures multi-agent architectures using empirical benchmark evidence and cost-aware execution models. While emerging systems such as Agent Bricks~\cite{databricks_agentbricks} and Microsoft Fabric IQ~\cite{microsoft_fabric_iq} offer early automation primitives, they remain constrained to fixed architectural templates and limited design spaces. By treating multi-agent system construction as a compilation and optimization process, ORCA elevates engineering to a first-class stage between benchmarking and deployment, enabling continuous adaptation as tasks, models, and execution environments evolve.\shorten

