\section{Architectural Taxonomy}
\label{sec:taxonomy_analysis}

This section introduces our architectural taxonomy for multi-agent LLM frameworks. Architectural design choices shape control flow, agent abstraction, communication, memory, and execution semantics, with first-order impact on performance, robustness, and scalability. The taxonomy enables systematic, framework-level comparison independent of specific models or tasks. We begin with formal definitions of agents and multi-agent frameworks.




\input{tables/framework_comparison_table}


% \noindent\textbf{Definition 2.1 (Agent).}
% An agent is an autonomous computational entity 
% $a = (\mathcal{R}, \mathcal{Y}, \mathcal{P}, \mathcal{S}, \mathcal{T}, f)$,
% where $\mathcal{R}$ denotes specialization, $\mathcal{Y}$ denotes objectives, $\mathcal{P}$ specifies planning mechanisms, $\mathcal{S}$ denotes storage and knowledge resources, $\mathcal{T}$ denotes accessible tools or actions, and $f$ is a reasoning function that maps observations and stored information to actions. In this work, we focus on LLM-based agents, where $f$ is instantiated by a large language model.

\noindent\textbf{Definition 2.1 (Agent).}
An agent is an autonomous computational entity
$a = (\mathcal{R}, \mathcal{Y}, \mathcal{P}, \mathcal{S}, \mathcal{T}, f)$,
where $\mathcal{R}$ denotes specialization or role context, $\mathcal{Y}$ denotes objectives, $\mathcal{P}$ specifies planning mechanisms, $\mathcal{S}$ denotes storage and knowledge resources, $\mathcal{T}$ denotes accessible tools or actions, and $f$ is a reasoning function that maps observations and stored state to actions. We focus on LLM-based agents, where $f$ is instantiated by an LLM and other capabilities may be implemented at the model or framework level.

% \noindent\textbf{Definition 2.2 (Multi-Agent Framework).}
% A multi-agent framework is an architectural system 
% $\mathcal{F}=(\{a_i\}_{i=1}^{n}, \mathcal{O}, \mathcal{C}, \mathcal{E})$,
% where $\{a_i\}$ denotes a set of agents, $\mathcal{O}$ specifies orchestration and control flow, $\mathcal{C}$ defines inter-agent communication and connectivity, and $\mathcal{E}$ denotes an environment state with transition rules governing interactions.

\noindent\textbf{Definition 2.2 (Multi-Agent LLM Framework).}
A multi-agent LLM framework is an architectural system
$\mathcal{F} = (\{a_i\}_{i=1}^{n}, \mathcal{O}, \mathcal{C}, \mathcal{E})$,
where $\{a_i\}$ is a set of LLM-based agents. $\mathcal{O}$ specifies orchestration logic and control flow for agent execution. $\mathcal{C}$ defines the communication structure and connectivity among agents. $\mathcal{E}$ represents the shared environment with state and transition rules that mediate interactions.\shorten

% Building on these definitions, Table~\ref{tab:framework-comparison} presents a unified architectural taxonomy that organizes framework design choices along two complementary axes. The columns correspond to three architectural paradigms, namely graph-based, role-based, and Generative Agent-Based Modeling (GABM), which arise from fundamentally different execution models (Section~\ref{sec:background}). The rows group architectural decisions into three categories: single-agent characteristics, multi-agent characteristics, and environment representation (Section~\ref{Architectural_Decisions}). Together, these dimensions provide a common vocabulary for systematic comparison and clarify which architectural decisions are fixed by design within each paradigm versus emergent at runtime.

Our taxonomy, derived from Definitions~2.1--2.2 and shown in Table~\ref{tab:framework-comparison}, provides a unified architectural view of multi-agent LLM frameworks and is instantiated on the nine representative frameworks summarized in Table~\ref{tab:github-stats-updated}. It organizes framework design choices along two complementary axes: architectural paradigms (graph-based, role-based, and GABM), which reflect distinct execution models (Section~\ref{sec:background}), and architectural dimensions capturing single-agent characteristics, multi-agent interaction, and environment representation (Section~\ref{Architectural_Decisions}). Together, these dimensions provide a common vocabulary for distinguishing design-fixed and runtime-emergent decisions.



\input{sections/background}
\input{sections/Qualitative_Analysis_Single_Agent_Characteristics}
\input{sections/Qualitative_Analysis_roles_planning}
\input{sections/Qualitative_Analysis_storage}
\input{sections/Qualitative_Analysis_tools}


% \vspace{-2mm}
% \subsubsection{Multi-Agent Characteristics}
% We next examine how frameworks structure agent connectivity and interaction.
% \input{sections/Qualitative Analysis_network_topology}
% \input{sections/Qualitative Analysis_communication}
% \input{sections/Qualitative Analysis_collaboration}

% \vspace{-2mm}
\subsubsection{Multi-Agent Characteristics}
Multi-agent LLM frameworks structure agent interaction through connectivity, communication, and collaboration mechanisms that shape information flow, coordination, and collective behavior at runtime. As shown in Table~\ref{tab:framework-comparison}, differences in topology and communication models strongly constrain coordination, scalability, and joint reasoning.


\smallskip
\noindent\textbf{- Network Topology.}
This architectural dimension governs how agents are connected and how interaction paths are structured within a framework, thereby shaping which coordination patterns are feasible at runtime. Graph-based frameworks provide flexibility at design time by allowing developers to define explicit topologies encoded as directed graphs. These graphs can represent hierarchical, peer-to-peer, or cyclic structures~\cite{langgraph2025,autogpt2025}, but the resulting topology remains fixed during execution. Role-based frameworks induce topology implicitly through task decomposition and role assignments, typically resulting in sequential pipelines or manager--worker hierarchies with limited lateral interaction~\cite{crewai2025,wu2024autogen,openaiagents2025}. In contrast, GABM frameworks centralize interaction through an environment controller (Game Master), enforcing a star topology where agents interact only with the environment~\cite{vezhnevets2023generative}.


\noindent\textbf{- Communication Pattern.}
This architectural dimension governs how information is exchanged and propagated among agents during execution. In graph-based frameworks, communication is realized through deterministic state propagation along predefined edges in the execution graph, rather than through explicit message passing between agents~\cite{langgraph2025,n8n2025,langflow2025}. Role-based frameworks route communication primarily through task assignment, intermediate result passing, and reporting mechanisms embedded in hierarchical or sequential coordination structures~\cite{crewai2025,wu2024autogen,openaiagents2025}. GABM frameworks eliminate direct inter-agent messaging altogether, mediating all interaction through a shared environment that aggregates agent actions and produces new observations for subsequent reasoning~\cite{vezhnevets2023generative}.


\smallskip
\noindent\textbf{- Collaboration.}
This architectural dimension captures whether frameworks provide explicit mechanisms for agents to jointly coordinate decisions beyond procedural execution. Graph-based frameworks do not support first-class collaboration, relying entirely on procedural coordination enforced by predefined workflows. Role-based frameworks enable limited forms of collaboration through delegation, task handoff, and manager--worker coordination among role-specialized agents, but they generally lack support for multi-turn negotiation or collective decision-making protocols~\cite{crewai2025,wu2024autogen,openaiagents2025}. GABM frameworks similarly expose no explicit collaboration mechanisms, with collective behavior emerging indirectly from shared environment dynamics rather than from intentional or negotiated coordination among agents~\cite{vezhnevets2023generative,coordinationcollaborativereasoning}.



%%%%%%%%%%%
\input{sections/Qualitative_Analysis_enviroment}

% \subsubsection{Synthesis of Architectural Trade-offs}

% Across the architectural dimensions in Table~\ref{tab:framework-comparison}, framework design trades execution control and efficiency against behavioral flexibility and persistent state modeling. Graph-based architectures favor deterministic control flow and low-overhead coordination for predictable, scalable pipelines. Role-based architectures relax structural constraints to enable adaptive reasoning and specialization through declarative roles and task decomposition. GABM architectures shift coordination and memory into a shared environment, supporting emergent behavior and simulation-based study at the cost of higher execution overhead and reduced direct control. Together, these architectures represent distinct trade-offs between predictability, adaptability, and long-horizon state coherence in multi-agent systems.

% Importantly, architectural behavior arises from both framework abstractions and developer-defined execution structures, with common mechanisms often shared across systems. For instance, planning is explicit in role-based frameworks but procedurally embedded in graph workflows, while storage frequently relies on similar retrieval-based techniques across paradigms. Coordination is largely constrained by paradigm-level communication structure rather than specific APIs. Accordingly, our evaluation (Section~\ref{sec:eval}) isolates individual architectural choices through controlled instantiations rather than performing end-to-end framework comparisons, revealing how design decisions drive overhead, reasoning effectiveness, memory behavior, and coordination outcomes.

\vspace{-1mm}
\subsubsection{Synthesis of Architectural Trade-offs}

Across the architectural dimensions in Table~\ref{tab:framework-comparison}, framework design trades execution control and efficiency for behavioral flexibility and persistent state modeling. Graph-based architectures favor deterministic control flow and low-overhead coordination, supporting predictable and scalable pipelines. Role-based architectures relax structural constraints to enable adaptive reasoning and specialization through declarative roles and task decomposition. GABM architectures shift coordination and memory into a shared environment, supporting emergent behavior and simulation-based analysis at the cost of higher execution overhead and reduced direct control. Together, these architectures represent distinct trade-offs among predictability, adaptability, and persistent state coherence in multi-agent systems.

Architectural behavior reflects both framework abstractions and developer-defined execution structures, with many mechanisms shared across frameworks. For example, planning is explicit in role-based frameworks but embedded procedurally in graph workflows, while storage often relies on similar retrieval-based techniques across paradigms. Coordination is largely constrained by paradigm-level communication structures rather than specific APIs. Accordingly, our evaluation (Section~\ref{sec:eval}) isolates individual architectural choices, revealing how design decisions affect overhead, reasoning effectiveness, memory behavior, and coordination outcomes.\shorten

