\documentclass{article}

\PassOptionsToPackage{numbers, compress}{natbib}
\usepackage[preprint]{neurips_2025}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xspace}

\usepackage{subcaption}
\usepackage{caption}

\usepackage[pdftex]{graphicx}
\graphicspath{{images/}}
\usepackage{rotating}

\usepackage{lineno}
\usepackage{siunitx}
\usepackage{multirow} % for table
% for table
\usepackage{makecell}  % For line breaks in cells
\usepackage{array}     % For better column formatting
\usepackage{colortbl}
\usepackage[x11names]{xcolor} % loads more named colors like SkyBlue1

\usepackage{tikz}
\usetikzlibrary{positioning}
% \usetikzlibrary{shapes.geometric}

\definecolor{skyhex}{HTML}{4E95D9}  % Sky blue in hex
\definecolor{orangebox}{HTML}{FDE7D0}
\definecolor{greenbox}{HTML}{D9F2D0}
\definecolor{bluebox}{HTML}{D4F0EA}
\definecolor{highlightyellow}{HTML}{FFF59D}  % a soft yellow
\usepackage{enumitem}
\setlist[itemize]{left=0pt, itemsep=1mm, topsep=0pt, parsep=0pt, partopsep=0pt, align=left}

\usepackage[normalem]{ulem}
\usepackage{wrapfig}


\definecolor{darkblue}{rgb}{0, 0, 0.5}
\hypersetup{colorlinks=true, citecolor=darkblue, linkcolor=darkblue, urlcolor=darkblue}

\usepackage[most]{tcolorbox}   % For creating the colored boxes around prompts
\usepackage{listings}
\usepackage[newfloat]{minted}
\newenvironment{code}{\captionsetup{type=listing}}{}
\SetupFloatingEnvironment{listing}{name=Listing}
\usepackage{titletoc}
\usepackage{fontawesome, titlesec }
\usepackage{appendix}
% \lstset{
%   backgroundcolor=\color{blue!10}, 
%   basicstyle=\ttfamily,          
%   frame=none,                    
%   showstringspaces=false,  
%   breaklines=true,
%   keepspaces=true,
%   breakindent=0pt,
%   columns=fullflexible           
% }
% \newtcolorbox{promptbox}[1][]{%
%   colback=blue!10,
%   colframe=blue!30!black,
%   fonttitle=\bfseries,
%   title=#1,
%   sharp corners,
%   breakable,
%   fontupper=\small
% }

\tcbuselibrary{listingsutf8, breakable}
\newtcblisting{greylisting}[2][]{
    listing only,
    colback=gray!10,
    colframe=gray!50,
    breakable, 
    listing options={
        basicstyle=\ttfamily\footnotesize,
        breaklines=true,
        language=Python,
        showstringspaces=false,
        escapeinside={(*@}{@*)} 
    },
    left=2mm,
    right=2mm,
    top=1mm,
    bottom=1mm,
    fonttitle=\bfseries,
    coltitle=black,
    title={#2},
    label={#1}
}

\setlength{\abovecaptionskip}{1pt plus 0pt minus 1pt}
\setlength{\belowcaptionskip}{1pt plus 0pt minus 1pt}
\setlength{\abovedisplayskip}{1pt}
\setlength{\belowdisplayskip}{1pt}

\setlength{\abovedisplayshortskip}{1pt}
\setlength{\belowdisplayshortskip}{1pt}


\setlength{\textfloatsep}{0.3cm}

\newcommand{\rohan}{\textcolor{red}}

\newcommand{\safeagentsn}{{\sc SafeAgents}\xspace}

\newcommand{\metricn}{{\sc Dharma}\xspace}

\usepackage{verbatim}    % For verbatim environment that preserves formatting
\usepackage{float}       % For controlling figure placement with [h!]

\graphicspath{ {./images/} }

\title{Exposing Weak Links in Multi-Agent Systems under Adversarial Prompting}


\author{
  Nirmit~Arora\thanks{Equal contribution} \quad Sathvik~Joel\footnotemark[1] \quad  Ishan~Kavathekar \quad Palak \\ \textbf{Rohan~Gandhi \quad Yash~Pandya \quad Tanuja~Ganu \quad  Aditya~Kanade \quad Akshay~Nambi} \\
    Microsoft Research \\
    \texttt{\{nirmitarora26,ksjoe30\}@gmail.com} \\
    \texttt{ishan.kavathekar@research.iiit.ac.in} \\
    \texttt{palak.palak@epfl.ch} \\
    \texttt{\{rohangandhi,yashpandya,tanuja.ganu,kanadeaditya,akshay.nambi\}@microsoft.com}
}

\begin{document}
\maketitle
\begin{abstract}
LLM-based agents are increasingly deployed in multi-agent systems (MAS). As these systems move toward real-world applications, their security becomes paramount. Existing research largely evaluates single-agent security, leaving a critical gap in understanding the vulnerabilities introduced by multi-agent design. However, existing systems fall short due to lack of unified frameworks and metrics focusing on unique rejection modes in MAS.  We present \safeagentsn, a unified and extensible framework for fine-grained security assessment of MAS. \safeagentsn systematically exposes how design choices such as plan construction strategies, inter-agent context sharing, and fallback behaviors affect susceptibility to adversarial prompting.  We introduce \metricn, a diagnostic measure that helps identify weak links within multi-agent pipelines. Using \safeagentsn, we conduct a comprehensive study across five widely adopted multi-agent architectures (centralized, decentralized, and hybrid variants) on four datasets spanning web tasks, tool use, and code generation. Our findings reveal that common design patterns carry significant vulnerabilities. For example, centralized systems that delegate only atomic instructions to sub-agents obscure harmful objectives, reducing robustness. Our results highlight the need for security-aware design in MAS. Link to code is \href{https://github.com/microsoft/SafeAgents}{https://github.com/microsoft/SafeAgents}.
\end{abstract}


% keywords can be removed
%\keywords{First keyword \and Second keyword \and More}


\input{introduction}

\input{related_work}

\input{background}

\input{methodology}

\input{research_questions}

\input{conclusion}

\bibliography{references}
\bibliographystyle{abbrvnat}

\begin{appendices}
\appendixpage



\input{rq2_app}

\input{prompts}
\end{appendices}



\end{document}
\typeout{get arXiv to do 4 passes: Label(s) may have changed. Rerun}