\subsection{How do different architectures compare to each other in terms of safety?}

Table~\ref{tab:eval:results} shows the main results comparing single agent, centralized and decentralized agentic systems. 


\textbf{1) Centralized MAS are not inherently safer than single-agent setups.} In several benchmarks, centralized MAS exhibits higher attack success rates than the single-agent baseline. For example, ARIA 4 in case of Magentic Centralized rises from 62.5\% to 83.70\% in RedCode and from 81.5\% to 92.52\% in ASB compared to ReAct. This suggests that strong planning and execution capabilities in MAS can fully realize harmful goals when model alignment fails to flag unsafe prompts. Our results indicate that a single orchestrator may propagate undetected harmful intent more efficiently than a single-agent or decentralized system.

\textbf{2) Decentralized MAS  perform better in context-heavy tasks.} Swarm, For example, achieves lower ASR in SafeArena (15.85\%) and outperforms Centralized Magentic in RedCode~(73\% vs. 83.70\%). Similarly, Decentralized Langraph, achieves lower ASR in SafeArena~(17.6\%) compared to Single-Agent and Other centralized MAS. This is likely because individual agents (e.g., Coder, WebSurfer) have full context and can independently reject unsafe actions. However, this is domain dependent and does not generalize to all types of tasks.


\textbf{3) Implementation choices within the same architectural family create substantial security variations}. Even when frameworks share the same fundamental architecture (centralized  or decentralized), their specific design primitives—such as planning strategies, subagent autonomy levels, and context organization—lead to dramatically different vulnerability profiles. For instance, among centralized systems, Magentic achieves 83.70\% ARIA 4 in RedCode while other centralized implementations Langraph and OpenAI significantly show varying ARIA 4 results, demonstrating that architectural category alone is insufficient for predicting security outcomes. This reinforces that security in MAS depends critically on granular implementation details rather than just high-level architectural patterns.


