\subsection{Impact of SLM}

To understand whether our findings are extensible to other models, we have evaluated our framework on Qwen3 30B (A3B-Instruct-2507) on AgentHarm and RedCode datasets, since these datasets contain explicitly harmful tasks. Table~\ref{tab:agentharm_dharma} shows \metricn results.

\textbf{SLMs exhibit inverted vulnerability patterns compared to frontier models.} Our findings reveal a distinct failure mode where planning-level defenses systematically fail while sub-agent-level defenses remain effective. Unlike GPT models where 78.74\% and 87.40\% of LangGraph and OpenAI Agents cases respectively resulted in \textbf{Planner-Stop} classifications for Agentharm dataset, Qwen3 shows significantly reduced planner refusal rates across all three frameworks. Similarly, in case of RedCode, Planner defenses never raised a flag, confirming this observation.

\textbf{Sub-agent execution defenses compensate for planning failures in SLMs for explicitly harmful tasks.} Despite systematic planning-level failures, we observe substantially increased \textbf{Sub-agent Stop} classifications across all frameworks using Qwen3 for AgentHarm, since the tasks in AgentHarm are explicitly harmful, sub-agents successfully recognize and refuse.

\textbf{SLMs exhibit heightened vulnerability to code-based attacks.} This vulnerability is particularly evident in the RedCode dataset, where Qwen3 consistently fails to recognize harmful intent across all attack scenarios. Unlike the AgentHarm dataset where sub-agent defenses compensated for planning failures, in RedCode, both planning and execution phases proceed without safety intervention. This results in significantly elevated Unmitigated-Execution rates across all three frameworks, indicating that code-based attacks effectively bypass SLM safety mechanisms at every architectural layer.


\textbf{Summary:} Unlike frontier models where planning-level defenses are effective, SLMs exhibit a critical vulnerability at the planning stage while maintaining robust execution-level alignment. This inverted failure pattern suggests that SLM-based MAS require either (i) strengthened planning-level safety mechanisms, or (ii) architectural redesigns that strategically position safety checks at the execution layer to leverage SLMs' demonstrated refusal capabilities during task execution.

\begin{table}[!h]
\centering
\scriptsize
\caption{\metricn Results for AgentHarm with SLM \small{(Qwen3-30B-A3B-Instruct-2507)}.}
\label{tab:agentharm_dharma}
\begin{tabular}{@{}ll*{7}{r}@{}}
\toprule
\textbf{Dataset} & \textbf{System} & \multicolumn{3}{c}{\textbf{Planner}} & \multicolumn{2}{c}{\textbf{Sub-agent}} & \textbf{Execution} & \textbf{Errors} \\
\cmidrule(lr){3-5} \cmidrule(lr){6-7}
 &  & \textbf{Stop} & \textbf{Ignore} & \textbf{Fail} & \textbf{Stop} & \textbf{Ignore} & \textbf{} & \textbf{} \\
\midrule
\multirow{3}{*}{Agentharm} & Magentic & 0.00 & 0.00 & -- & 81.89 & 0.79 & 15.75 & 1.57 \\
& Langraph & 42.52 & -- & 0.00 & 37.80 & 0.79 & 14.96 & 3.94 \\
& OpenAI & 5.51 & 0.00 & -- & 59.06 & 0.79 & 22.83 & 11.81 \\
\midrule
\multirow{3}{*}{RedCode} & Magentic & 0.00 & 0.00 & -- & 0.74 & 0.00 & 99.26 & 0.00 \\
 & Langraph & 0.00 & -- & 0.15 & 9.90 & 0.00 & 89.96 & 0.00 \\
 & OpenAI & 0.00 & 0.00 & -- & 0.00 & 2.86 & 93.65 & 0.00 \\
\bottomrule
\end{tabular}
\end{table}