\begin{abstract}
The dawn of embodied intelligence has ushered in an unprecedented imperative for resilient, cognition-enabled multi-agent collaboration across next-generation industrial ecosystems, revolutionizing paradigms in autonomous manufacturing, adaptive service robotics, and cyber-physical production architectures.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
However, current robotic systems face significant limitations, such as limited cross-embodiment adaptability, inefficient task scheduling, and insufficient dynamic error correction.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
While End-to-end Vision Language Action (VLA) models demonstrate inadequate long-horizon planning and task generalization, hierarchical VLA models suffer from a lack of cross-embodiment compatibility and multi-agent coordination capabilities.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
To address these challenges, we introduce \textit{\textbf{RoboOS}}, the first open-source embodied system built on a \texttt{Brain-Cerebellum} hierarchical architecture, enabling a paradigm shift from single-agent to multi-agent intelligence.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Specifically, \textit{\textbf{RoboOS}} consists of three key components: \textit{\textbf{(1) the Embodied Brain Model (RoboBrain)}}, a multimodal large language model (MLLM) designed for global perception and high-level decision-making; \textit{\textbf{(2) the Cerebellum Skill Library}}, a modular, plug-and-play toolkit that facilitates seamless execution of multiple skills; and \textit{\textbf{(3) Real-Time Shared Memory}}, a spatiotemporal synchronization mechanism for coordinating multi-agent states.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
By integrating hierarchical information flow, RoboOS bridges the Embodied Brain and the Cerebellum Skill Library, facilitating robust planning, scheduling, and error correction for long-horizon tasks, while ensuring efficient multi-agent collaboration through Real-Time Shared Memory.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Furthermore, we enhance edge-cloud communication and cloud-based distributed inference to facilitate high-frequency interactions and enable scalable deployment.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Extensive real-world experiments across various scenarios, such as \texttt{restaurants, households, and supermarket settings}, demonstrate RoboOS's versatility in supporting heterogeneous embodiments, including \texttt{single-arm, dual-arm, humanoid, and wheeled}.
This capability offers a scalable and practical solution for cross-embodiment collaboration, advancing the frontiers of embodied intelligence.
Project website: \href{https://github.com/FlagOpen/RoboOS}{RoboOS}.
\end{abstract}

% Two or three meaningful keywords should be added here
\keywords{Embodied System, Multi-Robot Collaboration, Cross-Embodiment} 