\section*{Acknowledgments}
\label{sec:acknowledgements} 
This research was supported by Saint-Gobain (Northboro Research and Development Center, United States). 
%
I.A.S. acknowledges that this material is based upon work supported by the U.S. Department of Energy, Office of Science, Office of Advanced Scientific Computing Research, under Award Number DE-SC0026073. T.P.H. acknowledges that this material is based upon work supported by Aker Scholarship.
%
We acknowledge valuable discussions with Lalitha Raghavan and Amir Kazemi-Moridani (both Saint-Gobain), whose contributions in identifying key PFAS material property keywords that shaped our corpus, maintaining the industrial relevance of the project, and guiding prospective experimental directions were instrumental to this work.

\section*{Author Contributions}
\label{sec:contributions}

M.J.B. supervised the project and led the research design and development. I.A.S. collected the data corpus, conceived the multi-agent framework and inference code, developed application of graph traversal methods, and carried out data analysis. T.P.H. conducted ablation studies on the multi-agent framework, performed the associated analyses, and contributed to data analysis. Y.-C.H. generated the knowledge graphs and performed data analysis. I.A.S. prepared the initial draft of the manuscript with contributions from T.P.H. All authors contributed to editing and finalizing the manuscript.

\section*{Competing Interests}
\label{sec:competingInterests}
The authors declare no competing interests.

\section*{Code and Data Availability}
\label{sec:codeAvailability}
All code, protocols, datassets, and notebooks developed in this study are available at: \url{https://github.com/lamm-mit/GraphAgents} . This repository also hosts supplementary files with the full agent outputs referenced in this manuscript.