\section{Related Work}
\label{sec:related}

\paragraph{Reasoning, reflection, and search.}
Methods such as ReAct~\cite{react2023}, Self-Refine~\cite{selfrefine2023}, Reflexion~\cite{reflexion2023}, and Tree-of-Thoughts (ToT)~\cite{tot2023} improve reasoning by coupling tool use, iterative self-feedback, episodic memory, or backtracking search. Agent-R~\cite{agentr2025} and recent surveys~\cite{guo2024survey} highlight reflection as central to multi-agent LLMs. Unlike these approaches, \method\ uses an \emph{explicit probabilistic controller}: Thompson sampling delegates under uncertainty, while binary judge outcomes update interpretable Beta posteriors that drive re-routing.

\paragraph{Orchestration, ensembles, and routing.}
Frameworks such as AutoGen~\cite{autogen2023} coordinate agents via scripted protocols, and Mixture-of-Agents (MoA)~\cite{moa2024} aggregate outputs via ensembles. Early orchestrators (e.g., LangChain graphs, AutoGPT workflows) hard-code pipelines, while systems like RopMura~\cite{ropmura2025}, DyLAN~\cite{dylan2023}, and MLPO~\cite{mlpo2025} introduce dynamic routing with agent team optimization. In contrast, \method\ performs online belief-guided delegation without retraining, maintaining efficiency and decentralization.

\paragraph{Learning-based coordination.}
Multi-agent reinforcement learning has long addressed coordination~\cite{lowe2017multi,foerster2018counterfactual}, with adaptations for LLMs such as SWEET-RL~\cite{zhou2025sweetrl}. Yet RL methods are sample-hungry. Probabilistic approaches, e.g., Bayesian Delegation~\cite{Wu21}, estimate expertise from sparse data. \method\ combines Thompson sampling with reflection-driven control,
cooldown-based exploration, and memory-aware priors in a unified,
training-free orchestration loop.

\paragraph{Benchmarks and positioning.}
Public environments (WebArena~\cite{webarena2023}, Mind2Web~\cite{mind2web2023}, GAIA~\cite{gaia2023}, SWE-bench~\cite{swebench2023}) highlight the difficulty of real-world, long-horizon tasks (e.g., GPT-4 achieves $\sim$14\% on WebArena vs.\ humans at $\sim$78\%). Against this backdrop, \method\ contributes a training-free adaptive controller that combines belief-guided delegation, embedded reflection and memory to improve efficiency, robustness and interpretability over static, ensemble or RL-based approaches.
