

Large language models (LLMs) have achieved remarkable success in recent years. Yet, most LLMs are trained on open-domain data before fixed cut-off dates ~\cite{gpt2}, which inevitably limits their performance when facing domain-specific questions due to outdated or missing knowledge. To address this issue, Retrieval-Augmented Generation (RAG) ~\cite{replug, graphrag} has emerged as a promising solution, where relevant knowledge is retrieved and incorporated to help LLMs generate accurate responses. 
Most existing GraphRAG methods ~\cite{graphrag,gretriever} rely on a simple yet strong assumption, that the generated response should include all relevant facts retrieved from the graph. However, this assumption overlooks a critical problem: the retrieved textual graph might contain unnecessary noise or irrelevant information.
Consider Figure ~\ref{example}(a), where a user asks “What is a good source of nutrients for a mushroom?” While the textual graph contains correct 'a cut peony', it also contains useless information 'a flying eagle' which may mislead the model. 
How to mitigate low-quality information from the retrieved textual graph to effectively guide answer generation is a problem.
Furthermore, existing GraphRAG methods mainly utilize zero shot learning. Selecting
high-quality demonstrations is crucial for improving reasoning and answer accuracy.

In this paper, we propose a GraphRAG framework that focuses on enhancing both textual graph understanding and QA performance by learning to select high-quality demonstrations and query specific information learning. 
Instead of assuming all retrieved subgraph content is useful, our approach adaptively identifies the most informative and context-relevant node-level and edge-level evidence. 
Specifically, we design a specialized, query-specific GraphEncoder to model the complex interactions between nodes within the retrieved subgraphs. 
This encoder generates a dense graph prompt embedding that captures relational patterns and serves as a bridge between structured knowledge and the LLM’s input space. 
Additionally, we incorporate a Mixture-of-Experts (MoE) ~\cite{deepseekmoe} paradigm to select the most informative demonstrations to enhance in-context learning. 
We evaluate our method on the GraphQA benchmark. Extensive experiments show that our model significantly outperforms existing baselines. 

