\section{Incentives and Adversarially-behaving Agents}\label{app:behavior}

In multi-agent systems, the interplay between incentives and adversarial behavior significantly influences how agents interact and collectively function. Malicious agents pose a substantial risk by potentially undermining collective outcomes through tactics such as data or communication "poisoning." To mitigate these threats, robust defensive measures, including credibility or trust scores, are crucial for limiting the negative influence of adversarial agents. Carefully structured incentive mechanisms can either promote cooperation when agents share common objectives or effectively regulate the influence of self-interested agents with differing goals on the final outcome.

A multi-agent system requires mechanisms to assess reliability, reward trustworthy behavior, and penalize dishonest or consistently erroneous agents. This approach ensures that agents engaging in malicious or detrimental actions gradually lose their ability to influence collective decisions. Similar to human social dynamics, we propose that Large Language Model (LLM) agents also adopt distinct roles and vary in their levels of influence within a collaborative group.

To systematically evaluate an agent's significance in collaborative scenarios, we introduce the Contribution Score (\textit{CSc}). Inspired by the Shapley value—originally employed to measure the importance of individual features in linear regression tasks—the Contribution Score quantifies the impact each agent has on the group's overall performance \cite{shap}. While this metric effectively captures an agent's overall influence within the group, it does not inherently differentiate between positive and negative contributions. Consequently, an agent can attain a high Contribution Score despite disseminating adversarial or misleading information, adversely affecting the group's final outcomes. 
To effectively address this challenge, we introduce the \textit{Credibility Score} (\textit{CrS}), which is initially assigned uniformly across all agents and dynamically evolves throughout successive iterations, serving as an agent profiling mechanism. 
