\section{Coordination Mechanisms}\label{app:coord}
% \abol{this section should talk about different aggregation strategies including majority vote, centroid-based, and llm-based aggregation (and others). Please update the content accordingly }



In multi-agent systems, coordination mechanisms determine how individual agents' outputs are integrated. %and how agents collaborate to accomplish tasks effectively. 
A critical component of coordination is the aggregation approach, which may include techniques such as majority voting, weighted averaging, or the utilization of specialized coordinator agents responsible for synthesizing multiple agent solutions into a cohesive outcome. In the following we briefly discuss each method.

\paragraph{Majority Voting}
 Each LLM agent produces an answer, and the ensemble selects the option most frequently proposed. In both self‑consistency decoding where multiple independent samples from a single model—and true multi‑model ensembles, majority vote reliably boosts accuracy because uncorrelated errors are out‑voted by repeated correct answers~\cite{self-consistency}. Its effectiveness scales with the number of agents, allowing a group of small LLMs to rival a single larger model~\cite{more-agents}. However, previous studies indicate that when adversarial or malicious behaviors are present in at least half ($N/2$) of the agents in a group of size $N$, traditional aggregation methods like majority voting become considerably less effective \cite{more-agents, multiagent-debate-attack}.


\paragraph{Weighted Averaging}
A generalization of majority vote assigns each agent a reliability weight, and the ensemble picks the answer backed by the highest total weight from all agents. Systems such as ReConcile~\cite{reconcile} and Boosted Prompt Ensembles~\cite{boosted-prompt} show that emphasizing historically accurate agents achieves higher overall accuracy and partial robustness to noisy or malicious peers. However, performance hinges on correct weight estimation; if adversaries obtain high weights, they can still dominate the ensemble.

\paragraph{Similarity-Based Ensemble}


Rather than relying on explicit voting, similarity-based ensemble methods select the response that is most semantically aligned with all others, assuming that the correct answer will form the tightest consensus cluster. Smoothie \cite{smoothie} and Agent-Forest \cite{more-agents} operationalize this by embedding candidate answers into a vector space and choosing the one with the lowest average distance to its peers, achieving strong performance without the need for supervised weights. These approaches naturally filter out outliers but remain vulnerable to coordinated adversarial agents that produce highly similar incorrect responses.

\paragraph{Centroid-based Aggregation} 
Ebrahimi et al. \cite{requal} extend similarity-based ensemble by combining weighted averaging with similarity-based selection. They propose a Monte Carlo-based strategy that selects the response closest to a weighted centroid of all answers, where the weights $w_i$ reflect the agents' reliability. 
The centroid vector, $\vec{x}^+$, is computed as a weighted average of the generated responses in the embedding space, i.e., $\vec{x}^+ = \frac{1}{|R|}\sum_{i=1}^{|R|} w_i.\vec{v}(x_i)$. Then, the final answer is identified as
\begin{equation}
x^{\star}=\arg\min_{x\in R} d(\vec{v}_x,\vec{x}^+)
\end{equation}
where $d(\cdot,\cdot)$ is the cosine distance between embeddings.
In our work, we adopt this aggregation method in a no inter-agent communication setting, using credibility scores as weights to guide the centroid-based coordination process.

\paragraph{LLM-based Coordination}

Recent works suggest that an llm-based \textbf{coordinator agent} is an effective aggregation mechanism for multi-agent systems. \cite{MA-LLM-debate} show that letting the agent debate before a coordinator renders the final verdictcan improve the overall accuracy. Yet, they warn that malicious participants may still steer the group toward suboptimal answers. Subsequent studies explore two types of task distribution paradigms: i) \textbf{redundant solving}, where the agents tackle same prompt to gain robustness through majority consensus and ii) divide-and-conquer where a complex task is broken into subtasks whose answers must be carefully integrated. In both setting a coordinator (or a manager) LLM synthesises the individual responses into a coherent final answer, mitigating inconsistencies and guarding local errors.
This manager-style coordination has been adopted in recent multi-agent LLM frameworks such as \cite{CoA} and \cite{MoA}, which report higher overall accuracy and improved resilience to adversarial or noisy agents compared with uncoordinated ensembles.

% oreover, research by \cite{MA-LLM-debate} highlights that employing debate among agents can significantly enhance collective decision-making. Yet, in adversarial contexts, there remains a substantial risk that malicious behaviors may lead agents toward incorrect or suboptimal conclusions. Another essential consideration involves task distribution strategies: agents may either collectively address the same task—typically enhancing robustness through redundancy or decompose complex problems into specialized subtasks that require careful integration to ensure accurate and effective final outcomes. For such scenarios, a coordinator agent provides an effective approach to aggregating individual solutions to subtasks into a coherent and reliable final outcome. The idea of a coordinator or a manager agent that produces the final response in a multi-agent setting has been previously practiced by \cite{CoA, MoA}  


% \abol{integrate the following to the text. Read section 3}

% \subsection{Standalone Agent Architecture (SAA)}
% In SAA all agents receive $Q$ and produce responses \emph{without communicating}.  The communication graph is therefore an edgeless graph $G=(\mathcal{A},\emptyset)$.  We use weighted aggregation \cite{requal} to pick the team answer
% \begin{equation}
% x^{\star}=\arg\min_{x\in R} d(v_x,v_c)
% \end{equation}
% where $d(\cdot,\cdot)$ is the cosine distance between embeddings, and the centroid vector, $v_c$, is the Credibility‑weighted mean of the response vectors:$\vec{v}_c = \frac{1}{|R|}\sum_{i=1}^{|R|} w_i\,\vec{v}(x_i),\quad w_i\propto\operatorname{CrS}^{(i)}$.  \ref{eq:csc}\ref{eq:crs} are then evaluated with $f$ defined over $R$.

% ,\quad w_n\propto\operatorname{CrS}^{(n)},
% \begin{equation}
% x^{\star}=\arg\min_{x_i\in R} w_i d(x,x_n),\quad w_n\propto\operatorname{CrS}^{(n)},
% % \end{equation}
% \subsection{Stochastic Interaction Architecture (SIA)}
% SIA introduces a random, sparse communication graph $G_t$. The topology is resampled for every query by selecting $m$ undirected edges from the $\binom{N}{2}$ possible edges.  Agents connected by an edge exchange their current answers and may revise them.  This design injects diversity while preventing full information saturation that would otherwise aid adversaries. 


% \subsection{Why Two Architectures?}
% SAA provides a lower bound on performance—no interactions means no adversarial persuasion—while SIA explores the hard regime where adversaries may form majorities and hijack discussions.  Experiments in \S\ref{sec:experiments} demonstrate that CSc/CrS significantly improve robustness in both settings.