\section{Related Work}\label{app:related}
% \abol{update...}

As large language models (LLMs) continue to exhibit impressive capabilities in text comprehension \cite{llm-in-edu}, language generation, and reasoning \cite{reasoning-llm}, there is an increasing inclination to treat them as autonomous \underline{agents}, akin to humans. This perspective is reinforced by their ability to demonstrate human-like social behaviors that align with foundational theories in social psychology \cite{llm-human-agent}. However, despite these advancements, numerous studies \cite{llm-in-edu, long-text-qa, survey-llm-shortcomings, CoA} highlight persistent challenges in key areas, including mathematical reasoning, coding, and complex logical inference, as well as difficulties in processing long texts and generating extended narratives.

% \mohsen{Context and Motivation:}

To overcome these limitations and improve factuality and reasoning, researchers have increasingly explored \underline{collaborative} problem-solving among multiple LLM agents rather than relying on a single model \cite{long-text-qa, survey-llm-shortcomings, MALLM-survey, MALLM-survey-2}. Similar to human teams that enhance their performance through collaboration, discussion, and iterative refinement, recent studies investigate whether LLMs can benefit from cooperative interactions. This paradigm shift leverages collective intelligence among LLM agents, allowing them to divide complex problems into manageable subtasks, particularly for more demanding and intricate problems. In these works, multiple LLM agents have been assembled to improve task performance through structured debate \cite{MA-LLM-debate, improving-fact-llm, div-think-llms} or ensemble methods \cite{more-agents}. 

% \mohsen{Context and Motivation:}

Research in multi-agent LLM systems has yielded significant advancements, leading to the development of powerful frameworks such as CAMEL, AutoGen, and MetaGPT \cite{autogen, metagpt, camel}. These systems have demonstrated promising performance in crucial domains, including coding, mathematical problem-solving, and collaborative decision-making among multiple agents.

% \mohsen{Context and Motivation:}

Despite these advancements, multi-agent LLM systems introduce inherent risks. If a subset of agents within the team is compromised—whether through poisoning attacks or adversarial intent—the collective output of the system can be corrupted. LLM agents are susceptible to persuasion, potentially leading them to reach incorrect consensus within the group. While previous studies \cite{psysafe, multiagent-debate-attack, MALLM-survey-2} have identified this vulnerability, existing solutions are primarily designed for specific, predefined architectures. 

% \mohsen{Existing solutions:}

This approach enhances prior multi-agent methods like the one by \citet{w_based_voting}, which used adversarial debate and credibility-weighted voting to reduce hallucinations. Instead of relying solely on inter-model disagreement, each LLM agent in this framework first undergoes internal self-refinement: tracking its own errors, measuring variance across multiple responses, and triggering self-reflection if thresholds are exceeded. Only after this process do agents engage in weighted voting, with conflicting outputs resolved through chain-of-thought comparisons. A final summarizing model then verifies consistency and coherence across agents. While this multi-phase design aims to improve robustness and factual accuracy, it implicitly assumes cooperative agents, making it vulnerable in adversarial settings. Moreover, the reliance on a summarization model that is stronger than the regular agents for final validation raises the question of why the task isn’t delegated to that model entirely.

% \mohsen{Research Gap:}

To the best of our knowledge, {\em there is currently no general framework that enables users to design robust multi-agent systems resilient to adversarial influence while minimizing the impact of such attacks without the need to eliminate an agent}.

% \mohsen{Existing solutions:}

One approach, proposed by \cite{DyLAN}, introduces a query-based method to dynamically select the most influential agents within a multi-step feedforward network. However, this method relies on agents evaluating both themselves and their peers to assign \textit{Agent Importance Score}, making it particularly vulnerable in adversarial settings where malicious agents can manipulate the selection process and consensus within the group. 

% \mohsen{Existing solutions:}
In summary, existing literature proposes various coordination mechanisms—such as weight-based voting, expert specialization, and moderated debate—to improve robustness against adversarial agents, showing promising initial results~\cite{w_based_voting, div-think-llms}. %\mohsen{Gap:}
However, no single solution effectively addresses all adversarial conditions; these mechanisms may still fail when adversaries form the majority or when the moderating model lacks significant superiority over adversarial agents.


