
\subsection{Efficiency Study}
\label{sec:efficiency}

To evaluate the computational efficiency of \model, we compare it with representative pretrained LM-based time series methods under a unified experimental setting. All measurements are conducted on the forecasting task of the ETTh1 dataset with an input length of 96 and a prediction length of 96. We report the number of trainable parameters, peak GPU memory consumption, end-to-end training time per epoch, and inference latency per batch. \model uses an instruction-following VLM interface (\textit{Qwen3-VL-235B-Instruct} by default) by default for anchor extraction to balance output quality and efficiency. %All experiments are performed on a single NVIDIA RTX 4090 GPU with batch size 32.

%\input{tables/efficiency}
\begin{table}[tbp]
\caption{Efficiency comparison between MAS4TS and pretrained LM-based time-series baselines on ETTh1 forecasting ($L{=}96$, $H{=}96$). We report trainable parameters, peak GPU memory, training time per epoch, and inference latency per batch. MAS4TS variants use \textit{Qwen3-VL-235B-Thinking} (Thinking) and \textit{Nano-Banana} (Generative), and the baselines use GPT-2 as the text encoding.}
  \label{tab:all_efficiency}
  \vskip 0.05in
  \centering
  \resizebox{0.95\columnwidth}{!}{
  \begin{threeparttable}
  \setlength{\tabcolsep}{4pt}
  \begin{tabular}{lcccc}
    \toprule
    Models & Params (M) & Mem (GB) & Train (s) & Infer (ms) \\
    \midrule
    \textbf{MAS4TS} & \textbf{5.38} & \textbf{0.05} & \textbf{24.55} & \textbf{90.49} \\
    \quad - Thinking & 5.38 & 0.05 & 35.98 & 133.75 \\
    \quad - Generative & 5.38 & 0.05 & 915.92 & 2767.01 \\
    \hline
    Time-VLM & 151.58 & 0.72 & 319.67 & 1067.14 \\
    UniTime$^\dagger$ & 107.32 & 5.18 & 53.49 & 165.77 \\
    TimeLLM$^\dagger$ & 134.90 & 15.96 & 853.75 & 2296.28 \\
    \bottomrule
  \end{tabular}
  \begin{tablenotes}
    \footnotesize
    \item[*] Experiments conducted on NVIDIA 4090 with batch size 32. 
    \item[*] The $\dagger$ represents the deployment and inference of local LMs, while we reason through the EAS API.
  \end{tablenotes}
  \end{threeparttable}
  }
  \vspace{-4mm}
\end{table}

Table~\ref{tab:all_efficiency} summarizes the efficiency comparison results. Although \model integrates a multi-agent workflow with foundation models, it maintains a compact backbone (5.38M parameters) and extremely low peak GPU memory footprint (0.05\,GB), which are orders of magnitude smaller than pretrained LM-based methods such as Time-VLM, UniTime, and TimeLLM. Concretely, these baselines involve over $100$M parameters and consume several to tens of gigabytes of GPU memory, whereas \model keeps the learnable core lightweight and invokes the VLM only when needed, in a mini-batched and parallel manner across samples. Default \textit{Instruct-style} anchoring provides the best efficiency-quality trade-off and extracts anchors using a structured, schema-constrained interface that avoids long, free-form decoding, while both thinking and generative variants introduce heavier reasoning overhead.
The results indicate that the practical efficiency of \model comes primarily from lightweight coordination plus structured tool usage, rather than scaling a monolithic architecture.