 Knowledge Graph Question Answering (KGQA) has largely focused on \textit{entity-centric} queries that return a single answer entity. However, many real-world questions are inherently relational, aiming to understand how entities are associated rather than which entity satisfies a query.
In this work, we introduce \textit{relation-centric} KGQA, a complementary setting in which the answer is a subgraph that represents the semantic relations among entities. The main challenge lies in the abundance of candidate subgraphs, where trivial or overly common connections often obscure the identification of unique and informative answers. 
To tackle this, we propose \textit{UniRel}, a unified modular framework that combines a subgraph retriever with an LLM fine-tuned using reinforcement learning. The framework uses a reward function to prefer compact and specific subgraphs with informative relations and low-degree intermediate entities.
Experiments show that UniRel improves connectivity and reward over Prompting baselines and generalizes well to unseen entities and relations. Moreover, UniRel can be applied to conventional entity-centric KGQA, achieving competitive or improved performance in several settings.





% Knowledge Graph Question Answering (KGQA) has traditionally focused on \textit{entity-centric} queries that return a single answer entity. 
% However, real-world queries are often relational, seeking to understand how entities are associated.
% In this work, we introduce \textit{relation-centric} KGQA, a complementary setting where the answer is a subgraph capturing the semantic connections among entities rather than an individual entity. 
% The main challenge lies in the abundance of candidate subgraphs, where trivial or overly common connections often obscure the identification of unique and informative answers. 
% To tackle this, we propose \textit{UniRel-R1}, a unified framework that integrates subgraph selection, multi-stage graph pruning, and an LLM fine-tuned with reinforcement learning. The reward function is designed to encourage compact and specific subgraphs with more informative relations and lower-degree intermediate entities.
% Extensive experiments show that UniRel-R1 achieves significant gains in connectivity and reward over Prompting baselines and generalizes effectively to unseen entities and relations.





% We propose a new framework XXX, which includes three modules: subgraph selection, graph pruning and a tuned LLM. We use reinforcement learning to finetune the LLM to better understand how informative a path is. Empircal results show that xxx can achieve xxxx. Further analysis prove that our method can generalize to unseen tasks.