\section{Planning in $\rho$Dec-POMDPs}
\label{sec:planning}
A planning algorithm for standard Dec-POMDPs can be applied to $\rho$Dec-POMDPs if it does not rest on the assumption that the reward is state and action dependent only.
For instance, approaches that cast the problem as a search through the joint policy space $\Pi_h$ can be applied once reward function evaluation is modified appropriately.
For example, variants of generalized multi-agent A* algorithms~\cite{Oliehoek2008} are applicable.

We applied the multi-agent A* (MAA*) algorithm~\cite{Szer2005}.
MAA* is a heuristic search algorithm similar to the classic A* algorithm.
Starting with $t=1$, MAA* constructs a search tree over partial joint policies $\phi_t = (\delta_0, \delta_1, \ldots, \delta_{t-1})$ with $t < h$ that specify how the agents act until time step $t$.
Thus, each node in the search tree represents a partial joint policy.
The search tree is expanded to cover the partial joint policies $\phi_{t+1}$ by appending to $\phi_t$ any possible joint decision rule: $\phi_{t+1} = (\phi_t, \delta_t)$.
The tree is expanded in a best-first order, as determined by a value estimate of the nodes currently in the tree.
The value estimate $\hat{V}(\phi_t)$ of a node with partial joint policy $\phi_t$ is computed in two parts: by exact evaluation of $\phi_t$ plus an estimate of the value of the remaining $h-t$ time steps via a heuristic function $H_{h-t}$: $\hat{V}(\phi_t) = V(\phi_t) + H_{h-t}(\phi_t)$.
Here, $V(\phi_t)$ is the value of $\phi_t$ computed via Eq.~\eqref{eq:rhodecpolicy_value}, and $H_{h-t}(\phi_t)$ is the heuristic value. % of the node.
If $H_{h-t}$ overestimates the true expected reward over the remaining $h-t$ time steps, MAA* returns an optimal policy~\cite{Szer2005}.

To define a heuristic function, the Dec-POMDP is relaxed, e.g., into a centralized POMDP, or into a fully observable centralized Markov decision process (MDP)~\cite{Oliehoek2008}.
The heuristic function is obtained, e.g., in the case of POMDP relaxation, by finding the optimal value of the POMDP.
We apply heuristic functions obtained via a POMDP relaxation.
This preserves the uncertainty aspect in the problem, and the optimal value can be computed even for information-theoretic reward functions by existing techniques~\cite{Araya2010}.